### 2024-01-01 Advice Giving.Rmd
Uploding the first draft

---
title: "Interpersonal Benefits of Flattering Advice"
shorttitle        : "Flattering Advice"
author: 
  - name          : "Amanda Chen"
    affiliation   : "1"
    corresponding : yes    
    email         : "zchengj@connect.ust.hk"
    address       : "Department of Management, The Hong Kong University of Science and Technology, Hong Kong"
  - name          : "David Hagmann"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "The Hong Kong University of Science and Technology"
note : |
  `r format(Sys.time(), "%e %B, %Y")`
authornote : |
  The authors are grateful to a lot of things.
abstract: |

  This is an interesting project! Please read through it!
keywords          : "Gender difference, Advice, Interpresonal relationship"
wordcount         : "4,362"
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
header-includes:
   - \usepackage{setspace, appendix, placeins, booktabs, tikz, siunitx}
   - \usepackage{tabularx, epigraph, float, colortbl, tabu, pdflscape}
   - \usetikzlibrary{positioning}
   - \raggedbottom
   - \usepackage[maxfloats=256]{morefloats}
   - \maxdeadcycles=1000
output: 
  # papaja::apa6_docx
  papaja::apa6_pdf
editor_options: 
  chunk_output_type: console
  markdown: 
    wrap: 72
always_allow_html: true
---

```{r setup, include=FALSE}
library(magrittr)

knitr::opts_chunk$set(fig.width = 8, fig.height = 4, cache = F, echo = F,
                      fig.align = 'center',warning = FALSE, message = FALSE)

study1_time1 <- readRDS(here::here("Data/Study1_time1.Rds"))
study1_time2_giver <- readRDS(here::here("Data/Study1_time2_giver.Rds"))
study1_time2_giver50 <- readRDS(here::here("Data/Study1_time2_giver50.Rds"))
study1_advice <- readRDS(here::here("Data/Study1_time2_advice.Rds"))
study1_time3 <- readRDS(here::here("Data/Study1_time3.Rds"))

```

# Introduction
Gender differences have been documented in various domains and attract plenty of scholarly attention to explain underlying causes. Extent research largely focuses on internal factors, such as cognitive styles, preference, personal beliefs, assuming females and males want to do different things. Another source of such differences may be the advice that people receive. Prior work has documented that men receive more aspirational advice and women more risk-averse advice, which may explain why women are less likely to apply for and ultimately obtain more rewarding positions. Research in this line of gender discrimination has emphasized the role of unconscious bias, but interventions that try to reduce this bias have been largely unsuccessful.
This paper propose a novel source of differences in advice by drawing on recent work on belief-based utility, expectation-based reference points, and the hedonic consequences of information. Specifically, we hypothesize that receiving information that is less favorable than one expects imposes a psychological cost on the recipient, because it is disappointing and suggests a less favorable future than one imagined. If people anticipate this cost when giving advice, they may be overly favorable or optimistic so as to protect the advisee’s belief utility. That is, they may not (only) give the advice that they believe will lead to the best decision but are also motivated to avoid disappointing the recipient. This requires the formation of beliefs about the advisee’s expectations, which is where we propose the differential treatment of men and women arises. Prior work has documented that men are more overconfident than women, conditional on equal performance, and that people anticipate this difference. An adviser who seeks to avoid disappointment and incorporates expectations into their advice would then present more favorable advice to male advisees than to female advisees. 
While the interpersonal concern has not been fully investigated as a source of gender difference regarding advice giving, its assumption, the hedonic consequences of information have been well documented. Research in economics and psychology has found that people avoid information that could make them feel bad, even when doing so leads to worse decisions. Recipients of information are even found to blame the people who deliver undesirable message, even though the messenger are not responsible for the situation. 
Advice is predicted to trigger a more intense emotional response because it is assumed to be tailored for its target, and reflects how the giver see the target. Individuals tend to desire positive social images and are protective when it comes to others' evaluation of them, and accordingly, prefer advice that implies a positive evaluation. However, we are unaware of research documenting whether people take this into account when advising others.

# A. Our study
We test whether gender difference in receiving advice is driven by givers' intention to meet target's expectation and avoid disappoint them. We report results from two preregistered experiment in which the interactions without deception between advice givers and recipients are captured. In each experiment, we first measure actual level and expectations of advisees, then provide these information to givers and collect advice. Lastly, we present advice to their targets, ask advisees to make final decision, and measure the utility of the advice.
We predict and find that males receive flattering advice than female counterparts when advisers take target's expectations into account. If advice for both gender is solely based on actual performance, there exists no gender difference regarding the chance of receiving aggressive advice. But when expectation of the target is provided along with actual performance, advisers consider this irrelevant information and give more aggressive advice to males because they have higher expectations for themselves compared with equally competent females. 
We also directly test the reason why advisers provide flattering advice. We compare advice given under the treatment condition where interpersonal concerns is the goal with that of baseline condition where, like usually assumed, effectiveness of facilitating decision making is emphasized. Advisers are more likely to inflate their advice so that it delivers a positive evaluation of its target when they hold interpersonal concerns and want to be liked by the target.

# B. Related Literature
People frequently obtain information by soliciting the advice of those with more expertise about or insight into an issue. A substantial literature has studied how people incorporate advice and whose advice they seek out. Briefly, people put less than optimal weight on the advice they receive, and prefer advice from those who are overconfident or who provide favorable information. Indeed, people punish advisers who tell them things they do not want to hear. Most of the studies in this stream of research have relied on deception and do not involve real people in the role of advisers; studies of advisers themselves remain scarce.

Notably, prior work on advice has emphasized the instrumental value of information, examining the extent to which the advice improves the quality of or satisfaction with a decision. In the proposed project, we will focus on the signaling value of advice: what does the advice imply about the adviser’s perception of the advisee? We propose that “flattering” advice creates a perception that the adviser holds the advisee in high esteem, and that this in turn increases the advisee’s liking for the adviser. Such interpersonal considerations may be as important (or even more important) in cases where it is difficult to evaluate ex post whether the advice was good or not.

Prior work has further documented that men and women receive different performance feedback at work. Managers are less likely to provide critical feedback to women, believing that doing so would hurt their feelings. Thus, interpersonal concerns can undermine constructive feedback, which then harms outcomes because it deprives the advisee of a learning opportunity. While this effect at first glance appears counter to our hypotheses (here, men receive more negative feedback), it is driven by different beliefs. Managers withhold critical feedback because they (perhaps incorrectly) believe that women suffer a greater cost from criticism. Our hypothesized effect is driven by (accurate) beliefs about performance expectations. While advice also communicates beliefs about ability, it does not do so through criticism.

# Study 1
In this study, we conducted an initial test to examine whether individuals take others' self-expectations into account when giving advice. Specifically, we predicted that people would adjust their advice to match the advisees' expectations of themselves, even when these expectations are not informative for the underlying decision problem. This study was preregistered on AsPredicted (https://aspredicted.org/R44_6SR).

## Methods
We recruited `r scales::comma(dim(study1_time1)[1])` participants (`r round(mean(study1_time1$Gender == "Female")*100)`\% Female, $M_{\text{Age}}$ = `r mean(study1_time1$Age)`) from Prolific Academic to take math test and another `r scales::comma(dim(study1_time2_giver)[1])` (`r round(mean(study1_time2_giver$gender == "Female")*100)`\% Female, $M_{\text{Age}}$ = `r mean(study1_time2_giver$age)`)
This study consisted of three stages involving recipients of advice taking an exam in Stage 1, givers providing advice in Stage 2, and recipients reacting to advice in Stage 3. During Stage 1, participants were asked to answer ten math questions in five minutes and were informed that they would receive 10 cents for each question they answered correctly. Participants were also asked to predict how many questions they would answer correctly. We manipulated their self-expectations by randomly assigning participants to either a High or Low Expectation condition. In the High Expectation condition, participants were informed that the average score of five other participants who took the same test was 6.4, while those in the Low Expectation condition were told that the average score was 2.6. We incentivized their performance in the math test to increase their attachment to the task. The number of correct answers and their predictions represented the recipients' performance and expectations, respectively, and were shown to advice givers.
After collecting performance and expectations from recipients, we recruited `r scales::comma(dim(study1_time2_giver)[1])`  participants and informed them of the results of the mathematics quiz completed by the first group of participants. Their task was to give advice to the previous participants about whether to compete against a group of "high" performers or a group of "low" performers (the top 20 and bottom 20 performers out of a separate group of 50 participants who completed the mathematics quiz). Advisees could earn a bonus if they performed as well or better than a randomly selected member of their chosen group, and the bonus differed depending on the group they chose (50 cents and 30 cents for the high-performing and low-performing group, respectively). Advisers received a bonus identical to the one earned by one of their advisees. They provided advice to 10 randomly selected advisees, and we clustered standard errors at the level of Stage 2 participants in subsequent analyses accordingly. We randomly assigned advisers to one of two conditions: they either observed only the true performance of the advisee (“Baseline” treatment), or they observed the true performance and the participant's own estimate of their performance (“Information” treatment). To give givers some sense of this task, we told them the average scores for a previous batch of 50 quiz-takers were 4.42. It is important to note that the advisee's own guess provided no information about the likelihood of winning against either the high or low group, as the outcome was based on past performance and not performance on a subsequent test.
Lastly, we invited the recipients back, reminded them of their previous self-expectations, and informed them that they could earn a bonus if they performed as well or better than a competitor. They could decide where that competitor was randomly drawn from, a group of "high" performers or a group of "low" performers. If they scored the same or higher than that competitor, they could earn a bonus, whose value differed depending on the group they chose (50 cents and 30 cents for the high-performing and low-performing group, respectively). Recipients were told that an external observer had provided a piece of advice. They then read the advice and made their decisions about who they wanted to compete with.

## Open Science Statement
We report all manipulations, measures, and data exclusion in this and the following study. 
The preregistration reports, screenshots of all experimental materials, and 
the analysis code to replicate all statistical analyses and figures are
available on the Open Science Framework (will do this later).

```{r}
library("papaja")
# Fit linear regression model
model1 <- lm(Guess ~ Condition + count, data = study1_time1)
model1_apa <- apa_print(model1)

model2 <- lm(Guess ~ Gender + count, data = study1_time1)
model2_apa <- apa_print(model2)
```

## Results
We begin by analyzing the performance and expectations of Stage 1 participants, as they will serve as input for Stage 2 participants and influence their advice. We compare the performance and expectations of participants in High and Low Expectation conditions, where they are told the average score for a five-participant group is 6.4 or 2.6. Although we randomly assigned participants, those in the Low Expectation condition scored slightly higher than those in the High Expectation condition (`r round(mean(study1_time1[study1_time1$Condition == "Low",]$count),2)` and `r round(mean(study1_time1[study1_time1$Condition == "High",]$count),2)`, respectively, `r papaja::apa_print(t.test(count ~ Condition, data = study1_time1, var.equal = T))$statistic`). However, the gap is not significant. Participants in the High Expectation condition had worse performance, but they also indicated a significantly higher guess of their score than their counterparts in the other condition (`r round(mean(study1_time1[study1_time1$Condition == "Low",]$count),2)` and `r round(mean(study1_time1[study1_time1$Condition == "High",]$Guess),2)`, respectively, `r papaja::apa_print(t.test(Guess ~ Condition, data = study1_time1, var.equal = T))$statistic`).It makes our experiment a conservative test. The gap between their expectations is `r round(mean(study1_time1[study1_time1$Condition == "High",]$Guess),2) - round(mean(study1_time1[study1_time1$Condition == "Low",]$Guess),2)`, which is not marginal considering the average expectations for all participants is only `r round(mean(study1_time1$Guess),2)`.It is worth mentioning that participants from both conditions reported having a hard time answering the math test, and thus, they are underconfident. However, participants from the High Expectation condition expected to solve more, indicating a successful manipulation. Despite the manipulation, the expectations are significantly correlated with the actual performance (`r model1_apa$estimate['count']`, `r model1_apa$statistic['count']`).
Next, we examine gender differences and find that male participants performed slightly better than female participants, and the gap is significant (`r round(mean(study1_time1[study1_time1$Gender == "Male",]$count),2)` and `r round(mean(study1_time1[study1_time1$Gender == "Female",]$count),2)`, respectively, `r papaja::apa_print(t.test(count ~ Gender, data = study1_time1, var.equal = T))$statistic`). On average, males are more confident than females, as they predicted to answer more questions correctly (`r round(mean(study1_time1[study1_time1$Gender == "Male",]$Guess),2)` and `r round(mean(study1_time1[study1_time1$Gender == "Female",]$Guess),2)`, respectively, `r papaja::apa_print(t.test(Guess ~ Gender, data = study1_time1, var.equal = T))$statistic`). We conducted an OLS regression with the performance and gender of participants and found that with the same score, male participants are more confident than their female counterparts (`r model2_apa$estimate['GenderMale']`, `r model2_apa$statistic['GenderMale']`).

```{r}
library("papaja")
# Fit linear regression model
model3 <- lm(Advice ~ Treatment + Performance, data = study1_advice %>% dplyr::filter(Condition == "E"))
model3_apa <- apa_print(model3)

model4 <- lm(Advice ~ Guess + Performance, data = study1_advice %>% dplyr::filter(Condition == "E"))
model4_apa <- apa_print(model4)

study1_advice <- study1_advice %>% dplyr::mutate(ExpShow = ifelse(Condition == 'E',1,0))

```

```{r study1regs}
modelsummary::modelsummary(list(`(1)` = lm(Advice ~ ExpShow*Gender , data = study1_advice),
                                `(2)` = lm(Advice ~ ExpShow*Gender , data = study1_advice),
                                `(3)` = lm(ExpectedBonus ~ ExpShow*Gender, data = study1_advice)),
                           vcov = c("classical", ~GiverID,~GiverID),
                            coef_map = c("ExpShow" = "Expectation Shown",
                                        "GenderMale" = "Advisee Male",
                                        "ExpShow:GenderMale" = "Expectation x Male",
                                        "(Intercept)" = "Constant"),
                           stars = T,
                           gof_map = list(list('raw' = 'nobs', 'clean' = 'N', 'fmt' = 0)),
                           caption = "Advice of competing against High Performance group, based on the gender of targets and whether their expectation is shown to adviser (Column 1). Column 2 show the results where standard errors are clusterd at the level of adviser. Expeccted Bonus of advice received, based on the gender of targets and whether their expectation is shown to adviser (Column 3)") %>%
  kableExtra::kable_styling(latex_option = "scale_down")

```

```{r study1gender, fig.cap="When expectation is shown to the adviser"}

library(ggplot2)
study1_advice <- study1_advice %>% dplyr::mutate(advice = as.numeric(Advice) )

ProbHG <- study1_advice %>%
  dplyr::group_by(Condition, Performance, Gender) %>%
  dplyr::summarize(avg_hardGroup = mean(advice))

df_exp <- subset(ProbHG, Condition == "E")
df_none <- subset(ProbHG, Condition == "None")

#it returns warning messages
#but I suppress them
ggplot(df_exp, aes(x = Performance, y = avg_hardGroup, color = Gender)) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = FALSE) +
  geom_smooth(data = df_none, aes(x = Performance, y = avg_hardGroup),
              method = "glm", method.args = list(family = "binomial"), color = "grey", se = FALSE) +
  scale_color_manual(values = c("#FFA500", "#4169E1", "grey"),
                      labels = c("Female_withExpectation", "Male_withExpectation", "NoExpectation")) +
  scale_y_continuous(name = "P(Compete Against High Performance)") +
  scale_x_continuous(name = "Performance") +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "grey"),
        legend.position = "bottom",
        legend.title = element_blank(),
        legend.key.size = unit(1.2, "lines"),          
        legend.text = element_text(size = 12),
        plot.title = element_text(hjust = 0.5, size = 20))

```

In Stage 2, we collected `r scales::comma(dim(study1_advice)[1])` pieces of advice for `r scales::comma(dplyr::n_distinct(study1_advice$Target))` Advisees. To exclude between-person differences from advice givers, we clustered standard errors at the level of the Stage 2 participants when running OLS regression. We conducted an OLS regression with the performance and Advisee Treatment (High or Low Expectation) for the subset of Stage 2 participants in the “Information” Treatment. Although Advisees in the High Expectation condition are more likely to be recommended to compete against the High Performer Group, the result is not significant (`r model3_apa$estimate['TreatmentLow']`, `r model3_apa$statistic['TreatmentLow']`). This may be because the confidence difference (`r round(mean(study1_advice[study1_advice$Treatment == "High",]$Guess),2) - round(mean(study1_advice[study1_advice$Treatment == "Low",]$Guess),2)`) is too minor for advice givers to take more risk. Only `r round(mean(study1_advice$Advice),4)*100`\% of the time, advice givers recommended the High Performer group as the competitor, and the average scores for those who received this advice is `r round(mean(study1_advice[study1_advice$Advice == 1,]$Performance),2)`, which is about at the `r round(ecdf(study1_advice$Performance)(6.64) * 100)`th  percentile in the performance distribution shown to the advice givers.
However, if we run an OLS regression with performance and the exact expectations of Advisees, the expectation does increase the chance of receiving aggressive advice (`r model4_apa$estimate['Guess']`, `r model4_apa$statistic['Guess']`). 
In Stage 2, each participant always sees five females and five males with the same score distribution, and the only difference lies in their expectations. Therefore, we predict that there will be no gender difference when advice givers only see performance, but males will receive more aggressive advice when their expectations are presented. We conducted an OLS regression with whether givers see the expectation (Baseline or Information condition) and the gender of the Advisee (Female or Male), as well as their interaction. In line with our prediction, only when expectations are known to the advice giver, male participants have a higher chance of being recommended to compete against the High Performer group (Column 2 of Table \@ref(tab:study1regs) ). As seen in Figure \@ref(fig:study1gender), gender differences emerge as a result of showing expectations.
Because we only have advice for `r scales::comma(dplyr::n_distinct(study1_advice$Target))` Advisees, to ensure that every participant in Stage 1 receives advice, we recruited `r scales::comma(dim(study1_time2_giver50)[1])` more participants to collect more advice for the other `r 1000-as.numeric(scales::comma(dplyr::n_distinct(study1_advice$Target)))` participants for Stage 1. We did not include any of this advice in the analysis of Stage 2 results.
```{r}
library("papaja")
# Fit linear regression model
study1_time3 <- study1_time3 %>% dplyr::mutate(HighExp = ifelse(AdviseeCondition=='High',1,0))

model5 <- lm(bonus ~ HighExp + AdviseeScore, data = study1_time3 %>% dplyr::filter(GiverCondition == 1))
model5_apa <- apa_print(model5)

```

Among `r scales::comma(dim(study1_time1)[1])` participants, `r round(dim(study1_time3)[1]/dim(study1_time1)[1]*100,2)`% of them returned for the Stage 3 experiment. Of all advice shown to Advisees, `r dim(study1_time3[study1_time3$GiverCondition==1,])[1]` of them are from givers in the ‘Information’ treatment condition, and the other `r dim(study1_time3[study1_time3$GiverCondition==0,])[1]` are from givers in the ‘Baseline’ treatment condition. To examine the impact of flattering advice on performance, we first looked at advice from givers who know the expectations of Advisees. We conducted an OLS regression with performance and Treatment condition (High or Low Expectation) of Advisees. As predicted, participants in the High Expectation condition received less (`r model5_apa$estimate['HighExp']`, `r model5_apa$statistic['HighExp']`), but it is not significant. We realize this result is less powerful because the advice presented was randomly selected and advisees who return to this follow-up survey also bring noise.
To avoid randomness, we computed the Expected Bonus for all `r scales::comma(dim(study1_advice)[1])` advice we collected in Stage 2, assuming they are adopted by the Advisees. We conducted an OLS regression with whether givers see the expectation (Baseline or Information condition) and the gender of the Advisee (Female or Male), as well as their interaction. Supporting our theory, male participants will receive less bonus given advice they receive (Column 3 of Table \@ref(tab:study1regs) ). It implies that when males receive more aggressive advice (competing against the High Performer group), they end up worse because this kind of advice is not necessarily based on their actual condition.

# Study 2
In the previous study, we found that individuals take into account the self-expectations of others when providing advice. In this study, we aimed to investigate whether people inflate advice due to the concern for interpersonal benefits. We hypothesized that individuals may exaggerate their advice in order to be viewed more favorably by the recipients. This study was preregistered on AsPredicted (https://aspredicted.org/45P_93G).

```{r}

study2_time1 <- readRDS(here::here("Data/Study2_time1.Rds"))
study2_time2 <- readRDS(here::here("Data/Study2_time2.Rds"))
study2_time3 <- readRDS(here::here("Data/Study2_time3.Rds"))

```

## Method
We recruited `r scales::comma(dim(study2_time1)[1])` workers from Prolific (`r round(mean(study2_time1$gender == "Female")*100)`\% Female, $M_{\text{Age}}$ = `r mean(study2_time1$age)`) to upload selfies and another `r scales::comma(dim(study2_time2)[1])` (`r round(mean(study2_time2$gender == "Female")*100)`\% Female, $M_{\text{Age}}$ = `r mean(study2_time2$age)`) participants to rate selfies regarding physical attractiveness and give advice. 
Study 2 consists of three surveys. At time 1, we invited participants to upload photos of themselves (selfies) to be rated by other participants on attractiveness. We assigned each participant to a group of 10 participants of their own gender. We also asked participants to predict how they rank in this 10-person group regarding physical attractiveness. To create a gender-balanced sample, among all `r dim(study2_time1 %>% dplyr::filter(gender == 'Female'))[1]` female participants who uploaded selfies, we select the first 100 and only include them in the following time 2 and time 3 studies. That is, in total we have 200 recipients. Next, we recruited `r scales::comma(dim(study2_time2)[1])` new participants and asked them to rank the attractiveness of one such group of 10 participants of the opposite gender. After they did so, we showed them the photo of the participant they ranked as the 7th most attractive (that is, the 4th least attractive) and reminded them that they had ranked this person at 7th place. We (truthfully) informed them that this participant would have a chance to earn a bonus if they accurately guessed their rank based on the aggregated ratings of all participants who had ranked this group. Participants were then randomly assigned to an “accuracy” or a “likability” treatment. In the accuracy treatment, they received a bonus identical to that of the advisee. In the “likability” treatment, their bonus depended on how the advisee rated them in terms of likability, after observing only the rank that they had advised the advisee to guess. At time 3, we invited the participants who uploaded selfies to return for the third stage of the experiment. Here, they observed the rank proposed by an adviser and made an incentivized bet on how they ranked across all of those who rated their photo. We then asked participants to evaluate the adviser based on their likability and warmth on a 5-point scale. The latter dimension was measured with 4-item scale adopted from Fiske, Cuddy, and Glick (2007).

## Open Science Statement
We report all manipulations, measures, and data exclusion in this and the following study. 
The preregistration reports, screenshots of all experimental materials, and 
the analysis code to replicate all statistical analyses and figures are
available on the Open Science Framework (will do this later).

## Results
```{r study2advice, fig.cap="Advice for 7th most attractive participants"}
library(dplyr)

count <- study2_time2 %>%
  group_by(Condition) %>%
  summarize(number = dplyr::n())

advice_avg <- study2_time2 %>%
  group_by(Condition, Advice) %>%
  summarize(n = dplyr::n()) %>%
  dplyr::mutate(conditionCount = ifelse(Condition == 'Likable',count[count$Condition == 'Likable',]$number,count[count$Condition == 'Accurate',]$number)) %>%
  dplyr::mutate(percent = n/conditionCount*100) %>% 
  dplyr::select(Condition,Advice,percent)

# Create a facet plot with condition as the facet variable and gender as the line color
ggplot(advice_avg, aes(x = Advice, y = percent, color = Condition)) +
  geom_line(linewidth = 0.75)+
  scale_color_manual(values = c("#FFA500", "#4169E1"),
                      labels = c("Accurate", "Likable")) +
  scale_y_continuous(name = "% of participants") +
  scale_x_continuous(name = "Advised Rank") +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "grey"),
        legend.position = "bottom",
        legend.title = element_blank(),
        legend.key.size = unit(1.2, "lines"),          
        legend.text = element_text(size = 12),
        plot.title = element_text(hjust = 0.5, size = 20))

```

First, in line with our prediction, participants advised a lower rank (that is, more attractive) in the likeability treatment than the accuracy treatment, $M_{\text{Likable}}$  =`r round(mean(study2_time2[study2_time2$Condition == "Likable",]$Advice),2)` and $M_{\text{Accurate}}$ = `r round(mean(study2_time2[study2_time2$Condition == "Accurate",]$Advice),2)`, `r papaja::apa_print(t.test(Advice ~ Condition, data = study2_time2, var.equal = T))$statistic`. As seen in Figure \@ref(fig:study2advice), notably, even in the accuracy treatment, participants advised a lower rank than they themselves had provided (`r papaja::apa_print(t.test(study2_time2[study2_time2$Condition == "Accurate",]$Advice, mu = 7, var.equal = T))$statistic`). This suggests that advisers inferred that advising someone that they were more attractive would make the adviser appear more likable and therefore provided advice that communicated a more favorable impression of the participants’ attractiveness.

```{r study2regs}

modelsummary::modelsummary(list(`(1)` = lm(likable ~ Advice, data = study2_time3),
                                `(2)` = lm(warmAvg ~ Advice, data = study2_time3)),
                           vcov = c("classical", "classical"),
                           coef_map = c("Advice" = "Advised Rank",
                                        "(Intercept)" = "Constant"),
                           stars = T,
                           gof_map = list(list('raw' = 'nobs', 'clean' = 'N', 'fmt' = 0)),
                           caption = "When individuals receive advice that implies a high level of attractiveness (lower rank), they tend to perceive the advice giver as more likable (Column 1) and warm (Column 2).") %>%
  kableExtra::kable_styling(latex_option = "scale_down")

```

```{r study2rating, fig.cap="The evaluation of advice givers"}

rating <- study2_time3 %>%
  group_by(Advice) %>%
  summarise(Likable = mean(likable), Warm = mean(warmAvg), Trust = mean(trustAvg))

ggplot(rating, aes(x = Advice)) +
  geom_line(aes(y = Likable, color = "Likable"), linewidth = 0.75) +
  geom_line(aes(y = Warm, color = "Warm"), linewidth = 0.75) +
  geom_line(aes(y = Trust, color = "Trust"), linewidth = 0.75) +
  scale_color_manual(values = c("Likable" = "#FFA500", "Warm" = "#4169E1", "Trust" = "grey"),
                      labels = c("Likable", "Warm", "Trust")) +
  scale_y_continuous(name = "Rating") +
  scale_x_continuous(name = "Advised Rank") +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "grey"),
        legend.position = "bottom",
        legend.title = element_blank(),
        legend.key.size = unit(1.2, "lines"),          
        legend.text = element_text(size = 12),
        plot.title = element_text(hjust = 0.5, size = 20))

```

Of the 200 advisees, `r round(dim(study2_time3)[1]/200*100,2)`% returned for a follow-up survey, provided their incentivized guess, and evaluated advisers on likeability and warmth. As seen in Figure \@ref(fig:study2rating), in line of our predictions, we found that advisees who suggested that the advisee was more attractive were indeed rated as more likeable (Column 1 of Table \@ref(tab:study2regs) ), and warmer (Column 2 of Table \@ref(tab:study2regs) ). Notably, however, we were not powered to do a comparison across the two experimental groups.

### 2024-01-01 Advice-Giving.tex
Uploding the first draft

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\centering\begin{threeparttable}}
%   {\end{threeparttable}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
% See https://github.com/crsh/papaja/issues/292
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\itshape\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

\makeatletter
\usepackage{etoolbox}
\patchcmd{\maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{Gender difference, Advice, Interpresonal relationship\newline\indent Word count: 4,362}
\usepackage{csquotes}
\usepackage{setspace, appendix, placeins, booktabs, tikz, siunitx}
\usepackage{tabularx, epigraph, float, colortbl, tabu, pdflscape}
\usetikzlibrary{positioning}
\raggedbottom
\usepackage[maxfloats=256]{morefloats}
\maxdeadcycles=1000
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Interpersonal Benefits of Flattering Advice},
  pdfauthor={Amanda Chen1 \& David Hagmann1},
  pdflang={en-EN},
  pdfkeywords={Gender difference, Advice, Interpresonal relationship},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Interpersonal Benefits of Flattering Advice}
\author{Amanda Chen\textsuperscript{1} \& David Hagmann\textsuperscript{1}}
\date{}

\shorttitle{Flattering Advice}

\authornote{

The authors are grateful to a lot of things.

Correspondence concerning this article should be addressed to Amanda Chen, Department of Management, The Hong Kong University of Science and Technology, Hong Kong. E-mail: \href{mailto:zchengj@connect.ust.hk}{\nolinkurl{zchengj@connect.ust.hk}}

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} The Hong Kong University of Science and Technology}

\note{

1 January, 2024

}

\abstract{%
This is an interesting project! Please read through it!
}

\begin{document}
\maketitle

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Gender differences have been documented in various domains and attract plenty of scholarly attention to explain underlying causes. Extent research largely focuses on internal factors, such as cognitive styles, preference, personal beliefs, assuming females and males want to do different things. Another source of such differences may be the advice that people receive. Prior work has documented that men receive more aspirational advice and women more risk-averse advice, which may explain why women are less likely to apply for and ultimately obtain more rewarding positions. Research in this line of gender discrimination has emphasized the role of unconscious bias, but interventions that try to reduce this bias have been largely unsuccessful.
This paper propose a novel source of differences in advice by drawing on recent work on belief-based utility, expectation-based reference points, and the hedonic consequences of information. Specifically, we hypothesize that receiving information that is less favorable than one expects imposes a psychological cost on the recipient, because it is disappointing and suggests a less favorable future than one imagined. If people anticipate this cost when giving advice, they may be overly favorable or optimistic so as to protect the advisee's belief utility. That is, they may not (only) give the advice that they believe will lead to the best decision but are also motivated to avoid disappointing the recipient. This requires the formation of beliefs about the advisee's expectations, which is where we propose the differential treatment of men and women arises. Prior work has documented that men are more overconfident than women, conditional on equal performance, and that people anticipate this difference. An adviser who seeks to avoid disappointment and incorporates expectations into their advice would then present more favorable advice to male advisees than to female advisees.
While the interpersonal concern has not been fully investigated as a source of gender difference regarding advice giving, its assumption, the hedonic consequences of information have been well documented. Research in economics and psychology has found that people avoid information that could make them feel bad, even when doing so leads to worse decisions. Recipients of information are even found to blame the people who deliver undesirable message, even though the messenger are not responsible for the situation.
Advice is predicted to trigger a more intense emotional response because it is assumed to be tailored for its target, and reflects how the giver see the target. Individuals tend to desire positive social images and are protective when it comes to others' evaluation of them, and accordingly, prefer advice that implies a positive evaluation. However, we are unaware of research documenting whether people take this into account when advising others.

\hypertarget{a.-our-study}{%
\section{A. Our study}\label{a.-our-study}}

We test whether gender difference in receiving advice is driven by givers' intention to meet target's expectation and avoid disappoint them. We report results from two preregistered experiment in which the interactions without deception between advice givers and recipients are captured. In each experiment, we first measure actual level and expectations of advisees, then provide these information to givers and collect advice. Lastly, we present advice to their targets, ask advisees to make final decision, and measure the utility of the advice.
We predict and find that males receive flattering advice than female counterparts when advisers take target's expectations into account. If advice for both gender is solely based on actual performance, there exists no gender difference regarding the chance of receiving aggressive advice. But when expectation of the target is provided along with actual performance, advisers consider this irrelevant information and give more aggressive advice to males because they have higher expectations for themselves compared with equally competent females.
We also directly test the reason why advisers provide flattering advice. We compare advice given under the treatment condition where interpersonal concerns is the goal with that of baseline condition where, like usually assumed, effectiveness of facilitating decision making is emphasized. Advisers are more likely to inflate their advice so that it delivers a positive evaluation of its target when they hold interpersonal concerns and want to be liked by the target.

\hypertarget{b.-related-literature}{%
\section{B. Related Literature}\label{b.-related-literature}}

People frequently obtain information by soliciting the advice of those with more expertise about or insight into an issue. A substantial literature has studied how people incorporate advice and whose advice they seek out. Briefly, people put less than optimal weight on the advice they receive, and prefer advice from those who are overconfident or who provide favorable information. Indeed, people punish advisers who tell them things they do not want to hear. Most of the studies in this stream of research have relied on deception and do not involve real people in the role of advisers; studies of advisers themselves remain scarce.

Notably, prior work on advice has emphasized the instrumental value of information, examining the extent to which the advice improves the quality of or satisfaction with a decision. In the proposed project, we will focus on the signaling value of advice: what does the advice imply about the adviser's perception of the advisee? We propose that ``flattering'' advice creates a perception that the adviser holds the advisee in high esteem, and that this in turn increases the advisee's liking for the adviser. Such interpersonal considerations may be as important (or even more important) in cases where it is difficult to evaluate ex post whether the advice was good or not.

Prior work has further documented that men and women receive different performance feedback at work. Managers are less likely to provide critical feedback to women, believing that doing so would hurt their feelings. Thus, interpersonal concerns can undermine constructive feedback, which then harms outcomes because it deprives the advisee of a learning opportunity. While this effect at first glance appears counter to our hypotheses (here, men receive more negative feedback), it is driven by different beliefs. Managers withhold critical feedback because they (perhaps incorrectly) believe that women suffer a greater cost from criticism. Our hypothesized effect is driven by (accurate) beliefs about performance expectations. While advice also communicates beliefs about ability, it does not do so through criticism.

\hypertarget{study-1}{%
\section{Study 1}\label{study-1}}

In this study, we conducted an initial test to examine whether individuals take others' self-expectations into account when giving advice. Specifically, we predicted that people would adjust their advice to match the advisees' expectations of themselves, even when these expectations are not informative for the underlying decision problem. This study was preregistered on AsPredicted (\url{https://aspredicted.org/R44_6SR}).

\hypertarget{methods}{%
\subsection{Methods}\label{methods}}

We recruited 1,002 participants (50\% Female, \(M_{\text{Age}}\) = 42.13) from Prolific Academic to take math test and another 1,000 (50\% Female, \(M_{\text{Age}}\) = 38.79)
This study consisted of three stages involving recipients of advice taking an exam in Stage 1, givers providing advice in Stage 2, and recipients reacting to advice in Stage 3. During Stage 1, participants were asked to answer ten math questions in five minutes and were informed that they would receive 10 cents for each question they answered correctly. Participants were also asked to predict how many questions they would answer correctly. We manipulated their self-expectations by randomly assigning participants to either a High or Low Expectation condition. In the High Expectation condition, participants were informed that the average score of five other participants who took the same test was 6.4, while those in the Low Expectation condition were told that the average score was 2.6. We incentivized their performance in the math test to increase their attachment to the task. The number of correct answers and their predictions represented the recipients' performance and expectations, respectively, and were shown to advice givers.
After collecting performance and expectations from recipients, we recruited 1,000 participants and informed them of the results of the mathematics quiz completed by the first group of participants. Their task was to give advice to the previous participants about whether to compete against a group of ``high'' performers or a group of ``low'' performers (the top 20 and bottom 20 performers out of a separate group of 50 participants who completed the mathematics quiz). Advisees could earn a bonus if they performed as well or better than a randomly selected member of their chosen group, and the bonus differed depending on the group they chose (50 cents and 30 cents for the high-performing and low-performing group, respectively). Advisers received a bonus identical to the one earned by one of their advisees. They provided advice to 10 randomly selected advisees, and we clustered standard errors at the level of Stage 2 participants in subsequent analyses accordingly. We randomly assigned advisers to one of two conditions: they either observed only the true performance of the advisee (``Baseline'' treatment), or they observed the true performance and the participant's own estimate of their performance (``Information'' treatment). To give givers some sense of this task, we told them the average scores for a previous batch of 50 quiz-takers were 4.42. It is important to note that the advisee's own guess provided no information about the likelihood of winning against either the high or low group, as the outcome was based on past performance and not performance on a subsequent test.
Lastly, we invited the recipients back, reminded them of their previous self-expectations, and informed them that they could earn a bonus if they performed as well or better than a competitor. They could decide where that competitor was randomly drawn from, a group of ``high'' performers or a group of ``low'' performers. If they scored the same or higher than that competitor, they could earn a bonus, whose value differed depending on the group they chose (50 cents and 30 cents for the high-performing and low-performing group, respectively). Recipients were told that an external observer had provided a piece of advice. They then read the advice and made their decisions about who they wanted to compete with.

\hypertarget{open-science-statement}{%
\subsection{Open Science Statement}\label{open-science-statement}}

We report all manipulations, measures, and data exclusion in this and the following study.
The preregistration reports, screenshots of all experimental materials, and
the analysis code to replicate all statistical analyses and figures are
available on the Open Science Framework (will do this later).

\hypertarget{results}{%
\subsection{Results}\label{results}}

We begin by analyzing the performance and expectations of Stage 1 participants, as they will serve as input for Stage 2 participants and influence their advice. We compare the performance and expectations of participants in High and Low Expectation conditions, where they are told the average score for a five-participant group is 6.4 or 2.6. Although we randomly assigned participants, those in the Low Expectation condition scored slightly higher than those in the High Expectation condition (4.80 and 4.55, respectively, \(t(1000) = -1.67\), \(p = .095\)). However, the gap is not significant. Participants in the High Expectation condition had worse performance, but they also indicated a significantly higher guess of their score than their counterparts in the other condition (4.80 and 4.42, respectively, \(t(1000) = 3.72\), \(p < .001\)).It makes our experiment a conservative test. The gap between their expectations is 0.52, which is not marginal considering the average expectations for all participants is only 4.16.It is worth mentioning that participants from both conditions reported having a hard time answering the math test, and thus, they are underconfident. However, participants from the High Expectation condition expected to solve more, indicating a successful manipulation. Despite the manipulation, the expectations are significantly correlated with the actual performance (\(b = 0.63\), 95\% CI \([0.58, 0.67]\), \(t(999) = 27.06\), \(p < .001\)).
Next, we examine gender differences and find that male participants performed slightly better than female participants, and the gap is significant (5.02 and 4.33, respectively, \(t(1000) = -4.77\), \(p < .001\)). On average, males are more confident than females, as they predicted to answer more questions correctly (4.75 and 3.56, respectively, \(t(1000) = -8.65\), \(p < .001\)). We conducted an OLS regression with the performance and gender of participants and found that with the same score, male participants are more confident than their female counterparts (\(b = 0.78\), 95\% CI \([0.56, 0.99]\), \(t(999) = 7.18\), \(p < .001\)).

\begin{table}

\caption{\label{tab:study1regs}Advice of competing against High Performance group, based on the gender of targets and whether their expectation is shown to adviser (Column 1). Column 2 show the results where standard errors are clusterd at the level of adviser. Expeccted Bonus of advice received, based on the gender of targets and whether their expectation is shown to adviser (Column 3)}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lccc}
\toprule
  & (1) & (2) & (3)\\
\midrule
Expectation Shown & \num{-0.034}** & \num{-0.034}* & \num{0.000}\\
 & (\num{0.013}) & (\num{0.013}) & (\num{0.003})\\
Advisee Male & \num{0.002} & \num{0.002} & \num{0.000}\\
 & (\num{0.013}) & (\num{0.005}) & (\num{0.001})\\
Expectation x Male & \num{0.032}+ & \num{0.032}*** & \num{-0.005}**\\
 & (\num{0.019}) & (\num{0.009}) & (\num{0.002})\\
Constant & \num{0.339}*** & \num{0.339}*** & \num{0.258}***\\
 & (\num{0.009}) & (\num{0.010}) & (\num{0.002})\\
\midrule
N & \num{10000} & \num{10000} & \num{10000}\\
\bottomrule
\multicolumn{4}{l}{\rule{0pt}{1em}+ p $<$ 0.1, * p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
\end{tabular}}
\end{table}

\begin{figure}

{\centering \includegraphics{Advice-Giving_files/figure-latex/study1gender-1}

}

\caption{When expectation is shown to the adviser}\label{fig:study1gender}
\end{figure}

In Stage 2, we collected 10,000 pieces of advice for 888 Advisees. To exclude between-person differences from advice givers, we clustered standard errors at the level of the Stage 2 participants when running OLS regression. We conducted an OLS regression with the performance and Advisee Treatment (High or Low Expectation) for the subset of Stage 2 participants in the ``Information'' Treatment. Although Advisees in the High Expectation condition are more likely to be recommended to compete against the High Performer Group, the result is not significant (\(b = -0.01\), 95\% CI \([-0.03, 0.01]\), \(t(4997) = -1.13\), \(p = .257\)). This may be because the confidence difference (0.60) is too minor for advice givers to take more risk. Only 33.11\% of the time, advice givers recommended the High Performer group as the competitor, and the average scores for those who received this advice is 6.64, which is about at the 80th percentile in the performance distribution shown to the advice givers.
However, if we run an OLS regression with performance and the exact expectations of Advisees, the expectation does increase the chance of receiving aggressive advice (\(b = 0.03\), 95\% CI \([0.02, 0.04]\), \(t(4997) = 10.13\), \(p < .001\)).
In Stage 2, each participant always sees five females and five males with the same score distribution, and the only difference lies in their expectations. Therefore, we predict that there will be no gender difference when advice givers only see performance, but males will receive more aggressive advice when their expectations are presented. We conducted an OLS regression with whether givers see the expectation (Baseline or Information condition) and the gender of the Advisee (Female or Male), as well as their interaction. In line with our prediction, only when expectations are known to the advice giver, male participants have a higher chance of being recommended to compete against the High Performer group (Column 2 of Table \ref{tab:study1regs} ). As seen in Figure \ref{fig:study1gender}, gender differences emerge as a result of showing expectations.
Because we only have advice for 888 Advisees, to ensure that every participant in Stage 1 receives advice, we recruited 48 more participants to collect more advice for the other 112 participants for Stage 1. We did not include any of this advice in the analysis of Stage 2 results.

Among 1,002 participants, 94.91\% of them returned for the Stage 3 experiment. Of all advice shown to Advisees, 483 of them are from givers in the `Information' treatment condition, and the other 468 are from givers in the `Baseline' treatment condition. To examine the impact of flattering advice on performance, we first looked at advice from givers who know the expectations of Advisees. We conducted an OLS regression with performance and Treatment condition (High or Low Expectation) of Advisees. As predicted, participants in the High Expectation condition received less (\(b = -0.02\), 95\% CI \([-0.05, 0.00]\), \(t(480) = -1.61\), \(p = .107\)), but it is not significant. We realize this result is less powerful because the advice presented was randomly selected and advisees who return to this follow-up survey also bring noise.
To avoid randomness, we computed the Expected Bonus for all 10,000 advice we collected in Stage 2, assuming they are adopted by the Advisees. We conducted an OLS regression with whether givers see the expectation (Baseline or Information condition) and the gender of the Advisee (Female or Male), as well as their interaction. Supporting our theory, male participants will receive less bonus given advice they receive (Column 3 of Table \ref{tab:study1regs} ). It implies that when males receive more aggressive advice (competing against the High Performer group), they end up worse because this kind of advice is not necessarily based on their actual condition.

\hypertarget{study-2}{%
\section{Study 2}\label{study-2}}

In the previous study, we found that individuals take into account the self-expectations of others when providing advice. In this study, we aimed to investigate whether people inflate advice due to the concern for interpersonal benefits. We hypothesized that individuals may exaggerate their advice in order to be viewed more favorably by the recipients. This study was preregistered on AsPredicted (\url{https://aspredicted.org/45P_93G}).

\hypertarget{method}{%
\subsection{Method}\label{method}}

We recruited 207 workers from Prolific (52\% Female, \(M_{\text{Age}}\) = 39.50) to upload selfies and another 472 (50\% Female, \(M_{\text{Age}}\) = 41.03) participants to rate selfies regarding physical attractiveness and give advice.
Study 2 consists of three surveys. At time 1, we invited participants to upload photos of themselves (selfies) to be rated by other participants on attractiveness. We assigned each participant to a group of 10 participants of their own gender. We also asked participants to predict how they rank in this 10-person group regarding physical attractiveness. To create a gender-balanced sample, among all 107 female participants who uploaded selfies, we select the first 100 and only include them in the following time 2 and time 3 studies. That is, in total we have 200 recipients. Next, we recruited 472 new participants and asked them to rank the attractiveness of one such group of 10 participants of the opposite gender. After they did so, we showed them the photo of the participant they ranked as the 7th most attractive (that is, the 4th least attractive) and reminded them that they had ranked this person at 7th place. We (truthfully) informed them that this participant would have a chance to earn a bonus if they accurately guessed their rank based on the aggregated ratings of all participants who had ranked this group. Participants were then randomly assigned to an ``accuracy'' or a ``likability'' treatment. In the accuracy treatment, they received a bonus identical to that of the advisee. In the ``likability'' treatment, their bonus depended on how the advisee rated them in terms of likability, after observing only the rank that they had advised the advisee to guess. At time 3, we invited the participants who uploaded selfies to return for the third stage of the experiment. Here, they observed the rank proposed by an adviser and made an incentivized bet on how they ranked across all of those who rated their photo. We then asked participants to evaluate the adviser based on their likability and warmth on a 5-point scale. The latter dimension was measured with 4-item scale adopted from Fiske, Cuddy, and Glick (2007).

\hypertarget{open-science-statement-1}{%
\subsection{Open Science Statement}\label{open-science-statement-1}}

We report all manipulations, measures, and data exclusion in this and the following study.
The preregistration reports, screenshots of all experimental materials, and
the analysis code to replicate all statistical analyses and figures are
available on the Open Science Framework (will do this later).

\hypertarget{results-1}{%
\subsection{Results}\label{results-1}}

\begin{figure}

{\centering \includegraphics{Advice-Giving_files/figure-latex/study2advice-1}

}

\caption{Advice for 7th most attractive participants}\label{fig:study2advice}
\end{figure}

First, in line with our prediction, participants advised a lower rank (that is, more attractive) in the likeability treatment than the accuracy treatment, \(M_{\text{Likable}}\) =5.38 and \(M_{\text{Accurate}}\) = 6.19, \(t(470) = 5.44\), \(p < .001\). As seen in Figure \ref{fig:study2advice}, notably, even in the accuracy treatment, participants advised a lower rank than they themselves had provided (\(t(234) = -8.82\), \(p < .001\)). This suggests that advisers inferred that advising someone that they were more attractive would make the adviser appear more likable and therefore provided advice that communicated a more favorable impression of the participants' attractiveness.

\begin{table}

\caption{\label{tab:study2regs}When individuals receive advice that implies a high level of attractiveness (lower rank), they tend to perceive the advice giver as more likable (Column 1) and warm (Column 2).}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lcc}
\toprule
  & (1) & (2)\\
\midrule
Advised Rank & \num{-0.109}* & \num{-0.133}**\\
 & (\num{0.046}) & (\num{0.044})\\
Constant & \num{3.777}*** & \num{3.903}***\\
 & (\num{0.279}) & (\num{0.266})\\
\midrule
N & \num{146} & \num{146}\\
\bottomrule
\multicolumn{3}{l}{\rule{0pt}{1em}+ p $<$ 0.1, * p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
\end{tabular}}
\end{table}

\begin{figure}

{\centering \includegraphics{Advice-Giving_files/figure-latex/study2rating-1}

}

\caption{The evaluation of advice givers}\label{fig:study2rating}
\end{figure}

Of the 200 advisees, 73\% returned for a follow-up survey, provided their incentivized guess, and evaluated advisers on likeability and warmth. As seen in Figure \ref{fig:study2rating}, in line of our predictions, we found that advisees who suggested that the advisee was more attractive were indeed rated as more likeable (Column 1 of Table \ref{tab:study2regs} ), and warmer (Column 2 of Table \ref{tab:study2regs} ). Notably, however, we were not powered to do a comparison across the two experimental groups.

\end{document}

### 2024-01-01 R/clean_study1_time1.R

@@ -1,0 +1,39 @@
+library(dplyr)
+library(ggplot2)
+library(magrittr)
+
+Advisee <- data.table::fread(here::here("Data/Raw Data/S1_time1.csv"),
+                             header = T,na.strings = '')[-c(1,2)] %>%
+  dplyr::filter(Progress == '100' & Status == 'IP Address' & !is.na(QID3) & Gender != 'Other') %>%
+  dplyr::rename('ProlificID' = 'QID3') %>%
+  dplyr::mutate(Guess = as.numeric(Guess), Age = as.numeric(Age))  %>%
+  dplyr::select(ProlificID,ResponseId,Condition, QID10:QID19,Guess,
+                Gender, Age, Ethnicity,Education)
+
+
+
+# count correct answers
+answerList <- c('113 feet','x = -2','x15','13','2.06',
+                '-34','6','63°','3','4x2 + 32x + 48')
+answer <- Advisee %>% dplyr::select(QID10:QID19)
+#count <-  apply(answer, 1, function(x) sum(x == answerList))
+
+count <- apply(answer, 1, function(x) {
+  # Check if there are NAs in the list
+  if (any(is.na(x))) {
+    # If there are NAs, count non-NA elements
+    sum(!is.na(x) & x %in% answerList)
+  } else {
+    # If there are no NAs, count all elements
+    sum(x == answerList)
+  }
+})
+
+
+count <- as.data.frame(count)
+Advisee <- cbind(Advisee,count)
+
+saveRDS(Advisee, file = here::here("Data/Study1_time1.Rds"))
+
+Advisee %>% write.csv("Data/Cleaned Data/S1_time1_clean.csv")
+

### 2024-01-01 R/clean_study1_time2.R

@@ -1,0 +1,116 @@
+library(dplyr)
+library(ggplot2)
+library(magrittr)
+
+giver <- data.table::fread(here::here("Data/Raw Data/S1_time2.csv"),
+                           header = T,na.strings = '')[-c(1,2)] %>%
+  dplyr::filter(Progress == '100',gender != 'Other', !is.na(PROLIFIC_PID)) %>%
+  dplyr::select(ResponseId, PROLIFIC_PID,Condition,dplyr::contains("_advice"),GoupNum,
+                age,gender, ethnicity,education,"0.AdviseeID":"9.Treatment" ) %>%
+  dplyr::mutate(dplyr::across(dplyr::contains("_advice"),
+                              ~ dplyr::case_when(stringr::str_starts(.,"Low") ~ 0,
+                                                 stringr::str_starts(.,"High") ~ 1))) %>%
+  dplyr::mutate_at(vars(contains("_advice")), as.numeric) %>%
+  dplyr::mutate_at(vars(contains('.Performance')), as.numeric) %>%
+  dplyr::mutate_at(vars(contains('.Estimate')), as.numeric) %>%
+  dplyr::rename('GroupNum' = 'GoupNum') %>%
+  dplyr::mutate(GroupNum = as.numeric(GroupNum), age = as.numeric(age))
+
+giver50 <- data.table::fread(here::here("Data/Raw Data/S1_time2_50.csv"),
+                           header = T,na.strings = '')[-c(1,2)] %>%
+  dplyr::filter(Progress == '100',gender != 'Other', !is.na(PROLIFIC_PID)) %>%
+  dplyr::select(ResponseId, PROLIFIC_PID,Condition,dplyr::contains("_advice"),
+                age,gender, ethnicity,education,"0.AdviseeID":"9.Treatment" ) %>%
+  dplyr::mutate(dplyr::across(dplyr::contains("_advice"),
+                              ~ dplyr::case_when(stringr::str_starts(.,"Low") ~ 0,
+                                                 stringr::str_starts(.,"High") ~ 1))) %>%
+  dplyr::mutate_at(vars(contains("_advice")), as.numeric) %>%
+  dplyr::mutate_at(vars(contains('.Performance')), as.numeric) %>%
+  dplyr::mutate_at(vars(contains('.Estimate')), as.numeric) %>%
[…]

### 2024-01-01 R/clean_study1_time3.R

@@ -1,0 +1,93 @@
+library(dplyr)
+library(ggplot2)
+library(magrittr)
+
+Advisee <- data.table::fread(here::here("Data/Raw Data/S1_time3.csv"),
+                             header = T,na.strings = '')[-c(1,2)] %>%
+  dplyr::filter(Progress == '100' & Status == 'IP Address') %>%
+  dplyr::rename('ProlificID' = 'Q3', 'Advice' = '0.Advice',
+                'AdviserID' = '0.AdviserID','Guess'='0.Guess','GiverCondition' = '0.Treatment') %>%
+  dplyr::mutate(Bet = case_when(bet == 'Compete against the Low Performer Group' ~ 0,
+                                bet == 'Compete against the High Performer Group' ~ 1)) %>%
+  dplyr::select(ProlificID,ResponseId,Bet, Guess, Advice, AdviserID, GiverCondition) %>%
+  dplyr::mutate(GiverCondition = case_when(GiverCondition == 'E' ~ 1,
+                                           GiverCondition == 'None' ~ 0)) %>%
+  dplyr::mutate(Guess = as.numeric(Guess) )
+
+# randomly select one competitor
+AdviseeScore <- data.table::fread(here::here("Data/Cleaned Data/S1_time1_clean.csv"),
+                                  header = T,na.strings = '') %>%
+  dplyr::select(ProlificID, count, Condition, Gender, Age) %>%
+  dplyr::rename('AdviseeScore' = 'count', 'AdviseeCondition' = 'Condition')
+
+Competitors <- data.table::fread(here::here("Data/Cleaned Data/S1_Math50_cleaned.csv"),
+                                    header = T,na.strings = '') %>%
+  dplyr::select(ProlificID, Score)
+
+Competitors <- Competitors[order(-Competitors$Score),]
+
+HighGroup <- Competitors[1:20,]
+LowGroup <- Competitors[31:50,]
+
+
+CompetitorList <- list()
+ScoreList <- list()
+
+set.seed(807)
+
+for(i in 1:nrow(Advisee)){
+
+  random_num <- sample(20, 1)
+
+  if (Advisee[i,]$Bet == 1){
+    ID_i <- HighGroup[random_num,"ProlificID"]
+    Score_i <- HighGroup[random_num,"Score"]
+  }
+  if (Advisee[i,]$Bet == 0){
[…]

### 2024-01-01 R/clean_study2_time1.R

@@ -1,0 +1,15 @@
+library(dplyr)
+library(ggplot2)
+library(magrittr)
+
+targets <- data.table::fread(here::here("Data/Raw Data/S2_time1.csv"),
+                           header = T,na.strings = '')[-c(1,2)] %>%
+  dplyr::filter(Progress == '100') %>%
+  dplyr::select(ResponseId, PROLIFIC_PID,gender, age, ranking,ethnicity,education, QID7_Id) %>%
+  dplyr::mutate(ranking = gsub("st|nd|rd|th| rank| \\(most attractive\\)| \\(least attractive\\)", "", ranking),
+                ranking = as.numeric(ranking),age = as.numeric(age)) %>%
+  dplyr::filter(!is.na(ranking)) %>%
+  dplyr::rename('Guess' = 'ranking')
+
+saveRDS(targets, file = here::here("Data/Study2_time1.Rds"))
+targets %>% write.csv("Data/Cleaned Data/S2_time1_clean.csv")

### 2024-01-01 R/clean_study2_time2.R

@@ -1,0 +1,86 @@
+library(dplyr)
+library(ggplot2)
+library(magrittr)
+
+giver <- data.table::fread(here::here("Data/Raw Data/S2_time2.csv"),
+                           header = T,na.strings = '')[-c(1,2)] %>%
+  dplyr::filter(Progress == '100',gender != 'Other')%>%
+
+  dplyr::select(ResponseId, PROLIFIC_PID,dplyr::starts_with("ranking_"),dplyr::contains("_advice"),Condition,
+                gender, age, ethnicity,education, dplyr::starts_with("url.")) %>%
+  tidyr::pivot_longer('1_advice':'10_advice') %>%
+  dplyr::filter(!is.na(value)) %>%
+  dplyr::mutate(value = gsub("st|nd|rd|th| rank| \\(most attractive\\)| \\(least attractive\\)", "", value),
+                value = as.numeric(value))
+
+# clean the url
+url <-  giver %>% dplyr::select(ResponseId,dplyr::starts_with("url."))
+
+url <- apply(url[,2:11],2,function(x)
+  {
+    basename(x)
+  })
+
+url <- apply(url,2,function(x)
+  {
+    gsub("\\\\\\\\|.png$", "",x)
+  })
+
+url <- as.data.frame(url)
+
+giver <- giver %>% dplyr::select(-dplyr::starts_with("url."))
+giver <- cbind(giver,url)
+
+#find the 7th participant
+giverRank <- giver[,grepl('ranking_',names(giver))]
+
+giverRank <- as.data.frame(apply(giverRank, 2, as.numeric))
+
+for(i in 1:nrow(giver)){
+    rankList = as.list(giverRank[i,])
+    participant <- NA
+    if (length(rankList)==length(unique(rankList))){
+      urlList = as.list(url[i,])
+
+      #if (7 %in% rankList == TRUE){
+      targetNum <- which(rankList == 7)
+      #if (length(targetNum)==1){
+      participant <- dplyr::nth(urlList,targetNum[1])}
+    giver[i,'Target'] <- participant
+}
+giverStat <- giver %>% dplyr::filter(!is.na(Target)) %>% dplyr::rename('Advice' = 'value')
+
+
+#calculate final ranking for each selfie
+selfie <- data.table::fread(here::here("Data/Raw Data/S2_time1.csv"),
[…]

### 2024-01-01 R/clean_study2_time3.R

@@ -1,0 +1,34 @@
+library(dplyr)
+library(ggplot2)
+library(magrittr)
+
+
+Target <- read.csv("Data/Cleaned Data/S2_time1_clean.csv")[-c(1,2)]  %>%
+  dplyr::mutate(Guess = as.numeric(Guess))
+
+
+Receiver <- data.table::fread(here::here("Data/Raw Data/S2_time3.csv"),
+                              header = T,na.strings = '')[-c(1,2)]  %>%
+  dplyr::filter(Progress == '100')%>%
+  dplyr::select(ResponseId, PROLIFIC_PID, bet:sincere, advice.0.finalRank,rank) %>%
+  dplyr::mutate(bet = gsub("st|nd|rd|th| rank| \\(most attractive\\)| \\(least attractive\\)", "", bet),
+                bet = as.numeric(bet), rank = as.numeric(rank),advice.0.finalRank = as.numeric(advice.0.finalRank) ) %>%
+  dplyr::mutate(dplyr::across(c(likable:sincere),
+                              ~ dplyr::case_when(grepl("Not at all", .) ~ 1,
+                                                 grepl("Slightly", .) ~ 2,
+                                                 grepl("Somewhat", .) ~ 3,
+                                                 grepl("Very", .) ~ 4,
+                                                 grepl("Extremely", .) ~ 5))) %>%
+  dplyr::mutate(warmAvg = rowMeans(select(.,c('warm','well-intentioned','friendly','good-natured')))) %>%
+  dplyr::mutate(trustAvg = rowMeans(select(.,c('trustworthy','sincere'))))
+
+Receiver <- merge(Receiver,Target,by = 'PROLIFIC_PID') %>% dplyr::rename('Advice' = 'rank', 'Final Rank' = 'advice.0.finalRank')
+
+Advice <- read.csv("Data/Raw Data/S2_Advice200.csv")[-c(1,2)] %>%
+  dplyr::select(PROLIFIC_PID,Giver_Id,Condition)
+
+
+Receiver <- merge(Receiver,Advice,by= 'PROLIFIC_PID')
+
+saveRDS(Receiver, file = here::here("Data/Study2_time3.Rds"))
+Receiver %>% write.csv("Data/Cleaned Data/S2_time3_clean.csv")

### 2024-01-04 Advice Giving.Rmd
Change based on AOM submission

@@
 ---
-title: "Interpersonal Benefits of Flattering Advice"
+title: "Flattering Advice: Avoiding Disappointment as a Driver of Gender Discrimination"
 shorttitle        : "Flattering Advice"
@@
    - \maxdeadcycles=1000
+bibliography      : bibliography.bib
 output: 
@@
 
+study1_math50 <- read.csv(here::here("Data/Cleaned Data/S1_Math50_cleaned.csv"))
+study1_time1All <- readRDS(here::here("Data/Study1_time1All.Rds"))
 study1_time1 <- readRDS(here::here("Data/Study1_time1.Rds"))
@@
 # Introduction
-Gender differences have been documented in various domains and attract plenty of scholarly attention to explain underlying causes.
-Extent research largely focuses on internal factors, such as cognitive styles, preference, personal beliefs, assuming females and males want to do different things.
-Another source of such differences may be the advice that people receive.
-Prior work has documented that men receive more aspirational advice and women more risk-averse advice, which may explain why women are less likely to apply for and ultimately obtain more rewarding positions.
-Research in this line of gender discrimination has emphasized the role of unconscious bias, but interventions that try to reduce this bias have been largely unsuccessful.
-This paper propose a novel source of differences in advice by drawing on recent work on belief-based utility, expectation-based reference points, and the hedonic consequences of information.
-Specifically, we hypothesize that receiving information that is less favorable than one expects imposes a psychological cost on the recipient, because it is disappointing and suggests a less favorable future than one imagined.
-If people anticipate this cost when giving advice, they may be overly favorable or optimistic so as to protect the advisee’s belief utility.
-That is, they may not (only) give the advice that they believe will lead to the best decision but are also motivated to avoid disappointing the recipient.
-This requires the formation of beliefs about the advisee’s expectations, which is where we propose the differential treatment of men and women arises.
-Prior work has documented that men are more overconfident than women, conditional on equal performance, and that people anticipate this difference.
-An adviser who seeks to avoid disappointment and incorporates expectations into their advice would then present more favorable advice to male advisees than to female advisees.
-While the interpersonal concern has not been fully investigated as a source of gender difference regarding advice giving, its assumption, the hedonic consequences of information have been well documented.
-Research in economics and psychology has found that people avoid information that could make them feel bad, even when doing so leads to worse decisions.
-Recipients of information are even found to blame the people who deliver undesirable message, even though the messenger are not responsible for the situation.
-Advice is predicted to trigger a more intense emotional response because it is assumed to be tailored for its target, and reflects how the giver see the target.
-Individuals tend to desire positive social images and are protective when it comes to others' evaluation of them, and accordingly, prefer advice that implies a positive evaluation.
-However, we are unaware of research documenting whether people take this into account when advising others.
+Seeking and giving advice can be challenging conversations to navigate.
+Advice seekers may be embarrassed to ask for help [@Benabou2022], and they may fail to do so if the information they receive could lead to disappointment [@Gill2012].
+Indeed, people prefer advisers who withhold unpleasant information [@Shalvi2019] and punish those who tell them things they do not want to hear [@John2019].
+People appear to engage in strategic selection of advice to avoid unpleasant information and protect the utility they get from positive beliefs about themselves and the future they anticipate [@Loewenstein2018; @Loewenstein1987].
+But do advice givers anticipate and consider the hedonic cost of honest information to the recipient?
+While previous work has emphasized the instrumental value of advice (e.g., satisfaction with a decision or accuracy of a prediction), we focus on the motivations of the person providing advice.
 
-# A. Our study
-We test whether gender difference in receiving advice is driven by givers' intention to meet target's expectation and avoid disappoint them.
-We report results from two preregistered experiment in which the interactions without deception between advice givers and recipients are captured.
-In each experiment, we first measure actual level and expectations of advisees, then provide these information to givers and collect advice.
-Lastly, we present advice to their targets, ask advisees to make final decision, and measure the utility of the advice.
-We predict and find that males receive flattering advice than female counterparts when advisers take target's expectations into account.
-If advice for both gender is solely based on actual performance, there exists no gender difference regarding the chance of receiving aggressive advice.
-But when expectation of the target is provided along with actual performance, advisers consider this irrelevant information and give more aggressive advice to males because they have higher expectations for themselves compared with equally competent females.
-We also directly test the reason why advisers provide flattering advice.
-We compare advice given under the treatment condition where interpersonal concerns is the goal with that of baseline condition where, like usually assumed, effectiveness of facilitating decision making is emphasized.
-Advisers are more likely to inflate their advice so that it delivers a positive evaluation of its target when they hold interpersonal concerns and want to be liked by the target.
+Research on advice has largely focused on settings that do not tackle belief utility.
+For example, participants may have been asked to estimate the number of balls in an urn or choose from pairs of lotteries [@Benjamin2015].
+Advisers have been shown to be motivated to give accurate advice [@Jonas2003], and engage in perspective-taking to meet the preferences of the advisee [@Kray2000; @Kray1999].
+When they are uncertain, they prefer that advisees do not rely (extensively) on their recommendations [@Ache2020].
+Thus, it seems that people are concerned about providing good advice even when they are not incentivized for the recipient’s decision quality.
 
-# B. Related Literature
-People frequently obtain information by soliciting the advice of those with more expertise about or insight into an issue.
-A substantial literature has studied how people incorporate advice and whose advice they seek out.
-Briefly, people put less than optimal weight on the advice they receive, and prefer advice from those who are overconfident or who provide favorable information.
-Indeed, people punish advisers who tell them things they do not want to hear.
-Most of the studies in this stream of research have relied on deception and do not involve real people in the role of advisers; studies of advisers themselves remain scarce.
+In many real settings, however, advice incorporates beliefs about the recipient.
+Someone recommending an expensive restaurant conveys that they think the advisee is wealthy enough to afford an expensive meal, and someone recommending a student pursue a PhD in economics assumes that they are intellectually capable.
+Conversely, telling a poorly performing student to switch to a less-demanding major conveys a belief that the student is not capable of improving.
+Thus, the painful truth may prevent someone from making a bad decision, it may come at a cost to the recipient and damage the relationship between the adviser and advisee.
+We propose that advisers take these costs into account, even when the interactions are entirely anonymous and they are incentivized for the quality of the advisee’s decision.
 
-Notably, prior work on advice has emphasized the instrumental value of information, examining the extent to which the advice improves the quality of or satisfaction with a decision.
-In the proposed project, we will focus on the signaling value of advice: what does the advice imply about the adviser’s perception of the advisee?
-We propose that “flattering” advice creates a perception that the adviser holds the advisee in high esteem, and that this in turn increases the advisee’s liking for the adviser.
-Such interpersonal considerations may be as important (or even more important) in cases where it is difficult to evaluate ex post whether the advice was good or not.
+Specifically, we focus on the signaling value of advice: what does the advice imply about the adviser's perception of the advisee?
+We propose that advisees have expectations about the advice they receive and treat this as a reference point [@Koszegi2006].
+Advice that falls short of these expectations creates disappointment, while advice that exceeds them is flattering and creates positive interpersonal benefits because it creates a perception that the adviser holds the advisee in high esteem.
+Such interpersonal considerations may be as important, if not more important, to the adviser than the instrumental value of the advice: the adviser directly experiences a souring relationship, but may suffer little and only much delayed consequences if an advisee makes a poor life decision.
 
-Prior work has further documented that men and women receive different performance feedback at work.
-Managers are less likely to provide critical feedback to women, believing that doing so would hurt their feelings.
-Thus, interpersonal concerns can undermine constructive feedback, which then harms outcomes because it deprives the advisee of a learning opportunity.
-While this effect at first glance appears counter to our hypotheses (here, men receive more negative feedback), it is driven by different beliefs.
-Managers withhold critical feedback because they (perhaps incorrectly) believe that women suffer a greater cost from criticism.
-Our hypothesized effect is driven by (accurate) beliefs about performance expectations.
-While advice also communicates beliefs about ability, it does not do so through criticism.
+Our account therefore predicts that people receive advice that is more flattering and suggestive of inflated ability and optimistic outcomes than would advice in the absence of such interpersonal considerations.
+However, we propose that this is not true for all advisees equally.
+Presenting flattering advice requires the formation of beliefs about the advisee's expectations (reference point).
+@Exley2022 show that men are more overconfident than women, conditional on equal performance and that people anticipate but fail to incorporate this difference into their decisions.
+An adviser who seeks to avoid disappointment and incorporates expectations into their advice would then present more favorable advice to male advisees than to female advisees (see Figure 1 for an illustration).
+This provides a novel account for a well-known finding that men receive more aspirational advice than do women [@Kanze2018].
+
+Notably, when it pays to have accurate beliefs, such flattering advice would come at a cost: while men would be more likely to aim higher, they would also suffer greater costs from aiming too high and failing to meet the objective.
+This may seem at odds with a gender gap favoring men.
+However, observational data often miss people who were unsuccessful.
+For example, job candidates who ask for a high starting salary may be less likely to receive a job offer, but will also have a higher starting salary conditional on receiving an offer.
+
+In a large, preregistered experiment (n = 2,000), we show that advisers consider the expectations of advisees, even when such expectations do not provide informative insights for the underlying decision-making problem.
+We find that as a result, showing expectations (but not gender) to advisers leads men to receive more aspirational advice than women.
+Incorporating expectations leads to worse advice, even when advisers are incentivized based on the outcome of the advisee’s decision.
+In a second preregistered experiment (n = 700), we show that advisers respond to interpersonal considerations.
+They advice people that they are more attractive than they believe them to be, and inflate to a greater extent when incentivized for likability rather than accuracy.
+Advisees indeed reward such flattering advice, finding the advisers more likeable and no less trustworthy than those who provide more accurate advice.
+
+# Open Science Statement
+We report all sample sizes, data exclusions, all manipulations, and all measures in the studies.
+Screen captures of the experimental materials are available in the Supplemental Information.
+The complete data, code to reproduce all statistical analyses and figures in the manuscript, as well as the preregistration reports are available via OSF.
+All our studies were preregistered on AsPredicted.org.
+(will do this later)
 
 # Study 1
-In this study, we conducted an initial test to examine whether individuals take others' self-expectations into account when giving advice.
-Specifically, we predicted that people would adjust their advice to match the advisees' expectations of themselves, even when these expectations are not informative for the underlying decision problem.
-This study was preregistered on AsPredicted (https://aspredicted.org/R44_6SR).
+We begin by examining whether advisers take the expectations of advisees into account, even when those expectations are not relevant to the quality of advice.
+In a three-stage experiment, we first recruit a sample of advisees and ask them to complete a mathematics quiz.
+After answering all ten multiple-choice questions, participants are anchored to low or high performance expectations and asked to guess how many questions they answered correctly.
+Next, we recruit advice givers and show them either only the true performance of the advisee, or the true performance and how many questions they guessed they answered correctly.
+Advisers are tasked with recommending whether the advisee should compete against a group of high-performers or a group of low-performers on the mathematics quiz.
+Finally, we invite the advisees back and show them the advice they have received.
+Advisees then pick whether to compete against high or low performers, based on their past performance on the quiz.
+Our key hypothesis is that advisees who were anchored to high expectations would be more likely to receive advice to compete against the high performer group.
 
 ## Methods
-We recruited `r scales::comma(dim(study1_time1)[1])` participants (`r round(mean(study1_time1$Gender == "Female")*100)`\% Female, $M_{\text{Age}}$ = `r mean(study1_time1$Age)`) from Prolific Academic to take math test and another `r scales::comma(dim(study1_time2_giver)[1])` (`r round(mean(study1_time2_giver$gender == "Female")*100)`\% Female, $M_{\text{Age}}$ = `r mean(study1_time2_giver$age)`)
-This study consisted of three stages involving recipients of advice taking an exam in Stage 1, givers providing advice in Stage 2, and recipients reacting to advice in Stage 3.
-During Stage 1, participants were asked to answer ten math questions in five minutes and were informed that they would receive 10 cents for each question they answered correctly.
-Participants were also asked to predict how many questions they would answer correctly.
-We manipulated their self-expectations by randomly assigning participants to either a High or Low Expectation condition.
-In the High Expectation condition, participants were informed that the average score of five other participants who took the same test was 6.4, while those in the Low Expectation condition were told that the average score was 2.6.
-We incentivized their performance in the math test to increase their attachment to the task.
-The number of correct answers and their predictions represented the recipients' performance and expectations, respectively, and were shown to advice givers.
-After collecting performance and expectations from recipients, we recruited `r scales::comma(dim(study1_time2_giver)[1])`  participants and informed them of the results of the mathematics quiz completed by the first group of participants.
-Their task was to give advice to the previous participants about whether to compete against a group of "high" performers or a group of "low" performers (the top 20 and bottom 20 performers out of a separate group of 50 participants who completed the mathematics quiz).
-Advisees could earn a bonus if they performed as well or better than a randomly selected member of their chosen group, and the bonus differed depending on the group they chose (50 cents and 30 cents for the high-performing and low-performing group, respectively).
-Advisers received a bonus identical to the one earned by one of their advisees.
-They provided advice to 10 randomly selected advisees, and we clustered standard errors at the level of Stage 2 participants in subsequent analyses accordingly.
-We randomly assigned advisers to one of two conditions: they either observed only the true performance of the advisee (“Baseline” treatment), or they observed the true performance and the participant's own estimate of their performance (“Information” treatment).
-To give givers some sense of this task, we told them the average scores for a previous batch of 50 quiz-takers were 4.42.
-It is important to note that the advisee's own guess provided no information about the likelihood of winning against either the high or low group, as the outcome was based on past performance and not performance on a subsequent test.
-Lastly, we invited the recipients back, reminded them of their previous self-expectations, and informed them that they could earn a bonus if they performed as well or better than a competitor.
-They could decide where that competitor was randomly drawn from, a group of "high" performers or a group of "low" performers.
-If they scored the same or higher than that competitor, they could earn a bonus, whose value differed depending on the group they chose (50 cents and 30 cents for the high-performing and low-performing group, respectively).
-Recipients were told that an external observer had provided a piece of advice.
-They then read the advice and made their decisions about who they wanted to compete with.
+```{r}
 
-## Open Science Statement
-We report all manipulations, measures, and data exclusion in this and the following study. 
-The preregistration reports, screenshots of all experimental materials, and 
-the analysis code to replicate all statistical analyses and figures are
-available on the Open Science Framework (will do this later).
+subgroup_averages <- data.frame(subgroup = numeric(), avg_score = numeric())
+set.seed(807)
+# loop through 1000 iterations of randomly selecting 10 participants and computing their average score
+for (i in 1:1000) {
+  # randomly select 10 participants
+  subgroup <- sample(study1_math50$ProlificID, size = 5, replace = FALSE)
+  # compute the average score for the selected participants
+  subgroup_avg <- mean(study1_math50$Score[study1_math50$ProlificID %in% subgroup])
+  # add the subgroup and its average score to the dataframe
+  subgroup_averages <- rbind(subgroup_averages, data.frame(subgroup = i, avg_score = subgroup_avg))
+}
+
+p5 <- quantile(subgroup_averages$avg_score, probs = 0.05)
+p95 <- quantile(subgroup_averages$avg_score, probs = 0.95)
+
+sortedScore <- sort(study1_math50$Score, decreasing = TRUE)
+LP_lower <- sortedScore[50]
+LP_upper <- sortedScore[31]
+HP_lower <- sortedScore[20]
+HP_upper <- sortedScore[1]
+
+```
+
+We first recruited a sample of `r scales::comma(dim(study1_math50)[1])` participants from Prolific to complete a 10-question multiple choice mathematics quiz.
+The questions were taken from a paper-version of the ASVAB standardized exam, such that answers were not available online.
+Participants had 5 minutes to answer the quiz and were paid 10 cents for each correctly answered question.
+We define the top 20 scorers as the “High Performers” and the bottom 20 scorers as the “Low Performers.” On average, participants answered `r round(mean(study1_math50$Score),2)` questions correctly, High Performers scored between `r HP_lower` and `r HP_upper`, and Low Performers scored between `r LP_lower` and `r LP_upper`.
+We further simulated 1,000 pairings of groups of five participants, with the 5 th percentile of groups scoring an average of `r p5` and the 95 th percentile scoring an average of `r p95`.
+We use these participants as the competitors for the advisees in our main experiment, and the average group scores to anchor expectations.
+
+Next, we recruited `r scales::comma(dim(study1_time1All)[1])` participants in Stage 1 of our main experiment, for the role of advisees.
+To arrive at a gender-balanced sample, we dropped the last two male participants to complete the survey, ending up with a sample of 500 men and 500 women ($M_{\text{Age}}$ = `r mean(study1_time1$Age)`,50\% Female,).
+Participants completed the same 10-item mathematics quiz as the earlier participants and were informed that their performance would affect their bonus earnings in a follow-up study to be conducted a few days later.
+After completing the quiz, we informed them of the average score of a group of five participants from the preliminary survey.
+We randomly assigned them to learn about the 5 th percentile of groups, which scored `r p5`.
+(“Low Expectations” treatment) or the 95 th percentile of groups, which scored `r p95` (“High Expectations” treatment).
+Participants then made a guess (unincentivized) about how many questions they think they answered correctly.
+The survey concluded with basic demographic questions.
+
+We then recruited `r scales::comma(dim(study1_time2_giver)[1])`  participants for Stage 2, placing them in the role of advisers.
+We began by informing them of the mathematics quiz that participants in the preliminary study and Stage 1 had completed, and informed them of the average score in the preliminary study.
+Advisers had to recommend whether an advisee should compete against the Low Performers or the High Performers (we used these terms in the survey).
+We anticipated that being told to compete against High Performers is more flattering.
+Advisees would earn 30 cents if their score was equal to or higher than a randomly selected member of the Low Performer group and they chose to compete against this group, or 50 cents if they performed as well or better than a randomly selected member of the High Performer group.
+If they scored lower, they would not receive any bonus.
+
+Advisers were randomly assigned to one of two treatments.
+In the “Baseline” treatment, they only observed the score of the advisee on the mathematics quiz.
+In the “Expectation” treatment, they observed the score as well as the advisee’s guess for how many questions they answered correctly.
+Note that since the outcome is determined only by the past score on the quiz, the advisee’s guess is immaterial to which group they should compete against, and in neither treatment did they receive any demographic information about their advisee.
+Participants gave recommendations to 10 advisees, which unbeknownst to them were five men and five women matched to have identical performance on the test.
+They were informed that if their advice was shown to a participant who returned for the follow-up survey, they would receive the identical bonus as that participant.
+The survey also concluded with basic demographic questions.
+Finally, we invited participants from Stage 1 back for the follow-up survey.
+Following our preregistration, we kept the survey open for 7 days.
+In total, `r scales::comma(dim(study1_time3)[1])`  participants (`r scales::comma(dim(study1_time3[study1_time3$Gender == 'Male',])[1])` men, `r scales::comma(dim(study1_time3[study1_time3$Gender == 'Female',])[1])` women) returned.
+The brief survey reminded them of the task they completed in Stage 1, informed them that other participants from Prolific had observed their real score and given them advice against which group to compete against, and finally were reminded about how many questions they guessed they had answered correctly.
+Importantly, they were not informed of their true score or the score of the groups they could compete against.
+Participants then observed the advice from a randomly selected adviser and made their decision.
 
@@
 # Fit linear regression model
-model1 <- lm(Guess ~ Condition + count, data = study1_time1)
+study1_advice <- study1_advice %>% dplyr::mutate(ExpShow = ifelse(Condition == 'E',1,0))
+
+model1 <- lm(Guess ~ Gender + count, data = study1_time1)
 model1_apa <- apa_print(model1)
-
-model2 <- lm(Guess ~ Gender + count, data = study1_time1)
-model2_apa <- apa_print(model2)
 ```
@@
 ## Results
-We begin by analyzing the performance and expectations of Stage 1 participants, as they will serve as input for Stage 2 participants and influence their advice.
-We compare the performance and expectations of participants in High and Low Expectation conditions, where they are told the average score for a five-participant group is 6.4 or 2.6.
-Although we randomly assigned participants, those in the Low Expectation condition scored slightly higher than those in the High Expectation condition (`r round(mean(study1_time1[study1_time1$Condition == "Low",]$count),2)` and `r round(mean(study1_time1[study1_time1$Condition == "High",]$count),2)`, respectively, `r papaja::apa_print(t.test(count ~ Condition, data = study1_time1, var.equal = T))$statistic`).
-However, the gap is not significant.
-Participants in the High Expectation condition had worse performance, but they also indicated a significantly higher guess of their score than their counterparts in the other condition (`r round(mean(study1_time1[study1_time1$Condition == "Low",]$count),2)` and `r round(mean(study1_time1[study1_time1$Condition == "High",]$Guess),2)`, respectively, `r papaja::apa_print(t.test(Guess ~ Condition, data = study1_time1, var.equal = T))$statistic`).It makes our experiment a conservative test.
-The gap between their expectations is `r round(mean(study1_time1[study1_time1$Condition == "High",]$Guess),2) - round(mean(study1_time1[study1_time1$Condition == "Low",]$Guess),2)`, which is not marginal considering the average expectations for all participants is only `r round(mean(study1_time1$Guess),2)`.It is worth mentioning that participants from both conditions reported having a hard time answering the math test, and thus, they are underconfident.
-However, participants from the High Expectation condition expected to solve more, indicating a successful manipulation.
-Despite the manipulation, the expectations are significantly correlated with the actual performance (`r model1_apa$estimate['count']`, `r model1_apa$statistic['count']`).
-Next, we examine gender differences and find that male participants performed slightly better than female participants, and the gap is significant (`r round(mean(study1_time1[study1_time1$Gender == "Male",]$count),2)` and `r round(mean(study1_time1[study1_time1$Gender == "Female",]$count),2)`, respectively, `r papaja::apa_print(t.test(count ~ Gender, data = study1_time1, var.equal = T))$statistic`).
-On average, males are more confident than females, as they predicted to answer more questions correctly (`r round(mean(study1_time1[study1_time1$Gender == "Male",]$Guess),2)` and `r round(mean(study1_time1[study1_time1$Gender == "Female",]$Guess),2)`, respectively, `r papaja::apa_print(t.test(Guess ~ Gender, data = study1_time1, var.equal = T))$statistic`).
-We conducted an OLS regression with the performance and gender of participants and found that with the same score, male participants are more confident than their female counterparts (`r model2_apa$estimate['GenderMale']`, `r model2_apa$statistic['GenderMale']`).
+We begin by examining the performance of the Stage 1 participants.
+Because our treatment takes place after participants complete the mathematics quiz, we would not expect a difference in performance across the Low and High Expectations treatments.
+Indeed, the two groups scored no different from one another (`r round(mean(study1_time1[study1_time1$Condition == "Low",]$count),2)` and `r round(mean(study1_time1[study1_time1$Condition == "High",]$count),2)` for Low and High Expectations treatments, respectively, `r papaja::apa_print(t.test(count ~ Condition, data = study1_time1, var.equal = T))$statistic`).
+The expectations treatment did, however, affect how well they thought they performed.
+Participants in the “Low Expectations” treatment guessed a score of `r round(mean(study1_time1[study1_time1$Condition == "Low",]$count),2)` vs.
+`r round(mean(study1_time1[study1_time1$Condition == "High",]$Guess),2)` in the High Expectations treatment (`r papaja::apa_print(t.test(Guess ~ Condition, data = study1_time1, var.equal = T))$statistic`), showing that the manipulation was successful.
+Contrary to our expectations, we did find a gender difference in performance: men scored `r round(mean(study1_time1[study1_time1$Gender == "Male",]$count),2)` on average, while women scored `r round(mean(study1_time1[study1_time1$Gender == "Female",]$count),2)` (`r papaja::apa_print(t.test(count ~ Gender, data = study1_time1, var.equal = T))$statistic`).
+This difference, however, does not affect the interpretation of our findings, which will rely on an interaction of gender with an experimental treatment for Stage 2 participants.
+Consistent with this difference, men thought they answered more questions correctly than did women (`r round(mean(study1_time1[study1_time1$Gender == "Male",]$Guess),2)` vs `r round(mean(study1_time1[study1_time1$Gender == "Female",]$Guess),2)`, `r papaja::apa_print(t.test(Guess ~ Gender, data = study1_time1, var.equal = T))$statistic`).
 
-```{r}
-library("papaja")
-# Fit linear regression model
-model3 <- lm(Advice ~ Treatment + Performance, data = study1_advice %>% dplyr::filter(Condition == "E"))
-model3_apa <- apa_print(model3)
-
-model4 <- lm(Advice ~ Guess + Performance, data = study1_advice %>% dplyr::filter(Condition == "E"))
-model4_apa <- apa_print(model4)
-
-study1_advice <- study1_advice %>% dplyr::mutate(ExpShow = ifelse(Condition == 'E',1,0))
-
-```
+We conducted an OLS regression with the performance and gender of participants and found that with the same performance, male participants are more confident than their female counterparts (`r model1_apa$estimate['GenderMale']`, `r model1_apa$statistic['GenderMale']`).
 
 ```{r study1regs}
-modelsummary::modelsummary(list(`(1)` = lm(Advice ~ ExpShow*Gender , data = study1_advice),
+study1_advice <- study1_advice %>% dplyr::mutate(TreatmentHigh = ifelse(Treatment == 'High',1,0))
+
+modelsummary::modelsummary(list(`(1)` = lm(Advice ~ TreatmentHigh + Performance , data = study1_advice %>% dplyr::filter(ExpShow == 1)),
                                 `(2)` = lm(Advice ~ ExpShow*Gender , data = study1_advice),
                                 `(3)` = lm(ExpectedBonus ~ ExpShow*Gender, data = study1_advice)),
-                           vcov = c("classical", ~GiverID,~GiverID),
-                            coef_map = c("ExpShow" = "Expectation Shown",
+                           vcov = c(~GiverID, ~GiverID,~GiverID),
+                            coef_map = c("TreatmentHigh" = "High Expectation",
+                                         "Performance" = "Performance",
+                                         "ExpShow" = "Expectation Shown",
                                         "GenderMale" = "Advisee Male",
@@
                            gof_map = list(list('raw' = 'nobs', 'clean' = 'N', 'fmt' = 0)),
-                           caption = "Advice of competing against High Performance group, based on the gender of targets and whether their expectation is shown to adviser (Column 1).
-Column 2 show the results where standard errors are clusterd at the level of adviser.
-Expeccted Bonus of advice received, based on the gender of targets and whether their expectation is shown to adviser (Column 3)") %>%
+                           caption = "Column 1 displays the advice given to compete against a High Performance group based on whether the advisees were primed with low or high expectations and the expectation level shown to the advisor.
+Column 2 displays the advice given to compete against a High Performance group based on the gender of the targets and the expectation level shown to the advisor.
+Column 3 displays the expected bonus of the advice received based on the gender of the targets and the expectation level shown to the advisor.
+All results are clustered at the level of the advisor and include standard errors.") %>%
   kableExtra::kable_styling(latex_option = "scale_down")
@@
 
-```{r study1gender, fig.cap="When expectation is shown to the adviser"}
-
+```{r study1genderdiff, fig.cap ="Male participants are more likely to be recommended to compete against the High Performer group than female counterparts, holding performance the same."} 
+library(dplyr)
 library(ggplot2)
-study1_advice <- study1_advice %>% dplyr::mutate(advice = as.numeric(Advice) )
+library(magrittr)
 
 ProbHG <- study1_advice %>%
-  dplyr::group_by(Condition, Performance, Gender) %>%
-  dplyr::summarize(avg_hardGroup = mean(advice))
+  group_by(Condition, Performance, Gender) %>%
+  dplyr::summarize(avg_hardGroup = mean(Advice))
 
@@
 
-#it returns warning messages
-#but I suppress them
 ggplot(df_exp, aes(x = Performance, y = avg_hardGroup, color = Gender)) +
-  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = FALSE) +
+  geom_smooth(method = "glm", method.args = list(family = "binomial"),se = FALSE) +
   geom_smooth(data = df_none, aes(x = Performance, y = avg_hardGroup),
@@
 ```
+Next, we examine whether advisers took the advisee’s expectations into account.
+Column 1 of Table \@ref(tab:study1regs) reports a linear probability model on advising to compete against the High Performer group for advisers in the “Expectations” treatment.
+Because each adviser was paired with ten advisees, we cluster standard errors at the adviser level.
+Consistent with our prediction, we find that advisees in the High Expectation condition are more likely to be recommended to compete against the High Performer Group, but the result is not significant.
 
-In Stage 2, we collected `r scales::comma(dim(study1_advice)[1])` pieces of advice for `r scales::comma(dplyr::n_distinct(study1_advice$Target))` Advisees.
-To exclude between-person differences from advice givers, we clustered standard errors at the level of the Stage 2 participants when running OLS regression.
-We conducted an OLS regression with the performance and Advisee Treatment (High or Low Expectation) for the subset of Stage 2 participants in the “Information” Treatment.
-Although Advisees in the High Expectation condition are more likely to be recommended to compete against the High Performer Group, the result is not significant (`r model3_apa$estimate['TreatmentLow']`, `r model3_apa$statistic['TreatmentLow']`).
-This may be because the confidence difference (`r round(mean(study1_advice[study1_advice$Treatment == "High",]$Guess),2) - round(mean(study1_advice[study1_advice$Treatment == "Low",]$Guess),2)`) is too minor for advice givers to take more risk.
-Only `r round(mean(study1_advice$Advice),4)*100`\% of the time, advice givers recommended the High Performer group as the competitor, and the average scores for those who received this advice is `r round(mean(study1_advice[study1_advice$Advice == 1,]$Performance),2)`, which is about at the `r round(ecdf(study1_advice$Performance)(6.64) * 100)`th  percentile in the performance distribution shown to the advice givers.
-However, if we run an OLS regression with performance and the exact expectations of Advisees, the expectation does increase the chance of receiving aggressive advice (`r model4_apa$estimate['Guess']`, `r model4_apa$statistic['Guess']`).
-In Stage 2, each participant always sees five females and five males with the same score distribution, and the only difference lies in their expectations.
-Therefore, we predict that there will be no gender difference when advice givers only see performance, but males will receive more aggressive advice when their expectations are presented.
+To test whether expectations can lead to more flattering advice for men than for women, we report a linear probability model with advice to compete against the high group as the outcome measure, and the advisee’s gender, whether expectations were shown to the adviser, and the interaction of the two (Column 2 of Table \@ref(tab:study1regs)).
+As predicted, we find a significant interaction effect: men are more likely to be advised to compete against the High Performers when expectations are shown than when they are hidden (p < 0.001; see Figure \@ref(fig:study1genderdiff),).
+
+To examine the quality of advice, we computed the expected bonus earnings for all recommendations.
+We made this calculation by assuming that participants adopted the advice and competed against the recommended competitor group.
+We then compared their scores with all 20 possible competitors one by one and calculated the bonus accordingly to determine the expected bonus earnings.
 We conducted an OLS regression with whether givers see the expectation (Baseline or Information condition) and the gender of the Advisee (Female or Male), as well as their interaction.
-In line with our prediction, only when expectations are known to the advice giver, male participants have a higher chance of being recommended to compete against the High Performer group (Column 2 of Table \@ref(tab:study1regs) ).
-As seen in Figure \@ref(fig:study1gender), gender differences emerge as a result of showing expectations.
-Because we only have advice for `r scales::comma(dplyr::n_distinct(study1_advice$Target))` Advisees, to ensure that every participant in Stage 1 receives advice, we recruited `r scales::comma(dim(study1_time2_giver50)[1])` more participants to collect more advice for the other `r 1000-as.numeric(scales::comma(dplyr::n_distinct(study1_advice$Target)))` participants for Stage 1.
-We did not include any of this advice in the analysis of Stage 2 results.
+Supporting our theory, male participants will receive less bonus given advice they receive (b = -0.005, p < .01; see also Column 3 of Table \@ref(tab:study1regs)
+
 ```{r}
-library("papaja")
-# Fit linear regression model
-study1_time3 <- study1_time3 %>% dplyr::mutate(HighExp = ifelse(AdviseeCondition=='High',1,0))
+study1_time3 <- study1_time3 %>% dplyr::mutate(AdviseeConditionHigh = ifelse(AdviseeCondition =='High',1,0))
 
-model5 <- lm(bonus ~ HighExp + AdviseeScore, data = study1_time3 %>% dplyr::filter(GiverCondition == 1))
-model5_apa <- apa_print(model5)
+model2 <- lm(bonus ~ AdviseeConditionHigh + AdviseeScore, data = study1_time3)
+model2_apa <- apa_print(model2)
+
+model3 <- lm(Bet ~ Gender + AdviseeScore, data = study1_time3)
+model3_apa <- apa_print(model3)
 
 ```
+Finally, we look at the actual earnings of advisees.
+Although participants in the High Expectation condition earned less, this difference is not significant (`r model2_apa$estimate['AdviseeConditionHigh']`, `r model2_apa$statistic['AdviseeConditionHigh']`).
 
-Among `r scales::comma(dim(study1_time1)[1])` participants, `r round(dim(study1_time3)[1]/dim(study1_time1)[1]*100,2)`% of them returned for the Stage 3 experiment.
-Of all advice shown to Advisees, `r dim(study1_time3[study1_time3$GiverCondition==1,])[1]` of them are from givers in the ‘Information’ treatment condition, and the other `r dim(study1_time3[study1_time3$GiverCondition==0,])[1]` are from givers in the ‘Baseline’ treatment condition.
-To examine the impact of flattering advice on performance, we first looked at advice from givers who know the expectations of Advisees.
-We conducted an OLS regression with performance and Treatment condition (High or Low Expectation) of Advisees.
-As predicted, participants in the High Expectation condition received less (`r model5_apa$estimate['HighExp']`, `r model5_apa$statistic['HighExp']`), but it is not significant.
-We realize this result is less powerful because the advice presented was randomly selected and advisees who return to this follow-up survey also bring noise.
-To avoid randomness, we computed the Expected Bonus for all `r scales::comma(dim(study1_advice)[1])` advice we collected in Stage 2, assuming they are adopted by the Advisees.
-We conducted an OLS regression with whether givers see the expectation (Baseline or Information condition) and the gender of the Advisee (Female or Male), as well as their interaction.
-Supporting our theory, male participants will receive less bonus given advice they receive (Column 3 of Table \@ref(tab:study1regs) ).
-It implies that when males receive more aggressive advice (competing against the High Performer group), they end up worse because this kind of advice is not necessarily based on their actual condition.
+We found that males are more competitive to the extent that they are more likely to choose to compete against High Performer group (`r model3_apa$estimate['GenderMale']`, `r model3_apa$statistic['GenderMale']`), holding performance the same.
+
+## Discussion
+In Study 1, we discovered that although advisers are encouraged to provide accurate advice, they still take into account the expectations of advisees, which are irrelevant to the utility of the advice.
+Due to the fact that males tend to be more confident than their equally competent female counterparts, they are more likely to be recommended to compete against high-performance competitors.
+However, when advice is given to match the advisees' expectations, these flattering recommendations result in lower expected bonus earnings for male participants.
 
@@
 library(dplyr)
+library(ggplot2)
 
@@
 Notably, however, we were not powered to do a comparison across the two experimental groups.
+
+# References
+
+```{=tex}
+\begingroup
+\singlespacing
+\setlength{\parindent}{-0.2in}
+\setlength{\leftskip}{0.2in}
+\noindent
+```
+::: {#refs}
+:::
+
+```{=tex}
+\endgroup
+```

### 2024-01-04 Advice-Giving.tex
Change based on AOM submission

@@
 \fi
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
+  % set entry spacing
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 \ifLuaTeX
@@
 \hypersetup{
-  pdftitle={Interpersonal Benefits of Flattering Advice},
+  pdftitle={Flattering Advice: Avoiding Disappointment as a Driver of Gender Discrimination},
   pdfauthor={Amanda Chen1 \& David Hagmann1},
@@
 
-\title{Interpersonal Benefits of Flattering Advice}
+\title{Flattering Advice: Avoiding Disappointment as a Driver of Gender Discrimination}
 \author{Amanda Chen\textsuperscript{1} \& David Hagmann\textsuperscript{1}}
@@
 
-1 January, 2024
+4 January, 2024
 
@@
 
-Gender differences have been documented in various domains and attract plenty of scholarly attention to explain underlying causes.
-Extent research largely focuses on internal factors, such as cognitive styles, preference, personal beliefs, assuming females and males want to do different things.
-Another source of such differences may be the advice that people receive.
-Prior work has documented that men receive more aspirational advice and women more risk-averse advice, which may explain why women are less likely to apply for and ultimately obtain more rewarding positions.
-Research in this line of gender discrimination has emphasized the role of unconscious bias, but interventions that try to reduce this bias have been largely unsuccessful.
-This paper propose a novel source of differences in advice by drawing on recent work on belief-based utility, expectation-based reference points, and the hedonic consequences of information.
-Specifically, we hypothesize that receiving information that is less favorable than one expects imposes a psychological cost on the recipient, because it is disappointing and suggests a less favorable future than one imagined.
-If people anticipate this cost when giving advice, they may be overly favorable or optimistic so as to protect the advisee's belief utility.
-That is, they may not (only) give the advice that they believe will lead to the best decision but are also motivated to avoid disappointing the recipient.
-This requires the formation of beliefs about the advisee's expectations, which is where we propose the differential treatment of men and women arises.
-Prior work has documented that men are more overconfident than women, conditional on equal performance, and that people anticipate this difference.
-An adviser who seeks to avoid disappointment and incorporates expectations into their advice would then present more favorable advice to male advisees than to female advisees.
-While the interpersonal concern has not been fully investigated as a source of gender difference regarding advice giving, its assumption, the hedonic consequences of information have been well documented.
-Research in economics and psychology has found that people avoid information that could make them feel bad, even when doing so leads to worse decisions.
-Recipients of information are even found to blame the people who deliver undesirable message, even though the messenger are not responsible for the situation.
-Advice is predicted to trigger a more intense emotional response because it is assumed to be tailored for its target, and reflects how the giver see the target.
-Individuals tend to desire positive social images and are protective when it comes to others' evaluation of them, and accordingly, prefer advice that implies a positive evaluation.
-However, we are unaware of research documenting whether people take this into account when advising others.
+Seeking and giving advice can be challenging conversations to navigate.
+Advice seekers may be embarrassed to ask for help (Bénabou, Jaroszewicz, \& Loewenstein, 2022), and they may fail to do so if the information they receive could lead to disappointment (Gill \& Prowse, 2012).
+Indeed, people prefer advisers who withhold unpleasant information (Shalvi, Soraperra, Weele, \& Villeval, 2019) and punish those who tell them things they do not want to hear (John, Jeong, Gino, \& Huang, 2019).
+People appear to engage in strategic selection of advice to avoid unpleasant information and protect the utility they get from positive beliefs about themselves and the future they anticipate (Loewenstein, 1987; Loewenstein \& Molnar, 2018).
+But do advice givers anticipate and consider the hedonic cost of honest information to the recipient?
+While previous work has emphasized the instrumental value of advice (e.g., satisfaction with a decision or accuracy of a prediction), we focus on the motivations of the person providing advice.
 
-\hypertarget{a.-our-study}{%
-\section{A. Our study}\label{a.-our-study}}
+Research on advice has largely focused on settings that do not tackle belief utility.
+For example, participants may have been asked to estimate the number of balls in an urn or choose from pairs of lotteries (Benjamin \& Budescu, 2015).
+Advisers have been shown to be motivated to give accurate advice (Jonas \& Frey, 2003), and engage in perspective-taking to meet the preferences of the advisee (L.
+J.
+Kray, 2000; L.
+Kray \& Gonzalez, 1999).
+When they are uncertain, they prefer that advisees do not rely (extensively) on their recommendations (Ache, Rader, \& Hütter, 2020).
+Thus, it seems that people are concerned about providing good advice even when they are not incentivized for the recipient's decision quality.
 
-We test whether gender difference in receiving advice is driven by givers' intention to meet target's expectation and avoid disappoint them.
-We report results from two preregistered experiment in which the interactions without deception between advice givers and recipients are captured.
-In each experiment, we first measure actual level and expectations of advisees, then provide these information to givers and collect advice.
-Lastly, we present advice to their targets, ask advisees to make final decision, and measure the utility of the advice.
-We predict and find that males receive flattering advice than female counterparts when advisers take target's expectations into account.
-If advice for both gender is solely based on actual performance, there exists no gender difference regarding the chance of receiving aggressive advice.
-But when expectation of the target is provided along with actual performance, advisers consider this irrelevant information and give more aggressive advice to males because they have higher expectations for themselves compared with equally competent females.
-We also directly test the reason why advisers provide flattering advice.
-We compare advice given under the treatment condition where interpersonal concerns is the goal with that of baseline condition where, like usually assumed, effectiveness of facilitating decision making is emphasized.
-Advisers are more likely to inflate their advice so that it delivers a positive evaluation of its target when they hold interpersonal concerns and want to be liked by the target.
+In many real settings, however, advice incorporates beliefs about the recipient.
+Someone recommending an expensive restaurant conveys that they think the advisee is wealthy enough to afford an expensive meal, and someone recommending a student pursue a PhD in economics assumes that they are intellectually capable.
+Conversely, telling a poorly performing student to switch to a less-demanding major conveys a belief that the student is not capable of improving.
+Thus, the painful truth may prevent someone from making a bad decision, it may come at a cost to the recipient and damage the relationship between the adviser and advisee.
+We propose that advisers take these costs into account, even when the interactions are entirely anonymous and they are incentivized for the quality of the advisee's decision.
 
-\hypertarget{b.-related-literature}{%
-\section{B. Related Literature}\label{b.-related-literature}}
+Specifically, we focus on the signaling value of advice: what does the advice imply about the adviser's perception of the advisee?
+We propose that advisees have expectations about the advice they receive and treat this as a reference point (Kőszegi \& Rabin, 2006).
+Advice that falls short of these expectations creates disappointment, while advice that exceeds them is flattering and creates positive interpersonal benefits because it creates a perception that the adviser holds the advisee in high esteem.
+Such interpersonal considerations may be as important, if not more important, to the adviser than the instrumental value of the advice: the adviser directly experiences a souring relationship, but may suffer little and only much delayed consequences if an advisee makes a poor life decision.
 
-People frequently obtain information by soliciting the advice of those with more expertise about or insight into an issue.
-A substantial literature has studied how people incorporate advice and whose advice they seek out.
-Briefly, people put less than optimal weight on the advice they receive, and prefer advice from those who are overconfident or who provide favorable information.
-Indeed, people punish advisers who tell them things they do not want to hear.
-Most of the studies in this stream of research have relied on deception and do not involve real people in the role of advisers; studies of advisers themselves remain scarce.
+Our account therefore predicts that people receive advice that is more flattering and suggestive of inflated ability and optimistic outcomes than would advice in the absence of such interpersonal considerations.
+However, we propose that this is not true for all advisees equally.
+Presenting flattering advice requires the formation of beliefs about the advisee's expectations (reference point).
+Exley and Nielsen (2022) show that men are more overconfident than women, conditional on equal performance and that people anticipate but fail to incorporate this difference into their decisions.
+An adviser who seeks to avoid disappointment and incorporates expectations into their advice would then present more favorable advice to male advisees than to female advisees (see Figure 1 for an illustration).
+This provides a novel account for a well-known finding that men receive more aspirational advice than do women (Kanze, Huang, Conley, \& Higgins, 2018).
 
-Notably, prior work on advice has emphasized the instrumental value of information, examining the extent to which the advice improves the quality of or satisfaction with a decision.
-In the proposed project, we will focus on the signaling value of advice: what does the advice imply about the adviser's perception of the advisee?
-We propose that ``flattering'' advice creates a perception that the adviser holds the advisee in high esteem, and that this in turn increases the advisee's liking for the adviser.
-Such interpersonal considerations may be as important (or even more important) in cases where it is difficult to evaluate ex post whether the advice was good or not.
+Notably, when it pays to have accurate beliefs, such flattering advice would come at a cost: while men would be more likely to aim higher, they would also suffer greater costs from aiming too high and failing to meet the objective.
+This may seem at odds with a gender gap favoring men.
+However, observational data often miss people who were unsuccessful.
+For example, job candidates who ask for a high starting salary may be less likely to receive a job offer, but will also have a higher starting salary conditional on receiving an offer.
 
-Prior work has further documented that men and women receive different performance feedback at work.
-Managers are less likely to provide critical feedback to women, believing that doing so would hurt their feelings.
-Thus, interpersonal concerns can undermine constructive feedback, which then harms outcomes because it deprives the advisee of a learning opportunity.
-While this effect at first glance appears counter to our hypotheses (here, men receive more negative feedback), it is driven by different beliefs.
-Managers withhold critical feedback because they (perhaps incorrectly) believe that women suffer a greater cost from criticism.
-Our hypothesized effect is driven by (accurate) beliefs about performance expectations.
-While advice also communicates beliefs about ability, it does not do so through criticism.
+In a large, preregistered experiment (n = 2,000), we show that advisers consider the expectations of advisees, even when such expectations do not provide informative insights for the underlying decision-making problem.
+We find that as a result, showing expectations (but not gender) to advisers leads men to receive more aspirational advice than women.
+Incorporating expectations leads to worse advice, even when advisers are incentivized based on the outcome of the advisee's decision.
+In a second preregistered experiment (n = 700), we show that advisers respond to interpersonal considerations.
+They advice people that they are more attractive than they believe them to be, and inflate to a greater extent when incentivized for likability rather than accuracy.
+Advisees indeed reward such flattering advice, finding the advisers more likeable and no less trustworthy than those who provide more accurate advice.
+
+\hypertarget{open-science-statement}{%
+\section{Open Science Statement}\label{open-science-statement}}
+
+We report all sample sizes, data exclusions, all manipulations, and all measures in the studies.
+Screen captures of the experimental materials are available in the Supplemental Information.
+The complete data, code to reproduce all statistical analyses and figures in the manuscript, as well as the preregistration reports are available via OSF.
+All our studies were preregistered on AsPredicted.org.
+(will do this later)
 
@@
 
-In this study, we conducted an initial test to examine whether individuals take others' self-expectations into account when giving advice.
-Specifically, we predicted that people would adjust their advice to match the advisees' expectations of themselves, even when these expectations are not informative for the underlying decision problem.
-This study was preregistered on AsPredicted (\url{https://aspredicted.org/R44_6SR}).
+We begin by examining whether advisers take the expectations of advisees into account, even when those expectations are not relevant to the quality of advice.
+In a three-stage experiment, we first recruit a sample of advisees and ask them to complete a mathematics quiz.
+After answering all ten multiple-choice questions, participants are anchored to low or high performance expectations and asked to guess how many questions they answered correctly.
+Next, we recruit advice givers and show them either only the true performance of the advisee, or the true performance and how many questions they guessed they answered correctly.
+Advisers are tasked with recommending whether the advisee should compete against a group of high-performers or a group of low-performers on the mathematics quiz.
+Finally, we invite the advisees back and show them the advice they have received.
+Advisees then pick whether to compete against high or low performers, based on their past performance on the quiz.
+Our key hypothesis is that advisees who were anchored to high expectations would be more likely to receive advice to compete against the high performer group.
 
@@
 
-We recruited 1,002 participants (50\% Female, \(M_{\text{Age}}\) = 42.13) from Prolific Academic to take math test and another 1,000 (50\% Female, \(M_{\text{Age}}\) = 38.79)
-This study consisted of three stages involving recipients of advice taking an exam in Stage 1, givers providing advice in Stage 2, and recipients reacting to advice in Stage 3.
-During Stage 1, participants were asked to answer ten math questions in five minutes and were informed that they would receive 10 cents for each question they answered correctly.
-Participants were also asked to predict how many questions they would answer correctly.
-We manipulated their self-expectations by randomly assigning participants to either a High or Low Expectation condition.
-In the High Expectation condition, participants were informed that the average score of five other participants who took the same test was 6.4, while those in the Low Expectation condition were told that the average score was 2.6.
-We incentivized their performance in the math test to increase their attachment to the task.
-The number of correct answers and their predictions represented the recipients' performance and expectations, respectively, and were shown to advice givers.
-After collecting performance and expectations from recipients, we recruited 1,000 participants and informed them of the results of the mathematics quiz completed by the first group of participants.
-Their task was to give advice to the previous participants about whether to compete against a group of ``high'' performers or a group of ``low'' performers (the top 20 and bottom 20 performers out of a separate group of 50 participants who completed the mathematics quiz).
-Advisees could earn a bonus if they performed as well or better than a randomly selected member of their chosen group, and the bonus differed depending on the group they chose (50 cents and 30 cents for the high-performing and low-performing group, respectively).
-Advisers received a bonus identical to the one earned by one of their advisees.
-They provided advice to 10 randomly selected advisees, and we clustered standard errors at the level of Stage 2 participants in subsequent analyses accordingly.
-We randomly assigned advisers to one of two conditions: they either observed only the true performance of the advisee (``Baseline'' treatment), or they observed the true performance and the participant's own estimate of their performance (``Information'' treatment).
-To give givers some sense of this task, we told them the average scores for a previous batch of 50 quiz-takers were 4.42.
-It is important to note that the advisee's own guess provided no information about the likelihood of winning against either the high or low group, as the outcome was based on past performance and not performance on a subsequent test.
-Lastly, we invited the recipients back, reminded them of their previous self-expectations, and informed them that they could earn a bonus if they performed as well or better than a competitor.
-They could decide where that competitor was randomly drawn from, a group of ``high'' performers or a group of ``low'' performers.
-If they scored the same or higher than that competitor, they could earn a bonus, whose value differed depending on the group they chose (50 cents and 30 cents for the high-performing and low-performing group, respectively).
-Recipients were told that an external observer had provided a piece of advice.
-They then read the advice and made their decisions about who they wanted to compete with.
+We first recruited a sample of 50 participants from Prolific to complete a 10-question multiple choice mathematics quiz.
+The questions were taken from a paper-version of the ASVAB standardized exam, such that answers were not available online.
+Participants had 5 minutes to answer the quiz and were paid 10 cents for each correctly answered question.
+We define the top 20 scorers as the ``High Performers'' and the bottom 20 scorers as the ``Low Performers.'' On average, participants answered 4.42 questions correctly, High Performers scored between 5 and 10, and Low Performers scored between 0 and 3.
+We further simulated 1,000 pairings of groups of five participants, with the 5 th percentile of groups scoring an average of 2.60 and the 95 th percentile scoring an average of 6.40.
+We use these participants as the competitors for the advisees in our main experiment, and the average group scores to anchor expectations.
 
-\hypertarget{open-science-statement}{%
-\subsection{Open Science Statement}\label{open-science-statement}}
+Next, we recruited 1,002 participants in Stage 1 of our main experiment, for the role of advisees.
+To arrive at a gender-balanced sample, we dropped the last two male participants to complete the survey, ending up with a sample of 500 men and 500 women (\(M_{\text{Age}}\) = 42.16,50\% Female,).
+Participants completed the same 10-item mathematics quiz as the earlier participants and were informed that their performance would affect their bonus earnings in a follow-up study to be conducted a few days later.
+After completing the quiz, we informed them of the average score of a group of five participants from the preliminary survey.
+We randomly assigned them to learn about the 5 th percentile of groups, which scored 2.60.
+(``Low Expectations'' treatment) or the 95 th percentile of groups, which scored 6.40 (``High Expectations'' treatment).
+Participants then made a guess (unincentivized) about how many questions they think they answered correctly.
+The survey concluded with basic demographic questions.
 
-We report all manipulations, measures, and data exclusion in this and the following study.
-The preregistration reports, screenshots of all experimental materials, and
-the analysis code to replicate all statistical analyses and figures are
-available on the Open Science Framework (will do this later).
+We then recruited 1,000 participants for Stage 2, placing them in the role of advisers.
+We began by informing them of the mathematics quiz that participants in the preliminary study and Stage 1 had completed, and informed them of the average score in the preliminary study.
+Advisers had to recommend whether an advisee should compete against the Low Performers or the High Performers (we used these terms in the survey).
+We anticipated that being told to compete against High Performers is more flattering.
+Advisees would earn 30 cents if their score was equal to or higher than a randomly selected member of the Low Performer group and they chose to compete against this group, or 50 cents if they performed as well or better than a randomly selected member of the High Performer group.
+If they scored lower, they would not receive any bonus.
+
+Advisers were randomly assigned to one of two treatments.
+In the ``Baseline'' treatment, they only observed the score of the advisee on the mathematics quiz.
+In the ``Expectation'' treatment, they observed the score as well as the advisee's guess for how many questions they answered correctly.
+Note that since the outcome is determined only by the past score on the quiz, the advisee's guess is immaterial to which group they should compete against, and in neither treatment did they receive any demographic information about their advisee.
+Participants gave recommendations to 10 advisees, which unbeknownst to them were five men and five women matched to have identical performance on the test.
+They were informed that if their advice was shown to a participant who returned for the follow-up survey, they would receive the identical bonus as that participant.
+The survey also concluded with basic demographic questions.
+Finally, we invited participants from Stage 1 back for the follow-up survey.
+Following our preregistration, we kept the survey open for 7 days.
+In total, 951 participants (481 men, 470 women) returned.
+The brief survey reminded them of the task they completed in Stage 1, informed them that other participants from Prolific had observed their real score and given them advice against which group to compete against, and finally were reminded about how many questions they guessed they had answered correctly.
+Importantly, they were not informed of their true score or the score of the groups they could compete against.
+Participants then observed the advice from a randomly selected adviser and made their decision.
 
@@
 
-We begin by analyzing the performance and expectations of Stage 1 participants, as they will serve as input for Stage 2 participants and influence their advice.
-We compare the performance and expectations of participants in High and Low Expectation conditions, where they are told the average score for a five-participant group is 6.4 or 2.6.
-Although we randomly assigned participants, those in the Low Expectation condition scored slightly higher than those in the High Expectation condition (4.80 and 4.55, respectively, \(t(1000) = -1.67\), \(p = .095\)).
-However, the gap is not significant.
-Participants in the High Expectation condition had worse performance, but they also indicated a significantly higher guess of their score than their counterparts in the other condition (4.80 and 4.42, respectively, \(t(1000) = 3.72\), \(p < .001\)).It makes our experiment a conservative test.
-The gap between their expectations is 0.52, which is not marginal considering the average expectations for all participants is only 4.16.It is worth mentioning that participants from both conditions reported having a hard time answering the math test, and thus, they are underconfident.
-However, participants from the High Expectation condition expected to solve more, indicating a successful manipulation.
-Despite the manipulation, the expectations are significantly correlated with the actual performance (\(b = 0.63\), 95\% CI \([0.58, 0.67]\), \(t(999) = 27.06\), \(p < .001\)).
-Next, we examine gender differences and find that male participants performed slightly better than female participants, and the gap is significant (5.02 and 4.33, respectively, \(t(1000) = -4.77\), \(p < .001\)).
-On average, males are more confident than females, as they predicted to answer more questions correctly (4.75 and 3.56, respectively, \(t(1000) = -8.65\), \(p < .001\)).
-We conducted an OLS regression with the performance and gender of participants and found that with the same score, male participants are more confident than their female counterparts (\(b = 0.78\), 95\% CI \([0.56, 0.99]\), \(t(999) = 7.18\), \(p < .001\)).
+We begin by examining the performance of the Stage 1 participants.
+Because our treatment takes place after participants complete the mathematics quiz, we would not expect a difference in performance across the Low and High Expectations treatments.
+Indeed, the two groups scored no different from one another (4.79 and 4.55 for Low and High Expectations treatments, respectively, \(t(998) = -1.64\), \(p = .102\)).
+The expectations treatment did, however, affect how well they thought they performed.
+Participants in the ``Low Expectations'' treatment guessed a score of 4.79 vs.~4.42 in the High Expectations treatment (\(t(998) = 3.78\), \(p < .001\)), showing that the manipulation was successful.
+Contrary to our expectations, we did find a gender difference in performance: men scored 5.02 on average, while women scored 4.33 (\(t(998) = -4.73\), \(p < .001\)).
+This difference, however, does not affect the interpretation of our findings, which will rely on an interaction of gender with an experimental treatment for Stage 2 participants.
+Consistent with this difference, men thought they answered more questions correctly than did women (4.75 vs 3.56, \(t(998) = -8.60\), \(p < .001\)).
+
+We conducted an OLS regression with the performance and gender of participants and found that with the same performance, male participants are more confident than their female counterparts (\(b = 0.77\), 95\% CI \([0.56, 0.99]\), \(t(997) = 7.15\), \(p < .001\)).
 
@@
 
-\caption{\label{tab:study1regs}Advice of competing against High Performance group, based on the gender of targets and whether their expectation is shown to adviser (Column 1).
-Column 2 show the results where standard errors are clusterd at the level of adviser.
-Expeccted Bonus of advice received, based on the gender of targets and whether their expectation is shown to adviser (Column 3)}
+\caption{\label{tab:study1regs}Column 1 displays the advice given to compete against a High Performance group based on whether the advisees were primed with low or high expectations and the expectation level shown to the advisor.
+Column 2 displays the advice given to compete against a High Performance group based on the gender of the targets and the expectation level shown to the advisor.
+Column 3 displays the expected bonus of the advice received based on the gender of the targets and the expectation level shown to the advisor.
+All results are clustered at the level of the advisor and include standard errors.}
 \centering
@@
 \midrule
-Expectation Shown & \num{-0.034}** & \num{-0.034}* & \num{0.000}\\
- & (\num{0.013}) & (\num{0.013}) & (\num{0.003})\\
-Advisee Male & \num{0.002} & \num{0.002} & \num{0.000}\\
- & (\num{0.013}) & (\num{0.005}) & (\num{0.001})\\
-Expectation x Male & \num{0.032}+ & \num{0.032}*** & \num{-0.005}**\\
- & (\num{0.019}) & (\num{0.009}) & (\num{0.002})\\
-Constant & \num{0.339}*** & \num{0.339}*** & \num{0.258}***\\
- & (\num{0.009}) & (\num{0.010}) & (\num{0.002})\\
+High Expectation & \num{0.012} &  & \\
+ & (\num{0.011}) &  & \\
+Performance & \num{0.128}*** &  & \\
+ & (\num{0.003}) &  & \\
+Expectation Shown &  & \num{-0.034}* & \num{0.000}\\
+ &  & (\num{0.013}) & (\num{0.003})\\
+Advisee Male &  & \num{0.002} & \num{0.000}\\
+ &  & (\num{0.005}) & (\num{0.001})\\
+Expectation x Male &  & \num{0.032}*** & \num{-0.005}**\\
+ &  & (\num{0.009}) & (\num{0.002})\\
+Constant & \num{-0.263}*** & \num{0.339}*** & \num{0.258}***\\
+ & (\num{0.015}) & (\num{0.010}) & (\num{0.002})\\
 \midrule
-N & \num{10000} & \num{10000} & \num{10000}\\
+N & \num{5000} & \num{10000} & \num{10000}\\
 \bottomrule
@@
 
-{\centering \includegraphics{Advice-Giving_files/figure-latex/study1gender-1}
+{\centering \includegraphics{Advice-Giving_files/figure-latex/study1genderdiff-1}
 
@@
 
-\caption{When expectation is shown to the adviser}\label{fig:study1gender}
+\caption{Male participants are more likely to be recommended to compete against the High Performer group than female counterparts, holding performance the same.}\label{fig:study1genderdiff}
 \end{figure}
 
-In Stage 2, we collected 10,000 pieces of advice for 888 Advisees.
-To exclude between-person differences from advice givers, we clustered standard errors at the level of the Stage 2 participants when running OLS regression.
-We conducted an OLS regression with the performance and Advisee Treatment (High or Low Expectation) for the subset of Stage 2 participants in the ``Information'' Treatment.
-Although Advisees in the High Expectation condition are more likely to be recommended to compete against the High Performer Group, the result is not significant (\(b = -0.01\), 95\% CI \([-0.03, 0.01]\), \(t(4997) = -1.13\), \(p = .257\)).
-This may be because the confidence difference (0.60) is too minor for advice givers to take more risk.
-Only 33.11\% of the time, advice givers recommended the High Performer group as the competitor, and the average scores for those who received this advice is 6.64, which is about at the 80th percentile in the performance distribution shown to the advice givers.
-However, if we run an OLS regression with performance and the exact expectations of Advisees, the expectation does increase the chance of receiving aggressive advice (\(b = 0.03\), 95\% CI \([0.02, 0.04]\), \(t(4997) = 10.13\), \(p < .001\)).
-In Stage 2, each participant always sees five females and five males with the same score distribution, and the only difference lies in their expectations.
-Therefore, we predict that there will be no gender difference when advice givers only see performance, but males will receive more aggressive advice when their expectations are presented.
+Next, we examine whether advisers took the advisee's expectations into account.
+Column 1 of Table \ref{tab:study1regs} reports a linear probability model on advising to compete against the High Performer group for advisers in the ``Expectations'' treatment.
+Because each adviser was paired with ten advisees, we cluster standard errors at the adviser level.
+Consistent with our prediction, we find that advisees in the High Expectation condition are more likely to be recommended to compete against the High Performer Group, but the result is not significant.
+
+To test whether expectations can lead to more flattering advice for men than for women, we report a linear probability model with advice to compete against the high group as the outcome measure, and the advisee's gender, whether expectations were shown to the adviser, and the interaction of the two (Column 2 of Table \ref{tab:study1regs}).
+As predicted, we find a significant interaction effect: men are more likely to be advised to compete against the High Performers when expectations are shown than when they are hidden (p \textless{} 0.001; see Figure \ref{fig:study1genderdiff},).
+
+To examine the quality of advice, we computed the expected bonus earnings for all recommendations.
+We made this calculation by assuming that participants adopted the advice and competed against the recommended competitor group.
+We then compared their scores with all 20 possible competitors one by one and calculated the bonus accordingly to determine the expected bonus earnings.
 We conducted an OLS regression with whether givers see the expectation (Baseline or Information condition) and the gender of the Advisee (Female or Male), as well as their interaction.
-In line with our prediction, only when expectations are known to the advice giver, male participants have a higher chance of being recommended to compete against the High Performer group (Column 2 of Table \ref{tab:study1regs} ).
-As seen in Figure \ref{fig:study1gender}, gender differences emerge as a result of showing expectations.
-Because we only have advice for 888 Advisees, to ensure that every participant in Stage 1 receives advice, we recruited 48 more participants to collect more advice for the other 112 participants for Stage 1.
-We did not include any of this advice in the analysis of Stage 2 results.
+Supporting our theory, male participants will receive less bonus given advice they receive (b = -0.005, p \textless{} .01; see also Column 3 of Table \ref{tab:study1regs}
 
-Among 1,002 participants, 94.91\% of them returned for the Stage 3 experiment.
-Of all advice shown to Advisees, 483 of them are from givers in the `Information' treatment condition, and the other 468 are from givers in the `Baseline' treatment condition.
-To examine the impact of flattering advice on performance, we first looked at advice from givers who know the expectations of Advisees.
-We conducted an OLS regression with performance and Treatment condition (High or Low Expectation) of Advisees.
-As predicted, participants in the High Expectation condition received less (\(b = -0.02\), 95\% CI \([-0.05, 0.00]\), \(t(480) = -1.61\), \(p = .107\)), but it is not significant.
-We realize this result is less powerful because the advice presented was randomly selected and advisees who return to this follow-up survey also bring noise.
-To avoid randomness, we computed the Expected Bonus for all 10,000 advice we collected in Stage 2, assuming they are adopted by the Advisees.
-We conducted an OLS regression with whether givers see the expectation (Baseline or Information condition) and the gender of the Advisee (Female or Male), as well as their interaction.
-Supporting our theory, male participants will receive less bonus given advice they receive (Column 3 of Table \ref{tab:study1regs} ).
-It implies that when males receive more aggressive advice (competing against the High Performer group), they end up worse because this kind of advice is not necessarily based on their actual condition.
+Finally, we look at the actual earnings of advisees.
+Although participants in the High Expectation condition earned less, this difference is not significant (\(b = -0.02\), 95\% CI \([-0.04, 0.00]\), \(t(948) = -1.92\), \(p = .055\)).
+
+We found that males are more competitive to the extent that they are more likely to choose to compete against High Performer group (\(b = 0.08\), 95\% CI \([0.03, 0.14]\), \(t(948) = 2.89\), \(p = .004\)), holding performance the same.
+
+\hypertarget{discussion}{%
+\subsection{Discussion}\label{discussion}}
+
+In Study 1, we discovered that although advisers are encouraged to provide accurate advice, they still take into account the expectations of advisees, which are irrelevant to the utility of the advice.
+Due to the fact that males tend to be more confident than their equally competent female counterparts, they are more likely to be recommended to compete against high-performance competitors.
+However, when advice is given to match the advisees' expectations, these flattering recommendations result in lower expected bonus earnings for male participants.
 
@@
 
+\hypertarget{references}{%
+\section{References}\label{references}}
+
+\begingroup
+\singlespacing
+\setlength{\parindent}{-0.2in}
+\setlength{\leftskip}{0.2in}
+\noindent
+
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-Ache2020}{}}%
+Ache, F., Rader, C., \& Hütter, M.
+(2020).
+Advisors want their advice to be used--but not too much: {An} interpersonal perspective on advice taking.
+\emph{Journal of Experimental Social Psychology}, \emph{89}, 103979.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Benabou2022}{}}%
+Bénabou, R., Jaroszewicz, A., \& Loewenstein, G. (2022). \emph{It {Hurts} to {Ask}}. National Bureau of Economic Research.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Benjamin2015}{}}%
+Benjamin, D., \& Budescu, D. V. (2015). Advice from experience: {Communicating} incomplete information incompletely. \emph{Journal of Behavioral Decision Making}, \emph{28}(1), 36--49.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Exley2022}{}}%
+Exley, C., \& Nielsen, K. (2022). The gender gap in confidence: {Expected} but not accounted for. \emph{Available at SSRN 4352381}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Gill2012}{}}%
+Gill, D., \& Prowse, V. (2012). A structural analysis of disappointment aversion in a real effort competition. \emph{American Economic Review}, \emph{102}(1), 469--503.
+
+\leavevmode\vadjust pre{\hypertarget{ref-John2019}{}}%
+John, L.
+K., Jeong, M., Gino, F., \& Huang, L.
+(2019).
+The self-presentational consequences of upholding one's stance in spite of the evidence.
+\emph{Organizational Behavior and Human Decision Processes}, \emph{154}, 1--14.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Jonas2003}{}}%
+Jonas, E., \& Frey, D. (2003). Information search and presentation in advisor--client interactions. \emph{Organizational Behavior and Human Decision Processes}, \emph{91}(2), 154--168.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Kanze2018}{}}%
+Kanze, D., Huang, L., Conley, M.
+A., \& Higgins, E.
+T.
+(2018).
+We ask men to win and women not to lose: {Closing} the gender gap in startup funding.
+\emph{Academy of Management Journal}, \emph{61}(2), 586--614.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Koszegi2006}{}}%
+Kőszegi, B., \& Rabin, M. (2006). A model of reference-dependent preferences. \emph{The Quarterly Journal of Economics}, \emph{121}(4), 1133--1165.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Kray2000}{}}%
+Kray, L. J. (2000). Contingent weighting in self-other decision making. \emph{Organizational Behavior and Human Decision Processes}, \emph{83}(1), 82--106.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Kray1999}{}}%
+Kray, L., \& Gonzalez, R. (1999). Differential weighting in choice versus advice: {I}'ll do this, you do that. \emph{Journal of Behavioral Decision Making}, \emph{12}(3), 207--218.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Loewenstein1987}{}}%
+Loewenstein, G. (1987). Anticipation and the valuation of delayed consumption. \emph{The Economic Journal}, \emph{97}(387), 666--684.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Loewenstein2018}{}}%
+Loewenstein, G., \& Molnar, A. (2018). The renaissance of belief-based utility in economics. \emph{Nature Human Behaviour}, \emph{2}(3), 166--167.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Shalvi2019}{}}%
+Shalvi, S., Soraperra, I., Weele, J. J. van der, \& Villeval, M. C. (2019). \emph{Shooting the messenger? Supply and demand in markets for willful ignorance}.
+
+\end{CSLReferences}
+
+\endgroup
+
 \end{document}

### 2024-01-04 R/clean_study1_time1.R

@@ -33,7 +33,18 @@ count <- apply(answer, 1, function(x) {
 count <- as.data.frame(count)
 Advisee <- cbind(Advisee,count)
 
-saveRDS(Advisee, file = here::here("Data/Study1_time1.Rds"))
+saveRDS(Advisee, file = here::here("Data/Study1_time1All.Rds"))
+Advisee %>% write.csv("Data/Cleaned Data/S1_time1All_clean.csv")
 
-Advisee %>% write.csv("Data/Cleaned Data/S1_time1_clean.csv")
+#create a gander-balance sample
+females <- Advisee %>% dplyr::filter(Gender == "Female")
+males <- Advisee %>% dplyr::filter(Gender == "Male")
+males <- males[1:500,]
+
+Advisee1000 <- rbind(females, males)
+
+saveRDS(Advisee1000, file = here::here("Data/Study1_time1.Rds"))
+Advisee1000 %>% write.csv("Data/Cleaned Data/S1_time1_clean.csv")
+
+
 

### 2024-01-04 Advice Giving.Rmd
Draft 2.0

@@
 Next, we recruited `r scales::comma(dim(study1_time1All)[1])` participants in Stage 1 of our main experiment, for the role of advisees.
-To arrive at a gender-balanced sample, we dropped the last two male participants to complete the survey, ending up with a sample of 500 men and 500 women ($M_{\text{Age}}$ = `r mean(study1_time1$Age)`,50\% Female,).
+To arrive at a gender-balanced sample, we dropped the last two male participants to complete the survey, ending up with a sample of 500 men and 500 women ($M_{\text{Age}}$ = `r mean(study1_time1$Age)`,50\% Female).
 Participants completed the same 10-item mathematics quiz as the earlier participants and were informed that their performance would affect their bonus earnings in a follow-up study to be conducted a few days later.
@@
 
-```{r study1genderdiff, fig.cap ="Male participants are more likely to be recommended to compete against the High Performer group than female counterparts, holding performance the same."} 
+```{r study1genderdiff, fig.cap ="Advice given to men and women.
+Advisers observed real performance and the participants’ estimated performance, but not their gender.
+As a result of their higher expectations, men were advised to compete against the high performance group more often.
+In the treatment in which expectations were not shown to the advisors, no gender differences emerged (not displayed in this figure).."}
 library(dplyr)
@@
                      labels = c("Female_withExpectation", "Male_withExpectation", "NoExpectation")) +
+  scale_y_continuous(name = "P(Compete Against High Performance)") +
+  scale_x_continuous(name = "Performance") +
+  theme_bw() +
+  theme(panel.grid = element_blank(),
+        panel.border = element_blank(),
+        axis.line = element_line(colour = "grey"),
+        legend.position = "bottom",
+        legend.title = element_blank(),
+        legend.key.size = unit(1.2, "lines"),
+        legend.text = element_text(size = 12),
+        plot.title = element_text(hjust = 0.5, size = 20))
+
+```
+
+```{r}
+library(dplyr)
+library(ggplot2)
+library(magrittr)
+
+ProbHG <- study1_advice %>%
+  group_by(Condition, Performance, Gender) %>%
+  dplyr::summarize(avg_hardGroup = mean(Advice))
+
+df_exp <- subset(ProbHG, Condition == "E")
+df_none <- subset(ProbHG, Condition == "None")
+
+ggplot(df_exp, aes(x = Performance, y = avg_hardGroup, color = Gender)) +
+  geom_smooth(method = "glm", method.args = list(family = "binomial"),se = FALSE) +
+  scale_color_manual(values = c("#FFA500", "#4169E1"),
+                     labels = c("Female_withExpectation", "Male_withExpectation")) +
   scale_y_continuous(name = "P(Compete Against High Performance)") +
@@
 # Study 2
-In the previous study, we found that individuals take into account the self-expectations of others when providing advice.
-In this study, we aimed to investigate whether people inflate advice due to the concern for interpersonal benefits.
-We hypothesized that individuals may exaggerate their advice in order to be viewed more favorably by the recipients.
-This study was preregistered on AsPredicted (https://aspredicted.org/45P_93G).
+We then conduct a three-stage experiment to determine why advisers give flattering advice.
+First, we ask a group of advisees to upload selfies and predict their rank in a group of ten people of the same gender based on physical attractiveness.
+Next, we recruit and ask advisers to rank selfies of the opposite gender and recommend which rank the participant ranked 7th should bet on, with the bonus being contingent on whether the participant guessed accurately or found the adviser likable.
+Finally, we show the advisees the advice they have received and ask them to make their final prediction about their rank and evaluate the advice giver in terms of likability, warmth, and trustworthiness.
+Our main hypothesis is that advisers who want to be liked by advisees would recommend a higher rank.
 
@@
 study2_time1 <- readRDS(here::here("Data/Study2_time1.Rds"))
+study2_time1_200 <- readRDS(here::here("Data/Study2_time1_200.Rds"))
 study2_time2 <- readRDS(here::here("Data/Study2_time2.Rds"))
@@
 
-## Method
-We recruited `r scales::comma(dim(study2_time1)[1])` workers from Prolific (`r round(mean(study2_time1$gender == "Female")*100)`\% Female, $M_{\text{Age}}$ = `r mean(study2_time1$age)`) to upload selfies and another `r scales::comma(dim(study2_time2)[1])` (`r round(mean(study2_time2$gender == "Female")*100)`\% Female, $M_{\text{Age}}$ = `r mean(study2_time2$age)`) participants to rate selfies regarding physical attractiveness and give advice.
-Study 2 consists of three surveys.
-At time 1, we invited participants to upload photos of themselves (selfies) to be rated by other participants on attractiveness.
+## Methods
+We recruited 300 participants and invited them to upload photos of themselves (selfies) to be rated by other participants on attractiveness.
+We ended up with a sample of `r scales::comma(dim(study2_time1[study2_time1$gender == 'Male',])[1])` men and `r scales::comma(dim(study2_time1[study2_time1$gender == 'Female',])[1])` women who agreed to do so and uploaded usable pictures.
+We selected the first 100 photos from women to arrive at a gender-balanced sample ($M_{\text{Age}}$ = `r mean(study2_time1_200$age)` years; 50.0\% Female).
+We informed them that their selfies will be randomly grouped into nine others from the same gender and ranked by people of the opposite gender and asked them to predict their rank, with 1st rank represents the most attractive and 10th rank represents the least attractive.
 We assigned each participant to a group of 10 participants of their own gender.
-We also asked participants to predict how they rank in this 10-person group regarding physical attractiveness.
-To create a gender-balanced sample, among all `r dim(study2_time1 %>% dplyr::filter(gender == 'Female'))[1]` female participants who uploaded selfies, we select the first 100 and only include them in the following time 2 and time 3 studies.
-That is, in total we have 200 recipients.
-Next, we recruited `r scales::comma(dim(study2_time2)[1])` new participants and asked them to rank the attractiveness of one such group of 10 participants of the opposite gender.
-After they did so, we showed them the photo of the participant they ranked as the 7th most attractive (that is, the 4th least attractive) and reminded them that they had ranked this person at 7th place.
+
+Next, we recruited `r scales::comma(dim(study2_time2)[1])`new participants and asked them to rank the attractiveness of one such group of 10 participants of the opposite gender ($M_{\text{Age}}$ = `r mean(study2_time2$age)` years; `r round(mean(study2_time2$gender == "Female")*100, 2)`\% Female).
+After they did so, we showed them the photo of the participant they ranked as the 7th  most attractive (that is, the 4th  least attractive) and reminded them that they had ranked this person at 7th attractive.
 We (truthfully) informed them that this participant would have a chance to earn a bonus if they accurately guessed their rank based on the aggregated ratings of all participants who had ranked this group.
-Participants were then randomly assigned to an “accuracy” or a “likability” treatment.
-In the accuracy treatment, they received a bonus identical to that of the advisee.
-In the “likability” treatment, their bonus depended on how the advisee rated them in terms of likability, after observing only the rank that they had advised the advisee to guess.
-At time 3, we invited the participants who uploaded selfies to return for the third stage of the experiment.
-Here, they observed the rank proposed by an adviser and made an incentivized bet on how they ranked across all of those who rated their photo.
-We then asked participants to evaluate the adviser based on their likability and warmth on a 5-point scale.
-The latter dimension was measured with 4-item scale adopted from Fiske, Cuddy, and Glick (2007).
+Participants were then randomly assigned to an “accuracy” or a “likeability” treatment.
+In the accuracy treatment, they were told that they would receive a bonus ($1) identical to that of the advisee.
+While in the “likeability” treatment, the amount their bonus depended on how the advisee rated them in terms of likeability, after observing only the rank that they had advised the advisee to guess.
+Advisees would rate to what extent they think the adviser is likable on a 5-point scale, and each point they earn increases their bonus by 20 cents.
 
-## Open Science Statement
-We report all manipulations, measures, and data exclusion in this and the following study. 
-The preregistration reports, screenshots of all experimental materials, and 
-the analysis code to replicate all statistical analyses and figures are
-available on the Open Science Framework (will do this later).
+Finally, we invited participants from Stage 1 and were ranked as the 7th attractive by at least one adviser (so that they received advice) back for the follow-up survey.
+Following our preregistration, we kept the survey open for 7 days.
+In total, `r scales::comma(dim(study2_time3)[1])`  participants (`r scales::comma(dim(study2_time3[study2_time3$gender == 'Male',])[1])` men, `r scales::comma(dim(study2_time3[study2_time3$gender == 'Female',])[1])` women) returned.
+They were reminded of the selfie they uploaded in Stage 1 and informed that a group of 10 selfies, including theirs, had been rated by other participants from Prolific.
+They were also introduced to the opportunity to earn a $1 bonus if they guessed their rank accurately.
+Participants were then shown the advice from a randomly selected adviser and made their predictions.
+After deciding which rank to bet on, advisees were reminded of the advice they received and asked to rate the advice giver's likability, warmth, friendliness, good-naturedness, trustworthiness, and sincerity on a 5-point scale.
+The last 6 items were adopted from @Fiske2007.
 
@@
 
-First, in line with our prediction, participants advised a lower rank (that is, more attractive) in the likeability treatment than the accuracy treatment, $M_{\text{Likable}}$  =`r round(mean(study2_time2[study2_time2$Condition == "Likable",]$Advice),2)` and $M_{\text{Accurate}}$ = `r round(mean(study2_time2[study2_time2$Condition == "Accurate",]$Advice),2)`, `r papaja::apa_print(t.test(Advice ~ Condition, data = study2_time2, var.equal = T))$statistic`.
-As seen in Figure \@ref(fig:study2advice), notably, even in the accuracy treatment, participants advised a lower rank than they themselves had provided (`r papaja::apa_print(t.test(study2_time2[study2_time2$Condition == "Accurate",]$Advice, mu = 7, var.equal = T))$statistic`).
-This suggests that advisers inferred that advising someone that they were more attractive would make the adviser appear more likable and therefore provided advice that communicated a more favorable impression of the participants’ attractiveness.
+Again, we found supportive evidence that males are more confident about themselves, giving higher initial rank prediction (more attractive) than female participants (`r round(mean(study2_time1[study2_time1$gender == "Male",]$Guess),2)` vs.
+`r round(mean(study2_time1[study2_time1$gender == "Female",]$Guess),2)`, `r papaja::apa_print(t.test(Guess ~ gender, data = study2_time1, var.equal = T))$statistic`).
+
+Examining advice from Stage 2 participants, we found that participants advised a lower rank (that is, more attractive) in the likeability treatment than the accuracy treatment (`r round(mean(study2_time2[study2_time2$Condition == "Likable",]$Advice),2)` vs `r round(mean(study2_time2[study2_time2$Condition == "Accurate",]$Advice),2)`, `r papaja::apa_print(t.test(Advice ~ Condition, data = study2_time2, var.equal = T))$statistic`).
+As seen in Figure \@ref(fig:study2advice), notably, however, even in the accuracy treatment, participants advised a lower rank than they themselves had provided (`r papaja::apa_print(t.test(study2_time2[study2_time2$Condition == "Accurate",]$Advice, mu = 7, var.equal = T))$statistic`).
+This suggests that advisers inferred that advising someone that they were more attractive would make the adviser appear more likeable and therefore provided advice that communicated a more favorable impression of the participants’ attractiveness.
 
@@
 modelsummary::modelsummary(list(`(1)` = lm(likable ~ Advice, data = study2_time3),
-                                `(2)` = lm(warmAvg ~ Advice, data = study2_time3)),
-                           vcov = c("classical", "classical"),
+                                `(2)` = lm(warmAvg ~ Advice, data = study2_time3),
+                                `(3)` = lm(trustAvg ~ Advice, data = study2_time3)),
+                           vcov = c("classical", "classical", "classical"),
                            coef_map = c("Advice" = "Advised Rank",
@@
                            gof_map = list(list('raw' = 'nobs', 'clean' = 'N', 'fmt' = 0)),
-                           caption = "When individuals receive advice that implies a high level of attractiveness (lower rank), they tend to perceive the advice giver as more likable (Column 1) and warm (Column 2).") %>%
+                           caption = "When individuals receive advice that implies a high level of attractiveness (lower rank), they tend to perceive the advice giver as more likable (Column 1), warm (Column 2).
+Column 3 shows that advisors are rated as more trustworthy when they advice lower ranks, but this relationship is only directional.") %>%
   kableExtra::kable_styling(latex_option = "scale_down")
@@
 
-Of the 200 advisees, `r round(dim(study2_time3)[1]/200*100,2)`% returned for a follow-up survey, provided their incentivized guess, and evaluated advisers on likeability and warmth.
-As seen in Figure \@ref(fig:study2rating), in line of our predictions, we found that advisees who suggested that the advisee was more attractive were indeed rated as more likeable (Column 1 of Table \@ref(tab:study2regs) ), and warmer (Column 2 of Table \@ref(tab:study2regs) ).
+To test whether flattering advice brings more positive evaluation of advisers, we create a single index for warmth and trustworthiness by taking average of ratings on warmth, friendliness, good-naturedness, trustworthiness for the former and ratings on trustworthiness, and sincerity for the later.
+As seen in Figure \@ref(fig:study2rating), we found that advisees who suggested that the advisee was more attractive (lower rank) were indeed rated as more likeable and warm (b = -0.109, p < .05; b = -0.133, p < .001; See Columns 1 and 2 of Table 2).
+Interestingly, these benefits are not at the cost of being hypocritical; advisers are also seen as more trustworthy, but the result is only directional (Column 3 of Table 2).
 Notably, however, we were not powered to do a comparison across the two experimental groups.
-
 # References

### 2024-01-04 Advice-Giving.tex
Draft 2.0

@@
 Next, we recruited 1,002 participants in Stage 1 of our main experiment, for the role of advisees.
-To arrive at a gender-balanced sample, we dropped the last two male participants to complete the survey, ending up with a sample of 500 men and 500 women (\(M_{\text{Age}}\) = 42.16,50\% Female,).
+To arrive at a gender-balanced sample, we dropped the last two male participants to complete the survey, ending up with a sample of 500 men and 500 women (\(M_{\text{Age}}\) = 42.16,50\% Female).
 Participants completed the same 10-item mathematics quiz as the earlier participants and were informed that their performance would affect their bonus earnings in a follow-up study to be conducted a few days later.
@@
 
-\caption{Male participants are more likely to be recommended to compete against the High Performer group than female counterparts, holding performance the same.}\label{fig:study1genderdiff}
+\caption{Advice given to men and women.
+Advisers observed real performance and the participants’ estimated performance, but not their gender.
+As a result of their higher expectations, men were advised to compete against the high performance group more often.
+In the treatment in which expectations were not shown to the advisors, no gender differences emerged (not displayed in this figure)..}\label{fig:study1genderdiff}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics{Advice-Giving_files/figure-latex/unnamed-chunk-3-1}
+
+}
+
+\caption{ }\label{fig:unnamed-chunk-3}
 \end{figure}
@@
 
-In the previous study, we found that individuals take into account the self-expectations of others when providing advice.
-In this study, we aimed to investigate whether people inflate advice due to the concern for interpersonal benefits.
-We hypothesized that individuals may exaggerate their advice in order to be viewed more favorably by the recipients.
-This study was preregistered on AsPredicted (\url{https://aspredicted.org/45P_93G}).
+We then conduct a three-stage experiment to determine why advisers give flattering advice.
+First, we ask a group of advisees to upload selfies and predict their rank in a group of ten people of the same gender based on physical attractiveness.
+Next, we recruit and ask advisers to rank selfies of the opposite gender and recommend which rank the participant ranked 7th should bet on, with the bonus being contingent on whether the participant guessed accurately or found the adviser likable.
+Finally, we show the advisees the advice they have received and ask them to make their final prediction about their rank and evaluate the advice giver in terms of likability, warmth, and trustworthiness.
+Our main hypothesis is that advisers who want to be liked by advisees would recommend a higher rank.
 
-\hypertarget{method}{%
-\subsection{Method}\label{method}}
+\hypertarget{methods-1}{%
+\subsection{Methods}\label{methods-1}}
 
-We recruited 207 workers from Prolific (52\% Female, \(M_{\text{Age}}\) = 39.50) to upload selfies and another 472 (50\% Female, \(M_{\text{Age}}\) = 41.03) participants to rate selfies regarding physical attractiveness and give advice.
-Study 2 consists of three surveys.
-At time 1, we invited participants to upload photos of themselves (selfies) to be rated by other participants on attractiveness.
+We recruited 300 participants and invited them to upload photos of themselves (selfies) to be rated by other participants on attractiveness.
+We ended up with a sample of 100 men and 107 women who agreed to do so and uploaded usable pictures.
+We selected the first 100 photos from women to arrive at a gender-balanced sample (\(M_{\text{Age}}\) = 39.37 years; 50.0\% Female).
+We informed them that their selfies will be randomly grouped into nine others from the same gender and ranked by people of the opposite gender and asked them to predict their rank, with 1st rank represents the most attractive and 10th rank represents the least attractive.
 We assigned each participant to a group of 10 participants of their own gender.
-We also asked participants to predict how they rank in this 10-person group regarding physical attractiveness.
-To create a gender-balanced sample, among all 107 female participants who uploaded selfies, we select the first 100 and only include them in the following time 2 and time 3 studies.
-That is, in total we have 200 recipients.
-Next, we recruited 472 new participants and asked them to rank the attractiveness of one such group of 10 participants of the opposite gender.
-After they did so, we showed them the photo of the participant they ranked as the 7th most attractive (that is, the 4th least attractive) and reminded them that they had ranked this person at 7th place.
+
+Next, we recruited 472new participants and asked them to rank the attractiveness of one such group of 10 participants of the opposite gender (\(M_{\text{Age}}\) = 41.03 years; 49.79\% Female).
+After they did so, we showed them the photo of the participant they ranked as the 7th most attractive (that is, the 4th least attractive) and reminded them that they had ranked this person at 7th attractive.
 We (truthfully) informed them that this participant would have a chance to earn a bonus if they accurately guessed their rank based on the aggregated ratings of all participants who had ranked this group.
-Participants were then randomly assigned to an ``accuracy'' or a ``likability'' treatment.
-In the accuracy treatment, they received a bonus identical to that of the advisee.
-In the ``likability'' treatment, their bonus depended on how the advisee rated them in terms of likability, after observing only the rank that they had advised the advisee to guess.
-At time 3, we invited the participants who uploaded selfies to return for the third stage of the experiment.
-Here, they observed the rank proposed by an adviser and made an incentivized bet on how they ranked across all of those who rated their photo.
-We then asked participants to evaluate the adviser based on their likability and warmth on a 5-point scale.
-The latter dimension was measured with 4-item scale adopted from Fiske, Cuddy, and Glick (2007).
+Participants were then randomly assigned to an ``accuracy'' or a ``likeability'' treatment.
+In the accuracy treatment, they were told that they would receive a bonus (\$1) identical to that of the advisee.
+While in the ``likeability'' treatment, the amount their bonus depended on how the advisee rated them in terms of likeability, after observing only the rank that they had advised the advisee to guess.
+Advisees would rate to what extent they think the adviser is likable on a 5-point scale, and each point they earn increases their bonus by 20 cents.
 
-\hypertarget{open-science-statement-1}{%
-\subsection{Open Science Statement}\label{open-science-statement-1}}
-
-We report all manipulations, measures, and data exclusion in this and the following study.
-The preregistration reports, screenshots of all experimental materials, and
-the analysis code to replicate all statistical analyses and figures are
-available on the Open Science Framework (will do this later).
+Finally, we invited participants from Stage 1 and were ranked as the 7th attractive by at least one adviser (so that they received advice) back for the follow-up survey.
+Following our preregistration, we kept the survey open for 7 days.
+In total, 146 participants (77 men, 69 women) returned.
+They were reminded of the selfie they uploaded in Stage 1 and informed that a group of 10 selfies, including theirs, had been rated by other participants from Prolific.
+They were also introduced to the opportunity to earn a \$1 bonus if they guessed their rank accurately.
+Participants were then shown the advice from a randomly selected adviser and made their predictions.
+After deciding which rank to bet on, advisees were reminded of the advice they received and asked to rate the advice giver's likability, warmth, friendliness, good-naturedness, trustworthiness, and sincerity on a 5-point scale.
+The last 6 items were adopted from Fiske, Cuddy, and Glick (2007).
 
@@
 
-First, in line with our prediction, participants advised a lower rank (that is, more attractive) in the likeability treatment than the accuracy treatment, \(M_{\text{Likable}}\) =5.38 and \(M_{\text{Accurate}}\) = 6.19, \(t(470) = 5.44\), \(p < .001\).
-As seen in Figure \ref{fig:study2advice}, notably, even in the accuracy treatment, participants advised a lower rank than they themselves had provided (\(t(234) = -8.82\), \(p < .001\)).
-This suggests that advisers inferred that advising someone that they were more attractive would make the adviser appear more likable and therefore provided advice that communicated a more favorable impression of the participants' attractiveness.
+Again, we found supportive evidence that males are more confident about themselves, giving higher initial rank prediction (more attractive) than female participants (5.76 vs.~6.37, \(t(205) = 2.15\), \(p = .033\)).
+
+Examining advice from Stage 2 participants, we found that participants advised a lower rank (that is, more attractive) in the likeability treatment than the accuracy treatment (5.38 vs 6.19, \(t(470) = 5.44\), \(p < .001\)).
+As seen in Figure \ref{fig:study2advice}, notably, however, even in the accuracy treatment, participants advised a lower rank than they themselves had provided (\(t(234) = -8.82\), \(p < .001\)).
+This suggests that advisers inferred that advising someone that they were more attractive would make the adviser appear more likeable and therefore provided advice that communicated a more favorable impression of the participants' attractiveness.
 
@@
 
-\caption{\label{tab:study2regs}When individuals receive advice that implies a high level of attractiveness (lower rank), they tend to perceive the advice giver as more likable (Column 1) and warm (Column 2).}
+\caption{\label{tab:study2regs}When individuals receive advice that implies a high level of attractiveness (lower rank), they tend to perceive the advice giver as more likable (Column 1), warm (Column 2).
+Column 3 shows that advisors are rated as more trustworthy when they advice lower ranks, but this relationship is only directional.}
 \centering
 \resizebox{\linewidth}{!}{
-\begin{tabular}[t]{lcc}
+\begin{tabular}[t]{lccc}
 \toprule
-  & (1) & (2)\\
+  & (1) & (2) & (3)\\
 \midrule
-Advised Rank & \num{-0.109}* & \num{-0.133}**\\
- & (\num{0.046}) & (\num{0.044})\\
-Constant & \num{3.777}*** & \num{3.903}***\\
- & (\num{0.279}) & (\num{0.266})\\
+Advised Rank & \num{-0.109}* & \num{-0.133}** & \num{-0.054}\\
+ & (\num{0.046}) & (\num{0.044}) & (\num{0.042})\\
+Constant & \num{3.777}*** & \num{3.903}*** & \num{3.397}***\\
+ & (\num{0.279}) & (\num{0.266}) & (\num{0.257})\\
 \midrule
-N & \num{146} & \num{146}\\
+N & \num{146} & \num{146} & \num{146}\\
 \bottomrule
-\multicolumn{3}{l}{\rule{0pt}{1em}+ p $<$ 0.1, * p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
+\multicolumn{4}{l}{\rule{0pt}{1em}+ p $<$ 0.1, * p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
 \end{tabular}}
@@
 
-Of the 200 advisees, 73\% returned for a follow-up survey, provided their incentivized guess, and evaluated advisers on likeability and warmth.
-As seen in Figure \ref{fig:study2rating}, in line of our predictions, we found that advisees who suggested that the advisee was more attractive were indeed rated as more likeable (Column 1 of Table \ref{tab:study2regs} ), and warmer (Column 2 of Table \ref{tab:study2regs} ).
+To test whether flattering advice brings more positive evaluation of advisers, we create a single index for warmth and trustworthiness by taking average of ratings on warmth, friendliness, good-naturedness, trustworthiness for the former and ratings on trustworthiness, and sincerity for the later.
+As seen in Figure \ref{fig:study2rating}, we found that advisees who suggested that the advisee was more attractive (lower rank) were indeed rated as more likeable and warm (b = -0.109, p \textless{} .05; b = -0.133, p \textless{} .001; See Columns 1 and 2 of Table 2).
+Interestingly, these benefits are not at the cost of being hypocritical; advisers are also seen as more trustworthy, but the result is only directional (Column 3 of Table 2).
 Notably, however, we were not powered to do a comparison across the two experimental groups.
@@
 Exley, C., \& Nielsen, K. (2022). The gender gap in confidence: {Expected} but not accounted for. \emph{Available at SSRN 4352381}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Fiske2007}{}}%
+Fiske, S. T., Cuddy, A. J., \& Glick, P. (2007). Universal dimensions of social cognition: Warmth and competence. \emph{Trends in Cognitive Sciences}, \emph{11}(2), 77--83.
 

### 2024-01-04 R/clean_study2_time1.R

@@ -13,3 +13,11 @@ targets <- data.table::fread(here::here("Data/Raw Data/S2_time1.csv"),
 
 saveRDS(targets, file = here::here("Data/Study2_time1.Rds"))
 targets %>% write.csv("Data/Cleaned Data/S2_time1_clean.csv")
+
+females <- targets %>% dplyr::filter(gender == 'Female')
+males <- targets %>% dplyr::filter(gender == 'Male')
+females <- females[1:100,]
+targets200 <- rbind(females, males)
+
+saveRDS(targets200, file = here::here("Data/Study2_time1_200.Rds"))
+targets200 %>% write.csv("Data/Cleaned Data/S2_time1_200_clean.csv")

### 2024-01-08 Advice Giving.Rmd
Manuscript for ICAM

@@
 abstract: |
+  The purpose of advice is to help recipients make better decisions and solve their problems.
+However, in this paper, we propose that advisors may also take recipients' responses into account and attempt to avoid disappointing them, leading to what we call "flattering advice." In two pre-registered experiments involving real interactions between advisors and advisees (n = 2,700), we show that individuals consider others' expectations when giving advice, even when such expectations do not provide informative insights for the underlying decision-making problem.
+As a result, men receive more aspirational advice than women, given their higher confidence, when expectations (but not gender) are shown to advisors.
+However, incorporating expectations leads to worse outcomes (Study 1).
+Individuals inflate their advice due to interpersonal considerations: people who are concerned about advisees' likability inflate their advice to a great extent.
+Advisees reward such flattering advice, finding the advisers more likable and no less trustworthy than those who provide more accurate advice (Study 2).
+We discuss practical and theoretical contributions and future research directions.
 
-  This is an interesting project! Please read through it!
 keywords          : "Gender difference, Advice, Interpresonal relationship"
@@
 Notably, however, we were not powered to do a comparison across the two experimental groups.
+
+# Discussion
+dvice substantially shapes people's career and personal outcomes.
+Therefore, understanding advisers' motivations has far-reaching implications.
+We propose that advisers' focus on advisees' expectations and the desire to avoid disappointing them can induce gender differences in the advice given and ultimately in the outcomes achieved.
+Gender differences in career outcomes contribute significantly to the gender wage gap, with women often holding less senior positions and experiencing worse career outcomes, even with equal performance.
+Therefore, identifying a factor such as expectations that contributes to this gap has important implications for organizational practice.
+
+In this paper, we examine a novel and unexplored factor of advice-giving: interpersonal considerations.
+Advisers who take into account the advisee's belief utility inflate their advice to convey a more favorable impression, leading to worse decisions and gender differences.
+Men have more inflated expectations than women, and taking expectations into account can lead to gender differences, even without discrimination.
+We ruled out discrimination as a separate channel by withholding information about the gender of the advisee.
+Finally, we expect that advisers are aware of the tradeoff between giving accurate advice and avoiding disappointment and, thus, are less likely to inflate their advice when advisees can compensate them after observing the outcome of their choice.
+
+The findings of this study suggest that organizations can promote gender equity by calibrating employees' expectations or shifting advisers' attention away from them.
+While these measures may not entirely solve the gender gap problem, they can make a meaningful difference when unconscious bias interventions have failed to show any effect [@Chang2019; @Paluck2009].
+We believe our findings may be particularly relevant to societies that value signaling in interpersonal relationships, including Hong Kong and many Asian countries.
+Future work could also examine whether people in different cultures place more weight on expectations.
+
 # References

### 2024-01-08 Advice-Giving.tex
Manuscript for ICAM

@@
 
-4 January, 2024
+8 January, 2024
 
@@
 
+\hypertarget{discussion-1}{%
+\section{Discussion}\label{discussion-1}}
+
+dvice substantially shapes people's career and personal outcomes.
+Therefore, understanding advisers' motivations has far-reaching implications.
+We propose that advisers' focus on advisees' expectations and the desire to avoid disappointing them can induce gender differences in the advice given and ultimately in the outcomes achieved.
+Gender differences in career outcomes contribute significantly to the gender wage gap, with women often holding less senior positions and experiencing worse career outcomes, even with equal performance.
+Therefore, identifying a factor such as expectations that contributes to this gap has important implications for organizational practice.
+
+In this paper, we examine a novel and unexplored factor of advice-giving: interpersonal considerations.
+Advisers who take into account the advisee's belief utility inflate their advice to convey a more favorable impression, leading to worse decisions and gender differences.
+Men have more inflated expectations than women, and taking expectations into account can lead to gender differences, even without discrimination.
+We ruled out discrimination as a separate channel by withholding information about the gender of the advisee.
+Finally, we expect that advisers are aware of the tradeoff between giving accurate advice and avoiding disappointment and, thus, are less likely to inflate their advice when advisees can compensate them after observing the outcome of their choice.
+
+The findings of this study suggest that organizations can promote gender equity by calibrating employees' expectations or shifting advisers' attention away from them.
+While these measures may not entirely solve the gender gap problem, they can make a meaningful difference when unconscious bias interventions have failed to show any effect (Chang et al., 2019; Paluck \& Green, 2009).
+We believe our findings may be particularly relevant to societies that value signaling in interpersonal relationships, including Hong Kong and many Asian countries.
+Future work could also examine whether people in different cultures place more weight on expectations.
+
 \hypertarget{references}{%
@@
 Benjamin, D., \& Budescu, D. V. (2015). Advice from experience: {Communicating} incomplete information incompletely. \emph{Journal of Behavioral Decision Making}, \emph{28}(1), 36--49.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Chang2019}{}}%
+Chang, E.
+H., Milkman, K.
+L., Gromet, D.
+M., Rebele, R.
+W., Massey, C., Duckworth, A.
+L., \& Grant, A.
+M.
+(2019).
+The mixed effects of online diversity training.
+\emph{Proceedings of the National Academy of Sciences}, \emph{116}(16), 7778--7783.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Paluck2009}{}}%
+Paluck, E. L., \& Green, D. P. (2009). Prejudice reduction: What works? A review and assessment of research and practice. \emph{Annual Review of Psychology}, \emph{60}, 339--367.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Shalvi2019}{}}%

### 2024-01-14 Advice Giving.Rmd
Added linebreaks for easier change tracking

@@
 # Introduction
+
 Seeking and giving advice can be challenging conversations to navigate.
-Advice seekers may be embarrassed to ask for help [@Benabou2022], and they may fail to do so if the information they receive could lead to disappointment [@Gill2012].
-Indeed, people prefer advisers who withhold unpleasant information [@Shalvi2019] and punish those who tell them things they do not want to hear [@John2019].
-People appear to engage in strategic selection of advice to avoid unpleasant information and protect the utility they get from positive beliefs about themselves and the future they anticipate [@Loewenstein2018; @Loewenstein1987].
-But do advice givers anticipate and consider the hedonic cost of honest information to the recipient?
-While previous work has emphasized the instrumental value of advice (e.g., satisfaction with a decision or accuracy of a prediction), we focus on the motivations of the person providing advice.
+Advice seekers may be embarrassed to ask for help [@Benabou2022], and
+they may fail to do so if the information they receive could lead to
+disappointment [@Gill2012]. Indeed, people prefer advisers who withhold
+unpleasant information [@Shalvi2019] and punish those who tell them
+things they do not want to hear [@John2019]. People appear to engage in
+strategic selection of advice to avoid unpleasant information and
+protect the utility they get from positive beliefs about themselves and
+the future they anticipate [@Loewenstein2018; @Loewenstein1987]. But do
+advice givers anticipate and consider the hedonic cost of honest
+information to the recipient? While previous work has emphasized the
+instrumental value of advice (e.g., satisfaction with a decision or
+accuracy of a prediction), we focus on the motivations of the person
+providing advice.
 
-Research on advice has largely focused on settings that do not tackle belief utility.
-For example, participants may have been asked to estimate the number of balls in an urn or choose from pairs of lotteries [@Benjamin2015].
-Advisers have been shown to be motivated to give accurate advice [@Jonas2003], and engage in perspective-taking to meet the preferences of the advisee [@Kray2000; @Kray1999].
-When they are uncertain, they prefer that advisees do not rely (extensively) on their recommendations [@Ache2020].
-Thus, it seems that people are concerned about providing good advice even when they are not incentivized for the recipient’s decision quality.
+Research on advice has largely focused on settings that do not tackle
+belief utility. For example, participants may have been asked to
+estimate the number of balls in an urn or choose from pairs of lotteries
+[@Benjamin2015]. Advisers have been shown to be motivated to give
+accurate advice [@Jonas2003], and engage in perspective-taking to meet
+the preferences of the advisee [@Kray2000; @Kray1999]. When they are
+uncertain, they prefer that advisees do not rely (extensively) on their
+recommendations [@Ache2020]. Thus, it seems that people are concerned
+about providing good advice even when they are not incentivized for the
+recipient’s decision quality.
 
-In many real settings, however, advice incorporates beliefs about the recipient.
-Someone recommending an expensive restaurant conveys that they think the advisee is wealthy enough to afford an expensive meal, and someone recommending a student pursue a PhD in economics assumes that they are intellectually capable.
-Conversely, telling a poorly performing student to switch to a less-demanding major conveys a belief that the student is not capable of improving.
-Thus, the painful truth may prevent someone from making a bad decision, it may come at a cost to the recipient and damage the relationship between the adviser and advisee.
-We propose that advisers take these costs into account, even when the interactions are entirely anonymous and they are incentivized for the quality of the advisee’s decision.
+In many real settings, however, advice incorporates beliefs about the
+recipient. Someone recommending an expensive restaurant conveys that
+they think the advisee is wealthy enough to afford an expensive meal,
+and someone recommending a student pursue a PhD in economics assumes
+that they are intellectually capable. Conversely, telling a poorly
+performing student to switch to a less-demanding major conveys a belief
+that the student is not capable of improving. Thus, the painful truth
+may prevent someone from making a bad decision, it may come at a cost to
+the recipient and damage the relationship between the adviser and
+advisee. We propose that advisers take these costs into account, even
+when the interactions are entirely anonymous and they are incentivized
+for the quality of the advisee’s decision.
 
-Specifically, we focus on the signaling value of advice: what does the advice imply about the adviser's perception of the advisee?
-We propose that advisees have expectations about the advice they receive and treat this as a reference point [@Koszegi2006].
-Advice that falls short of these expectations creates disappointment, while advice that exceeds them is flattering and creates positive interpersonal benefits because it creates a perception that the adviser holds the advisee in high esteem.
-Such interpersonal considerations may be as important, if not more important, to the adviser than the instrumental value of the advice: the adviser directly experiences a souring relationship, but may suffer little and only much delayed consequences if an advisee makes a poor life decision.
+Specifically, we focus on the signaling value of advice: what does the
+advice imply about the adviser's perception of the advisee? We propose
+that advisees have expectations about the advice they receive and treat
+this as a reference point [@Koszegi2006]. Advice that falls short of
+these expectations creates disappointment, while advice that exceeds
+them is flattering and creates positive interpersonal benefits because
+it creates a perception that the adviser holds the advisee in high
+esteem. Such interpersonal considerations may be as important, if not
+more important, to the adviser than the instrumental value of the
+advice: the adviser directly experiences a souring relationship, but may
+suffer little and only much delayed consequences if an advisee makes a
+poor life decision.
 
-Our account therefore predicts that people receive advice that is more flattering and suggestive of inflated ability and optimistic outcomes than would advice in the absence of such interpersonal considerations.
+Our account therefore predicts that people receive advice that is more
+flattering and suggestive of inflated ability and optimistic outcomes
+than would advice in the absence of such interpersonal considerations.
 However, we propose that this is not true for all advisees equally.
-Presenting flattering advice requires the formation of beliefs about the advisee's expectations (reference point).
-@Exley2022 show that men are more overconfident than women, conditional on equal performance and that people anticipate but fail to incorporate this difference into their decisions.
-An adviser who seeks to avoid disappointment and incorporates expectations into their advice would then present more favorable advice to male advisees than to female advisees (see Figure 1 for an illustration).
-This provides a novel account for a well-known finding that men receive more aspirational advice than do women [@Kanze2018].
+Presenting flattering advice requires the formation of beliefs about the
+advisee's expectations (reference point). @Exley2022 show that men are
+more overconfident than women, conditional on equal performance and that
+people anticipate but fail to incorporate this difference into their
+decisions. An adviser who seeks to avoid disappointment and incorporates
+expectations into their advice would then present more favorable advice
+to male advisees than to female advisees (see Figure 1 for an
+illustration). This provides a novel account for a well-known finding
+that men receive more aspirational advice than do women [@Kanze2018].
 
-Notably, when it pays to have accurate beliefs, such flattering advice would come at a cost: while men would be more likely to aim higher, they would also suffer greater costs from aiming too high and failing to meet the objective.
-This may seem at odds with a gender gap favoring men.
-However, observational data often miss people who were unsuccessful.
-For example, job candidates who ask for a high starting salary may be less likely to receive a job offer, but will also have a higher starting salary conditional on receiving an offer.
+Notably, when it pays to have accurate beliefs, such flattering advice
+would come at a cost: while men would be more likely to aim higher, they
+would also suffer greater costs from aiming too high and failing to meet
+the objective. This may seem at odds with a gender gap favoring men.
+However, observational data often miss people who were unsuccessful. For
+example, job candidates who ask for a high starting salary may be less
+likely to receive a job offer, but will also have a higher starting
+salary conditional on receiving an offer.
 
-In a large, preregistered experiment (n = 2,000), we show that advisers consider the expectations of advisees, even when such expectations do not provide informative insights for the underlying decision-making problem.
-We find that as a result, showing expectations (but not gender) to advisers leads men to receive more aspirational advice than women.
-Incorporating expectations leads to worse advice, even when advisers are incentivized based on the outcome of the advisee’s decision.
-In a second preregistered experiment (n = 700), we show that advisers respond to interpersonal considerations.
-They advice people that they are more attractive than they believe them to be, and inflate to a greater extent when incentivized for likability rather than accuracy.
-Advisees indeed reward such flattering advice, finding the advisers more likeable and no less trustworthy than those who provide more accurate advice.
+In a large, preregistered experiment (n = 2,000), we show that advisers
+consider the expectations of advisees, even when such expectations do
+not provide informative insights for the underlying decision-making
+problem. We find that as a result, showing expectations (but not gender)
+to advisers leads men to receive more aspirational advice than women.
+Incorporating expectations leads to worse advice, even when advisers are
+incentivized based on the outcome of the advisee’s decision. In a second
+preregistered experiment (n = 700), we show that advisers respond to
+interpersonal considerations. They advice people that they are more
+attractive than they believe them to be, and inflate to a greater extent
+when incentivized for likability rather than accuracy. Advisees indeed
+reward such flattering advice, finding the advisers more likeable and no
+less trustworthy than those who provide more accurate advice.
 
 # Open Science Statement
-We report all sample sizes, data exclusions, all manipulations, and all measures in the studies.
-Screen captures of the experimental materials are available in the Supplemental Information.
-The complete data, code to reproduce all statistical analyses and figures in the manuscript, as well as the preregistration reports are available via OSF.
-All our studies were preregistered on AsPredicted.org.
-(will do this later)
+
+We report all sample sizes, data exclusions, all manipulations, and all
+measures in the studies. Screen captures of the experimental materials
+are available in the Supplemental Information. The complete data, code
+to reproduce all statistical analyses and figures in the manuscript, as
+well as the preregistration reports are available via OSF. All our
+studies were preregistered on AsPredicted.org. (will do this later)
 
 # Study 1
-We begin by examining whether advisers take the expectations of advisees into account, even when those expectations are not relevant to the quality of advice.
-In a three-stage experiment, we first recruit a sample of advisees and ask them to complete a mathematics quiz.
-After answering all ten multiple-choice questions, participants are anchored to low or high performance expectations and asked to guess how many questions they answered correctly.
-Next, we recruit advice givers and show them either only the true performance of the advisee, or the true performance and how many questions they guessed they answered correctly.
-Advisers are tasked with recommending whether the advisee should compete against a group of high-performers or a group of low-performers on the mathematics quiz.
-Finally, we invite the advisees back and show them the advice they have received.
-Advisees then pick whether to compete against high or low performers, based on their past performance on the quiz.
-Our key hypothesis is that advisees who were anchored to high expectations would be more likely to receive advice to compete against the high performer group.
+
+We begin by examining whether advisers take the expectations of advisees
+into account, even when those expectations are not relevant to the
+quality of advice. In a three-stage experiment, we first recruit a
+sample of advisees and ask them to complete a mathematics quiz. After
+answering all ten multiple-choice questions, participants are anchored
+to low or high performance expectations and asked to guess how many
+questions they answered correctly. Next, we recruit advice givers and
+show them either only the true performance of the advisee, or the true
+performance and how many questions they guessed they answered correctly.
+Advisers are tasked with recommending whether the advisee should compete
+against a group of high-performers or a group of low-performers on the
+mathematics quiz. Finally, we invite the advisees back and show them the
+advice they have received. Advisees then pick whether to compete against
+high or low performers, based on their past performance on the quiz. Our
+key hypothesis is that advisees who were anchored to high expectations
+would be more likely to receive advice to compete against the high
+performer group.
 
 ## Methods
+
 ```{r}
@@
 
-We first recruited a sample of `r scales::comma(dim(study1_math50)[1])` participants from Prolific to complete a 10-question multiple choice mathematics quiz.
-The questions were taken from a paper-version of the ASVAB standardized exam, such that answers were not available online.
-Participants had 5 minutes to answer the quiz and were paid 10 cents for each correctly answered question.
-We define the top 20 scorers as the “High Performers” and the bottom 20 scorers as the “Low Performers.” On average, participants answered `r round(mean(study1_math50$Score),2)` questions correctly, High Performers scored between `r HP_lower` and `r HP_upper`, and Low Performers scored between `r LP_lower` and `r LP_upper`.
-We further simulated 1,000 pairings of groups of five participants, with the 5 th percentile of groups scoring an average of `r p5` and the 95 th percentile scoring an average of `r p95`.
-We use these participants as the competitors for the advisees in our main experiment, and the average group scores to anchor expectations.
+We first recruited a sample of `r scales::comma(dim(study1_math50)[1])`
+participants from Prolific to complete a 10-question multiple choice
+mathematics quiz. The questions were taken from a paper-version of the
+ASVAB standardized exam, such that answers were not available online.
+Participants had 5 minutes to answer the quiz and were paid 10 cents for
+each correctly answered question. We define the top 20 scorers as the
+“High Performers” and the bottom 20 scorers as the “Low Performers.” On
+average, participants answered `r round(mean(study1_math50$Score),2)`
+questions correctly, High Performers scored between `r HP_lower` and
+`r HP_upper`, and Low Performers scored between `r LP_lower` and
+`r LP_upper`. We further simulated 1,000 pairings of groups of five
+participants, with the 5 th percentile of groups scoring an average of
+`r p5` and the 95 th percentile scoring an average of `r p95`. We use
+these participants as the competitors for the advisees in our main
+experiment, and the average group scores to anchor expectations.
 
-Next, we recruited `r scales::comma(dim(study1_time1All)[1])` participants in Stage 1 of our main experiment, for the role of advisees.
-To arrive at a gender-balanced sample, we dropped the last two male participants to complete the survey, ending up with a sample of 500 men and 500 women ($M_{\text{Age}}$ = `r mean(study1_time1$Age)`,50\% Female).
-Participants completed the same 10-item mathematics quiz as the earlier participants and were informed that their performance would affect their bonus earnings in a follow-up study to be conducted a few days later.
-After completing the quiz, we informed them of the average score of a group of five participants from the preliminary survey.
-We randomly assigned them to learn about the 5 th percentile of groups, which scored `r p5`.
-(“Low Expectations” treatment) or the 95 th percentile of groups, which scored `r p95` (“High Expectations” treatment).
-Participants then made a guess (unincentivized) about how many questions they think they answered correctly.
-The survey concluded with basic demographic questions.
+Next, we recruited `r scales::comma(dim(study1_time1All)[1])`
+participants in Stage 1 of our main experiment, for the role of
+advisees. To arrive at a gender-balanced sample, we dropped the last two
+male participants to complete the survey, ending up with a sample of 500
+men and 500 women ($M_{\text{Age}}$ = `r mean(study1_time1$Age)`,50%
+Female). Participants completed the same 10-item mathematics quiz as the
+earlier participants and were informed that their performance would
+affect their bonus earnings in a follow-up study to be conducted a few
+days later. After completing the quiz, we informed them of the average
+score of a group of five participants from the preliminary survey. We
+randomly assigned them to learn about the 5 th percentile of groups,
+which scored `r p5`. (“Low Expectations” treatment) or the 95 th
+percentile of groups, which scored `r p95` (“High Expectations”
+treatment). Participants then made a guess (unincentivized) about how
+many questions they think they answered correctly. The survey concluded
+with basic demographic questions.
 
-We then recruited `r scales::comma(dim(study1_time2_giver)[1])`  participants for Stage 2, placing them in the role of advisers.
-We began by informing them of the mathematics quiz that participants in the preliminary study and Stage 1 had completed, and informed them of the average score in the preliminary study.
-Advisers had to recommend whether an advisee should compete against the Low Performers or the High Performers (we used these terms in the survey).
-We anticipated that being told to compete against High Performers is more flattering.
-Advisees would earn 30 cents if their score was equal to or higher than a randomly selected member of the Low Performer group and they chose to compete against this group, or 50 cents if they performed as well or better than a randomly selected member of the High Performer group.
-If they scored lower, they would not receive any bonus.
+We then recruited `r scales::comma(dim(study1_time2_giver)[1])`
+participants for Stage 2, placing them in the role of advisers. We began
+by informing them of the mathematics quiz that participants in the
+preliminary study and Stage 1 had completed, and informed them of the
+average score in the preliminary study. Advisers had to recommend
+whether an advisee should compete against the Low Performers or the High
+Performers (we used these terms in the survey). We anticipated that
+being told to compete against High Performers is more flattering.
+Advisees would earn 30 cents if their score was equal to or higher than
+a randomly selected member of the Low Performer group and they chose to
+compete against this group, or 50 cents if they performed as well or
+better than a randomly selected member of the High Performer group. If
+they scored lower, they would not receive any bonus.
 
-Advisers were randomly assigned to one of two treatments.
-In the “Baseline” treatment, they only observed the score of the advisee on the mathematics quiz.
-In the “Expectation” treatment, they observed the score as well as the advisee’s guess for how many questions they answered correctly.
-Note that since the outcome is determined only by the past score on the quiz, the advisee’s guess is immaterial to which group they should compete against, and in neither treatment did they receive any demographic information about their advisee.
-Participants gave recommendations to 10 advisees, which unbeknownst to them were five men and five women matched to have identical performance on the test.
-They were informed that if their advice was shown to a participant who returned for the follow-up survey, they would receive the identical bonus as that participant.
-The survey also concluded with basic demographic questions.
-Finally, we invited participants from Stage 1 back for the follow-up survey.
-Following our preregistration, we kept the survey open for 7 days.
-In total, `r scales::comma(dim(study1_time3)[1])`  participants (`r scales::comma(dim(study1_time3[study1_time3$Gender == 'Male',])[1])` men, `r scales::comma(dim(study1_time3[study1_time3$Gender == 'Female',])[1])` women) returned.
-The brief survey reminded them of the task they completed in Stage 1, informed them that other participants from Prolific had observed their real score and given them advice against which group to compete against, and finally were reminded about how many questions they guessed they had answered correctly.
-Importantly, they were not informed of their true score or the score of the groups they could compete against.
-Participants then observed the advice from a randomly selected adviser and made their decision.
+Advisers were randomly assigned to one of two treatments. In the
+“Baseline” treatment, they only observed the score of the advisee on the
+mathematics quiz. In the “Expectation” treatment, they observed the
+score as well as the advisee’s guess for how many questions they
+answered correctly. Note that since the outcome is determined only by
+the past score on the quiz, the advisee’s guess is immaterial to which
+group they should compete against, and in neither treatment did they
+receive any demographic information about their advisee. Participants
+gave recommendations to 10 advisees, which unbeknownst to them were five
+men and five women matched to have identical performance on the test.
+They were informed that if their advice was shown to a participant who
+returned for the follow-up survey, they would receive the identical
+bonus as that participant. The survey also concluded with basic
+demographic questions. Finally, we invited participants from Stage 1
+back for the follow-up survey. Following our preregistration, we kept
+the survey open for 7 days. In total,
+`r scales::comma(dim(study1_time3)[1])` participants
+(`r scales::comma(dim(study1_time3[study1_time3$Gender == 'Male',])[1])`
+men,
+`r scales::comma(dim(study1_time3[study1_time3$Gender == 'Female',])[1])`
+women) returned. The brief survey reminded them of the task they
+completed in Stage 1, informed them that other participants from
+Prolific had observed their real score and given them advice against
+which group to compete against, and finally were reminded about how many
+questions they guessed they had answered correctly. Importantly, they
+were not informed of their true score or the score of the groups they
+could compete against. Participants then observed the advice from a
+randomly selected adviser and made their decision.
 
@@
 ## Results
+
 We begin by examining the performance of the Stage 1 participants.
-Because our treatment takes place after participants complete the mathematics quiz, we would not expect a difference in performance across the Low and High Expectations treatments.
-Indeed, the two groups scored no different from one another (`r round(mean(study1_time1[study1_time1$Condition == "Low",]$count),2)` and `r round(mean(study1_time1[study1_time1$Condition == "High",]$count),2)` for Low and High Expectations treatments, respectively, `r papaja::apa_print(t.test(count ~ Condition, data = study1_time1, var.equal = T))$statistic`).
-The expectations treatment did, however, affect how well they thought they performed.
-Participants in the “Low Expectations” treatment guessed a score of `r round(mean(study1_time1[study1_time1$Condition == "Low",]$count),2)` vs.
-`r round(mean(study1_time1[study1_time1$Condition == "High",]$Guess),2)` in the High Expectations treatment (`r papaja::apa_print(t.test(Guess ~ Condition, data = study1_time1, var.equal = T))$statistic`), showing that the manipulation was successful.
-Contrary to our expectations, we did find a gender difference in performance: men scored `r round(mean(study1_time1[study1_time1$Gender == "Male",]$count),2)` on average, while women scored `r round(mean(study1_time1[study1_time1$Gender == "Female",]$count),2)` (`r papaja::apa_print(t.test(count ~ Gender, data = study1_time1, var.equal = T))$statistic`).
-This difference, however, does not affect the interpretation of our findings, which will rely on an interaction of gender with an experimental treatment for Stage 2 participants.
-Consistent with this difference, men thought they answered more questions correctly than did women (`r round(mean(study1_time1[study1_time1$Gender == "Male",]$Guess),2)` vs `r round(mean(study1_time1[study1_time1$Gender == "Female",]$Guess),2)`, `r papaja::apa_print(t.test(Guess ~ Gender, data = study1_time1, var.equal = T))$statistic`).
+Because our treatment takes place after participants complete the
+mathematics quiz, we would not expect a difference in performance across
+the Low and High Expectations treatments. Indeed, the two groups scored
+no different from one another
+(`r round(mean(study1_time1[study1_time1$Condition == "Low",]$count),2)`
+and
+`r round(mean(study1_time1[study1_time1$Condition == "High",]$count),2)`
+for Low and High Expectations treatments, respectively,
+`r papaja::apa_print(t.test(count ~ Condition, data = study1_time1, var.equal = T))$statistic`).
+The expectations treatment did, however, affect how well they thought
+they performed. Participants in the “Low Expectations” treatment guessed
+a score of
+`r round(mean(study1_time1[study1_time1$Condition == "Low",]$count),2)`
+vs.
+`r round(mean(study1_time1[study1_time1$Condition == "High",]$Guess),2)`
+in the High Expectations treatment
+(`r papaja::apa_print(t.test(Guess ~ Condition, data = study1_time1, var.equal = T))$statistic`),
+showing that the manipulation was successful. Contrary to our
+expectations, we did find a gender difference in performance: men scored
+`r round(mean(study1_time1[study1_time1$Gender == "Male",]$count),2)` on
+average, while women scored
+`r round(mean(study1_time1[study1_time1$Gender == "Female",]$count),2)`
+(`r papaja::apa_print(t.test(count ~ Gender, data = study1_time1, var.equal = T))$statistic`).
+This difference, however, does not affect the interpretation of our
+findings, which will rely on an interaction of gender with an
+experimental treatment for Stage 2 participants. Consistent with this
+difference, men thought they answered more questions correctly than did
+women
+(`r round(mean(study1_time1[study1_time1$Gender == "Male",]$Guess),2)`
+vs
+`r round(mean(study1_time1[study1_time1$Gender == "Female",]$Guess),2)`,
+`r papaja::apa_print(t.test(Guess ~ Gender, data = study1_time1, var.equal = T))$statistic`).
 
-We conducted an OLS regression with the performance and gender of participants and found that with the same performance, male participants are more confident than their female counterparts (`r model1_apa$estimate['GenderMale']`, `r model1_apa$statistic['GenderMale']`).
+We conducted an OLS regression with the performance and gender of
+participants and found that with the same performance, male participants
+are more confident than their female counterparts
+(`r model1_apa$estimate['GenderMale']`,
+`r model1_apa$statistic['GenderMale']`).
 
@@
 ```
-Next, we examine whether advisers took the advisee’s expectations into account.
-Column 1 of Table \@ref(tab:study1regs) reports a linear probability model on advising to compete against the High Performer group for advisers in the “Expectations” treatment.
-Because each adviser was paired with ten advisees, we cluster standard errors at the adviser level.
-Consistent with our prediction, we find that advisees in the High Expectation condition are more likely to be recommended to compete against the High Performer Group, but the result is not significant.
 
-To test whether expectations can lead to more flattering advice for men than for women, we report a linear probability model with advice to compete against the high group as the outcome measure, and the advisee’s gender, whether expectations were shown to the adviser, and the interaction of the two (Column 2 of Table \@ref(tab:study1regs)).
-As predicted, we find a significant interaction effect: men are more likely to be advised to compete against the High Performers when expectations are shown than when they are hidden (p < 0.001; see Figure \@ref(fig:study1genderdiff),).
+Next, we examine whether advisers took the advisee’s expectations into
+account. Column 1 of Table \@ref(tab:study1regs) reports a linear
+probability model on advising to compete against the High Performer
+group for advisers in the “Expectations” treatment. Because each adviser
+was paired with ten advisees, we cluster standard errors at the adviser
+level. Consistent with our prediction, we find that advisees in the High
+Expectation condition are more likely to be recommended to compete
+against the High Performer Group, but the result is not significant.
 
-To examine the quality of advice, we computed the expected bonus earnings for all recommendations.
-We made this calculation by assuming that participants adopted the advice and competed against the recommended competitor group.
-We then compared their scores with all 20 possible competitors one by one and calculated the bonus accordingly to determine the expected bonus earnings.
-We conducted an OLS regression with whether givers see the expectation (Baseline or Information condition) and the gender of the Advisee (Female or Male), as well as their interaction.
-Supporting our theory, male participants will receive less bonus given advice they receive (b = -0.005, p < .01; see also Column 3 of Table \@ref(tab:study1regs)
+To test whether expectations can lead to more flattering advice for men
+than for women, we report a linear probability model with advice to
+compete against the high group as the outcome measure, and the advisee’s
+gender, whether expectations were shown to the adviser, and the
+interaction of the two (Column 2 of Table \@ref(tab:study1regs)). As
+predicted, we find a significant interaction effect: men are more likely
+to be advised to compete against the High Performers when expectations
+are shown than when they are hidden (p \< 0.001; see Figure
+\@ref(fig:study1genderdiff),).
+
+To examine the quality of advice, we computed the expected bonus
+earnings for all recommendations. We made this calculation by assuming
+that participants adopted the advice and competed against the
+recommended competitor group. We then compared their scores with all 20
+possible competitors one by one and calculated the bonus accordingly to
+determine the expected bonus earnings. We conducted an OLS regression
+with whether givers see the expectation (Baseline or Information
+condition) and the gender of the Advisee (Female or Male), as well as
+their interaction. Supporting our theory, male participants will receive
+less bonus given advice they receive (b = -0.005, p \< .01; see also
+Column 3 of Table \@ref(tab:study1regs)
 
@@
 ```
-Finally, we look at the actual earnings of advisees.
-Although participants in the High Expectation condition earned less, this difference is not significant (`r model2_apa$estimate['AdviseeConditionHigh']`, `r model2_apa$statistic['AdviseeConditionHigh']`).
 
-We found that males are more competitive to the extent that they are more likely to choose to compete against High Performer group (`r model3_apa$estimate['GenderMale']`, `r model3_apa$statistic['GenderMale']`), holding performance the same.
+Finally, we look at the actual earnings of advisees. Although
+participants in the High Expectation condition earned less, this
+difference is not significant
+(`r model2_apa$estimate['AdviseeConditionHigh']`,
+`r model2_apa$statistic['AdviseeConditionHigh']`).
+
+We found that males are more competitive to the extent that they are
+more likely to choose to compete against High Performer group
+(`r model3_apa$estimate['GenderMale']`,
+`r model3_apa$statistic['GenderMale']`), holding performance the same.
 
 ## Discussion
-In Study 1, we discovered that although advisers are encouraged to provide accurate advice, they still take into account the expectations of advisees, which are irrelevant to the utility of the advice.
-Due to the fact that males tend to be more confident than their equally competent female counterparts, they are more likely to be recommended to compete against high-performance competitors.
-However, when advice is given to match the advisees' expectations, these flattering recommendations result in lower expected bonus earnings for male participants.
+
+In Study 1, we discovered that although advisers are encouraged to
+provide accurate advice, they still take into account the expectations
+of advisees, which are irrelevant to the utility of the advice. Due to
+the fact that males tend to be more confident than their equally
+competent female counterparts, they are more likely to be recommended to
+compete against high-performance competitors. However, when advice is
+given to match the advisees' expectations, these flattering
+recommendations result in lower expected bonus earnings for male
+participants.
 
 # Study 2
-We then conduct a three-stage experiment to determine why advisers give flattering advice.
-First, we ask a group of advisees to upload selfies and predict their rank in a group of ten people of the same gender based on physical attractiveness.
-Next, we recruit and ask advisers to rank selfies of the opposite gender and recommend which rank the participant ranked 7th should bet on, with the bonus being contingent on whether the participant guessed accurately or found the adviser likable.
-Finally, we show the advisees the advice they have received and ask them to make their final prediction about their rank and evaluate the advice giver in terms of likability, warmth, and trustworthiness.
-Our main hypothesis is that advisers who want to be liked by advisees would recommend a higher rank.
+
+We then conduct a three-stage experiment to determine why advisers give
+flattering advice. First, we ask a group of advisees to upload selfies
+and predict their rank in a group of ten people of the same gender based
+on physical attractiveness. Next, we recruit and ask advisers to rank
+selfies of the opposite gender and recommend which rank the participant
+ranked 7th should bet on, with the bonus being contingent on whether the
+participant guessed accurately or found the adviser likable. Finally, we
+show the advisees the advice they have received and ask them to make
+their final prediction about their rank and evaluate the advice giver in
+terms of likability, warmth, and trustworthiness. Our main hypothesis is
+that advisers who want to be liked by advisees would recommend a higher
+rank.
 
@@
 ## Methods
-We recruited 300 participants and invited them to upload photos of themselves (selfies) to be rated by other participants on attractiveness.
-We ended up with a sample of `r scales::comma(dim(study2_time1[study2_time1$gender == 'Male',])[1])` men and `r scales::comma(dim(study2_time1[study2_time1$gender == 'Female',])[1])` women who agreed to do so and uploaded usable pictures.
-We selected the first 100 photos from women to arrive at a gender-balanced sample ($M_{\text{Age}}$ = `r mean(study2_time1_200$age)` years; 50.0\% Female).
-We informed them that their selfies will be randomly grouped into nine others from the same gender and ranked by people of the opposite gender and asked them to predict their rank, with 1st rank represents the most attractive and 10th rank represents the least attractive.
-We assigned each participant to a group of 10 participants of their own gender.
 
-Next, we recruited `r scales::comma(dim(study2_time2)[1])`new participants and asked them to rank the attractiveness of one such group of 10 participants of the opposite gender ($M_{\text{Age}}$ = `r mean(study2_time2$age)` years; `r round(mean(study2_time2$gender == "Female")*100, 2)`\% Female).
-After they did so, we showed them the photo of the participant they ranked as the 7th  most attractive (that is, the 4th  least attractive) and reminded them that they had ranked this person at 7th attractive.
-We (truthfully) informed them that this participant would have a chance to earn a bonus if they accurately guessed their rank based on the aggregated ratings of all participants who had ranked this group.
-Participants were then randomly assigned to an “accuracy” or a “likeability” treatment.
-In the accuracy treatment, they were told that they would receive a bonus ($1) identical to that of the advisee.
-While in the “likeability” treatment, the amount their bonus depended on how the advisee rated them in terms of likeability, after observing only the rank that they had advised the advisee to guess.
-Advisees would rate to what extent they think the adviser is likable on a 5-point scale, and each point they earn increases their bonus by 20 cents.
+We recruited 300 participants and invited them to upload photos of
+themselves (selfies) to be rated by other participants on
+attractiveness. We ended up with a sample of
+`r scales::comma(dim(study2_time1[study2_time1$gender == 'Male',])[1])`
+men and
+`r scales::comma(dim(study2_time1[study2_time1$gender == 'Female',])[1])`
+women who agreed to do so and uploaded usable pictures. We selected the
+first 100 photos from women to arrive at a gender-balanced sample
+($M_{\text{Age}}$ = `r mean(study2_time1_200$age)` years; 50.0% Female).
+We informed them that their selfies will be randomly grouped into nine
+others from the same gender and ranked by people of the opposite gender
+and asked them to predict their rank, with 1st rank represents the most
+attractive and 10th rank represents the least attractive. We assigned
+each participant to a group of 10 participants of their own gender.
 
-Finally, we invited participants from Stage 1 and were ranked as the 7th attractive by at least one adviser (so that they received advice) back for the follow-up survey.
-Following our preregistration, we kept the survey open for 7 days.
-In total, `r scales::comma(dim(study2_time3)[1])`  participants (`r scales::comma(dim(study2_time3[study2_time3$gender == 'Male',])[1])` men, `r scales::comma(dim(study2_time3[study2_time3$gender == 'Female',])[1])` women) returned.
-They were reminded of the selfie they uploaded in Stage 1 and informed that a group of 10 selfies, including theirs, had been rated by other participants from Prolific.
-They were also introduced to the opportunity to earn a $1 bonus if they guessed their rank accurately.
-Participants were then shown the advice from a randomly selected adviser and made their predictions.
-After deciding which rank to bet on, advisees were reminded of the advice they received and asked to rate the advice giver's likability, warmth, friendliness, good-naturedness, trustworthiness, and sincerity on a 5-point scale.
-The last 6 items were adopted from @Fiske2007.
+Next, we recruited `r scales::comma(dim(study2_time2)[1])`new
+participants and asked them to rank the attractiveness of one such group
+of 10 participants of the opposite gender ($M_{\text{Age}}$ =
+`r mean(study2_time2$age)` years;
+`r round(mean(study2_time2$gender == "Female")*100, 2)`% Female). After
+they did so, we showed them the photo of the participant they ranked as
+the 7th most attractive (that is, the 4th least attractive) and reminded
+them that they had ranked this person at 7th attractive. We (truthfully)
+informed them that this participant would have a chance to earn a bonus
+if they accurately guessed their rank based on the aggregated ratings of
+all participants who had ranked this group. Participants were then
+randomly assigned to an “accuracy” or a “likeability” treatment. In the
+accuracy treatment, they were told that they would receive a bonus (\$1)
+identical to that of the advisee. While in the “likeability” treatment,
+the amount their bonus depended on how the advisee rated them in terms
+of likeability, after observing only the rank that they had advised the
+advisee to guess. Advisees would rate to what extent they think the
+adviser is likable on a 5-point scale, and each point they earn
+increases their bonus by 20 cents.
+
+Finally, we invited participants from Stage 1 and were ranked as the 7th
+attractive by at least one adviser (so that they received advice) back
+for the follow-up survey. Following our preregistration, we kept the
+survey open for 7 days. In total,
+`r scales::comma(dim(study2_time3)[1])` participants
+(`r scales::comma(dim(study2_time3[study2_time3$gender == 'Male',])[1])`
+men,
+`r scales::comma(dim(study2_time3[study2_time3$gender == 'Female',])[1])`
+women) returned. They were reminded of the selfie they uploaded in Stage
+1 and informed that a group of 10 selfies, including theirs, had been
+rated by other participants from Prolific. They were also introduced to
+the opportunity to earn a \$1 bonus if they guessed their rank
+accurately. Participants were then shown the advice from a randomly
+selected adviser and made their predictions. After deciding which rank
+to bet on, advisees were reminded of the advice they received and asked
+to rate the advice giver's likability, warmth, friendliness,
+good-naturedness, trustworthiness, and sincerity on a 5-point scale. The
+last 6 items were adopted from @Fiske2007.
 
 ## Results
+
 ```{r study2advice, fig.cap="Advice for 7th most attractive participants"}
@@
 
-Again, we found supportive evidence that males are more confident about themselves, giving higher initial rank prediction (more attractive) than female participants (`r round(mean(study2_time1[study2_time1$gender == "Male",]$Guess),2)` vs.
-`r round(mean(study2_time1[study2_time1$gender == "Female",]$Guess),2)`, `r papaja::apa_print(t.test(Guess ~ gender, data = study2_time1, var.equal = T))$statistic`).
+Again, we found supportive evidence that males are more confident about
+themselves, giving higher initial rank prediction (more attractive) than
+female participants
+(`r round(mean(study2_time1[study2_time1$gender == "Male",]$Guess),2)`
+vs.
+`r round(mean(study2_time1[study2_time1$gender == "Female",]$Guess),2)`,
+`r papaja::apa_print(t.test(Guess ~ gender, data = study2_time1, var.equal = T))$statistic`).
 
-Examining advice from Stage 2 participants, we found that participants advised a lower rank (that is, more attractive) in the likeability treatment than the accuracy treatment (`r round(mean(study2_time2[study2_time2$Condition == "Likable",]$Advice),2)` vs `r round(mean(study2_time2[study2_time2$Condition == "Accurate",]$Advice),2)`, `r papaja::apa_print(t.test(Advice ~ Condition, data = study2_time2, var.equal = T))$statistic`).
-As seen in Figure \@ref(fig:study2advice), notably, however, even in the accuracy treatment, participants advised a lower rank than they themselves had provided (`r papaja::apa_print(t.test(study2_time2[study2_time2$Condition == "Accurate",]$Advice, mu = 7, var.equal = T))$statistic`).
-This suggests that advisers inferred that advising someone that they were more attractive would make the adviser appear more likeable and therefore provided advice that communicated a more favorable impression of the participants’ attractiveness.
+Examining advice from Stage 2 participants, we found that participants
+advised a lower rank (that is, more attractive) in the likeability
+treatment than the accuracy treatment
+(`r round(mean(study2_time2[study2_time2$Condition == "Likable",]$Advice),2)`
+vs
+`r round(mean(study2_time2[study2_time2$Condition == "Accurate",]$Advice),2)`,
+`r papaja::apa_print(t.test(Advice ~ Condition, data = study2_time2, var.equal = T))$statistic`).
+As seen in Figure \@ref(fig:study2advice), notably, however, even in the
+accuracy treatment, participants advised a lower rank than they
+themselves had provided
+(`r papaja::apa_print(t.test(study2_time2[study2_time2$Condition == "Accurate",]$Advice, mu = 7, var.equal = T))$statistic`).
+This suggests that advisers inferred that advising someone that they
+were more attractive would make the adviser appear more likeable and
+therefore provided advice that communicated a more favorable impression
+of the participants’ attractiveness.
 
@@
 
-To test whether flattering advice brings more positive evaluation of advisers, we create a single index for warmth and trustworthiness by taking average of ratings on warmth, friendliness, good-naturedness, trustworthiness for the former and ratings on trustworthiness, and sincerity for the later.
-As seen in Figure \@ref(fig:study2rating), we found that advisees who suggested that the advisee was more attractive (lower rank) were indeed rated as more likeable and warm (b = -0.109, p < .05; b = -0.133, p < .001; See Columns 1 and 2 of Table 2).
-Interestingly, these benefits are not at the cost of being hypocritical; advisers are also seen as more trustworthy, but the result is only directional (Column 3 of Table 2).
-Notably, however, we were not powered to do a comparison across the two experimental groups.
+To test whether flattering advice brings more positive evaluation of
+advisers, we create a single index for warmth and trustworthiness by
+taking average of ratings on warmth, friendliness, good-naturedness,
+trustworthiness for the former and ratings on trustworthiness, and
+sincerity for the later. As seen in Figure \@ref(fig:study2rating), we
+found that advisees who suggested that the advisee was more attractive
+(lower rank) were indeed rated as more likeable and warm (b = -0.109, p
+\< .05; b = -0.133, p \< .001; See Columns 1 and 2 of Table 2).
+Interestingly, these benefits are not at the cost of being hypocritical;
+advisers are also seen as more trustworthy, but the result is only
+directional (Column 3 of Table 2). Notably, however, we were not powered
+to do a comparison across the two experimental groups.
 
 # Discussion
+
 dvice substantially shapes people's career and personal outcomes.
-Therefore, understanding advisers' motivations has far-reaching implications.
-We propose that advisers' focus on advisees' expectations and the desire to avoid disappointing them can induce gender differences in the advice given and ultimately in the outcomes achieved.
-Gender differences in career outcomes contribute significantly to the gender wage gap, with women often holding less senior positions and experiencing worse career outcomes, even with equal performance.
-Therefore, identifying a factor such as expectations that contributes to this gap has important implications for organizational practice.
+Therefore, understanding advisers' motivations has far-reaching
+implications. We propose that advisers' focus on advisees' expectations
+and the desire to avoid disappointing them can induce gender differences
+in the advice given and ultimately in the outcomes achieved. Gender
+differences in career outcomes contribute significantly to the gender
+wage gap, with women often holding less senior positions and
+experiencing worse career outcomes, even with equal performance.
+Therefore, identifying a factor such as expectations that contributes to
+this gap has important implications for organizational practice.
 
-In this paper, we examine a novel and unexplored factor of advice-giving: interpersonal considerations.
-Advisers who take into account the advisee's belief utility inflate their advice to convey a more favorable impression, leading to worse decisions and gender differences.
-Men have more inflated expectations than women, and taking expectations into account can lead to gender differences, even without discrimination.
-We ruled out discrimination as a separate channel by withholding information about the gender of the advisee.
-Finally, we expect that advisers are aware of the tradeoff between giving accurate advice and avoiding disappointment and, thus, are less likely to inflate their advice when advisees can compensate them after observing the outcome of their choice.
+In this paper, we examine a novel and unexplored factor of
+advice-giving: interpersonal considerations. Advisers who take into
+account the advisee's belief utility inflate their advice to convey a
+more favorable impression, leading to worse decisions and gender
+differences. Men have more inflated expectations than women, and taking
+expectations into account can lead to gender differences, even without
+discrimination. We ruled out discrimination as a separate channel by
+withholding information about the gender of the advisee. Finally, we
+expect that advisers are aware of the tradeoff between giving accurate
+advice and avoiding disappointment and, thus, are less likely to inflate
+their advice when advisees can compensate them after observing the
+outcome of their choice.
 
-The findings of this study suggest that organizations can promote gender equity by calibrating employees' expectations or shifting advisers' attention away from them.
-While these measures may not entirely solve the gender gap problem, they can make a meaningful difference when unconscious bias interventions have failed to show any effect [@Chang2019; @Paluck2009].
-We believe our findings may be particularly relevant to societies that value signaling in interpersonal relationships, including Hong Kong and many Asian countries.
-Future work could also examine whether people in different cultures place more weight on expectations.
+The findings of this study suggest that organizations can promote gender
+equity by calibrating employees' expectations or shifting advisers'
+attention away from them. While these measures may not entirely solve
+the gender gap problem, they can make a meaningful difference when
+unconscious bias interventions have failed to show any effect
+[@Chang2019; @Paluck2009]. We believe our findings may be particularly
+relevant to societies that value signaling in interpersonal
+relationships, including Hong Kong and many Asian countries. Future work
+could also examine whether people in different cultures place more
+weight on expectations.
 

### 2024-01-14 manuscript/manuscript.Rmd
Reorganized folder

--- 2024-01-14 Advice Giving.Rmd
@@
 
-Seeking and giving advice can be challenging conversations to navigate.
-Advice seekers may be embarrassed to ask for help [@Benabou2022], and
-they may fail to do so if the information they receive could lead to
-disappointment [@Gill2012]. Indeed, people prefer advisers who withhold
-unpleasant information [@Shalvi2019] and punish those who tell them
-things they do not want to hear [@John2019]. People appear to engage in
-strategic selection of advice to avoid unpleasant information and
-protect the utility they get from positive beliefs about themselves and
-the future they anticipate [@Loewenstein2018; @Loewenstein1987]. But do
-advice givers anticipate and consider the hedonic cost of honest
-information to the recipient? While previous work has emphasized the
-instrumental value of advice (e.g., satisfaction with a decision or
-accuracy of a prediction), we focus on the motivations of the person
-providing advice.
+Seeking and giving advice can present conversational challenges that
+are difficult to navigate. Advice seekers may be embarrassed to ask for
+help [@Benabou2022], and they may fail to do so if the information they
+receive could lead to disappointment [@Gill2012]. Indeed, people prefer
+advisers who withhold unpleasant information [@Shalvi2019] and punish
+those who tell them things they do not want to hear [@John2019]. People
+appear to engage in strategic selection of advice to avoid unpleasant
+information and protect the utility they get from positive beliefs about
+themselves and the future they anticipate [@Loewenstein2018;
+@Loewenstein1987]. But do advice givers anticipate and consider the
+hedonic cost of honest information to the recipient? While previous work
+has emphasized the instrumental value of advice (e.g., satisfaction with
+a decision or accuracy of a prediction), we focus on the motivations of
+the person providing advice.
 
@@
 the preferences of the advisee [@Kray2000; @Kray1999]. When they are
-uncertain, they prefer that advisees do not rely (extensively) on their
+uncertain, they even prefer that advisees do not rely (extensively) on their
 recommendations [@Ache2020]. Thus, it seems that people are concerned
@@
 performing student to switch to a less-demanding major conveys a belief
-that the student is not capable of improving. Thus, the painful truth
-may prevent someone from making a bad decision, it may come at a cost to
+that the student is not capable of improving. Thus, while the painful truth
+may prevent someone from making a bad decision, it may come at a hedonic cost to
 the recipient and damage the relationship between the adviser and
@@
 
-Our account therefore predicts that people receive advice that is more
+Our account therefore predicts that people give and receive advice that is more
 flattering and suggestive of inflated ability and optimistic outcomes
@@
 advisee's expectations (reference point). @Exley2022 show that men are
-more overconfident than women, conditional on equal performance and that
-people anticipate but fail to incorporate this difference into their
-decisions. An adviser who seeks to avoid disappointment and incorporates
+more overconfident than women, conditional on equal performance, and that
+people anticipate this difference. An adviser who seeks to avoid disappointment and incorporates
 expectations into their advice would then present more favorable advice
@@
 that men receive more aspirational advice than do women [@Kanze2018].
-
 Notably, when it pays to have accurate beliefs, such flattering advice
@@
 would also suffer greater costs from aiming too high and failing to meet
-the objective. This may seem at odds with a gender gap favoring men.
-However, observational data often miss people who were unsuccessful. For
-example, job candidates who ask for a high starting salary may be less
-likely to receive a job offer, but will also have a higher starting
-salary conditional on receiving an offer.
+the objective.
 
@@
 incentivized based on the outcome of the advisee’s decision. In a second
-preregistered experiment (n = 700), we show that advisers respond to
-interpersonal considerations. They advice people that they are more
+preregistered experiment (n = 700), we show that advisers respond to incentives for
+interpersonal considerations. They tell people that they are more
 attractive than they believe them to be, and inflate to a greater extent
-when incentivized for likability rather than accuracy. Advisees indeed
-reward such flattering advice, finding the advisers more likeable and no
+when incentivized for likability rather than accuracy. Notably, they inflate
+even when only incentivized for accuracy. Advisees indeed
+reward such flattering advice, rating the advisers more likeable and no
 less trustworthy than those who provide more accurate advice.
@@
 
-We report all sample sizes, data exclusions, all manipulations, and all
+We report all sample sizes, data exclusions, manipulations, and
 measures in the studies. Screen captures of the experimental materials
@@
 well as the preregistration reports are available via OSF. All our
-studies were preregistered on AsPredicted.org. (will do this later)
+studies were preregistered on AsPredicted.org.^[<https://osf.io/8r3d4/?view_only=5ad7bafcd16b4d4ba08bb28b0e2bd02d>]
 

### 2024-01-14 manuscript/manuscript.Rmd
Study 1.

@@
 about providing good advice even when they are not incentivized for the
-recipient’s decision quality.
+recipient's decision quality.
 
@@
 when the interactions are entirely anonymous and they are incentivized
-for the quality of the advisee’s decision.
+for the quality of the advisee's decision.
 
@@
 Incorporating expectations leads to worse advice, even when advisers are
-incentivized based on the outcome of the advisee’s decision. In a second
+incentivized based on the outcome of the advisee's decision. In a second
 preregistered experiment (n = 700), we show that advisers respond to incentives for
@@
 We begin by examining whether advisers take the expectations of advisees
-into account, even when those expectations are not relevant to the
-quality of advice. In a three-stage experiment, we first recruit a
+into account, even when those expectations are not relevant to the decision
+the advisee has to make. In a three-stage experiment, we first recruit a
 sample of advisees and ask them to complete a mathematics quiz. After
-answering all ten multiple-choice questions, participants are anchored
+answering ten multiple-choice questions, participants are anchored
 to low or high performance expectations and asked to guess how many
-questions they answered correctly. Next, we recruit advice givers and
+questions they answered correctly. Next, we recruit advisers and
 show them either only the true performance of the advisee, or the true
@@
 against a group of high-performers or a group of low-performers on the
-mathematics quiz. Finally, we invite the advisees back and show them the
+mathematics quiz, where a potential bonus depends on outperforming the competitor
+and which group was chosen. Finally, we invite the advisees back and show them the
 advice they have received. Advisees then pick whether to compete against
-high or low performers, based on their past performance on the quiz. Our
-key hypothesis is that advisees who were anchored to high expectations
+high or low performers, with the outcome determined by their past performance on the quiz. Our
+key hypotheses are that (1) advisees who were anchored to high expectations
 would be more likely to receive advice to compete against the high
-performer group.
+performer group, and (2) that men are more likely than women to be advised to 
+compete against the high-performer group when expectations are shown.
 
@@
 
-We first recruited a sample of `r scales::comma(dim(study1_math50)[1])`
+As part of our main experiment, participants choose to compete against a group
+of previous participants and have their expectations anchored based on their performance.
+Thus, we begin by first recruiting a sample of `r scales::comma(dim(study1_math50)[1])`
 participants from Prolific to complete a 10-question multiple choice
@@
 ASVAB standardized exam, such that answers were not available online.
-Participants had 5 minutes to answer the quiz and were paid 10 cents for
+Participants had five minutes to answer the quiz and were paid 10 cents for
 each correctly answered question. We define the top 20 scorers as the
-“High Performers” and the bottom 20 scorers as the “Low Performers.” On
+"High Performers" and the bottom 20 scorers as the "Low Performers." On
 average, participants answered `r round(mean(study1_math50$Score),2)`
@@
 `r HP_upper`, and Low Performers scored between `r LP_lower` and
-`r LP_upper`. We further simulated 1,000 pairings of groups of five
-participants, with the 5 th percentile of groups scoring an average of
-`r p5` and the 95 th percentile scoring an average of `r p95`. We use
-these participants as the competitors for the advisees in our main
-experiment, and the average group scores to anchor expectations.
+`r LP_upper`. In order to anchor the expectations of participants in our main
+experiment, we simulated 1,000 pairings of groups of five
+participants, with the 5<sup>th</sup> percentile of groups scoring an average of
+`r p5` and the 95 th percentile scoring an average of `r p95`. We report these
+averages to participants in the Low Expectations and High Expectations treatment,
+respectively.
 
-Next, we recruited `r scales::comma(dim(study1_time1All)[1])`
-participants in Stage 1 of our main experiment, for the role of
-advisees. To arrive at a gender-balanced sample, we dropped the last two
+We then recruited `r scales::comma(dim(study1_time1All)[1])`
+participants for the role of advisees in Stage 1 of our main experiment.
+To arrive at a gender-balanced sample, we dropped the last two
 male participants to complete the survey, ending up with a sample of 500
-men and 500 women ($M_{\text{Age}}$ = `r mean(study1_time1$Age)`,50%
-Female). Participants completed the same 10-item mathematics quiz as the
+men and 500 women ($M_{\text{Age}}$ = `r mean(study1_time1$Age)`). 
+Participants completed the same 10-item mathematics quiz as the
 earlier participants and were informed that their performance would
-affect their bonus earnings in a follow-up study to be conducted a few
+affect their bonus earnings in a follow-up stage to be conducted a few
 days later. After completing the quiz, we informed them of the average
 score of a group of five participants from the preliminary survey. We
-randomly assigned them to learn about the 5 th percentile of groups,
-which scored `r p5`. (“Low Expectations” treatment) or the 95 th
-percentile of groups, which scored `r p95` (“High Expectations”
+randomly assigned them to learn about the 5<sup>th</sup> percentile of groups,
+which scored `r p5`. ("Low Expectations" treatment) or the 95<sup>th</sup>
+percentile of groups, which scored `r p95` ("High Expectations"
 treatment). Participants then made a guess (unincentivized) about how
@@
 preliminary study and Stage 1 had completed, and informed them of the
-average score in the preliminary study. Advisers had to recommend
+average score of all participants in the preliminary study. Advisers had to recommend
 whether an advisee should compete against the Low Performers or the High
 Performers (we used these terms in the survey). We anticipated that
-being told to compete against High Performers is more flattering.
+being told to compete against High Performers is more flattering and hence being
+told to compete against the Low Performers would be disappointing if one had
+expected to do well.
 Advisees would earn 30 cents if their score was equal to or higher than
@@
 compete against this group, or 50 cents if they performed as well or
-better than a randomly selected member of the High Performer group. If
+better than a randomly selected member of the High Performer group and they
+chose to compete against that group. If
 they scored lower, they would not receive any bonus.
@@
 Advisers were randomly assigned to one of two treatments. In the
-“Baseline” treatment, they only observed the score of the advisee on the
-mathematics quiz. In the “Expectation” treatment, they observed the
-score as well as the advisee’s guess for how many questions they
+"Baseline" treatment, they only observed the score of the advisee on the
+mathematics quiz. In the "Expectation" treatment, they observed the
+score as well as the advisee's guess for how many questions they
 answered correctly. Note that since the outcome is determined only by
-the past score on the quiz, the advisee’s guess is immaterial to which
-group they should compete against, and in neither treatment did they
+the past score on the quiz, the advisee's guess is immaterial to which
+group they should compete against. Moreover, in neither treatment did they
 receive any demographic information about their advisee. Participants
 gave recommendations to 10 advisees, which unbeknownst to them were five
-men and five women matched to have identical performance on the test.
+men and five women matched to have identical performance on the test.^[We made this decision to account for the possibility of gender differences in performance.]
 They were informed that if their advice was shown to a participant who
 returned for the follow-up survey, they would receive the identical
-bonus as that participant. The survey also concluded with basic
-demographic questions. Finally, we invited participants from Stage 1
+bonus as that participant. The survey then concluded with basic
+demographic questions.
+
+Finally, we invited participants from Stage 1
 back for the follow-up survey. Following our preregistration, we kept
@@
 Prolific had observed their real score and given them advice against
-which group to compete against, and finally were reminded about how many
+which group to compete against, and finally were reminded them of how many
 questions they guessed they had answered correctly. Importantly, they
@@
 We begin by examining the performance of the Stage 1 participants.
-Because our treatment takes place after participants complete the
+Because our treatment takes place after participants completed the
 mathematics quiz, we would not expect a difference in performance across
@@
 `r round(mean(study1_time1[study1_time1$Condition == "High",]$count),2)`
-for Low and High Expectations treatments, respectively,
+for the Low Expectations and High Expectations treatments, respectively,
 `r papaja::apa_print(t.test(count ~ Condition, data = study1_time1, var.equal = T))$statistic`).
 The expectations treatment did, however, affect how well they thought
-they performed. Participants in the “Low Expectations” treatment guessed
+they performed. Participants in the "Low Expectations" treatment guessed
 a score of
@@
 (`r papaja::apa_print(t.test(Guess ~ Condition, data = study1_time1, var.equal = T))$statistic`),
-showing that the manipulation was successful. Contrary to our
+showing that the manipulation was successful, albeit small. Contrary to our
 expectations, we did find a gender difference in performance: men scored
@@
 (`r papaja::apa_print(t.test(count ~ Gender, data = study1_time1, var.equal = T))$statistic`).
-This difference, however, does not affect the interpretation of our
-findings, which will rely on an interaction of gender with an
-experimental treatment for Stage 2 participants. Consistent with this
-difference, men thought they answered more questions correctly than did
+Consistent with this difference, men thought they answered more questions 
+correctly than did
 women
@@
 `r papaja::apa_print(t.test(Guess ~ Gender, data = study1_time1, var.equal = T))$statistic`).
+This difference, however, does not affect the interpretation of our
+findings, which will rely on an interaction of gender with an
+experimental treatment for Stage 2 participants.
 
-We conducted an OLS regression with the performance and gender of
-participants and found that with the same performance, male participants
-are more confident than their female counterparts
-(`r model1_apa$estimate['GenderMale']`,
-`r model1_apa$statistic['GenderMale']`).
+We define a measure of "overconfidence" as (Performance - Estimate). We observe
+that women underestimate their performance by 0.76 points, while men do so by
+only 0.27 points `r papaja::apa_print(t.test(overconfidence ~ Gender, data = study1_time1 %>% dplyr::mutate(overconfidence = Guess - count)))$full_result`.
+Although neither gender is overconfident, men on average are more confident in
+their performance than are women, as we had expected.
+
+<!-- We conducted an OLS regression with the performance and gender of -->
+<!-- participants and found that with the same performance, male participants -->
+<!-- are more confident than their female counterparts -->
+<!-- (`r model1_apa$estimate['GenderMale']`, -->
+<!-- `r model1_apa$statistic['GenderMale']`). -->
+
+<!-- David: I don't think we can do this regression, but defining overconfidence with a difference score and doing a t-test should be fine. -->
 
 ```{r study1regs}
-study1_advice <- study1_advice %>% dplyr::mutate(TreatmentHigh = ifelse(Treatment == 'High',1,0))
+study1_advice <- study1_advice %>% dplyr::mutate(Treatment = factor(Treatment, levels = c('Low', 'High')))
 
-modelsummary::modelsummary(list(`(1)` = lm(Advice ~ TreatmentHigh + Performance , data = study1_advice %>% dplyr::filter(ExpShow == 1)),
+# David: No need to redefine a factor variable as a continuous number. Easier to just change the reference level.
+
+modelsummary::modelsummary(list(`(1)` = lm(Advice ~ Treatment + Performance , data = study1_advice %>% dplyr::filter(ExpShow == 1)),
                                 `(2)` = lm(Advice ~ ExpShow*Gender , data = study1_advice),
@@
 Column 3 displays the expected bonus of the advice received based on the gender of the targets and the expectation level shown to the advisor.
-All results are clustered at the level of the advisor and include standard errors.") %>%
+All standard errors clustered at the level of the advisor.") %>%
   kableExtra::kable_styling(latex_option = "scale_down")
@@
 
-```{r study1genderdiff, fig.cap ="Advice given to men and women.
-Advisers observed real performance and the participants’ estimated performance, but not their gender.
-As a result of their higher expectations, men were advised to compete against the high performance group more often.
-In the treatment in which expectations were not shown to the advisors, no gender differences emerged (not displayed in this figure).."}
+```{r study1genderdiff, fig.cap ="Advisers observed real performance and the participants' estimated performance, but not their gender.
+As a result of their higher expectations, men (blue) were advised to compete against the high performance group more often than women (red).
+The grey line shows advice absent expectations, which did not differ by gender."}
 library(dplyr)
@@
               method = "glm", method.args = list(family = "binomial"), color = "grey", se = FALSE) +
-  scale_color_manual(values = c("#FFA500", "#4169E1", "grey"),
-                     labels = c("Female_withExpectation", "Male_withExpectation", "NoExpectation")) +
-  scale_y_continuous(name = "P(Compete Against High Performance)") +
-  scale_x_continuous(name = "Performance") +
+  scale_color_manual(values = c("red", "#4169E1", "grey"),
+                     labels = c("Female + Expectations", "Male + Expectations", "Expectation Hidden")) +
+  scale_y_continuous(name = "P(Compete Against High Performance)",
+                     labels = scales::percent,
+                     expand = c(0, 0)) +
+  scale_x_continuous(name = "Performance",
+                     expand = c(0, 0),
+                     breaks = seq(0, 10, 2)) +
   theme_bw() +
@@
 
-```{r}
+<!-- David: Is there something different about the figure below or can we delete? -->
+```{r, eval = F}
 library(dplyr)
@@
 
-Next, we examine whether advisers took the advisee’s expectations into
+Next, we examine whether advisers took the advisee's expectations into
 account. Column 1 of Table \@ref(tab:study1regs) reports a linear
 probability model on advising to compete against the High Performer
-group for advisers in the “Expectations” treatment. Because each adviser
-was paired with ten advisees, we cluster standard errors at the adviser
-level. Consistent with our prediction, we find that advisees in the High
-Expectation condition are more likely to be recommended to compete
-against the High Performer Group, but the result is not significant.
+group for advisers in the "Expectations" treatment, controlling for the
+true performance of the advisee. Because each adviser
+made ten recommendations, we cluster standard errors at the adviser
+level. However, contrary to our expectations, we do not see a significant
+effect of the expectations treatment. This may be because the induced difference
+in expectations was too small.
 
-To test whether expectations can lead to more flattering advice for men
-than for women, we report a linear probability model with advice to
-compete against the high group as the outcome measure, and the advisee’s
+However, recall that men were more confident in their performance than were women.
+Our theory thus predicts that showing expectations should lead to more flattering
+advice (i.e., a recommendation to compete against the High Performer group) for
+men than for women. We report a linear probability model with advice to
+compete against the high group as the outcome measure, and the advisee's
 gender, whether expectations were shown to the adviser, and the
-interaction of the two (Column 2 of Table \@ref(tab:study1regs)). As
+interaction of the two in Column 2 of Table \@ref(tab:study1regs). As
 predicted, we find a significant interaction effect: men are more likely
 to be advised to compete against the High Performers when expectations
-are shown than when they are hidden (p \< 0.001; see Figure
-\@ref(fig:study1genderdiff),).
+are shown than when they are hidden ($p < 0.001$).
+We show this result graphically in Figure \@ref(fig:study1genderdiff)).
+<!-- David: Can you add a description of the figure here? -->
 
 To examine the quality of advice, we computed the expected bonus
-earnings for all recommendations. We made this calculation by assuming
-that participants adopted the advice and competed against the
-recommended competitor group. We then compared their scores with all 20
-possible competitors one by one and calculated the bonus accordingly to
-determine the expected bonus earnings. We conducted an OLS regression
-with whether givers see the expectation (Baseline or Information
-condition) and the gender of the Advisee (Female or Male), as well as
-their interaction. Supporting our theory, male participants will receive
-less bonus given advice they receive (b = -0.005, p \< .01; see also
-Column 3 of Table \@ref(tab:study1regs)
+earnings for someone who followed the recommendations. For example, if an
+adviser suggested competing against the High Performer group, we matched the
+advisee against all 20 members of that group and determined how often their score
+matched or exceeded that of the member. We then multiplied this number by the
+respective bonus earnings (50 cents and 30 cents for the High and Low Performer 
+group, respectively). To see if including expectations leads to worse advise
+for men, we report a linear probability model with the experimental treatment
+of the adviser, the gender of the advisee, and their interaction in Column 3
+of Table \@ref(tab:study1regs). Displaying expectations led men to be advised
+to compete against the High Performer group more often, and this advise turned
+out to be bad: men receive worse advise than do women when expectations are 
+displayed, but not in their absence.^[This analysis was not preregistered, and we note here that the reduction in expected earnings is small.
+However, it is interesting that expectations have a negative effect for men who underestimate their performance on average.
+One possibility is that advisers suggest the High Performer group more often than is optimal.
+We return to the possibility that advice is overall biased to be flattering in Study 2.]
 
@@
 
-Finally, we look at the actual earnings of advisees. Although
-participants in the High Expectation condition earned less, this
-difference is not significant
-(`r model2_apa$estimate['AdviseeConditionHigh']`,
-`r model2_apa$statistic['AdviseeConditionHigh']`).
+To determine whether flattering advice is truly costly, however, we need
+to examine the outcome of the advisees. In particular, they could ignore flattering
+advice, recognizing it as such and thus failing to adhere to it.
 
-We found that males are more competitive to the extent that they are
-more likely to choose to compete against High Performer group
-(`r model3_apa$estimate['GenderMale']`,
-`r model3_apa$statistic['GenderMale']`), holding performance the same.
+<!-- David: Let's turn the regression you discussed below into a column of the Table above -->
+<!-- David: Also, one more suggestion for an analysis: let's look at whether Advisees followed the recommendation they received as an other linear probability model (1/0).
+I would suggest predictors of whether it's the High Performer group, whether the adviser saw expectations, the gender of the advisee.
+Also, another model that has the two-way interaction for all of those.
+We may not end up reporting this, but I would be curious to see.
+-->
+
+<!-- Finally, we look at the actual earnings of advisees. Although -->
+<!-- participants in the High Expectation condition earned less, this -->
+<!-- difference is not significant -->
+<!-- (`r model2_apa$estimate['AdviseeConditionHigh']`, -->
+<!-- `r model2_apa$statistic['AdviseeConditionHigh']`). -->
+
+<!-- We found that males are more competitive to the extent that they are -->
+<!-- more likely to choose to compete against High Performer group -->
+<!-- (`r model3_apa$estimate['GenderMale']`, -->
+<!-- `r model3_apa$statistic['GenderMale']`), holding performance the same. -->
 
 ## Discussion
+When the quality of a decision is not dependent on someone's expectations,
+advice should not be moved by whether an adviser is aware of the advisees
+expectations. However, consistent with our account that advisers consider the
+belief utility of the advisee and want to flatter, rather than disappoint them,
+we find that displaying expectations to advisers does matter.
+Specifically, we found that men underestimate their score on a mathematics test
+less than do women. When these expectations are displayed to advisers, they
+are more likely to tell men to compete against the High Performer group.
+Notably, this is bad advice: men's expected earnings decreases if their
+expectations are shown to advisers.
 
-In Study 1, we discovered that although advisers are encouraged to
-provide accurate advice, they still take into account the expectations
-of advisees, which are irrelevant to the utility of the advice. Due to
-the fact that males tend to be more confident than their equally
-competent female counterparts, they are more likely to be recommended to
-compete against high-performance competitors. However, when advice is
-given to match the advisees' expectations, these flattering
-recommendations result in lower expected bonus earnings for male
-participants.
+<!-- David: One more sentence about the earnings difference here, which does not -->
+<!-- differ significantly. And one sentence about the new analysis of whether -->
+<!-- people follow the advice or not. -->
 
@@
 all participants who had ranked this group. Participants were then
-randomly assigned to an “accuracy” or a “likeability” treatment. In the
+randomly assigned to an "accuracy" or a "likeability" treatment. In the
 accuracy treatment, they were told that they would receive a bonus (\$1)
-identical to that of the advisee. While in the “likeability” treatment,
+identical to that of the advisee. While in the "likeability" treatment,
 the amount their bonus depended on how the advisee rated them in terms
@@
 therefore provided advice that communicated a more favorable impression
-of the participants’ attractiveness.
+of the participants' attractiveness.
 

### 2024-01-14 manuscript/manuscript.Rmd
Study 1.

@@
 ## Discussion
-When the quality of a decision is not dependent on someone's expectations,
-advice should not be moved by whether an adviser is aware of the advisees
-expectations. However, consistent with our account that advisers consider the
-belief utility of the advisee and want to flatter, rather than disappoint them,
-we find that displaying expectations to advisers does matter.
-Specifically, we found that men underestimate their score on a mathematics test
-less than do women. When these expectations are displayed to advisers, they
-are more likely to tell men to compete against the High Performer group.
-Notably, this is bad advice: men's expected earnings decreases if their
-expectations are shown to advisers.
 
-<!-- David: One more sentence about the earnings difference here, which does not -->
-<!-- differ significantly. And one sentence about the new analysis of whether -->
-<!-- people follow the advice or not. -->
+In Study 1, we discovered that although advisers are encouraged to
+provide accurate advice, they still take into account the expectations
+of advisees, which are irrelevant to the utility of the advice. Due to
+the fact that males tend to be more confident than their equally
+competent female counterparts, they are more likely to be recommended to
+compete against high-performance competitors. However, when advice is
+given to match the advisees' expectations, these flattering
+recommendations result in lower expected bonus earnings for male
+participants.
 

### 2024-01-14 manuscript/manuscript.Rmd
Edits up to the beginning of Methods of Study 2.

--- 2024-01-14 manuscript/manuscript.Rmd
@@
 Column 3 displays the expected bonus of the advice received based on the gender of the targets and the expectation level shown to the advisor.
-All standard errors clustered at the level of the advisor.") %>%
-  kableExtra::kable_styling(latex_option = "scale_down")
+All standard errors clustered at the level of the advisor.")
 
@@
 are more likely to tell men to compete against the High Performer group.
-Notably, this is bad advice: men's expected earnings decreases if their
-expectations are shown to advisers.
+Notably, this is bad advice: men whose advisers observed their expectations
+got worse advice as a result.
 
@@
 
-We then conduct a three-stage experiment to determine why advisers give
-flattering advice. First, we ask a group of advisees to upload selfies
-and predict their rank in a group of ten people of the same gender based
-on physical attractiveness. Next, we recruit and ask advisers to rank
-selfies of the opposite gender and recommend which rank the participant
-ranked 7th should bet on, with the bonus being contingent on whether the
-participant guessed accurately or found the adviser likable. Finally, we
-show the advisees the advice they have received and ask them to make
-their final prediction about their rank and evaluate the advice giver in
-terms of likability, warmth, and trustworthiness. Our main hypothesis is
-that advisers who want to be liked by advisees would recommend a higher
-rank.
+<!-- David: Just commenting on what I tried to do here... a bit of a transition -->
+<!-- for why this study follows from the last. -->
+So far, we have shown that displaying expectations can induce gender
+differences in advice given. Specifically, advisers were more likely to
+recommend competing against a group of High Performers to men who had higher
+expectations about their performance. We now test directly whether this 
+is driven by interpersonal concerns. Specifically, we examine whether 
+more flattering advice is the result of a desire to be liked and whether
+advisees indeed do like advisers more when they give flattering advice.
+
+We conducted a three-stage experiment in which we experimentally manipulated
+the incentives for advicers. We began by inviting a group of advisees to upload 
+photos of themselves ("selfies") and informed them that they would be rated
+on their attractiveness. We grouped them with nine other participants of the
+same gender and recruited participants of the opposing gender to rank them from
+most to least attractive and to provide advice. Specifically, we asked them
+to advise the participant they ranked as the 7th most attractive (4th least attractive)
+on what rank they should bet they were ranked by a larger group of raters.
+Advisers were randomly assigned to two treatments, receiving a bonus payment
+either if the advisee guessed their rank accurately or if the advisee evaluated
+the adviser as likeable as measured by an unincentivized scale response.
+We hypothesize that advisers who want to be liked by advisees will recommend 
+that they bet on a lower rank, i.e. that they are more attractive.
 
@@
                            caption = "When individuals receive advice that implies a high level of attractiveness (lower rank), they tend to perceive the advice giver as more likable (Column 1), warm (Column 2).
-Column 3 shows that advisors are rated as more trustworthy when they advice lower ranks, but this relationship is only directional.") %>%
-  kableExtra::kable_styling(latex_option = "scale_down")
+Column 3 shows that advisors are rated as more trustworthy when they advice lower ranks, but this relationship is only directional.")
 

### 2024-01-15 manuscript/manuscript.Rmd
Before Study 2 Method

@@
 We discuss practical and theoretical contributions and future research directions.
-
 keywords          : "Gender difference, Advice, Interpresonal relationship"
@@
 
-<!-- We conducted an OLS regression with the performance and gender of -->
-<!-- participants and found that with the same performance, male participants -->
-<!-- are more confident than their female counterparts -->
-<!-- (`r model1_apa$estimate['GenderMale']`, -->
-<!-- `r model1_apa$statistic['GenderMale']`). -->
-
-<!-- David: I don't think we can do this regression, but defining overconfidence with a difference score and doing a t-test should be fine. -->
-
 ```{r study1regs}
@@
         plot.title = element_text(hjust = 0.5, size = 20))
-
-```
-
-<!-- David: Is there something different about the figure below or can we delete? -->
-```{r, eval = F}
-library(dplyr)
-library(ggplot2)
-library(magrittr)
-
-ProbHG <- study1_advice %>%
-  group_by(Condition, Performance, Gender) %>%
-  dplyr::summarize(avg_hardGroup = mean(Advice))
-
-df_exp <- subset(ProbHG, Condition == "E")
-df_none <- subset(ProbHG, Condition == "None")
-
-ggplot(df_exp, aes(x = Performance, y = avg_hardGroup, color = Gender)) +
-  geom_smooth(method = "glm", method.args = list(family = "binomial"),se = FALSE) +
-  scale_color_manual(values = c("#FFA500", "#4169E1"),
-                     labels = c("Female_withExpectation", "Male_withExpectation")) +
-  scale_y_continuous(name = "P(Compete Against High Performance)") +
-  scale_x_continuous(name = "Performance") +
-  theme_bw() +
-  theme(panel.grid = element_blank(),
-        panel.border = element_blank(),
-        axis.line = element_line(colour = "grey"),
-        legend.position = "bottom",
-        legend.title = element_blank(),
-        legend.key.size = unit(1.2, "lines"),
-        legend.text = element_text(size = 12),
-        plot.title = element_text(hjust = 0.5, size = 20))
-
 ```
@@
 We show this result graphically in Figure \@ref(fig:study1genderdiff)).
-<!-- David: Can you add a description of the figure here? -->
+<!-- Amanda: The gender discrepancy in advice is more significant when performance is less decisive.
+When performance is extremely low, there is no chance to win high performers and only a slim chance when competing with low performers.
+When performance is extremely high, it makes no sense to forgo the high chance to win more and choose a low bonus.
+However, in the middle range of performance, either option has pros and cons, and neither is absolutely better.
+In such a situation, advisers would take participants' expectations into account, regarding them as a critical factor.
+-->
 
@@
 
-```{r}
-study1_time3 <- study1_time3 %>% dplyr::mutate(AdviseeConditionHigh = ifelse(AdviseeCondition =='High',1,0))
+```{r study1time3}
 
-model2 <- lm(bonus ~ AdviseeConditionHigh + AdviseeScore, data = study1_time3)
-model2_apa <- apa_print(model2)
+study1_time3 <- study1_time3 %>% dplyr::mutate(AdviseeCondition = factor(AdviseeCondition, levels = c('Low', 'High'))) %>%
+     dplyr::mutate(Adopt = ifelse(Bet == Advice,1,0))
 
-model3 <- lm(Bet ~ Gender + AdviseeScore, data = study1_time3)
-model3_apa <- apa_print(model3)
+modelsummary::modelsummary(list(`(1)` = lm(bonus ~ AdviseeCondition + AdviseeScore , data = study1_time3),
+                                `(2)` = lm(Bet ~ Gender + AdviseeScore , data = study1_time3),
+                                `(3)` = lm(Adopt ~ Gender + GiverCondition + Advice, data = study1_time3),
+                                `(4)` = lm(Adopt ~ Gender + GiverCondition + Advice + Gender*GiverCondition + GiverCondition*Advice + Gender*Advice, data = study1_time3)),
+                           vcov = c("classical", "classical","classical","classical"),
+                            coef_map = c("AdviseeScore" = "Performance",
+                                         "AdviseeConditionHigh" = "High Expectation",
+                                        "GenderMale" = "Advisee Male",
+                                        "GenderMale:GiverCondition" = "Expectation x Male",
+                                        "GiverCondition" = "Expectation Shown",
+                                        "Advice1" = "Advice: High Performer",
+                                        "GenderMale:Advice1" = "Advice: High Performer x Male",
+                                        "GiverCondition:Advice1" = "Expectation x Advice: High Performer",
+                                        "(Intercept)" = "Constant"),
+                           stars = T,
+                           gof_map = list(list('raw' = 'nobs', 'clean' = 'N', 'fmt' = 0)),
+                           caption = "Column 1 displays the actual bonus based on the performance and whether the participant is primed with high expectations.
+Column 2 displays whether the participant chooses to compete against a high-performance group based on performance and gender of the participants.
+Columns 3 and 4 display the chance of adopting the advice based on the gender of the participants, whether the advisee sees expectations, and whether the advice is to compete against high performers.
+The former considers only the main effect, while the latter also includes the interactive effect.")
 
@@
 <!-- David: Let's turn the regression you discussed below into a column of the Table above --> 
+<!-- Amanda: Can we create a new table for analyzing time 3 data?
+Because the variables are different from the previous table, the current table might be difficult to read with new columns.
+Additionally, the new analysis is only focused on fr advice shown to its target, not all 10,000 advice.
+It might be vonfusing if we put them together.
+-->
 <!-- David: Also, one more suggestion for an analysis: let's look at whether Advisees followed the recommendation they received as an other linear probability model (1/0).
@@
 -->
-
-<!-- Finally, we look at the actual earnings of advisees. Although -->
-<!-- participants in the High Expectation condition earned less, this -->
-<!-- difference is not significant -->
-<!-- (`r model2_apa$estimate['AdviseeConditionHigh']`, -->
-<!-- `r model2_apa$statistic['AdviseeConditionHigh']`). -->
-
-<!-- We found that males are more competitive to the extent that they are -->
-<!-- more likely to choose to compete against High Performer group -->
-<!-- (`r model3_apa$estimate['GenderMale']`, -->
-<!-- `r model3_apa$statistic['GenderMale']`), holding performance the same. -->
 

### 2024-01-15 manuscript/manuscript.Rmd
Study 2 methods & results

--- 2024-01-14 manuscript/manuscript.Rmd
@@
   `r format(Sys.time(), "%e %B, %Y")`
-authornote : |
-  The authors are grateful to a lot of things.
 abstract: |
@@
 draft             : no
-documentclass     : "apa6"
+documentclass     : "apa7"
+csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
 classoption       : "man"
@@
 So far, we have shown that displaying expectations can induce gender
-differences in advice given. Specifically, advisers were more likely to
+differences in advice-giving. Specifically, advisers were more likely to
 recommend competing against a group of High Performers to men who had higher
-expectations about their performance. We now test directly whether this 
+expectations about their performance than did women. We now test directly whether this 
 is driven by interpersonal concerns. Specifically, we examine whether 
@@
 
-We recruited 300 participants and invited them to upload photos of
+We recruited 300 participants from Prolific and invited them to upload photos of
 themselves (selfies) to be rated by other participants on
-attractiveness. We ended up with a sample of
+attractiveness.
 `r scales::comma(dim(study2_time1[study2_time1$gender == 'Male',])[1])`
@@
 `r scales::comma(dim(study2_time1[study2_time1$gender == 'Female',])[1])`
-women who agreed to do so and uploaded usable pictures. We selected the
+women agreed to do so and uploaded pictures that adhered to our
+instructions (e.g., did not include other people). We selected the
 first 100 photos from women to arrive at a gender-balanced sample
-($M_{\text{Age}}$ = `r mean(study2_time1_200$age)` years; 50.0% Female).
-We informed them that their selfies will be randomly grouped into nine
-others from the same gender and ranked by people of the opposite gender
-and asked them to predict their rank, with 1st rank represents the most
-attractive and 10th rank represents the least attractive. We assigned
-each participant to a group of 10 participants of their own gender.
+($M_{\text{Age}}$ = `r mean(study2_time1_200$age)` years).
+Participants were informed that their selfies would be randomly grouped with
+those of nine other participants of their gender and ranked in terms of attractiveness
+by a group of new Prolific participants of the opposite gender.
+They then guessed their rank (unincentivized) and the survey concluded
+with demographic questions **David: or did we start with those?**
 
-Next, we recruited `r scales::comma(dim(study2_time2)[1])`new
-participants and asked them to rank the attractiveness of one such group
-of 10 participants of the opposite gender ($M_{\text{Age}}$ =
+Next, we recruited a new, gender-balanced sample for the role
+of advisers. `r scales::comma(dim(study2_time2)[1])`
+participants from Prolific ($M_{\text{Age}}$ =
 `r mean(study2_time2$age)` years;
-`r round(mean(study2_time2$gender == "Female")*100, 2)`% Female). After
-they did so, we showed them the photo of the participant they ranked as
-the 7th most attractive (that is, the 4th least attractive) and reminded
-them that they had ranked this person at 7th attractive. We (truthfully)
-informed them that this participant would have a chance to earn a bonus
-if they accurately guessed their rank based on the aggregated ratings of
-all participants who had ranked this group. Participants were then
-randomly assigned to an "accuracy" or a "likeability" treatment. In the
-accuracy treatment, they were told that they would receive a bonus (\$1)
-identical to that of the advisee. While in the "likeability" treatment,
-the amount their bonus depended on how the advisee rated them in terms
-of likeability, after observing only the rank that they had advised the
-advisee to guess. Advisees would rate to what extent they think the
-adviser is likable on a 5-point scale, and each point they earn
-increases their bonus by 20 cents.
+`r round(mean(study2_time2$gender == "Female")*100, 2)`% Female) started by
+providing demographic information, then were matched to a group of the opposite
+gender. They then ranked participants from most to least attractive using a
+drop-down menu next to each picture.
+<!-- David: wasn't there something with participants selecting the same rank more -->
+<!-- than once, and we dropped people who did that? Or were we able to solve this -->
+<!-- and it happened only during a pilot? -->
+After submitting their ratings, they saw the photo of the participant they
+had ranked as the 7th most attractive (i.e., the 4th least attractive). They
+were reminded of the rank they had given to that perso and informed
+that this participant would be invited back and could earn a \$1 bonus if they
+guessed their rank correctly. The rank was determined by the aggregate ratings
+of all participants who had ranked this group. Their task was to give advice
+to this participant about the rank they should bet on based on having observed
+all ten selfies and their own assessment. We randomly assigned participants to
+one of two incentivization schemes. In the "Accuracy" treatment, they received
+a bonus identical to the advisee: \$1 if they guessed their rank correctly.
+In the "Likeability" treatment, we informed them that they would be rated by
+the advisee on a 5-point Likert scale for how likeable they thought they were.
+Each point on the scale would translate to a bonus of 20 cents. They then
+selected a rank that they would recommend the advisee to bet on.
 
@@
 1 and informed that a group of 10 selfies, including theirs, had been
-rated by other participants from Prolific. They were also introduced to
-the opportunity to earn a \$1 bonus if they guessed their rank
-accurately. Participants were then shown the advice from a randomly
-selected adviser and made their predictions. After deciding which rank
-to bet on, advisees were reminded of the advice they received and asked
-to rate the advice giver's likability, warmth, friendliness,
-good-naturedness, trustworthiness, and sincerity on a 5-point scale. The
-last 6 items were adopted from @Fiske2007.
+rated by other participants from Prolific. They then saw the advice from a 
+randomly selected adviser and made their estimate with a \$1 incentive for
+guessing accurately. They then saw the rank they had been advised to bet on
+one more time and were asked
+to rate the adviser's likability, warmth, friendliness,
+good-naturedness, trustworthiness, and sincerity on 5-point Likert scales
+(adapted from @Fiske2007).
 
@@
 
-```{r study2advice, fig.cap="Advice for 7th most attractive participants"}
+<!-- David: The treatment differences here are hard to see. The most salient feature -->
+<!-- is the spike at 7th (which suggests no flattering advice), and the spike at 5. -->
+<!-- Can we try a violin plot for the advised rank?  And maybe we can add a -->
+<!-- dotted horizontal line at 7. This is would be consistent with what they said -->
+<!-- just on the previous screen. So a good reference line. -->
+
+```{r study2advice, fig.cap="Advice given to the 7th most attractive participants"}
 library(dplyr)
@@
   scale_y_continuous(name = "% of participants") +
-  scale_x_continuous(name = "Advised Rank") +
+  scale_x_continuous(name = "Advised Rank",
+                     breaks = seq(1, 10)) +
   theme_bw() +
@@
 
-Again, we found supportive evidence that males are more confident about
-themselves, giving higher initial rank prediction (more attractive) than
-female participants
-(`r round(mean(study2_time1[study2_time1$gender == "Male",]$Guess),2)`
-vs.
-`r round(mean(study2_time1[study2_time1$gender == "Female",]$Guess),2)`,
-`r papaja::apa_print(t.test(Guess ~ gender, data = study2_time1, var.equal = T))$statistic`).
+We begin by examining the prior beliefs of advisees who uploaded their selfies.
+On average, men guessed they ranked `r round(mean(study2_time1[study2_time1$gender == "Male",]$Guess),2)` in their group of 10 and women guessed that they ranked
+`r round(mean(study2_time1[study2_time1$gender == "Female",]$Guess),2)`.
+Participants overall underestimate their attractiveness relative to the benchmark
+average of 5.5. Moreover, women do so more than men
+`r papaja::apa_print(t.test(Guess ~ gender, data = study2_time1, var.equal = T))$statistic`.
+Notably, people's self-perceptions correlated strongly/weakly with the aggregate
+ratings of the advisers (correlation coefficient & cor.test). However, there
+was substantial heterogeneity in perceptions of attractiveness.
+Of the 200 participants, XXX were ranked as 7th most attractive by at least one
+adviser. On average,
+men in this subset estimated they were ranked Xth and women estimated they were
+ranked Xth (t-test).
 
-Examining advice from Stage 2 participants, we found that participants
-advised a lower rank (that is, more attractive) in the likeability
-treatment than the accuracy treatment
-(`r round(mean(study2_time2[study2_time2$Condition == "Likable",]$Advice),2)`
-vs
-`r round(mean(study2_time2[study2_time2$Condition == "Accurate",]$Advice),2)`,
+<!-- David: Some stats to fill in above. I think this would be interesting to include -->
+<!-- even though we don't make any predictions about this. -->
+
+Next, we turn our attention to the advisers (Figure \@ref(fig:study2advice)). 
+In the Accuracy condition, those
+uploading selfies were advised to bet on rank `r round(mean(study2_time2[study2_time2$Condition == "Accurate",]$Advice),2)`.
+Notably, this is significantly more attractive than the 7th rank those advisers
+had themselves guessed just on the prior screen
+(`r papaja::apa_print(t.test(study2_time2[study2_time2$Condition == "Accurate",]$Advice, mu = 7, var.equal = T))$statistic`).
+This suggests that even when incentivized for accuracy, participants offered
+flattering advice.^[This shading could be due to concerns of avoiding disappointment.
+However, it could also be that advisers are uncertain about the rankings they had given and make a recommendation that combines their own belief with a uniform prior.]
+Importantly, and as predicted, we find that advisers in the Likeable treatment
+recommend betting on a lower rank, communicating that they think the participant
+in the selfie is more attractive
+(`r round(mean(study2_time2[study2_time2$Condition == "Likable",]$Advice),2)`,
 `r papaja::apa_print(t.test(Advice ~ Condition, data = study2_time2, var.equal = T))$statistic`).
-As seen in Figure \@ref(fig:study2advice), notably, however, even in the
-accuracy treatment, participants advised a lower rank than they
-themselves had provided
-(`r papaja::apa_print(t.test(study2_time2[study2_time2$Condition == "Accurate",]$Advice, mu = 7, var.equal = T))$statistic`).
 This suggests that advisers inferred that advising someone that they
@@
 therefore provided advice that communicated a more favorable impression
-of the participants' attractiveness.
+of the participants' attractiveness. The distribution shown in Figure \@ref(fig:study2advice)
+shows that participants do not simply tell participants that they are the
+most attractive person in the group. They may infer that flattering advise needs
+to be somewhat realistic to be believable. We return to this in the general discussion.
+
+<!-- David: Making a note here that we should be sure to discuss this at the end -->
+<!-- as something for future research. -->
 
@@
 
-To test whether flattering advice brings more positive evaluation of
-advisers, we create a single index for warmth and trustworthiness by
-taking average of ratings on warmth, friendliness, good-naturedness,
-trustworthiness for the former and ratings on trustworthiness, and
-sincerity for the later. As seen in Figure \@ref(fig:study2rating), we
+Finally, we examine whether flattering advice indeed leads to more positive evaluations of
+advisers, or whether flattering advice is dismissed as insencere.
+Following our preregistration, we average the ratings on likeability,
+warmth,  friendliness, and good-naturedness to create a scale of likeability
+($\alpha$ = XXX);
+<!-- David: The draft had trustworthiness as part of this scale. -->
+<!-- Can we just double-check against the preregistration? -->
+<!-- And was Likeable part of that? -->
+<!-- We might also want a name for the scale that isn't the same as one -->
+<!-- of the items, though I'm not sure what. -->
+<!-- Same for trustworthiness -- though that could simply be "Trust" -->
+and we create a scale of trustworthiness by averaging the ratings of
+trustworthiness and sincerity ($\alpha$ = XXX).
+
+<!-- The Figure is not super clear. How about we try a series of box plots, -->
+<!-- with the x-axis as the advised rank? Standard errors will be huge at the -->
+<!-- extremes. -->
+
+<!-- Also, we need to do something relative to the advisees' expectations. -->
+<!-- I wonder what would be interesting here? Maybe averages for three groups: -->
+<!-- more attractive than the participants' own guess, equally attractive, and less -->
+<!-- attractive? -->
+
+As seen in Figure \@ref(fig:study2rating), we
 found that advisees who suggested that the advisee was more attractive
 (lower rank) were indeed rated as more likeable and warm (b = -0.109, p
-\< .05; b = -0.133, p \< .001; See Columns 1 and 2 of Table 2).
+\< .05; b = -0.133, p \< .001, respectively; See Columns 1 and 2 of Table \@ref(tab:study2regs)).
 Interestingly, these benefits are not at the cost of being hypocritical;
-advisers are also seen as more trustworthy, but the result is only
-directional (Column 3 of Table 2). Notably, however, we were not powered
-to do a comparison across the two experimental groups.
+advisers who recommend a more favorable rank are viewed as no less trustworthy
+(Column 3 of Table \@ref(tab:study2regs)).
 
-# Discussion
+We were not powered to do a comparison across the two 
+experimental groups and did not preregister such a difference.
+<!-- David: But we still need to report warmth & trust across treatments. -->
 
-dvice substantially shapes people's career and personal outcomes.
+## Discussion
+
+# General Discussion
+
+Advice substantially shapes people's career and personal outcomes.
 Therefore, understanding advisers' motivations has far-reaching
@@
 relevant to societies that value signaling in interpersonal
-relationships, including Hong Kong and many Asian countries. Future work
+relationships. Future work
 could also examine whether people in different cultures place more

### 2024-01-15 manuscript/manuscript.Rmd
Study 2 discussion

@@
 
+<!-- David: We should also report something on accuracy of the advice given across -->
+<!-- the treatments. Even if no difference. -->
+
 ```{r study2regs}
@@
 ## Discussion
+In a context where advice communicates ego-relevant information (here, people's
+attractiveness), we find that the advice people give is contingent on their
+incentives. Specifically, when they get rewarded for being more likeable, they
+recommend that the advisee bet on a more favorable rank than when they are
+incentivized for accuracy. Importantly, advisees do not discount flattering
+advice and instead evaluate people who advise them to bet on a more attractive
+rank as warmer and more likeable. These gains to interpersonal perceptions do
+not come at the cost of trustworthiness, even when the advice is substantially
+inflated (e.g., a recommendation that the advisee is the most attractive in the group).
 
 # General Discussion
-
 Advice substantially shapes people's career and personal outcomes.

### 2024-01-15 manuscript/manuscript.Rmd
General discussion

@@
 # General Discussion
-Advice substantially shapes people's career and personal outcomes.
-Therefore, understanding advisers' motivations has far-reaching
-implications. We propose that advisers' focus on advisees' expectations
-and the desire to avoid disappointing them can induce gender differences
-in the advice given and ultimately in the outcomes achieved. Gender
-differences in career outcomes contribute significantly to the gender
-wage gap, with women often holding less senior positions and
-experiencing worse career outcomes, even with equal performance.
-Therefore, identifying a factor such as expectations that contributes to
-this gap has important implications for organizational practice.
+Advice has the potential to shape people's career and personal outcomes.
+Honest feedback, however, may be painful to learn if it falls short of one's
+expectations. As prior work notes, this may motivate people to avoid information 
+and avoid seeking help [@Benabou2022; @Golman2017; @Jaroszewicz2022].
+We present evidence from two experiments that advisers are also cognizant of this
+cost. As a result, they present flattering advice that avoids disappointing the
+recipient, and correctly anticipate that this boosts how advisees perceive them.
 
-In this paper, we examine a novel and unexplored factor of
-advice-giving: interpersonal considerations. Advisers who take into
-account the advisee's belief utility inflate their advice to convey a
-more favorable impression, leading to worse decisions and gender
-differences. Men have more inflated expectations than women, and taking
-expectations into account can lead to gender differences, even without
-discrimination. We ruled out discrimination as a separate channel by
-withholding information about the gender of the advisee. Finally, we
-expect that advisers are aware of the tradeoff between giving accurate
-advice and avoiding disappointment and, thus, are less likely to inflate
-their advice when advisees can compensate them after observing the
-outcome of their choice.
+However, this flattering advice comes at a cost to advisees, who would do worse
+if they followed it blindly, as we show in Study 1.
+<!-- David: But not Study 2? I guess we're not sure yet? -->
+Moreover, a desire to avoid disappointment also means that advisers have to
+take into account the expectations of the advisee. 
+We document that men are more optimistic about their performance than
+women are. As a result, they receive more flattering advice and are more likely
+to be told to aim higher. Notably, in the context of our experiment, this turns
+out to be bad advice ex post.
 
-The findings of this study suggest that organizations can promote gender
-equity by calibrating employees' expectations or shifting advisers'
-attention away from them. While these measures may not entirely solve
-the gender gap problem, they can make a meaningful difference when
-unconscious bias interventions have failed to show any effect
-[@Chang2019; @Paluck2009]. We believe our findings may be particularly
-relevant to societies that value signaling in interpersonal
-relationships. Future work
-could also examine whether people in different cultures place more
-weight on expectations.
+Our findings have implications for organizational practice, where mentoring
+and advice-giving may take into account an employees' expectation. We
+document this as a novel source of gender bias. Organizations could reduce
+this bias by calibrating employees' expectations to reduce overconfidence.
+
+Participants in our experiment were paired anonymously. Even so, we document
+this desire to avoid disappointment. We anticipate that advice would be more
+flattering in face-to-face communication and without anonymity. Moreover,
+existing relationships might make it even more difficult for advisers to be
+honest.
+
+In our experiments, participants only received advice once and did not evaluate
+the adviser after observing the outcome of their decision.
+For example, advice that leads to bad outcomes may undermine the
+interpersonal benefits of flattery. Alternatively, people may still like the
+flattering advice and not fault the adviser for the bad outcome.
+Moreover, our setting involved only a single piece of advice on one task.
+Future research could examine whether people return to those who gave them
+flattering advice, or if they prefer someone who gave them the honest
+(but unpleasant) truth.
+
+Advice has long been studied from the perspective of the receiver. Similarly,
+research on belief utility has examined how recipients respond to the valence
+of the information they receive. Here, we show that advisers, too, take into
+account the psychological impact of the information they convey. They may have
+even greater motivations to avoid conveying bad news, because they incur the
+interpersonal costs of delivering unfavorable information without reaping the
+benefits from helping someone make a better choice.
 

### 2024-01-16 manuscript/manuscript.Rmd
Revised on Jan 16 by Amanda

@@
 library(magrittr)
+library(ltm)
 
@@
 
-```{r}
-library("papaja")
-# Fit linear regression model
-study1_advice <- study1_advice %>% dplyr::mutate(ExpShow = ifelse(Condition == 'E',1,0))
-
-model1 <- lm(Guess ~ Gender + count, data = study1_time1)
-model1_apa <- apa_print(model1)
-```
-
 ## Results
@@
 ```{r study1regs}
-study1_advice <- study1_advice %>% dplyr::mutate(Treatment = factor(Treatment, levels = c('Low', 'High')))
+study1_advice <- study1_advice %>% dplyr::mutate(Treatment = factor(Treatment, levels = c('Low', 'High'))) %>%
+  dplyr::mutate(ExpShow = ifelse(Condition == 'E',1,0))
 
@@
               method = "glm", method.args = list(family = "binomial"), color = "grey", se = FALSE) +
-  scale_color_manual(values = c("red", "#4169E1", "grey"),
+  scale_color_manual(values = c("#E74C3C", "#4169E1", "grey"),
                      labels = c("Female + Expectations", "Male + Expectations", "Expectation Hidden")) +
@@
 
-modelsummary::modelsummary(list(`(1)` = lm(bonus ~ AdviseeCondition + AdviseeScore , data = study1_time3),
-                                `(2)` = lm(Bet ~ Gender + AdviseeScore , data = study1_time3),
+modelsummary::modelsummary(list(`(1)` = lm(bonus ~ AdviseeCondition + AdviseeScore, data = study1_time3 %>%
+                                             dplyr::filter(GiverCondition == 1)),
+                                `(2)` = lm(bonus ~ Gender + AdviseeScore, data = study1_time3 %>%
+                                             dplyr::filter(GiverCondition == 1)),
                                 `(3)` = lm(Adopt ~ Gender + GiverCondition + Advice, data = study1_time3),
@@
                            caption = "Column 1 displays the actual bonus based on the performance and whether the participant is primed with high expectations.
-Column 2 displays whether the participant chooses to compete against a high-performance group based on performance and gender of the participants.
+Column 2 displays the actual bonus based on the performance and gender of the participant.
 Columns 3 and 4 display the chance of adopting the advice based on the gender of the participants, whether the advisee sees expectations, and whether the advice is to compete against high performers.
@@
 advice, recognizing it as such and thus failing to adhere to it.
+Align with our prediction, participants who were primed with high expectations earned less when their expectations were conveyed to the advisers, although this result is only directional  (see Column 1 of Table \@ref(tab:study1time3)).
+Similarly, as shown in Column 2 of Table \@ref(tab:study1time3), Similarly, as shown in Column 2 of Table 1, we also found that male participants received less reward when their expectations were presented, even when their performance was the same.
+These findings suggest that flattering advice is not without consequences.
+Furthermore, our research indicates that because males are more likely to follow such advice (see Column 4 of Table \@ref(tab:study1time3), their tendency towards competition intensifies the cost of such advice.
 
 <!-- David: Let's turn the regression you discussed below into a column of the Table above --> 
-<!-- Amanda: Can we create a new table for analyzing time 3 data?
-Because the variables are different from the previous table, the current table might be difficult to read with new columns.
-Additionally, the new analysis is only focused on fr advice shown to its target, not all 10,000 advice.
-It might be vonfusing if we put them together.
--->
 <!-- David: Also, one more suggestion for an analysis: let's look at whether Advisees followed the recommendation they received as an other linear probability model (1/0).
@@
 We may not end up reporting this, but I would be curious to see.
+-->
+
+<!-- Amanda: Can we create a new table for analyzing time 3 data?
+Because the variables are different from the previous table, the current table might be difficult to read with new columns.
+Additionally, the new analysis is only focused on fr advice shown to its target, not all 10,000 advice.
+It might be confusing if we put them together.
 -->
@@
 got worse advice as a result.
+<!-- Amanda: Our findings suggest that males earned less than their female counterparts who scored the same as them, although the evidence is only directional.
+This could be attributed to the fact that males received more flattering advice and were more likely to adopt it, resulting in even worse outcomes.-->
 
@@
 study2_time2 <- readRDS(here::here("Data/Study2_time2.Rds"))
+study2_finalRank <- readRDS(here::here("Data/Study2_finalRank.Rds"))
 study2_time3 <- readRDS(here::here("Data/Study2_time3.Rds"))
@@
 
-We recruited 300 participants from Prolific and invited them to upload photos of
+We recruited 300 participants from Prolific and, after asking demographic questions, invited them to upload photos of
 themselves (selfies) to be rated by other participants on
@@
 by a group of new Prolific participants of the opposite gender.
-They then guessed their rank (unincentivized) and the survey concluded
-with demographic questions **David: or did we start with those?**
+Lastly, they guessed their rank (unincentivized). **David: or did we start with those?**
+<!-- Amanda: We started with demographic questions -->
 
@@
 gender. They then ranked participants from most to least attractive using a
-drop-down menu next to each picture.
+drop-down menu next to each picture. <!-- Amanda: We excluded data from participants who assigned the same rank to multiple selfies.-->
 <!-- David: wasn't there something with participants selecting the same rank more -->
@@
 <!-- and it happened only during a pilot? -->
+<!-- Amanda: We did not catch this error in pilot, so we decided to use this as a manipulation check -->
 After submitting their ratings, they saw the photo of the participant they
@@
 
-<!-- David: The treatment differences here are hard to see. The most salient feature -->
-<!-- is the spike at 7th (which suggests no flattering advice), and the spike at 5. -->
-<!-- Can we try a violin plot for the advised rank?  And maybe we can add a -->
-<!-- dotted horizontal line at 7. This is would be consistent with what they said -->
-<!-- just on the previous screen. So a good reference line. -->
+```{r}
+library(dplyr)
+
+TargetsUnique <- study2_time2 %>%
+  dplyr::select(Target) %>%
+  unique()
+
+TargetsUnique <- merge(TargetsUnique,study2_finalRank, by.x = 'Target', by.y = 'QID7_Id')
+
+```
 
 ```{r study2advice, fig.cap="Advice given to the 7th most attractive participants"}
-library(dplyr)
-library(ggplot2)
 
-count <- study2_time2 %>%
-  group_by(Condition) %>%
-  summarize(number = dplyr::n())
+study2_time2 <- study2_time2 %>% dplyr::mutate(Advice = as.numeric(Advice))
 
-advice_avg <- study2_time2 %>%
-  group_by(Condition, Advice) %>%
-  summarize(n = dplyr::n()) %>%
-  dplyr::mutate(conditionCount = ifelse(Condition == 'Likable',count[count$Condition == 'Likable',]$number,count[count$Condition == 'Accurate',]$number)) %>%
-  dplyr::mutate(percent = n/conditionCount*100) %>% 
-  dplyr::select(Condition,Advice,percent)
-
-# Create a facet plot with condition as the facet variable and gender as the line color
-ggplot(advice_avg, aes(x = Advice, y = percent, color = Condition)) +
-  geom_line(linewidth = 0.75)+
-  scale_color_manual(values = c("#FFA500", "#4169E1"),
-                      labels = c("Accurate", "Likable")) +
-  scale_y_continuous(name = "% of participants") +
-  scale_x_continuous(name = "Advised Rank",
-                     breaks = seq(1, 10)) +
+ggplot(study2_time2, aes(x = Condition, y = Advice, fill = Condition)) +
+    geom_violin(trim = FALSE) +
+     scale_fill_manual(values = c("#E74C3C", "#4169E1"), labels = c("Accurate", "Likable")) +
+  geom_hline(yintercept = 7, col = 'grey', linetype = 'dashed', linewidth = 0.7) +
+  scale_y_continuous(name = "Advised Rank", breaks = seq(1, 10)) +
   theme_bw() +
@@
 `r papaja::apa_print(t.test(Guess ~ gender, data = study2_time1, var.equal = T))$statistic`.
-Notably, people's self-perceptions correlated strongly/weakly with the aggregate
-ratings of the advisers (correlation coefficient & cor.test). However, there
+Notably, people's self-perceptions correlated strongly with the aggregate
+ratings of the advisers (`r round(cor(study2_finalRank$Guess, study2_finalRank$finalRank),2)`, `r papaja::apa_print(cor.test(study2_finalRank$Guess, study2_finalRank$finalRank))$statistic`).
+However, there
 was substantial heterogeneity in perceptions of attractiveness.
-Of the 200 participants, XXX were ranked as 7th most attractive by at least one
-adviser. On average,
-men in this subset estimated they were ranked Xth and women estimated they were
-ranked Xth (t-test).
-
-<!-- David: Some stats to fill in above. I think this would be interesting to include -->
-<!-- even though we don't make any predictions about this. -->
+Of the 200 participants, `r length(unique(study2_time2$Target))` were ranked as 7th most attractive by at least one adviser. 
+On average, men in this subset estimated they were ranked `r round(mean(TargetsUnique[TargetsUnique$gender == 'Male',]$Guess),2)`th and women estimated they were
+ranked `r `round(mean(TargetsUnique[TargetsUnique$gender == 'Female',]$Guess),2)`th (`r papaja::apa_print(t.test(Guess ~ gender, data = TargetsUnique, var.equal = T))$statistic`).
 
@@
 
-```{r study2rating, fig.cap="The evaluation of advice givers"}
+<!-- Amanda: How about this -->
+```{r study2Rating, fig.cap="The evaluation of advice givers"}
+# Load the necessary packages
+library(ggplot2)
+library(gridExtra)
+library(dplyr)
 
-rating <- study2_time3 %>%
-  group_by(Advice) %>%
-  summarise(Likable = mean(likable), Warm = mean(warmAvg), Trust = mean(trustAvg))
+study2_time3 <- study2_time3 %>% dplyr::mutate(Advice = as.factor(Advice))
 
-ggplot(rating, aes(x = Advice)) +
-  geom_line(aes(y = Likable, color = "Likable"), linewidth = 0.75) +
-  geom_line(aes(y = Warm, color = "Warm"), linewidth = 0.75) +
-  geom_line(aes(y = Trust, color = "Trust"), linewidth = 0.75) +
-  scale_color_manual(values = c("Likable" = "#FFA500", "Warm" = "#4169E1", "Trust" = "grey"),
-                      labels = c("Likable", "Warm", "Trust")) +
-  scale_y_continuous(name = "Rating") +
-  scale_x_continuous(name = "Advised Rank") +
+# Create the first plot
+plot1 <- ggplot(study2_time3, aes(x = Advice)) +
+  geom_boxplot(aes(y = likable),position = position_dodge()) +
+  scale_y_continuous(name = "Rating on Likability") +
+  scale_x_discrete(name = "Advised Rank") +
   theme_bw() +
@@
 
+# Create the second plot
+plot2 <- ggplot(study2_time3, aes(x = Advice)) +
+  geom_boxplot(aes(y = warmAvg),position = position_dodge()) +
+  scale_y_continuous(name = "Rating on Warmth") +
+  scale_x_discrete(name = "Advised Rank") +
+  theme_bw() +
+  theme(panel.grid = element_blank(),
+        panel.border = element_blank(),
+        axis.line = element_line(colour = "grey"),
+        legend.position = "bottom",
+        legend.title = element_blank(),
+        legend.key.size = unit(1.2, "lines"),          
+        legend.text = element_text(size = 12),
+        plot.title = element_text(hjust = 0.5, size = 20))
+
+# Combine the plots side by side
+grid.arrange(plot1, plot2, ncol = 2)
+
 ```
@@
 warmth,  friendliness, and good-naturedness to create a scale of likeability
-($\alpha$ = XXX);
+($\alpha$ = `r cronbach.alpha(study2_time3[, 5:8])$alpha`);
 <!-- David: The draft had trustworthiness as part of this scale. -->
@@
 <!-- Same for trustworthiness -- though that could simply be "Trust" -->
+
+<!-- Amanda: My bad. We only pre-reg that we will measure likable (single item) and warm (four items)" -->
+<!-- I include trustworthiness here because it is part of that existing scale" -->
+
 and we create a scale of trustworthiness by averaging the ratings of
-trustworthiness and sincerity ($\alpha$ = XXX).
+trustworthiness and sincerity ($\alpha$ = `r cronbach.alpha(study2_time3[, 9:10])$alpha`).
 
@@
 
-As seen in Figure \@ref(fig:study2rating), we
+<!-- Amanda: How about the following picture? -->
+
+```{r study2ratingByGroup, fig.cap="The Response to Different Advice"}
+
+library(dplyr)
+library(ggplot2)
+
+study2_time3 <- study2_time3 %>% dplyr::mutate(Guess = as.numeric(Guess), Advice = as.numeric(Advice)) %>%
+  dplyr::mutate(HorL = ifelse(Guess == Advice,0, ifelse(Guess > Advice, 1,-1))) %>%
+  dplyr::mutate(HorL = as.factor(HorL)) %>% 
+  dplyr::mutate(bonus = ifelse(bet == `Final Rank`,1,0))
+
+ratings <- study2_time3 %>%
+  group_by(HorL) %>%
+  summarise(like = mean(likable), warmth = mean(warmAvg))
+
+rating_table <- matrix(c(ratings$like,ratings$warmth), nrow = 2, byrow = TRUE, dimnames = list( c("Likable",'Warm'),c("Pessimistic", "Accurate", "Flattering")))
+
+rating_df = as.data.frame.table(rating_table) %>%
+  dplyr::rename( 'Condition'='Var1', 'Advice' ='Var2') %>%
+  dplyr::mutate(Freq = round(Freq,2))
+
+ggplot(rating_df, aes(x = Advice, y = Freq, fill = Condition)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  scale_fill_manual(values = c("#E74C3C",'#4169E1')) +
+  labs(x = "Advice", y = "Rating") +
+  ggtitle('Response to Advice') +
+  theme_bw() +
+  theme(panel.grid = element_blank(),
+        panel.border = element_blank(),
+        axis.line = element_line(colour = "grey"),
+        legend.position = "bottom",
+        legend.title = element_blank(),
+        legend.key.size = unit(1.2, "lines"),          
+        legend.text = element_text(size = 12),
+        plot.title = element_text(hjust = 0.5, size = 20)) +
+  geom_text(aes(label = paste0(Freq), y = 0.5), position = position_dodge(width = 0.9), size = 2, color = 'white')
+
+```
+
+As seen in Figure \@ref(fig:study2Rating), we
 found that advisees who suggested that the advisee was more attractive
@@
 experimental groups and did not preregister such a difference.
+Indeed, we observed that advisers in the Accurate condition received higher ratings in both likable and warm dimensions (`r papaja::apa_print(t.test(likable ~ Condition, data = study2_time3, var.equal = T))$statistic`, and `r papaja::apa_print(t.test(warmAvg ~ Condition, data = study2_time3, var.equal = T))$statistic`, respectively).
+While the difference is not statistically significant, the results suggest that there may be an optimal range for the level of inflation.
 <!-- David: But we still need to report warmth & trust across treatments. -->
@@
 if they followed it blindly, as we show in Study 1.
+
 <!-- David: But not Study 2? I guess we're not sure yet? -->
+
+<!-- Amanda: among 146 participants in time 3, only 25 guessed correctly. not enough variation-->
+<!-- Nonetheless, participants received advice from accurate condition earned less (0.15 vs 0.2) -->
+
 Moreover, a desire to avoid disappointment also means that advisers have to

### 2024-01-16 R/clean_study2_time2.R

@@ -13,6 +13,11 @@ giver <- data.table::fread(here::here("Data/Raw Data/S2_time2.csv"),
   dplyr::mutate(value = gsub("st|nd|rd|th| rank| \\(most attractive\\)| \\(least attractive\\)", "", value),
                 value = as.numeric(value))
 
+duplicates <- apply(giver[,3:12], 1, function(x) any(duplicated(x)))
+
+giver <- giver %>% dplyr::mutate(duplicates = duplicates) %>%
+  dplyr::filter(duplicates == 'FALSE')
+
 # clean the url
 url <-  giver %>% dplyr::select(ResponseId,dplyr::starts_with("url."))
 
@@ -51,36 +56,36 @@ for(i in 1:nrow(giver)){
 giverStat <- giver %>% dplyr::filter(!is.na(Target)) %>% dplyr::rename('Advice' = 'value')
 
 
+# We then randomly select one piece of advice for each participant who upload selfies
+#advice <- giverStat %>% dplyr::group_by(Target) %>% dplyr::slice_sample(n=1)  %>%
+#  dplyr::select(Target,Advice,PROLIFIC_PID)%>% dplyr::rename('QID7_Id'='Target') %>% dplyr::rename('Giver_Id'='PROLIFIC_PID')
+
+giverStat <- giverStat %>% dplyr::mutate(age = as.numeric(age))
+
+saveRDS(giverStat, file = here::here("Data/Study2_time2.Rds"))
+giverStat %>% write.csv("Data/Cleaned Data/S2_time2_clean.csv")
+
+
 #calculate final ranking for each selfie
-selfie <- data.table::fread(here::here("Data/Raw Data/S2_time1.csv"),
-                            header = T,na.strings = '')[-c(1,2)]  %>%
-  dplyr::filter(Progress == '100',gender != 'Other',!is.na(QID7_Id)) %>%
-  dplyr::select(ResponseId, PROLIFIC_PID,QID7_Id)
+selfie <- readRDS(here::here("Data/Study2_time1_200.Rds"))
 
-selfies <- as.data.frame(unique(giverStat$Target))
+selfies <- as.data.frame(unique(selfie$QID7_Id))
 selfies[,c('scores','raterNr')] <- 0
-
 
 for(i in 1:nrow(giver)){
   rankList = as.list(giverRank[i,])
   urlList = as.list(url[i,])
   for (j in 1:10){
[…]

### 2024-01-17 manuscript/manuscript.Rmd
Minor edits

@@
 to reproduce all statistical analyses and figures in the manuscript, as
-well as the preregistration reports are available via OSF. All our
-studies were preregistered on AsPredicted.org.^[<https://osf.io/8r3d4/?view_only=5ad7bafcd16b4d4ba08bb28b0e2bd02d>]
+well as the preregistration reports will be available via OSF. All our
+studies were preregistered on AsPredicted.org.
+
+<!-- ^[<https://osf.io/8r3d4/?view_only=5ad7bafcd16b4d4ba08bb28b0e2bd02d>] -->
+<!-- Commenting this out for IACM -->
 
@@
 
-# David: No need to redefine a factor variable as a continuous number. Easier to just change the reference level.
-
 modelsummary::modelsummary(list(`(1)` = lm(Advice ~ Treatment + Performance , data = study1_advice %>% dplyr::filter(ExpShow == 1)),
@@
 We show this result graphically in Figure \@ref(fig:study1genderdiff)).
+
 <!-- Amanda: The gender discrepancy in advice is more significant when performance is less decisive.
@@
 -->
+
+<!-- David: If we plotted on the x-axis performance and on the y-axis the difference -->
+<!-- between recommendations for men & women, this would look inverse-U shaped, right? -->
+<!-- Might be a nice way to illustrate what you describe. -->
 
@@
 -->
+
+<!-- Yes, new table is fine. -->
 
@@
 by a group of new Prolific participants of the opposite gender.
-Lastly, they guessed their rank (unincentivized). **David: or did we start with those?**
-<!-- Amanda: We started with demographic questions -->
+Lastly, they guessed their rank (unincentivized).
 
@@
 gender. They then ranked participants from most to least attractive using a
-drop-down menu next to each picture. <!-- Amanda: We excluded data from participants who assigned the same rank to multiple selfies.-->
-<!-- David: wasn't there something with participants selecting the same rank more -->
-<!-- than once, and we dropped people who did that? Or were we able to solve this -->
-<!-- and it happened only during a pilot? -->
-<!-- Amanda: We did not catch this error in pilot, so we decided to use this as a manipulation check -->
+drop-down menu next to each picture. Because of a limitation with the survey software,
+participants were able to select the same rank for multiple participants, rather
+than rank them uniquely. We remove XX participants who did not follow instructions
+and provide a unique ranking.
+
+<!-- David: Note the number above to fill in. -->
+
 After submitting their ratings, they saw the photo of the participant they
@@
 <!-- Amanda: How about this -->
-```{r study2Rating, fig.cap="The evaluation of advice givers"}
+<!-- For warmth it looks interesting, but I think the plot is hard -->
+<!-- to read. Let's hold off on this for now. -->
+
+```{r study2Rating, fig.cap="The evaluation of advice givers", eval = F}
 # Load the necessary packages
@@
 We were not powered to do a comparison across the two 
-experimental groups and did not preregister such a difference.
-Indeed, we observed that advisers in the Accurate condition received higher ratings in both likable and warm dimensions (`r papaja::apa_print(t.test(likable ~ Condition, data = study2_time3, var.equal = T))$statistic`, and `r papaja::apa_print(t.test(warmAvg ~ Condition, data = study2_time3, var.equal = T))$statistic`, respectively).
-While the difference is not statistically significant, the results suggest that there may be an optimal range for the level of inflation.
-<!-- David: But we still need to report warmth & trust across treatments. -->
+experimental groups and did not preregister such a difference. Indeed, we find
+no difference in likeability and warmth across the two treatments 
+(`r papaja::apa_print(t.test(likable ~ Condition, data = study2_time3, var.equal = T))$statistic`, 
+and `r papaja::apa_print(t.test(warmAvg ~ Condition, data = study2_time3, var.equal = T))$statistic`, 
+respectively).
 
@@
 recipient, and correctly anticipate that this boosts how advisees perceive them.
-
 However, this flattering advice comes at a cost to advisees, who would do worse
 if they followed it blindly, as we show in Study 1.
-
-<!-- David: But not Study 2? I guess we're not sure yet? -->
-
-<!-- Amanda: among 146 participants in time 3, only 25 guessed correctly. not enough variation-->
-<!-- Nonetheless, participants received advice from accurate condition earned less (0.15 vs 0.2) -->
 

### 2024-01-18 manuscript/manuscript.Rmd
IACM submission

@@
               method = "glm", method.args = list(family = "binomial"), color = "grey", se = FALSE) +
-  scale_color_manual(values = c("#E74C3C", "#4169E1", "grey"),
+  scale_color_manual(values = c("firebrick3",'dodgerblue3', "grey"),
                      labels = c("Female + Expectations", "Male + Expectations", "Expectation Hidden")) +
@@
 <!-- Might be a nice way to illustrate what you describe. -->
+
+<!-- Amanda: I think our primary purpose here is still showing the existence of gender difference -->
+<!-- The current plot shows discrepancy between two lines, allowing us to demonstrate gender gap -->
 
@@
 Align with our prediction, participants who were primed with high expectations earned less when their expectations were conveyed to the advisers, although this result is only directional  (see Column 1 of Table \@ref(tab:study1time3)).
-Similarly, as shown in Column 2 of Table \@ref(tab:study1time3), Similarly, as shown in Column 2 of Table 1, we also found that male participants received less reward when their expectations were presented, even when their performance was the same.
+Similarly, as shown in Column 2 of Table \@ref(tab:study1time3), we also found that male participants received less reward when their expectations were presented, even when their performance was the same.
 These findings suggest that flattering advice is not without consequences.
 Furthermore, our research indicates that because males are more likely to follow such advice (see Column 4 of Table \@ref(tab:study1time3), their tendency towards competition intensifies the cost of such advice.
-
-<!-- David: Let's turn the regression you discussed below into a column of the Table above --> 
-<!-- David: Also, one more suggestion for an analysis: let's look at whether Advisees followed the recommendation they received as an other linear probability model (1/0).
-I would suggest predictors of whether it's the High Performer group, whether the adviser saw expectations, the gender of the advisee.
-Also, another model that has the two-way interaction for all of those.
-We may not end up reporting this, but I would be curious to see.
--->
-
-<!-- Amanda: Can we create a new table for analyzing time 3 data?
-Because the variables are different from the previous table, the current table might be difficult to read with new columns.
-Additionally, the new analysis is only focused on fr advice shown to its target, not all 10,000 advice.
-It might be confusing if we put them together.
--->
-
-<!-- Yes, new table is fine. -->
 
@@
 got worse advice as a result.
-<!-- Amanda: Our findings suggest that males earned less than their female counterparts who scored the same as them, although the evidence is only directional.
-This could be attributed to the fact that males received more flattering advice and were more likely to adopt it, resulting in even worse outcomes.-->
+Our findings suggest that males with the same scores as their female counterparts earned less, although the evidence is only directional.
+This may be due to males receiving more favorable advice and being more likely to adopt it, resulting in even worse outcomes.
 
@@
 participants were able to select the same rank for multiple participants, rather
-than rank them uniquely. We remove XX participants who did not follow instructions
+than rank them uniquely. We remove 115 participants who did not follow instructions
 and provide a unique ranking.
-
-<!-- David: Note the number above to fill in. -->
 
@@
 
-```{r study2advice, fig.cap="Advice given to the 7th most attractive participants"}
+```{r study2advice, fig.cap="Advisers were asked to suggest what rank to bet on for someone they ranked as the 7th most attractive out of ten people.
+When incentivized for accuracy, most of them advised betting on 7, which was based on their evaluation of the recipient's attractiveness.
+However, when incentivized for likability, many participants gave flattering advice by suggesting betting on higher ranks that imply a higher evaluation of attractiveness."}
 
@@
     geom_violin(trim = FALSE) +
-     scale_fill_manual(values = c("#E74C3C", "#4169E1"), labels = c("Accurate", "Likable")) +
+     scale_fill_manual(values = c("firebrick3",'dodgerblue3'), labels = c("Accurate", "Likable")) +
   geom_hline(yintercept = 7, col = 'grey', linetype = 'dashed', linewidth = 0.7) +
@@
 On average, men in this subset estimated they were ranked `r round(mean(TargetsUnique[TargetsUnique$gender == 'Male',]$Guess),2)`th and women estimated they were
-ranked `r `round(mean(TargetsUnique[TargetsUnique$gender == 'Female',]$Guess),2)`th (`r papaja::apa_print(t.test(Guess ~ gender, data = TargetsUnique, var.equal = T))$statistic`).
+ranked `r round(mean(TargetsUnique[TargetsUnique$gender == 'Female',]$Guess),2)`th (`r papaja::apa_print(t.test(Guess ~ gender, data = TargetsUnique, var.equal = T))$statistic`).
 
@@
 
-```{r study2Rating, fig.cap="The evaluation of advice givers", eval = F}
-# Load the necessary packages
+Finally, we examine whether flattering advice indeed leads to more positive evaluations of
+advisers, or whether flattering advice is dismissed as insencere.
+Following our preregistration, we average the ratings on likeability,
+warmth,  friendliness, and good-naturedness to create a scale of likeability
+($\alpha$ = `r cronbach.alpha(study2_time3[, 5:8])$alpha`); and we create a scale of trustworthiness by averaging the ratings of trustworthiness and sincerity ($\alpha$ = `r cronbach.alpha(study2_time3[, 9:10])$alpha`).
+
+<!-- The Figure is not super clear. How about we try a series of box plots, -->
+<!-- with the x-axis as the advised rank? Standard errors will be huge at the -->
+<!-- extremes. -->
+
+<!-- Also, we need to do something relative to the advisees' expectations. -->
+<!-- I wonder what would be interesting here? Maybe averages for three groups: -->
+<!-- more attractive than the participants' own guess, equally attractive, and less -->
+<!-- attractive? -->
+
+<!-- Amanda: How about the following picture? -->
+```{r study2rating, fig.cap="Participants tend to rate advisors who suggest betting on a higher rank (implying greater attractiveness) as more likable and warm."}
+
 library(ggplot2)
@@
 plot1 <- ggplot(study2_time3, aes(x = Advice)) +
-  geom_boxplot(aes(y = likable),position = position_dodge()) +
-  scale_y_continuous(name = "Rating on Likability") +
+  geom_boxplot(aes(y = likable),position = position_dodge(width = 0.8), alpha = 0.8, color = "black", fill = "firebrick3") +
+  scale_y_continuous(name = "Likability") +
   scale_x_discrete(name = "Advised Rank") +
@@
 plot2 <- ggplot(study2_time3, aes(x = Advice)) +
-  geom_boxplot(aes(y = warmAvg),position = position_dodge()) +
-  scale_y_continuous(name = "Rating on Warmth") +
+  geom_boxplot(aes(y = warmAvg),position = position_dodge(width = 0.8), alpha = 0.8, color = "black", fill = "dodgerblue3") +
+  scale_y_continuous(name = "Warmth") +
   scale_x_discrete(name = "Advised Rank") +
@@
 
-Finally, we examine whether flattering advice indeed leads to more positive evaluations of
-advisers, or whether flattering advice is dismissed as insencere.
-Following our preregistration, we average the ratings on likeability,
-warmth,  friendliness, and good-naturedness to create a scale of likeability
-($\alpha$ = `r cronbach.alpha(study2_time3[, 5:8])$alpha`);
-<!-- David: The draft had trustworthiness as part of this scale. -->
-<!-- Can we just double-check against the preregistration? -->
-<!-- And was Likeable part of that? -->
-<!-- We might also want a name for the scale that isn't the same as one -->
-<!-- of the items, though I'm not sure what. -->
-<!-- Same for trustworthiness -- though that could simply be "Trust" -->
-
-<!-- Amanda: My bad. We only pre-reg that we will measure likable (single item) and warm (four items)" -->
-<!-- I include trustworthiness here because it is part of that existing scale" -->
-
-and we create a scale of trustworthiness by averaging the ratings of
-trustworthiness and sincerity ($\alpha$ = `r cronbach.alpha(study2_time3[, 9:10])$alpha`).
-
-<!-- The Figure is not super clear. How about we try a series of box plots, -->
-<!-- with the x-axis as the advised rank? Standard errors will be huge at the -->
-<!-- extremes. -->
-
-<!-- Also, we need to do something relative to the advisees' expectations. -->
-<!-- I wonder what would be interesting here? Maybe averages for three groups: -->
-<!-- more attractive than the participants' own guess, equally attractive, and less -->
-<!-- attractive? -->
-
-<!-- Amanda: How about the following picture? -->
-
-```{r study2ratingByGroup, fig.cap="The Response to Different Advice"}
+```{r study2ratingByGroup, fig.cap="After participants received advice that suggested betting on a rank that was lower than, equal to, or higher than their self-expectations, they evaluated advisors based on their likability and warmth.
+Participants rated advisors who gave flattering advice and delivered a high evaluation of their attractiveness as more likable and warm than those whose advice implied a lower evaluation of their attractiveness."}
 
@@
   geom_bar(stat = "identity", position = "dodge") +
-  scale_fill_manual(values = c("#E74C3C",'#4169E1')) +
+  scale_fill_manual(values = c("firebrick3",'dodgerblue3')) +
   labs(x = "Advice", y = "Rating") +
@@
         plot.title = element_text(hjust = 0.5, size = 20)) +
-  geom_text(aes(label = paste0(Freq), y = 0.5), position = position_dodge(width = 0.9), size = 2, color = 'white')
+  geom_text(aes(label = paste0(Freq), y = 0.5), position = position_dodge(width = 0.9), size = 5, color = 'white', fontface = "bold")
 
@@
 
-As seen in Figure \@ref(fig:study2Rating), we
+As seen in Figure \@ref(fig:study2rating), we
 found that advisees who suggested that the advisee was more attractive
@@
 \< .05; b = -0.133, p \< .001, respectively; See Columns 1 and 2 of Table \@ref(tab:study2regs)).
+When using their self-expectations as a reference point, advisors who suggest a rank lower than that point are perceived as less likable and warm (see Figure \@ref(fig:study2ratingByGroup)).
 Interestingly, these benefits are not at the cost of being hypocritical;

### 2024-05-22 manuscript/manuscript.Rmd
Upload new Study 1

@@
 
-study1_math50 <- read.csv(here::here("Data/Cleaned Data/S1_Math50_cleaned.csv"))
-study1_time1All <- readRDS(here::here("Data/Study1_time1All.Rds"))
-study1_time1 <- readRDS(here::here("Data/Study1_time1.Rds"))
-study1_time2_giver <- readRDS(here::here("Data/Study1_time2_giver.Rds"))
-study1_time2_giver50 <- readRDS(here::here("Data/Study1_time2_giver50.Rds"))
-study1_advice <- readRDS(here::here("Data/Study1_time2_advice.Rds"))
-study1_time3 <- readRDS(here::here("Data/Study1_time3.Rds"))
+study3_math50 <- read.csv(here::here("Data/Cleaned Data/S3_Math50_cleaned.csv"))
+study3_time1All <- readRDS(here::here("Data/Study3_time1All.Rds"))
+study3_time1 <- readRDS(here::here("Data/Study3_time1.Rds"))
+study3_time2_giver <- readRDS(here::here("Data/Study3_time2_giver.Rds"))
+study3_time2_giver50 <- readRDS(here::here("Data/Study3_time2_giver50.Rds"))
+study3_advice <- readRDS(here::here("Data/Study3_time2_advice.Rds"))
+study3_time3 <- readRDS(here::here("Data/Study3_time3.Rds"))
 
@@
   # randomly select 10 participants
-  subgroup <- sample(study1_math50$ProlificID, size = 5, replace = FALSE)
+  subgroup <- sample(study3_math50$ProlificID, size = 5, replace = FALSE)
   # compute the average score for the selected participants
-  subgroup_avg <- mean(study1_math50$Score[study1_math50$ProlificID %in% subgroup])
+  subgroup_avg <- mean(study3_math50$Score[study3_math50$ProlificID %in% subgroup])
   # add the subgroup and its average score to the dataframe
@@
 
-sortedScore <- sort(study1_math50$Score, decreasing = TRUE)
+sortedScore <- sort(study3_math50$Score, decreasing = TRUE)
 LP_lower <- sortedScore[50]
@@
 of previous participants and have their expectations anchored based on their performance.
-Thus, we begin by first recruiting a sample of `r scales::comma(dim(study1_math50)[1])`
+Thus, we begin by first recruiting a sample of `r scales::comma(dim(study3_math50)[1])`
 participants from Prolific to complete a 10-question multiple choice
@@
 "High Performers" and the bottom 20 scorers as the "Low Performers." On
-average, participants answered `r round(mean(study1_math50$Score),2)`
+average, participants answered `r round(mean(study3_math50$Score),2)`
 questions correctly, High Performers scored between `r HP_lower` and
@@
 
-We then recruited `r scales::comma(dim(study1_time1All)[1])`
+We then recruited `r scales::comma(dim(study3_time1All)[1])`
 participants for the role of advisees in Stage 1 of our main experiment.
@@
 male participants to complete the survey, ending up with a sample of 500
-men and 500 women ($M_{\text{Age}}$ = `r mean(study1_time1$Age)`). 
+men and 500 women ($M_{\text{Age}}$ = `r mean(study3_time1$Age)`). 
 Participants completed the same 10-item mathematics quiz as the
@@
 
-We then recruited `r scales::comma(dim(study1_time2_giver)[1])`
+We then recruited `r scales::comma(dim(study3_time2_giver)[1])`
 participants for Stage 2, placing them in the role of advisers. We began
@@
 the survey open for 7 days. In total,
-`r scales::comma(dim(study1_time3)[1])` participants
-(`r scales::comma(dim(study1_time3[study1_time3$Gender == 'Male',])[1])`
+`r scales::comma(dim(study3_time3)[1])` participants
+(`r scales::comma(dim(study3_time3[study3_time3$Gender == 'Male',])[1])`
 men,
-`r scales::comma(dim(study1_time3[study1_time3$Gender == 'Female',])[1])`
+`r scales::comma(dim(study3_time3[study3_time3$Gender == 'Female',])[1])`
 women) returned. The brief survey reminded them of the task they
@@
 no different from one another
-(`r round(mean(study1_time1[study1_time1$Condition == "Low",]$count),2)`
+(`r round(mean(study3_time1[study3_time1$Condition == "Low",]$count),2)`
 and
-`r round(mean(study1_time1[study1_time1$Condition == "High",]$count),2)`
+`r round(mean(study3_time1[study3_time1$Condition == "High",]$count),2)`
 for the Low Expectations and High Expectations treatments, respectively,
-`r papaja::apa_print(t.test(count ~ Condition, data = study1_time1, var.equal = T))$statistic`).
+`r papaja::apa_print(t.test(count ~ Condition, data = study3_time1, var.equal = T))$statistic`).
 The expectations treatment did, however, affect how well they thought
@@
 a score of
-`r round(mean(study1_time1[study1_time1$Condition == "Low",]$count),2)`
+`r round(mean(study3_time1[study3_time1$Condition == "Low",]$count),2)`
 vs.
-`r round(mean(study1_time1[study1_time1$Condition == "High",]$Guess),2)`
+`r round(mean(study3_time1[study3_time1$Condition == "High",]$Guess),2)`
 in the High Expectations treatment
-(`r papaja::apa_print(t.test(Guess ~ Condition, data = study1_time1, var.equal = T))$statistic`),
+(`r papaja::apa_print(t.test(Guess ~ Condition, data = study3_time1, var.equal = T))$statistic`),
 showing that the manipulation was successful, albeit small. Contrary to our
 expectations, we did find a gender difference in performance: men scored
-`r round(mean(study1_time1[study1_time1$Gender == "Male",]$count),2)` on
+`r round(mean(study3_time1[study3_time1$Gender == "Male",]$count),2)` on
 average, while women scored
-`r round(mean(study1_time1[study1_time1$Gender == "Female",]$count),2)`
-(`r papaja::apa_print(t.test(count ~ Gender, data = study1_time1, var.equal = T))$statistic`).
+`r round(mean(study3_time1[study3_time1$Gender == "Female",]$count),2)`
+(`r papaja::apa_print(t.test(count ~ Gender, data = study3_time1, var.equal = T))$statistic`).
 Consistent with this difference, men thought they answered more questions 
@@
 women
-(`r round(mean(study1_time1[study1_time1$Gender == "Male",]$Guess),2)`
+(`r round(mean(study3_time1[study3_time1$Gender == "Male",]$Guess),2)`
 vs
-`r round(mean(study1_time1[study1_time1$Gender == "Female",]$Guess),2)`,
-`r papaja::apa_print(t.test(Guess ~ Gender, data = study1_time1, var.equal = T))$statistic`).
+`r round(mean(study3_time1[study3_time1$Gender == "Female",]$Guess),2)`,
+`r papaja::apa_print(t.test(Guess ~ Gender, data = study3_time1, var.equal = T))$statistic`).
 This difference, however, does not affect the interpretation of our
@@
 that women underestimate their performance by 0.76 points, while men do so by
-only 0.27 points `r papaja::apa_print(t.test(overconfidence ~ Gender, data = study1_time1 %>% dplyr::mutate(overconfidence = Guess - count)))$full_result`.
+only 0.27 points `r papaja::apa_print(t.test(overconfidence ~ Gender, data = study3_time1 %>% dplyr::mutate(overconfidence = Guess - count)))$full_result`.
 Although neither gender is overconfident, men on average are more confident in
@@
 ```{r study1regs}
-study1_advice <- study1_advice %>% dplyr::mutate(Treatment = factor(Treatment, levels = c('Low', 'High'))) %>%
+study3_advice <- study3_advice %>% dplyr::mutate(Treatment = factor(Treatment, levels = c('Low', 'High'))) %>%
   dplyr::mutate(ExpShow = ifelse(Condition == 'E',1,0))
 
-modelsummary::modelsummary(list(`(1)` = lm(Advice ~ Treatment + Performance , data = study1_advice %>% dplyr::filter(ExpShow == 1)),
-                                `(2)` = lm(Advice ~ ExpShow*Gender , data = study1_advice),
-                                `(3)` = lm(ExpectedBonus ~ ExpShow*Gender, data = study1_advice)),
+modelsummary::modelsummary(list(`(1)` = lm(Advice ~ Treatment + Performance , data = study3_advice %>% dplyr::filter(ExpShow == 1)),
+                                `(2)` = lm(Advice ~ ExpShow*Gender , data = study3_advice),
+                                `(3)` = lm(ExpectedBonus ~ ExpShow*Gender, data = study3_advice)),
                            vcov = c(~GiverID, ~GiverID,~GiverID),
@@
 
-ProbHG <- study1_advice %>%
+ProbHG <- study3_advice %>%
   group_by(Condition, Performance, Gender) %>%
@@
 
-study1_time3 <- study1_time3 %>% dplyr::mutate(AdviseeCondition = factor(AdviseeCondition, levels = c('Low', 'High'))) %>%
+study3_time3 <- study3_time3 %>% dplyr::mutate(AdviseeCondition = factor(AdviseeCondition, levels = c('Low', 'High'))) %>%
      dplyr::mutate(Adopt = ifelse(Bet == Advice,1,0))
 
-modelsummary::modelsummary(list(`(1)` = lm(bonus ~ AdviseeCondition + AdviseeScore, data = study1_time3 %>%
+modelsummary::modelsummary(list(`(1)` = lm(bonus ~ AdviseeCondition + AdviseeScore, data = study3_time3 %>%
                                              dplyr::filter(GiverCondition == 1)),
-                                `(2)` = lm(bonus ~ Gender + AdviseeScore, data = study1_time3 %>%
+                                `(2)` = lm(bonus ~ Gender + AdviseeScore, data = study3_time3 %>%
                                              dplyr::filter(GiverCondition == 1)),
-                                `(3)` = lm(Adopt ~ Gender + GiverCondition + Advice, data = study1_time3),
-                                `(4)` = lm(Adopt ~ Gender + GiverCondition + Advice + Gender*GiverCondition + GiverCondition*Advice + Gender*Advice, data = study1_time3)),
+                                `(3)` = lm(Adopt ~ Gender + GiverCondition + Advice, data = study3_time3),
+                                `(4)` = lm(Adopt ~ Gender + GiverCondition + Advice + Gender*GiverCondition + GiverCondition*Advice + Gender*Advice, data = study3_time3)),
                            vcov = c("classical", "classical","classical","classical"),

### 2024-05-22 R/clean_study1_time1.R

@@ -4,47 +4,15 @@ library(magrittr)
 
 Advisee <- data.table::fread(here::here("Data/Raw Data/S1_time1.csv"),
                              header = T,na.strings = '')[-c(1,2)] %>%
-  dplyr::filter(Progress == '100' & Status == 'IP Address' & !is.na(QID3) & Gender != 'Other') %>%
-  dplyr::rename('ProlificID' = 'QID3') %>%
-  dplyr::mutate(Guess = as.numeric(Guess), Age = as.numeric(Age))  %>%
-  dplyr::select(ProlificID,ResponseId,Condition, QID10:QID19,Guess,
-                Gender, Age, Ethnicity,Education)
+  dplyr::filter(Status == 'IP Address',Progress == '100',!is.na(PROLIFIC_PID) ,!is.na(Gender)) %>%
+  dplyr::filter(!is.na(ResponseId) ,!is.na(Age) ) %>%
+  dplyr::mutate(Guess = coalesce(Guess, Guess_L)) %>%
+  dplyr::mutate(Guess = ifelse(Guess == "Compete against the High Performer Group",1,0)) %>%
+  dplyr::select(PROLIFIC_PID,Guess,default,Score,Age,Gender, Ethnicity,Education) %>%
+  dplyr::mutate(Score = as.numeric(Score))
 
 
-
-# count correct answers
-answerList <- c('113 feet','x = -2','x15','13','2.06',
-                '-34','6','63°','3','4x2 + 32x + 48')
-answer <- Advisee %>% dplyr::select(QID10:QID19)
-#count <-  apply(answer, 1, function(x) sum(x == answerList))
-
-count <- apply(answer, 1, function(x) {
-  # Check if there are NAs in the list
-  if (any(is.na(x))) {
-    # If there are NAs, count non-NA elements
-    sum(!is.na(x) & x %in% answerList)
-  } else {
-    # If there are no NAs, count all elements
-    sum(x == answerList)
-  }
-})
-
-
-count <- as.data.frame(count)
-Advisee <- cbind(Advisee,count)
-
-saveRDS(Advisee, file = here::here("Data/Study1_time1All.Rds"))
-Advisee %>% write.csv("Data/Cleaned Data/S1_time1All_clean.csv")
-
-#create a gander-balance sample
-females <- Advisee %>% dplyr::filter(Gender == "Female")
[…]

### 2024-05-22 R/clean_study1_time2.R

@@ -4,83 +4,56 @@ library(magrittr)
 
 giver <- data.table::fread(here::here("Data/Raw Data/S1_time2.csv"),
                            header = T,na.strings = '')[-c(1,2)] %>%
-  dplyr::filter(Progress == '100',gender != 'Other', !is.na(PROLIFIC_PID)) %>%
-  dplyr::select(ResponseId, PROLIFIC_PID,Condition,dplyr::contains("_advice"),GoupNum,
-                age,gender, ethnicity,education,"0.AdviseeID":"9.Treatment" ) %>%
+  dplyr::filter(Progress == '100', !is.na(PROLIFIC_PID),!is.na(gender)) %>%
+  dplyr::select(PROLIFIC_PID,Condition,dplyr::contains("_advice"),
+                age,gender, ethnicity,education,"0.PROLIFIC_PID":"9.Guess" ) %>%
   dplyr::mutate(dplyr::across(dplyr::contains("_advice"),
                               ~ dplyr::case_when(stringr::str_starts(.,"Low") ~ 0,
                                                  stringr::str_starts(.,"High") ~ 1))) %>%
   dplyr::mutate_at(vars(contains("_advice")), as.numeric) %>%
-  dplyr::mutate_at(vars(contains('.Performance')), as.numeric) %>%
-  dplyr::mutate_at(vars(contains('.Estimate')), as.numeric) %>%
-  dplyr::rename('GroupNum' = 'GoupNum') %>%
-  dplyr::mutate(GroupNum = as.numeric(GroupNum), age = as.numeric(age))
-
-giver50 <- data.table::fread(here::here("Data/Raw Data/S1_time2_50.csv"),
-                           header = T,na.strings = '')[-c(1,2)] %>%
-  dplyr::filter(Progress == '100',gender != 'Other', !is.na(PROLIFIC_PID)) %>%
-  dplyr::select(ResponseId, PROLIFIC_PID,Condition,dplyr::contains("_advice"),
-                age,gender, ethnicity,education,"0.AdviseeID":"9.Treatment" ) %>%
-  dplyr::mutate(dplyr::across(dplyr::contains("_advice"),
-                              ~ dplyr::case_when(stringr::str_starts(.,"Low") ~ 0,
-                                                 stringr::str_starts(.,"High") ~ 1))) %>%
[…]

### 2024-05-22 R/clean_study3_time3.R

@@ -2,7 +2,7 @@ library(dplyr)
 library(ggplot2)
 library(magrittr)
 
-Advisee <- data.table::fread(here::here("Data/Raw Data/S1_time3.csv"),
+Advisee <- data.table::fread(here::here("Data/Raw Data/S3_time3.csv"),
                              header = T,na.strings = '')[-c(1,2)] %>%
   dplyr::filter(Progress == '100' & Status == 'IP Address') %>%
   dplyr::rename('ProlificID' = 'Q3', 'Advice' = '0.Advice',
@@ -15,12 +15,12 @@ Advisee <- data.table::fread(here::here("Data/Raw Data/S1_time3.csv"),
   dplyr::mutate(Guess = as.numeric(Guess) )
 
 # randomly select one competitor
-AdviseeScore <- data.table::fread(here::here("Data/Cleaned Data/S1_time1_clean.csv"),
+AdviseeScore <- data.table::fread(here::here("Data/Cleaned Data/S3_time1_clean.csv"),
                                   header = T,na.strings = '') %>%
   dplyr::select(ProlificID, count, Condition, Gender, Age) %>%
   dplyr::rename('AdviseeScore' = 'count', 'AdviseeCondition' = 'Condition')
 
-Competitors <- data.table::fread(here::here("Data/Cleaned Data/S1_Math50_cleaned.csv"),
+Competitors <- data.table::fread(here::here("Data/Cleaned Data/S3_Math50_cleaned.csv"),
                                     header = T,na.strings = '') %>%
   dplyr::select(ProlificID, Score)
 
@@ -86,8 +86,8 @@ Return <- data_frame(ExpectedBonus = unlist(ReturnList))
 
 AdviseeResult <- cbind(AdviseeResult, Return)
 
-saveRDS(AdviseeResult, file = here::here("Data/Study1_time3.Rds"))
+saveRDS(AdviseeResult, file = here::here("Data/Study3_time3.Rds"))
 
-AdviseeResult %>% write.csv("Data/Cleaned Data/S1_time3_clean.csv")
+AdviseeResult %>% write.csv("Data/Cleaned Data/S3_time3_clean.csv")
 
 

### 2024-09-20 manuscript/manuscript.Rmd
Update all datasets

@@
 ```{r setup, include=FALSE}
+
 library(magrittr)
@@
 
-Seeking and giving advice can present conversational challenges that
-are difficult to navigate. Advice seekers may be embarrassed to ask for
-help [@Benabou2022], and they may fail to do so if the information they
+Seeking and giving advice can present conversational challenges that are
+difficult to navigate. Advice seekers may be embarrassed to ask for help
+[@Benabou2022], and they may fail to do so if the information they
 receive could lead to disappointment [@Gill2012]. Indeed, people prefer
@@
 the preferences of the advisee [@Kray2000; @Kray1999]. When they are
-uncertain, they even prefer that advisees do not rely (extensively) on their
-recommendations [@Ache2020]. Thus, it seems that people are concerned
-about providing good advice even when they are not incentivized for the
-recipient's decision quality.
+uncertain, they even prefer that advisees do not rely (extensively) on
+their recommendations [@Ache2020]. Thus, it seems that people are
+concerned about providing good advice even when they are not
+incentivized for the recipient's decision quality.
 
@@
 performing student to switch to a less-demanding major conveys a belief
-that the student is not capable of improving. Thus, while the painful truth
-may prevent someone from making a bad decision, it may come at a hedonic cost to
-the recipient and damage the relationship between the adviser and
-advisee. We propose that advisers take these costs into account, even
-when the interactions are entirely anonymous and they are incentivized
-for the quality of the advisee's decision.
+that the student is not capable of improving. Thus, while the painful
+truth may prevent someone from making a bad decision, it may come at a
+hedonic cost to the recipient and damage the relationship between the
+adviser and advisee. We propose that advisers take these costs into
+account, even when the interactions are entirely anonymous and they are
+incentivized for the quality of the advisee's decision.
 
@@
 
-Our account therefore predicts that people give and receive advice that is more
-flattering and suggestive of inflated ability and optimistic outcomes
-than would advice in the absence of such interpersonal considerations.
-However, we propose that this is not true for all advisees equally.
-Presenting flattering advice requires the formation of beliefs about the
-advisee's expectations (reference point). @Exley2022 show that men are
-more overconfident than women, conditional on equal performance, and that
-people anticipate this difference. An adviser who seeks to avoid disappointment and incorporates
-expectations into their advice would then present more favorable advice
-to male advisees than to female advisees (see Figure 1 for an
-illustration). This provides a novel account for a well-known finding
-that men receive more aspirational advice than do women [@Kanze2018].
-Notably, when it pays to have accurate beliefs, such flattering advice
-would come at a cost: while men would be more likely to aim higher, they
-would also suffer greater costs from aiming too high and failing to meet
-the objective.
+Our account therefore predicts that people give and receive advice that
+is more flattering and suggestive of inflated ability and optimistic
+outcomes than would advice in the absence of such interpersonal
+considerations. However, we propose that this is not true for all
+advisees equally. Presenting flattering advice requires the formation of
+beliefs about the advisee's expectations (reference point). @Exley2022
+show that men are more overconfident than women, conditional on equal
+performance, and that people anticipate this difference. An adviser who
+seeks to avoid disappointment and incorporates expectations into their
+advice would then present more favorable advice to male advisees than to
+female advisees (see Figure 1 for an illustration). This provides a
+novel account for a well-known finding that men receive more
+aspirational advice than do women [@Kanze2018]. Notably, when it pays to
+have accurate beliefs, such flattering advice would come at a cost:
+while men would be more likely to aim higher, they would also suffer
+greater costs from aiming too high and failing to meet the objective.
 
@@
 incentivized based on the outcome of the advisee's decision. In a second
-preregistered experiment (n = 700), we show that advisers respond to incentives for
-interpersonal considerations. They tell people that they are more
-attractive than they believe them to be, and inflate to a greater extent
-when incentivized for likability rather than accuracy. Notably, they inflate
-even when only incentivized for accuracy. Advisees indeed
-reward such flattering advice, rating the advisers more likeable and no
-less trustworthy than those who provide more accurate advice.
+preregistered experiment (n = 700), we show that advisers respond to
+incentives for interpersonal considerations. They tell people that they
+are more attractive than they believe them to be, and inflate to a
+greater extent when incentivized for likability rather than accuracy.
+Notably, they inflate even when only incentivized for accuracy. Advisees
+indeed reward such flattering advice, rating the advisers more likeable
+and no less trustworthy than those who provide more accurate advice.
 
@@
 
-We report all sample sizes, data exclusions, manipulations, and
-measures in the studies. Screen captures of the experimental materials
-are available in the Supplemental Information. The complete data, code
-to reproduce all statistical analyses and figures in the manuscript, as
+We report all sample sizes, data exclusions, manipulations, and measures
+in the studies. Screen captures of the experimental materials are
+available in the Supplemental Information. The complete data, code to
+reproduce all statistical analyses and figures in the manuscript, as
 well as the preregistration reports will be available via OSF. All our
@@
 <!-- ^[<https://osf.io/8r3d4/?view_only=5ad7bafcd16b4d4ba08bb28b0e2bd02d>] -->
+
 <!-- Commenting this out for IACM -->
@@
 We begin by examining whether advisers take the expectations of advisees
-into account, even when those expectations are not relevant to the decision
-the advisee has to make. In a three-stage experiment, we first recruit a
-sample of advisees and ask them to complete a mathematics quiz. After
-answering ten multiple-choice questions, participants are anchored
-to low or high performance expectations and asked to guess how many
-questions they answered correctly. Next, we recruit advisers and
+into account, even when those expectations are not relevant to the
+decision the advisee has to make. In a three-stage experiment, we first
+recruit a sample of advisees and ask them to complete a mathematics
+quiz. After answering ten multiple-choice questions, participants are
+anchored to low or high performance expectations and asked to guess how
+many questions they answered correctly. Next, we recruit advisers and
 show them either only the true performance of the advisee, or the true
@@
 against a group of high-performers or a group of low-performers on the
-mathematics quiz, where a potential bonus depends on outperforming the competitor
-and which group was chosen. Finally, we invite the advisees back and show them the
-advice they have received. Advisees then pick whether to compete against
-high or low performers, with the outcome determined by their past performance on the quiz. Our
-key hypotheses are that (1) advisees who were anchored to high expectations
-would be more likely to receive advice to compete against the high
-performer group, and (2) that men are more likely than women to be advised to 
-compete against the high-performer group when expectations are shown.
+mathematics quiz, where a potential bonus depends on outperforming the
+competitor and which group was chosen. Finally, we invite the advisees
+back and show them the advice they have received. Advisees then pick
+whether to compete against high or low performers, with the outcome
+determined by their past performance on the quiz. Our key hypotheses are
+that (1) advisees who were anchored to high expectations would be more
+likely to receive advice to compete against the high performer group,
+and (2) that men are more likely than women to be advised to compete
+against the high-performer group when expectations are shown.
 
@@
 
-As part of our main experiment, participants choose to compete against a group
-of previous participants and have their expectations anchored based on their performance.
-Thus, we begin by first recruiting a sample of `r scales::comma(dim(study3_math50)[1])`
-participants from Prolific to complete a 10-question multiple choice
-mathematics quiz. The questions were taken from a paper-version of the
-ASVAB standardized exam, such that answers were not available online.
-Participants had five minutes to answer the quiz and were paid 10 cents for
-each correctly answered question. We define the top 20 scorers as the
-"High Performers" and the bottom 20 scorers as the "Low Performers." On
-average, participants answered `r round(mean(study3_math50$Score),2)`
-questions correctly, High Performers scored between `r HP_lower` and
-`r HP_upper`, and Low Performers scored between `r LP_lower` and
-`r LP_upper`. In order to anchor the expectations of participants in our main
-experiment, we simulated 1,000 pairings of groups of five
-participants, with the 5<sup>th</sup> percentile of groups scoring an average of
-`r p5` and the 95 th percentile scoring an average of `r p95`. We report these
-averages to participants in the Low Expectations and High Expectations treatment,
+As part of our main experiment, participants choose to compete against a
+group of previous participants and have their expectations anchored
+based on their performance. Thus, we begin by first recruiting a sample
+of `r scales::comma(dim(study3_math50)[1])` participants from Prolific
+to complete a 10-question multiple choice mathematics quiz. The
+questions were taken from a paper-version of the ASVAB standardized
+exam, such that answers were not available online. Participants had five
+minutes to answer the quiz and were paid 10 cents for each correctly
+answered question. We define the top 20 scorers as the "High Performers"
+and the bottom 20 scorers as the "Low Performers." On average,
+participants answered `r round(mean(study3_math50$Score),2)` questions
+correctly, High Performers scored between `r HP_lower` and `r HP_upper`,
+and Low Performers scored between `r LP_lower` and `r LP_upper`. In
+order to anchor the expectations of participants in our main experiment,
+we simulated 1,000 pairings of groups of five participants, with the
+5<sup>th</sup> percentile of groups scoring an average of `r p5` and the
+95 th percentile scoring an average of `r p95`. We report these averages
+to participants in the Low Expectations and High Expectations treatment,
 respectively.
@@
 participants for the role of advisees in Stage 1 of our main experiment.
-To arrive at a gender-balanced sample, we dropped the last two
-male participants to complete the survey, ending up with a sample of 500
-men and 500 women ($M_{\text{Age}}$ = `r mean(study3_time1$Age)`). 
-Participants completed the same 10-item mathematics quiz as the
-earlier participants and were informed that their performance would
-affect their bonus earnings in a follow-up stage to be conducted a few
-days later. After completing the quiz, we informed them of the average
-score of a group of five participants from the preliminary survey. We
-randomly assigned them to learn about the 5<sup>th</sup> percentile of groups,
-which scored `r p5`. ("Low Expectations" treatment) or the 95<sup>th</sup>
-percentile of groups, which scored `r p95` ("High Expectations"
-treatment). Participants then made a guess (unincentivized) about how
-many questions they think they answered correctly. The survey concluded
-with basic demographic questions.
+To arrive at a gender-balanced sample, we dropped the last two male
+participants to complete the survey, ending up with a sample of 500 men
+and 500 women ($M_{\text{Age}}$ = `r mean(study3_time1$Age)`).
+Participants completed the same 10-item mathematics quiz as the earlier
+participants and were informed that their performance would affect their
+bonus earnings in a follow-up stage to be conducted a few days later.
+After completing the quiz, we informed them of the average score of a
+group of five participants from the preliminary survey. We randomly
+assigned them to learn about the 5<sup>th</sup> percentile of groups,
+which scored `r p5`. ("Low Expectations" treatment) or the
+95<sup>th</sup> percentile of groups, which scored `r p95` ("High
+Expectations" treatment). Participants then made a guess
+(unincentivized) about how many questions they think they answered
+correctly. The survey concluded with basic demographic questions.
 
@@
 preliminary study and Stage 1 had completed, and informed them of the
-average score of all participants in the preliminary study. Advisers had to recommend
-whether an advisee should compete against the Low Performers or the High
-Performers (we used these terms in the survey). We anticipated that
-being told to compete against High Performers is more flattering and hence being
-told to compete against the Low Performers would be disappointing if one had
-expected to do well.
+average score of all participants in the preliminary study. Advisers had
+to recommend whether an advisee should compete against the Low
+Performers or the High Performers (we used these terms in the survey).
+We anticipated that being told to compete against High Performers is
+more flattering and hence being told to compete against the Low
+Performers would be disappointing if one had expected to do well.
 Advisees would earn 30 cents if their score was equal to or higher than
@@
 compete against this group, or 50 cents if they performed as well or
-better than a randomly selected member of the High Performer group and they
-chose to compete against that group. If
-they scored lower, they would not receive any bonus.
+better than a randomly selected member of the High Performer group and
+they chose to compete against that group. If they scored lower, they
+would not receive any bonus.
 
@@
 the past score on the quiz, the advisee's guess is immaterial to which
-group they should compete against. Moreover, in neither treatment did they
-receive any demographic information about their advisee. Participants
-gave recommendations to 10 advisees, which unbeknownst to them were five
-men and five women matched to have identical performance on the test.^[We made this decision to account for the possibility of gender differences in performance.]
-They were informed that if their advice was shown to a participant who
-returned for the follow-up survey, they would receive the identical
-bonus as that participant. The survey then concluded with basic
-demographic questions.
+group they should compete against. Moreover, in neither treatment did
+they receive any demographic information about their advisee.
+Participants gave recommendations to 10 advisees, which unbeknownst to
+them were five men and five women matched to have identical performance
+on the test.[^1] They were informed that if their advice was shown to a
+participant who returned for the follow-up survey, they would receive
+the identical bonus as that participant. The survey then concluded with
+basic demographic questions.
 
-Finally, we invited participants from Stage 1
-back for the follow-up survey. Following our preregistration, we kept
-the survey open for 7 days. In total,
-`r scales::comma(dim(study3_time3)[1])` participants
+[^1]: We made this decision to account for the possibility of gender
+    differences in performance.
+
+Finally, we invited participants from Stage 1 back for the follow-up
+survey. Following our preregistration, we kept the survey open for 7
+days. In total, `r scales::comma(dim(study3_time3)[1])` participants
 (`r scales::comma(dim(study3_time3[study3_time3$Gender == 'Male',])[1])`
@@
 Prolific had observed their real score and given them advice against
-which group to compete against, and finally were reminded them of how many
-questions they guessed they had answered correctly. Importantly, they
-were not informed of their true score or the score of the groups they
-could compete against. Participants then observed the advice from a
+which group to compete against, and finally were reminded them of how
+many questions they guessed they had answered correctly. Importantly,
+they were not informed of their true score or the score of the groups
+they could compete against. Participants then observed the advice from a
 randomly selected adviser and made their decision.
@@
 (`r papaja::apa_print(t.test(Guess ~ Condition, data = study3_time1, var.equal = T))$statistic`),
-showing that the manipulation was successful, albeit small. Contrary to our
-expectations, we did find a gender difference in performance: men scored
+showing that the manipulation was successful, albeit small. Contrary to
+our expectations, we did find a gender difference in performance: men
+scored
 `r round(mean(study3_time1[study3_time1$Gender == "Male",]$count),2)` on
@@
 (`r papaja::apa_print(t.test(count ~ Gender, data = study3_time1, var.equal = T))$statistic`).
-Consistent with this difference, men thought they answered more questions 
-correctly than did
-women
+Consistent with this difference, men thought they answered more
+questions correctly than did women
 (`r round(mean(study3_time1[study3_time1$Gender == "Male",]$Guess),2)`
@@
 
-We define a measure of "overconfidence" as (Performance - Estimate). We observe
-that women underestimate their performance by 0.76 points, while men do so by
-only 0.27 points `r papaja::apa_print(t.test(overconfidence ~ Gender, data = study3_time1 %>% dplyr::mutate(overconfidence = Guess - count)))$full_result`.
-Although neither gender is overconfident, men on average are more confident in
-their performance than are women, as we had expected.
+We define a measure of "overconfidence" as (Performance - Estimate). We
+observe that women underestimate their performance by 0.76 points, while
+men do so by only 0.27 points
+`r papaja::apa_print(t.test(overconfidence ~ Gender, data = study3_time1 %>% dplyr::mutate(overconfidence = Guess - count)))$full_result`.
+Although neither gender is overconfident, men on average are more
+confident in their performance than are women, as we had expected.
 
@@
               method = "glm", method.args = list(family = "binomial"), color = "grey", se = FALSE) +
-  scale_color_manual(values = c("firebrick3",'dodgerblue3', "grey"),
+  scale_color_manual(values = c("#2A629A",'#FF7F3E', "grey"),
                      labels = c("Female + Expectations", "Male + Expectations", "Expectation Hidden")) +
@@
 group for advisers in the "Expectations" treatment, controlling for the
-true performance of the advisee. Because each adviser
-made ten recommendations, we cluster standard errors at the adviser
-level. However, contrary to our expectations, we do not see a significant
-effect of the expectations treatment. This may be because the induced difference
-in expectations was too small.
+true performance of the advisee. Because each adviser made ten
+recommendations, we cluster standard errors at the adviser level.
+However, contrary to our expectations, we do not see a significant
+effect of the expectations treatment. This may be because the induced
+difference in expectations was too small.
 
-However, recall that men were more confident in their performance than were women.
-Our theory thus predicts that showing expectations should lead to more flattering
-advice (i.e., a recommendation to compete against the High Performer group) for
-men than for women. We report a linear probability model with advice to
-compete against the high group as the outcome measure, and the advisee's
-gender, whether expectations were shown to the adviser, and the
-interaction of the two in Column 2 of Table \@ref(tab:study1regs). As
-predicted, we find a significant interaction effect: men are more likely
-to be advised to compete against the High Performers when expectations
-are shown than when they are hidden ($p < 0.001$).
-We show this result graphically in Figure \@ref(fig:study1genderdiff)).
+However, recall that men were more confident in their performance than
+were women. Our theory thus predicts that showing expectations should
+lead to more flattering advice (i.e., a recommendation to compete
+against the High Performer group) for men than for women. We report a
+linear probability model with advice to compete against the high group
+as the outcome measure, and the advisee's gender, whether expectations
+were shown to the adviser, and the interaction of the two in Column 2 of
+Table \@ref(tab:study1regs). As predicted, we find a significant
+interaction effect: men are more likely to be advised to compete against
+the High Performers when expectations are shown than when they are
+hidden ($p < 0.001$). We show this result graphically in Figure
+\@ref(fig:study1genderdiff)).
 
@@
 <!-- David: If we plotted on the x-axis performance and on the y-axis the difference -->
+
 <!-- between recommendations for men & women, this would look inverse-U shaped, right? -->
+
 <!-- Might be a nice way to illustrate what you describe. -->
@@
 <!-- Amanda: I think our primary purpose here is still showing the existence of gender difference -->
+
 <!-- The current plot shows discrepancy between two lines, allowing us to demonstrate gender gap -->
@@
 To examine the quality of advice, we computed the expected bonus
-earnings for someone who followed the recommendations. For example, if an
-adviser suggested competing against the High Performer group, we matched the
-advisee against all 20 members of that group and determined how often their score
-matched or exceeded that of the member. We then multiplied this number by the
-respective bonus earnings (50 cents and 30 cents for the High and Low Performer 
-group, respectively). To see if including expectations leads to worse advise
-for men, we report a linear probability model with the experimental treatment
-of the adviser, the gender of the advisee, and their interaction in Column 3
-of Table \@ref(tab:study1regs). Displaying expectations led men to be advised
-to compete against the High Performer group more often, and this advise turned
-out to be bad: men receive worse advise than do women when expectations are 
-displayed, but not in their absence.^[This analysis was not preregistered, and we note here that the reduction in expected earnings is small.
-However, it is interesting that expectations have a negative effect for men who underestimate their performance on average.
-One possibility is that advisers suggest the High Performer group more often than is optimal.
-We return to the possibility that advice is overall biased to be flattering in Study 2.]
+earnings for someone who followed the recommendations. For example, if
+an adviser suggested competing against the High Performer group, we
+matched the advisee against all 20 members of that group and determined
+how often their score matched or exceeded that of the member. We then
+multiplied this number by the respective bonus earnings (50 cents and 30
+cents for the High and Low Performer group, respectively). To see if
+including expectations leads to worse advise for men, we report a linear
+probability model with the experimental treatment of the adviser, the
+gender of the advisee, and their interaction in Column 3 of Table
+\@ref(tab:study1regs). Displaying expectations led men to be advised to
+compete against the High Performer group more often, and this advise
+turned out to be bad: men receive worse advise than do women when
+expectations are displayed, but not in their absence.[^2]
 
-```{r study1time3}
+[^2]: This analysis was not preregistered, and we note here that the
+    reduction in expected earnings is small. However, it is interesting
+    that expectations have a negative effect for men who underestimate
+    their performance on average. One possibility is that advisers
+    suggest the High Performer group more often than is optimal. We
+    return to the possibility that advice is overall biased to be
+    flattering in Study 2.
+
+```{r study3time3}
 
@@
 To determine whether flattering advice is truly costly, however, we need
-to examine the outcome of the advisees. In particular, they could ignore flattering
-advice, recognizing it as such and thus failing to adhere to it.
-Align with our prediction, participants who were primed with high expectations earned less when their expectations were conveyed to the advisers, although this result is only directional  (see Column 1 of Table \@ref(tab:study1time3)).
-Similarly, as shown in Column 2 of Table \@ref(tab:study1time3), we also found that male participants received less reward when their expectations were presented, even when their performance was the same.
-These findings suggest that flattering advice is not without consequences.
-Furthermore, our research indicates that because males are more likely to follow such advice (see Column 4 of Table \@ref(tab:study1time3), their tendency towards competition intensifies the cost of such advice.
+to examine the outcome of the advisees. In particular, they could ignore
+flattering advice, recognizing it as such and thus failing to adhere to
+it. Align with our prediction, participants who were primed with high
+expectations earned less when their expectations were conveyed to the
+advisers, although this result is only directional (see Column 1 of
+Table \@ref(tab:study3time3)). Similarly, as shown in Column 2 of Table
+\@ref(tab:study3time3), we also found that male participants received
+less reward when their expectations were presented, even when their
+performance was the same. These findings suggest that flattering advice
+is not without consequences. Furthermore, our research indicates that
+because males are more likely to follow such advice (see Column 4 of
+Table \@ref(tab:study3time3), their tendency towards competition
+intensifies the cost of such advice.
 
 ## Discussion
-When the quality of a decision is not dependent on someone's expectations,
-advice should not be moved by whether an adviser is aware of the advisees
-expectations. However, consistent with our account that advisers consider the
-belief utility of the advisee and want to flatter, rather than disappoint them,
-we find that displaying expectations to advisers does matter.
-Specifically, we found that men underestimate their score on a mathematics test
-less than do women. When these expectations are displayed to advisers, they
-are more likely to tell men to compete against the High Performer group.
-Notably, this is bad advice: men whose advisers observed their expectations
-got worse advice as a result.
-Our findings suggest that males with the same scores as their female counterparts earned less, although the evidence is only directional.
-This may be due to males receiving more favorable advice and being more likely to adopt it, resulting in even worse outcomes.
+
+When the quality of a decision is not dependent on someone's
+expectations, advice should not be moved by whether an adviser is aware
+of the advisees expectations. However, consistent with our account that
+advisers consider the belief utility of the advisee and want to flatter,
+rather than disappoint them, we find that displaying expectations to
+advisers does matter. Specifically, we found that men underestimate
+their score on a mathematics test less than do women. When these
+expectations are displayed to advisers, they are more likely to tell men
+to compete against the High Performer group. Notably, this is bad
+advice: men whose advisers observed their expectations got worse advice
+as a result. Our findings suggest that males with the same scores as
+their female counterparts earned less, although the evidence is only
+directional. This may be due to males receiving more favorable advice
+and being more likely to adopt it, resulting in even worse outcomes.
 
 <!-- David: One more sentence about the earnings difference here, which does not -->
+
 <!-- differ significantly. And one sentence about the new analysis of whether -->
+
 <!-- people follow the advice or not. -->
@@
 <!-- David: Just commenting on what I tried to do here... a bit of a transition -->
+
 <!-- for why this study follows from the last. -->
+
 So far, we have shown that displaying expectations can induce gender
 differences in advice-giving. Specifically, advisers were more likely to
-recommend competing against a group of High Performers to men who had higher
-expectations about their performance than did women. We now test directly whether this 
-is driven by interpersonal concerns. Specifically, we examine whether 
-more flattering advice is the result of a desire to be liked and whether
-advisees indeed do like advisers more when they give flattering advice.
+recommend competing against a group of High Performers to men who had
+higher expectations about their performance than did women. We now test
+directly whether this is driven by interpersonal concerns. Specifically,
+we examine whether more flattering advice is the result of a desire to
+be liked and whether advisees indeed do like advisers more when they
+give flattering advice.
 
-We conducted a three-stage experiment in which we experimentally manipulated
-the incentives for advicers. We began by inviting a group of advisees to upload 
-photos of themselves ("selfies") and informed them that they would be rated
-on their attractiveness. We grouped them with nine other participants of the
-same gender and recruited participants of the opposing gender to rank them from
-most to least attractive and to provide advice. Specifically, we asked them
-to advise the participant they ranked as the 7th most attractive (4th least attractive)
-on what rank they should bet they were ranked by a larger group of raters.
-Advisers were randomly assigned to two treatments, receiving a bonus payment
-either if the advisee guessed their rank accurately or if the advisee evaluated
-the adviser as likeable as measured by an unincentivized scale response.
-We hypothesize that advisers who want to be liked by advisees will recommend 
-that they bet on a lower rank, i.e. that they are more attractive.
+We conducted a three-stage experiment in which we experimentally
+manipulated the incentives for advicers. We began by inviting a group of
+advisees to upload photos of themselves ("selfies") and informed them
+that they would be rated on their attractiveness. We grouped them with
+nine other participants of the same gender and recruited participants of
+the opposing gender to rank them from most to least attractive and to
+provide advice. Specifically, we asked them to advise the participant
+they ranked as the 7th most attractive (4th least attractive) on what
+rank they should bet they were ranked by a larger group of raters.
+Advisers were randomly assigned to two treatments, receiving a bonus
+payment either if the advisee guessed their rank accurately or if the
+advisee evaluated the adviser as likeable as measured by an
+unincentivized scale response. We hypothesize that advisers who want to
+be liked by advisees will recommend that they bet on a lower rank, i.e.
+that they are more attractive.
 
@@
 
-We recruited 300 participants from Prolific and, after asking demographic questions, invited them to upload photos of
-themselves (selfies) to be rated by other participants on
-attractiveness. 
+We recruited 300 participants from Prolific and, after asking
+demographic questions, invited them to upload photos of themselves
+(selfies) to be rated by other participants on attractiveness.
 `r scales::comma(dim(study2_time1[study2_time1$gender == 'Male',])[1])`
@@
 women agreed to do so and uploaded pictures that adhered to our
-instructions (e.g., did not include other people). We selected the
-first 100 photos from women to arrive at a gender-balanced sample
-($M_{\text{Age}}$ = `r mean(study2_time1_200$age)` years).
-Participants were informed that their selfies would be randomly grouped with
-those of nine other participants of their gender and ranked in terms of attractiveness
-by a group of new Prolific participants of the opposite gender.
-Lastly, they guessed their rank (unincentivized).
+instructions (e.g., did not include other people). We selected the first
+100 photos from women to arrive at a gender-balanced sample
+($M_{\text{Age}}$ = `r mean(study2_time1_200$age)` years). Participants
+were informed that their selfies would be randomly grouped with those of
+nine other participants of their gender and ranked in terms of
+attractiveness by a group of new Prolific participants of the opposite
+gender. Lastly, they guessed their rank (unincentivized).
 
-Next, we recruited a new, gender-balanced sample for the role
-of advisers. `r scales::comma(dim(study2_time2)[1])`
-participants from Prolific ($M_{\text{Age}}$ =
-`r mean(study2_time2$age)` years;
-`r round(mean(study2_time2$gender == "Female")*100, 2)`% Female) started by
-providing demographic information, then were matched to a group of the opposite
-gender. They then ranked participants from most to least attractive using a
-drop-down menu next to each picture. Because of a limitation with the survey software,
-participants were able to select the same rank for multiple participants, rather
-than rank them uniquely. We remove 115 participants who did not follow instructions
-and provide a unique ranking.
+Next, we recruited a new, gender-balanced sample for the role of
+advisers. `r scales::comma(dim(study2_time2)[1])` participants from
+Prolific ($M_{\text{Age}}$ = `r mean(study2_time2$age)` years;
+`r round(mean(study2_time2$gender == "Female")*100, 2)`% Female) started
+by providing demographic information, then were matched to a group of
+the opposite gender. They then ranked participants from most to least
+attractive using a drop-down menu next to each picture. Because of a
+limitation with the survey software, participants were able to select
+the same rank for multiple participants, rather than rank them uniquely.
+We remove 115 participants who did not follow instructions and provide a
+unique ranking.
 
-After submitting their ratings, they saw the photo of the participant they
-had ranked as the 7th most attractive (i.e., the 4th least attractive). They
-were reminded of the rank they had given to that perso and informed
-that this participant would be invited back and could earn a \$1 bonus if they
-guessed their rank correctly. The rank was determined by the aggregate ratings
-of all participants who had ranked this group. Their task was to give advice
-to this participant about the rank they should bet on based on having observed
-all ten selfies and their own assessment. We randomly assigned participants to
-one of two incentivization schemes. In the "Accuracy" treatment, they received
-a bonus identical to the advisee: \$1 if they guessed their rank correctly.
-In the "Likeability" treatment, we informed them that they would be rated by
-the advisee on a 5-point Likert scale for how likeable they thought they were.
-Each point on the scale would translate to a bonus of 20 cents. They then
-selected a rank that they would recommend the advisee to bet on.
+After submitting their ratings, they saw the photo of the participant
+they had ranked as the 7th most attractive (i.e., the 4th least
+attractive). They were reminded of the rank they had given to that perso
+and informed that this participant would be invited back and could earn
+a \$1 bonus if they guessed their rank correctly. The rank was
+determined by the aggregate ratings of all participants who had ranked
+this group. Their task was to give advice to this participant about the
+rank they should bet on based on having observed all ten selfies and
+their own assessment. We randomly assigned participants to one of two
+incentivization schemes. In the "Accuracy" treatment, they received a
+bonus identical to the advisee: \$1 if they guessed their rank
+correctly. In the "Likeability" treatment, we informed them that they
+would be rated by the advisee on a 5-point Likert scale for how likeable
+they thought they were. Each point on the scale would translate to a
+bonus of 20 cents. They then selected a rank that they would recommend
+the advisee to bet on.
 
@@
 1 and informed that a group of 10 selfies, including theirs, had been
-rated by other participants from Prolific. They then saw the advice from a 
-randomly selected adviser and made their estimate with a \$1 incentive for
-guessing accurately. They then saw the rank they had been advised to bet on
-one more time and were asked
-to rate the adviser's likability, warmth, friendliness,
-good-naturedness, trustworthiness, and sincerity on 5-point Likert scales
-(adapted from @Fiske2007).
+rated by other participants from Prolific. They then saw the advice from
+a randomly selected adviser and made their estimate with a \$1 incentive
+for guessing accurately. They then saw the rank they had been advised to
+bet on one more time and were asked to rate the adviser's likability,
+warmth, friendliness, good-naturedness, trustworthiness, and sincerity
+on 5-point Likert scales (adapted from @Fiske2007).
 
@@
     geom_violin(trim = FALSE) +
-     scale_fill_manual(values = c("firebrick3",'dodgerblue3'), labels = c("Accurate", "Likable")) +
+     scale_fill_manual(values = c("#2A629A",'#FF7F3E'), labels = c("Accurate", "Likable")) +
   geom_hline(yintercept = 7, col = 'grey', linetype = 'dashed', linewidth = 0.7) +
@@
 
-We begin by examining the prior beliefs of advisees who uploaded their selfies.
-On average, men guessed they ranked `r round(mean(study2_time1[study2_time1$gender == "Male",]$Guess),2)` in their group of 10 and women guessed that they ranked
+We begin by examining the prior beliefs of advisees who uploaded their
+selfies. On average, men guessed they ranked
+`r round(mean(study2_time1[study2_time1$gender == "Male",]$Guess),2)` in
+their group of 10 and women guessed that they ranked
 `r round(mean(study2_time1[study2_time1$gender == "Female",]$Guess),2)`.
-Participants overall underestimate their attractiveness relative to the benchmark
-average of 5.5. Moreover, women do so more than men
+Participants overall underestimate their attractiveness relative to the
+benchmark average of 5.5. Moreover, women do so more than men
 `r papaja::apa_print(t.test(Guess ~ gender, data = study2_time1, var.equal = T))$statistic`.
-Notably, people's self-perceptions correlated strongly with the aggregate
-ratings of the advisers (`r round(cor(study2_finalRank$Guess, study2_finalRank$finalRank),2)`, `r papaja::apa_print(cor.test(study2_finalRank$Guess, study2_finalRank$finalRank))$statistic`).
-However, there
-was substantial heterogeneity in perceptions of attractiveness.
-Of the 200 participants, `r length(unique(study2_time2$Target))` were ranked as 7th most attractive by at least one adviser. 
-On average, men in this subset estimated they were ranked `r round(mean(TargetsUnique[TargetsUnique$gender == 'Male',]$Guess),2)`th and women estimated they were
-ranked `r round(mean(TargetsUnique[TargetsUnique$gender == 'Female',]$Guess),2)`th (`r papaja::apa_print(t.test(Guess ~ gender, data = TargetsUnique, var.equal = T))$statistic`).
+Notably, people's self-perceptions correlated strongly with the
+aggregate ratings of the advisers
+(`r round(cor(study2_finalRank$Guess, study2_finalRank$finalRank),2)`,
+`r papaja::apa_print(cor.test(study2_finalRank$Guess, study2_finalRank$finalRank))$statistic`).
+However, there was substantial heterogeneity in perceptions of
+attractiveness. Of the 200 participants,
+`r length(unique(study2_time2$Target))` were ranked as 7th most
+attractive by at least one adviser. On average, men in this subset
+estimated they were ranked
+`r round(mean(TargetsUnique[TargetsUnique$gender == 'Male',]$Guess),2)`th
+and women estimated they were ranked
+`r round(mean(TargetsUnique[TargetsUnique$gender == 'Female',]$Guess),2)`th
+(`r papaja::apa_print(t.test(Guess ~ gender, data = TargetsUnique, var.equal = T))$statistic`).
 
-Next, we turn our attention to the advisers (Figure \@ref(fig:study2advice)). 
-In the Accuracy condition, those
-uploading selfies were advised to bet on rank `r round(mean(study2_time2[study2_time2$Condition == "Accurate",]$Advice),2)`.
-Notably, this is significantly more attractive than the 7th rank those advisers
-had themselves guessed just on the prior screen
+Next, we turn our attention to the advisers (Figure
+\@ref(fig:study2advice)). In the Accuracy condition, those uploading
+selfies were advised to bet on rank
+`r round(mean(study2_time2[study2_time2$Condition == "Accurate",]$Advice),2)`.
+Notably, this is significantly more attractive than the 7th rank those
+advisers had themselves guessed just on the prior screen
 (`r papaja::apa_print(t.test(study2_time2[study2_time2$Condition == "Accurate",]$Advice, mu = 7, var.equal = T))$statistic`).
-This suggests that even when incentivized for accuracy, participants offered
-flattering advice.^[This shading could be due to concerns of avoiding disappointment.
-However, it could also be that advisers are uncertain about the rankings they had given and make a recommendation that combines their own belief with a uniform prior.]
-Importantly, and as predicted, we find that advisers in the Likeable treatment
-recommend betting on a lower rank, communicating that they think the participant
-in the selfie is more attractive
+This suggests that even when incentivized for accuracy, participants
+offered flattering advice.[^3] Importantly, and as predicted, we find
+that advisers in the Likeable treatment recommend betting on a lower
+rank, communicating that they think the participant in the selfie is
+more attractive
 (`r round(mean(study2_time2[study2_time2$Condition == "Likable",]$Advice),2)`,
@@
 therefore provided advice that communicated a more favorable impression
-of the participants' attractiveness. The distribution shown in Figure \@ref(fig:study2advice)
-shows that participants do not simply tell participants that they are the
-most attractive person in the group. They may infer that flattering advise needs
-to be somewhat realistic to be believable. We return to this in the general discussion.
+of the participants' attractiveness. The distribution shown in Figure
+\@ref(fig:study2advice) shows that participants do not simply tell
+participants that they are the most attractive person in the group. They
+may infer that flattering advise needs to be somewhat realistic to be
+believable. We return to this in the general discussion.
+
+[^3]: This shading could be due to concerns of avoiding disappointment.
+    However, it could also be that advisers are uncertain about the
+    rankings they had given and make a recommendation that combines
+    their own belief with a uniform prior.
 
 <!-- David: Making a note here that we should be sure to discuss this at the end -->
+
 <!-- as something for future research. -->
@@
 <!-- David: We should also report something on accuracy of the advice given across -->
+
 <!-- the treatments. Even if no difference. -->
@@
 <!-- Amanda: How about this -->
+
 <!-- For warmth it looks interesting, but I think the plot is hard -->
+
 <!-- to read. Let's hold off on this for now. -->
 
-Finally, we examine whether flattering advice indeed leads to more positive evaluations of
-advisers, or whether flattering advice is dismissed as insencere.
-Following our preregistration, we average the ratings on likeability,
-warmth,  friendliness, and good-naturedness to create a scale of likeability
-($\alpha$ = `r cronbach.alpha(study2_time3[, 5:8])$alpha`); and we create a scale of trustworthiness by averaging the ratings of trustworthiness and sincerity ($\alpha$ = `r cronbach.alpha(study2_time3[, 9:10])$alpha`).
+Finally, we examine whether flattering advice indeed leads to more
+positive evaluations of advisers, or whether flattering advice is
+dismissed as insencere. Following our preregistration, we average the
+ratings on likeability, warmth, friendliness, and good-naturedness to
+create a scale of likeability ($\alpha$ =
+`r cronbach.alpha(study2_time3[, 5:8])$alpha`); and we create a scale of
+trustworthiness by averaging the ratings of trustworthiness and
+sincerity ($\alpha$ = `r cronbach.alpha(study2_time3[, 9:10])$alpha`).
 
 <!-- The Figure is not super clear. How about we try a series of box plots, -->
+
 <!-- with the x-axis as the advised rank? Standard errors will be huge at the -->
+
 <!-- extremes. -->
@@
 <!-- Also, we need to do something relative to the advisees' expectations. -->
+
 <!-- I wonder what would be interesting here? Maybe averages for three groups: -->
+
 <!-- more attractive than the participants' own guess, equally attractive, and less -->
+
 <!-- attractive? -->
@@
 <!-- Amanda: How about the following picture? -->
+
 ```{r study2rating, fig.cap="Participants tend to rate advisors who suggest betting on a higher rank (implying greater attractiveness) as more likable and warm."}
@@
 plot1 <- ggplot(study2_time3, aes(x = Advice)) +
-  geom_boxplot(aes(y = likable),position = position_dodge(width = 0.8), alpha = 0.8, color = "black", fill = "firebrick3") +
+  geom_boxplot(aes(y = likable),position = position_dodge(width = 0.8), alpha = 0.8, color = "darkgrey", fill = "#2A629A") +
   scale_y_continuous(name = "Likability") +
@@
 plot2 <- ggplot(study2_time3, aes(x = Advice)) +
-  geom_boxplot(aes(y = warmAvg),position = position_dodge(width = 0.8), alpha = 0.8, color = "black", fill = "dodgerblue3") +
+  geom_boxplot(aes(y = warmAvg),position = position_dodge(width = 0.8), alpha = 0.8, color = "darkgrey", fill = "#FF7F3E") +
   scale_y_continuous(name = "Warmth") +
@@
   geom_bar(stat = "identity", position = "dodge") +
-  scale_fill_manual(values = c("firebrick3",'dodgerblue3')) +
+  scale_fill_manual(values = c("#2A629A",'#FF7F3E')) +
   labs(x = "Advice", y = "Rating") +
@@
 
-As seen in Figure \@ref(fig:study2rating), we
-found that advisees who suggested that the advisee was more attractive
-(lower rank) were indeed rated as more likeable and warm (b = -0.109, p
-\< .05; b = -0.133, p \< .001, respectively; See Columns 1 and 2 of Table \@ref(tab:study2regs)).
-When using their self-expectations as a reference point, advisors who suggest a rank lower than that point are perceived as less likable and warm (see Figure \@ref(fig:study2ratingByGroup)).
-Interestingly, these benefits are not at the cost of being hypocritical;
-advisers who recommend a more favorable rank are viewed as no less trustworthy
+As seen in Figure \@ref(fig:study2rating), we found that advisees who
+suggested that the advisee was more attractive (lower rank) were indeed
+rated as more likeable and warm (b = -0.109, p \< .05; b = -0.133, p \<
+.001, respectively; See Columns 1 and 2 of Table \@ref(tab:study2regs)).
+When using their self-expectations as a reference point, advisors who
+suggest a rank lower than that point are perceived as less likable and
+warm (see Figure \@ref(fig:study2ratingByGroup)). Interestingly, these
+benefits are not at the cost of being hypocritical; advisers who
+recommend a more favorable rank are viewed as no less trustworthy
 (Column 3 of Table \@ref(tab:study2regs)).
 
-We were not powered to do a comparison across the two 
-experimental groups and did not preregister such a difference. Indeed, we find
-no difference in likeability and warmth across the two treatments 
+We were not powered to do a comparison across the two experimental
+groups and did not preregister such a difference. Indeed, we find no
+difference in likeability and warmth across the two treatments
 (`r papaja::apa_print(t.test(likable ~ Condition, data = study2_time3, var.equal = T))$statistic`,
-and `r papaja::apa_print(t.test(warmAvg ~ Condition, data = study2_time3, var.equal = T))$statistic`, 
+and
+`r papaja::apa_print(t.test(warmAvg ~ Condition, data = study2_time3, var.equal = T))$statistic`,
 respectively).
@@
 ## Discussion
-In a context where advice communicates ego-relevant information (here, people's
-attractiveness), we find that the advice people give is contingent on their
-incentives. Specifically, when they get rewarded for being more likeable, they
-recommend that the advisee bet on a more favorable rank than when they are
-incentivized for accuracy. Importantly, advisees do not discount flattering
-advice and instead evaluate people who advise them to bet on a more attractive
-rank as warmer and more likeable. These gains to interpersonal perceptions do
-not come at the cost of trustworthiness, even when the advice is substantially
-inflated (e.g., a recommendation that the advisee is the most attractive in the group).
+
+In a context where advice communicates ego-relevant information (here,
+people's attractiveness), we find that the advice people give is
+contingent on their incentives. Specifically, when they get rewarded for
+being more likeable, they recommend that the advisee bet on a more
+favorable rank than when they are incentivized for accuracy.
+Importantly, advisees do not discount flattering advice and instead
+evaluate people who advise them to bet on a more attractive rank as
+warmer and more likeable. These gains to interpersonal perceptions do
+not come at the cost of trustworthiness, even when the advice is
+substantially inflated (e.g., a recommendation that the advisee is the
+most attractive in the group).
 
 # General Discussion
+
 Advice has the potential to shape people's career and personal outcomes.
-Honest feedback, however, may be painful to learn if it falls short of one's
-expectations. As prior work notes, this may motivate people to avoid information 
-and avoid seeking help [@Benabou2022; @Golman2017; @Jaroszewicz2022].
-We present evidence from two experiments that advisers are also cognizant of this
-cost. As a result, they present flattering advice that avoids disappointing the
-recipient, and correctly anticipate that this boosts how advisees perceive them.
-However, this flattering advice comes at a cost to advisees, who would do worse
-if they followed it blindly, as we show in Study 1.
+Honest feedback, however, may be painful to learn if it falls short of
+one's expectations. As prior work notes, this may motivate people to
+avoid information and avoid seeking help [@Benabou2022; @Golman2017;
+@Jaroszewicz2022]. We present evidence from two experiments that
+advisers are also cognizant of this cost. As a result, they present
+flattering advice that avoids disappointing the recipient, and correctly
+anticipate that this boosts how advisees perceive them. However, this
+flattering advice comes at a cost to advisees, who would do worse if
+they followed it blindly, as we show in Study 1.
 
-Moreover, a desire to avoid disappointment also means that advisers have to
-take into account the expectations of the advisee. 
-We document that men are more optimistic about their performance than
-women are. As a result, they receive more flattering advice and are more likely
-to be told to aim higher. Notably, in the context of our experiment, this turns
-out to be bad advice ex post.
+Moreover, a desire to avoid disappointment also means that advisers have
+to take into account the expectations of the advisee. We document that
+men are more optimistic about their performance than women are. As a
+result, they receive more flattering advice and are more likely to be
+told to aim higher. Notably, in the context of our experiment, this
+turns out to be bad advice ex post.
 
-Our findings have implications for organizational practice, where mentoring
-and advice-giving may take into account an employees' expectation. We
-document this as a novel source of gender bias. Organizations could reduce
-this bias by calibrating employees' expectations to reduce overconfidence.
+Our findings have implications for organizational practice, where
+mentoring and advice-giving may take into account an employees'
+expectation. We document this as a novel source of gender bias.
+Organizations could reduce this bias by calibrating employees'
+expectations to reduce overconfidence.
 
-Participants in our experiment were paired anonymously. Even so, we document
-this desire to avoid disappointment. We anticipate that advice would be more
-flattering in face-to-face communication and without anonymity. Moreover,
-existing relationships might make it even more difficult for advisers to be
-honest.
+Participants in our experiment were paired anonymously. Even so, we
+document this desire to avoid disappointment. We anticipate that advice
+would be more flattering in face-to-face communication and without
+anonymity. Moreover, existing relationships might make it even more
+difficult for advisers to be honest.
 
-In our experiments, participants only received advice once and did not evaluate
-the adviser after observing the outcome of their decision.
-For example, advice that leads to bad outcomes may undermine the
-interpersonal benefits of flattery. Alternatively, people may still like the
-flattering advice and not fault the adviser for the bad outcome.
-Moreover, our setting involved only a single piece of advice on one task.
-Future research could examine whether people return to those who gave them
-flattering advice, or if they prefer someone who gave them the honest
-(but unpleasant) truth.
+In our experiments, participants only received advice once and did not
+evaluate the adviser after observing the outcome of their decision. For
+example, advice that leads to bad outcomes may undermine the
+interpersonal benefits of flattery. Alternatively, people may still like
+the flattering advice and not fault the adviser for the bad outcome.
+Moreover, our setting involved only a single piece of advice on one
+task. Future research could examine whether people return to those who
+gave them flattering advice, or if they prefer someone who gave them the
+honest (but unpleasant) truth.
 
-Advice has long been studied from the perspective of the receiver. Similarly,
-research on belief utility has examined how recipients respond to the valence
-of the information they receive. Here, we show that advisers, too, take into
-account the psychological impact of the information they convey. They may have
-even greater motivations to avoid conveying bad news, because they incur the
-interpersonal costs of delivering unfavorable information without reaping the
-benefits from helping someone make a better choice.
+Advice has long been studied from the perspective of the receiver.
+Similarly, research on belief utility has examined how recipients
+respond to the valence of the information they receive. Here, we show
+that advisers, too, take into account the psychological impact of the
+information they convey. They may have even greater motivations to avoid
+conveying bad news, because they incur the interpersonal costs of
+delivering unfavorable information without reaping the benefits from
+helping someone make a better choice.
 

### 2024-09-20 R/clean_study1_time1.R

@@ -9,10 +9,11 @@ Advisee <- data.table::fread(here::here("Data/Raw Data/S1_time1.csv"),
   dplyr::mutate(Guess = coalesce(Guess, Guess_L)) %>%
   dplyr::mutate(Guess = ifelse(Guess == "Compete against the High Performer Group",1,0)) %>%
   dplyr::select(PROLIFIC_PID,Guess,default,Score,Age,Gender, Ethnicity,Education) %>%
+  dplyr::rename("ProlificID" = "PROLIFIC_PID") %>%
   dplyr::mutate(Score = as.numeric(Score))
 
 
 saveRDS(Advisee, file = here::here("Data/Study1_time1.Rds"))
-Advisee %>% write.csv("Data/Cleaned Data/S1_time1_cleaned.csv")
+Advisee %>% write.csv("Data/Cleaned Data/S1_time1_clean.csv")
 
 

### 2024-09-20 manuscript/manuscript.Rmd
Before Abstract

@@
   The purpose of advice is to help recipients make better decisions and solve their problems.
-However, in this paper, we propose that advisors may also take recipients' responses into account and attempt to avoid disappointing them, leading to what we call "flattering advice." In two pre-registered experiments involving real interactions between advisors and advisees (n = 2,700), we show that individuals consider others' expectations when giving advice, even when such expectations do not provide informative insights for the underlying decision-making problem.
+However, in this paper, we propose that advisors may also take recipients' responses into account and attempt to avoid disappointing them, leading to what we call "flattering advice." In three pre-registered experiments involving real interactions between advisors and advisees (n = 3,900), we show that individuals consider others' expectations when giving advice, even when such expectations do not provide informative insights for the underlying decision-making problem.
 As a result, men receive more aspirational advice than women, given their higher confidence, when expectations (but not gender) are shown to advisors.
-However, incorporating expectations leads to worse outcomes (Study 1).
 Individuals inflate their advice due to interpersonal considerations: people who are concerned about advisees' likability inflate their advice to a great extent.
 Advisees reward such flattering advice, finding the advisers more likable and no less trustworthy than those who provide more accurate advice (Study 2).
+However, incorporating expectations leads to worse outcomes (Study 3).
 We discuss practical and theoretical contributions and future research directions.

### 2024-09-20 R/clean_study1_time3.R

@@ -1,0 +1,24 @@
+library(dplyr)
+library(ggplot2)
+library(magrittr)
+
+
+Target <- read.csv("Data/Cleaned Data/S1_time1_clean.csv")[-c(1,3)]
+
+
+
+Receiver <- data.table::fread(here::here("Data/Raw Data/S1_time3.csv"),
+                              header = T,na.strings = '')[-c(1,2)]  %>%
+dplyr::filter(Progress == '100' & Status == 'IP Address') %>%
+  dplyr::rename('ProlificID' = 'Q3', 'Advice' = '0.Advice','GiverID' = '0.GiverID','IntGuess' = 'Guess',
+                'GiverCondition' = '0.Condition') %>%
+  dplyr::mutate(Bet = case_when(bet == 'Compete against the Low Performer Group' ~ 0,
+                                bet == 'Compete against the High Performer Group' ~ 1)) %>%
+  dplyr::select(ProlificID,Bet, IntGuess, Advice, GiverID, GiverCondition) %>%
+  dplyr::mutate(GiverCondition = case_when(GiverCondition == 'E' ~ 1,
+                                           GiverCondition == 'None' ~ 0))
+
+Receiver <- merge(Receiver,Target,by = 'ProlificID')
+
+saveRDS(Receiver, file = here::here("Data/Study1_time3.Rds"))
+Receiver %>% write.csv("Data/Cleaned Data/S1_time3_clean.csv")

### 2024-09-21 manuscript/manuscript.Rmd
Abstract

--- 2024-09-20 manuscript/manuscript.Rmd
@@
 abstract: |
-  The purpose of advice is to help recipients make better decisions and solve their problems.
-However, in this paper, we propose that advisors may also take recipients' responses into account and attempt to avoid disappointing them, leading to what we call "flattering advice." In two pre-registered experiments involving real interactions between advisors and advisees (n = 2,700), we show that individuals consider others' expectations when giving advice, even when such expectations do not provide informative insights for the underlying decision-making problem.
-As a result, men receive more aspirational advice than women, given their higher confidence, when expectations (but not gender) are shown to advisors.
-However, incorporating expectations leads to worse outcomes (Study 1).
-Individuals inflate their advice due to interpersonal considerations: people who are concerned about advisees' likability inflate their advice to a great extent.
-Advisees reward such flattering advice, finding the advisers more likable and no less trustworthy than those who provide more accurate advice (Study 2).
-We discuss practical and theoretical contributions and future research directions.
+  The purpose of advice is typically understood as helping recipients make better decisions and solve problems.
+However, in this paper, we propose that advisors also consider the recipient's belief utility and may try to avoid disappointing them, leading to what we term "flattering advice." Across three pre-registered experiments involving real interactions between advisors and advisees (n = 3,900), we demonstrate that individuals factor in others' expectations when giving advice, even when those expectations are not relevant to solving the decision-making problem.
+Specifically, advisors take advisees' expectations into account, tailoring their advice to create a more positive impression of the advisee and avoid causing disappointment.
+(Study 1).
+Advisors inflate their advice due to interpersonal concerns, with those who care about being liked by the advisee inflating their advice to a greater extent.
+Advisees, in turn, reward this flattery, perceiving these advisors as more likable and equally trustworthy compared to those who give more accurate advice (Study 2).
+Additionally, when advisors match advisees' expectations, men tend to receive more aspirational advice than women, due to their higher confidence, even when only expectations (not gender) are visible to the advisor.
+However, relying on these expectations leads to poorer decision outcomes (Study 3).
+We conclude by discussing the practical and theoretical implications of our findings, as well as directions for future research.
+
 keywords          : "Gender difference, Advice, Interpresonal relationship"
@@
    - \usepackage{tabularx, epigraph, float, colortbl, tabu, pdflscape}
+   - \usepackage{tabularray}
    - \usetikzlibrary{positioning}
@@
 library(ltm)
+library(ggplot2)
+library(gridExtra)
+library(dplyr)
 
@@
 
-study3_math50 <- read.csv(here::here("Data/Cleaned Data/S3_Math50_cleaned.csv"))
-study3_time1All <- readRDS(here::here("Data/Study3_time1All.Rds"))
-study3_time1 <- readRDS(here::here("Data/Study3_time1.Rds"))
-study3_time2_giver <- readRDS(here::here("Data/Study3_time2_giver.Rds"))
-study3_time2_giver50 <- readRDS(here::here("Data/Study3_time2_giver50.Rds"))
-study3_advice <- readRDS(here::here("Data/Study3_time2_advice.Rds"))
-study3_time3 <- readRDS(here::here("Data/Study3_time3.Rds"))
+study1_time1 <- readRDS(here::here("Data/Study1_time1.Rds"))
+study1_time2_giver <- readRDS(here::here("Data/Study1_time2_giver.Rds"))
+study1_time2_advice <- readRDS(here::here("Data/Study1_time2_advice.Rds"))
+study1_time3 <- readRDS(here::here("Data/Study1_time3.Rds"))
 
@@
 
-We report all sample sizes, data exclusions, manipulations, and measures
-in the studies. Screen captures of the experimental materials are
-available in the Supplemental Information. The complete data, code to
-reproduce all statistical analyses and figures in the manuscript, as
-well as the preregistration reports will be available via OSF. All our
-studies were preregistered on AsPredicted.org.
-
-<!-- ^[<https://osf.io/8r3d4/?view_only=5ad7bafcd16b4d4ba08bb28b0e2bd02d>] -->
-
-<!-- Commenting this out for IACM -->
+We report all manipulations, measures, and data exclusion in this and the following study.
+The preregistration reports, screenshots of all experimental materials, and the analysis code to replicate all statistical analyses and figures are available on the Open Science Framework
+(<https://osf.io/8r3d4/?view_only=5ad7bafcd16b4d4ba08bb28b0e2bd02d>).
 
 # Study 1
+
+# Study 2
+
+<!-- David: Just commenting on what I tried to do here... a bit of a transition -->
+
+<!-- for why this study follows from the last. -->
+
+So far, we have shown that displaying expectations can induce gender
+differences in advice-giving. Specifically, advisers were more likely to
+recommend competing against a group of High Performers to men who had
+higher expectations about their performance than did women. We now test
+directly whether this is driven by interpersonal concerns. Specifically,
+we examine whether more flattering advice is the result of a desire to
+be liked and whether advisees indeed do like advisers more when they
+give flattering advice.
+
+We conducted a three-stage experiment in which we experimentally
+manipulated the incentives for advicers. We began by inviting a group of
+advisees to upload photos of themselves ("selfies") and informed them
+that they would be rated on their attractiveness. We grouped them with
+nine other participants of the same gender and recruited participants of
+the opposing gender to rank them from most to least attractive and to
+provide advice. Specifically, we asked them to advise the participant
+they ranked as the 7th most attractive (4th least attractive) on what
+rank they should bet they were ranked by a larger group of raters.
+Advisers were randomly assigned to two treatments, receiving a bonus
+payment either if the advisee guessed their rank accurately or if the
+advisee evaluated the adviser as likeable as measured by an
+unincentivized scale response. We hypothesize that advisers who want to
+be liked by advisees will recommend that they bet on a lower rank, i.e.
+that they are more attractive.
+
+```{r}
+
+study2_time1 <- readRDS(here::here("Data/Study2_time1.Rds"))
+study2_time1_200 <- readRDS(here::here("Data/Study2_time1_200.Rds"))
+study2_time2 <- readRDS(here::here("Data/Study2_time2.Rds"))
+study2_finalRank <- readRDS(here::here("Data/Study2_finalRank.Rds"))
+study2_time3 <- readRDS(here::here("Data/Study2_time3.Rds"))
+
+```
+
+## Methods
+
+We recruited 300 participants from Prolific and, after asking
+demographic questions, invited them to upload photos of themselves
+(selfies) to be rated by other participants on attractiveness.
+`r scales::comma(dim(study2_time1[study2_time1$gender == 'Male',])[1])`
+men and
+`r scales::comma(dim(study2_time1[study2_time1$gender == 'Female',])[1])`
+women agreed to do so and uploaded pictures that adhered to our
+instructions (e.g., did not include other people). We selected the first
+100 photos from women to arrive at a gender-balanced sample
+($M_{\text{Age}}$ = `r mean(study2_time1_200$age)` years). Participants
+were informed that their selfies would be randomly grouped with those of
+nine other participants of their gender and ranked in terms of
+attractiveness by a group of new Prolific participants of the opposite
+gender. Lastly, they guessed their rank (unincentivized).
+
+Next, we recruited a new, gender-balanced sample for the role of
+advisers. `r scales::comma(dim(study2_time2)[1])` participants from
+Prolific ($M_{\text{Age}}$ = `r mean(study2_time2$age)` years;
+`r round(mean(study2_time2$gender == "Female")*100, 2)`% Female) started
+by providing demographic information, then were matched to a group of
+the opposite gender. They then ranked participants from most to least
+attractive using a drop-down menu next to each picture. Because of a
+limitation with the survey software, participants were able to select
+the same rank for multiple participants, rather than rank them uniquely.
+We remove 115 participants who did not follow instructions and provide a
+unique ranking.
+
+After submitting their ratings, they saw the photo of the participant
+they had ranked as the 7th most attractive (i.e., the 4th least
+attractive). They were reminded of the rank they had given to that perso
+and informed that this participant would be invited back and could earn
+a \$1 bonus if they guessed their rank correctly. The rank was
+determined by the aggregate ratings of all participants who had ranked
+this group. Their task was to give advice to this participant about the
+rank they should bet on based on having observed all ten selfies and
+their own assessment. We randomly assigned participants to one of two
+incentivization schemes. In the "Accuracy" treatment, they received a
+bonus identical to the advisee: \$1 if they guessed their rank
+correctly. In the "Likeability" treatment, we informed them that they
+would be rated by the advisee on a 5-point Likert scale for how likeable
+they thought they were. Each point on the scale would translate to a
+bonus of 20 cents. They then selected a rank that they would recommend
+the advisee to bet on.
+
+Finally, we invited participants from Stage 1 and were ranked as the 7th
+attractive by at least one adviser (so that they received advice) back
+for the follow-up survey. Following our preregistration, we kept the
+survey open for 7 days. In total,
+`r scales::comma(dim(study2_time3)[1])` participants
+(`r scales::comma(dim(study2_time3[study2_time3$gender == 'Male',])[1])`
+men,
+`r scales::comma(dim(study2_time3[study2_time3$gender == 'Female',])[1])`
+women) returned. They were reminded of the selfie they uploaded in Stage
+1 and informed that a group of 10 selfies, including theirs, had been
+rated by other participants from Prolific. They then saw the advice from
+a randomly selected adviser and made their estimate with a \$1 incentive
+for guessing accurately. They then saw the rank they had been advised to
+bet on one more time and were asked to rate the adviser's likability,
+warmth, friendliness, good-naturedness, trustworthiness, and sincerity
+on 5-point Likert scales (adapted from @Fiske2007).
+
+## Results
+
+```{r}
+library(dplyr)
+
+TargetsUnique <- study2_time2 %>%
+  dplyr::select(Target) %>%
+  unique()
+
+TargetsUnique <- merge(TargetsUnique,study2_finalRank, by.x = 'Target', by.y = 'QID7_Id')
+
+```
+
+```{r study2advice, fig.cap="Advisers were asked to suggest what rank to bet on for someone they ranked as the 7th most attractive out of ten people.
+When incentivized for accuracy, most of them advised betting on 7, which was based on their evaluation of the recipient's attractiveness.
+However, when incentivized for likability, many participants gave flattering advice by suggesting betting on higher ranks that imply a higher evaluation of attractiveness."}
+
+study2_time2 <- study2_time2 %>% dplyr::mutate(Advice = as.numeric(Advice))
+
+ggplot(study2_time2, aes(x = Condition, y = Advice, fill = Condition)) +
+    geom_violin(trim = FALSE) +
+     scale_fill_manual(values = c("#2A629A",'#FF7F3E'), labels = c("Accurate", "Likable")) +
+  geom_hline(yintercept = 7, col = 'grey', linetype = 'dashed', linewidth = 0.7) +
+  scale_y_continuous(name = "Advised Rank", breaks = seq(1, 10)) +
+  theme_bw() +
+  theme(panel.grid = element_blank(),
+        panel.border = element_blank(),
+        axis.line = element_line(colour = "grey"),
+        legend.position = "bottom",
+        legend.title = element_blank(),
+        legend.key.size = unit(1.2, "lines"),
+        legend.text = element_text(size = 12),
+        plot.title = element_text(hjust = 0.5, size = 20))
+
+```
+
+We begin by examining the prior beliefs of advisees who uploaded their
+selfies. On average, men guessed they ranked
+`r round(mean(study2_time1[study2_time1$gender == "Male",]$Guess),2)` in
+their group of 10 and women guessed that they ranked
+`r round(mean(study2_time1[study2_time1$gender == "Female",]$Guess),2)`.
+Participants overall underestimate their attractiveness relative to the
+benchmark average of 5.5. Moreover, women do so more than men
+`r papaja::apa_print(t.test(Guess ~ gender, data = study2_time1, var.equal = T))$statistic`.
+Notably, people's self-perceptions correlated strongly with the
+aggregate ratings of the advisers
+(`r round(cor(study2_finalRank$Guess, study2_finalRank$finalRank),2)`,
+`r papaja::apa_print(cor.test(study2_finalRank$Guess, study2_finalRank$finalRank))$statistic`).
+However, there was substantial heterogeneity in perceptions of
+attractiveness. Of the 200 participants,
+`r length(unique(study2_time2$Target))` were ranked as 7th most
+attractive by at least one adviser. On average, men in this subset
+estimated they were ranked
+`r round(mean(TargetsUnique[TargetsUnique$gender == 'Male',]$Guess),2)`th
+and women estimated they were ranked
+`r round(mean(TargetsUnique[TargetsUnique$gender == 'Female',]$Guess),2)`th
+(`r papaja::apa_print(t.test(Guess ~ gender, data = TargetsUnique, var.equal = T))$statistic`).
+
+Next, we turn our attention to the advisers (Figure
+\@ref(fig:study2advice)). In the Accuracy condition, those uploading
+selfies were advised to bet on rank
+`r round(mean(study2_time2[study2_time2$Condition == "Accurate",]$Advice),2)`.
+Notably, this is significantly more attractive than the 7th rank those
+advisers had themselves guessed just on the prior screen
+(`r papaja::apa_print(t.test(study2_time2[study2_time2$Condition == "Accurate",]$Advice, mu = 7, var.equal = T))$statistic`).
+This suggests that even when incentivized for accuracy, participants
+offered flattering advice.[^3] Importantly, and as predicted, we find
+that advisers in the Likeable treatment recommend betting on a lower
+rank, communicating that they think the participant in the selfie is
+more attractive
+(`r round(mean(study2_time2[study2_time2$Condition == "Likable",]$Advice),2)`,
+`r papaja::apa_print(t.test(Advice ~ Condition, data = study2_time2, var.equal = T))$statistic`).
+This suggests that advisers inferred that advising someone that they
+were more attractive would make the adviser appear more likeable and
+therefore provided advice that communicated a more favorable impression
+of the participants' attractiveness. The distribution shown in Figure
+\@ref(fig:study2advice) shows that participants do not simply tell
+participants that they are the most attractive person in the group. They
+may infer that flattering advise needs to be somewhat realistic to be
+believable. We return to this in the general discussion.
+
+[^3]: This shading could be due to concerns of avoiding disappointment.
+    However, it could also be that advisers are uncertain about the
+    rankings they had given and make a recommendation that combines
+    their own belief with a uniform prior.
+
+<!-- David: Making a note here that we should be sure to discuss this at the end -->
+
+<!-- as something for future research. -->
+
+<!-- David: We should also report something on accuracy of the advice given across -->
+
+<!-- the treatments. Even if no difference. -->
+
+```{r study2regs}
+
+modelsummary::modelsummary(list(`(1)` = lm(likable ~ Advice, data = study2_time3),
+                                `(2)` = lm(warmAvg ~ Advice, data = study2_time3),
+                                `(3)` = lm(trustAvg ~ Advice, data = study2_time3)),
+                           vcov = c("classical", "classical", "classical"),
+                           coef_map = c("Advice" = "Advised Rank",
+                                        "(Intercept)" = "Constant"),
+                           stars = T,
+                           gof_map = list(list('raw' = 'nobs', 'clean' = 'N', 'fmt' = 0)),
+                           caption = "When individuals receive advice that implies a high level of attractiveness (lower rank), they tend to perceive the advice giver as more likable (Column 1), warm (Column 2).
+Column 3 shows that advisors are rated as more trustworthy when they advice lower ranks, but this relationship is only directional.")
+
+```
+
+<!-- Amanda: How about this -->
+
+<!-- For warmth it looks interesting, but I think the plot is hard -->
+
+<!-- to read. Let's hold off on this for now. -->
+
+Finally, we examine whether flattering advice indeed leads to more
+positive evaluations of advisers, or whether flattering advice is
+dismissed as insencere. Following our preregistration, we average the
+ratings on likeability, warmth, friendliness, and good-naturedness to
+create a scale of likeability ($\alpha$ =
+`r cronbach.alpha(study2_time3[, 5:8])$alpha`); and we create a scale of
+trustworthiness by averaging the ratings of trustworthiness and
+sincerity ($\alpha$ = `r cronbach.alpha(study2_time3[, 9:10])$alpha`).
+
+<!-- The Figure is not super clear. How about we try a series of box plots, -->
+
+<!-- with the x-axis as the advised rank? Standard errors will be huge at the -->
+
+<!-- extremes. -->
+
+<!-- Also, we need to do something relative to the advisees' expectations. -->
+
+<!-- I wonder what would be interesting here? Maybe averages for three groups: -->
+
+<!-- more attractive than the participants' own guess, equally attractive, and less -->
+
+<!-- attractive? -->
+
+<!-- Amanda: How about the following picture? -->
+
+```{r study2rating, fig.cap="Participants tend to rate advisors who suggest betting on a higher rank (implying greater attractiveness) as more likable and warm."}
+
+study2_time3 <- study2_time3 %>% dplyr::mutate(Advice = as.factor(Advice))
+
+# Create the first plot
+plot1 <- ggplot(study2_time3, aes(x = Advice)) +
+  geom_boxplot(aes(y = likable),position = position_dodge(width = 0.8), alpha = 0.8, color = "darkgrey", fill = "#2A629A") +
+  scale_y_continuous(name = "Likability") +
+  scale_x_discrete(name = "Advised Rank") +
+  theme_bw() +
+  theme(panel.grid = element_blank(),
+        panel.border = element_blank(),
+        axis.line = element_line(colour = "grey"),
+        legend.position = "bottom",
+        legend.title = element_blank(),
+        legend.key.size = unit(1.2, "lines"),
+        legend.text = element_text(size = 12),
+        plot.title = element_text(hjust = 0.5, size = 20))
+
+# Create the second plot
+plot2 <- ggplot(study2_time3, aes(x = Advice)) +
+  geom_boxplot(aes(y = warmAvg),position = position_dodge(width = 0.8), alpha = 0.8, color = "darkgrey", fill = "#FF7F3E") +
+  scale_y_continuous(name = "Warmth") +
+  scale_x_discrete(name = "Advised Rank") +
+  theme_bw() +
+  theme(panel.grid = element_blank(),
+        panel.border = element_blank(),
+        axis.line = element_line(colour = "grey"),
+        legend.position = "bottom",
+        legend.title = element_blank(),
+        legend.key.size = unit(1.2, "lines"),
+        legend.text = element_text(size = 12),
+        plot.title = element_text(hjust = 0.5, size = 20))
+
+# Combine the plots side by side
+grid.arrange(plot1, plot2, ncol = 2)
+
+```
+
+```{r study2ratingByGroup, fig.cap="After participants received advice that suggested betting on a rank that was lower than, equal to, or higher than their self-expectations, they evaluated advisors based on their likability and warmth.
+Participants rated advisors who gave flattering advice and delivered a high evaluation of their attractiveness as more likable and warm than those whose advice implied a lower evaluation of their attractiveness."}
+
+library(dplyr)
+library(ggplot2)
+
+study2_time3 <- study2_time3 %>% dplyr::mutate(Guess = as.numeric(Guess), Advice = as.numeric(Advice)) %>%
+  dplyr::mutate(HorL = ifelse(Guess == Advice,0, ifelse(Guess > Advice, 1,-1))) %>%
+  dplyr::mutate(HorL = as.factor(HorL)) %>% 
+  dplyr::mutate(bonus = ifelse(bet == `Final Rank`,1,0))
+
+ratings <- study2_time3 %>%
+  group_by(HorL) %>%
+  summarise(like = mean(likable), warmth = mean(warmAvg))
+
+rating_table <- matrix(c(ratings$like,ratings$warmth), nrow = 2, byrow = TRUE, dimnames = list( c("Likable",'Warm'),c("Pessimistic", "Accurate", "Flattering")))
+
+rating_df = as.data.frame.table(rating_table) %>%
+  dplyr::rename( 'Condition'='Var1', 'Advice' ='Var2') %>%
+  dplyr::mutate(Freq = round(Freq,2))
+
+ggplot(rating_df, aes(x = Advice, y = Freq, fill = Condition)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  scale_fill_manual(values = c("#2A629A",'#FF7F3E')) +
+  labs(x = "Advice", y = "Rating") +
+  ggtitle('Response to Advice') +
+  theme_bw() +
+  theme(panel.grid = element_blank(),
+        panel.border = element_blank(),
+        axis.line = element_line(colour = "grey"),
+        legend.position = "bottom",
+        legend.title = element_blank(),
+        legend.key.size = unit(1.2, "lines"),          
+        legend.text = element_text(size = 12),
+        plot.title = element_text(hjust = 0.5, size = 20)) +
+  geom_text(aes(label = paste0(Freq), y = 0.5), position = position_dodge(width = 0.9), size = 5, color = 'white', fontface = "bold")
+
+```
+
+As seen in Figure \@ref(fig:study2rating), we found that advisees who
+suggested that the advisee was more attractive (lower rank) were indeed
+rated as more likeable and warm (b = -0.109, p \< .05; b = -0.133, p \<
+.001, respectively; See Columns 1 and 2 of Table \@ref(tab:study2regs)).
+When using their self-expectations as a reference point, advisors who
+suggest a rank lower than that point are perceived as less likable and
+warm (see Figure \@ref(fig:study2ratingByGroup)). Interestingly, these
+benefits are not at the cost of being hypocritical; advisers who
+recommend a more favorable rank are viewed as no less trustworthy
+(Column 3 of Table \@ref(tab:study2regs)).
+
+We were not powered to do a comparison across the two experimental
+groups and did not preregister such a difference. Indeed, we find no
+difference in likeability and warmth across the two treatments
+(`r papaja::apa_print(t.test(likable ~ Condition, data = study2_time3, var.equal = T))$statistic`,
+and
+`r papaja::apa_print(t.test(warmAvg ~ Condition, data = study2_time3, var.equal = T))$statistic`,
+respectively).
+
+## Discussion
+
+In a context where advice communicates ego-relevant information (here,
+people's attractiveness), we find that the advice people give is
+contingent on their incentives. Specifically, when they get rewarded for
+being more likeable, they recommend that the advisee bet on a more
+favorable rank than when they are incentivized for accuracy.
+Importantly, advisees do not discount flattering advice and instead
+evaluate people who advise them to bet on a more attractive rank as
+warmer and more likeable. These gains to interpersonal perceptions do
+not come at the cost of trustworthiness, even when the advice is
+substantially inflated (e.g., a recommendation that the advisee is the
+most attractive in the group).
+
+# Study 3
+
+```{r}
+
+study3_math50 <- read.csv(here::here("Data/Cleaned Data/S3_Math50_cleaned.csv"))
+study3_time1All <- readRDS(here::here("Data/Study3_time1All.Rds"))
+study3_time1 <- readRDS(here::here("Data/Study3_time1.Rds"))
+study3_time2_giver <- readRDS(here::here("Data/Study3_time2_giver.Rds"))
+study3_time2_giver50 <- readRDS(here::here("Data/Study3_time2_giver50.Rds"))
+study3_advice <- readRDS(here::here("Data/Study3_time2_advice.Rds"))
+study3_time3 <- readRDS(here::here("Data/Study3_time3.Rds"))
+
+```
 
@@
 
-# Study 2
-
-<!-- David: Just commenting on what I tried to do here... a bit of a transition -->
-
-<!-- for why this study follows from the last. -->
-
-So far, we have shown that displaying expectations can induce gender
-differences in advice-giving. Specifically, advisers were more likely to
-recommend competing against a group of High Performers to men who had
-higher expectations about their performance than did women. We now test
-directly whether this is driven by interpersonal concerns. Specifically,
-we examine whether more flattering advice is the result of a desire to
-be liked and whether advisees indeed do like advisers more when they
-give flattering advice.
-
-We conducted a three-stage experiment in which we experimentally
-manipulated the incentives for advicers. We began by inviting a group of
-advisees to upload photos of themselves ("selfies") and informed them
-that they would be rated on their attractiveness. We grouped them with
-nine other participants of the same gender and recruited participants of
-the opposing gender to rank them from most to least attractive and to
-provide advice. Specifically, we asked them to advise the participant
-they ranked as the 7th most attractive (4th least attractive) on what
-rank they should bet they were ranked by a larger group of raters.
-Advisers were randomly assigned to two treatments, receiving a bonus
-payment either if the advisee guessed their rank accurately or if the
-advisee evaluated the adviser as likeable as measured by an
-unincentivized scale response. We hypothesize that advisers who want to
-be liked by advisees will recommend that they bet on a lower rank, i.e.
-that they are more attractive.
-
-```{r}
-
-study2_time1 <- readRDS(here::here("Data/Study2_time1.Rds"))
-study2_time1_200 <- readRDS(here::here("Data/Study2_time1_200.Rds"))
-study2_time2 <- readRDS(here::here("Data/Study2_time2.Rds"))
-study2_finalRank <- readRDS(here::here("Data/Study2_finalRank.Rds"))
-study2_time3 <- readRDS(here::here("Data/Study2_time3.Rds"))
-
-```
-
-## Methods
-
-We recruited 300 participants from Prolific and, after asking
-demographic questions, invited them to upload photos of themselves
-(selfies) to be rated by other participants on attractiveness.
-`r scales::comma(dim(study2_time1[study2_time1$gender == 'Male',])[1])`
-men and
-`r scales::comma(dim(study2_time1[study2_time1$gender == 'Female',])[1])`
-women agreed to do so and uploaded pictures that adhered to our
-instructions (e.g., did not include other people). We selected the first
-100 photos from women to arrive at a gender-balanced sample
-($M_{\text{Age}}$ = `r mean(study2_time1_200$age)` years). Participants
-were informed that their selfies would be randomly grouped with those of
-nine other participants of their gender and ranked in terms of
-attractiveness by a group of new Prolific participants of the opposite
-gender. Lastly, they guessed their rank (unincentivized).
-
-Next, we recruited a new, gender-balanced sample for the role of
-advisers. `r scales::comma(dim(study2_time2)[1])` participants from
-Prolific ($M_{\text{Age}}$ = `r mean(study2_time2$age)` years;
-`r round(mean(study2_time2$gender == "Female")*100, 2)`% Female) started
-by providing demographic information, then were matched to a group of
-the opposite gender. They then ranked participants from most to least
-attractive using a drop-down menu next to each picture. Because of a
-limitation with the survey software, participants were able to select
-the same rank for multiple participants, rather than rank them uniquely.
-We remove 115 participants who did not follow instructions and provide a
-unique ranking.
-
-After submitting their ratings, they saw the photo of the participant
-they had ranked as the 7th most attractive (i.e., the 4th least
-attractive). They were reminded of the rank they had given to that perso
-and informed that this participant would be invited back and could earn
-a \$1 bonus if they guessed their rank correctly. The rank was
-determined by the aggregate ratings of all participants who had ranked
-this group. Their task was to give advice to this participant about the
-rank they should bet on based on having observed all ten selfies and
-their own assessment. We randomly assigned participants to one of two
-incentivization schemes. In the "Accuracy" treatment, they received a
-bonus identical to the advisee: \$1 if they guessed their rank
-correctly. In the "Likeability" treatment, we informed them that they
-would be rated by the advisee on a 5-point Likert scale for how likeable
-they thought they were. Each point on the scale would translate to a
-bonus of 20 cents. They then selected a rank that they would recommend
-the advisee to bet on.
-
-Finally, we invited participants from Stage 1 and were ranked as the 7th
-attractive by at least one adviser (so that they received advice) back
-for the follow-up survey. Following our preregistration, we kept the
-survey open for 7 days. In total,
-`r scales::comma(dim(study2_time3)[1])` participants
-(`r scales::comma(dim(study2_time3[study2_time3$gender == 'Male',])[1])`
-men,
-`r scales::comma(dim(study2_time3[study2_time3$gender == 'Female',])[1])`
-women) returned. They were reminded of the selfie they uploaded in Stage
-1 and informed that a group of 10 selfies, including theirs, had been
-rated by other participants from Prolific. They then saw the advice from
-a randomly selected adviser and made their estimate with a \$1 incentive
-for guessing accurately. They then saw the rank they had been advised to
-bet on one more time and were asked to rate the adviser's likability,
-warmth, friendliness, good-naturedness, trustworthiness, and sincerity
-on 5-point Likert scales (adapted from @Fiske2007).
-
-## Results
-
-```{r}
-library(dplyr)
-
-TargetsUnique <- study2_time2 %>%
-  dplyr::select(Target) %>%
-  unique()
-
-TargetsUnique <- merge(TargetsUnique,study2_finalRank, by.x = 'Target', by.y = 'QID7_Id')
-
-```
-
-```{r study2advice, fig.cap="Advisers were asked to suggest what rank to bet on for someone they ranked as the 7th most attractive out of ten people.
-When incentivized for accuracy, most of them advised betting on 7, which was based on their evaluation of the recipient's attractiveness.
-However, when incentivized for likability, many participants gave flattering advice by suggesting betting on higher ranks that imply a higher evaluation of attractiveness."}
-
-study2_time2 <- study2_time2 %>% dplyr::mutate(Advice = as.numeric(Advice))
-
-ggplot(study2_time2, aes(x = Condition, y = Advice, fill = Condition)) +
-    geom_violin(trim = FALSE) +
-     scale_fill_manual(values = c("#2A629A",'#FF7F3E'), labels = c("Accurate", "Likable")) +
-  geom_hline(yintercept = 7, col = 'grey', linetype = 'dashed', linewidth = 0.7) +
-  scale_y_continuous(name = "Advised Rank", breaks = seq(1, 10)) +
-  theme_bw() +
-  theme(panel.grid = element_blank(),
-        panel.border = element_blank(),
-        axis.line = element_line(colour = "grey"),
-        legend.position = "bottom",
-        legend.title = element_blank(),
-        legend.key.size = unit(1.2, "lines"),
-        legend.text = element_text(size = 12),
-        plot.title = element_text(hjust = 0.5, size = 20))
-
-```
-
-We begin by examining the prior beliefs of advisees who uploaded their
-selfies. On average, men guessed they ranked
-`r round(mean(study2_time1[study2_time1$gender == "Male",]$Guess),2)` in
-their group of 10 and women guessed that they ranked
-`r round(mean(study2_time1[study2_time1$gender == "Female",]$Guess),2)`.
-Participants overall underestimate their attractiveness relative to the
-benchmark average of 5.5. Moreover, women do so more than men
-`r papaja::apa_print(t.test(Guess ~ gender, data = study2_time1, var.equal = T))$statistic`.
-Notably, people's self-perceptions correlated strongly with the
-aggregate ratings of the advisers
-(`r round(cor(study2_finalRank$Guess, study2_finalRank$finalRank),2)`,
-`r papaja::apa_print(cor.test(study2_finalRank$Guess, study2_finalRank$finalRank))$statistic`).
-However, there was substantial heterogeneity in perceptions of
-attractiveness. Of the 200 participants,
-`r length(unique(study2_time2$Target))` were ranked as 7th most
-attractive by at least one adviser. On average, men in this subset
-estimated they were ranked
-`r round(mean(TargetsUnique[TargetsUnique$gender == 'Male',]$Guess),2)`th
-and women estimated they were ranked
-`r round(mean(TargetsUnique[TargetsUnique$gender == 'Female',]$Guess),2)`th
-(`r papaja::apa_print(t.test(Guess ~ gender, data = TargetsUnique, var.equal = T))$statistic`).
-
-Next, we turn our attention to the advisers (Figure
-\@ref(fig:study2advice)). In the Accuracy condition, those uploading
-selfies were advised to bet on rank
-`r round(mean(study2_time2[study2_time2$Condition == "Accurate",]$Advice),2)`.
-Notably, this is significantly more attractive than the 7th rank those
-advisers had themselves guessed just on the prior screen
-(`r papaja::apa_print(t.test(study2_time2[study2_time2$Condition == "Accurate",]$Advice, mu = 7, var.equal = T))$statistic`).
-This suggests that even when incentivized for accuracy, participants
-offered flattering advice.[^3] Importantly, and as predicted, we find
-that advisers in the Likeable treatment recommend betting on a lower
-rank, communicating that they think the participant in the selfie is
-more attractive
-(`r round(mean(study2_time2[study2_time2$Condition == "Likable",]$Advice),2)`,
-`r papaja::apa_print(t.test(Advice ~ Condition, data = study2_time2, var.equal = T))$statistic`).
-This suggests that advisers inferred that advising someone that they
-were more attractive would make the adviser appear more likeable and
-therefore provided advice that communicated a more favorable impression
-of the participants' attractiveness. The distribution shown in Figure
-\@ref(fig:study2advice) shows that participants do not simply tell
-participants that they are the most attractive person in the group. They
-may infer that flattering advise needs to be somewhat realistic to be
-believable. We return to this in the general discussion.
-
-[^3]: This shading could be due to concerns of avoiding disappointment.
-    However, it could also be that advisers are uncertain about the
-    rankings they had given and make a recommendation that combines
-    their own belief with a uniform prior.
-
-<!-- David: Making a note here that we should be sure to discuss this at the end -->
-
-<!-- as something for future research. -->
-
-<!-- David: We should also report something on accuracy of the advice given across -->
-
-<!-- the treatments. Even if no difference. -->
-
-```{r study2regs}
-
-modelsummary::modelsummary(list(`(1)` = lm(likable ~ Advice, data = study2_time3),
-                                `(2)` = lm(warmAvg ~ Advice, data = study2_time3),
-                                `(3)` = lm(trustAvg ~ Advice, data = study2_time3)),
-                           vcov = c("classical", "classical", "classical"),
-                           coef_map = c("Advice" = "Advised Rank",
-                                        "(Intercept)" = "Constant"),
-                           stars = T,
-                           gof_map = list(list('raw' = 'nobs', 'clean' = 'N', 'fmt' = 0)),
-                           caption = "When individuals receive advice that implies a high level of attractiveness (lower rank), they tend to perceive the advice giver as more likable (Column 1), warm (Column 2).
-Column 3 shows that advisors are rated as more trustworthy when they advice lower ranks, but this relationship is only directional.")
-
-```
-
-<!-- Amanda: How about this -->
-
-<!-- For warmth it looks interesting, but I think the plot is hard -->
-
-<!-- to read. Let's hold off on this for now. -->
-
-Finally, we examine whether flattering advice indeed leads to more
-positive evaluations of advisers, or whether flattering advice is
-dismissed as insencere. Following our preregistration, we average the
-ratings on likeability, warmth, friendliness, and good-naturedness to
-create a scale of likeability ($\alpha$ =
-`r cronbach.alpha(study2_time3[, 5:8])$alpha`); and we create a scale of
-trustworthiness by averaging the ratings of trustworthiness and
-sincerity ($\alpha$ = `r cronbach.alpha(study2_time3[, 9:10])$alpha`).
-
-<!-- The Figure is not super clear. How about we try a series of box plots, -->
-
-<!-- with the x-axis as the advised rank? Standard errors will be huge at the -->
-
-<!-- extremes. -->
-
-<!-- Also, we need to do something relative to the advisees' expectations. -->
-
-<!-- I wonder what would be interesting here? Maybe averages for three groups: -->
-
-<!-- more attractive than the participants' own guess, equally attractive, and less -->
-
-<!-- attractive? -->
-
-<!-- Amanda: How about the following picture? -->
-
-```{r study2rating, fig.cap="Participants tend to rate advisors who suggest betting on a higher rank (implying greater attractiveness) as more likable and warm."}
-
-library(ggplot2)
-library(gridExtra)
-library(dplyr)
-
-study2_time3 <- study2_time3 %>% dplyr::mutate(Advice = as.factor(Advice))
-
-# Create the first plot
-plot1 <- ggplot(study2_time3, aes(x = Advice)) +
-  geom_boxplot(aes(y = likable),position = position_dodge(width = 0.8), alpha = 0.8, color = "darkgrey", fill = "#2A629A") +
-  scale_y_continuous(name = "Likability") +
-  scale_x_discrete(name = "Advised Rank") +
-  theme_bw() +
-  theme(panel.grid = element_blank(),
-        panel.border = element_blank(),
-        axis.line = element_line(colour = "grey"),
-        legend.position = "bottom",
-        legend.title = element_blank(),
-        legend.key.size = unit(1.2, "lines"),
-        legend.text = element_text(size = 12),
-        plot.title = element_text(hjust = 0.5, size = 20))
-
-# Create the second plot
-plot2 <- ggplot(study2_time3, aes(x = Advice)) +
-  geom_boxplot(aes(y = warmAvg),position = position_dodge(width = 0.8), alpha = 0.8, color = "darkgrey", fill = "#FF7F3E") +
-  scale_y_continuous(name = "Warmth") +
-  scale_x_discrete(name = "Advised Rank") +
-  theme_bw() +
-  theme(panel.grid = element_blank(),
-        panel.border = element_blank(),
-        axis.line = element_line(colour = "grey"),
-        legend.position = "bottom",
-        legend.title = element_blank(),
-        legend.key.size = unit(1.2, "lines"),
-        legend.text = element_text(size = 12),
-        plot.title = element_text(hjust = 0.5, size = 20))
-
-# Combine the plots side by side
-grid.arrange(plot1, plot2, ncol = 2)
-
-```
-
-```{r study2ratingByGroup, fig.cap="After participants received advice that suggested betting on a rank that was lower than, equal to, or higher than their self-expectations, they evaluated advisors based on their likability and warmth.
-Participants rated advisors who gave flattering advice and delivered a high evaluation of their attractiveness as more likable and warm than those whose advice implied a lower evaluation of their attractiveness."}
-
-library(dplyr)
-library(ggplot2)
-
-study2_time3 <- study2_time3 %>% dplyr::mutate(Guess = as.numeric(Guess), Advice = as.numeric(Advice)) %>%
-  dplyr::mutate(HorL = ifelse(Guess == Advice,0, ifelse(Guess > Advice, 1,-1))) %>%
-  dplyr::mutate(HorL = as.factor(HorL)) %>% 
-  dplyr::mutate(bonus = ifelse(bet == `Final Rank`,1,0))
-
-ratings <- study2_time3 %>%
-  group_by(HorL) %>%
-  summarise(like = mean(likable), warmth = mean(warmAvg))
-
-rating_table <- matrix(c(ratings$like,ratings$warmth), nrow = 2, byrow = TRUE, dimnames = list( c("Likable",'Warm'),c("Pessimistic", "Accurate", "Flattering")))
-
-rating_df = as.data.frame.table(rating_table) %>%
-  dplyr::rename( 'Condition'='Var1', 'Advice' ='Var2') %>%
-  dplyr::mutate(Freq = round(Freq,2))
-
-ggplot(rating_df, aes(x = Advice, y = Freq, fill = Condition)) +
-  geom_bar(stat = "identity", position = "dodge") +
-  scale_fill_manual(values = c("#2A629A",'#FF7F3E')) +
-  labs(x = "Advice", y = "Rating") +
-  ggtitle('Response to Advice') +
-  theme_bw() +
-  theme(panel.grid = element_blank(),
-        panel.border = element_blank(),
-        axis.line = element_line(colour = "grey"),
-        legend.position = "bottom",
-        legend.title = element_blank(),
-        legend.key.size = unit(1.2, "lines"),          
-        legend.text = element_text(size = 12),
-        plot.title = element_text(hjust = 0.5, size = 20)) +
-  geom_text(aes(label = paste0(Freq), y = 0.5), position = position_dodge(width = 0.9), size = 5, color = 'white', fontface = "bold")
-
-```
-
-As seen in Figure \@ref(fig:study2rating), we found that advisees who
-suggested that the advisee was more attractive (lower rank) were indeed
-rated as more likeable and warm (b = -0.109, p \< .05; b = -0.133, p \<
-.001, respectively; See Columns 1 and 2 of Table \@ref(tab:study2regs)).
-When using their self-expectations as a reference point, advisors who
-suggest a rank lower than that point are perceived as less likable and
-warm (see Figure \@ref(fig:study2ratingByGroup)). Interestingly, these
-benefits are not at the cost of being hypocritical; advisers who
-recommend a more favorable rank are viewed as no less trustworthy
-(Column 3 of Table \@ref(tab:study2regs)).
-
-We were not powered to do a comparison across the two experimental
-groups and did not preregister such a difference. Indeed, we find no
-difference in likeability and warmth across the two treatments
-(`r papaja::apa_print(t.test(likable ~ Condition, data = study2_time3, var.equal = T))$statistic`,
-and
-`r papaja::apa_print(t.test(warmAvg ~ Condition, data = study2_time3, var.equal = T))$statistic`,
-respectively).
-
-## Discussion
-
-In a context where advice communicates ego-relevant information (here,
-people's attractiveness), we find that the advice people give is
-contingent on their incentives. Specifically, when they get rewarded for
-being more likeable, they recommend that the advisee bet on a more
-favorable rank than when they are incentivized for accuracy.
-Importantly, advisees do not discount flattering advice and instead
-evaluate people who advise them to bet on a more attractive rank as
-warmer and more likeable. These gains to interpersonal perceptions do
-not come at the cost of trustworthiness, even when the advice is
-substantially inflated (e.g., a recommendation that the advisee is the
-most attractive in the group).
-
 # General Discussion

### 2024-09-25 manuscript/manuscript.Rmd
S1 Method time 1

@@
 study1_time1 <- readRDS(here::here("Data/Study1_time1.Rds"))
+study1_ability50 <- read.csv(here::here("Data/Cleaned Data/S1_Ability50_clean.csv"))
 study1_time2_giver <- readRDS(here::here("Data/Study1_time2_giver.Rds"))
@@
 # Study 1
+In Study 1, we investigate whether givers take into account advisees' expectations 
+when providing advice. We compare the advice given to recipients who expressed either
+high or low expectations, across two treatments: one where givers were aware of these 
+expectations (Expectation treatment) and one where this information was unknown to them 
+(Performance treatment).
+
+The experiment consisted of three stages, in which we manipulated advisees' expectations and whether givers had access to this information.
+First, we measured participants' performance, then informed them that their performance would be compared to that of another participant, with the higher scorer eligible to win a bonus.
+Participants were asked to choose their competitor from either the top 20 performers ("High Performer Group") or the bottom 20 performers ("Low Performer Group") out of a pool of 50 competitors.
+We nudged participants to have high or low expectations by encouraging them to compete against either the High Performer Group or the Low Performer Group.
+Advisors were randomly assigned to one of two treatments: seeing only performance information or both performance and expectation information.
+We hypothesize that advisees who indicate they are capable of competing against strong competitors will be more likely to receive advice to do so.
+
+## Methods
+
+As part of our main experiment, participants were asked to choose a group 
+of previous participants to compete against. To create these groups, we 
+first recruited a sample of  `r scales::comma(dim(study1_ability50)[1])`
+participants from Prolific to complete a 10-question ability quiz. The quiz 
+included word puzzles, identifying emotions from photos, and selecting the
+best responses in given scenarios. These questions were adapted from surveys 
+that measure problem-solving, emotional intelligence, and communication
+skills. We selected these specific abilities based on a pretest in which 
+participants ranked them as the three most critical skills in modern society, 
+making performance on this task ego-relevant.Participants had five minutes to 
+answer the quiz and were paid 5 cents for each correctly answered question. 
+We define the top 20 scorers as the "High Performer Group"
+and the bottom 20 scorers as the "Low Performer Group."
+
+We then recruited `r scales::comma(dim(study1_time1)[1])`
+participants to serve as advisees in Stage 1 of our main experiment. These 
+participants completed the same 10-item ability quiz as the earlier group, 
+with the opportunity to earn 5 cents for each correct answer. After the 
+quiz, we asked them to indicate their initial preference for competitors. 
+Half of the participants were randomly shown the default option of the 
+'High Performer Group,' highlighted in blue, while the other half were 
+shown the 'Low Performer Group' as the default. This manipulation was 
+designed to influence advisees' expectations, as advisees who believed 
+they could compete against stronger competitors were perceived by givers 
+to have higher expectations. However, participants were free to opt out 
+of the default choice.
 

### 2024-09-25 R/clean_study1_time3.R

@@ -5,8 +5,6 @@ library(magrittr)
 
 Target <- read.csv("Data/Cleaned Data/S1_time1_clean.csv")[-c(1,3)]
 
-
-
 Receiver <- data.table::fread(here::here("Data/Raw Data/S1_time3.csv"),
                               header = T,na.strings = '')[-c(1,2)]  %>%
 dplyr::filter(Progress == '100' & Status == 'IP Address') %>%
@@ -19,6 +17,59 @@ dplyr::filter(Progress == '100' & Status == 'IP Address') %>%
                                            GiverCondition == 'None' ~ 0))
 
 Receiver <- merge(Receiver,Target,by = 'ProlificID')
+
+
+Competitors <- data.table::fread(here::here("Data/Raw Data/S1_Ability50.csv"),
+                                 header = T,na.strings = '')[-c(1,2)] %>%
+  dplyr::filter(Progress == '100' & Status == 'IP Address' & !is.na(QID3) & !is.na(Gender) ) %>%
+  dplyr::rename('ProlificID' = 'QID3', 'score' = 'Score') %>%
+  dplyr::mutate(Score = as.numeric(score)) %>%
+  dplyr::select(ProlificID,ResponseId, Score,
+                Gender, Age, Ethnicity,Education)
+
+Competitors %>% write.csv("Data/Cleaned Data/S1_Ability50_clean.csv")
+
+
+# Paired with competitors
+Competitors <- Competitors[order(-Competitors$Score),] %>%
+  dplyr::select(ProlificID, Score)
+
+HighGroup <- Competitors[1:20,]
+LowGroup <- Competitors[31:50,]
+
+CompetitorList <- list()
+ScoreList <- list()
+
+set.seed(807)
+
+for(i in 1:nrow(Receiver)){
+
+  random_num <- sample(20, 1)
+
+  if (Receiver[i,]$Bet == 1){
+    ID_i <- HighGroup[random_num,"ProlificID"]
+    Score_i <- HighGroup[random_num,"Score"]
+  }
+  if (Receiver[i,]$Bet == 0){
+    ID_i <- LowGroup[random_num,"ProlificID"]
+    Score_i <- LowGroup[random_num,"Score"]
+  }
+
+  CompetitorList <- c(CompetitorList, ID_i)
+  ScoreList <- c(ScoreList,Score_i)
+
+}
+
+Competitors_Target <- data_frame(CompetitorID = unlist(CompetitorList) ,CompetitorScore = unlist(ScoreList))
+
[…]

### 2024-09-27 manuscript/manuscript.Rmd
Study 1 Result (1/2)

@@
 
-In a large, preregistered experiment (n = 2,000), we show that advisers
+In a large, preregistered experiment (n = 1,200), we show that advisers
 consider the expectations of advisees, even when such expectations do
@@
 Half of the participants were randomly shown the default option of the 
-'High Performer Group,' highlighted in blue, while the other half were 
-shown the 'Low Performer Group' as the default. This manipulation was 
+'High Performer Group,' highlighted in blue ("High Default" treatment), while the other half were 
+shown the 'Low Performer Group' as the default ("Low Default" treatment). This manipulation was 
 designed to influence advisees' expectations, as advisees who believed 
@@
 of the default choice.
+
+We then recruited `r scales::comma(dim(study1_time2_giver)[1])`
+participants for Stage 2, placing them in the role of advisers. We began
+by informing them of the ability quiz that participants in the
+preliminary study and Stage 1 had completed, and informed them of the
+average score of all participants in the preliminary study. Advisers had
+to recommend whether an advisee should compete against the Low
+Performer Group or the High Performer Group (we used these terms in the survey).
+We anticipated that being told to compete against High Performers is
+more flattering and hence being told to compete against the Low
+Performers would be disappointing if one had expected to do well.
+Advisees would earn 20 cents if their score was equal to or higher than
+a randomly selected member of the Low Performer Group and they chose to
+compete against this group, or 50 cents if they performed as well or
+better than a randomly selected member of the High Performer Group and
+they chose to compete against that group. If they scored lower, they
+would not receive any bonus.
+
+Advisers were randomly assigned to one of two treatments. In the
+"Performance" treatment, they only observed the score of the advisee on the
+ability quiz. In the "Expectation" treatment, they observed the
+score as well as the advisee's initial preference for which group to compete against.
+However, since the outcome was based solely on the quiz score and advisees didn’t 
+know their scores, their initial choice wasn’t useful in deciding which group had a 
+higher expected bonus. Advisers gave recommendations to 10 advisees and were told that 
+if their advice was used by a participant in a follow-up survey, they would receive 
+the same bonus as that participant. The survey concluded with basic demographic 
+questions.
+
+Finally, we invited participants from Stage 1 back for the follow-up
+survey. Following our preregistration, we kept the survey open for 7
+days. In total, `r scales::comma(dim(study1_time3)[1])` participants
+(`r scales::comma(dim(study1_time3[study1_time3$Gender == 'Male',])[1])`
+men,
+`r scales::comma(dim(study1_time3[study1_time3$Gender == 'Female',])[1])`
+women) returned. The brief survey reminded them of the task they
+completed in Stage 1, informed them that other participants from
+Prolific had observed their real score and given them advice against
+which group to compete against, and finally were reminded them of how
+many questions they guessed they had answered correctly. Importantly,
+they were not informed of their true score or the score of the groups
+they could compete against. Participants then observed the advice from a
+randomly selected adviser and made their decision.
+
+##Results
+
+<!-- Amanda: Wondering if we need to report the p-value of priming manipulation -->
+
+```{r}
+contingency_table <- table(study1_time1$Guess, study1_time1$default)
+
+chi_test <- chisq.test(contingency_table)
+
+```
+
+We begin by examining the performance of the Stage 1 participants.
+Because our treatment takes place after participants completed the
+ability quiz, we would not expect a difference in performance across
+the Low and High Default treatments. Indeed, the two groups scored
+no different from one another
+(`r round(mean(study1_time1[study1_time1$default == "Low",]$Score),2)`
+and
+`r round(mean(study1_time1[study1_time1$default == "High",]$Score),2)`
+for the Low Defult and High Defult treatments, respectively,
+`r papaja::apa_print(t.test(Score ~ default, data = study1_time1, var.equal = T))$statistic`).
+The priming did, however, affect advisees' initial choices. In the "Low Default" treatment, 
+only `r round(mean(study1_time1[study1_time1$default == "Low",]$Guess),2)*100`% 
+of participants initially preferred competing against the High Performer Group, 
+compared to `r round(mean(study1_time1[study1_time1$default == "High",]$Guess),2)*100`%
+of participants who saw the High Performer Group highlighted ($\chi^2$(1, n = 201) = 36.62, p < .001).
+
+```{r study1regs}
+
+study1_advice <- study1_time2_advice %>%
+  dplyr::mutate(Treatment = factor(Treatment, levels = c('Low', 'High'))) %>%
+  dplyr::mutate(ExpShow = ifelse(Condition == 'E', 1, 0))
+
+# Fit the two models
+model1 <- lm(Advice ~ ExpShow * Treatment, data = study1_advice)
+model2 <- lm(Advice ~ Treatment + Score, data = study1_advice %>% dplyr::filter(ExpShow == 1))
+
+# Use sandwich package for clustered standard errors
+library(sandwich)
+
+# Clustered standard errors by GiverID
+vcov_list <- list(sandwich::vcovCL(model1, cluster = ~GiverID), 
+                  sandwich::vcovCL(model2, cluster = ~GiverID))
+
+modelsummary::modelsummary(
+  list(`(1)` = model1, `(2)` = model2),
+  vcov = vcov_list,
+  coef_map = c(
+    "TreatmentHigh" = "High Default",
+    "ExpShow" = "Expectation Shown",
+    "ExpShow:TreatmentHigh" = "Expectation x Default",
+    "Score" = "Performance",
+    "(Intercept)" = "Constant"
+  ),
+  stars = TRUE,
+  gof_map = list(list('raw' = 'nobs', 'clean' = 'N', 'fmt' = 0)),
+  caption = "Column 1 displays the advice given to compete against a High Performer Group based on whether the advisees were primed with low or high default and the initial preference shown to the advisor.
+Column 2 displays the advice given to compete against a High Performer Group based on the default and advisees' performance when their initial preference was visible to the advisor.
+All standard errors are clustered at the level of the advisor."
+)
+
+```
+
+Next, we examine whether advisers took the advisee's expectations into
+account. Column 1 of Table \@ref(tab:study1regs) reports a linear
+probability model on advising to compete against the High Performer
+group for advisers in the "Expectations" treatment, controlling for the
+true performance of the advisee. Because each adviser made ten
+recommendations, we cluster standard errors at the adviser level.
+However, contrary to our expectations, we do not see a significant
+effect of the expectations treatment. This may be because the induced
+difference in expectations was too small.
+
+However, recall that men were more confident in their performance than
+were women. Our theory thus predicts that showing expectations should
+lead to more flattering advice (i.e., a recommendation to compete
+against the High Performer group) for men than for women. We report a
+linear probability model with advice to compete against the high group
+as the outcome measure, and the advisee's gender, whether expectations
+were shown to the adviser, and the interaction of the two in Column 2 of
+Table \@ref(tab:study3regs). As predicted, we find a significant
+interaction effect: men are more likely to be advised to compete against
+the High Performers when expectations are shown than when they are
+hidden ($p < 0.001$). We show this result graphically in Figure
+\@ref(fig:study3genderdiff)).
 
@@
 
-```{r study1regs}
+```{r study3regs}
 study3_advice <- study3_advice %>% dplyr::mutate(Treatment = factor(Treatment, levels = c('Low', 'High'))) %>%
@@
 
-```{r study1genderdiff, fig.cap ="Advisers observed real performance and the participants' estimated performance, but not their gender.
+```{r study3genderdiff, fig.cap ="Advisers observed real performance and the participants' estimated performance, but not their gender.
 As a result of their higher expectations, men (blue) were advised to compete against the high performance group more often than women (red).
@@
 Next, we examine whether advisers took the advisee's expectations into
-account. Column 1 of Table \@ref(tab:study1regs) reports a linear
+account. Column 1 of Table \@ref(tab:study3regs) reports a linear
 probability model on advising to compete against the High Performer
@@
 were shown to the adviser, and the interaction of the two in Column 2 of
-Table \@ref(tab:study1regs). As predicted, we find a significant
+Table \@ref(tab:study3regs). As predicted, we find a significant
 interaction effect: men are more likely to be advised to compete against
@@
 hidden ($p < 0.001$). We show this result graphically in Figure
-\@ref(fig:study1genderdiff)).
+\@ref(fig:study3genderdiff)).
 
@@
 gender of the advisee, and their interaction in Column 3 of Table
-\@ref(tab:study1regs). Displaying expectations led men to be advised to
+\@ref(tab:study3regs). Displaying expectations led men to be advised to
 compete against the High Performer group more often, and this advise

### 2024-09-28 manuscript/manuscript.Rmd
Before S1 discussion

@@
 
+<!-- No main interactive effect on expected bonus, therefore I did not include it in this tabel -->
+
 ```{r study1regs}
@@
     "ExpShow" = "Expectation Shown",
-    "ExpShow:TreatmentHigh" = "Expectation x Default",
+    "ExpShow:TreatmentHigh" = "Expectation x High Default",
     "Score" = "Performance",
@@
 
-Next, we examine whether advisers took the advisee's expectations into
-account. Column 1 of Table \@ref(tab:study1regs) reports a linear
-probability model on advising to compete against the High Performer
+Next, we examine whether advisers took the advisees' expectations into account. 
+Recall that advisees who defaulted to competing against the High Performer 
+Group were indeed more likely to choose this group, which, from the advisers' 
+perspective, could signal high confidence in their abilities. Our theory 
+predicts that showing expectations should lead to more flattering advice—
+specifically, a recommendation to compete against the High Performer Group—
+for advisees with a high default choice compared to those with a low 
+default choice. Column 1 of Table \@ref(tab:study1regs) reports a linear
+probability model with advice to compete against the high group
+as the outcome measure, incorporating the default choice advisees saw, whether expectations
+were shown to the adviser, and the interaction of the two. Because each adviser made ten
+recommendations, we cluster standard errors at the adviser level.
+As predicted, we find a marginally significant interaction effect: advisees 
+with a default choice to compete against the High Performer Group (nudged 
+to have high expectations, though not necessarily holding them) were more 
+likely to receive advice to compete against stronger competitors when 
+their expectations were shown compared to when they were hidden.
+We reported a linear probability model on advising to compete against the High Performer
 group for advisers in the "Expectations" treatment, controlling for the
-true performance of the advisee. Because each adviser made ten
-recommendations, we cluster standard errors at the adviser level.
-However, contrary to our expectations, we do not see a significant
-effect of the expectations treatment. This may be because the induced
-difference in expectations was too small.
-
-However, recall that men were more confident in their performance than
-were women. Our theory thus predicts that showing expectations should
-lead to more flattering advice (i.e., a recommendation to compete
-against the High Performer group) for men than for women. We report a
-linear probability model with advice to compete against the high group
-as the outcome measure, and the advisee's gender, whether expectations
-were shown to the adviser, and the interaction of the two in Column 2 of
-Table \@ref(tab:study3regs). As predicted, we find a significant
-interaction effect: men are more likely to be advised to compete against
-the High Performers when expectations are shown than when they are
-hidden ($p < 0.001$). We show this result graphically in Figure
-\@ref(fig:study3genderdiff)).
+true performance of the advisee in Column 2 of Table \@ref(tab:study1regs).
+We observe a significant main effect of the default treatment, where a high default
+increased the likelihood of receiving flattering advice. It is worth noting that, 
+since only `r round(mean(study1_time1[study1_time1$default == "High",]$Guess),2)*100`
+% of advisees in the high default group actually stuck with their default 
+choice, this represents a conservative test of the effect of high expectations on 
+the likelihood of receiving flattering advice.
+
+```{r study1Advice fig.cap ="Advisees who were nudged to express high expectations were more likely to receive advice to compete against the High Performer Group."}
+study1_time2_advice %>%
+  mutate(Treatment=factor(Treatment, levels=c('High','Low'), labels = c('High default', 'Low default'))) %>%
+  group_by(Condition, Treatment) %>%
+  summarize(avg_count = mean(Advice), ci = qnorm(0.975)*sd(Advice)/sqrt(dplyr::n())) %>%
+  ggplot2::ggplot(ggplot2::aes(x = Condition, y = avg_count, fill = Treatment)) +
+  ggplot2::geom_col(position = 'dodge') +
+  ggplot2::geom_errorbar(ggplot2::aes(ymin = avg_count - ci, ymax = avg_count + ci), 
+                         position = ggplot2::position_dodge(0.9), linewidth = 0.2, width = 0.1) +
+  ggtitle("Advice: Meeting Expectations vs. Absent Expectations") +
+  scale_fill_manual(values = c("#d19715", "#29526d")) +
+  theme_bw() +
+  labs(y = "P(Compete Against High Performer)", x = NULL) +
+  theme(panel.grid = element_blank(),
+        panel.border = element_blank(),
+        axis.line = element_line(colour = "grey"),
+        axis.text.x = element_text(size = 12),
+        legend.position = "none", # No legend
+        plot.title = element_text(hjust = 0.5, size = 16)) +
+  scale_x_discrete(labels = c("Expectation shown", "Expectation Absent")) +
+   geom_text(aes(label=Treatment, y = -0.01), position = position_dodge(0.90))
+
+```
+
+## Discussion
 

### 2024-09-28 R/clean_study1_time2.R

@@ -39,9 +39,9 @@ AdviceAll <- data_frame(Target = unlist(TargetList) ,Advice = unlist(AdviceList)
 AdviceAll <- cbind(AdviceAll,conditions)
 
 
-advisee <- readRDS(here::here("Data/Study1_time1.Rds"))%>%
-  dplyr::select(PROLIFIC_PID,Guess, default,Score,Gender) %>%
-  dplyr::rename('Target' = "PROLIFIC_PID", "intChoice" = 'Guess', 'Treatment' = 'default','TarGender' = 'Gender')
+advisee <- readRDS(here::here("Data/Study1_time1.Rds")) %>%
+  dplyr::select(ProlificID,Guess, default,Score) %>%
+  dplyr::rename('Target' = "ProlificID", "intChoice" = 'Guess', 'Treatment' = 'default')
 
 AdviceAll <- merge(AdviceAll,advisee,by.x = 'Target',by.y = "Target")
 
@@ -63,7 +63,7 @@ LowGroup <- Competitors[31:50,]
 ReturnList <- list()
 
 for(i in 1:nrow(AdviceAll)){
-  performance <- AdviceAll$Performance[i]
+  performance <- AdviceAll$Score[i]
   if (AdviceAll$Advice[i] == '1'){
     reward = 0.5
     group <- HighGroup

### 2024-09-30 manuscript/manuscript.Rmd
Pics for Study 2

@@
 
-##Results
+## Results
 
@@
 
-```{r study1Advice fig.cap ="Advisees who were nudged to express high expectations were more likely to receive advice to compete against the High Performer Group."}
+```{r study1Advice, fig.cap ="Advisees who were nudged to express high expectations were more likely to receive advice to compete against the High Performer Group."}
 study1_time2_advice %>%
@@
   ggtitle("Advice: Meeting Expectations vs. Absent Expectations") +
-  scale_fill_manual(values = c("#d19715", "#29526d")) +
+  scale_fill_manual(values = c("#2A629A",'#FF7F3E')) +
   theme_bw() +
@@
 ## Discussion
+
+When the quality of a decision does not depend on someone's expectations,
+the adviser's awareness of the advisee's expectations should not influence
+the advice given. However, in line with our argument that advisers take
+into account the belief utility of the advisee and prefer to flatter 
+rather than disappoint, we find that displaying the advisee's expectations
+does make a difference. Specifically, advisees who expressed a preference
+for stronger competitors were more likely to receive 'flattering' advice,
+encouraging them to pursue that option. One possible explanation for this
+finding is that, rather than trying to flatter, advisers may simply be 
+telling advisees what they want to hear. In the next study, we aim to 
+investigate the mechanism behind this discrepancy in advice-giving when
+expectations are revealed, exploring the question: Why do people give 
+flattering advice?
 
@@
 
+library(ggplot2)
+library(ggridges)
+
 study2_time2 <- study2_time2 %>% dplyr::mutate(Advice = as.numeric(Advice))
 
-ggplot(study2_time2, aes(x = Condition, y = Advice, fill = Condition)) +
-    geom_violin(trim = FALSE) +
-     scale_fill_manual(values = c("#2A629A",'#FF7F3E'), labels = c("Accurate", "Likable")) +
-  geom_hline(yintercept = 7, col = 'grey', linetype = 'dashed', linewidth = 0.7) +
-  scale_y_continuous(name = "Advised Rank", breaks = seq(1, 10)) +
+ggplot(study2_time2, aes(x = Advice, y = Condition, fill = Condition)) +
+    # Reduce vertical spacing with rel_min_height and scale
+    geom_density_ridges(scale = 1.0, rel_min_height = 0.01, alpha = 0.7) +
+
+    # Shading the left side of x = 7 in light grey
+    geom_rect(aes(xmin = 7, xmax = Inf, ymin = -Inf, ymax = Inf), fill = "gray95", alpha = 0.01) +
+
+    # Add the dashed line at x = 7
+    geom_vline(xintercept = 7, col = 'black', linetype = 'dashed', linewidth = 0.7) +
+
+    # Add the text "Flattering" on the left of the line
+    annotate("text", x = 5, y = 0.6, label = "Flattering Ranks", hjust = 1, size = 8, fontface = "bold") +
+
+    # Manual fill colors
+    scale_fill_manual(values = c("#2A629A", '#FF7F3E'), labels = c("Accurate", "Likable")) +
+
+    # X-axis adjustments
+    scale_x_continuous(name = "Advised Rank", breaks = seq(1, 10)) +
+
+    # Theme adjustments
     theme_bw() +
@@
           panel.border = element_blank(),
-        axis.line = element_line(colour = "grey"),
+          axis.line = element_line(colour = "black"),
           legend.position = "bottom",
@@
           legend.text = element_text(size = 12),
-        plot.title = element_text(hjust = 0.5, size = 20))
+          plot.title = element_text(hjust = 0.5, size = 20),
+          axis.text.x = element_text(size = 14),  # X-axis text size
+          axis.text.y = element_text(size = 14),
+          axis.title.x = element_text(size = 16, face = "bold"),  # X-axis title size
+          axis.title.y = element_text(size = 16, face = "bold"))
 
@@
 
-study2_time3 <- study2_time3 %>% dplyr::mutate(Advice = as.factor(Advice))
-
-# Create the first plot
-plot1 <- ggplot(study2_time3, aes(x = Advice)) +
-  geom_boxplot(aes(y = likable),position = position_dodge(width = 0.8), alpha = 0.8, color = "darkgrey", fill = "#2A629A") +
-  scale_y_continuous(name = "Likability") +
-  scale_x_discrete(name = "Advised Rank") +
+study2_time3 <- study2_time3 %>% dplyr::mutate(Advice = as.numeric(Advice))
+
+# Load necessary library
+library(ggplot2)
+library(dplyr)
+library(tidyr)
+
+# Reshape the data to long format
+study2_long <- study2_time3 %>%
+  pivot_longer(cols = c(likable, warmAvg), 
+               names_to = "Metric", 
+               values_to = "Value")
+
+# Create the plot
+ggplot(study2_long, aes(x = Advice, y = Value, color = Metric)) +  
+  # Add points for each observation
+  geom_point(size = 2, alpha = 0.7) +
+
+  # Add linear regression lines for each metric
+  geom_smooth(method = "lm", se = TRUE, aes(fill = Metric), alpha = 0.2, show.legend = FALSE) +
+
+  # Customize axis labels
+  scale_y_continuous(name = "Scores",limits = c(0.9, 5.1)) +  
+  scale_x_continuous(name = "Advised Rank",limits = c(1, 10), breaks = c(1,2,3,4,5,6,7,8,9,10)) +
+
+  # Apply a theme
   theme_bw() +  
@@
         axis.line = element_line(colour = "grey"),
-        legend.position = "bottom",
-        legend.title = element_blank(),
-        legend.key.size = unit(1.2, "lines"),
-        legend.text = element_text(size = 12),
-        plot.title = element_text(hjust = 0.5, size = 20))
-
-# Create the second plot
-plot2 <- ggplot(study2_time3, aes(x = Advice)) +
-  geom_boxplot(aes(y = warmAvg),position = position_dodge(width = 0.8), alpha = 0.8, color = "darkgrey", fill = "#FF7F3E") +
-  scale_y_continuous(name = "Warmth") +
-  scale_x_discrete(name = "Advised Rank") +
-  theme_bw() +
-  theme(panel.grid = element_blank(),
-        panel.border = element_blank(),
-        axis.line = element_line(colour = "grey"),
-        legend.position = "bottom",
-        legend.title = element_blank(),
-        legend.key.size = unit(1.2, "lines"),
-        legend.text = element_text(size = 12),
-        plot.title = element_text(hjust = 0.5, size = 20))
-
-# Combine the plots side by side
-grid.arrange(plot1, plot2, ncol = 2)
+        legend.position = "right",
+        plot.title = element_text(hjust = 0.5, size = 20)) +
+
+  # Set custom colors for each metric
+  scale_color_manual(values = c("#FF7F3E", "#2A629A"), 
+                     labels = c("Likability", "Warm")) + 
+  scale_fill_manual(values = c("#FF7F3E", "#2A629A"))
 
@@
 
-When the quality of a decision is not dependent on someone's
-expectations, advice should not be moved by whether an adviser is aware
-of the advisees expectations. However, consistent with our account that
-advisers consider the belief utility of the advisee and want to flatter,
-rather than disappoint them, we find that displaying expectations to
-advisers does matter. Specifically, we found that men underestimate
+ men underestimate
 their score on a mathematics test less than do women. When these

### 2024-09-30 manuscript/manuscript.Rmd
Method part

@@
 
-<!-- David: Just commenting on what I tried to do here... a bit of a transition -->
-
-<!-- for why this study follows from the last. -->
-
-So far, we have shown that displaying expectations can induce gender
-differences in advice-giving. Specifically, advisers were more likely to
-recommend competing against a group of High Performers to men who had
-higher expectations about their performance than did women. We now test
-directly whether this is driven by interpersonal concerns. Specifically,
-we examine whether more flattering advice is the result of a desire to
-be liked and whether advisees indeed do like advisers more when they
-give flattering advice.
+So far, we have shown that displaying expectations influences the advice given. 
+Specifically, advisers were more likely to recommend competing against a group 
+of high performers to advisees with higher performance expectations compared to 
+those without. We now directly test whether this effect is driven by 
+interpersonal concerns. In particular, we explore whether more flattering advice
+stems from a desire to be liked, and whether advisees, in turn, like advisers 
+more when they receive flattering advice.
 
 We conducted a three-stage experiment in which we experimentally
-manipulated the incentives for advicers. We began by inviting a group of
+manipulated the incentives for advisers. We began by inviting a group of
 advisees to upload photos of themselves ("selfies") and informed them
@@
 they had ranked as the 7th most attractive (i.e., the 4th least
-attractive). They were reminded of the rank they had given to that perso
+attractive). They were reminded of the rank they had given to that person
 and informed that this participant would be invited back and could earn
@@
 
-<!-- Amanda: How about this -->
-
-<!-- For warmth it looks interesting, but I think the plot is hard -->
-
-<!-- to read. Let's hold off on this for now. -->
-
 Finally, we examine whether flattering advice indeed leads to more
@@
 
-<!-- The Figure is not super clear. How about we try a series of box plots, -->
-
-<!-- with the x-axis as the advised rank? Standard errors will be huge at the -->
-
-<!-- extremes. -->
-
-<!-- Also, we need to do something relative to the advisees' expectations. -->
-
-<!-- I wonder what would be interesting here? Maybe averages for three groups: -->
-
-<!-- more attractive than the participants' own guess, equally attractive, and less -->
-
-<!-- attractive? -->
-
-<!-- Amanda: How about the following picture? -->
-
 ```{r study2rating, fig.cap="Participants tend to rate advisors who suggest betting on a higher rank (implying greater attractiveness) as more likable and warm."}
@@
 library(ggplot2)
+library(reshape2)
 
@@
   dplyr::mutate(HorL = as.factor(HorL)) %>% 
-  dplyr::mutate(bonus = ifelse(bet == `Final Rank`,1,0))
+  dplyr::mutate(bonus = ifelse(bet == `Final Rank`,1,0)) %>%
+  dplyr::mutate(accuracy = `Final Rank`-Advice)
 
@@
   group_by(HorL) %>%
-  summarise(like = mean(likable), warmth = mean(warmAvg))
-
-rating_table <- matrix(c(ratings$like,ratings$warmth), nrow = 2, byrow = TRUE, dimnames = list( c("Likable",'Warm'),c("Pessimistic", "Accurate", "Flattering")))
+  summarise(like = round(mean(likable),2), warmth = round(mean(warmAvg),2))
+
+rating_table <- matrix(c(ratings$like,ratings$warmth), nrow = 2, byrow = TRUE, dimnames = list( c("Likable",'Warm'),c("Lower than", "Equal to", "Higher than")))
 
@@
 
-ggplot(rating_df, aes(x = Advice, y = Freq, fill = Condition)) +
-  geom_bar(stat = "identity", position = "dodge") +
-  scale_fill_manual(values = c("#2A629A",'#FF7F3E')) +
-  labs(x = "Advice", y = "Rating") +
-  ggtitle('Response to Advice') +
-  theme_bw() +
-  theme(panel.grid = element_blank(),
-        panel.border = element_blank(),
-        axis.line = element_line(colour = "grey"),
-        legend.position = "bottom",
-        legend.title = element_blank(),
-        legend.key.size = unit(1.2, "lines"),          
-        legend.text = element_text(size = 12),
-        plot.title = element_text(hjust = 0.5, size = 20)) +
-  geom_text(aes(label = paste0(Freq), y = 0.5), position = position_dodge(width = 0.9), size = 5, color = 'white', fontface = "bold")
+# Create a data frame similar to your structure
+data <- rating_df
+
+# Reshape the data to wide format for the heatmap
+heatmap_data <- dcast(data, Condition ~ Advice, value.var = "Freq")
+
+# Melt the data for ggplot
+melted_data <- melt(heatmap_data, id.vars = "Condition", variable.name = "Advice", value.name = "Rating")
+
+# Create the heatmap
+ggplot(melted_data, aes(x = Advice, y = Condition, fill = Rating)) +
+  geom_tile(color = "white") +
+  scale_fill_gradient(low = "grey80", high = "grey30", name = "Rating") +  # Grey gradient from light to dark
+  geom_text(aes(label = sprintf("%.2f", Rating)), color = "white", size = 8) +
+  theme_minimal() +
+  labs(x = "Attractiveness (Advice Relative to Self-Expectations)", y = "Evaluation") +
+  theme(
+    axis.text.x = element_text(size = 12),  # X-axis text size
+          axis.text.y = element_text(size = 12),
+          axis.title.x = element_text(size = 12),  # X-axis title size
+          axis.title.y = element_text(size = 12))
 
@@
 `r papaja::apa_print(t.test(warmAvg ~ Condition, data = study2_time3, var.equal = T))$statistic`,
-respectively).
+respectively). We also assess the quality of advice by measuring the 
+discrepancy between the advised rank and the final rank. Our analysis
+revealed no significant difference between the two treatments in terms 
+of how helpful the advice was for advisees in making accurate guesses,
+`r papaja::apa_print(t.test(accuracy ~ Condition, data = study2_time3, var.equal = T))$statistic`.
 
@@
 
-In a context where advice communicates ego-relevant information (here,
+In another context where advice communicates ego-relevant information (here,
 people's attractiveness), we find that the advice people give is
@@
 
-We begin by examining whether advisers take the expectations of advisees
-into account, even when those expectations are not relevant to the
-decision the advisee has to make. In a three-stage experiment, we first
-recruit a sample of advisees and ask them to complete a mathematics
-quiz. After answering ten multiple-choice questions, participants are
-anchored to low or high performance expectations and asked to guess how
-many questions they answered correctly. Next, we recruit advisers and
-show them either only the true performance of the advisee, or the true
-performance and how many questions they guessed they answered correctly.
-Advisers are tasked with recommending whether the advisee should compete
-against a group of high-performers or a group of low-performers on the
-mathematics quiz, where a potential bonus depends on outperforming the
-competitor and which group was chosen. Finally, we invite the advisees
-back and show them the advice they have received. Advisees then pick
-whether to compete against high or low performers, with the outcome
-determined by their past performance on the quiz. Our key hypotheses are
-that (1) advisees who were anchored to high expectations would be more
-likely to receive advice to compete against the high performer group,
-and (2) that men are more likely than women to be advised to compete
-against the high-performer group when expectations are shown.
+In Study 3, we replicate the main effect in a different ego-relevant domain: 
+intelligence. The experimental design is conceptually identical to Study 1, 
+but this time we utilize a more direct measure of expectation by asking 
+participants to estimate their scores.
+
+This three-stage experiment begins with measuring actual performance. 
+Participants are then anchored to low or high performance expectations 
+and asked to guess how many questions they answered correctly. As in 
+previous studies, we recruit advisers who are presented with either 
+just the advisee's true performance or both the true performance and 
+the number of questions the advisee believes they answered correctly. 
+Advisers are then asked to provide advice on choosing a competitor. 
+Finally, we present the advice to the advisees and ask them to make 
+their final choice. Our key hypotheses are: (1) advisees anchored to 
+high expectations will be more likely to receive advice to compete 
+against the high-performing group, and (2) men will be more likely 
+than women to be advised to compete against the high-performing group
+when expectations are disclosed.
 
@@
 
-As part of our main experiment, participants choose to compete against a
-group of previous participants and have their expectations anchored
-based on their performance. Thus, we begin by first recruiting a sample
+We begin by first recruiting a sample
 of `r scales::comma(dim(study3_math50)[1])` participants from Prolific
@@
 minutes to answer the quiz and were paid 10 cents for each correctly
-answered question. We define the top 20 scorers as the "High Performers"
+answered question. Like before, we define top 20 scores as "High Performers"
 and the bottom 20 scorers as the "Low Performers." On average,
@@
 more flattering and hence being told to compete against the Low
-Performers would be disappointing if one had expected to do well.
-Advisees would earn 30 cents if their score was equal to or higher than
-a randomly selected member of the Low Performer group and they chose to
-compete against this group, or 50 cents if they performed as well or
-better than a randomly selected member of the High Performer group and
-they chose to compete against that group. If they scored lower, they
-would not receive any bonus.
-
-Advisers were randomly assigned to one of two treatments. In the
+Performers would be disappointing if one had expected to do well. Advisees
+could earn a bonus if their score was equal to or higher than that of 
+a randomly selected member from their chosen group. Competing against 
+the High Performers was more challenging, resulting in an average bonus
+of 50 cents, compared to 30 cents when competing against other groups.
+
+Like before, advisers were randomly assigned to one of two treatments. In the
 "Baseline" treatment, they only observed the score of the advisee on the
@@
 score as well as the advisee's guess for how many questions they
-answered correctly. Note that since the outcome is determined only by
+answered correctly. We want to emphasize that sice the outcome is determined only by
 the past score on the quiz, the advisee's guess is immaterial to which
@@
 library(ggplot2)
-library(magrittr)
-
+
+# Calculate averages for the performance, grouped by condition and gender
 ProbHG <- study3_advice %>%  
   group_by(Condition, Performance, Gender) %>%  
-  dplyr::summarize(avg_hardGroup = mean(Advice))
-
-df_exp <- subset(ProbHG, Condition == "E")
-df_none <- subset(ProbHG, Condition == "None")
-
-ggplot(df_exp, aes(x = Performance, y = avg_hardGroup, color = Gender)) +
-  geom_smooth(method = "glm", method.args = list(family = "binomial"),se = FALSE) +
-  geom_smooth(data = df_none, aes(x = Performance, y = avg_hardGroup),
-              method = "glm", method.args = list(family = "binomial"), color = "grey", se = FALSE) +
-  scale_color_manual(values = c("#2A629A",'#FF7F3E', "grey"),
-                     labels = c("Female + Expectations", "Male + Expectations", "Expectation Hidden")) +
+  summarise(avg_hardGroup = mean(Advice), .groups = 'drop')
+
+# Create a data frame for the NONE condition as the baseline
+baseline <- ProbHG %>%  
+  filter(Condition == "None") %>%  
+  select(Performance, baseline_avg = avg_hardGroup)
+
+# Merge with the original data to get comparison values
+comparison_data <- ProbHG %>%  
+  filter(Condition != "None") %>%  
+  left_join(baseline, by = "Performance") %>%  
+  mutate(diff = avg_hardGroup - baseline_avg)  # Calculate the difference
+
+# Create a scatter plot comparing conditions with NONE as baseline
+ggplot() +
+  # Step lines for the NONE condition
+  geom_segment(data = baseline,
+               aes(x = Performance, 
+                   xend = lead(Performance, 1),  # Create horizontal lines to the next performance point
+                   y = baseline_avg, 
+                   yend = baseline_avg,
+                   linetype = "None"), 
+               color = "grey70", size = 0.5, 
+               na.rm = TRUE,
+               show.legend = TRUE) + 
+  geom_point(data = comparison_data %>% filter(Gender == "Male"), 
+             aes(x = Performance + 0.5, y = avg_hardGroup, shape = Gender, color = Gender), 
+             size = 4) +  # Males with an offset to the left
+  geom_point(data = comparison_data %>% filter(Gender == "Female"), 
+             aes(x = Performance + 0.5, y = avg_hardGroup, shape = Gender, color = Gender), 
+             size = 4) +  # Females with an offset to the right
+  scale_shape_manual(values = c(16, 17), labels = c("Female", "Male")) +  # Circle for Females, Triangle for Males
+  scale_color_manual(values = c( "#FF7F3E","#2A629A"), 
+                     labels = c("Female", "Male")) +  
   scale_y_continuous(name = "P(Compete Against High Performance)",
                      labels = scales::percent,
-                     expand = c(0, 0)) +
+                     limits = c(0, 1.1),
+                     breaks = c(0,1)) +  # Set limits for y-axis
   scale_x_continuous(name = "Performance",
-                     expand = c(0, 0),
-                     breaks = seq(0, 10, 2)) +
+                     limits = c(0, 11),expand = c(0, 0), 
+                     breaks = seq(0, 10, 1)) +  
   theme_bw() +  
@@
         plot.title = element_text(hjust = 0.5, size = 20))
+
 ```
@@
 \@ref(fig:study3genderdiff)).
-
-<!-- Amanda: The gender discrepancy in advice is more significant when performance is less decisive.
-When performance is extremely low, there is no chance to win high performers and only a slim chance when competing with low performers.
-When performance is extremely high, it makes no sense to forgo the high chance to win more and choose a low bonus.
-However, in the middle range of performance, either option has pros and cons, and neither is absolutely better.
-In such a situation, advisers would take participants' expectations into account, regarding them as a critical factor.
--->
-
-<!-- David: If we plotted on the x-axis performance and on the y-axis the difference -->
-
-<!-- between recommendations for men & women, this would look inverse-U shaped, right? -->
-
-<!-- Might be a nice way to illustrate what you describe. -->
-
-<!-- Amanda: I think our primary purpose here is still showing the existence of gender difference -->
-
-<!-- The current plot shows discrepancy between two lines, allowing us to demonstrate gender gap -->
 
@@
 
- men underestimate
-their score on a mathematics test less than do women. When these
-expectations are displayed to advisers, they are more likely to tell men
-to compete against the High Performer group. Notably, this is bad
-advice: men whose advisers observed their expectations got worse advice
-as a result. Our findings suggest that males with the same scores as
-their female counterparts earned less, although the evidence is only
-directional. This may be due to males receiving more favorable advice
-and being more likely to adopt it, resulting in even worse outcomes.
+We found supportive evidence for our argument in a different domain. 
+Advisors tend to consider advisees' self-expectations and match 
+their advice accordingly, aiming to avoid disappointment. Consistent
+with the confidence gap narrative, men tend to underestimate their 
+mathematics test scores less than women. When these expectations are
+displayed to advisors, they are more likely to advise men to compete
+against high performers. Notably, this turns out to be poor advice: 
+men whose advisors were aware of their expectations received worse 
+advice. Our findings suggest that men with the same scores as their
+female counterparts ended up earning less, although this result is 
+only directional. This discrepancy may be due to men receiving more
+favorable advice, being more likely to follow it, and ultimately 
+facing worse outcomes.
 

### 2024-09-30 manuscript/manuscript.Rmd
Three studies

@@
 
-study2_time3 <- study2_time3 %>% dplyr::mutate(Advice = as.numeric(Advice))
-
-# Load necessary library
 library(ggplot2)
@@
 
+study2_time3 <- study2_time3 %>% dplyr::mutate(Advice = as.numeric(Advice))
+
 # Reshape the data to long format
@@
   pivot_longer(cols = c(likable, warmAvg), 
-               names_to = "Metric", 
+               names_to = "Evaluation", 
                values_to = "Value")
@@
 # Create the plot
-ggplot(study2_long, aes(x = Advice, y = Value, color = Metric)) +  
+ggplot(study2_long, aes(x = Advice, y = Value, color = Evaluation)) +  
   # Add points for each observation
@@
   # Add linear regression lines for each metric
-  geom_smooth(method = "lm", se = TRUE, aes(fill = Metric), alpha = 0.2, show.legend = FALSE) +
+  geom_smooth(method = "lm", se = TRUE, aes(fill = Evaluation), alpha = 0.2, show.legend = FALSE) +
 
   # Customize axis labels
-  scale_y_continuous(name = "Scores",limits = c(0.9, 5.1)) +  
+  scale_y_continuous(name = "Evaluation",limits = c(0.9, 5.1)) +  
   scale_x_continuous(name = "Advised Rank",limits = c(1, 10), breaks = c(1,2,3,4,5,6,7,8,9,10)) +

### 2024-10-08 manuscript/manuscript.Rmd
Abstract

@@
 abstract: |
-  The purpose of advice is typically understood as helping recipients make better decisions and solve problems.
-However, in this paper, we propose that advisors also consider the recipient's belief utility and may try to avoid disappointing them, leading to what we term "flattering advice." Across three pre-registered experiments involving real interactions between advisors and advisees (n = 3,900), we demonstrate that individuals factor in others' expectations when giving advice, even when those expectations are not relevant to solving the decision-making problem.
-Specifically, advisors take advisees' expectations into account, tailoring their advice to create a more positive impression of the advisee and avoid causing disappointment.
-(Study 1).
+  The primary purpose of advice is often seen as helping recipients make better decisions and solve problems.
+However, this paper reveals that advisors are also influenced by interpersonal concerns.
+Specifically, we propose that advisors consider the recipient's "belief utility" and may seek to avoid disappointing them, resulting in what we call "flattering advice." Through three pre-registered experiments involving real interactions between advisors and advisees (n = 3,900), we demonstrate that advisors account for advisees' expectations, even when irrelevant to solving the problem.
+Specifically, advisors tailor their advice to match advisees' expectations about their own capabilities, aiming to avoid disappointing them (Study 1).
 Advisors inflate their advice due to interpersonal concerns, with those who care about being liked by the advisee inflating their advice to a greater extent.
-Advisees, in turn, reward this flattery, perceiving these advisors as more likable and equally trustworthy compared to those who give more accurate advice (Study 2).
+Advisees, in turn, reward this flattery, perceiving these advisors as more likable and equally trustworthy compared to those who aim to give more accurate advice (Study 2).
 Additionally, when advisors match advisees' expectations, men tend to receive more aspirational advice than women, due to their higher confidence, even when only expectations (not gender) are visible to the advisor.

### 2024-10-08 manuscript/manuscript.Rmd
Before GD

@@
 keywords          : "Gender difference, Advice, Interpresonal relationship"
-wordcount         : "4,362"
+wordcount         : "6,104"
 figsintext        : yes
@@
 
-Seeking and giving advice can present conversational challenges that are
-difficult to navigate. Advice seekers may be embarrassed to ask for help
-[@Benabou2022], and they may fail to do so if the information they
-receive could lead to disappointment [@Gill2012]. Indeed, people prefer
-advisers who withhold unpleasant information [@Shalvi2019] and punish
-those who tell them things they do not want to hear [@John2019]. People
-appear to engage in strategic selection of advice to avoid unpleasant
-information and protect the utility they get from positive beliefs about
-themselves and the future they anticipate [@Loewenstein2018;
-@Loewenstein1987]. But do advice givers anticipate and consider the
-hedonic cost of honest information to the recipient? While previous work
-has emphasized the instrumental value of advice (e.g., satisfaction with
-a decision or accuracy of a prediction), we focus on the motivations of
-the person providing advice.
-
-Research on advice has largely focused on settings that do not tackle
-belief utility. For example, participants may have been asked to
-estimate the number of balls in an urn or choose from pairs of lotteries
-[@Benjamin2015]. Advisers have been shown to be motivated to give
-accurate advice [@Jonas2003], and engage in perspective-taking to meet
-the preferences of the advisee [@Kray2000; @Kray1999]. When they are
-uncertain, they even prefer that advisees do not rely (extensively) on
-their recommendations [@Ache2020]. Thus, it seems that people are
-concerned about providing good advice even when they are not
-incentivized for the recipient's decision quality.
-
-In many real settings, however, advice incorporates beliefs about the
+We frequently seek and offer advice, often with the hope of solving problems 
+more effectively. Whether we are navigating personal dilemmas or making 
+professional decisions, advice is seen as a valuable tool for improving 
+outcomes. For instance, in some studies, participants are asked to estimate 
+quantities or choose between lotteries [@Benjamin2015]. Advisors are often 
+motivated to provide accurate advice [@Jonas2003], and engage in perspective-taking
+to align with the preferences of the advisee [@Kray2000; @Kray1999]. When 
+uncertain, they may even prefer that advisees rely less on their recommendations
+[@Ache2020]. This suggests that people are generally concerned with offering 
+good advice, assuming accuracy is the primary objective.
+
+Indeed, seeking and giving advice often involve complex conversational dynamics 
+that can be challenging to manage. People frequently struggle with 
+decisions about whom to approach for advice, whether they seek it too 
+often or too little, and the potential consequences of asking for advice—or
+failing to—when it’s expected [@lee1997;@minson2012;@see2011]. 
+From the advisor's perspective, factors such as knowledge and expertise [@sniezek2001],
+confidence [@sah2013], age [@zhang2020], and communication style [@yaniv2012]
+also play critical roles in determining whether accurate advice is 
+effectively conveyed.
+
+While much of the advice literature emphasizes the instrumental value of 
+advice—such as improving decision satisfaction or prediction accuracy, assuming
+both parties prioritize accuracy—research suggests that solving the problem is 
+not the only concern in these interactions. Advice seekers may feel embarrassed 
+to ask for help [@Benabou2022] and may avoid seeking advice if they fear the 
+information could lead to disappointment [@Gill2012]. Moreover, people tend 
+to favor advisors who withhold unpleasant information [@Shalvi2019] and even 
+punish those who tell them things they would rather not hear [@John2019] This 
+indicates that individuals strategically select advice to shield themselves 
+from uncomfortable truths, protecting the positive beliefs they hold about 
+themselves and their anticipated future [@Loewenstein2018;
+@Loewenstein1987]. But do advice givers recognize and account 
+for the emotional cost of delivering honest information to the recipient?
+
+In many real settings, advice often incorporates beliefs about the
 recipient. Someone recommending an expensive restaurant conveys that
@@
 
-In a large, preregistered experiment (n = 1,200), we show that advisers
-consider the expectations of advisees, even when such expectations do
-not provide informative insights for the underlying decision-making
-problem. We find that as a result, showing expectations (but not gender)
-to advisers leads men to receive more aspirational advice than women.
-Incorporating expectations leads to worse advice, even when advisers are
-incentivized based on the outcome of the advisee's decision. In a second
-preregistered experiment (n = 700), we show that advisers respond to
-incentives for interpersonal considerations. They tell people that they
-are more attractive than they believe them to be, and inflate to a
-greater extent when incentivized for likability rather than accuracy.
-Notably, they inflate even when only incentivized for accuracy. Advisees
-indeed reward such flattering advice, rating the advisers more likeable
-and no less trustworthy than those who provide more accurate advice.
+In a large, preregistered experiment (n = 1,200), we demonstrate that 
+advisors take into account advisees' expectations, even when those expectations
+offer no relevant insights for solving the decision-making problem. 
+Advisors were more likely to encourage advisees to compete against strong
+competitors when they saw that the advisees had high expectations of their 
+own abilities, compared to when the advisees had low expectations. In a second
+preregistered experiment (n = 700), we show that advisors respond to interpersonal
+incentives, telling advisees they are more attractive than they believe, and 
+inflating their advice more when incentivized for likability rather than accuracy.
+Notably, they still inflate their advice even when incentivized solely for accuracy.
+Advisees, in turn, reward this flattering advice, rating these advisors as more 
+likable and no less trustworthy than those who provide more accurate feedback. 
+In the third preregistered experiment (n = 2,000), we replicate the finding that
+advisors consider advisees' expectations when giving advice. Additionally, we find
+that when only expectations (but not gender) are shown, men receive more aspirational
+advice than women. This tendency to factor in expectations ultimately leads to poorer
+advice, even when advisors are incentivized based on the outcome of the advisee’s 
+decision.
 

### 2024-12-12 manuscript/manuscript.Rmd
Intro edits (in progress)

@@
 
-We frequently seek and offer advice, often with the hope of solving problems 
-more effectively. Whether we are navigating personal dilemmas or making 
-professional decisions, advice is seen as a valuable tool for improving 
-outcomes. For instance, in some studies, participants are asked to estimate 
+Individuals seek (and give) advice on complex choices in their professional and
+personal lives. While advice is widely viewed as a mechanism for improving 
+outcomes (CITE), recent findings suggest systematic gender differences in 
+the advice received: men are more likely to be encouraged toward competitive 
+positions and risk-taking behaviors (CITE, if real), and women are less likely to receive
+criticism (CITE). These differences in advice can result in gender gaps in
+career advancement, as opportunities often depend on individuals applying (even
+if they do not meet all requirements, CITE-women apply for jobs when they meet all reqs)
+and direct feedback, even if unpleasant, can help people improve their performance.
+In this paper, we propose and present evidence for a novel mechanism to explain
+gendered patterns in advice received: advisers are motivated by interpersonal
+considerations and do not want to disappoint the advisee.
+
+Models of decision-making that incorporate belief utility (Loewenstein & Molnar) 
+imply a tradeoff between the benefits from having accurate beliefs and the
+hedonic costs of receiving bad news. For example, someone expecting a good outcome
+may feel disappointment if the realized outcome is not as good as what they had
+expected holding accurate beliefs and the hedonic
+costs of receiving bad news, such as disappointment from a desired outcome
+failing to materialize (Gul and Pesendorfer, I think, disappointment aversion, Golman et al 2017). 
+Because outcomes are frequently evaluated with respect to expectations
+(Koszegi and Rabin), advice that falls short of someone's expectation can be
+painful. Thus, advice may be shaped by the *beliefs* about someone else's
+expectations.
+
+perpetuate gender gaps in career advancement, as many opportunities depend on 
+individual initiative and self-selection. This paper proposes a novel mechanism 
+to explain gendered patterns in advice-giving: advisors calibrate their 
+recommendations to match perceived advisee expectations. In professional 
+contexts where women typically demonstrate lower confidence levels, advisors 
+may provide less ambitious guidance that aligns with these reduced expectations.
+In two experimental studies, we establish evidence for this expectation-matching 
+mechanism. Specifically, men are more confident in their performance on a task
+than women and advisers, who observe performance and confidence but not gender,
+give more flattering advice to men than to women. A third experiment shows that 
+advisors strategically provide "flattering" advice to avoid disappointing their 
+advisees, further illuminating how interpersonal dynamics shape advice content.
+
+For instance, in some studies, participants are asked to estimate 
 quantities or choose between lotteries [@Benjamin2015]. Advisors are often 

### 2024-12-15 manuscript/manuscript.Rmd
Edits up to study1regs

--- 2024-10-08 manuscript/manuscript.Rmd
@@
 ---
-title: "Flattering Advice: Avoiding Disappointment as a Driver of Gender Discrimination"
+title: "Flattering Advice: Avoiding Disappointment in Advice-Giving"
 shorttitle        : "Flattering Advice"
@@
 abstract: |
-  The primary purpose of advice is often seen as helping recipients make better decisions and solve problems.
-However, this paper reveals that advisors are also influenced by interpersonal concerns.
-Specifically, we propose that advisors consider the recipient's "belief utility" and may seek to avoid disappointing them, resulting in what we call "flattering advice." Through three pre-registered experiments involving real interactions between advisors and advisees (n = 3,900), we demonstrate that advisors account for advisees' expectations, even when irrelevant to solving the problem.
-Specifically, advisors tailor their advice to match advisees' expectations about their own capabilities, aiming to avoid disappointing them (Study 1).
-Advisors inflate their advice due to interpersonal concerns, with those who care about being liked by the advisee inflating their advice to a greater extent.
-Advisees, in turn, reward this flattery, perceiving these advisors as more likable and equally trustworthy compared to those who aim to give more accurate advice (Study 2).
-Additionally, when advisors match advisees' expectations, men tend to receive more aspirational advice than women, due to their higher confidence, even when only expectations (not gender) are visible to the advisor.
-However, relying on these expectations leads to poorer decision outcomes (Study 3).
-We conclude by discussing the practical and theoretical implications of our findings, as well as directions for future research.
+  Good advice improves decision quality but often requires delivering unpleasant truths that may disappoint advisees.
+Across three pre-registered and incentivized experiments involving real adviser-advisee interactions (n = 3,900), we demonstrate that advisers prioritize avoiding disappointment, even at the expense of accuracy.
+In Study 1, advisers financially rewarded for accuracy still tailored recommendations to aspirational goals expressed by advisees, resulting in poorer advice.
+When incentivized to be liked, advisers provided even more flattering advice, and advisees rated these advisers as more likable, despite the advice being less honest and less accurate (Study 2).
+In Study 3, advisers incorporated advisees' subjective and uninformative performance expectations into recommendations, leading to systematically different advice for men and women.
+Because men expected to perform better than women, they received more aspirational advice, even when their gender was unknown to advisers.
+Advisers' efforts to avoid disappointment may thus contribute to systematic gender disparities in advice, with implications for downstream decision-making and equity.
 
@@
 # Introduction
-
-We frequently seek and offer advice, often with the hope of solving problems 
-more effectively. Whether we are navigating personal dilemmas or making 
-professional decisions, advice is seen as a valuable tool for improving 
-outcomes. For instance, in some studies, participants are asked to estimate 
-quantities or choose between lotteries [@Benjamin2015]. Advisors are often 
-motivated to provide accurate advice [@Jonas2003], and engage in perspective-taking
-to align with the preferences of the advisee [@Kray2000; @Kray1999]. When 
-uncertain, they may even prefer that advisees rely less on their recommendations
-[@Ache2020]. This suggests that people are generally concerned with offering 
-good advice, assuming accuracy is the primary objective.
-
-Indeed, seeking and giving advice often involve complex conversational dynamics 
-that can be challenging to manage. People frequently struggle with 
-decisions about whom to approach for advice, whether they seek it too 
-often or too little, and the potential consequences of asking for advice—or
-failing to—when it’s expected [@lee1997;@minson2012;@see2011]. 
-From the advisor's perspective, factors such as knowledge and expertise [@sniezek2001],
-confidence [@sah2013], age [@zhang2020], and communication style [@yaniv2012]
-also play critical roles in determining whether accurate advice is 
-effectively conveyed.
-
-While much of the advice literature emphasizes the instrumental value of 
-advice—such as improving decision satisfaction or prediction accuracy, assuming
-both parties prioritize accuracy—research suggests that solving the problem is 
-not the only concern in these interactions. Advice seekers may feel embarrassed 
-to ask for help [@Benabou2022] and may avoid seeking advice if they fear the 
-information could lead to disappointment [@Gill2012]. Moreover, people tend 
-to favor advisors who withhold unpleasant information [@Shalvi2019] and even 
-punish those who tell them things they would rather not hear [@John2019] This 
-indicates that individuals strategically select advice to shield themselves 
-from uncomfortable truths, protecting the positive beliefs they hold about 
-themselves and their anticipated future [@Loewenstein2018;
-@Loewenstein1987]. But do advice givers recognize and account 
-for the emotional cost of delivering honest information to the recipient?
-
-In many real settings, advice often incorporates beliefs about the
-recipient. Someone recommending an expensive restaurant conveys that
-they think the advisee is wealthy enough to afford an expensive meal,
-and someone recommending a student pursue a PhD in economics assumes
-that they are intellectually capable. Conversely, telling a poorly
-performing student to switch to a less-demanding major conveys a belief
-that the student is not capable of improving. Thus, while the painful
-truth may prevent someone from making a bad decision, it may come at a
-hedonic cost to the recipient and damage the relationship between the
-adviser and advisee. We propose that advisers take these costs into
-account, even when the interactions are entirely anonymous and they are
-incentivized for the quality of the advisee's decision.
-
-Specifically, we focus on the signaling value of advice: what does the
-advice imply about the adviser's perception of the advisee? We propose
-that advisees have expectations about the advice they receive and treat
-this as a reference point [@Koszegi2006]. Advice that falls short of
-these expectations creates disappointment, while advice that exceeds
-them is flattering and creates positive interpersonal benefits because
-it creates a perception that the adviser holds the advisee in high
-esteem. Such interpersonal considerations may be as important, if not
-more important, to the adviser than the instrumental value of the
-advice: the adviser directly experiences a souring relationship, but may
-suffer little and only much delayed consequences if an advisee makes a
-poor life decision.
-
-Our account therefore predicts that people give and receive advice that
-is more flattering and suggestive of inflated ability and optimistic
-outcomes than would advice in the absence of such interpersonal
-considerations. However, we propose that this is not true for all
-advisees equally. Presenting flattering advice requires the formation of
-beliefs about the advisee's expectations (reference point). @Exley2022
-show that men are more overconfident than women, conditional on equal
-performance, and that people anticipate this difference. An adviser who
-seeks to avoid disappointment and incorporates expectations into their
-advice would then present more favorable advice to male advisees than to
-female advisees (see Figure 1 for an illustration). This provides a
-novel account for a well-known finding that men receive more
-aspirational advice than do women [@Kanze2018]. Notably, when it pays to
-have accurate beliefs, such flattering advice would come at a cost:
-while men would be more likely to aim higher, they would also suffer
-greater costs from aiming too high and failing to meet the objective.
-
-In a large, preregistered experiment (n = 1,200), we demonstrate that 
-advisors take into account advisees' expectations, even when those expectations
-offer no relevant insights for solving the decision-making problem. 
-Advisors were more likely to encourage advisees to compete against strong
-competitors when they saw that the advisees had high expectations of their 
-own abilities, compared to when the advisees had low expectations. In a second
-preregistered experiment (n = 700), we show that advisors respond to interpersonal
-incentives, telling advisees they are more attractive than they believe, and 
-inflating their advice more when incentivized for likability rather than accuracy.
-Notably, they still inflate their advice even when incentivized solely for accuracy.
-Advisees, in turn, reward this flattering advice, rating these advisors as more 
-likable and no less trustworthy than those who provide more accurate feedback. 
-In the third preregistered experiment (n = 2,000), we replicate the finding that
-advisors consider advisees' expectations when giving advice. Additionally, we find
-that when only expectations (but not gender) are shown, men receive more aspirational
-advice than women. This tendency to factor in expectations ultimately leads to poorer
-advice, even when advisors are incentivized based on the outcome of the advisee’s 
-decision.
+Advice plays a critical role in both professional and personal decision-making, 
+often serving as a crucial tool for navigating complex challenges and improving 
+outcomes [@Gino2007; @Harvey1997; @Soll2009]. While prior research has 
+extensively examined the *recipients* of advice (e.g., how they evaluate or act 
+on recommendations) far less attention has been devoted to understanding the 
+motivations and behaviors of the *givers* of advice. In this paper, we shift the 
+focus to advisers, proposing that their recommendations are shaped not only by 
+accuracy considerations but also by interpersonal concerns. Specifically, we 
+propose that advisers factor in advisees' subjective expectations, providing 
+flattering advice that aligns with these expectations, even when doing so leads 
+to objectively worse recommendations. Notably, this tendency persists in our 
+experimental settings, where advisees' expectations are clearly uninformative 
+and advisers are financially incentivized for accuracy.
+
+Advice is often viewed as a mechanism to improve decision satisfaction or 
+prediction accuracy, assuming both parties prioritize solving the problem at 
+hand. However, prior research highlights that interpersonal dynamics can 
+complicate these interactions. Advice seekers may avoid asking for help due to 
+fear of rejection [@Benabou2022], and people generally have been shown to avoid
+information that could lead to disappointment [@Gill2012; @Golman2017]. 
+They are motivated to avoid unpleasant truths in an ethical dilemma [@Shalvi2019] 
+and dislike those who deliver unwelcome feedback even when they had no role in
+the outcome [@John2019]. These tendencies align with models of belief utility 
+[@Loewenstein2018], which suggest that individuals experience 
+hedonic costs when receiving bad news. A natural reference point for evaluating 
+the valence of advice is the advisee's expectation in the absence of advice
+[@Koszegi2006]. Consequently, advisers who are aware of expectations may 
+strategically adapt their advice to avoid delivering bad news, even at the 
+expense of accuracy.
+
+This interpersonal dimension of advice-giving has significant implications for 
+understanding systematic gender differences in advice quality. Men are more 
+likely than women to receive aspirational advice and encouragement to pursue 
+competitive or risky opportunities [@Kanze2018]. Conversely, women are often 
+shielded from criticism [@Jampol2023], which, while intended to be kind, 
+may ultimately limit their professional growth. We propose a novel mechanism to 
+explain these patterns: advisers calibrate their recommendations to match 
+advisees’ expectations. Because, in many tasks (including those in our experiments)
+men are more confident and have higher expectations about their performance than
+do women, they are more likely to receive flattering (but, in our setting, worse) 
+advice.
+
+We present evidence for this mechanism from three preregistered and incentivized 
+experiments involving real interactions between advisers and advisees (N = 3,900). 
+In Study 1, we experimentally manipulate advisee's expectations and show
+that advisers account for those expectations, even when they offer no relevant
+insight for the decision. In Study 2, we show that advisers put more weight on
+interpersonal concerns when they are incentivized to be liked. Advisees reward
+this flattery by rating advisers as more likeable and equally trustworthy compared
+to those offering more honest (and accurate) feedback. In Study 3, we measure
+expected performance on a math quiz and show that advisers take these expectations
+into account even when they have information about actual performance. Because
+men expect to score higher, they are more likely to be advised to compete against
+a stronger group for a higher potential payment than are women, even when advisers
+are unaware of the advisees' gender. Notably, this leads to worse advice for men.
 
@@
 # Study 1
-In Study 1, we investigate whether givers take into account advisees' expectations 
-when providing advice. We compare the advice given to recipients who expressed either
-high or low expectations, across two treatments: one where givers were aware of these 
-expectations (Expectation treatment) and one where this information was unknown to them 
-(Performance treatment).
-
-The experiment consisted of three stages, in which we manipulated advisees' expectations and whether givers had access to this information.
-First, we measured participants' performance, then informed them that their performance would be compared to that of another participant, with the higher scorer eligible to win a bonus.
-Participants were asked to choose their competitor from either the top 20 performers ("High Performer Group") or the bottom 20 performers ("Low Performer Group") out of a pool of 50 competitors.
-We nudged participants to have high or low expectations by encouraging them to compete against either the High Performer Group or the Low Performer Group.
-Advisors were randomly assigned to one of two treatments: seeing only performance information or both performance and expectation information.
-We hypothesize that advisees who indicate they are capable of competing against strong competitors will be more likely to receive advice to do so.
+We first examine whether advisers take into account the expectations of advisees
+when providing a recommendation. A group of participants ("Advisees") complete 
+a quiz consisting of ten questions that draw on ego-relevant domains. They then
+express a non-binding preference to compete against a group of high performers
+or low performers on the same task, based on their past performance. We nudge
+participants towards picking either the low or the high performer group by 
+selecting one of the two by default. A second group of participants ("Advisers") 
+observe Advisees' score on the quiz and, in one treatment, also which group
+they had selected. We predicted that Advisees who were nudged toward the high
+performer group would be more likely to receive advice to compete against this
+high group when Advisers observed their non-binding choice.
 
 ## Methods
-
-As part of our main experiment, participants were asked to choose a group 
-of previous participants to compete against. To create these groups, we 
-first recruited a sample of  `r scales::comma(dim(study1_ability50)[1])`
-participants from Prolific to complete a 10-question ability quiz. The quiz 
-included word puzzles, identifying emotions from photos, and selecting the
-best responses in given scenarios. These questions were adapted from surveys 
-that measure problem-solving, emotional intelligence, and communication
-skills. We selected these specific abilities based on a pretest in which 
-participants ranked them as the three most critical skills in modern society, 
-making performance on this task ego-relevant.Participants had five minutes to 
-answer the quiz and were paid 5 cents for each correctly answered question. 
-We define the top 20 scorers as the "High Performer Group"
-and the bottom 20 scorers as the "Low Performer Group."
-
-We then recruited `r scales::comma(dim(study1_time1)[1])`
-participants to serve as advisees in Stage 1 of our main experiment. These 
-participants completed the same 10-item ability quiz as the earlier group, 
-with the opportunity to earn 5 cents for each correct answer. After the 
-quiz, we asked them to indicate their initial preference for competitors. 
-Half of the participants were randomly shown the default option of the 
-'High Performer Group,' highlighted in blue ("High Default" treatment), while the other half were 
-shown the 'Low Performer Group' as the default ("Low Default" treatment). This manipulation was 
-designed to influence advisees' expectations, as advisees who believed 
-they could compete against stronger competitors were perceived by givers 
-to have higher expectations. However, participants were free to opt out 
-of the default choice.
+In a preliminary stage, we recruited `r scales::comma(dim(study1_ability50)[1])` 
+participants from Prolific and gave them five minutes to complete a quiz 
+consisting of ten items. The quiz included word puzzles,
+identifying emotions from photos, and selecting the best responses for hypothetical
+scenarios. These questions were adapted from surveys that measure problem-solving,
+emotional intelligence, and communication skills---which we pre-tested as being
+important in modern society and hence where participants might have a stake in
+doing well. Participants received a bonus of five cents for each correctly
+answered question. We then ranked them based on their score and label the 20
+participants with the lowest (highest) scores as the Low (High) Performer Group.
+
+Next, we recruited `r scales::comma(dim(study1_time1)[1])` participants who
+completed the same 10-item quiz, also earning five cents for each correct answer.
+We then asked them to express a non-binding preference for whether they would
+like to compete against the High or Low Performer Group. We informed them that
+they would be invited back at a later date when they could make a binding decision
+and they could earn a bonus based on whether their score on this quiz was equal
+to or higher than a randomly selected member from their comparison group.
+If they picked the High Performer Group and had an equal or higher score than
+a randomly selected member of that group, they would earn a bonus of 50 cents.
+If they picked the Low Performer Group, they could earn a bonus of 20 cents.
+If their score was lower in this comparison, they would not earn an additional
+bonus. We randomized which of the two groups (High or Low Performers) was 
+selected by default, and participants were free to select the other group.
+Participants also made a guess as to their score, and the survey concluded with 
+basic demographic questions.
 
 We then recruited `r scales::comma(dim(study1_time2_giver)[1])`
-participants for Stage 2, placing them in the role of advisers. We began
-by informing them of the ability quiz that participants in the
-preliminary study and Stage 1 had completed, and informed them of the
-average score of all participants in the preliminary study. Advisers had
-to recommend whether an advisee should compete against the Low
-Performer Group or the High Performer Group (we used these terms in the survey).
-We anticipated that being told to compete against High Performers is
-more flattering and hence being told to compete against the Low
-Performers would be disappointing if one had expected to do well.
-Advisees would earn 20 cents if their score was equal to or higher than
-a randomly selected member of the Low Performer Group and they chose to
-compete against this group, or 50 cents if they performed as well or
-better than a randomly selected member of the High Performer Group and
-they chose to compete against that group. If they scored lower, they
-would not receive any bonus.
-
+participants for the role of advisers, and the focal part of our experiment. 
+They were informed of the ability quiz that participants had completed, how the 
+Low Performer Group and High Performer Groups were constructed, as well as the
+choice and incentives for the other participants. We then asked participants
+to give advice to ten participants on which group they should compete against.
 Advisers were randomly assigned to one of two treatments. In the
-"Performance" treatment, they only observed the score of the advisee on the
-ability quiz. In the "Expectation" treatment, they observed the
-score as well as the advisee's initial preference for which group to compete against.
-However, since the outcome was based solely on the quiz score and advisees didn’t 
-know their scores, their initial choice wasn’t useful in deciding which group had a 
-higher expected bonus. Advisers gave recommendations to 10 advisees and were told that 
-if their advice was used by a participant in a follow-up survey, they would receive 
-the same bonus as that participant. The survey concluded with basic demographic 
-questions.
-
-Finally, we invited participants from Stage 1 back for the follow-up
-survey. Following our preregistration, we kept the survey open for 7
+"Performance" treatment, they observed the score of the other participant.
+In the "Performance + Expectation" treatment, they additionally observed the
+advisee's non-binding choice for which group to compete against.
+However, since the outcome was based solely on the past quiz score and advisers,
+but not advisees, know the score, this initial choice was not informative.
+Advisers could earn the same bonus as one of the participants they had given
+advice to and who returned to make a decision. The survey concluded with basic 
+demographic questions.
+
+Finally, we invited advisees back for the follow-up survey. Following our 
+preregistration, we kept the survey open for 7
 days. In total, `r scales::comma(dim(study1_time3)[1])` participants
-(`r scales::comma(dim(study1_time3[study1_time3$Gender == 'Male',])[1])`
-men,
-`r scales::comma(dim(study1_time3[study1_time3$Gender == 'Female',])[1])`
-women) returned. The brief survey reminded them of the task they
-completed in Stage 1, informed them that other participants from
+returned. The short survey reminded them of the task they
+completed in the previous survey, informed them that other participants from
 Prolific had observed their real score and given them advice against
-which group to compete against, and finally were reminded them of how
+which group to compete against, and finally reminded them of how
 many questions they guessed they had answered correctly. Importantly,
@@
 
-<!-- Amanda: Wondering if we need to report the p-value of priming manipulation -->
-
 ```{r}
@@
 We begin by examining the performance of the Stage 1 participants.
-Because our treatment takes place after participants completed the
-ability quiz, we would not expect a difference in performance across
+Because our default treatment takes place after participants completed the
+ability quiz, we do not expect a difference in performance across
 the Low and High Default treatments. Indeed, the two groups scored
@@
 `r round(mean(study1_time1[study1_time1$default == "High",]$Score),2)`
-for the Low Defult and High Defult treatments, respectively,
+for the Low Default and High Default treatments, respectively,
 `r papaja::apa_print(t.test(Score ~ default, data = study1_time1, var.equal = T))$statistic`).
-The priming did, however, affect advisees' initial choices. In the "Low Default" treatment, 
+The default manipulation affected their initial choices. In the "Low Default" treatment, 
 only `r round(mean(study1_time1[study1_time1$default == "Low",]$Guess),2)*100`% 
@@
 
-<!-- No main interactive effect on expected bonus, therefore I did not include it in this tabel -->
-
 ```{r study1regs}
@@
 
-# Fit the two models
-model1 <- lm(Advice ~ ExpShow * Treatment, data = study1_advice)
-model2 <- lm(Advice ~ Treatment + Score, data = study1_advice %>% dplyr::filter(ExpShow == 1))
-
-# Use sandwich package for clustered standard errors
-library(sandwich)
-
-# Clustered standard errors by GiverID
-vcov_list <- list(sandwich::vcovCL(model1, cluster = ~GiverID), 
-                  sandwich::vcovCL(model2, cluster = ~GiverID))
-
 modelsummary::modelsummary(
-  list(`(1)` = model1, `(2)` = model2),
-  vcov = vcov_list,
+  list(`(1)` = lm(Advice ~ ExpShow * Treatment, data = study1_advice), 
+       `(2)` = lm(Advice ~ Treatment + Score, data = study1_advice %>% dplyr::filter(ExpShow == 1))),
+  vcov = ~GiverID,
   coef_map = c(
@@
   gof_map = list(list('raw' = 'nobs', 'clean' = 'N', 'fmt' = 0)),
-  caption = "Column 1 displays the advice given to compete against a High Performer Group based on whether the advisees were primed with low or high default and the initial preference shown to the advisor.
-Column 2 displays the advice given to compete against a High Performer Group based on the default and advisees' performance when their initial preference was visible to the advisor.
-All standard errors are clustered at the level of the advisor."
+  caption = "Advice to compete against the High Performer Group in Study 1.
+Displaying the non-binding choice of those for whom the Low Performer Group was selected by default makes it more likely that they are advised to compete against the High Performer Group (Column 1).
+Column 2 restricts the analysis to advisers who observed advisees' initial non-binding choice and controls for advisees' score on the quiz.
+Standard errors are clustered at the adviser level."
 )
@@
 
-Next, we examine whether advisers took the advisees' expectations into account. 
-Recall that advisees who defaulted to competing against the High Performer 
+We now examine whether advisers took the advisees' expectations into account. 
+Recall that advisees who were defaulted to competing against the High Performer 
 Group were indeed more likely to choose this group, which, from the advisers' 

### 2024-12-15 manuscript/manuscript.Rmd
citations needed

@@
 on recommendations) far less attention has been devoted to understanding the 
-motivations and behaviors of the *givers* of advice. In this paper, we shift the 
+motivations and behaviors of the *givers* of advice (CITES). In this paper, we shift the 
 focus to advisers, proposing that their recommendations are shaped not only by 
@@
 hand. However, prior research highlights that interpersonal dynamics can 
-complicate these interactions. Advice seekers may avoid asking for help due to 
+complicate these interactions (CITE). Advice seekers may avoid asking for help due to 
 fear of rejection [@Benabou2022], and people generally have been shown to avoid

### 2024-12-17 manuscript/manuscript.Rmd
Add citations

--- 2024-12-15 manuscript/manuscript.Rmd
@@
 on recommendations) far less attention has been devoted to understanding the 
-motivations and behaviors of the *givers* of advice. In this paper, we shift the 
+motivations and behaviors of the *givers* of advice [@Yaniv2004; @Yaniv2012; 
+with a few exceptions: @Blunden2019; @Schaerer2018]. In this paper, we shift the 
 focus to advisers, proposing that their recommendations are shaped not only by 
@@
 hand. However, prior research highlights that interpersonal dynamics can 
-complicate these interactions. Advice seekers may avoid asking for help due to 
+complicate these interactions [@Brooks2015; @Minson2011]. Advice seekers may avoid asking for help due to 
 fear of rejection [@Benabou2022], and people generally have been shown to avoid

### 2025-01-09 manuscript/manuscript.Rmd
Revised introduction

--- 2024-12-15 manuscript/manuscript.Rmd
@@
   Good advice improves decision quality but often requires delivering unpleasant truths that may disappoint advisees.
-Across three pre-registered and incentivized experiments involving real adviser-advisee interactions (n = 3,900), we demonstrate that advisers prioritize avoiding disappointment, even at the expense of accuracy.
-In Study 1, advisers financially rewarded for accuracy still tailored recommendations to aspirational goals expressed by advisees, resulting in poorer advice.
-When incentivized to be liked, advisers provided even more flattering advice, and advisees rated these advisers as more likable, despite the advice being less honest and less accurate (Study 2).
-In Study 3, advisers incorporated advisees' subjective and uninformative performance expectations into recommendations, leading to systematically different advice for men and women.
-Because men expected to perform better than women, they received more aspirational advice, even when their gender was unknown to advisers.
-Advisers' efforts to avoid disappointment may thus contribute to systematic gender disparities in advice, with implications for downstream decision-making and equity.
+Across three pre-registered and incentivized experiments involving real adviser-advisee interactions (N = 3,900), we show that advisers prioritize avoiding disappointment at the expense of accuracy and their own earnings.
+In Study 1, advisers financially rewarded for accuracy still tailor recommendations to aspirational goals expressed by advisees, resulting in worse advice.
+When incentivized to be liked, advisers provide even more flattering advice, and advisees reward this by rating these advisers as more likable, despite the advice being less honest and less accurate (Study 2).
+The desire to avoid disappointment may lead to inequities if there are differences in expectations across social groups.
+In Study 3, we examine a setting in which men expect to perform better than women.
+We show that advisers take into account these expectations, leading to systematically different advice for men and women even when their gender is unknown to advisers.
+Advisers' efforts to avoid disappointment may thus contribute to systematic gender disparities in advice, with implications for downstream decision-making.
 
@@
 always_allow_html: true
+# bibliography: references.bib
 ---
@@
 # Introduction
-Advice plays a critical role in both professional and personal decision-making, 
-often serving as a crucial tool for navigating complex challenges and improving 
-outcomes [@Gino2007; @Harvey1997; @Soll2009]. While prior research has 
-extensively examined the *recipients* of advice (e.g., how they evaluate or act 
-on recommendations) far less attention has been devoted to understanding the 
-motivations and behaviors of the *givers* of advice. In this paper, we shift the 
-focus to advisers, proposing that their recommendations are shaped not only by 
-accuracy considerations but also by interpersonal concerns. Specifically, we 
-propose that advisers factor in advisees' subjective expectations, providing 
-flattering advice that aligns with these expectations, even when doing so leads 
-to objectively worse recommendations. Notably, this tendency persists in our 
-experimental settings, where advisees' expectations are clearly uninformative 
-and advisers are financially incentivized for accuracy.
-
-Advice is often viewed as a mechanism to improve decision satisfaction or 
-prediction accuracy, assuming both parties prioritize solving the problem at 
-hand. However, prior research highlights that interpersonal dynamics can 
-complicate these interactions. Advice seekers may avoid asking for help due to 
-fear of rejection [@Benabou2022], and people generally have been shown to avoid
-information that could lead to disappointment [@Gill2012; @Golman2017]. 
-They are motivated to avoid unpleasant truths in an ethical dilemma [@Shalvi2019] 
-and dislike those who deliver unwelcome feedback even when they had no role in
-the outcome [@John2019]. These tendencies align with models of belief utility 
-[@Loewenstein2018], which suggest that individuals experience 
-hedonic costs when receiving bad news. A natural reference point for evaluating 
-the valence of advice is the advisee's expectation in the absence of advice
-[@Koszegi2006]. Consequently, advisers who are aware of expectations may 
-strategically adapt their advice to avoid delivering bad news, even at the 
-expense of accuracy.
-
-This interpersonal dimension of advice-giving has significant implications for 
-understanding systematic gender differences in advice quality. Men are more 
-likely than women to receive aspirational advice and encouragement to pursue 
-competitive or risky opportunities [@Kanze2018]. Conversely, women are often 
-shielded from criticism [@Jampol2023], which, while intended to be kind, 
-may ultimately limit their professional growth. We propose a novel mechanism to 
-explain these patterns: advisers calibrate their recommendations to match 
-advisees’ expectations. Because, in many tasks (including those in our experiments)
-men are more confident and have higher expectations about their performance than
-do women, they are more likely to receive flattering (but, in our setting, worse) 
-advice.
-
-We present evidence for this mechanism from three preregistered and incentivized 
-experiments involving real interactions between advisers and advisees (N = 3,900). 
-In Study 1, we experimentally manipulate advisee's expectations and show
-that advisers account for those expectations, even when they offer no relevant
-insight for the decision. In Study 2, we show that advisers put more weight on
-interpersonal concerns when they are incentivized to be liked. Advisees reward
-this flattery by rating advisers as more likeable and equally trustworthy compared
-to those offering more honest (and accurate) feedback. In Study 3, we measure
-expected performance on a math quiz and show that advisers take these expectations
-into account even when they have information about actual performance. Because
-men expect to score higher, they are more likely to be advised to compete against
-a stronger group for a higher potential payment than are women, even when advisers
-are unaware of the advisees' gender. Notably, this leads to worse advice for men.
+
+Career trajectories for men and women often differ substantially, even
+among those with similar qualifications. One source of such differences
+may be the advice that people receive. Prior work has documented that
+men receive more aspirational advice and women more risk-averse advice,
+which may explain why women are less likely to apply for and ultimately
+obtain more rewarding positions (Kanze et al., 2018). Research on gender
+discrimination has focused on the role of unconscious bias (Greenwald et
+al., 2009; Greenwald & Banaji, 1995), but interventions that try to
+reduce this bias have been largely unsuccessful (Chang et al., 2019;
+Paluck & Green, 2009). Recent work has proposed cognitive, rather than
+unconscious, biases that can lead to gender discrimination through the
+formation of false beliefs (Hagmann et al., 2024). Here, we propose a
+novel source of differences in advice by drawing on recent work on
+belief-based utility, expectation-based reference points (Köszegi, 2006;
+Kőszegi & Rabin, 2009), and the hedonic consequences of information
+(Golman et al., 2017).
+
+Advice figures prominently in workplace and personal decision-making,
+shaping choices about promotions, career paths, and everyday dilemmas
+[@Gino2007; @Harvey1997; @Soll2009]. Its fundamental premise is to
+improve outcomes by enabling decision-makers to learn from others'
+expertise. However, while honest advice can lead to better decisions, it
+can also lead to disappointment when it suggests a desired outcome is
+unlikely to materialize. Advisers may be motivated to offer flattering
+recommendations that align with advisees' hopes, sparing them the
+disappointment of a more sobering forecast.
+
+Advice with the potential for disappointment appears in diverse
+organizational settings: supervisors deliver feedback on employee
+performance, lawyers convey likely outcomes of litigation to their
+clients, and academics offer thoughts on colleagues' manuscripts.
+Ideally, honest information would help people identify their strengths
+and weaknesses, make informed decisions about whether to pursue legal
+cases, and strengthen papers prior to submission to academic journals,
+thus improving long-term outcomes. In practice, however, interpersonal
+considerations may prevent candor. When someone's expectations are (too)
+high, an adviser might hesitate to deliver information that undermines
+it---particularly if doing so risks negative interpersonal
+repercussions.
+
+People often go to great lengths to avoid unpleasant information,
+deriving belief-based utility from maintaining favorable views of
+themselves [@Golman2017; @Ho2018; @Loewenstein2018]. Moreover, they
+often prefer advisers who withhold bad news from them [@Shalvi2019] and
+punish those who communicate bad news [@John2019]. Advisers,
+anticipating these preferences and consequences face a dilemma: Should
+they provide the accurate but potentially painful truth, or shade their
+recommendations to preserve the advisee's mood and the adviser's own
+standing? Advisers who fear they will be blamed or disliked for
+undermining someone's confidence may reasonably avoid candid feedback,
+particularly if they don't incur a cost when the advisee makes a
+mistake.
+
+In our experiments, however, advisees have no opportunity to punish the
+adviser, and advisers' financial incentives are linked to the decisions
+the advisees make. We propose that advisers nonetheless have reason to
+provide flattering advise because they recognize the psychological toll
+of disappointing news. As a result, they may similarly incur a hedonic
+cost for delivering unpleasant information that they anticipate may
+distress the advisee. Thus, even in the anonymized context of an online
+experiment, we hypothesize (and find) that advisers are relucant to
+disappoint advisees and advice is thus biased upward, away from accuracy
+and toward confirming advisees' priors. We show that this reduces the
+quality of advice—but that advisees nonetheless view flattering advisers
+more favorably.
+
+We present the results of three preregistered experiments in which
+participants are paired anonymously as advisers and advisees. Advisers
+are incentivized to offer accurate advice, with bonus earnings depending
+on the outcome of an advisee's decision. We study a setting in which
+advisees can communicate their expectations to an adviser, and
+experimentally manipulate whether advisers observe this expectation. Our
+design simulates organizational contexts where mentors and managers
+often have some sense of an employee's confidence or aspirations and
+thus could adjust their feedback to avoid disappointing them.
+Interpersonal considerations would likely be stronger in situations in
+which the adviser and advisee have an existing relationship and when the
+advice is delivered face-to-face. Moreover, advisers usually do not
+suffer any direct costs when their flattering advice leads to a poor
+outcome for the recipient, particularly when it is not clear what would
+have happened under a counterfactual.\^[In some cases, however, repeated
+interaction might also increase incentives for honest feedback. Someone
+who is known to persistently give overoptimistic advice may be viewed as
+less trustworthy in the long run.]
+
+In Study 1, we nudge advisees into a preference for competing against
+either a group of top-performers or a group of low-performers, through
+the use of a default option. Advisers who observe the actual performance
+of advisees and therefore have the relevant information needed to make a
+recommendation nonetheless take into account the initial preference when
+recommending which group they should compete against. In Study 2, we ask
+advisees to upload photos of themselves and advisers rank them on their
+attractiveness. Advisers then recommend which rank the advisee should
+bet on, receiving an incentive either for the advisee's accuracy or for
+being evaluated favorably. Both groups of advisers recommend a rank that
+is more attractive than what they themselves have evaluated the advisee,
+and those incentivized for likability further inflate the ranking.
+Advisees evaluate advisers more favorably when they recommend betting on
+a more attractive rank, including viewing them as more trustworthy.
+
+In Study 3, we examine a setting in which participants report their
+expected performance on a mathematics quiz. Advisers observe the
+test-taker's true score and, in one treatment, the score they guessed
+they would receive. They then recommend whether the advisee should
+compete against a group of high performers or low performers.
+Importantly, this "competition" is based on the past performance
+observed by the adviser and thus the advisee's expectation does not
+provide instrumental information. However, we find that (1) men expect
+to perform better than women, given identical performance, and (2)
+advisers take these expectations into account. As a result, when
+expectations (but not gender) are known to advisers, the advice given to
+men and women differs, and men are more often advised to compete against
+the group of high performers. Notably, this leads to worse advice for
+men than for women.
 
@@
 
-We report all manipulations, measures, and data exclusion in this and the following study.
-The preregistration reports, screenshots of all experimental materials, and the analysis code to replicate all statistical analyses and figures are available on the Open Science Framework
+We report all manipulations, measures, and data exclusion in our
+experiments. The preregistration reports, screenshots of all
+experimental materials, and the analysis code to replicate all
+statistical analyses and figures are available on the Open Science
+Framework
 (<https://osf.io/8r3d4/?view_only=5ad7bafcd16b4d4ba08bb28b0e2bd02d>).
@@
 # Study 1
-We first examine whether advisers take into account the expectations of advisees
-when providing a recommendation. A group of participants ("Advisees") complete 
-a quiz consisting of ten questions that draw on ego-relevant domains. They then
-express a non-binding preference to compete against a group of high performers
-or low performers on the same task, based on their past performance. We nudge
-participants towards picking either the low or the high performer group by 
-selecting one of the two by default. A second group of participants ("Advisers") 
-observe Advisees' score on the quiz and, in one treatment, also which group
-they had selected. We predicted that Advisees who were nudged toward the high
-performer group would be more likely to receive advice to compete against this
-high group when Advisers observed their non-binding choice.
+
+We first examine whether advisers take into account the expectations of
+advisees when providing a recommendation. A group of participants
+("Advisees") complete a quiz consisting of ten questions that draw on
+ego-relevant domains. They then express a non-binding preference to
+compete against a group of high performers or low performers on the same
+task, based on their past performance. We nudge participants towards
+picking either the low or the high performer group by selecting one of
+the two by default. A second group of participants ("Advisers") observe
+Advisees' score on the quiz and, in one treatment, also which group they
+had selected. We predicted that Advisees who were nudged toward the high
+performer group would be more likely to receive advice to compete
+against this high group when Advisers observed their non-binding choice.
 
 ## Methods
-In a preliminary stage, we recruited `r scales::comma(dim(study1_ability50)[1])` 
-participants from Prolific and gave them five minutes to complete a quiz 
-consisting of ten items. The quiz included word puzzles,
-identifying emotions from photos, and selecting the best responses for hypothetical
-scenarios. These questions were adapted from surveys that measure problem-solving,
-emotional intelligence, and communication skills---which we pre-tested as being
-important in modern society and hence where participants might have a stake in
-doing well. Participants received a bonus of five cents for each correctly
-answered question. We then ranked them based on their score and label the 20
-participants with the lowest (highest) scores as the Low (High) Performer Group.
-
-Next, we recruited `r scales::comma(dim(study1_time1)[1])` participants who
-completed the same 10-item quiz, also earning five cents for each correct answer.
-We then asked them to express a non-binding preference for whether they would
-like to compete against the High or Low Performer Group. We informed them that
-they would be invited back at a later date when they could make a binding decision
-and they could earn a bonus based on whether their score on this quiz was equal
-to or higher than a randomly selected member from their comparison group.
-If they picked the High Performer Group and had an equal or higher score than
-a randomly selected member of that group, they would earn a bonus of 50 cents.
-If they picked the Low Performer Group, they could earn a bonus of 20 cents.
-If their score was lower in this comparison, they would not earn an additional
-bonus. We randomized which of the two groups (High or Low Performers) was 
-selected by default, and participants were free to select the other group.
-Participants also made a guess as to their score, and the survey concluded with 
-basic demographic questions.
+
+In a preliminary stage, we recruited
+`r scales::comma(dim(study1_ability50)[1])` participants from Prolific
+and gave them five minutes to complete a quiz consisting of ten items.
+The quiz included word puzzles, identifying emotions from photos, and
+selecting the best responses for hypothetical scenarios. These questions
+were adapted from surveys that measure problem-solving, emotional
+intelligence, and communication skills---which we pre-tested as being
+important in modern society and hence where participants might have a
+stake in doing well. Participants received a bonus of five cents for
+each correctly answered question. We then ranked them based on their
+score and label the 20 participants with the lowest (highest) scores as
+the Low (High) Performer Group.
+
+Next, we recruited `r scales::comma(dim(study1_time1)[1])` participants
+for the role of Advisees. They completed the same 10-item quiz, also
+earning five cents for each correct answer. We then asked them to
+express a non-binding preference for whether they would like to compete
+against the High or Low Performer Group. We informed them that they
+would be invited back at a later date when they could make a binding
+decision and they could earn a bonus based on whether their score on
+this quiz was equal to or higher than a randomly selected member from
+their comparison group. If they picked the High Performer Group and had
+an equal or higher score than a randomly selected member of that group,
+they would earn a bonus of 50 cents. If they picked the Low Performer
+Group and outperformed a randomly selected member of that group, they
+could earn a bonus of 20 cents. If their score was lower in this
+comparison, they would not earn an additional bonus. We randomized which
+of the two groups (High or Low Performers) was selected by default, and
+Advisees were free to select the other group. They also made a guess as
+to their score, and the survey concluded with basic demographic
+questions.
 
 We then recruited `r scales::comma(dim(study1_time2_giver)[1])`
-participants for the role of advisers, and the focal part of our experiment. 
-They were informed of the ability quiz that participants had completed, how the 
-Low Performer Group and High Performer Groups were constructed, as well as the
-choice and incentives for the other participants. We then asked participants
-to give advice to ten participants on which group they should compete against.
-Advisers were randomly assigned to one of two treatments. In the
-"Performance" treatment, they observed the score of the other participant.
-In the "Performance + Expectation" treatment, they additionally observed the
-advisee's non-binding choice for which group to compete against.
-However, since the outcome was based solely on the past quiz score and advisers,
-but not advisees, know the score, this initial choice was not informative.
-Advisers could earn the same bonus as one of the participants they had given
-advice to and who returned to make a decision. The survey concluded with basic 
+participants for the role of Advisers, and the focal part of our
+experiment. They were informed of the ability quiz that the Advisees had
+completed, how the Low Performer Group and High Performer Groups were
+constructed, as well as the choice and incentives for the Advisees. We
+then asked Advisers to give advice to ten participants on which group
+they should compete against. Advisers were randomly assigned to one of
+two treatments. In the "Performance" treatment, they observed only the
+score of the other participant. In the "Performance + Expectation"
+treatment, they additionally observed the advisee's non-binding choice
+of which group to compete against. However, since the outcome was based
+solely on the past quiz score and advisers, but not advisees, know the
+score, this initial choice was not informative for the purpose of
+recommending competing against one group or the other. Advisers could
+earn the same bonus as one of the participants they had given advice to
+and who returned to make a decision. The survey concluded with basic
 demographic questions.
 
-Finally, we invited advisees back for the follow-up survey. Following our 
-preregistration, we kept the survey open for 7
-days. In total, `r scales::comma(dim(study1_time3)[1])` participants
-returned. The short survey reminded them of the task they
-completed in the previous survey, informed them that other participants from
-Prolific had observed their real score and given them advice against
-which group to compete against, and finally reminded them of how
-many questions they guessed they had answered correctly. Importantly,
-they were not informed of their true score or the score of the groups
-they could compete against. Participants then observed the advice from a
-randomly selected adviser and made their decision.
+Finally, we invited Advisees back for the follow-up survey. Following
+our preregistration, we kept the survey open for 7 days. In total,
+`r scales::comma(dim(study1_time3)[1])` Advisees returned. The short
+survey reminded them of the task they completed in the previous survey,
+informed them that other participants from Prolific had observed their
+real score and given them advice on which group to compete against, and
+finally reminded them of how many questions they guessed they had
+answered correctly. They were not informed of their true score or the
+score of the groups they could compete against. Participants then
+observed the advice from a randomly selected adviser and made their
+decision.
 
@@
 We begin by examining the performance of the Stage 1 participants.
-Because our default treatment takes place after participants completed the
-ability quiz, we do not expect a difference in performance across
-the Low and High Default treatments. Indeed, the two groups scored
-no different from one another
+Because our default treatment takes place after participants completed
+the ability quiz, we do not expect a difference in performance across
+the Low and High Default treatments. Indeed, the two groups scored no
+different from one another
 (`r round(mean(study1_time1[study1_time1$default == "Low",]$Score),2)`
@@
 `r papaja::apa_print(t.test(Score ~ default, data = study1_time1, var.equal = T))$statistic`).
-The default manipulation affected their initial choices. In the "Low Default" treatment, 
-only `r round(mean(study1_time1[study1_time1$default == "Low",]$Guess),2)*100`% 
-of participants initially preferred competing against the High Performer Group, 
-compared to `r round(mean(study1_time1[study1_time1$default == "High",]$Guess),2)*100`%
-of participants who saw the High Performer Group highlighted ($\chi^2$(1, n = 201) = 36.62, p < .001).
+The default manipulation affected their initial choices. In the "Low
+Default" treatment, only
+`r round(mean(study1_time1[study1_time1$default == "Low",]$Guess),2)*100`%
+of participants initially preferred competing against the High Performer
+Group, compared to
+`r round(mean(study1_time1[study1_time1$default == "High",]$Guess),2)*100`%
+of participants who saw the High Performer Group highlighted
+($\chi^2$(1, n = 201) = 36.62, p \< .001).
 
@@
 
-We now examine whether advisers took the advisees' expectations into account. 
-Recall that advisees who were defaulted to competing against the High Performer 
-Group were indeed more likely to choose this group, which, from the advisers' 
-perspective, could signal high confidence in their abilities. Our theory 
-predicts that showing expectations should lead to more flattering advice—
-specifically, a recommendation to compete against the High Performer Group—
-for advisees with a high default choice compared to those with a low 
-default choice. Column 1 of Table \@ref(tab:study1regs) reports a linear
-probability model with advice to compete against the high group
-as the outcome measure, incorporating the default choice advisees saw, whether expectations
-were shown to the adviser, and the interaction of the two. Because each adviser made ten
-recommendations, we cluster standard errors at the adviser level.
-As predicted, we find a marginally significant interaction effect: advisees 
-with a default choice to compete against the High Performer Group (nudged 
-to have high expectations, though not necessarily holding them) were more 
-likely to receive advice to compete against stronger competitors when 
-their expectations were shown compared to when they were hidden.
-We reported a linear probability model on advising to compete against the High Performer
-group for advisers in the "Expectations" treatment, controlling for the
-true performance of the advisee in Column 2 of Table \@ref(tab:study1regs).
-We observe a significant main effect of the default treatment, where a high default
-increased the likelihood of receiving flattering advice. It is worth noting that, 
-since only `r round(mean(study1_time1[study1_time1$default == "High",]$Guess),2)*100`
-% of advisees in the high default group actually stuck with their default 
-choice, this represents a conservative test of the effect of high expectations on 
-the likelihood of receiving flattering advice.
+We now examine whether advisers took the advisees' expectations into
+account. Recall that advisees who were defaulted to competing against
+the High Performer Group were indeed more likely to choose this group,
+which, from the advisers' perspective, could signal high confidence in
+their abilities. Our theory predicts that showing expectations should
+lead to more flattering advice--- specifically, a recommendation to
+compete against the High Performer Group--- for advisees with a high
+default choice compared to those with a low default choice. Column 1 of
+Table \@ref(tab:study1regs) reports a linear probability model with
+advice to compete against the high group as the outcome measure,
+incorporating the default choice advisees saw, whether expectations were
+shown to the adviser, and the interaction of the two. Because each
+adviser made ten recommendations, we cluster standard errors at the
+adviser level. As predicted, we find a marginally significant
+interaction effect: advisees with a default choice to compete against
+the High Performer Group (nudged to have high expectations, though not
+necessarily holding them) were more likely to receive advice to compete
+against stronger competitors when their expectations were shown compared
+to when they were hidden. We reported a linear probability model on
+advising to compete against the High Performer group for advisers in the
+"Expectations" treatment, controlling for the true performance of the
+advisee in Column 2 of Table \@ref(tab:study1regs). We observe a
+significant main effect of the default treatment, where a high default
+increased the likelihood of receiving flattering advice. It is worth
+noting that, since only
+`r round(mean(study1_time1[study1_time1$default == "High",]$Guess),2)*100`
+% of advisees in the high default group actually stuck with their
+default choice, this represents a conservative test of the effect of
+high expectations on the likelihood of receiving flattering advice.
 
@@
 
-When the quality of a decision does not depend on someone's expectations,
-the adviser's awareness of the advisee's expectations should not influence
-the advice given. However, in line with our argument that advisers take
-into account the belief utility of the advisee and prefer to flatter 
-rather than disappoint, we find that displaying the advisee's expectations
-does make a difference. Specifically, advisees who expressed a preference
-for stronger competitors were more likely to receive 'flattering' advice,
-encouraging them to pursue that option. One possible explanation for this
-finding is that, rather than trying to flatter, advisers may simply be 
-telling advisees what they want to hear. In the next study, we aim to 
+When the quality of a decision does not depend on someone's
+expectations, the adviser's awareness of the advisee's expectations
+should not influence the advice given. However, in line with our
+argument that advisers take into account the belief utility of the
+advisee and prefer to flatter rather than disappoint, we find that
+displaying the advisee's expectations does make a difference.
+Specifically, advisees who expressed a preference for stronger
+competitors were more likely to receive 'flattering' advice, encouraging
+them to pursue that option. One possible explanation for this finding is
+that, rather than trying to flatter, advisers may simply be telling
+advisees what they want to hear. In the next study, we aim to
 investigate the mechanism behind this discrepancy in advice-giving when
@@
 
-So far, we have shown that displaying expectations influences the advice given. 
-Specifically, advisers were more likely to recommend competing against a group 
-of high performers to advisees with higher performance expectations compared to 
-those without. We now directly test whether this effect is driven by 
-interpersonal concerns. In particular, we explore whether more flattering advice
-stems from a desire to be liked, and whether advisees, in turn, like advisers 
-more when they receive flattering advice.
+So far, we have shown that displaying expectations influences the advice
+given. Specifically, advisers were more likely to recommend competing
+against a group of high performers to advisees with higher performance
+expectations compared to those without. We now directly test whether
+this effect is driven by interpersonal concerns. In particular, we
+explore whether more flattering advice stems from a desire to be liked,
+and whether advisees, in turn, like advisers more when they receive
+flattering advice.
 
@@
 they had ranked as the 7th most attractive (i.e., the 4th least
-attractive). They were reminded of the rank they had given to that person
-and informed that this participant would be invited back and could earn
-a \$1 bonus if they guessed their rank correctly. The rank was
-determined by the aggregate ratings of all participants who had ranked
-this group. Their task was to give advice to this participant about the
-rank they should bet on based on having observed all ten selfies and
-their own assessment. We randomly assigned participants to one of two
-incentivization schemes. In the "Accuracy" treatment, they received a
-bonus identical to the advisee: \$1 if they guessed their rank
-correctly. In the "Likeability" treatment, we informed them that they
-would be rated by the advisee on a 5-point Likert scale for how likeable
-they thought they were. Each point on the scale would translate to a
-bonus of 20 cents. They then selected a rank that they would recommend
-the advisee to bet on.
+attractive). They were reminded of the rank they had given to that
+person and informed that this participant would be invited back and
+could earn a \$1 bonus if they guessed their rank correctly. The rank
+was determined by the aggregate ratings of all participants who had
+ranked this group. Their task was to give advice to this participant
+about the rank they should bet on based on having observed all ten
+selfies and their own assessment. We randomly assigned participants to
+one of two incentivization schemes. In the "Accuracy" treatment, they
+received a bonus identical to the advisee: \$1 if they guessed their
+rank correctly. In the "Likeability" treatment, we informed them that
+they would be rated by the advisee on a 5-point Likert scale for how
+likeable they thought they were. Each point on the scale would translate
+to a bonus of 20 cents. They then selected a rank that they would
+recommend the advisee to bet on.
 
@@
 This suggests that even when incentivized for accuracy, participants
-offered flattering advice.[^3] Importantly, and as predicted, we find
+offered flattering advice.[^1] Importantly, and as predicted, we find
 that advisers in the Likeable treatment recommend betting on a lower
@@
 
-[^3]: This shading could be due to concerns of avoiding disappointment.
+[^1]: This shading could be due to concerns of avoiding disappointment.
     However, it could also be that advisers are uncertain about the
@@
 
-In another context where advice communicates ego-relevant information (here,
-people's attractiveness), we find that the advice people give is
+In another context where advice communicates ego-relevant information
+(here, people's attractiveness), we find that the advice people give is
 contingent on their incentives. Specifically, when they get rewarded for
@@
 
-In Study 3, we replicate the main effect in a different ego-relevant domain: 
-intelligence. The experimental design is conceptually identical to Study 1, 
-but this time we utilize a more direct measure of expectation by asking 
-participants to estimate their scores.
+In Study 3, we replicate the main effect in a different ego-relevant
+domain: intelligence. The experimental design is conceptually identical
+to Study 1, but this time we utilize a more direct measure of
+expectation by asking participants to estimate their scores.
 
@@
 and asked to guess how many questions they answered correctly. As in
-previous studies, we recruit advisers who are presented with either 
-just the advisee's true performance or both the true performance and 
-the number of questions the advisee believes they answered correctly. 
+previous studies, we recruit advisers who are presented with either just
+the advisee's true performance or both the true performance and the
+number of questions the advisee believes they answered correctly.
 Advisers are then asked to provide advice on choosing a competitor.
@@
 high expectations will be more likely to receive advice to compete
-against the high-performing group, and (2) men will be more likely 
-than women to be advised to compete against the high-performing group
-when expectations are disclosed.
+against the high-performing group, and (2) men will be more likely than
+women to be advised to compete against the high-performing group when
+expectations are disclosed.
 
@@
 
-We begin by first recruiting a sample
-of `r scales::comma(dim(study3_math50)[1])` participants from Prolific
-to complete a 10-question multiple choice mathematics quiz. The
-questions were taken from a paper-version of the ASVAB standardized
-exam, such that answers were not available online. Participants had five
-minutes to answer the quiz and were paid 10 cents for each correctly
-answered question. Like before, we define top 20 scores as "High Performers"
-and the bottom 20 scorers as the "Low Performers." On average,
-participants answered `r round(mean(study3_math50$Score),2)` questions
-correctly, High Performers scored between `r HP_lower` and `r HP_upper`,
-and Low Performers scored between `r LP_lower` and `r LP_upper`. In
-order to anchor the expectations of participants in our main experiment,
-we simulated 1,000 pairings of groups of five participants, with the
+We begin by first recruiting a sample of
+`r scales::comma(dim(study3_math50)[1])` participants from Prolific to
+complete a 10-question multiple choice mathematics quiz. The questions
+were taken from a paper-version of the ASVAB standardized exam, such
+that answers were not available online. Participants had five minutes to
+answer the quiz and were paid 10 cents for each correctly answered
+question. Like before, we define top 20 scores as "High Performers" and
+the bottom 20 scorers as the "Low Performers." On average, participants
+answered `r round(mean(study3_math50$Score),2)` questions correctly,
+High Performers scored between `r HP_lower` and `r HP_upper`, and Low
+Performers scored between `r LP_lower` and `r LP_upper`. In order to
+anchor the expectations of participants in our main experiment, we
+simulated 1,000 pairings of groups of five participants, with the
 5<sup>th</sup> percentile of groups scoring an average of `r p5` and the
@@
 more flattering and hence being told to compete against the Low
-Performers would be disappointing if one had expected to do well. Advisees
-could earn a bonus if their score was equal to or higher than that of 
-a randomly selected member from their chosen group. Competing against 
-the High Performers was more challenging, resulting in an average bonus
-of 50 cents, compared to 30 cents when competing against other groups.
-
-Like before, advisers were randomly assigned to one of two treatments. In the
-"Baseline" treatment, they only observed the score of the advisee on the
-mathematics quiz. In the "Expectation" treatment, they observed the
-score as well as the advisee's guess for how many questions they
-answered correctly. We want to emphasize that sice the outcome is determined only by
-the past score on the quiz, the advisee's guess is immaterial to which
-group they should compete against. Moreover, in neither treatment did
-they receive any demographic information about their advisee.
-Participants gave recommendations to 10 advisees, which unbeknownst to
-them were five men and five women matched to have identical performance
-on the test.[^1] They were informed that if their advice was shown to a
-participant who returned for the follow-up survey, they would receive
-the identical bonus as that participant. The survey then concluded with
-basic demographic questions.
-
-[^1]: We made this decision to account for the possibility of gender
+Performers would be disappointing if one had expected to do well.
+Advisees could earn a bonus if their score was equal to or higher than
+that of a randomly selected member from their chosen group. Competing
+against the High Performers was more challenging, resulting in an
+average bonus of 50 cents, compared to 30 cents when competing against
+other groups.
+
+Like before, advisers were randomly assigned to one of two treatments.
+In the "Baseline" treatment, they only observed the score of the advisee
+on the mathematics quiz. In the "Expectation" treatment, they observed
+the score as well as the advisee's guess for how many questions they
+answered correctly. We want to emphasize that sice the outcome is
+determined only by the past score on the quiz, the advisee's guess is
+immaterial to which group they should compete against. Moreover, in
+neither treatment did they receive any demographic information about
+their advisee. Participants gave recommendations to 10 advisees, which
+unbeknownst to them were five men and five women matched to have
+identical performance on the test.[^2] They were informed that if their
+advice was shown to a participant who returned for the follow-up survey,
+they would receive the identical bonus as that participant. The survey
+then concluded with basic demographic questions.
+
+[^2]: We made this decision to account for the possibility of gender
     differences in performance.
@@
 turned out to be bad: men receive worse advise than do women when
-expectations are displayed, but not in their absence.[^2]
-
-[^2]: This analysis was not preregistered, and we note here that the
+expectations are displayed, but not in their absence.[^3]
+
+[^3]: This analysis was not preregistered, and we note here that the
     reduction in expected earnings is small. However, it is interesting
@@
 We found supportive evidence for our argument in a different domain.
-Advisors tend to consider advisees' self-expectations and match 
-their advice accordingly, aiming to avoid disappointment. Consistent
-with the confidence gap narrative, men tend to underestimate their 
-mathematics test scores less than women. When these expectations are
-displayed to advisors, they are more likely to advise men to compete
-against high performers. Notably, this turns out to be poor advice: 
-men whose advisors were aware of their expectations received worse 
-advice. Our findings suggest that men with the same scores as their
-female counterparts ended up earning less, although this result is 
-only directional. This discrepancy may be due to men receiving more
-favorable advice, being more likely to follow it, and ultimately 
-facing worse outcomes.
+Advisors tend to consider advisees' self-expectations and match their
+advice accordingly, aiming to avoid disappointment. Consistent with the
+confidence gap narrative, men tend to underestimate their mathematics
+test scores less than women. When these expectations are displayed to
+advisors, they are more likely to advise men to compete against high
+performers. Notably, this turns out to be poor advice: men whose
+advisors were aware of their expectations received worse advice. Our
+findings suggest that men with the same scores as their female
+counterparts ended up earning less, although this result is only
+directional. This discrepancy may be due to men receiving more favorable
+advice, being more likely to follow it, and ultimately facing worse
+outcomes.
 
@@
 
-```{=tex}
 \begingroup
@@
 \setlength{\leftskip}{0.2in}
+
 \noindent
-```
+
 ::: {#refs}
@@
 
-```{=tex}
 \endgroup
-```

### 2025-01-09 manuscript/manuscript.qmd
Conversion to Quarto file

--- 2025-01-09 manuscript/manuscript.Rmd
@@
 title: "Flattering Advice: Avoiding Disappointment in Advice-Giving"
-shorttitle        : "Flattering Advice"
+shorttitle: "Flattering Advice"
+date: yes
 author: 
-  - name          : "Amanda Chen"
-    affiliation   : "1"
-    corresponding : yes    
-    email         : "zchengj@connect.ust.hk"
-    address       : "Department of Management, The Hong Kong University of Science and Technology, Hong Kong"
-  - name          : "David Hagmann"
-    affiliation   : "1"
-affiliation:
-  - id            : "1"
-    institution   : "The Hong Kong University of Science and Technology"
-note : |
-  `r format(Sys.time(), "%e %B, %Y")`
-abstract: |
-  Good advice improves decision quality but often requires delivering unpleasant truths that may disappoint advisees.
+  - name: "Amanda Chen"
+    corresponding: true
+    orcid: 0000-0002-4428-627X
+    email: zchengj@connect.ust.hk
+    affiliations:
+      - id: id1
+        name: "The Hong Kong University of Science and Technology"
+        department: "Department of Management"
+        city: "Hong Kong"
+  - name: "David Hagmann"
+    orcid: 0000-0002-2080-997X
+    affiliations:
+    - id: id1
+author-note:
+  disclosures:
+    gratitude: The authors are grateful to XXX for their helpful comments.
+abstract: Good advice improves decision quality but often requires delivering unpleasant truths that may disappoint advisees.
 Across three pre-registered and incentivized experiments involving real adviser-advisee interactions (N = 3,900), we show that advisers prioritize avoiding disappointment at the expense of accuracy and their own earnings.
@@
 
-keywords          : "Gender difference, Advice, Interpresonal relationship"
-wordcount         : "6,104"
-figsintext        : yes
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-linenumbers       : no
-mask              : no
-draft             : no
-documentclass     : "apa7"
-csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
-classoption       : "man"
-header-includes:
-   - \usepackage{setspace, appendix, placeins, booktabs, tikz, siunitx}
-   - \usepackage{tabularx, epigraph, float, colortbl, tabu, pdflscape}
-   - \usepackage{tabularray}
-   - \usetikzlibrary{positioning}
-   - \raggedbottom
-   - \usepackage[maxfloats=256]{morefloats}
-   - \maxdeadcycles=1000
-bibliography      : bibliography.bib
-output: 
-  # papaja::apa6_docx
-  papaja::apa6_pdf
-editor_options: 
-  chunk_output_type: console
-  markdown: 
-    wrap: 72
-always_allow_html: true
-# bibliography: references.bib
+keywords: [Gender difference, Advice, Interpresonal relationship]
+bibliography: bibliography.bib
+floatsintext: true
+mask: false
+link-citations: false
+format:
+  apaquarto-html: default
+  apaquarto-pdf:
+    documentmode: man
+    keep-tex: true
+    prefer-html: true
+  apaquarto-docx:
+    default: true
+    prefer-html: true
 ---
 
-```{r setup, include=FALSE}
+```{r}
+#| label: setup
+#| include: false
 
@@
 
-Career trajectories for men and women often differ substantially, even
-among those with similar qualifications. One source of such differences
-may be the advice that people receive. Prior work has documented that
-men receive more aspirational advice and women more risk-averse advice,
-which may explain why women are less likely to apply for and ultimately
-obtain more rewarding positions (Kanze et al., 2018). Research on gender
-discrimination has focused on the role of unconscious bias (Greenwald et
-al., 2009; Greenwald & Banaji, 1995), but interventions that try to
-reduce this bias have been largely unsuccessful (Chang et al., 2019;
-Paluck & Green, 2009). Recent work has proposed cognitive, rather than
-unconscious, biases that can lead to gender discrimination through the
-formation of false beliefs (Hagmann et al., 2024). Here, we propose a
-novel source of differences in advice by drawing on recent work on
-belief-based utility, expectation-based reference points (Köszegi, 2006;
-Kőszegi & Rabin, 2009), and the hedonic consequences of information
-(Golman et al., 2017).
-
-Advice figures prominently in workplace and personal decision-making,
-shaping choices about promotions, career paths, and everyday dilemmas
-[@Gino2007; @Harvey1997; @Soll2009]. Its fundamental premise is to
-improve outcomes by enabling decision-makers to learn from others'
-expertise. However, while honest advice can lead to better decisions, it
-can also lead to disappointment when it suggests a desired outcome is
-unlikely to materialize. Advisers may be motivated to offer flattering
-recommendations that align with advisees' hopes, sparing them the
-disappointment of a more sobering forecast.
-
-Advice with the potential for disappointment appears in diverse
-organizational settings: supervisors deliver feedback on employee
-performance, lawyers convey likely outcomes of litigation to their
-clients, and academics offer thoughts on colleagues' manuscripts.
-Ideally, honest information would help people identify their strengths
-and weaknesses, make informed decisions about whether to pursue legal
-cases, and strengthen papers prior to submission to academic journals,
-thus improving long-term outcomes. In practice, however, interpersonal
-considerations may prevent candor. When someone's expectations are (too)
-high, an adviser might hesitate to deliver information that undermines
-it---particularly if doing so risks negative interpersonal
-repercussions.
-
-People often go to great lengths to avoid unpleasant information,
-deriving belief-based utility from maintaining favorable views of
-themselves [@Golman2017; @Ho2018; @Loewenstein2018]. Moreover, they
-often prefer advisers who withhold bad news from them [@Shalvi2019] and
-punish those who communicate bad news [@John2019]. Advisers,
-anticipating these preferences and consequences face a dilemma: Should
-they provide the accurate but potentially painful truth, or shade their
-recommendations to preserve the advisee's mood and the adviser's own
-standing? Advisers who fear they will be blamed or disliked for
-undermining someone's confidence may reasonably avoid candid feedback,
-particularly if they don't incur a cost when the advisee makes a
-mistake.
-
-In our experiments, however, advisees have no opportunity to punish the
-adviser, and advisers' financial incentives are linked to the decisions
-the advisees make. We propose that advisers nonetheless have reason to
-provide flattering advise because they recognize the psychological toll
-of disappointing news. As a result, they may similarly incur a hedonic
-cost for delivering unpleasant information that they anticipate may
-distress the advisee. Thus, even in the anonymized context of an online
-experiment, we hypothesize (and find) that advisers are relucant to
-disappoint advisees and advice is thus biased upward, away from accuracy
-and toward confirming advisees' priors. We show that this reduces the
-quality of advice—but that advisees nonetheless view flattering advisers
-more favorably.
-
-We present the results of three preregistered experiments in which
-participants are paired anonymously as advisers and advisees. Advisers
-are incentivized to offer accurate advice, with bonus earnings depending
-on the outcome of an advisee's decision. We study a setting in which
-advisees can communicate their expectations to an adviser, and
-experimentally manipulate whether advisers observe this expectation. Our
-design simulates organizational contexts where mentors and managers
-often have some sense of an employee's confidence or aspirations and
-thus could adjust their feedback to avoid disappointing them.
-Interpersonal considerations would likely be stronger in situations in
-which the adviser and advisee have an existing relationship and when the
-advice is delivered face-to-face. Moreover, advisers usually do not
-suffer any direct costs when their flattering advice leads to a poor
-outcome for the recipient, particularly when it is not clear what would
-have happened under a counterfactual.\^[In some cases, however, repeated
-interaction might also increase incentives for honest feedback. Someone
-who is known to persistently give overoptimistic advice may be viewed as
-less trustworthy in the long run.]
-
-In Study 1, we nudge advisees into a preference for competing against
-either a group of top-performers or a group of low-performers, through
-the use of a default option. Advisers who observe the actual performance
-of advisees and therefore have the relevant information needed to make a
-recommendation nonetheless take into account the initial preference when
-recommending which group they should compete against. In Study 2, we ask
-advisees to upload photos of themselves and advisers rank them on their
-attractiveness. Advisers then recommend which rank the advisee should
-bet on, receiving an incentive either for the advisee's accuracy or for
-being evaluated favorably. Both groups of advisers recommend a rank that
-is more attractive than what they themselves have evaluated the advisee,
-and those incentivized for likability further inflate the ranking.
-Advisees evaluate advisers more favorably when they recommend betting on
-a more attractive rank, including viewing them as more trustworthy.
-
-In Study 3, we examine a setting in which participants report their
-expected performance on a mathematics quiz. Advisers observe the
-test-taker's true score and, in one treatment, the score they guessed
-they would receive. They then recommend whether the advisee should
-compete against a group of high performers or low performers.
-Importantly, this "competition" is based on the past performance
-observed by the adviser and thus the advisee's expectation does not
-provide instrumental information. However, we find that (1) men expect
-to perform better than women, given identical performance, and (2)
-advisers take these expectations into account. As a result, when
-expectations (but not gender) are known to advisers, the advice given to
-men and women differs, and men are more often advised to compete against
-the group of high performers. Notably, this leads to worse advice for
-men than for women.
+Career trajectories for men and women often differ substantially, even among those with similar qualifications.
+One source of such differences may be the advice that people receive.
+Prior work has documented that men receive more aspirational advice and women more risk-averse advice, which may explain why women are less likely to apply for and ultimately obtain more rewarding positions (Kanze et al., 2018).
+Research on gender discrimination has focused on the role of unconscious bias (Greenwald et al., 2009; Greenwald & Banaji, 1995), but interventions that try to reduce this bias have been largely unsuccessful (Chang et al., 2019; Paluck & Green, 2009).
+Recent work has proposed cognitive, rather than unconscious, biases that can lead to gender discrimination through the formation of false beliefs (Hagmann et al., 2024).
+Here, we propose a novel source of differences in advice by drawing on recent work on belief-based utility, expectation-based reference points (Köszegi, 2006; Kőszegi & Rabin, 2009), and the hedonic consequences of information (Golman et al., 2017).
+
+Advice figures prominently in workplace and personal decision-making, shaping choices about promotions, career paths, and everyday dilemmas [@Gino2007; @Harvey1997; @Soll2009].
+Its fundamental premise is to improve outcomes by enabling decision-makers to learn from others' expertise.
+However, while honest advice can lead to better decisions, it can also lead to disappointment when it suggests a desired outcome is unlikely to materialize.
+Advisers may be motivated to offer flattering recommendations that align with advisees' hopes, sparing them the disappointment of a more sobering forecast.
+
+Advice with the potential for disappointment appears in diverse organizational settings: supervisors deliver feedback on employee performance, lawyers convey likely outcomes of litigation to their clients, and academics offer thoughts on colleagues' manuscripts.
+Ideally, honest information would help people identify their strengths and weaknesses, make informed decisions about whether to pursue legal cases, and strengthen papers prior to submission to academic journals, thus improving long-term outcomes.
+In practice, however, interpersonal considerations may prevent candor.
+When someone's expectations are (too) high, an adviser might hesitate to deliver information that undermines it---particularly if doing so risks negative interpersonal repercussions.
+
+People often go to great lengths to avoid unpleasant information, deriving belief-based utility from maintaining favorable views of themselves [@Golman2017; @Ho2018; @Loewenstein2018].
+Moreover, they often prefer advisers who withhold bad news from them [@Shalvi2019] and punish those who communicate bad news [@John2019].
+Advisers, anticipating these preferences and consequences face a dilemma: Should they provide the accurate but potentially painful truth, or shade their recommendations to preserve the advisee's mood and the adviser's own standing?
+Advisers who fear they will be blamed or disliked for undermining someone's confidence may reasonably avoid candid feedback, particularly if they don't incur a cost when the advisee makes a mistake.
+
+In our experiments, however, advisees have no opportunity to punish the adviser, and advisers' financial incentives are linked to the decisions the advisees make.
+We propose that advisers nonetheless have reason to provide flattering advise because they recognize the psychological toll of disappointing news.
+As a result, they may similarly incur a hedonic cost for delivering unpleasant information that they anticipate may distress the advisee.
+Thus, even in the anonymized context of an online experiment, we hypothesize (and find) that advisers are relucant to disappoint advisees and advice is thus biased upward, away from accuracy and toward confirming advisees' priors.
+We show that this reduces the quality of advice—but that advisees nonetheless view flattering advisers more favorably.
+
+We present the results of three preregistered experiments in which participants are paired anonymously as advisers and advisees.
+Advisers are incentivized to offer accurate advice, with bonus earnings depending on the outcome of an advisee's decision.
+We study a setting in which advisees can communicate their expectations to an adviser, and experimentally manipulate whether advisers observe this expectation.
+Our design simulates organizational contexts where mentors and managers often have some sense of an employee's confidence or aspirations and thus could adjust their feedback to avoid disappointing them.
+Interpersonal considerations would likely be stronger in situations in which the adviser and advisee have an existing relationship and when the advice is delivered face-to-face.
+Moreover, advisers usually do not suffer any direct costs when their flattering advice leads to a poor outcome for the recipient, particularly when it is not clear what would have happened under a counterfactual.\^\[In some cases, however, repeated interaction might also increase incentives for honest feedback.
+Someone who is known to persistently give overoptimistic advice may be viewed as less trustworthy in the long run.\]
+
+In Study 1, we nudge advisees into a preference for competing against either a group of top-performers or a group of low-performers, through the use of a default option.
+Advisers who observe the actual performance of advisees and therefore have the relevant information needed to make a recommendation nonetheless take into account the initial preference when recommending which group they should compete against.
+In Study 2, we ask advisees to upload photos of themselves and advisers rank them on their attractiveness.
+Advisers then recommend which rank the advisee should bet on, receiving an incentive either for the advisee's accuracy or for being evaluated favorably.
+Both groups of advisers recommend a rank that is more attractive than what they themselves have evaluated the advisee, and those incentivized for likability further inflate the ranking.
+Advisees evaluate advisers more favorably when they recommend betting on a more attractive rank, including viewing them as more trustworthy.
+
+In Study 3, we examine a setting in which participants report their expected performance on a mathematics quiz.
+Advisers observe the test-taker's true score and, in one treatment, the score they guessed they would receive.
+They then recommend whether the advisee should compete against a group of high performers or low performers.
+Importantly, this "competition" is based on the past performance observed by the adviser and thus the advisee's expectation does not provide instrumental information.
+However, we find that (1) men expect to perform better than women, given identical performance, and (2) advisers take these expectations into account.
+As a result, when expectations (but not gender) are known to advisers, the advice given to men and women differs, and men are more often advised to compete against the group of high performers.
+Notably, this leads to worse advice for men than for women.
 
@@
 
-We report all manipulations, measures, and data exclusion in our
-experiments. The preregistration reports, screenshots of all
-experimental materials, and the analysis code to replicate all
-statistical analyses and figures are available on the Open Science
-Framework
-(<https://osf.io/8r3d4/?view_only=5ad7bafcd16b4d4ba08bb28b0e2bd02d>).
+We report all manipulations, measures, and data exclusion in our experiments.
+The preregistration reports, screenshots of all experimental materials, and the analysis code to replicate all statistical analyses and figures are available on the Open Science Framework (<https://osf.io/8r3d4/?view_only=5ad7bafcd16b4d4ba08bb28b0e2bd02d>).
 
@@
 
-We first examine whether advisers take into account the expectations of
-advisees when providing a recommendation. A group of participants
-("Advisees") complete a quiz consisting of ten questions that draw on
-ego-relevant domains. They then express a non-binding preference to
-compete against a group of high performers or low performers on the same
-task, based on their past performance. We nudge participants towards
-picking either the low or the high performer group by selecting one of
-the two by default. A second group of participants ("Advisers") observe
-Advisees' score on the quiz and, in one treatment, also which group they
-had selected. We predicted that Advisees who were nudged toward the high
-performer group would be more likely to receive advice to compete
-against this high group when Advisers observed their non-binding choice.
+We first examine whether advisers take into account the expectations of advisees when providing a recommendation.
+A group of participants ("Advisees") complete a quiz consisting of ten questions that draw on ego-relevant domains.
+They then express a non-binding preference to compete against a group of high performers or low performers on the same task, based on their past performance.
+We nudge participants towards picking either the low or the high performer group by selecting one of the two by default.
+A second group of participants ("Advisers") observe Advisees' score on the quiz and, in one treatment, also which group they had selected.
+We predicted that Advisees who were nudged toward the high performer group would be more likely to receive advice to compete against this high group when Advisers observed their non-binding choice.
 
@@
 
-In a preliminary stage, we recruited
-`r scales::comma(dim(study1_ability50)[1])` participants from Prolific
-and gave them five minutes to complete a quiz consisting of ten items.
-The quiz included word puzzles, identifying emotions from photos, and
-selecting the best responses for hypothetical scenarios. These questions
-were adapted from surveys that measure problem-solving, emotional
-intelligence, and communication skills---which we pre-tested as being
-important in modern society and hence where participants might have a
-stake in doing well. Participants received a bonus of five cents for
-each correctly answered question. We then ranked them based on their
-score and label the 20 participants with the lowest (highest) scores as
-the Low (High) Performer Group.
-
-Next, we recruited `r scales::comma(dim(study1_time1)[1])` participants
-for the role of Advisees. They completed the same 10-item quiz, also
-earning five cents for each correct answer. We then asked them to
-express a non-binding preference for whether they would like to compete
-against the High or Low Performer Group. We informed them that they
-would be invited back at a later date when they could make a binding
-decision and they could earn a bonus based on whether their score on
-this quiz was equal to or higher than a randomly selected member from
-their comparison group. If they picked the High Performer Group and had
-an equal or higher score than a randomly selected member of that group,
-they would earn a bonus of 50 cents. If they picked the Low Performer
-Group and outperformed a randomly selected member of that group, they
-could earn a bonus of 20 cents. If their score was lower in this
-comparison, they would not earn an additional bonus. We randomized which
-of the two groups (High or Low Performers) was selected by default, and
-Advisees were free to select the other group. They also made a guess as
-to their score, and the survey concluded with basic demographic
-questions.
-
-We then recruited `r scales::comma(dim(study1_time2_giver)[1])`
-participants for the role of Advisers, and the focal part of our
-experiment. They were informed of the ability quiz that the Advisees had
-completed, how the Low Performer Group and High Performer Groups were
-constructed, as well as the choice and incentives for the Advisees. We
-then asked Advisers to give advice to ten participants on which group
-they should compete against. Advisers were randomly assigned to one of
-two treatments. In the "Performance" treatment, they observed only the
-score of the other participant. In the "Performance + Expectation"
-treatment, they additionally observed the advisee's non-binding choice
-of which group to compete against. However, since the outcome was based
-solely on the past quiz score and advisers, but not advisees, know the
-score, this initial choice was not informative for the purpose of
-recommending competing against one group or the other. Advisers could
-earn the same bonus as one of the participants they had given advice to
-and who returned to make a decision. The survey concluded with basic
-demographic questions.
-
-Finally, we invited Advisees back for the follow-up survey. Following
-our preregistration, we kept the survey open for 7 days. In total,
-`r scales::comma(dim(study1_time3)[1])` Advisees returned. The short
-survey reminded them of the task they completed in the previous survey,
-informed them that other participants from Prolific had observed their
-real score and given them advice on which group to compete against, and
-finally reminded them of how many questions they guessed they had
-answered correctly. They were not informed of their true score or the
-score of the groups they could compete against. Participants then
-observed the advice from a randomly selected adviser and made their
-decision.
+In a preliminary stage, we recruited `r scales::comma(dim(study1_ability50)[1])` participants from Prolific and gave them five minutes to complete a quiz consisting of ten items.
+The quiz included word puzzles, identifying emotions from photos, and selecting the best responses for hypothetical scenarios.
+These questions were adapted from surveys that measure problem-solving, emotional intelligence, and communication skills---which we pre-tested as being important in modern society and hence where participants might have a stake in doing well.
+Participants received a bonus of five cents for each correctly answered question.
+We then ranked them based on their score and label the 20 participants with the lowest (highest) scores as the Low (High) Performer Group.
+
+Next, we recruited `r scales::comma(dim(study1_time1)[1])` participants for the role of Advisees.
+They completed the same 10-item quiz, also earning five cents for each correct answer.
+We then asked them to express a non-binding preference for whether they would like to compete against the High or Low Performer Group.
+We informed them that they would be invited back at a later date when they could make a binding decision and they could earn a bonus based on whether their score on this quiz was equal to or higher than a randomly selected member from their comparison group.
+If they picked the High Performer Group and had an equal or higher score than a randomly selected member of that group, they would earn a bonus of 50 cents.
+If they picked the Low Performer Group and outperformed a randomly selected member of that group, they could earn a bonus of 20 cents.
+If their score was lower in this comparison, they would not earn an additional bonus.
+We randomized which of the two groups (High or Low Performers) was selected by default, and Advisees were free to select the other group.
+They also made a guess as to their score, and the survey concluded with basic demographic questions.
+
+We then recruited `r scales::comma(dim(study1_time2_giver)[1])` participants for the role of Advisers, and the focal part of our experiment.
+They were informed of the ability quiz that the Advisees had completed, how the Low Performer Group and High Performer Groups were constructed, as well as the choice and incentives for the Advisees.
+We then asked Advisers to give advice to ten participants on which group they should compete against.
+Advisers were randomly assigned to one of two treatments.
+In the "Performance" treatment, they observed only the score of the other participant.
+In the "Performance + Expectation" treatment, they additionally observed the advisee's non-binding choice of which group to compete against.
+However, since the outcome was based solely on the past quiz score and advisers, but not advisees, know the score, this initial choice was not informative for the purpose of recommending competing against one group or the other.
+Advisers could earn the same bonus as one of the participants they had given advice to and who returned to make a decision.
+The survey concluded with basic demographic questions.
+
+Finally, we invited Advisees back for the follow-up survey.
+Following our preregistration, we kept the survey open for 7 days.
+In total, `r scales::comma(dim(study1_time3)[1])` Advisees returned.
+The short survey reminded them of the task they completed in the previous survey, informed them that other participants from Prolific had observed their real score and given them advice on which group to compete against, and finally reminded them of how many questions they guessed they had answered correctly.
+They were not informed of their true score or the score of the groups they could compete against.
+Participants then observed the advice from a randomly selected adviser and made their decision.
 
@@
 We begin by examining the performance of the Stage 1 participants.
-Because our default treatment takes place after participants completed
-the ability quiz, we do not expect a difference in performance across
-the Low and High Default treatments. Indeed, the two groups scored no
-different from one another
-(`r round(mean(study1_time1[study1_time1$default == "Low",]$Score),2)`
-and
-`r round(mean(study1_time1[study1_time1$default == "High",]$Score),2)`
-for the Low Default and High Default treatments, respectively,
-`r papaja::apa_print(t.test(Score ~ default, data = study1_time1, var.equal = T))$statistic`).
-The default manipulation affected their initial choices. In the "Low
-Default" treatment, only
-`r round(mean(study1_time1[study1_time1$default == "Low",]$Guess),2)*100`%
-of participants initially preferred competing against the High Performer
-Group, compared to
-`r round(mean(study1_time1[study1_time1$default == "High",]$Guess),2)*100`%
-of participants who saw the High Performer Group highlighted
-($\chi^2$(1, n = 201) = 36.62, p \< .001).
-
-```{r study1regs}
+Because our default treatment takes place after participants completed the ability quiz, we do not expect a difference in performance across the Low and High Default treatments.
+Indeed, the two groups scored no different from one another (`r round(mean(study1_time1[study1_time1$default == "Low",]$Score),2)` and `r round(mean(study1_time1[study1_time1$default == "High",]$Score),2)` for the Low Default and High Default treatments, respectively, `r papaja::apa_print(t.test(Score ~ default, data = study1_time1, var.equal = T))$statistic`).
+The default manipulation affected their initial choices.
+In the "Low Default" treatment, only `r round(mean(study1_time1[study1_time1$default == "Low",]$Guess),2)*100`% of participants initially preferred competing against the High Performer Group, compared to `r round(mean(study1_time1[study1_time1$default == "High",]$Guess),2)*100`% of participants who saw the High Performer Group highlighted ($\chi^2$(1, n = 201) = 36.62, p \< .001).
+
+```{r}
+#| label: tbl-study1regs
+#| tbl-cap: "Advice to compete against the High Performer Group in Study 1.
+Displaying the non-binding choice of those for whom the Low Performer Group was selected by default makes it more likely that they are advised to compete against the High Performer Group (Column 1).
+Column 2 restricts the analysis to advisers who observed advisees' initial non-binding choice and controls for advisees' score on the quiz.
+Standard errors are clustered at the adviser level."
 
@@
   stars = TRUE,
-  gof_map = list(list('raw' = 'nobs', 'clean' = 'N', 'fmt' = 0)),
-  caption = "Advice to compete against the High Performer Group in Study 1.
-Displaying the non-binding choice of those for whom the Low Performer Group was selected by default makes it more likely that they are advised to compete against the High Performer Group (Column 1).
-Column 2 restricts the analysis to advisers who observed advisees' initial non-binding choice and controls for advisees' score on the quiz.
-Standard errors are clustered at the adviser level."
+  gof_map = list(list('raw' = 'nobs', 'clean' = 'N', 'fmt' = 0))
 )
@@
 
-We now examine whether advisers took the advisees' expectations into
-account. Recall that advisees who were defaulted to competing against
-the High Performer Group were indeed more likely to choose this group,
-which, from the advisers' perspective, could signal high confidence in
-their abilities. Our theory predicts that showing expectations should
-lead to more flattering advice--- specifically, a recommendation to
-compete against the High Performer Group--- for advisees with a high
-default choice compared to those with a low default choice. Column 1 of
-Table \@ref(tab:study1regs) reports a linear probability model with
-advice to compete against the high group as the outcome measure,
-incorporating the default choice advisees saw, whether expectations were
-shown to the adviser, and the interaction of the two. Because each
-adviser made ten recommendations, we cluster standard errors at the
-adviser level. As predicted, we find a marginally significant
-interaction effect: advisees with a default choice to compete against
-the High Performer Group (nudged to have high expectations, though not
-necessarily holding them) were more likely to receive advice to compete
-against stronger competitors when their expectations were shown compared
-to when they were hidden. We reported a linear probability model on
-advising to compete against the High Performer group for advisers in the
-"Expectations" treatment, controlling for the true performance of the
-advisee in Column 2 of Table \@ref(tab:study1regs). We observe a
-significant main effect of the default treatment, where a high default
-increased the likelihood of receiving flattering advice. It is worth
-noting that, since only
-`r round(mean(study1_time1[study1_time1$default == "High",]$Guess),2)*100`
-% of advisees in the high default group actually stuck with their
-default choice, this represents a conservative test of the effect of
-high expectations on the likelihood of receiving flattering advice.
-
-```{r study1Advice, fig.cap ="Advisees who were nudged to express high expectations were more likely to receive advice to compete against the High Performer Group."}
+We now examine whether advisers took the advisees' expectations into account.
+Recall that advisees who were defaulted to competing against the High Performer Group were indeed more likely to choose this group, which, from the advisers' perspective, could signal high confidence in their abilities.
+Our theory predicts that showing expectations should lead to more flattering advice--- specifically, a recommendation to compete against the High Performer Group--- for advisees with a high default choice compared to those with a low default choice.
+Column 1 of @tbl-study1regs reports a linear probability model with advice to compete against the high group as the outcome measure, incorporating the default choice advisees saw, whether expectations were shown to the adviser, and the interaction of the two.
+Because each adviser made ten recommendations, we cluster standard errors at the adviser level.
+As predicted, we find a marginally significant interaction effect: advisees with a default choice to compete against the High Performer Group (nudged to have high expectations, though not necessarily holding them) were more likely to receive advice to compete against stronger competitors when their expectations were shown compared to when they were hidden.
+We reported a linear probability model on advising to compete against the High Performer group for advisers in the "Expectations" treatment, controlling for the true performance of the advisee in Column 2 of @tbl-study1regs.
+We observe a significant main effect of the default treatment, where a high default increased the likelihood of receiving flattering advice.
+It is worth noting that, since only `r round(mean(study1_time1[study1_time1$default == "High",]$Guess),2)*100` % of advisees in the high default group actually stuck with their default choice, this represents a conservative test of the effect of high expectations on the likelihood of receiving flattering advice.
+
+```{r}
+#| label: fig-study1Advice
+#| fig-cap: "Advisees who were nudged to express high expectations were more likely to receive advice to compete against the High Performer Group."
+
 study1_time2_advice %>%
@@
 
-When the quality of a decision does not depend on someone's
-expectations, the adviser's awareness of the advisee's expectations
-should not influence the advice given. However, in line with our
-argument that advisers take into account the belief utility of the
-advisee and prefer to flatter rather than disappoint, we find that
-displaying the advisee's expectations does make a difference.
-Specifically, advisees who expressed a preference for stronger
-competitors were more likely to receive 'flattering' advice, encouraging
-them to pursue that option. One possible explanation for this finding is
-that, rather than trying to flatter, advisers may simply be telling
-advisees what they want to hear. In the next study, we aim to
-investigate the mechanism behind this discrepancy in advice-giving when
-expectations are revealed, exploring the question: Why do people give
-flattering advice?
+When the quality of a decision does not depend on someone's expectations, the adviser's awareness of the advisee's expectations should not influence the advice given.
+However, in line with our argument that advisers take into account the belief utility of the advisee and prefer to flatter rather than disappoint, we find that displaying the advisee's expectations does make a difference.
+Specifically, advisees who expressed a preference for stronger competitors were more likely to receive 'flattering' advice, encouraging them to pursue that option.
+One possible explanation for this finding is that, rather than trying to flatter, advisers may simply be telling advisees what they want to hear.
+In the next study, we aim to investigate the mechanism behind this discrepancy in advice-giving when expectations are revealed, exploring the question: Why do people give flattering advice?
 
@@
 
-So far, we have shown that displaying expectations influences the advice
-given. Specifically, advisers were more likely to recommend competing
-against a group of high performers to advisees with higher performance
-expectations compared to those without. We now directly test whether
-this effect is driven by interpersonal concerns. In particular, we
-explore whether more flattering advice stems from a desire to be liked,
-and whether advisees, in turn, like advisers more when they receive
-flattering advice.
-
-We conducted a three-stage experiment in which we experimentally
-manipulated the incentives for advisers. We began by inviting a group of
-advisees to upload photos of themselves ("selfies") and informed them
-that they would be rated on their attractiveness. We grouped them with
-nine other participants of the same gender and recruited participants of
-the opposing gender to rank them from most to least attractive and to
-provide advice. Specifically, we asked them to advise the participant
-they ranked as the 7th most attractive (4th least attractive) on what
-rank they should bet they were ranked by a larger group of raters.
-Advisers were randomly assigned to two treatments, receiving a bonus
-payment either if the advisee guessed their rank accurately or if the
-advisee evaluated the adviser as likeable as measured by an
-unincentivized scale response. We hypothesize that advisers who want to
-be liked by advisees will recommend that they bet on a lower rank, i.e.
+So far, we have shown that displaying expectations influences the advice given.
+Specifically, advisers were more likely to recommend competing against a group of high performers to advisees with higher performance expectations compared to those without.
+We now directly test whether this effect is driven by interpersonal concerns.
+In particular, we explore whether more flattering advice stems from a desire to be liked, and whether advisees, in turn, like advisers more when they receive flattering advice.
+
+We conducted a three-stage experiment in which we experimentally manipulated the incentives for advisers.
+We began by inviting a group of advisees to upload photos of themselves ("selfies") and informed them that they would be rated on their attractiveness.
+We grouped them with nine other participants of the same gender and recruited participants of the opposing gender to rank them from most to least attractive and to provide advice.
+Specifically, we asked them to advise the participant they ranked as the 7th most attractive (4th least attractive) on what rank they should bet they were ranked by a larger group of raters.
+Advisers were randomly assigned to two treatments, receiving a bonus payment either if the advisee guessed their rank accurately or if the advisee evaluated the adviser as likeable as measured by an unincentivized scale response.
+We hypothesize that advisers who want to be liked by advisees will recommend that they bet on a lower rank, i.e.
 that they are more attractive.
@@
 ```{r}
+#| include: false
 
@@
 
-We recruited 300 participants from Prolific and, after asking
-demographic questions, invited them to upload photos of themselves
-(selfies) to be rated by other participants on attractiveness.
-`r scales::comma(dim(study2_time1[study2_time1$gender == 'Male',])[1])`
-men and
-`r scales::comma(dim(study2_time1[study2_time1$gender == 'Female',])[1])`
-women agreed to do so and uploaded pictures that adhered to our
-instructions (e.g., did not include other people). We selected the first
-100 photos from women to arrive at a gender-balanced sample
-($M_{\text{Age}}$ = `r mean(study2_time1_200$age)` years). Participants
-were informed that their selfies would be randomly grouped with those of
-nine other participants of their gender and ranked in terms of
-attractiveness by a group of new Prolific participants of the opposite
-gender. Lastly, they guessed their rank (unincentivized).
-
-Next, we recruited a new, gender-balanced sample for the role of
-advisers. `r scales::comma(dim(study2_time2)[1])` participants from
-Prolific ($M_{\text{Age}}$ = `r mean(study2_time2$age)` years;
-`r round(mean(study2_time2$gender == "Female")*100, 2)`% Female) started
-by providing demographic information, then were matched to a group of
-the opposite gender. They then ranked participants from most to least
-attractive using a drop-down menu next to each picture. Because of a
-limitation with the survey software, participants were able to select
-the same rank for multiple participants, rather than rank them uniquely.
-We remove 115 participants who did not follow instructions and provide a
-unique ranking.
-
-After submitting their ratings, they saw the photo of the participant
-they had ranked as the 7th most attractive (i.e., the 4th least
-attractive). They were reminded of the rank they had given to that
-person and informed that this participant would be invited back and
-could earn a \$1 bonus if they guessed their rank correctly. The rank
-was determined by the aggregate ratings of all participants who had
-ranked this group. Their task was to give advice to this participant
-about the rank they should bet on based on having observed all ten
-selfies and their own assessment. We randomly assigned participants to
-one of two incentivization schemes. In the "Accuracy" treatment, they
-received a bonus identical to the advisee: \$1 if they guessed their
-rank correctly. In the "Likeability" treatment, we informed them that
-they would be rated by the advisee on a 5-point Likert scale for how
-likeable they thought they were. Each point on the scale would translate
-to a bonus of 20 cents. They then selected a rank that they would
-recommend the advisee to bet on.
-
-Finally, we invited participants from Stage 1 and were ranked as the 7th
-attractive by at least one adviser (so that they received advice) back
-for the follow-up survey. Following our preregistration, we kept the
-survey open for 7 days. In total,
-`r scales::comma(dim(study2_time3)[1])` participants
-(`r scales::comma(dim(study2_time3[study2_time3$gender == 'Male',])[1])`
-men,
-`r scales::comma(dim(study2_time3[study2_time3$gender == 'Female',])[1])`
-women) returned. They were reminded of the selfie they uploaded in Stage
-1 and informed that a group of 10 selfies, including theirs, had been
-rated by other participants from Prolific. They then saw the advice from
-a randomly selected adviser and made their estimate with a \$1 incentive
-for guessing accurately. They then saw the rank they had been advised to
-bet on one more time and were asked to rate the adviser's likability,
-warmth, friendliness, good-naturedness, trustworthiness, and sincerity
-on 5-point Likert scales (adapted from @Fiske2007).
+We recruited 300 participants from Prolific and, after asking demographic questions, invited them to upload photos of themselves (selfies) to be rated by other participants on attractiveness.
+`r scales::comma(dim(study2_time1[study2_time1$gender == 'Male',])[1])` men and `r scales::comma(dim(study2_time1[study2_time1$gender == 'Female',])[1])` women agreed to do so and uploaded pictures that adhered to our instructions (e.g., did not include other people).
+We selected the first 100 photos from women to arrive at a gender-balanced sample ($M_{\text{Age}}$ = `r mean(study2_time1_200$age)` years).
+Participants were informed that their selfies would be randomly grouped with those of nine other participants of their gender and ranked in terms of attractiveness by a group of new Prolific participants of the opposite gender.
+Lastly, they guessed their rank (unincentivized).
+
+Next, we recruited a new, gender-balanced sample for the role of advisers.
+`r scales::comma(dim(study2_time2)[1])` participants from Prolific ($M_{\text{Age}}$ = `r mean(study2_time2$age)` years; `r round(mean(study2_time2$gender == "Female")*100, 2)`% Female) started by providing demographic information, then were matched to a group of the opposite gender.
+They then ranked participants from most to least attractive using a drop-down menu next to each picture.
+Because of a limitation with the survey software, participants were able to select the same rank for multiple participants, rather than rank them uniquely.
+We remove 115 participants who did not follow instructions and provide a unique ranking.
+
+After submitting their ratings, they saw the photo of the participant they had ranked as the 7th most attractive (i.e., the 4th least attractive).
+They were reminded of the rank they had given to that person and informed that this participant would be invited back and could earn a \$1 bonus if they guessed their rank correctly.
+The rank was determined by the aggregate ratings of all participants who had ranked this group.
+Their task was to give advice to this participant about the rank they should bet on based on having observed all ten selfies and their own assessment.
+We randomly assigned participants to one of two incentivization schemes.
+In the "Accuracy" treatment, they received a bonus identical to the advisee: \$1 if they guessed their rank correctly.
+In the "Likeability" treatment, we informed them that they would be rated by the advisee on a 5-point Likert scale for how likeable they thought they were.
+Each point on the scale would translate to a bonus of 20 cents.
+They then selected a rank that they would recommend the advisee to bet on.
+
+Finally, we invited participants from Stage 1 and were ranked as the 7th attractive by at least one adviser (so that they received advice) back for the follow-up survey.
+Following our preregistration, we kept the survey open for 7 days.
+In total, `r scales::comma(dim(study2_time3)[1])` participants (`r scales::comma(dim(study2_time3[study2_time3$gender == 'Male',])[1])` men, `r scales::comma(dim(study2_time3[study2_time3$gender == 'Female',])[1])` women) returned.
+They were reminded of the selfie they uploaded in Stage 1 and informed that a group of 10 selfies, including theirs, had been rated by other participants from Prolific.
+They then saw the advice from a randomly selected adviser and made their estimate with a \$1 incentive for guessing accurately.
+They then saw the rank they had been advised to bet on one more time and were asked to rate the adviser's likability, warmth, friendliness, good-naturedness, trustworthiness, and sincerity on 5-point Likert scales (adapted from @Fiske2007).
 
@@
 ```{r}
+#| include: false
 library(dplyr)
@@
 
-```{r study2advice, fig.cap="Advisers were asked to suggest what rank to bet on for someone they ranked as the 7th most attractive out of ten people.
+```{r}
+#| label: fig-study2advice
+#| fig-cap: "Advisers were asked to suggest what rank to bet on for someone they ranked as the 7th most attractive out of ten people.
 When incentivized for accuracy, most of them advised betting on 7, which was based on their evaluation of the recipient's attractiveness.
-However, when incentivized for likability, many participants gave flattering advice by suggesting betting on higher ranks that imply a higher evaluation of attractiveness."}
+However, when incentivized for likability, many participants gave flattering advice by suggesting betting on higher ranks that imply a higher evaluation of attractiveness."
 
@@
 
-We begin by examining the prior beliefs of advisees who uploaded their
-selfies. On average, men guessed they ranked
-`r round(mean(study2_time1[study2_time1$gender == "Male",]$Guess),2)` in
-their group of 10 and women guessed that they ranked
-`r round(mean(study2_time1[study2_time1$gender == "Female",]$Guess),2)`.
-Participants overall underestimate their attractiveness relative to the
-benchmark average of 5.5. Moreover, women do so more than men
-`r papaja::apa_print(t.test(Guess ~ gender, data = study2_time1, var.equal = T))$statistic`.
-Notably, people's self-perceptions correlated strongly with the
-aggregate ratings of the advisers
-(`r round(cor(study2_finalRank$Guess, study2_finalRank$finalRank),2)`,
-`r papaja::apa_print(cor.test(study2_finalRank$Guess, study2_finalRank$finalRank))$statistic`).
-However, there was substantial heterogeneity in perceptions of
-attractiveness. Of the 200 participants,
-`r length(unique(study2_time2$Target))` were ranked as 7th most
-attractive by at least one adviser. On average, men in this subset
-estimated they were ranked
-`r round(mean(TargetsUnique[TargetsUnique$gender == 'Male',]$Guess),2)`th
-and women estimated they were ranked
-`r round(mean(TargetsUnique[TargetsUnique$gender == 'Female',]$Guess),2)`th
-(`r papaja::apa_print(t.test(Guess ~ gender, data = TargetsUnique, var.equal = T))$statistic`).
-
-Next, we turn our attention to the advisers (Figure
-\@ref(fig:study2advice)). In the Accuracy condition, those uploading
-selfies were advised to bet on rank
-`r round(mean(study2_time2[study2_time2$Condition == "Accurate",]$Advice),2)`.
-Notably, this is significantly more attractive than the 7th rank those
-advisers had themselves guessed just on the prior screen
-(`r papaja::apa_print(t.test(study2_time2[study2_time2$Condition == "Accurate",]$Advice, mu = 7, var.equal = T))$statistic`).
-This suggests that even when incentivized for accuracy, participants
-offered flattering advice.[^1] Importantly, and as predicted, we find
-that advisers in the Likeable treatment recommend betting on a lower
-rank, communicating that they think the participant in the selfie is
-more attractive
-(`r round(mean(study2_time2[study2_time2$Condition == "Likable",]$Advice),2)`,
-`r papaja::apa_print(t.test(Advice ~ Condition, data = study2_time2, var.equal = T))$statistic`).
-This suggests that advisers inferred that advising someone that they
-were more attractive would make the adviser appear more likeable and
-therefore provided advice that communicated a more favorable impression
-of the participants' attractiveness. The distribution shown in Figure
-\@ref(fig:study2advice) shows that participants do not simply tell
-participants that they are the most attractive person in the group. They
-may infer that flattering advise needs to be somewhat realistic to be
-believable. We return to this in the general discussion.
+We begin by examining the prior beliefs of advisees who uploaded their selfies.
+On average, men guessed they ranked `r round(mean(study2_time1[study2_time1$gender == "Male",]$Guess),2)` in their group of 10 and women guessed that they ranked `r round(mean(study2_time1[study2_time1$gender == "Female",]$Guess),2)`.
+Participants overall underestimate their attractiveness relative to the benchmark average of 5.5.
+Moreover, women do so more than men `r papaja::apa_print(t.test(Guess ~ gender, data = study2_time1, var.equal = T))$statistic`.
+Notably, people's self-perceptions correlated strongly with the aggregate ratings of the advisers (`r round(cor(study2_finalRank$Guess, study2_finalRank$finalRank),2)`, `r papaja::apa_print(cor.test(study2_finalRank$Guess, study2_finalRank$finalRank))$statistic`).
+However, there was substantial heterogeneity in perceptions of attractiveness.
+Of the 200 participants, `r length(unique(study2_time2$Target))` were ranked as 7th most attractive by at least one adviser.
+On average, men in this subset estimated they were ranked `r round(mean(TargetsUnique[TargetsUnique$gender == 'Male',]$Guess),2)`th and women estimated they were ranked `r round(mean(TargetsUnique[TargetsUnique$gender == 'Female',]$Guess),2)`th (`r papaja::apa_print(t.test(Guess ~ gender, data = TargetsUnique, var.equal = T))$statistic`).
+
+Next, we turn our attention to the advisers (@fig-study2advice).
+In the Accuracy condition, those uploading selfies were advised to bet on rank `r round(mean(study2_time2[study2_time2$Condition == "Accurate",]$Advice),2)`.
+Notably, this is significantly more attractive than the 7th rank those advisers had themselves guessed just on the prior screen (`r papaja::apa_print(t.test(study2_time2[study2_time2$Condition == "Accurate",]$Advice, mu = 7, var.equal = T))$statistic`).
+This suggests that even when incentivized for accuracy, participants offered flattering advice.[^1] Importantly, and as predicted, we find that advisers in the Likeable treatment recommend betting on a lower rank, communicating that they think the participant in the selfie is more attractive (`r round(mean(study2_time2[study2_time2$Condition == "Likable",]$Advice),2)`, `r papaja::apa_print(t.test(Advice ~ Condition, data = study2_time2, var.equal = T))$statistic`).
+This suggests that advisers inferred that advising someone that they were more attractive would make the adviser appear more likeable and therefore provided advice that communicated a more favorable impression of the participants' attractiveness.
+The distribution shown in @fig-study2advice shows that participants do not simply tell participants that they are the most attractive person in the group.
+They may infer that flattering advise needs to be somewhat realistic to be believable.
+We return to this in the general discussion.
 
 [^1]: This shading could be due to concerns of avoiding disappointment.
-    However, it could also be that advisers are uncertain about the
-    rankings they had given and make a recommendation that combines
-    their own belief with a uniform prior.
+However, it could also be that advisers are uncertain about the rankings they had given and make a recommendation that combines their own belief with a uniform prior.
 
@@
 
-```{r study2regs}
+```{r}
+#| label: tbl-study2regs
+#| tbl-cap: "When individuals receive advice that implies a high level of attractiveness (lower rank), they tend to perceive the advice giver as more likable (Column 1), warm (Column 2).
+Column 3 shows that advisors are rated as more trustworthy when they advice lower ranks, but this relationship is only directional."
 
@@
                            stars = T,
-                           gof_map = list(list('raw' = 'nobs', 'clean' = 'N', 'fmt' = 0)),
-                           caption = "When individuals receive advice that implies a high level of attractiveness (lower rank), they tend to perceive the advice giver as more likable (Column 1), warm (Column 2).
-Column 3 shows that advisors are rated as more trustworthy when they advice lower ranks, but this relationship is only directional.")
-
-```
-
-Finally, we examine whether flattering advice indeed leads to more
-positive evaluations of advisers, or whether flattering advice is
-dismissed as insencere. Following our preregistration, we average the
-ratings on likeability, warmth, friendliness, and good-naturedness to
-create a scale of likeability ($\alpha$ =
-`r cronbach.alpha(study2_time3[, 5:8])$alpha`); and we create a scale of
-trustworthiness by averaging the ratings of trustworthiness and
-sincerity ($\alpha$ = `r cronbach.alpha(study2_time3[, 9:10])$alpha`).
-
-```{r study2rating, fig.cap="Participants tend to rate advisors who suggest betting on a higher rank (implying greater attractiveness) as more likable and warm."}
+                           gof_map = list(list('raw' = 'nobs', 'clean' = 'N', 'fmt' = 0)))
+
+```
+
+Finally, we examine whether flattering advice indeed leads to more positive evaluations of advisers, or whether flattering advice is dismissed as insencere.
+Following our preregistration, we average the ratings on likeability, warmth, friendliness, and good-naturedness to create a scale of likeability ($\alpha$ = `r cronbach.alpha(study2_time3[, 5:8])$alpha`); and we create a scale of trustworthiness by averaging the ratings of trustworthiness and sincerity ($\alpha$ = `r cronbach.alpha(study2_time3[, 9:10])$alpha`).
+
+```{r}
+#| label: fig-study2rating
+#| fig-cap: "Participants tend to rate advisors who suggest betting on a higher rank (implying greater attractiveness) as more likable and warm."
 
@@
 
-```{r study2ratingByGroup, fig.cap="After participants received advice that suggested betting on a rank that was lower than, equal to, or higher than their self-expectations, they evaluated advisors based on their likability and warmth.
-Participants rated advisors who gave flattering advice and delivered a high evaluation of their attractiveness as more likable and warm than those whose advice implied a lower evaluation of their attractiveness."}
+```{r}
+#| label: fig-study2ratingByGroup
+#| fig-cap: "After participants received advice that suggested betting on a rank that was lower than, equal to, or higher than their self-expectations, they evaluated advisors based on their likability and warmth.
+Participants rated advisors who gave flattering advice and delivered a high evaluation of their attractiveness as more likable and warm than those whose advice implied a lower evaluation of their attractiveness."
 
@@
 
-As seen in Figure \@ref(fig:study2rating), we found that advisees who
-suggested that the advisee was more attractive (lower rank) were indeed
-rated as more likeable and warm (b = -0.109, p \< .05; b = -0.133, p \<
-.001, respectively; See Columns 1 and 2 of Table \@ref(tab:study2regs)).
-When using their self-expectations as a reference point, advisors who
-suggest a rank lower than that point are perceived as less likable and
-warm (see Figure \@ref(fig:study2ratingByGroup)). Interestingly, these
-benefits are not at the cost of being hypocritical; advisers who
-recommend a more favorable rank are viewed as no less trustworthy
-(Column 3 of Table \@ref(tab:study2regs)).
-
-We were not powered to do a comparison across the two experimental
-groups and did not preregister such a difference. Indeed, we find no
-difference in likeability and warmth across the two treatments
-(`r papaja::apa_print(t.test(likable ~ Condition, data = study2_time3, var.equal = T))$statistic`,
-and
-`r papaja::apa_print(t.test(warmAvg ~ Condition, data = study2_time3, var.equal = T))$statistic`,
-respectively). We also assess the quality of advice by measuring the
-discrepancy between the advised rank and the final rank. Our analysis
-revealed no significant difference between the two treatments in terms
-of how helpful the advice was for advisees in making accurate guesses,
-`r papaja::apa_print(t.test(accuracy ~ Condition, data = study2_time3, var.equal = T))$statistic`.
+As seen in @fig-study2rating, we found that advisees who suggested that the advisee was more attractive (lower rank) were indeed rated as more likeable and warm (b = -0.109, p \< .05; b = -0.133, p \< .001, respectively; See Columns 1 and 2 of @tbl-study2regs).
+When using their self-expectations as a reference point, advisors who suggest a rank lower than that point are perceived as less likable and warm (see @fig-study2ratingByGroup).
+Interestingly, these benefits are not at the cost of being hypocritical; advisers who recommend a more favorable rank are viewed as no less trustworthy (Column 3 of @tbl-study2regs).
+
+We were not powered to do a comparison across the two experimental groups and did not preregister such a difference.
+Indeed, we find no difference in likeability and warmth across the two treatments (`r papaja::apa_print(t.test(likable ~ Condition, data = study2_time3, var.equal = T))$statistic`, and `r papaja::apa_print(t.test(warmAvg ~ Condition, data = study2_time3, var.equal = T))$statistic`, respectively).
+We also assess the quality of advice by measuring the discrepancy between the advised rank and the final rank.
+Our analysis revealed no significant difference between the two treatments in terms of how helpful the advice was for advisees in making accurate guesses, `r papaja::apa_print(t.test(accuracy ~ Condition, data = study2_time3, var.equal = T))$statistic`.
 
@@
 
-In another context where advice communicates ego-relevant information
-(here, people's attractiveness), we find that the advice people give is
-contingent on their incentives. Specifically, when they get rewarded for
-being more likeable, they recommend that the advisee bet on a more
-favorable rank than when they are incentivized for accuracy.
-Importantly, advisees do not discount flattering advice and instead
-evaluate people who advise them to bet on a more attractive rank as
-warmer and more likeable. These gains to interpersonal perceptions do
-not come at the cost of trustworthiness, even when the advice is
-substantially inflated (e.g., a recommendation that the advisee is the
-most attractive in the group).
+In another context where advice communicates ego-relevant information (here, people's attractiveness), we find that the advice people give is contingent on their incentives.
+Specifically, when they get rewarded for being more likeable, they recommend that the advisee bet on a more favorable rank than when they are incentivized for accuracy.
+Importantly, advisees do not discount flattering advice and instead evaluate people who advise them to bet on a more attractive rank as warmer and more likeable.
+These gains to interpersonal perceptions do not come at the cost of trustworthiness, even when the advice is substantially inflated (e.g., a recommendation that the advisee is the most attractive in the group).
 
@@
 
-In Study 3, we replicate the main effect in a different ego-relevant
-domain: intelligence. The experimental design is conceptually identical
-to Study 1, but this time we utilize a more direct measure of
-expectation by asking participants to estimate their scores.
+In Study 3, we replicate the main effect in a different ego-relevant domain: intelligence.
+The experimental design is conceptually identical to Study 1, but this time we utilize a more direct measure of expectation by asking participants to estimate their scores.
 
 This three-stage experiment begins with measuring actual performance.
-Participants are then anchored to low or high performance expectations
-and asked to guess how many questions they answered correctly. As in
-previous studies, we recruit advisers who are presented with either just
-the advisee's true performance or both the true performance and the
-number of questions the advisee believes they answered correctly.
+Participants are then anchored to low or high performance expectations and asked to guess how many questions they answered correctly.
+As in previous studies, we recruit advisers who are presented with either just the advisee's true performance or both the true performance and the number of questions the advisee believes they answered correctly.
 Advisers are then asked to provide advice on choosing a competitor.
-Finally, we present the advice to the advisees and ask them to make
-their final choice. Our key hypotheses are: (1) advisees anchored to
-high expectations will be more likely to receive advice to compete
-against the high-performing group, and (2) men will be more likely than
-women to be advised to compete against the high-performing group when
-expectations are disclosed.
+Finally, we present the advice to the advisees and ask them to make their final choice.
+Our key hypotheses are: (1) advisees anchored to high expectations will be more likely to receive advice to compete against the high-performing group, and (2) men will be more likely than women to be advised to compete against the high-performing group when expectations are disclosed.
 
@@
 
-We begin by first recruiting a sample of
-`r scales::comma(dim(study3_math50)[1])` participants from Prolific to
-complete a 10-question multiple choice mathematics quiz. The questions
-were taken from a paper-version of the ASVAB standardized exam, such
-that answers were not available online. Participants had five minutes to
-answer the quiz and were paid 10 cents for each correctly answered
-question. Like before, we define top 20 scores as "High Performers" and
-the bottom 20 scorers as the "Low Performers." On average, participants
-answered `r round(mean(study3_math50$Score),2)` questions correctly,
-High Performers scored between `r HP_lower` and `r HP_upper`, and Low
-Performers scored between `r LP_lower` and `r LP_upper`. In order to
-anchor the expectations of participants in our main experiment, we
-simulated 1,000 pairings of groups of five participants, with the
-5<sup>th</sup> percentile of groups scoring an average of `r p5` and the
-95 th percentile scoring an average of `r p95`. We report these averages
-to participants in the Low Expectations and High Expectations treatment,
-respectively.
-
-We then recruited `r scales::comma(dim(study3_time1All)[1])`
-participants for the role of advisees in Stage 1 of our main experiment.
-To arrive at a gender-balanced sample, we dropped the last two male
-participants to complete the survey, ending up with a sample of 500 men
-and 500 women ($M_{\text{Age}}$ = `r mean(study3_time1$Age)`).
-Participants completed the same 10-item mathematics quiz as the earlier
-participants and were informed that their performance would affect their
-bonus earnings in a follow-up stage to be conducted a few days later.
-After completing the quiz, we informed them of the average score of a
-group of five participants from the preliminary survey. We randomly
-assigned them to learn about the 5<sup>th</sup> percentile of groups,
-which scored `r p5`. ("Low Expectations" treatment) or the
-95<sup>th</sup> percentile of groups, which scored `r p95` ("High
-Expectations" treatment). Participants then made a guess
-(unincentivized) about how many questions they think they answered
-correctly. The survey concluded with basic demographic questions.
-
-We then recruited `r scales::comma(dim(study3_time2_giver)[1])`
-participants for Stage 2, placing them in the role of advisers. We began
-by informing them of the mathematics quiz that participants in the
-preliminary study and Stage 1 had completed, and informed them of the
-average score of all participants in the preliminary study. Advisers had
-to recommend whether an advisee should compete against the Low
-Performers or the High Performers (we used these terms in the survey).
-We anticipated that being told to compete against High Performers is
-more flattering and hence being told to compete against the Low
-Performers would be disappointing if one had expected to do well.
-Advisees could earn a bonus if their score was equal to or higher than
-that of a randomly selected member from their chosen group. Competing
-against the High Performers was more challenging, resulting in an
-average bonus of 50 cents, compared to 30 cents when competing against
-other groups.
+We begin by first recruiting a sample of `r scales::comma(dim(study3_math50)[1])` participants from Prolific to complete a 10-question multiple choice mathematics quiz.
+The questions were taken from a paper-version of the ASVAB standardized exam, such that answers were not available online.
+Participants had five minutes to answer the quiz and were paid 10 cents for each correctly answered question.
+Like before, we define top 20 scores as "High Performers" and the bottom 20 scorers as the "Low Performers." On average, participants answered `r round(mean(study3_math50$Score),2)` questions correctly, High Performers scored between `r HP_lower` and `r HP_upper`, and Low Performers scored between `r LP_lower` and `r LP_upper`.
+In order to anchor the expectations of participants in our main experiment, we simulated 1,000 pairings of groups of five participants, with the 5<sup>th</sup> percentile of groups scoring an average of `r p5` and the 95 th percentile scoring an average of `r p95`.
+We report these averages to participants in the Low Expectations and High Expectations treatment, respectively.
+
+We then recruited `r scales::comma(dim(study3_time1All)[1])` participants for the role of advisees in Stage 1 of our main experiment.
+To arrive at a gender-balanced sample, we dropped the last two male participants to complete the survey, ending up with a sample of 500 men and 500 women ($M_{\text{Age}}$ = `r mean(study3_time1$Age)`).
+Participants completed the same 10-item mathematics quiz as the earlier participants and were informed that their performance would affect their bonus earnings in a follow-up stage to be conducted a few days later.
+After completing the quiz, we informed them of the average score of a group of five participants from the preliminary survey.
+We randomly assigned them to learn about the 5<sup>th</sup> percentile of groups, which scored `r p5`.
+("Low Expectations" treatment) or the 95<sup>th</sup> percentile of groups, which scored `r p95` ("High Expectations" treatment).
+Participants then made a guess (unincentivized) about how many questions they think they answered correctly.
+The survey concluded with basic demographic questions.
+
+We then recruited `r scales::comma(dim(study3_time2_giver)[1])` participants for Stage 2, placing them in the role of advisers.
+We began by informing them of the mathematics quiz that participants in the preliminary study and Stage 1 had completed, and informed them of the average score of all participants in the preliminary study.
+Advisers had to recommend whether an advisee should compete against the Low Performers or the High Performers (we used these terms in the survey).
+We anticipated that being told to compete against High Performers is more flattering and hence being told to compete against the Low Performers would be disappointing if one had expected to do well.
+Advisees could earn a bonus if their score was equal to or higher than that of a randomly selected member from their chosen group.
+Competing against the High Performers was more challenging, resulting in an average bonus of 50 cents, compared to 30 cents when competing against other groups.
 
 Like before, advisers were randomly assigned to one of two treatments.
-In the "Baseline" treatment, they only observed the score of the advisee
-on the mathematics quiz. In the "Expectation" treatment, they observed
-the score as well as the advisee's guess for how many questions they
-answered correctly. We want to emphasize that sice the outcome is
-determined only by the past score on the quiz, the advisee's guess is
-immaterial to which group they should compete against. Moreover, in
-neither treatment did they receive any demographic information about
-their advisee. Participants gave recommendations to 10 advisees, which
-unbeknownst to them were five men and five women matched to have
-identical performance on the test.[^2] They were informed that if their
-advice was shown to a participant who returned for the follow-up survey,
-they would receive the identical bonus as that participant. The survey
-then concluded with basic demographic questions.
-
-[^2]: We made this decision to account for the possibility of gender
-    differences in performance.
-
-Finally, we invited participants from Stage 1 back for the follow-up
-survey. Following our preregistration, we kept the survey open for 7
-days. In total, `r scales::comma(dim(study3_time3)[1])` participants
-(`r scales::comma(dim(study3_time3[study3_time3$Gender == 'Male',])[1])`
-men,
-`r scales::comma(dim(study3_time3[study3_time3$Gender == 'Female',])[1])`
-women) returned. The brief survey reminded them of the task they
-completed in Stage 1, informed them that other participants from
-Prolific had observed their real score and given them advice against
-which group to compete against, and finally were reminded them of how
-many questions they guessed they had answered correctly. Importantly,
-they were not informed of their true score or the score of the groups
-they could compete against. Participants then observed the advice from a
-randomly selected adviser and made their decision.
+In the "Baseline" treatment, they only observed the score of the advisee on the mathematics quiz.
+In the "Expectation" treatment, they observed the score as well as the advisee's guess for how many questions they answered correctly.
+We want to emphasize that sice the outcome is determined only by the past score on the quiz, the advisee's guess is immaterial to which group they should compete against.
+Moreover, in neither treatment did they receive any demographic information about their advisee.
+Participants gave recommendations to 10 advisees, which unbeknownst to them were five men and five women matched to have identical performance on the test.[^2] They were informed that if their advice was shown to a participant who returned for the follow-up survey, they would receive the identical bonus as that participant.
+The survey then concluded with basic demographic questions.
+
+[^2]: We made this decision to account for the possibility of gender differences in performance.
+
+Finally, we invited participants from Stage 1 back for the follow-up survey.
+Following our preregistration, we kept the survey open for 7 days.
+In total, `r scales::comma(dim(study3_time3)[1])` participants (`r scales::comma(dim(study3_time3[study3_time3$Gender == 'Male',])[1])` men, `r scales::comma(dim(study3_time3[study3_time3$Gender == 'Female',])[1])` women) returned.
+The brief survey reminded them of the task they completed in Stage 1, informed them that other participants from Prolific had observed their real score and given them advice against which group to compete against, and finally were reminded them of how many questions they guessed they had answered correctly.
+Importantly, they were not informed of their true score or the score of the groups they could compete against.
+Participants then observed the advice from a randomly selected adviser and made their decision.
 
@@
 We begin by examining the performance of the Stage 1 participants.
-Because our treatment takes place after participants completed the
-mathematics quiz, we would not expect a difference in performance across
-the Low and High Expectations treatments. Indeed, the two groups scored
-no different from one another
-(`r round(mean(study3_time1[study3_time1$Condition == "Low",]$count),2)`
-and
-`r round(mean(study3_time1[study3_time1$Condition == "High",]$count),2)`
-for the Low Expectations and High Expectations treatments, respectively,
-`r papaja::apa_print(t.test(count ~ Condition, data = study3_time1, var.equal = T))$statistic`).
-The expectations treatment did, however, affect how well they thought
-they performed. Participants in the "Low Expectations" treatment guessed
-a score of
-`r round(mean(study3_time1[study3_time1$Condition == "Low",]$count),2)`
-vs.
-`r round(mean(study3_time1[study3_time1$Condition == "High",]$Guess),2)`
-in the High Expectations treatment
-(`r papaja::apa_print(t.test(Guess ~ Condition, data = study3_time1, var.equal = T))$statistic`),
-showing that the manipulation was successful, albeit small. Contrary to
-our expectations, we did find a gender difference in performance: men
-scored
-`r round(mean(study3_time1[study3_time1$Gender == "Male",]$count),2)` on
-average, while women scored
-`r round(mean(study3_time1[study3_time1$Gender == "Female",]$count),2)`
-(`r papaja::apa_print(t.test(count ~ Gender, data = study3_time1, var.equal = T))$statistic`).
-Consistent with this difference, men thought they answered more
-questions correctly than did women
-(`r round(mean(study3_time1[study3_time1$Gender == "Male",]$Guess),2)`
-vs
-`r round(mean(study3_time1[study3_time1$Gender == "Female",]$Guess),2)`,
-`r papaja::apa_print(t.test(Guess ~ Gender, data = study3_time1, var.equal = T))$statistic`).
-This difference, however, does not affect the interpretation of our
-findings, which will rely on an interaction of gender with an
-experimental treatment for Stage 2 participants.
-
-We define a measure of "overconfidence" as (Performance - Estimate). We
-observe that women underestimate their performance by 0.76 points, while
-men do so by only 0.27 points
-`r papaja::apa_print(t.test(overconfidence ~ Gender, data = study3_time1 %>% dplyr::mutate(overconfidence = Guess - count)))$full_result`.
-Although neither gender is overconfident, men on average are more
-confident in their performance than are women, as we had expected.
-
-```{r study3regs}
+Because our treatment takes place after participants completed the mathematics quiz, we would not expect a difference in performance across the Low and High Expectations treatments.
+Indeed, the two groups scored no different from one another (`r round(mean(study3_time1[study3_time1$Condition == "Low",]$count),2)` and `r round(mean(study3_time1[study3_time1$Condition == "High",]$count),2)` for the Low Expectations and High Expectations treatments, respectively, `r papaja::apa_print(t.test(count ~ Condition, data = study3_time1, var.equal = T))$statistic`).
+The expectations treatment did, however, affect how well they thought they performed.
+Participants in the "Low Expectations" treatment guessed a score of `r round(mean(study3_time1[study3_time1$Condition == "Low",]$count),2)` vs.
+`r round(mean(study3_time1[study3_time1$Condition == "High",]$Guess),2)` in the High Expectations treatment (`r papaja::apa_print(t.test(Guess ~ Condition, data = study3_time1, var.equal = T))$statistic`), showing that the manipulation was successful, albeit small.
+Contrary to our expectations, we did find a gender difference in performance: men scored `r round(mean(study3_time1[study3_time1$Gender == "Male",]$count),2)` on average, while women scored `r round(mean(study3_time1[study3_time1$Gender == "Female",]$count),2)` (`r papaja::apa_print(t.test(count ~ Gender, data = study3_time1, var.equal = T))$statistic`).
+Consistent with this difference, men thought they answered more questions correctly than did women (`r round(mean(study3_time1[study3_time1$Gender == "Male",]$Guess),2)` vs `r round(mean(study3_time1[study3_time1$Gender == "Female",]$Guess),2)`, `r papaja::apa_print(t.test(Guess ~ Gender, data = study3_time1, var.equal = T))$statistic`).
+This difference, however, does not affect the interpretation of our findings, which will rely on an interaction of gender with an experimental treatment for Stage 2 participants.
+
+We define a measure of "overconfidence" as (Performance - Estimate).
+We observe that women underestimate their performance by 0.76 points, while men do so by only 0.27 points `r papaja::apa_print(t.test(overconfidence ~ Gender, data = study3_time1 %>% dplyr::mutate(overconfidence = Guess - count)))$full_result`.
+Although neither gender is overconfident, men on average are more confident in their performance than are women, as we had expected.
+
+```{r}
+#| label: tbl-study3regs
+#| tbl-cap: "Column 1 displays the advice given to compete against a High Performance group based on whether the advisees were primed with low or high expectations and the expectation level shown to the advisor.
+Column 2 displays the advice given to compete against a High Performance group based on the gender of the targets and the expectation level shown to the advisor.
+Column 3 displays the expected bonus of the advice received based on the gender of the targets and the expectation level shown to the advisor.
+All standard errors clustered at the level of the advisor."
+
 study3_advice <- study3_advice %>% dplyr::mutate(Treatment = factor(Treatment, levels = c('Low', 'High'))) %>%
@@
                            stars = T,
-                           gof_map = list(list('raw' = 'nobs', 'clean' = 'N', 'fmt' = 0)),
-                           caption = "Column 1 displays the advice given to compete against a High Performance group based on whether the advisees were primed with low or high expectations and the expectation level shown to the advisor.
-Column 2 displays the advice given to compete against a High Performance group based on the gender of the targets and the expectation level shown to the advisor.
-Column 3 displays the expected bonus of the advice received based on the gender of the targets and the expectation level shown to the advisor.
-All standard errors clustered at the level of the advisor.")
-
-```
-
-```{r study3genderdiff, fig.cap ="Advisers observed real performance and the participants' estimated performance, but not their gender.
+                           gof_map = list(list('raw' = 'nobs', 'clean' = 'N', 'fmt' = 0)))
+
+```
+
+```{r}
+#| label: fig-study3genderdiff
+#| fig-cap: "Advisers observed real performance and the participants' estimated performance, but not their gender.
 As a result of their higher expectations, men (blue) were advised to compete against the high performance group more often than women (red).
-The grey line shows advice absent expectations, which did not differ by gender."}
+The grey line shows advice absent expectations, which did not differ by gender."
+
 library(dplyr)
@@
 
-Next, we examine whether advisers took the advisee's expectations into
-account. Column 1 of Table \@ref(tab:study3regs) reports a linear
-probability model on advising to compete against the High Performer
-group for advisers in the "Expectations" treatment, controlling for the
-true performance of the advisee. Because each adviser made ten
-recommendations, we cluster standard errors at the adviser level.
-However, contrary to our expectations, we do not see a significant
-effect of the expectations treatment. This may be because the induced
-difference in expectations was too small.
-
-However, recall that men were more confident in their performance than
-were women. Our theory thus predicts that showing expectations should
-lead to more flattering advice (i.e., a recommendation to compete
-against the High Performer group) for men than for women. We report a
-linear probability model with advice to compete against the high group
-as the outcome measure, and the advisee's gender, whether expectations
-were shown to the adviser, and the interaction of the two in Column 2 of
-Table \@ref(tab:study3regs). As predicted, we find a significant
-interaction effect: men are more likely to be advised to compete against
-the High Performers when expectations are shown than when they are
-hidden ($p < 0.001$). We show this result graphically in Figure
-\@ref(fig:study3genderdiff)).
-
-To examine the quality of advice, we computed the expected bonus
-earnings for someone who followed the recommendations. For example, if
-an adviser suggested competing against the High Performer group, we
-matched the advisee against all 20 members of that group and determined
-how often their score matched or exceeded that of the member. We then
-multiplied this number by the respective bonus earnings (50 cents and 30
-cents for the High and Low Performer group, respectively). To see if
-including expectations leads to worse advise for men, we report a linear
-probability model with the experimental treatment of the adviser, the
-gender of the advisee, and their interaction in Column 3 of Table
-\@ref(tab:study3regs). Displaying expectations led men to be advised to
-compete against the High Performer group more often, and this advise
-turned out to be bad: men receive worse advise than do women when
-expectations are displayed, but not in their absence.[^3]
-
-[^3]: This analysis was not preregistered, and we note here that the
-    reduction in expected earnings is small. However, it is interesting
-    that expectations have a negative effect for men who underestimate
-    their performance on average. One possibility is that advisers
-    suggest the High Performer group more often than is optimal. We
-    return to the possibility that advice is overall biased to be
-    flattering in Study 2.
-
-```{r study3time3}
+Next, we examine whether advisers took the advisee's expectations into account.
+Column 1 of @tbl-study3regs reports a linear probability model on advising to compete against the High Performer group for advisers in the "Expectations" treatment, controlling for the true performance of the advisee.
+Because each adviser made ten recommendations, we cluster standard errors at the adviser level.
+However, contrary to our expectations, we do not see a significant effect of the expectations treatment.
+This may be because the induced difference in expectations was too small.
+
+However, recall that men were more confident in their performance than were women.
+Our theory thus predicts that showing expectations should lead to more flattering advice (i.e., a recommendation to compete against the High Performer group) for men than for women.
+We report a linear probability model with advice to compete against the high group as the outcome measure, and the advisee's gender, whether expectations were shown to the adviser, and the interaction of the two in Column 2 of @tbl-study3regs.
+As predicted, we find a significant interaction effect: men are more likely to be advised to compete against the High Performers when expectations are shown than when they are hidden ($p < 0.001$).
+We show this result graphically in @fig-study3genderdiff.
+
+To examine the quality of advice, we computed the expected bonus earnings for someone who followed the recommendations.
+For example, if an adviser suggested competing against the High Performer group, we matched the advisee against all 20 members of that group and determined how often their score matched or exceeded that of the member.
+We then multiplied this number by the respective bonus earnings (50 cents and 30 cents for the High and Low Performer group, respectively).
+To see if including expectations leads to worse advise for men, we report a linear probability model with the experimental treatment of the adviser, the gender of the advisee, and their interaction in Column 3 of @tbl-study3regs.
+Displaying expectations led men to be advised to compete against the High Performer group more often, and this advise turned out to be bad: men receive worse advise than do women when expectations are displayed, but not in their absence.[^3]
+
+[^3]: This analysis was not preregistered, and we note here that the reduction in expected earnings is small.
+However, it is interesting that expectations have a negative effect for men who underestimate their performance on average.
+One possibility is that advisers suggest the High Performer group more often than is optimal.
+We return to the possibility that advice is overall biased to be flattering in Study 2.
+
+```{r}
+#| label: tbl-study3time3
+#| tbl-cap: "Column 1 displays the actual bonus based on the performance and whether the participant is primed with high expectations.
+Column 2 displays the actual bonus based on the performance and gender of the participant.
+Columns 3 and 4 display the chance of adopting the advice based on the gender of the participants, whether the advisee sees expectations, and whether the advice is to compete against high performers.
+The former considers only the main effect, while the latter also includes the interactive effect."
 
@@
                            stars = T,
-                           gof_map = list(list('raw' = 'nobs', 'clean' = 'N', 'fmt' = 0)),
-                           caption = "Column 1 displays the actual bonus based on the performance and whether the participant is primed with high expectations.
-Column 2 displays the actual bonus based on the performance and gender of the participant.
-Columns 3 and 4 display the chance of adopting the advice based on the gender of the participants, whether the advisee sees expectations, and whether the advice is to compete against high performers.
-The former considers only the main effect, while the latter also includes the interactive effect.")
-
-```
-
-To determine whether flattering advice is truly costly, however, we need
-to examine the outcome of the advisees. In particular, they could ignore
-flattering advice, recognizing it as such and thus failing to adhere to
-it. Align with our prediction, participants who were primed with high
-expectations earned less when their expectations were conveyed to the
-advisers, although this result is only directional (see Column 1 of
-Table \@ref(tab:study3time3)). Similarly, as shown in Column 2 of Table
-\@ref(tab:study3time3), we also found that male participants received
-less reward when their expectations were presented, even when their
-performance was the same. These findings suggest that flattering advice
-is not without consequences. Furthermore, our research indicates that
-because males are more likely to follow such advice (see Column 4 of
-Table \@ref(tab:study3time3), their tendency towards competition
-intensifies the cost of such advice.
+                           gof_map = list(list('raw' = 'nobs', 'clean' = 'N', 'fmt' = 0)))
+
+```
+
+To determine whether flattering advice is truly costly, however, we need to examine the outcome of the advisees.
+In particular, they could ignore flattering advice, recognizing it as such and thus failing to adhere to it.
+Align with our prediction, participants who were primed with high expectations earned less when their expectations were conveyed to the advisers, although this result is only directional (see Column 1 of @tbl-study3time3).
+Similarly, as shown in Column 2 of @tbl-study3time3, we also found that male participants received less reward when their expectations were presented, even when their performance was the same.
+These findings suggest that flattering advice is not without consequences.
+Furthermore, our research indicates that because males are more likely to follow such advice (see Column 4 of @tbl-study3time3), their tendency towards competition intensifies the cost of such advice.
 
@@
 We found supportive evidence for our argument in a different domain.
-Advisors tend to consider advisees' self-expectations and match their
-advice accordingly, aiming to avoid disappointment. Consistent with the
-confidence gap narrative, men tend to underestimate their mathematics
-test scores less than women. When these expectations are displayed to
-advisors, they are more likely to advise men to compete against high
-performers. Notably, this turns out to be poor advice: men whose
-advisors were aware of their expectations received worse advice. Our
-findings suggest that men with the same scores as their female
-counterparts ended up earning less, although this result is only
-directional. This discrepancy may be due to men receiving more favorable
-advice, being more likely to follow it, and ultimately facing worse
-outcomes.
+Advisors tend to consider advisees' self-expectations and match their advice accordingly, aiming to avoid disappointment.
+Consistent with the confidence gap narrative, men tend to underestimate their mathematics test scores less than women.
+When these expectations are displayed to advisors, they are more likely to advise men to compete against high performers.
+Notably, this turns out to be poor advice: men whose advisors were aware of their expectations received worse advice.
+Our findings suggest that men with the same scores as their female counterparts ended up earning less, although this result is only directional.
+This discrepancy may be due to men receiving more favorable advice, being more likely to follow it, and ultimately facing worse outcomes.
 
@@
 Advice has the potential to shape people's career and personal outcomes.
-Honest feedback, however, may be painful to learn if it falls short of
-one's expectations. As prior work notes, this may motivate people to
-avoid information and avoid seeking help [@Benabou2022; @Golman2017;
-@Jaroszewicz2022]. We present evidence from two experiments that
-advisers are also cognizant of this cost. As a result, they present
-flattering advice that avoids disappointing the recipient, and correctly
-anticipate that this boosts how advisees perceive them. However, this
-flattering advice comes at a cost to advisees, who would do worse if
-they followed it blindly, as we show in Study 1.
-
-Moreover, a desire to avoid disappointment also means that advisers have
-to take into account the expectations of the advisee. We document that
-men are more optimistic about their performance than women are. As a
-result, they receive more flattering advice and are more likely to be
-told to aim higher. Notably, in the context of our experiment, this
-turns out to be bad advice ex post.
-
-Our findings have implications for organizational practice, where
-mentoring and advice-giving may take into account an employees'
-expectation. We document this as a novel source of gender bias.
-Organizations could reduce this bias by calibrating employees'
-expectations to reduce overconfidence.
-
-Participants in our experiment were paired anonymously. Even so, we
-document this desire to avoid disappointment. We anticipate that advice
-would be more flattering in face-to-face communication and without
-anonymity. Moreover, existing relationships might make it even more
-difficult for advisers to be honest.
-
-In our experiments, participants only received advice once and did not
-evaluate the adviser after observing the outcome of their decision. For
-example, advice that leads to bad outcomes may undermine the
-interpersonal benefits of flattery. Alternatively, people may still like
-the flattering advice and not fault the adviser for the bad outcome.
-Moreover, our setting involved only a single piece of advice on one
-task. Future research could examine whether people return to those who
-gave them flattering advice, or if they prefer someone who gave them the
-honest (but unpleasant) truth.
+Honest feedback, however, may be painful to learn if it falls short of one's expectations.
+As prior work notes, this may motivate people to avoid information and avoid seeking help [@Benabou2022; @Golman2017; @Jaroszewicz2022].
+We present evidence from two experiments that advisers are also cognizant of this cost.
+As a result, they present flattering advice that avoids disappointing the recipient, and correctly anticipate that this boosts how advisees perceive them.
+However, this flattering advice comes at a cost to advisees, who would do worse if they followed it blindly, as we show in Study 1.
+
+Moreover, a desire to avoid disappointment also means that advisers have to take into account the expectations of the advisee.
+We document that men are more optimistic about their performance than women are.
+As a result, they receive more flattering advice and are more likely to be told to aim higher.
+Notably, in the context of our experiment, this turns out to be bad advice ex post.
+
+Our findings have implications for organizational practice, where mentoring and advice-giving may take into account an employees' expectation.
+We document this as a novel source of gender bias.
+Organizations could reduce this bias by calibrating employees' expectations to reduce overconfidence.
+
+Participants in our experiment were paired anonymously.
+Even so, we document this desire to avoid disappointment.
+We anticipate that advice would be more flattering in face-to-face communication and without anonymity.
+Moreover, existing relationships might make it even more difficult for advisers to be honest.
+
+In our experiments, participants only received advice once and did not evaluate the adviser after observing the outcome of their decision.
+For example, advice that leads to bad outcomes may undermine the interpersonal benefits of flattery.
+Alternatively, people may still like the flattering advice and not fault the adviser for the bad outcome.
+Moreover, our setting involved only a single piece of advice on one task.
+Future research could examine whether people return to those who gave them flattering advice, or if they prefer someone who gave them the honest (but unpleasant) truth.
 
 Advice has long been studied from the perspective of the receiver.
-Similarly, research on belief utility has examined how recipients
-respond to the valence of the information they receive. Here, we show
-that advisers, too, take into account the psychological impact of the
-information they convey. They may have even greater motivations to avoid
-conveying bad news, because they incur the interpersonal costs of
-delivering unfavorable information without reaping the benefits from
-helping someone make a better choice.
+Similarly, research on belief utility has examined how recipients respond to the valence of the information they receive.
+Here, we show that advisers, too, take into account the psychological impact of the information they convey.
+They may have even greater motivations to avoid conveying bad news, because they incur the interpersonal costs of delivering unfavorable information without reaping the benefits from helping someone make a better choice.
 
 # References
-
-\begingroup
-\singlespacing
-\setlength{\parindent}{-0.2in}
-\setlength{\leftskip}{0.2in}
-
-\noindent
 
@@
 :::
-
-\endgroup

### 2025-01-09 manuscript/manuscript.tex
Conversion to Quarto file

--- 2025-01-09 manuscript/manuscript.qmd
@@
----
-title: "Flattering Advice: Avoiding Disappointment in Advice-Giving"
-shorttitle: "Flattering Advice"
-date: yes
-author: 
-  - name: "Amanda Chen"
-    corresponding: true
-    orcid: 0000-0002-4428-627X
-    email: zchengj@connect.ust.hk
-    affiliations:
-      - id: id1
-        name: "The Hong Kong University of Science and Technology"
-        department: "Department of Management"
-        city: "Hong Kong"
-  - name: "David Hagmann"
-    orcid: 0000-0002-2080-997X
-    affiliations:
-    - id: id1
-author-note:
-  disclosures:
-    gratitude: The authors are grateful to XXX for their helpful comments.
-abstract: Good advice improves decision quality but often requires delivering unpleasant truths that may disappoint advisees.
-Across three pre-registered and incentivized experiments involving real adviser-advisee interactions (N = 3,900), we show that advisers prioritize avoiding disappointment at the expense of accuracy and their own earnings.
-In Study 1, advisers financially rewarded for accuracy still tailor recommendations to aspirational goals expressed by advisees, resulting in worse advice.
-When incentivized to be liked, advisers provide even more flattering advice, and advisees reward this by rating these advisers as more likable, despite the advice being less honest and less accurate (Study 2).
-The desire to avoid disappointment may lead to inequities if there are differences in expectations across social groups.
-In Study 3, we examine a setting in which men expect to perform better than women.
-We show that advisers take into account these expectations, leading to systematically different advice for men and women even when their gender is unknown to advisers.
-Advisers' efforts to avoid disappointment may thus contribute to systematic gender disparities in advice, with implications for downstream decision-making.
-
-keywords: [Gender difference, Advice, Interpresonal relationship]
-bibliography: bibliography.bib
-floatsintext: true
-mask: false
-link-citations: false
-format:
-  apaquarto-html: default
-  apaquarto-pdf:
-    documentmode: man
-    keep-tex: true
-    prefer-html: true
-  apaquarto-docx:
-    default: true
-    prefer-html: true
----
-
-```{r}
-#| label: setup
-#| include: false
-
-library(magrittr)
-library(ltm)
-library(ggplot2)
-library(gridExtra)
-library(dplyr)
-
-knitr::opts_chunk$set(fig.width = 8, fig.height = 4, cache = F, echo = F,
-                      fig.align = 'center',warning = FALSE, message = FALSE)
-
-study1_time1 <- readRDS(here::here("Data/Study1_time1.Rds"))
-study1_ability50 <- read.csv(here::here("Data/Cleaned Data/S1_Ability50_clean.csv"))
-study1_time2_giver <- readRDS(here::here("Data/Study1_time2_giver.Rds"))
-study1_time2_advice <- readRDS(here::here("Data/Study1_time2_advice.Rds"))
-study1_time3 <- readRDS(here::here("Data/Study1_time3.Rds"))
-
-```
-
-# Introduction
-
-Career trajectories for men and women often differ substantially, even among those with similar qualifications.
-One source of such differences may be the advice that people receive.
-Prior work has documented that men receive more aspirational advice and women more risk-averse advice, which may explain why women are less likely to apply for and ultimately obtain more rewarding positions (Kanze et al., 2018).
-Research on gender discrimination has focused on the role of unconscious bias (Greenwald et al., 2009; Greenwald & Banaji, 1995), but interventions that try to reduce this bias have been largely unsuccessful (Chang et al., 2019; Paluck & Green, 2009).
-Recent work has proposed cognitive, rather than unconscious, biases that can lead to gender discrimination through the formation of false beliefs (Hagmann et al., 2024).
-Here, we propose a novel source of differences in advice by drawing on recent work on belief-based utility, expectation-based reference points (Köszegi, 2006; Kőszegi & Rabin, 2009), and the hedonic consequences of information (Golman et al., 2017).
-
-Advice figures prominently in workplace and personal decision-making, shaping choices about promotions, career paths, and everyday dilemmas [@Gino2007; @Harvey1997; @Soll2009].
-Its fundamental premise is to improve outcomes by enabling decision-makers to learn from others' expertise.
-However, while honest advice can lead to better decisions, it can also lead to disappointment when it suggests a desired outcome is unlikely to materialize.
-Advisers may be motivated to offer flattering recommendations that align with advisees' hopes, sparing them the disappointment of a more sobering forecast.
-
-Advice with the potential for disappointment appears in diverse organizational settings: supervisors deliver feedback on employee performance, lawyers convey likely outcomes of litigation to their clients, and academics offer thoughts on colleagues' manuscripts.
-Ideally, honest information would help people identify their strengths and weaknesses, make informed decisions about whether to pursue legal cases, and strengthen papers prior to submission to academic journals, thus improving long-term outcomes.
-In practice, however, interpersonal considerations may prevent candor.
-When someone's expectations are (too) high, an adviser might hesitate to deliver information that undermines it---particularly if doing so risks negative interpersonal repercussions.
-
-People often go to great lengths to avoid unpleasant information, deriving belief-based utility from maintaining favorable views of themselves [@Golman2017; @Ho2018; @Loewenstein2018].
-Moreover, they often prefer advisers who withhold bad news from them [@Shalvi2019] and punish those who communicate bad news [@John2019].
-Advisers, anticipating these preferences and consequences face a dilemma: Should they provide the accurate but potentially painful truth, or shade their recommendations to preserve the advisee's mood and the adviser's own standing?
-Advisers who fear they will be blamed or disliked for undermining someone's confidence may reasonably avoid candid feedback, particularly if they don't incur a cost when the advisee makes a mistake.
-
-In our experiments, however, advisees have no opportunity to punish the adviser, and advisers' financial incentives are linked to the decisions the advisees make.
-We propose that advisers nonetheless have reason to provide flattering advise because they recognize the psychological toll of disappointing news.
-As a result, they may similarly incur a hedonic cost for delivering unpleasant information that they anticipate may distress the advisee.
-Thus, even in the anonymized context of an online experiment, we hypothesize (and find) that advisers are relucant to disappoint advisees and advice is thus biased upward, away from accuracy and toward confirming advisees' priors.
-We show that this reduces the quality of advice—but that advisees nonetheless view flattering advisers more favorably.
-
-We present the results of three preregistered experiments in which participants are paired anonymously as advisers and advisees.
-Advisers are incentivized to offer accurate advice, with bonus earnings depending on the outcome of an advisee's decision.
-We study a setting in which advisees can communicate their expectations to an adviser, and experimentally manipulate whether advisers observe this expectation.
-Our design simulates organizational contexts where mentors and managers often have some sense of an employee's confidence or aspirations and thus could adjust their feedback to avoid disappointing them.
-Interpersonal considerations would likely be stronger in situations in which the adviser and advisee have an existing relationship and when the advice is delivered face-to-face.
-Moreover, advisers usually do not suffer any direct costs when their flattering advice leads to a poor outcome for the recipient, particularly when it is not clear what would have happened under a counterfactual.\^\[In some cases, however, repeated interaction might also increase incentives for honest feedback.
-Someone who is known to persistently give overoptimistic advice may be viewed as less trustworthy in the long run.\]
-
-In Study 1, we nudge advisees into a preference for competing against either a group of top-performers or a group of low-performers, through the use of a default option.
-Advisers who observe the actual performance of advisees and therefore have the relevant information needed to make a recommendation nonetheless take into account the initial preference when recommending which group they should compete against.
-In Study 2, we ask advisees to upload photos of themselves and advisers rank them on their attractiveness.
-Advisers then recommend which rank the advisee should bet on, receiving an incentive either for the advisee's accuracy or for being evaluated favorably.
-Both groups of advisers recommend a rank that is more attractive than what they themselves have evaluated the advisee, and those incentivized for likability further inflate the ranking.
-Advisees evaluate advisers more favorably when they recommend betting on a more attractive rank, including viewing them as more trustworthy.
-
-In Study 3, we examine a setting in which participants report their expected performance on a mathematics quiz.
-Advisers observe the test-taker's true score and, in one treatment, the score they guessed they would receive.
-They then recommend whether the advisee should compete against a group of high performers or low performers.
-Importantly, this "competition" is based on the past performance observed by the adviser and thus the advisee's expectation does not provide instrumental information.
-However, we find that (1) men expect to perform better than women, given identical performance, and (2) advisers take these expectations into account.
-As a result, when expectations (but not gender) are known to advisers, the advice given to men and women differs, and men are more often advised to compete against the group of high performers.
-Notably, this leads to worse advice for men than for women.
-
-# Open Science Statement
-
-We report all manipulations, measures, and data exclusion in our experiments.
-The preregistration reports, screenshots of all experimental materials, and the analysis code to replicate all statistical analyses and figures are available on the Open Science Framework (<https://osf.io/8r3d4/?view_only=5ad7bafcd16b4d4ba08bb28b0e2bd02d>).
-
-# Study 1
-
-We first examine whether advisers take into account the expectations of advisees when providing a recommendation.
-A group of participants ("Advisees") complete a quiz consisting of ten questions that draw on ego-relevant domains.
-They then express a non-binding preference to compete against a group of high performers or low performers on the same task, based on their past performance.
-We nudge participants towards picking either the low or the high performer group by selecting one of the two by default.
-A second group of participants ("Advisers") observe Advisees' score on the quiz and, in one treatment, also which group they had selected.
-We predicted that Advisees who were nudged toward the high performer group would be more likely to receive advice to compete against this high group when Advisers observed their non-binding choice.
-
-## Methods
-
-In a preliminary stage, we recruited `r scales::comma(dim(study1_ability50)[1])` participants from Prolific and gave them five minutes to complete a quiz consisting of ten items.
-The quiz included word puzzles, identifying emotions from photos, and selecting the best responses for hypothetical scenarios.
-These questions were adapted from surveys that measure problem-solving, emotional intelligence, and communication skills---which we pre-tested as being important in modern society and hence where participants might have a stake in doing well.
-Participants received a bonus of five cents for each correctly answered question.
-We then ranked them based on their score and label the 20 participants with the lowest (highest) scores as the Low (High) Performer Group.
-
-Next, we recruited `r scales::comma(dim(study1_time1)[1])` participants for the role of Advisees.
-They completed the same 10-item quiz, also earning five cents for each correct answer.
-We then asked them to express a non-binding preference for whether they would like to compete against the High or Low Performer Group.
-We informed them that they would be invited back at a later date when they could make a binding decision and they could earn a bonus based on whether their score on this quiz was equal to or higher than a randomly selected member from their comparison group.
-If they picked the High Performer Group and had an equal or higher score than a randomly selected member of that group, they would earn a bonus of 50 cents.
-If they picked the Low Performer Group and outperformed a randomly selected member of that group, they could earn a bonus of 20 cents.
-If their score was lower in this comparison, they would not earn an additional bonus.
-We randomized which of the two groups (High or Low Performers) was selected by default, and Advisees were free to select the other group.
-They also made a guess as to their score, and the survey concluded with basic demographic questions.
-
-We then recruited `r scales::comma(dim(study1_time2_giver)[1])` participants for the role of Advisers, and the focal part of our experiment.
-They were informed of the ability quiz that the Advisees had completed, how the Low Performer Group and High Performer Groups were constructed, as well as the choice and incentives for the Advisees.
-We then asked Advisers to give advice to ten participants on which group they should compete against.
-Advisers were randomly assigned to one of two treatments.
-In the "Performance" treatment, they observed only the score of the other participant.
-In the "Performance + Expectation" treatment, they additionally observed the advisee's non-binding choice of which group to compete against.
-However, since the outcome was based solely on the past quiz score and advisers, but not advisees, know the score, this initial choice was not informative for the purpose of recommending competing against one group or the other.
-Advisers could earn the same bonus as one of the participants they had given advice to and who returned to make a decision.
-The survey concluded with basic demographic questions.
-
-Finally, we invited Advisees back for the follow-up survey.
-Following our preregistration, we kept the survey open for 7 days.
-In total, `r scales::comma(dim(study1_time3)[1])` Advisees returned.
-The short survey reminded them of the task they completed in the previous survey, informed them that other participants from Prolific had observed their real score and given them advice on which group to compete against, and finally reminded them of how many questions they guessed they had answered correctly.
-They were not informed of their true score or the score of the groups they could compete against.
-Participants then observed the advice from a randomly selected adviser and made their decision.
-
-## Results
-
-```{r}
-contingency_table <- table(study1_time1$Guess, study1_time1$default)
-
-chi_test <- chisq.test(contingency_table)
-
-```
+\documentclass[
+  man,
+  floatsintext,
+  longtable,
+  nolmodern,
+  notxfonts,
+  notimes,
+  colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{apa7}
+
+\usepackage{amsmath}
+\usepackage{amssymb}
+
+\RequirePackage{longtable}
+\RequirePackage{threeparttablex}
+
+\makeatletter
+\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+	{0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+	{-.5em}%
+	{\normalfont\normalsize\bfseries\typesectitle}}
+
+\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{0.5em}%
+	{0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+	{-\z@\relax}%
+	{\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+\makeatother
+
+\usepackage{longtable, booktabs, multirow, multicol, colortbl, hhline, caption, array, float, xpatch}
+\setcounter{topnumber}{2}
+\setcounter{bottomnumber}{2}
+\setcounter{totalnumber}{4}
+\renewcommand{\topfraction}{0.85}
+\renewcommand{\bottomfraction}{0.85}
+\renewcommand{\textfraction}{0.15}
+\renewcommand{\floatpagefraction}{0.7}
+
+\usepackage{tcolorbox}
+\tcbuselibrary{listings,theorems, breakable, skins}
+\usepackage{fontawesome5}
+
+\definecolor{quarto-callout-color}{HTML}{909090}
+\definecolor{quarto-callout-note-color}{HTML}{0758E5}
+\definecolor{quarto-callout-important-color}{HTML}{CC1914}
+\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
+\definecolor{quarto-callout-tip-color}{HTML}{00A047}
+\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
+\definecolor{quarto-callout-color-frame}{HTML}{ACACAC}
+\definecolor{quarto-callout-note-color-frame}{HTML}{4582EC}
+\definecolor{quarto-callout-important-color-frame}{HTML}{D9534F}
+\definecolor{quarto-callout-warning-color-frame}{HTML}{F0AD4E}
+\definecolor{quarto-callout-tip-color-frame}{HTML}{02B875}
+\definecolor{quarto-callout-caution-color-frame}{HTML}{FD7E14}
+
+%\newlength\Oldarrayrulewidth
+%\newlength\Oldtabcolsep
+
+\usepackage{hyperref}
+
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\usepackage{longtable,booktabs,array}
+\usepackage{calc} % for calculating minipage widths
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
+
+\usepackage{graphicx}
+\makeatletter
+\newsavebox\pandoc@box
+\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
+  \sbox\pandoc@box{#1}%
+  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
+  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
+  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
+  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
+  \else\usebox{\pandoc@box}%
+  \fi%
+}
+% Set default figure placement to htbp
+\def\fps@figure{htbp}
+\makeatother
+
+% definitions for citeproc citations
+\NewDocumentCommand\citeproctext{}{}
+\NewDocumentCommand\citeproc{mm}{%
+  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
+\makeatletter
+ % allow citations to break across lines
+ \let\@cite@ofmt\@firstofone
+ % avoid brackets around text for \cite:
+ \def\@biblabel#1{}
+ \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
+\makeatother
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
+ {\begin{list}{}{%
+  \setlength{\itemindent}{0pt}
+  \setlength{\leftmargin}{0pt}
+  \setlength{\parsep}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+   \setlength{\leftmargin}{\cslhangindent}
+   \setlength{\itemindent}{-1\cslhangindent}
+  \fi
+  % set entry spacing
+  \setlength{\itemsep}{#2\baselineskip}}}
+ {\end{list}}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+
+\usepackage{newtx}
+
+\defaultfontfeatures{Scale=MatchLowercase}
+\defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+
+\title{Flattering Advice: Avoiding Disappointment in Advice-Giving}
+
+\shorttitle{Flattering Advice}
+
+\usepackage{etoolbox}
+
+\authorsnames{Amanda Chen,David Hagmann}
+
+\authorsaffiliations{
+{Department of Management, The Hong Kong University of Science and
+Technology},{}}
+
+\leftheader{Chen and Hagmann}
+
+\date{Invalid Date}
+
+\abstract{Good advice improves decision quality but often requires
+delivering unpleasant truths that may disappoint advisees. Across three
+pre-registered and incentivized experiments involving real
+adviser-advisee interactions (N = 3,900), we show that advisers
+prioritize avoiding disappointment at the expense of accuracy and their
+own earnings. In Study 1, advisers financially rewarded for accuracy
+still tailor recommendations to aspirational goals expressed by
+advisees, resulting in worse advice. When incentivized to be liked,
+advisers provide even more flattering advice, and advisees reward this
+by rating these advisers as more likable, despite the advice being less
+honest and less accurate (Study 2). The desire to avoid disappointment
+may lead to inequities if there are differences in expectations across
+social groups. In Study 3, we examine a setting in which men expect to
+perform better than women. We show that advisers take into account these
+expectations, leading to systematically different advice for men and
+women even when their gender is unknown to advisers. Advisers' efforts
+to avoid disappointment may thus contribute to systematic gender
+disparities in advice, with implications for downstream
+decision-making.}
+
+\keywords{Gender difference, Advice, Interpresonal relationship}
+
+\authornote{\par{\addORCIDlink{Amanda
+Chen}{0000-0002-4428-627X}}\par{\addORCIDlink{David
+Hagmann}{0000-0002-2080-997X}}
+
+\par{     The authors are grateful to XXX for their helpful comments.  }
+\par{Correspondence concerning this article should be addressed
+to Amanda Chen, Email: zchengj@connect.ust.hk}
+}
+
+\makeatletter
+\let\endoldlt\endlongtable
+\def\endlongtable{
+\hline
+\endoldlt
+}
+\makeatother
+
+\urlstyle{same}
+
+\usepackage{float}
+\usepackage{tabularray}
+\usepackage[normalem]{ulem}
+\usepackage{graphicx}
+\UseTblrLibrary{booktabs}
+\UseTblrLibrary{rotating}
+\UseTblrLibrary{siunitx}
+\NewTableCommand{\tinytableDefineColor}[3]{\definecolor{#1}{#2}{#3}}
+\newcommand{\tinytableTabularrayUnderline}[1]{\underline{#1}}
+\newcommand{\tinytableTabularrayStrikeout}[1]{\sout{#1}}
+\makeatletter
+\@ifpackageloaded{caption}{}{\usepackage{caption}}
+\AtBeginDocument{%
+\ifdefined\contentsname
+  \renewcommand*\contentsname{Table of contents}
+\else
+  \newcommand\contentsname{Table of contents}
+\fi
+\ifdefined\listfigurename
+  \renewcommand*\listfigurename{List of Figures}
+\else
+  \newcommand\listfigurename{List of Figures}
+\fi
+\ifdefined\listtablename
+  \renewcommand*\listtablename{List of Tables}
+\else
+  \newcommand\listtablename{List of Tables}
+\fi
+\ifdefined\figurename
+  \renewcommand*\figurename{Figure}
+\else
+  \newcommand\figurename{Figure}
+\fi
+\ifdefined\tablename
+  \renewcommand*\tablename{Table}
+\else
+  \newcommand\tablename{Table}
+\fi
+}
+\@ifpackageloaded{float}{}{\usepackage{float}}
+\floatstyle{ruled}
+\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
+\floatname{codelisting}{Listing}
+\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
+\makeatother
+\makeatletter
+\makeatother
+\makeatletter
+\@ifpackageloaded{caption}{}{\usepackage{caption}}
+\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
+\makeatother
+
+% From https://tex.stackexchange.com/a/645996/211326
+%%% apa7 doesn't want to add appendix section titles in the toc
+%%% let's make it do it
+\makeatletter
+\xpatchcmd{\appendix}
+  {\par}
+  {\addcontentsline{toc}{section}{\@currentlabelname}\par}
+  {}{}
+\makeatother
+
+%% Disable longtable counter
+%% https://tex.stackexchange.com/a/248395/211326
+
+\usepackage{etoolbox}
+
+\makeatletter
+\patchcmd{\LT@caption}
+  {\bgroup}
+  {\bgroup\global\LTpatch@captiontrue}
+  {}{}
+\patchcmd{\longtable}
+  {\par}
+  {\par\global\LTpatch@captionfalse}
+  {}{}
+\apptocmd{\endlongtable}
+  {\ifLTpatch@caption\else\addtocounter{table}{-1}\fi}
+  {}{}
+\newif\ifLTpatch@caption
+\makeatother
+
+\begin{document}
+
+\maketitle
+
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+
+\setlength\LTleft{0pt}
+
+\section{Introduction}\label{introduction}
+
+Career trajectories for men and women often differ substantially, even
+among those with similar qualifications. One source of such differences
+may be the advice that people receive. Prior work has documented that
+men receive more aspirational advice and women more risk-averse advice,
+which may explain why women are less likely to apply for and ultimately
+obtain more rewarding positions (Kanze et al., 2018). Research on gender
+discrimination has focused on the role of unconscious bias (Greenwald et
+al., 2009; Greenwald \& Banaji, 1995), but interventions that try to
+reduce this bias have been largely unsuccessful (Chang et al., 2019;
+Paluck \& Green, 2009). Recent work has proposed cognitive, rather than
+unconscious, biases that can lead to gender discrimination through the
+formation of false beliefs (Hagmann et al., 2024). Here, we propose a
+novel source of differences in advice by drawing on recent work on
+belief-based utility, expectation-based reference points (Köszegi, 2006;
+Kőszegi \& Rabin, 2009), and the hedonic consequences of information
+(Golman et al., 2017).
+
+Advice figures prominently in workplace and personal decision-making,
+shaping choices about promotions, career paths, and everyday dilemmas
+(Gino \& Moore, 2007; Harvey \& Fischer, 1997; Soll \& Larrick, 2009).
+Its fundamental premise is to improve outcomes by enabling
+decision-makers to learn from others' expertise. However, while honest
+advice can lead to better decisions, it can also lead to disappointment
+when it suggests a desired outcome is unlikely to materialize. Advisers
+may be motivated to offer flattering recommendations that align with
+advisees' hopes, sparing them the disappointment of a more sobering
+forecast.
+
+Advice with the potential for disappointment appears in diverse
+organizational settings: supervisors deliver feedback on employee
+performance, lawyers convey likely outcomes of litigation to their
+clients, and academics offer thoughts on colleagues' manuscripts.
+Ideally, honest information would help people identify their strengths
+and weaknesses, make informed decisions about whether to pursue legal
+cases, and strengthen papers prior to submission to academic journals,
+thus improving long-term outcomes. In practice, however, interpersonal
+considerations may prevent candor. When someone's expectations are (too)
+high, an adviser might hesitate to deliver information that undermines
+it---particularly if doing so risks negative interpersonal
+repercussions.
+
+People often go to great lengths to avoid unpleasant information,
+deriving belief-based utility from maintaining favorable views of
+themselves (Golman et al., 2017; Loewenstein \& Molnar, 2018;
+\textbf{Ho2018?}). Moreover, they often prefer advisers who withhold bad
+news from them (Shalvi et al., 2019) and punish those who communicate
+bad news (John et al., 2019). Advisers, anticipating these preferences
+and consequences face a dilemma: Should they provide the accurate but
+potentially painful truth, or shade their recommendations to preserve
+the advisee's mood and the adviser's own standing? Advisers who fear
+they will be blamed or disliked for undermining someone's confidence may
+reasonably avoid candid feedback, particularly if they don't incur a
+cost when the advisee makes a mistake.
+
+In our experiments, however, advisees have no opportunity to punish the
+adviser, and advisers' financial incentives are linked to the decisions
+the advisees make. We propose that advisers nonetheless have reason to
+provide flattering advise because they recognize the psychological toll
+of disappointing news. As a result, they may similarly incur a hedonic
+cost for delivering unpleasant information that they anticipate may
+distress the advisee. Thus, even in the anonymized context of an online
+experiment, we hypothesize (and find) that advisers are relucant to
+disappoint advisees and advice is thus biased upward, away from accuracy
+and toward confirming advisees' priors. We show that this reduces the
+quality of advice---but that advisees nonetheless view flattering
+advisers more favorably.
+
+We present the results of three preregistered experiments in which
+participants are paired anonymously as advisers and advisees. Advisers
+are incentivized to offer accurate advice, with bonus earnings depending
+on the outcome of an advisee's decision. We study a setting in which
+advisees can communicate their expectations to an adviser, and
+experimentally manipulate whether advisers observe this expectation. Our
+design simulates organizational contexts where mentors and managers
+often have some sense of an employee's confidence or aspirations and
+thus could adjust their feedback to avoid disappointing them.
+Interpersonal considerations would likely be stronger in situations in
+which the adviser and advisee have an existing relationship and when the
+advice is delivered face-to-face. Moreover, advisers usually do not
+suffer any direct costs when their flattering advice leads to a poor
+outcome for the recipient, particularly when it is not clear what would
+have happened under a counterfactual.\^{}{[}In some cases, however,
+repeated interaction might also increase incentives for honest feedback.
+Someone who is known to persistently give overoptimistic advice may be
+viewed as less trustworthy in the long run.{]}
+
+In Study 1, we nudge advisees into a preference for competing against
+either a group of top-performers or a group of low-performers, through
+the use of a default option. Advisers who observe the actual performance
+of advisees and therefore have the relevant information needed to make a
+recommendation nonetheless take into account the initial preference when
+recommending which group they should compete against. In Study 2, we ask
+advisees to upload photos of themselves and advisers rank them on their
+attractiveness. Advisers then recommend which rank the advisee should
+bet on, receiving an incentive either for the advisee's accuracy or for
+being evaluated favorably. Both groups of advisers recommend a rank that
+is more attractive than what they themselves have evaluated the advisee,
+and those incentivized for likability further inflate the ranking.
+Advisees evaluate advisers more favorably when they recommend betting on
+a more attractive rank, including viewing them as more trustworthy.
+
+In Study 3, we examine a setting in which participants report their
+expected performance on a mathematics quiz. Advisers observe the
+test-taker's true score and, in one treatment, the score they guessed
+they would receive. They then recommend whether the advisee should
+compete against a group of high performers or low performers.
+Importantly, this ``competition'' is based on the past performance
+observed by the adviser and thus the advisee's expectation does not
+provide instrumental information. However, we find that (1) men expect
+to perform better than women, given identical performance, and (2)
+advisers take these expectations into account. As a result, when
+expectations (but not gender) are known to advisers, the advice given to
+men and women differs, and men are more often advised to compete against
+the group of high performers. Notably, this leads to worse advice for
+men than for women.
+
+\section{Open Science Statement}\label{open-science-statement}
+
+We report all manipulations, measures, and data exclusion in our
+experiments. The preregistration reports, screenshots of all
+experimental materials, and the analysis code to replicate all
+statistical analyses and figures are available on the Open Science
+Framework
+(\url{https://osf.io/8r3d4/?view_only=5ad7bafcd16b4d4ba08bb28b0e2bd02d}).
+
+\section{Study 1}\label{study-1}
+
+We first examine whether advisers take into account the expectations of
+advisees when providing a recommendation. A group of participants
+(``Advisees'') complete a quiz consisting of ten questions that draw on
+ego-relevant domains. They then express a non-binding preference to
+compete against a group of high performers or low performers on the same
+task, based on their past performance. We nudge participants towards
+picking either the low or the high performer group by selecting one of
+the two by default. A second group of participants (``Advisers'')
+observe Advisees' score on the quiz and, in one treatment, also which
+group they had selected. We predicted that Advisees who were nudged
+toward the high performer group would be more likely to receive advice
+to compete against this high group when Advisers observed their
+non-binding choice.
+
+\subsection{Methods}\label{methods}
+
+In a preliminary stage, we recruited 50 participants from Prolific and
+gave them five minutes to complete a quiz consisting of ten items. The
+quiz included word puzzles, identifying emotions from photos, and
+selecting the best responses for hypothetical scenarios. These questions
+were adapted from surveys that measure problem-solving, emotional
+intelligence, and communication skills---which we pre-tested as being
+important in modern society and hence where participants might have a
+stake in doing well. Participants received a bonus of five cents for
+each correctly answered question. We then ranked them based on their
+score and label the 20 participants with the lowest (highest) scores as
+the Low (High) Performer Group.
+
+Next, we recruited 201 participants for the role of Advisees. They
+completed the same 10-item quiz, also earning five cents for each
+correct answer. We then asked them to express a non-binding preference
+for whether they would like to compete against the High or Low Performer
+Group. We informed them that they would be invited back at a later date
+when they could make a binding decision and they could earn a bonus
+based on whether their score on this quiz was equal to or higher than a
+randomly selected member from their comparison group. If they picked the
+High Performer Group and had an equal or higher score than a randomly
+selected member of that group, they would earn a bonus of 50 cents. If
+they picked the Low Performer Group and outperformed a randomly selected
+member of that group, they could earn a bonus of 20 cents. If their
+score was lower in this comparison, they would not earn an additional
+bonus. We randomized which of the two groups (High or Low Performers)
+was selected by default, and Advisees were free to select the other
+group. They also made a guess as to their score, and the survey
+concluded with basic demographic questions.
+
+We then recruited 1,000 participants for the role of Advisers, and the
+focal part of our experiment. They were informed of the ability quiz
+that the Advisees had completed, how the Low Performer Group and High
+Performer Groups were constructed, as well as the choice and incentives
+for the Advisees. We then asked Advisers to give advice to ten
+participants on which group they should compete against. Advisers were
+randomly assigned to one of two treatments. In the ``Performance''
+treatment, they observed only the score of the other participant. In the
+``Performance + Expectation'' treatment, they additionally observed the
+advisee's non-binding choice of which group to compete against. However,
+since the outcome was based solely on the past quiz score and advisers,
+but not advisees, know the score, this initial choice was not
+informative for the purpose of recommending competing against one group
+or the other. Advisers could earn the same bonus as one of the
+participants they had given advice to and who returned to make a
+decision. The survey concluded with basic demographic questions.
+
+Finally, we invited Advisees back for the follow-up survey. Following
+our preregistration, we kept the survey open for 7 days. In total, 176
+Advisees returned. The short survey reminded them of the task they
+completed in the previous survey, informed them that other participants
+from Prolific had observed their real score and given them advice on
+which group to compete against, and finally reminded them of how many
+questions they guessed they had answered correctly. They were not
+informed of their true score or the score of the groups they could
+compete against. Participants then observed the advice from a randomly
+selected adviser and made their decision.
+
+\subsection{Results}\label{results}
 
 We begin by examining the performance of the Stage 1 participants.
-Because our default treatment takes place after participants completed the ability quiz, we do not expect a difference in performance across the Low and High Default treatments.
-Indeed, the two groups scored no different from one another (`r round(mean(study1_time1[study1_time1$default == "Low",]$Score),2)` and `r round(mean(study1_time1[study1_time1$default == "High",]$Score),2)` for the Low Default and High Default treatments, respectively, `r papaja::apa_print(t.test(Score ~ default, data = study1_time1, var.equal = T))$statistic`).
-The default manipulation affected their initial choices.
-In the "Low Default" treatment, only `r round(mean(study1_time1[study1_time1$default == "Low",]$Guess),2)*100`% of participants initially preferred competing against the High Performer Group, compared to `r round(mean(study1_time1[study1_time1$default == "High",]$Guess),2)*100`% of participants who saw the High Performer Group highlighted ($\chi^2$(1, n = 201) = 36.62, p \< .001).
-
-```{r}
-#| label: tbl-study1regs
-#| tbl-cap: "Advice to compete against the High Performer Group in Study 1.
-Displaying the non-binding choice of those for whom the Low Performer Group was selected by default makes it more likely that they are advised to compete against the High Performer Group (Column 1).
-Column 2 restricts the analysis to advisers who observed advisees' initial non-binding choice and controls for advisees' score on the quiz.
-Standard errors are clustered at the adviser level."
-
-study1_advice <- study1_time2_advice %>%
-  dplyr::mutate(Treatment = factor(Treatment, levels = c('Low', 'High'))) %>%
-  dplyr::mutate(ExpShow = ifelse(Condition == 'E', 1, 0))
-
-modelsummary::modelsummary(
-  list(`(1)` = lm(Advice ~ ExpShow * Treatment, data = study1_advice), 
-       `(2)` = lm(Advice ~ Treatment + Score, data = study1_advice %>% dplyr::filter(ExpShow == 1))),
-  vcov = ~GiverID,
-  coef_map = c(
-    "TreatmentHigh" = "High Default",
-    "ExpShow" = "Expectation Shown",
-    "ExpShow:TreatmentHigh" = "Expectation x High Default",
-    "Score" = "Performance",
-    "(Intercept)" = "Constant"
-  ),
-  stars = TRUE,
-  gof_map = list(list('raw' = 'nobs', 'clean' = 'N', 'fmt' = 0))
-)
-
-```
-
-We now examine whether advisers took the advisees' expectations into account.
-Recall that advisees who were defaulted to competing against the High Performer Group were indeed more likely to choose this group, which, from the advisers' perspective, could signal high confidence in their abilities.
-Our theory predicts that showing expectations should lead to more flattering advice--- specifically, a recommendation to compete against the High Performer Group--- for advisees with a high default choice compared to those with a low default choice.
-Column 1 of @tbl-study1regs reports a linear probability model with advice to compete against the high group as the outcome measure, incorporating the default choice advisees saw, whether expectations were shown to the adviser, and the interaction of the two.
-Because each adviser made ten recommendations, we cluster standard errors at the adviser level.
-As predicted, we find a marginally significant interaction effect: advisees with a default choice to compete against the High Performer Group (nudged to have high expectations, though not necessarily holding them) were more likely to receive advice to compete against stronger competitors when their expectations were shown compared to when they were hidden.
-We reported a linear probability model on advising to compete against the High Performer group for advisers in the "Expectations" treatment, controlling for the true performance of the advisee in Column 2 of @tbl-study1regs.
-We observe a significant main effect of the default treatment, where a high default increased the likelihood of receiving flattering advice.
-It is worth noting that, since only `r round(mean(study1_time1[study1_time1$default == "High",]$Guess),2)*100` % of advisees in the high default group actually stuck with their default choice, this represents a conservative test of the effect of high expectations on the likelihood of receiving flattering advice.
-
-```{r}
-#| label: fig-study1Advice
-#| fig-cap: "Advisees who were nudged to express high expectations were more likely to receive advice to compete against the High Performer Group."
-
-study1_time2_advice %>%
-  mutate(Treatment=factor(Treatment, levels=c('High','Low'), labels = c('High default', 'Low default'))) %>%
-  group_by(Condition, Treatment) %>%
-  summarize(avg_count = mean(Advice), ci = qnorm(0.975)*sd(Advice)/sqrt(dplyr::n())) %>%
-  ggplot2::ggplot(ggplot2::aes(x = Condition, y = avg_count, fill = Treatment)) +
-  ggplot2::geom_col(position = 'dodge') +
-  ggplot2::geom_errorbar(ggplot2::aes(ymin = avg_count - ci, ymax = avg_count + ci), 
-                         position = ggplot2::position_dodge(0.9), linewidth = 0.2, width = 0.1) +
-  ggtitle("Advice: Meeting Expectations vs. Absent Expectations") +
-  scale_fill_manual(values = c("#2A629A",'#FF7F3E')) +
-  theme_bw() +
-  labs(y = "P(Compete Against High Performer)", x = NULL) +
-  theme(panel.grid = element_blank(),
-        panel.border = element_blank(),
-        axis.line = element_line(colour = "grey"),
-        axis.text.x = element_text(size = 12),
-        legend.position = "none", # No legend
-        plot.title = element_text(hjust = 0.5, size = 16)) +
-  scale_x_discrete(labels = c("Expectation shown", "Expectation Absent")) +
-   geom_text(aes(label=Treatment, y = -0.01), position = position_dodge(0.90))
-
-```
-
-## Discussion
-
-When the quality of a decision does not depend on someone's expectations, the adviser's awareness of the advisee's expectations should not influence the advice given.
-However, in line with our argument that advisers take into account the belief utility of the advisee and prefer to flatter rather than disappoint, we find that displaying the advisee's expectations does make a difference.
-Specifically, advisees who expressed a preference for stronger competitors were more likely to receive 'flattering' advice, encouraging them to pursue that option.
-One possible explanation for this finding is that, rather than trying to flatter, advisers may simply be telling advisees what they want to hear.
-In the next study, we aim to investigate the mechanism behind this discrepancy in advice-giving when expectations are revealed, exploring the question: Why do people give flattering advice?
-
-# Study 2
-
-So far, we have shown that displaying expectations influences the advice given.
-Specifically, advisers were more likely to recommend competing against a group of high performers to advisees with higher performance expectations compared to those without.
-We now directly test whether this effect is driven by interpersonal concerns.
-In particular, we explore whether more flattering advice stems from a desire to be liked, and whether advisees, in turn, like advisers more when they receive flattering advice.
-
-We conducted a three-stage experiment in which we experimentally manipulated the incentives for advisers.
-We began by inviting a group of advisees to upload photos of themselves ("selfies") and informed them that they would be rated on their attractiveness.
-We grouped them with nine other participants of the same gender and recruited participants of the opposing gender to rank them from most to least attractive and to provide advice.
-Specifically, we asked them to advise the participant they ranked as the 7th most attractive (4th least attractive) on what rank they should bet they were ranked by a larger group of raters.
-Advisers were randomly assigned to two treatments, receiving a bonus payment either if the advisee guessed their rank accurately or if the advisee evaluated the adviser as likeable as measured by an unincentivized scale response.
-We hypothesize that advisers who want to be liked by advisees will recommend that they bet on a lower rank, i.e.
-that they are more attractive.
-
-```{r}
-#| include: false
-
-study2_time1 <- readRDS(here::here("Data/Study2_time1.Rds"))
-study2_time1_200 <- readRDS(here::here("Data/Study2_time1_200.Rds"))
-study2_time2 <- readRDS(here::here("Data/Study2_time2.Rds"))
-study2_finalRank <- readRDS(here::here("Data/Study2_finalRank.Rds"))
-study2_time3 <- readRDS(here::here("Data/Study2_time3.Rds"))
-
-```
-
-## Methods
-
-We recruited 300 participants from Prolific and, after asking demographic questions, invited them to upload photos of themselves (selfies) to be rated by other participants on attractiveness.
-`r scales::comma(dim(study2_time1[study2_time1$gender == 'Male',])[1])` men and `r scales::comma(dim(study2_time1[study2_time1$gender == 'Female',])[1])` women agreed to do so and uploaded pictures that adhered to our instructions (e.g., did not include other people).
-We selected the first 100 photos from women to arrive at a gender-balanced sample ($M_{\text{Age}}$ = `r mean(study2_time1_200$age)` years).
-Participants were informed that their selfies would be randomly grouped with those of nine other participants of their gender and ranked in terms of attractiveness by a group of new Prolific participants of the opposite gender.
-Lastly, they guessed their rank (unincentivized).
-
-Next, we recruited a new, gender-balanced sample for the role of advisers.
-`r scales::comma(dim(study2_time2)[1])` participants from Prolific ($M_{\text{Age}}$ = `r mean(study2_time2$age)` years; `r round(mean(study2_time2$gender == "Female")*100, 2)`% Female) started by providing demographic information, then were matched to a group of the opposite gender.
-They then ranked participants from most to least attractive using a drop-down menu next to each picture.
-Because of a limitation with the survey software, participants were able to select the same rank for multiple participants, rather than rank them uniquely.
-We remove 115 participants who did not follow instructions and provide a unique ranking.
-
-After submitting their ratings, they saw the photo of the participant they had ranked as the 7th most attractive (i.e., the 4th least attractive).
-They were reminded of the rank they had given to that person and informed that this participant would be invited back and could earn a \$1 bonus if they guessed their rank correctly.
-The rank was determined by the aggregate ratings of all participants who had ranked this group.
-Their task was to give advice to this participant about the rank they should bet on based on having observed all ten selfies and their own assessment.
-We randomly assigned participants to one of two incentivization schemes.
-In the "Accuracy" treatment, they received a bonus identical to the advisee: \$1 if they guessed their rank correctly.
-In the "Likeability" treatment, we informed them that they would be rated by the advisee on a 5-point Likert scale for how likeable they thought they were.
-Each point on the scale would translate to a bonus of 20 cents.
-They then selected a rank that they would recommend the advisee to bet on.
-
-Finally, we invited participants from Stage 1 and were ranked as the 7th attractive by at least one adviser (so that they received advice) back for the follow-up survey.
-Following our preregistration, we kept the survey open for 7 days.
-In total, `r scales::comma(dim(study2_time3)[1])` participants (`r scales::comma(dim(study2_time3[study2_time3$gender == 'Male',])[1])` men, `r scales::comma(dim(study2_time3[study2_time3$gender == 'Female',])[1])` women) returned.
-They were reminded of the selfie they uploaded in Stage 1 and informed that a group of 10 selfies, including theirs, had been rated by other participants from Prolific.
-They then saw the advice from a randomly selected adviser and made their estimate with a \$1 incentive for guessing accurately.
-They then saw the rank they had been advised to bet on one more time and were asked to rate the adviser's likability, warmth, friendliness, good-naturedness, trustworthiness, and sincerity on 5-point Likert scales (adapted from @Fiske2007).
-
-## Results
-
-```{r}
-#| include: false
-library(dplyr)
-
-TargetsUnique <- study2_time2 %>%
-  dplyr::select(Target) %>%
-  unique()
-
-TargetsUnique <- merge(TargetsUnique,study2_finalRank, by.x = 'Target', by.y = 'QID7_Id')
-
-```
-
-```{r}
-#| label: fig-study2advice
-#| fig-cap: "Advisers were asked to suggest what rank to bet on for someone they ranked as the 7th most attractive out of ten people.
-When incentivized for accuracy, most of them advised betting on 7, which was based on their evaluation of the recipient's attractiveness.
-However, when incentivized for likability, many participants gave flattering advice by suggesting betting on higher ranks that imply a higher evaluation of attractiveness."
-
-library(ggplot2)
-library(ggridges)
-
-study2_time2 <- study2_time2 %>% dplyr::mutate(Advice = as.numeric(Advice))
-
-ggplot(study2_time2, aes(x = Advice, y = Condition, fill = Condition)) +
-    # Reduce vertical spacing with rel_min_height and scale
-    geom_density_ridges(scale = 1.0, rel_min_height = 0.01, alpha = 0.7) +
-
-    # Shading the left side of x = 7 in light grey
-    geom_rect(aes(xmin = 7, xmax = Inf, ymin = -Inf, ymax = Inf), fill = "gray95", alpha = 0.01) +
-
-    # Add the dashed line at x = 7
-    geom_vline(xintercept = 7, col = 'black', linetype = 'dashed', linewidth = 0.7) +
-
-    # Add the text "Flattering" on the left of the line
-    annotate("text", x = 5, y = 0.6, label = "Flattering Ranks", hjust = 1, size = 8, fontface = "bold") +
-
-    # Manual fill colors
-    scale_fill_manual(values = c("#2A629A", '#FF7F3E'), labels = c("Accurate", "Likable")) +
-
-    # X-axis adjustments
-    scale_x_continuous(name = "Advised Rank", breaks = seq(1, 10)) +
-
-    # Theme adjustments
-    theme_bw() +
-    theme(panel.grid = element_blank(),
-          panel.border = element_blank(),
-          axis.line = element_line(colour = "black"),
-          legend.position = "bottom",
-          legend.title = element_blank(),
-          legend.key.size = unit(1.2, "lines"),
-          legend.text = element_text(size = 12),
-          plot.title = element_text(hjust = 0.5, size = 20),
-          axis.text.x = element_text(size = 14),  # X-axis text size
-          axis.text.y = element_text(size = 14),
-          axis.title.x = element_text(size = 16, face = "bold"),  # X-axis title size
-          axis.title.y = element_text(size = 16, face = "bold"))
-
-```
-
-We begin by examining the prior beliefs of advisees who uploaded their selfies.
-On average, men guessed they ranked `r round(mean(study2_time1[study2_time1$gender == "Male",]$Guess),2)` in their group of 10 and women guessed that they ranked `r round(mean(study2_time1[study2_time1$gender == "Female",]$Guess),2)`.
-Participants overall underestimate their attractiveness relative to the benchmark average of 5.5.
-Moreover, women do so more than men `r papaja::apa_print(t.test(Guess ~ gender, data = study2_time1, var.equal = T))$statistic`.
-Notably, people's self-perceptions correlated strongly with the aggregate ratings of the advisers (`r round(cor(study2_finalRank$Guess, study2_finalRank$finalRank),2)`, `r papaja::apa_print(cor.test(study2_finalRank$Guess, study2_finalRank$finalRank))$statistic`).
-However, there was substantial heterogeneity in perceptions of attractiveness.
-Of the 200 participants, `r length(unique(study2_time2$Target))` were ranked as 7th most attractive by at least one adviser.
-On average, men in this subset estimated they were ranked `r round(mean(TargetsUnique[TargetsUnique$gender == 'Male',]$Guess),2)`th and women estimated they were ranked `r round(mean(TargetsUnique[TargetsUnique$gender == 'Female',]$Guess),2)`th (`r papaja::apa_print(t.test(Guess ~ gender, data = TargetsUnique, var.equal = T))$statistic`).
-
-Next, we turn our attention to the advisers (@fig-study2advice).
-In the Accuracy condition, those uploading selfies were advised to bet on rank `r round(mean(study2_time2[study2_time2$Condition == "Accurate",]$Advice),2)`.
-Notably, this is significantly more attractive than the 7th rank those advisers had themselves guessed just on the prior screen (`r papaja::apa_print(t.test(study2_time2[study2_time2$Condition == "Accurate",]$Advice, mu = 7, var.equal = T))$statistic`).
-This suggests that even when incentivized for accuracy, participants offered flattering advice.[^1] Importantly, and as predicted, we find that advisers in the Likeable treatment recommend betting on a lower rank, communicating that they think the participant in the selfie is more attractive (`r round(mean(study2_time2[study2_time2$Condition == "Likable",]$Advice),2)`, `r papaja::apa_print(t.test(Advice ~ Condition, data = study2_time2, var.equal = T))$statistic`).
-This suggests that advisers inferred that advising someone that they were more attractive would make the adviser appear more likeable and therefore provided advice that communicated a more favorable impression of the participants' attractiveness.
-The distribution shown in @fig-study2advice shows that participants do not simply tell participants that they are the most attractive person in the group.
-They may infer that flattering advise needs to be somewhat realistic to be believable.
-We return to this in the general discussion.
-
-[^1]: This shading could be due to concerns of avoiding disappointment.
-However, it could also be that advisers are uncertain about the rankings they had given and make a recommendation that combines their own belief with a uniform prior.
-
-<!-- David: Making a note here that we should be sure to discuss this at the end -->
-
-<!-- as something for future research. -->
-
-<!-- David: We should also report something on accuracy of the advice given across -->
-
-<!-- the treatments. Even if no difference. -->
-
-```{r}
-#| label: tbl-study2regs
-#| tbl-cap: "When individuals receive advice that implies a high level of attractiveness (lower rank), they tend to perceive the advice giver as more likable (Column 1), warm (Column 2).
-Column 3 shows that advisors are rated as more trustworthy when they advice lower ranks, but this relationship is only directional."
-
-modelsummary::modelsummary(list(`(1)` = lm(likable ~ Advice, data = study2_time3),
-                                `(2)` = lm(warmAvg ~ Advice, data = study2_time3),
-                                `(3)` = lm(trustAvg ~ Advice, data = study2_time3)),
-                           vcov = c("classical", "classical", "classical"),
-                           coef_map = c("Advice" = "Advised Rank",
-                                        "(Intercept)" = "Constant"),
-                           stars = T,
-                           gof_map = list(list('raw' = 'nobs', 'clean' = 'N', 'fmt' = 0)))
-
-```
-
-Finally, we examine whether flattering advice indeed leads to more positive evaluations of advisers, or whether flattering advice is dismissed as insencere.
-Following our preregistration, we average the ratings on likeability, warmth, friendliness, and good-naturedness to create a scale of likeability ($\alpha$ = `r cronbach.alpha(study2_time3[, 5:8])$alpha`); and we create a scale of trustworthiness by averaging the ratings of trustworthiness and sincerity ($\alpha$ = `r cronbach.alpha(study2_time3[, 9:10])$alpha`).
-
-```{r}
-#| label: fig-study2rating
-#| fig-cap: "Participants tend to rate advisors who suggest betting on a higher rank (implying greater attractiveness) as more likable and warm."
-
-library(ggplot2)
-library(dplyr)
-library(tidyr)
-
-study2_time3 <- study2_time3 %>% dplyr::mutate(Advice = as.numeric(Advice))
-
-# Reshape the data to long format
-study2_long <- study2_time3 %>%
-  pivot_longer(cols = c(likable, warmAvg), 
-               names_to = "Evaluation", 
-               values_to = "Value")
-
-# Create the plot
-ggplot(study2_long, aes(x = Advice, y = Value, color = Evaluation)) +  
-  # Add points for each observation
-  geom_point(size = 2, alpha = 0.7) +
-
-  # Add linear regression lines for each metric
-  geom_smooth(method = "lm", se = TRUE, aes(fill = Evaluation), alpha = 0.2, show.legend = FALSE) +
-
-  # Customize axis labels
-  scale_y_continuous(name = "Evaluation",limits = c(0.9, 5.1)) +  
-  scale_x_continuous(name = "Advised Rank",limits = c(1, 10), breaks = c(1,2,3,4,5,6,7,8,9,10)) +
-
-  # Apply a theme
-  theme_bw() +  
-  theme(panel.grid = element_blank(),
-        panel.border = element_blank(),
-        axis.line = element_line(colour = "grey"),
-        legend.position = "right",
-        plot.title = element_text(hjust = 0.5, size = 20)) +
-
-  # Set custom colors for each metric
-  scale_color_manual(values = c("#FF7F3E", "#2A629A"), 
-                     labels = c("Likability", "Warm")) + 
-  scale_fill_manual(values = c("#FF7F3E", "#2A629A"))
-
-```
-
-```{r}
-#| label: fig-study2ratingByGroup
-#| fig-cap: "After participants received advice that suggested betting on a rank that was lower than, equal to, or higher than their self-expectations, they evaluated advisors based on their likability and warmth.
-Participants rated advisors who gave flattering advice and delivered a high evaluation of their attractiveness as more likable and warm than those whose advice implied a lower evaluation of their attractiveness."
-
-library(dplyr)
-library(ggplot2)
-library(reshape2)
-
-study2_time3 <- study2_time3 %>% dplyr::mutate(Guess = as.numeric(Guess), Advice = as.numeric(Advice)) %>%
-  dplyr::mutate(HorL = ifelse(Guess == Advice,0, ifelse(Guess > Advice, 1,-1))) %>%
-  dplyr::mutate(HorL = as.factor(HorL)) %>% 
-  dplyr::mutate(bonus = ifelse(bet == `Final Rank`,1,0)) %>%
-  dplyr::mutate(accuracy = `Final Rank`-Advice)
-
-ratings <- study2_time3 %>%
-  group_by(HorL) %>%
-  summarise(like = round(mean(likable),2), warmth = round(mean(warmAvg),2))
-
-rating_table <- matrix(c(ratings$like,ratings$warmth), nrow = 2, byrow = TRUE, dimnames = list( c("Likable",'Warm'),c("Lower than", "Equal to", "Higher than")))
-
-rating_df = as.data.frame.table(rating_table) %>%
-  dplyr::rename( 'Condition'='Var1', 'Advice' ='Var2') %>%
-  dplyr::mutate(Freq = round(Freq,2))
-
-# Create a data frame similar to your structure
-data <- rating_df
-
-# Reshape the data to wide format for the heatmap
-heatmap_data <- dcast(data, Condition ~ Advice, value.var = "Freq")
-
-# Melt the data for ggplot
-melted_data <- melt(heatmap_data, id.vars = "Condition", variable.name = "Advice", value.name = "Rating")
-
-# Create the heatmap
-ggplot(melted_data, aes(x = Advice, y = Condition, fill = Rating)) +
-  geom_tile(color = "white") +
-  scale_fill_gradient(low = "grey80", high = "grey30", name = "Rating") +  # Grey gradient from light to dark
-  geom_text(aes(label = sprintf("%.2f", Rating)), color = "white", size = 8) +
-  theme_minimal() +
-  labs(x = "Attractiveness (Advice Relative to Self-Expectations)", y = "Evaluation") +
-  theme(
-    axis.text.x = element_text(size = 12),  # X-axis text size
-          axis.text.y = element_text(size = 12),
-          axis.title.x = element_text(size = 12),  # X-axis title size
-          axis.title.y = element_text(size = 12))
-
-```
-
-As seen in @fig-study2rating, we found that advisees who suggested that the advisee was more attractive (lower rank) were indeed rated as more likeable and warm (b = -0.109, p \< .05; b = -0.133, p \< .001, respectively; See Columns 1 and 2 of @tbl-study2regs).
-When using their self-expectations as a reference point, advisors who suggest a rank lower than that point are perceived as less likable and warm (see @fig-study2ratingByGroup).
-Interestingly, these benefits are not at the cost of being hypocritical; advisers who recommend a more favorable rank are viewed as no less trustworthy (Column 3 of @tbl-study2regs).
-
-We were not powered to do a comparison across the two experimental groups and did not preregister such a difference.
-Indeed, we find no difference in likeability and warmth across the two treatments (`r papaja::apa_print(t.test(likable ~ Condition, data = study2_time3, var.equal = T))$statistic`, and `r papaja::apa_print(t.test(warmAvg ~ Condition, data = study2_time3, var.equal = T))$statistic`, respectively).
-We also assess the quality of advice by measuring the discrepancy between the advised rank and the final rank.
-Our analysis revealed no significant difference between the two treatments in terms of how helpful the advice was for advisees in making accurate guesses, `r papaja::apa_print(t.test(accuracy ~ Condition, data = study2_time3, var.equal = T))$statistic`.
-
-## Discussion
-
-In another context where advice communicates ego-relevant information (here, people's attractiveness), we find that the advice people give is contingent on their incentives.
-Specifically, when they get rewarded for being more likeable, they recommend that the advisee bet on a more favorable rank than when they are incentivized for accuracy.
-Importantly, advisees do not discount flattering advice and instead evaluate people who advise them to bet on a more attractive rank as warmer and more likeable.
-These gains to interpersonal perceptions do not come at the cost of trustworthiness, even when the advice is substantially inflated (e.g., a recommendation that the advisee is the most attractive in the group).
-
-# Study 3
-
-```{r}
-#| include: false
-
-study3_math50 <- read.csv(here::here("Data/Cleaned Data/S3_Math50_cleaned.csv"))
-study3_time1All <- readRDS(here::here("Data/Study3_time1All.Rds"))
-study3_time1 <- readRDS(here::here("Data/Study3_time1.Rds"))
-study3_time2_giver <- readRDS(here::here("Data/Study3_time2_giver.Rds"))
-study3_time2_giver50 <- readRDS(here::here("Data/Study3_time2_giver50.Rds"))
-study3_advice <- readRDS(here::here("Data/Study3_time2_advice.Rds"))
-study3_time3 <- readRDS(here::here("Data/Study3_time3.Rds"))
-
-```
-
-In Study 3, we replicate the main effect in a different ego-relevant domain: intelligence.
-The experimental design is conceptually identical to Study 1, but this time we utilize a more direct measure of expectation by asking participants to estimate their scores.
+Because our default treatment takes place after participants completed
+the ability quiz, we do not expect a difference in performance across
+the Low and High Default treatments. Indeed, the two groups scored no
+different from one another (5.1 and 5.18 for the Low Default and High
+Default treatments, respectively, \(t(199) = 0.31\), \(p = .756\)). The
+default manipulation affected their initial choices. In the ``Low
+Default'' treatment, only 22\% of participants initially preferred
+competing against the High Performer Group, compared to 65\% of
+participants who saw the High Performer Group highlighted (\(\chi^2\)(1,
+n = 201) = 36.62, p \textless{} .001).
+
+\begin{table}
+
+{\caption{{Advice to compete against the High Performer Group in Study
+1. Displaying the non-binding choice of those for whom the Low Performer
+Group was selected by default makes it more likely that they are advised
+to compete against the High Performer Group (Column 1). Column 2
+restricts the analysis to advisers who observed advisees' initial
+non-binding choice and controls for advisees' score on the quiz.
+Standard errors are clustered at the adviser
+level.}{\label{tbl-study1regs}}}
+\vspace{-20pt}}
+
+\centering
+\begin{talltblr}[         %% tabularray outer open
+entry=none,label=none,
+note{}={+ p \num{< 0.1}, * p \num{< 0.05}, ** p \num{< 0.01}, *** p \num{< 0.001}},
+]                     %% tabularray outer close
+{                     %% tabularray inner open
+colspec={Q[]Q[]Q[]},
+column{2,3}={}{halign=c,},
+column{1}={}{halign=l,},
+hline{12}={1,2,3}{solid, black, 0.05em},
+}                     %% tabularray inner close
+\toprule
+& (1) & (2) \\ \midrule %% TinyTableHeader
+High Default               & \num{0.011}    & \num{0.025}*    \\
+& (\num{0.013})  & (\num{0.011})   \\
+Expectation Shown          & \num{-0.041}*  &                  \\
+& (\num{0.016})  &                  \\
+Expectation x High Default & \num{0.037}+   &                  \\
+& (\num{0.019})  &                  \\
+Performance                &                 & \num{0.168}***  \\
+&                 & (\num{0.004})   \\
+Constant                   & \num{0.389}*** & \num{-0.503}*** \\
+& (\num{0.012})  & (\num{0.020})   \\
+N                          & \num{10000}    & \num{5000}      \\
+\bottomrule
+\end{talltblr}
+
+\end{table}
+
+We now examine whether advisers took the advisees' expectations into
+account. Recall that advisees who were defaulted to competing against
+the High Performer Group were indeed more likely to choose this group,
+which, from the advisers' perspective, could signal high confidence in
+their abilities. Our theory predicts that showing expectations should
+lead to more flattering advice--- specifically, a recommendation to
+compete against the High Performer Group--- for advisees with a high
+default choice compared to those with a low default choice. Column 1 of
+Table~\ref{tbl-study1regs} reports a linear probability model with
+advice to compete against the high group as the outcome measure,
+incorporating the default choice advisees saw, whether expectations were
+shown to the adviser, and the interaction of the two. Because each
+adviser made ten recommendations, we cluster standard errors at the
+adviser level. As predicted, we find a marginally significant
+interaction effect: advisees with a default choice to compete against
+the High Performer Group (nudged to have high expectations, though not
+necessarily holding them) were more likely to receive advice to compete
+against stronger competitors when their expectations were shown compared
+to when they were hidden. We reported a linear probability model on
+advising to compete against the High Performer group for advisers in the
+``Expectations'' treatment, controlling for the true performance of the
+advisee in Column 2 of Table~\ref{tbl-study1regs}. We observe a
+significant main effect of the default treatment, where a high default
+increased the likelihood of receiving flattering advice. It is worth
+noting that, since only 65 \% of advisees in the high default group
+actually stuck with their default choice, this represents a conservative
+test of the effect of high expectations on the likelihood of receiving
+flattering advice.
+
+\begin{figure}
+
+\caption{\label{fig-study1Advice}Advisees who were nudged to express
+high expectations were more likely to receive advice to compete against
+the High Performer Group.}
+
+\centering{
+
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-study1Advice-1.pdf}}
+
+}
+
+\end{figure}%
+
+\subsection{Discussion}\label{discussion}
+
+When the quality of a decision does not depend on someone's
+expectations, the adviser's awareness of the advisee's expectations
+should not influence the advice given. However, in line with our
+argument that advisers take into account the belief utility of the
+advisee and prefer to flatter rather than disappoint, we find that
+displaying the advisee's expectations does make a difference.
+Specifically, advisees who expressed a preference for stronger
+competitors were more likely to receive `flattering' advice, encouraging
+them to pursue that option. One possible explanation for this finding is
+that, rather than trying to flatter, advisers may simply be telling
+advisees what they want to hear. In the next study, we aim to
+investigate the mechanism behind this discrepancy in advice-giving when
+expectations are revealed, exploring the question: Why do people give
+flattering advice?
+
+\section{Study 2}\label{study-2}
+
+So far, we have shown that displaying expectations influences the advice
+given. Specifically, advisers were more likely to recommend competing
+against a group of high performers to advisees with higher performance
+expectations compared to those without. We now directly test whether
+this effect is driven by interpersonal concerns. In particular, we
+explore whether more flattering advice stems from a desire to be liked,
+and whether advisees, in turn, like advisers more when they receive
+flattering advice.
+
+We conducted a three-stage experiment in which we experimentally
+manipulated the incentives for advisers. We began by inviting a group of
+advisees to upload photos of themselves (``selfies'') and informed them
+that they would be rated on their attractiveness. We grouped them with
+nine other participants of the same gender and recruited participants of
+the opposing gender to rank them from most to least attractive and to
+provide advice. Specifically, we asked them to advise the participant
+they ranked as the 7th most attractive (4th least attractive) on what
+rank they should bet they were ranked by a larger group of raters.
+Advisers were randomly assigned to two treatments, receiving a bonus
+payment either if the advisee guessed their rank accurately or if the
+advisee evaluated the adviser as likeable as measured by an
+unincentivized scale response. We hypothesize that advisers who want to
+be liked by advisees will recommend that they bet on a lower rank,
+i.e.~that they are more attractive.
+
+\subsection{Methods}\label{methods-1}
+
+We recruited 300 participants from Prolific and, after asking
+demographic questions, invited them to upload photos of themselves
+(selfies) to be rated by other participants on attractiveness. 100 men
+and 107 women agreed to do so and uploaded pictures that adhered to our
+instructions (e.g., did not include other people). We selected the first
+100 photos from women to arrive at a gender-balanced sample
+(\(M_{\text{Age}}\) = 39.37 years). Participants were informed that
+their selfies would be randomly grouped with those of nine other
+participants of their gender and ranked in terms of attractiveness by a
+group of new Prolific participants of the opposite gender. Lastly, they
+guessed their rank (unincentivized).
+
+Next, we recruited a new, gender-balanced sample for the role of
+advisers. 472 participants from Prolific (\(M_{\text{Age}}\) =
+41.0275424 years; 49.79\% Female) started by providing demographic
+information, then were matched to a group of the opposite gender. They
+then ranked participants from most to least attractive using a drop-down
+menu next to each picture. Because of a limitation with the survey
+software, participants were able to select the same rank for multiple
+participants, rather than rank them uniquely. We remove 115 participants
+who did not follow instructions and provide a unique ranking.
+
+After submitting their ratings, they saw the photo of the participant
+they had ranked as the 7th most attractive (i.e., the 4th least
+attractive). They were reminded of the rank they had given to that
+person and informed that this participant would be invited back and
+could earn a \$1 bonus if they guessed their rank correctly. The rank
+was determined by the aggregate ratings of all participants who had
+ranked this group. Their task was to give advice to this participant
+about the rank they should bet on based on having observed all ten
+selfies and their own assessment. We randomly assigned participants to
+one of two incentivization schemes. In the ``Accuracy'' treatment, they
+received a bonus identical to the advisee: \$1 if they guessed their
+rank correctly. In the ``Likeability'' treatment, we informed them that
+they would be rated by the advisee on a 5-point Likert scale for how
+likeable they thought they were. Each point on the scale would translate
+to a bonus of 20 cents. They then selected a rank that they would
+recommend the advisee to bet on.
+
+Finally, we invited participants from Stage 1 and were ranked as the 7th
+attractive by at least one adviser (so that they received advice) back
+for the follow-up survey. Following our preregistration, we kept the
+survey open for 7 days. In total, 146 participants (77 men, 69 women)
+returned. They were reminded of the selfie they uploaded in Stage 1 and
+informed that a group of 10 selfies, including theirs, had been rated by
+other participants from Prolific. They then saw the advice from a
+randomly selected adviser and made their estimate with a \$1 incentive
+for guessing accurately. They then saw the rank they had been advised to
+bet on one more time and were asked to rate the adviser's likability,
+warmth, friendliness, good-naturedness, trustworthiness, and sincerity
+on 5-point Likert scales (adapted from Fiske et al. (2007)).
+
+\subsection{Results}\label{results-1}
+
+\begin{figure}
+
+\caption{\label{fig-study2advice}Advisers were asked to suggest what
+rank to bet on for someone they ranked as the 7th most attractive out of
+ten people. When incentivized for accuracy, most of them advised betting
+on 7, which was based on their evaluation of the recipient's
+attractiveness. However, when incentivized for likability, many
+participants gave flattering advice by suggesting betting on higher
+ranks that imply a higher evaluation of attractiveness.}
+
+\centering{
+
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-study2advice-1.pdf}}
+
+}
+
+\end{figure}%
+
+We begin by examining the prior beliefs of advisees who uploaded their
+selfies. On average, men guessed they ranked 5.76 in their group of 10
+and women guessed that they ranked 6.37. Participants overall
+underestimate their attractiveness relative to the benchmark average of
+5.5. Moreover, women do so more than men \(t(205) = 2.15\),
+\(p = .033\). Notably, people's self-perceptions correlated strongly
+with the aggregate ratings of the advisers (0.43, \(t(193) = 6.70\),
+\(p < .001\)). However, there was substantial heterogeneity in
+perceptions of attractiveness. Of the 200 participants, 149 were ranked
+as 7th most attractive by at least one adviser. On average, men in this
+subset estimated they were ranked 5.94th and women estimated they were
+ranked 6.59th (\(t(143) = 1.94\), \(p = .054\)).
+
+Next, we turn our attention to the advisers
+(Figure~\ref{fig-study2advice}). In the Accuracy condition, those
+uploading selfies were advised to bet on rank 6.19. Notably, this is
+significantly more attractive than the 7th rank those advisers had
+themselves guessed just on the prior screen (\(t(234) = -8.82\),
+\(p < .001\)). This suggests that even when incentivized for accuracy,
+participants offered flattering advice.\footnote{This shading could be
+  due to concerns of avoiding disappointment. However, it could also be
+  that advisers are uncertain about the rankings they had given and make
+  a recommendation that combines their own belief with a uniform prior.}
+Importantly, and as predicted, we find that advisers in the Likeable
+treatment recommend betting on a lower rank, communicating that they
+think the participant in the selfie is more attractive (5.38,
+\(t(470) = 5.44\), \(p < .001\)). This suggests that advisers inferred
+that advising someone that they were more attractive would make the
+adviser appear more likeable and therefore provided advice that
+communicated a more favorable impression of the participants'
+attractiveness. The distribution shown in Figure~\ref{fig-study2advice}
+shows that participants do not simply tell participants that they are
+the most attractive person in the group. They may infer that flattering
+advise needs to be somewhat realistic to be believable. We return to
+this in the general discussion.
+
+\begin{table}
+
+{\caption{{When individuals receive advice that implies a high level of
+attractiveness (lower rank), they tend to perceive the advice giver as
+more likable (Column 1), warm (Column 2). Column 3 shows that advisors
+are rated as more trustworthy when they advice lower ranks, but this
+relationship is only directional.}{\label{tbl-study2regs}}}
+\vspace{-20pt}}
+
+\centering
+\begin{talltblr}[         %% tabularray outer open
+entry=none,label=none,
+note{}={+ p \num{< 0.1}, * p \num{< 0.05}, ** p \num{< 0.01}, *** p \num{< 0.001}},
+]                     %% tabularray outer close
+{                     %% tabularray inner open
+colspec={Q[]Q[]Q[]Q[]},
+column{2,3,4}={}{halign=c,},
+column{1}={}{halign=l,},
+hline{6}={1,2,3,4}{solid, black, 0.05em},
+}                     %% tabularray inner close
+\toprule
+& (1) & (2) & (3) \\ \midrule %% TinyTableHeader
+Advised Rank & \num{-0.109}*  & \num{-0.133}** & \num{-0.054}   \\
+& (\num{0.046})  & (\num{0.044})  & (\num{0.042})  \\
+Constant     & \num{3.777}*** & \num{3.903}*** & \num{3.397}*** \\
+& (\num{0.279})  & (\num{0.266})  & (\num{0.257})  \\
+N            & \num{146}      & \num{146}      & \num{146}      \\
+\bottomrule
+\end{talltblr}
+
+\end{table}
+
+Finally, we examine whether flattering advice indeed leads to more
+positive evaluations of advisers, or whether flattering advice is
+dismissed as insencere. Following our preregistration, we average the
+ratings on likeability, warmth, friendliness, and good-naturedness to
+create a scale of likeability (\(\alpha\) = 0.9243334); and we create a
+scale of trustworthiness by averaging the ratings of trustworthiness and
+sincerity (\(\alpha\) = 0.8740347).
+
+\begin{figure}
+
+\caption{\label{fig-study2rating}Participants tend to rate advisors who
+suggest betting on a higher rank (implying greater attractiveness) as
+more likable and warm.}
+
+\centering{
+
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-study2rating-1.pdf}}
+
+}
+
+\end{figure}%
+
+\begin{figure}
+
+\caption{\label{fig-study2ratingByGroup}After participants received
+advice that suggested betting on a rank that was lower than, equal to,
+or higher than their self-expectations, they evaluated advisors based on
+their likability and warmth. Participants rated advisors who gave
+flattering advice and delivered a high evaluation of their
+attractiveness as more likable and warm than those whose advice implied
+a lower evaluation of their attractiveness.}
+
+\centering{
+
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-study2ratingByGroup-1.pdf}}
+
+}
+
+\end{figure}%
+
+As seen in Figure~\ref{fig-study2rating}, we found that advisees who
+suggested that the advisee was more attractive (lower rank) were indeed
+rated as more likeable and warm (b = -0.109, p \textless{} .05; b =
+-0.133, p \textless{} .001, respectively; See Columns 1 and 2 of
+Table~\ref{tbl-study2regs}). When using their self-expectations as a
+reference point, advisors who suggest a rank lower than that point are
+perceived as less likable and warm (see
+Figure~\ref{fig-study2ratingByGroup}). Interestingly, these benefits are
+not at the cost of being hypocritical; advisers who recommend a more
+favorable rank are viewed as no less trustworthy (Column 3 of
+Table~\ref{tbl-study2regs}).
+
+We were not powered to do a comparison across the two experimental
+groups and did not preregister such a difference. Indeed, we find no
+difference in likeability and warmth across the two treatments
+(\(t(144) = 1.09\), \(p = .275\), and \(t(144) = 0.58\), \(p = .562\),
+respectively). We also assess the quality of advice by measuring the
+discrepancy between the advised rank and the final rank. Our analysis
+revealed no significant difference between the two treatments in terms
+of how helpful the advice was for advisees in making accurate guesses,
+\(t(144) = -0.29\), \(p = .776\).
+
+\subsection{Discussion}\label{discussion-1}
+
+In another context where advice communicates ego-relevant information
+(here, people's attractiveness), we find that the advice people give is
+contingent on their incentives. Specifically, when they get rewarded for
+being more likeable, they recommend that the advisee bet on a more
+favorable rank than when they are incentivized for accuracy.
+Importantly, advisees do not discount flattering advice and instead
+evaluate people who advise them to bet on a more attractive rank as
+warmer and more likeable. These gains to interpersonal perceptions do
+not come at the cost of trustworthiness, even when the advice is
+substantially inflated (e.g., a recommendation that the advisee is the
+most attractive in the group).
+
+\section{Study 3}\label{study-3}
+
+In Study 3, we replicate the main effect in a different ego-relevant
+domain: intelligence. The experimental design is conceptually identical
+to Study 1, but this time we utilize a more direct measure of
+expectation by asking participants to estimate their scores.
 
 This three-stage experiment begins with measuring actual performance.
-Participants are then anchored to low or high performance expectations and asked to guess how many questions they answered correctly.
-As in previous studies, we recruit advisers who are presented with either just the advisee's true performance or both the true performance and the number of questions the advisee believes they answered correctly.
+Participants are then anchored to low or high performance expectations
+and asked to guess how many questions they answered correctly. As in
+previous studies, we recruit advisers who are presented with either just
+the advisee's true performance or both the true performance and the
+number of questions the advisee believes they answered correctly.
 Advisers are then asked to provide advice on choosing a competitor.
-Finally, we present the advice to the advisees and ask them to make their final choice.
-Our key hypotheses are: (1) advisees anchored to high expectations will be more likely to receive advice to compete against the high-performing group, and (2) men will be more likely than women to be advised to compete against the high-performing group when expectations are disclosed.
-
-## Methods
-
-```{r}
-#| include: false
-
-subgroup_averages <- data.frame(subgroup = numeric(), avg_score = numeric())
-set.seed(807)
-# loop through 1000 iterations of randomly selecting 10 participants and computing their average score
-for (i in 1:1000) {
-  # randomly select 10 participants
-  subgroup <- sample(study3_math50$ProlificID, size = 5, replace = FALSE)
-  # compute the average score for the selected participants
-  subgroup_avg <- mean(study3_math50$Score[study3_math50$ProlificID %in% subgroup])
-  # add the subgroup and its average score to the dataframe
-  subgroup_averages <- rbind(subgroup_averages, data.frame(subgroup = i, avg_score = subgroup_avg))
+Finally, we present the advice to the advisees and ask them to make
+their final choice. Our key hypotheses are: (1) advisees anchored to
+high expectations will be more likely to receive advice to compete
+against the high-performing group, and (2) men will be more likely than
+women to be advised to compete against the high-performing group when
+expectations are disclosed.
+
+\subsection{Methods}\label{methods-2}
+
+We begin by first recruiting a sample of 50 participants from Prolific
+to complete a 10-question multiple choice mathematics quiz. The
+questions were taken from a paper-version of the ASVAB standardized
+exam, such that answers were not available online. Participants had five
+minutes to answer the quiz and were paid 10 cents for each correctly
+answered question. Like before, we define top 20 scores as ``High
+Performers'' and the bottom 20 scorers as the ``Low Performers.'' On
+average, participants answered 4.42 questions correctly, High Performers
+scored between 5 and 10, and Low Performers scored between 0 and 3. In
+order to anchor the expectations of participants in our main experiment,
+we simulated 1,000 pairings of groups of five participants, with the 5th
+percentile of groups scoring an average of 2.6 and the 95 th percentile
+scoring an average of 6.4. We report these averages to participants in
+the Low Expectations and High Expectations treatment, respectively.
+
+We then recruited 1,002 participants for the role of advisees in Stage 1
+of our main experiment. To arrive at a gender-balanced sample, we
+dropped the last two male participants to complete the survey, ending up
+with a sample of 500 men and 500 women (\(M_{\text{Age}}\) = 42.16).
+Participants completed the same 10-item mathematics quiz as the earlier
+participants and were informed that their performance would affect their
+bonus earnings in a follow-up stage to be conducted a few days later.
+After completing the quiz, we informed them of the average score of a
+group of five participants from the preliminary survey. We randomly
+assigned them to learn about the 5th percentile of groups, which scored
+2.6. (``Low Expectations'' treatment) or the 95th percentile of groups,
+which scored 6.4 (``High Expectations'' treatment). Participants then
+made a guess (unincentivized) about how many questions they think they
+answered correctly. The survey concluded with basic demographic
+questions.
+
+We then recruited 1,000 participants for Stage 2, placing them in the
+role of advisers. We began by informing them of the mathematics quiz
+that participants in the preliminary study and Stage 1 had completed,
+and informed them of the average score of all participants in the
+preliminary study. Advisers had to recommend whether an advisee should
+compete against the Low Performers or the High Performers (we used these
+terms in the survey). We anticipated that being told to compete against
+High Performers is more flattering and hence being told to compete
+against the Low Performers would be disappointing if one had expected to
+do well. Advisees could earn a bonus if their score was equal to or
+higher than that of a randomly selected member from their chosen group.
+Competing against the High Performers was more challenging, resulting in
+an average bonus of 50 cents, compared to 30 cents when competing
+against other groups.
+
+Like before, advisers were randomly assigned to one of two treatments.
+In the ``Baseline'' treatment, they only observed the score of the
+advisee on the mathematics quiz. In the ``Expectation'' treatment, they
+observed the score as well as the advisee's guess for how many questions
+they answered correctly. We want to emphasize that sice the outcome is
+determined only by the past score on the quiz, the advisee's guess is
+immaterial to which group they should compete against. Moreover, in
+neither treatment did they receive any demographic information about
+their advisee. Participants gave recommendations to 10 advisees, which
+unbeknownst to them were five men and five women matched to have
+identical performance on the test.\footnote{We made this decision to
+  account for the possibility of gender differences in performance.}
+They were informed that if their advice was shown to a participant who
+returned for the follow-up survey, they would receive the identical
+bonus as that participant. The survey then concluded with basic
+demographic questions.
+
+Finally, we invited participants from Stage 1 back for the follow-up
+survey. Following our preregistration, we kept the survey open for 7
+days. In total, 951 participants (481 men, 470 women) returned. The
+brief survey reminded them of the task they completed in Stage 1,
+informed them that other participants from Prolific had observed their
+real score and given them advice against which group to compete against,
+and finally were reminded them of how many questions they guessed they
+had answered correctly. Importantly, they were not informed of their
+true score or the score of the groups they could compete against.
+Participants then observed the advice from a randomly selected adviser
+and made their decision.
+
+\subsection{Results}\label{results-2}
+
+We begin by examining the performance of the Stage 1 participants.
+Because our treatment takes place after participants completed the
+mathematics quiz, we would not expect a difference in performance across
+the Low and High Expectations treatments. Indeed, the two groups scored
+no different from one another (4.79 and 4.55 for the Low Expectations
+and High Expectations treatments, respectively, \(t(998) = -1.64\),
+\(p = .102\)). The expectations treatment did, however, affect how well
+they thought they performed. Participants in the ``Low Expectations''
+treatment guessed a score of 4.79 vs.~4.42 in the High Expectations
+treatment (\(t(998) = 3.78\), \(p < .001\)), showing that the
+manipulation was successful, albeit small. Contrary to our expectations,
+we did find a gender difference in performance: men scored 5.02 on
+average, while women scored 4.33 (\(t(998) = -4.73\), \(p < .001\)).
+Consistent with this difference, men thought they answered more
+questions correctly than did women (4.75 vs 3.56, \(t(998) = -8.60\),
+\(p < .001\)). This difference, however, does not affect the
+interpretation of our findings, which will rely on an interaction of
+gender with an experimental treatment for Stage 2 participants.
+
+We define a measure of ``overconfidence'' as (Performance - Estimate).
+We observe that women underestimate their performance by 0.76 points,
+while men do so by only 0.27 points \(\Delta M = -0.49\), 95\% CI
+\([-0.73, -0.25]\), \(t(997.87) = -4.03\), \(p < .001\). Although
+neither gender is overconfident, men on average are more confident in
+their performance than are women, as we had expected.
+
+\begin{table}
+
+{\caption{{Column 1 displays the advice given to compete against a High
+Performance group based on whether the advisees were primed with low or
+high expectations and the expectation level shown to the advisor. Column
+2 displays the advice given to compete against a High Performance group
+based on the gender of the targets and the expectation level shown to
+the advisor. Column 3 displays the expected bonus of the advice received
+based on the gender of the targets and the expectation level shown to
+the advisor. All standard errors clustered at the level of the
+advisor.}{\label{tbl-study3regs}}}
+\vspace{-20pt}}
+
+\centering
+\begin{talltblr}[         %% tabularray outer open
+entry=none,label=none,
+note{}={+ p \num{< 0.1}, * p \num{< 0.05}, ** p \num{< 0.01}, *** p \num{< 0.001}},
+]                     %% tabularray outer close
+{                     %% tabularray inner open
+colspec={Q[]Q[]Q[]Q[]},
+column{2,3,4}={}{halign=c,},
+column{1}={}{halign=l,},
+hline{14}={1,2,3,4}{solid, black, 0.05em},
+}                     %% tabularray inner close
+\toprule
+& (1) & (2) & (3) \\ \midrule %% TinyTableHeader
+High Expectation   & \num{0.012}     &                 &                 \\
+& (\num{0.011})   &                 &                 \\
+Performance        & \num{0.128}***  &                 &                 \\
+& (\num{0.003})   &                 &                 \\
+Expectation Shown  &                  & \num{-0.034}*  & \num{0.000}    \\
+&                  & (\num{0.013})  & (\num{0.003})  \\
+Advisee Male       &                  & \num{0.002}    & \num{0.000}    \\
+&                  & (\num{0.005})  & (\num{0.001})  \\
+Expectation x Male &                  & \num{0.032}*** & \num{-0.005}** \\
+&                  & (\num{0.009})  & (\num{0.002})  \\
+Constant           & \num{-0.263}*** & \num{0.339}*** & \num{0.258}*** \\
+& (\num{0.015})   & (\num{0.010})  & (\num{0.002})  \\
+N                  & \num{5000}      & \num{10000}    & \num{10000}    \\
+\bottomrule
+\end{talltblr}
+
+\end{table}
+
+\begin{figure}
+
+\caption{\label{fig-study3genderdiff}Advisers observed real performance
+and the participants' estimated performance, but not their gender. As a
+result of their higher expectations, men (blue) were advised to compete
+against the high performance group more often than women (red). The grey
+line shows advice absent expectations, which did not differ by gender.}
+
+\centering{
+
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-study3genderdiff-1.pdf}}
+
 }
 
-p5 <- quantile(subgroup_averages$avg_score, probs = 0.05)
-p95 <- quantile(subgroup_averages$avg_score, probs = 0.95)
-
-sortedScore <- sort(study3_math50$Score, decreasing = TRUE)
-LP_lower <- sortedScore[50]
-LP_upper <- sortedScore[31]
-HP_lower <- sortedScore[20]
-HP_upper <- sortedScore[1]
-
-```
-
-We begin by first recruiting a sample of `r scales::comma(dim(study3_math50)[1])` participants from Prolific to complete a 10-question multiple choice mathematics quiz.
-The questions were taken from a paper-version of the ASVAB standardized exam, such that answers were not available online.
-Participants had five minutes to answer the quiz and were paid 10 cents for each correctly answered question.
-Like before, we define top 20 scores as "High Performers" and the bottom 20 scorers as the "Low Performers." On average, participants answered `r round(mean(study3_math50$Score),2)` questions correctly, High Performers scored between `r HP_lower` and `r HP_upper`, and Low Performers scored between `r LP_lower` and `r LP_upper`.
-In order to anchor the expectations of participants in our main experiment, we simulated 1,000 pairings of groups of five participants, with the 5<sup>th</sup> percentile of groups scoring an average of `r p5` and the 95 th percentile scoring an average of `r p95`.
-We report these averages to participants in the Low Expectations and High Expectations treatment, respectively.
-
-We then recruited `r scales::comma(dim(study3_time1All)[1])` participants for the role of advisees in Stage 1 of our main experiment.
-To arrive at a gender-balanced sample, we dropped the last two male participants to complete the survey, ending up with a sample of 500 men and 500 women ($M_{\text{Age}}$ = `r mean(study3_time1$Age)`).
-Participants completed the same 10-item mathematics quiz as the earlier participants and were informed that their performance would affect their bonus earnings in a follow-up stage to be conducted a few days later.
-After completing the quiz, we informed them of the average score of a group of five participants from the preliminary survey.
-We randomly assigned them to learn about the 5<sup>th</sup> percentile of groups, which scored `r p5`.
-("Low Expectations" treatment) or the 95<sup>th</sup> percentile of groups, which scored `r p95` ("High Expectations" treatment).
-Participants then made a guess (unincentivized) about how many questions they think they answered correctly.
-The survey concluded with basic demographic questions.
-
-We then recruited `r scales::comma(dim(study3_time2_giver)[1])` participants for Stage 2, placing them in the role of advisers.
-We began by informing them of the mathematics quiz that participants in the preliminary study and Stage 1 had completed, and informed them of the average score of all participants in the preliminary study.
-Advisers had to recommend whether an advisee should compete against the Low Performers or the High Performers (we used these terms in the survey).
-We anticipated that being told to compete against High Performers is more flattering and hence being told to compete against the Low Performers would be disappointing if one had expected to do well.
-Advisees could earn a bonus if their score was equal to or higher than that of a randomly selected member from their chosen group.
-Competing against the High Performers was more challenging, resulting in an average bonus of 50 cents, compared to 30 cents when competing against other groups.
-
-Like before, advisers were randomly assigned to one of two treatments.
-In the "Baseline" treatment, they only observed the score of the advisee on the mathematics quiz.
-In the "Expectation" treatment, they observed the score as well as the advisee's guess for how many questions they answered correctly.
-We want to emphasize that sice the outcome is determined only by the past score on the quiz, the advisee's guess is immaterial to which group they should compete against.
-Moreover, in neither treatment did they receive any demographic information about their advisee.
-Participants gave recommendations to 10 advisees, which unbeknownst to them were five men and five women matched to have identical performance on the test.[^2] They were informed that if their advice was shown to a participant who returned for the follow-up survey, they would receive the identical bonus as that participant.
-The survey then concluded with basic demographic questions.
-
-[^2]: We made this decision to account for the possibility of gender differences in performance.
-
-Finally, we invited participants from Stage 1 back for the follow-up survey.
-Following our preregistration, we kept the survey open for 7 days.
-In total, `r scales::comma(dim(study3_time3)[1])` participants (`r scales::comma(dim(study3_time3[study3_time3$Gender == 'Male',])[1])` men, `r scales::comma(dim(study3_time3[study3_time3$Gender == 'Female',])[1])` women) returned.
-The brief survey reminded them of the task they completed in Stage 1, informed them that other participants from Prolific had observed their real score and given them advice against which group to compete against, and finally were reminded them of how many questions they guessed they had answered correctly.
-Importantly, they were not informed of their true score or the score of the groups they could compete against.
-Participants then observed the advice from a randomly selected adviser and made their decision.
-
-## Results
-
-We begin by examining the performance of the Stage 1 participants.
-Because our treatment takes place after participants completed the mathematics quiz, we would not expect a difference in performance across the Low and High Expectations treatments.
-Indeed, the two groups scored no different from one another (`r round(mean(study3_time1[study3_time1$Condition == "Low",]$count),2)` and `r round(mean(study3_time1[study3_time1$Condition == "High",]$count),2)` for the Low Expectations and High Expectations treatments, respectively, `r papaja::apa_print(t.test(count ~ Condition, data = study3_time1, var.equal = T))$statistic`).
-The expectations treatment did, however, affect how well they thought they performed.
-Participants in the "Low Expectations" treatment guessed a score of `r round(mean(study3_time1[study3_time1$Condition == "Low",]$count),2)` vs.
-`r round(mean(study3_time1[study3_time1$Condition == "High",]$Guess),2)` in the High Expectations treatment (`r papaja::apa_print(t.test(Guess ~ Condition, data = study3_time1, var.equal = T))$statistic`), showing that the manipulation was successful, albeit small.
-Contrary to our expectations, we did find a gender difference in performance: men scored `r round(mean(study3_time1[study3_time1$Gender == "Male",]$count),2)` on average, while women scored `r round(mean(study3_time1[study3_time1$Gender == "Female",]$count),2)` (`r papaja::apa_print(t.test(count ~ Gender, data = study3_time1, var.equal = T))$statistic`).
-Consistent with this difference, men thought they answered more questions correctly than did women (`r round(mean(study3_time1[study3_time1$Gender == "Male",]$Guess),2)` vs `r round(mean(study3_time1[study3_time1$Gender == "Female",]$Guess),2)`, `r papaja::apa_print(t.test(Guess ~ Gender, data = study3_time1, var.equal = T))$statistic`).
-This difference, however, does not affect the interpretation of our findings, which will rely on an interaction of gender with an experimental treatment for Stage 2 participants.
-
-We define a measure of "overconfidence" as (Performance - Estimate).
-We observe that women underestimate their performance by 0.76 points, while men do so by only 0.27 points `r papaja::apa_print(t.test(overconfidence ~ Gender, data = study3_time1 %>% dplyr::mutate(overconfidence = Guess - count)))$full_result`.
-Although neither gender is overconfident, men on average are more confident in their performance than are women, as we had expected.
-
-```{r}
-#| label: tbl-study3regs
-#| tbl-cap: "Column 1 displays the advice given to compete against a High Performance group based on whether the advisees were primed with low or high expectations and the expectation level shown to the advisor.
-Column 2 displays the advice given to compete against a High Performance group based on the gender of the targets and the expectation level shown to the advisor.
-Column 3 displays the expected bonus of the advice received based on the gender of the targets and the expectation level shown to the advisor.
-All standard errors clustered at the level of the advisor."
-
-study3_advice <- study3_advice %>% dplyr::mutate(Treatment = factor(Treatment, levels = c('Low', 'High'))) %>%
-  dplyr::mutate(ExpShow = ifelse(Condition == 'E',1,0))
-
-modelsummary::modelsummary(list(`(1)` = lm(Advice ~ Treatment + Performance , data = study3_advice %>% dplyr::filter(ExpShow == 1)),
-                                `(2)` = lm(Advice ~ ExpShow*Gender , data = study3_advice),
-                                `(3)` = lm(ExpectedBonus ~ ExpShow*Gender, data = study3_advice)),
-                           vcov = c(~GiverID, ~GiverID,~GiverID),
-                            coef_map = c("TreatmentHigh" = "High Expectation",
-                                         "Performance" = "Performance",
-                                         "ExpShow" = "Expectation Shown",
-                                        "GenderMale" = "Advisee Male",
-                                        "ExpShow:GenderMale" = "Expectation x Male",
-                                        "(Intercept)" = "Constant"),
-                           stars = T,
-                           gof_map = list(list('raw' = 'nobs', 'clean' = 'N', 'fmt' = 0)))
-
-```
-
-```{r}
-#| label: fig-study3genderdiff
-#| fig-cap: "Advisers observed real performance and the participants' estimated performance, but not their gender.
-As a result of their higher expectations, men (blue) were advised to compete against the high performance group more often than women (red).
-The grey line shows advice absent expectations, which did not differ by gender."
-
-library(dplyr)
-library(ggplot2)
-
-# Calculate averages for the performance, grouped by condition and gender
-ProbHG <- study3_advice %>%  
-  group_by(Condition, Performance, Gender) %>%  
-  summarise(avg_hardGroup = mean(Advice), .groups = 'drop')
-
-# Create a data frame for the NONE condition as the baseline
-baseline <- ProbHG %>%  
-  filter(Condition == "None") %>%  
-  select(Performance, baseline_avg = avg_hardGroup)
-
-# Merge with the original data to get comparison values
-comparison_data <- ProbHG %>%  
-  filter(Condition != "None") %>%  
-  left_join(baseline, by = "Performance") %>%  
-  mutate(diff = avg_hardGroup - baseline_avg)  # Calculate the difference
-
-# Create a scatter plot comparing conditions with NONE as baseline
-ggplot() +
-  # Step lines for the NONE condition
-  geom_segment(data = baseline,
-               aes(x = Performance, 
-                   xend = lead(Performance, 1),  # Create horizontal lines to the next performance point
-                   y = baseline_avg, 
-                   yend = baseline_avg,
-                   linetype = "None"), 
-               color = "grey70", size = 0.5, 
-               na.rm = TRUE,
-               show.legend = TRUE) + 
-  geom_point(data = comparison_data %>% filter(Gender == "Male"), 
-             aes(x = Performance + 0.5, y = avg_hardGroup, shape = Gender, color = Gender), 
-             size = 4) +  # Males with an offset to the left
-  geom_point(data = comparison_data %>% filter(Gender == "Female"), 
-             aes(x = Performance + 0.5, y = avg_hardGroup, shape = Gender, color = Gender), 
-             size = 4) +  # Females with an offset to the right
-  scale_shape_manual(values = c(16, 17), labels = c("Female", "Male")) +  # Circle for Females, Triangle for Males
-  scale_color_manual(values = c( "#FF7F3E","#2A629A"), 
-                     labels = c("Female", "Male")) +  
-  scale_y_continuous(name = "P(Compete Against High Performance)",
-                     labels = scales::percent,
-                     limits = c(0, 1.1),
-                     breaks = c(0,1)) +  # Set limits for y-axis
-  scale_x_continuous(name = "Performance",
-                     limits = c(0, 11),expand = c(0, 0), 
-                     breaks = seq(0, 10, 1)) +  
-  theme_bw() +  
-  theme(panel.grid = element_blank(), 
-        panel.border = element_blank(), 
-        axis.line = element_line(colour = "grey"), 
-        legend.position = "bottom", 
-        legend.title = element_blank(), 
-        legend.key.size = unit(1.2, "lines"), 
-        legend.text = element_text(size = 12), 
-        plot.title = element_text(hjust = 0.5, size = 20))
-
-```
-
-Next, we examine whether advisers took the advisee's expectations into account.
-Column 1 of @tbl-study3regs reports a linear probability model on advising to compete against the High Performer group for advisers in the "Expectations" treatment, controlling for the true performance of the advisee.
-Because each adviser made ten recommendations, we cluster standard errors at the adviser level.
-However, contrary to our expectations, we do not see a significant effect of the expectations treatment.
-This may be because the induced difference in expectations was too small.
-
-However, recall that men were more confident in their performance than were women.
-Our theory thus predicts that showing expectations should lead to more flattering advice (i.e., a recommendation to compete against the High Performer group) for men than for women.
-We report a linear probability model with advice to compete against the high group as the outcome measure, and the advisee's gender, whether expectations were shown to the adviser, and the interaction of the two in Column 2 of @tbl-study3regs.
-As predicted, we find a significant interaction effect: men are more likely to be advised to compete against the High Performers when expectations are shown than when they are hidden ($p < 0.001$).
-We show this result graphically in @fig-study3genderdiff.
-
-To examine the quality of advice, we computed the expected bonus earnings for someone who followed the recommendations.
-For example, if an adviser suggested competing against the High Performer group, we matched the advisee against all 20 members of that group and determined how often their score matched or exceeded that of the member.
-We then multiplied this number by the respective bonus earnings (50 cents and 30 cents for the High and Low Performer group, respectively).
-To see if including expectations leads to worse advise for men, we report a linear probability model with the experimental treatment of the adviser, the gender of the advisee, and their interaction in Column 3 of @tbl-study3regs.
-Displaying expectations led men to be advised to compete against the High Performer group more often, and this advise turned out to be bad: men receive worse advise than do women when expectations are displayed, but not in their absence.[^3]
-
-[^3]: This analysis was not preregistered, and we note here that the reduction in expected earnings is small.
-However, it is interesting that expectations have a negative effect for men who underestimate their performance on average.
-One possibility is that advisers suggest the High Performer group more often than is optimal.
-We return to the possibility that advice is overall biased to be flattering in Study 2.
-
-```{r}
-#| label: tbl-study3time3
-#| tbl-cap: "Column 1 displays the actual bonus based on the performance and whether the participant is primed with high expectations.
-Column 2 displays the actual bonus based on the performance and gender of the participant.
-Columns 3 and 4 display the chance of adopting the advice based on the gender of the participants, whether the advisee sees expectations, and whether the advice is to compete against high performers.
-The former considers only the main effect, while the latter also includes the interactive effect."
-
-study3_time3 <- study3_time3 %>% dplyr::mutate(AdviseeCondition = factor(AdviseeCondition, levels = c('Low', 'High'))) %>%
-     dplyr::mutate(Adopt = ifelse(Bet == Advice,1,0))
-
-modelsummary::modelsummary(list(`(1)` = lm(bonus ~ AdviseeCondition + AdviseeScore, data = study3_time3 %>%
-                                             dplyr::filter(GiverCondition == 1)),
-                                `(2)` = lm(bonus ~ Gender + AdviseeScore, data = study3_time3 %>%
-                                             dplyr::filter(GiverCondition == 1)),
-                                `(3)` = lm(Adopt ~ Gender + GiverCondition + Advice, data = study3_time3),
-                                `(4)` = lm(Adopt ~ Gender + GiverCondition + Advice + Gender*GiverCondition + GiverCondition*Advice + Gender*Advice, data = study3_time3)),
-                           vcov = c("classical", "classical","classical","classical"),
-                            coef_map = c("AdviseeScore" = "Performance",
-                                         "AdviseeConditionHigh" = "High Expectation",
-                                        "GenderMale" = "Advisee Male",
-                                        "GenderMale:GiverCondition" = "Expectation x Male",
-                                        "GiverCondition" = "Expectation Shown",
-                                        "Advice1" = "Advice: High Performer",
-                                        "GenderMale:Advice1" = "Advice: High Performer x Male",
-                                        "GiverCondition:Advice1" = "Expectation x Advice: High Performer",
-                                        "(Intercept)" = "Constant"),
-                           stars = T,
-                           gof_map = list(list('raw' = 'nobs', 'clean' = 'N', 'fmt' = 0)))
-
-```
-
-To determine whether flattering advice is truly costly, however, we need to examine the outcome of the advisees.
-In particular, they could ignore flattering advice, recognizing it as such and thus failing to adhere to it.
-Align with our prediction, participants who were primed with high expectations earned less when their expectations were conveyed to the advisers, although this result is only directional (see Column 1 of @tbl-study3time3).
-Similarly, as shown in Column 2 of @tbl-study3time3, we also found that male participants received less reward when their expectations were presented, even when their performance was the same.
-These findings suggest that flattering advice is not without consequences.
-Furthermore, our research indicates that because males are more likely to follow such advice (see Column 4 of @tbl-study3time3), their tendency towards competition intensifies the cost of such advice.
-
-## Discussion
+\end{figure}%
+
+Next, we examine whether advisers took the advisee's expectations into
+account. Column 1 of Table~\ref{tbl-study3regs} reports a linear
+probability model on advising to compete against the High Performer
+group for advisers in the ``Expectations'' treatment, controlling for
+the true performance of the advisee. Because each adviser made ten
+recommendations, we cluster standard errors at the adviser level.
+However, contrary to our expectations, we do not see a significant
+effect of the expectations treatment. This may be because the induced
+difference in expectations was too small.
+
+However, recall that men were more confident in their performance than
+were women. Our theory thus predicts that showing expectations should
+lead to more flattering advice (i.e., a recommendation to compete
+against the High Performer group) for men than for women. We report a
+linear probability model with advice to compete against the high group
+as the outcome measure, and the advisee's gender, whether expectations
+were shown to the adviser, and the interaction of the two in Column 2 of
+Table~\ref{tbl-study3regs}. As predicted, we find a significant
+interaction effect: men are more likely to be advised to compete against
+the High Performers when expectations are shown than when they are
+hidden (\(p < 0.001\)). We show this result graphically in
+Figure~\ref{fig-study3genderdiff}.
+
+To examine the quality of advice, we computed the expected bonus
+earnings for someone who followed the recommendations. For example, if
+an adviser suggested competing against the High Performer group, we
+matched the advisee against all 20 members of that group and determined
+how often their score matched or exceeded that of the member. We then
+multiplied this number by the respective bonus earnings (50 cents and 30
+cents for the High and Low Performer group, respectively). To see if
+including expectations leads to worse advise for men, we report a linear
+probability model with the experimental treatment of the adviser, the
+gender of the advisee, and their interaction in Column 3 of
+Table~\ref{tbl-study3regs}. Displaying expectations led men to be
+advised to compete against the High Performer group more often, and this
+advise turned out to be bad: men receive worse advise than do women when
+expectations are displayed, but not in their absence.\footnote{This
+  analysis was not preregistered, and we note here that the reduction in
+  expected earnings is small. However, it is interesting that
+  expectations have a negative effect for men who underestimate their
+  performance on average. One possibility is that advisers suggest the
+  High Performer group more often than is optimal. We return to the
+  possibility that advice is overall biased to be flattering in Study 2.}
+
+\begin{table}
+
+{\caption{{Column 1 displays the actual bonus based on the performance
+and whether the participant is primed with high expectations. Column 2
+displays the actual bonus based on the performance and gender of the
+participant. Columns 3 and 4 display the chance of adopting the advice
+based on the gender of the participants, whether the advisee sees
+expectations, and whether the advice is to compete against high
+performers. The former considers only the main effect, while the latter
+also includes the interactive effect.}{\label{tbl-study3time3}}}
+\vspace{-20pt}}
+
+\centering
+\begin{talltblr}[         %% tabularray outer open
+entry=none,label=none,
+note{}={+ p \num{< 0.1}, * p \num{< 0.05}, ** p \num{< 0.01}, *** p \num{< 0.001}},
+]                     %% tabularray outer close
+{                     %% tabularray inner open
+colspec={Q[]Q[]Q[]Q[]Q[]},
+column{2,3,4,5}={}{halign=c,},
+column{1}={}{halign=l,},
+hline{20}={1,2,3,4,5}{solid, black, 0.05em},
+}                     %% tabularray inner close
+\toprule
+& (1) & (2) & (3) & (4) \\ \midrule %% TinyTableHeader
+Performance                          & \num{0.038}*** & \num{0.039}*** &                  &                  \\
+& (\num{0.003})  & (\num{0.003})  &                  &                  \\
+High Expectation                     & \num{-0.020}   &                 &                  &                  \\
+& (\num{0.013})  &                 &                  &                  \\
+Advisee Male                         &                 & \num{-0.002}   & \num{-0.045}+   & \num{-0.144}*** \\
+&                 & (\num{0.013})  & (\num{0.026})   & (\num{0.041})   \\
+Expectation x Male                   &                 &                 &                  & \num{0.113}*    \\
+&                 &                 &                  & (\num{0.053})   \\
+Expectation Shown                    &                 &                 & \num{-0.002}    & \num{-0.057}    \\
+&                 &                 & (\num{0.026})   & (\num{0.040})   \\
+Advice: High Performer               &                 &                 & \num{-0.138}*** & \num{-0.207}*** \\
+&                 &                 & (\num{0.028})   & (\num{0.051})   \\
+Advice: High Performer x Male        &                 &                 &                  & \num{0.131}*    \\
+&                 &                 &                  & (\num{0.056})   \\
+Expectation x Advice: High Performer &                 &                 &                  & \num{-0.009}    \\
+&                 &                 &                  & (\num{0.056})   \\
+Constant                             & \num{0.087}*** & \num{0.076}*** & \num{0.857}***  & \num{0.906}***  \\
+& (\num{0.016})  & (\num{0.015})  & (\num{0.024})   & (\num{0.030})   \\
+N                                    & \num{483}      & \num{483}      & \num{951}       & \num{951}       \\
+\bottomrule
+\end{talltblr}
+
+\end{table}
+
+To determine whether flattering advice is truly costly, however, we need
+to examine the outcome of the advisees. In particular, they could ignore
+flattering advice, recognizing it as such and thus failing to adhere to
+it. Align with our prediction, participants who were primed with high
+expectations earned less when their expectations were conveyed to the
+advisers, although this result is only directional (see Column 1 of
+Table~\ref{tbl-study3time3}). Similarly, as shown in Column 2 of
+Table~\ref{tbl-study3time3}, we also found that male participants
+received less reward when their expectations were presented, even when
+their performance was the same. These findings suggest that flattering
+advice is not without consequences. Furthermore, our research indicates
+that because males are more likely to follow such advice (see Column 4
+of Table~\ref{tbl-study3time3}), their tendency towards competition
+intensifies the cost of such advice.
+
+\subsection{Discussion}\label{discussion-2}
 
 We found supportive evidence for our argument in a different domain.
-Advisors tend to consider advisees' self-expectations and match their advice accordingly, aiming to avoid disappointment.
-Consistent with the confidence gap narrative, men tend to underestimate their mathematics test scores less than women.
-When these expectations are displayed to advisors, they are more likely to advise men to compete against high performers.
-Notably, this turns out to be poor advice: men whose advisors were aware of their expectations received worse advice.
-Our findings suggest that men with the same scores as their female counterparts ended up earning less, although this result is only directional.
-This discrepancy may be due to men receiving more favorable advice, being more likely to follow it, and ultimately facing worse outcomes.
-
-<!-- David: One more sentence about the earnings difference here, which does not -->
-
-<!-- differ significantly. And one sentence about the new analysis of whether -->
-
-<!-- people follow the advice or not. -->
-
-# General Discussion
+Advisors tend to consider advisees' self-expectations and match their
+advice accordingly, aiming to avoid disappointment. Consistent with the
+confidence gap narrative, men tend to underestimate their mathematics
+test scores less than women. When these expectations are displayed to
+advisors, they are more likely to advise men to compete against high
+performers. Notably, this turns out to be poor advice: men whose
+advisors were aware of their expectations received worse advice. Our
+findings suggest that men with the same scores as their female
+counterparts ended up earning less, although this result is only
+directional. This discrepancy may be due to men receiving more favorable
+advice, being more likely to follow it, and ultimately facing worse
+outcomes.
+
+\section{General Discussion}\label{general-discussion}
 
 Advice has the potential to shape people's career and personal outcomes.
-Honest feedback, however, may be painful to learn if it falls short of one's expectations.
-As prior work notes, this may motivate people to avoid information and avoid seeking help [@Benabou2022; @Golman2017; @Jaroszewicz2022].
-We present evidence from two experiments that advisers are also cognizant of this cost.
-As a result, they present flattering advice that avoids disappointing the recipient, and correctly anticipate that this boosts how advisees perceive them.
-However, this flattering advice comes at a cost to advisees, who would do worse if they followed it blindly, as we show in Study 1.
-
-Moreover, a desire to avoid disappointment also means that advisers have to take into account the expectations of the advisee.
-We document that men are more optimistic about their performance than women are.
-As a result, they receive more flattering advice and are more likely to be told to aim higher.
-Notably, in the context of our experiment, this turns out to be bad advice ex post.
-
-Our findings have implications for organizational practice, where mentoring and advice-giving may take into account an employees' expectation.
-We document this as a novel source of gender bias.
-Organizations could reduce this bias by calibrating employees' expectations to reduce overconfidence.
-
-Participants in our experiment were paired anonymously.
-Even so, we document this desire to avoid disappointment.
-We anticipate that advice would be more flattering in face-to-face communication and without anonymity.
-Moreover, existing relationships might make it even more difficult for advisers to be honest.
-
-In our experiments, participants only received advice once and did not evaluate the adviser after observing the outcome of their decision.
-For example, advice that leads to bad outcomes may undermine the interpersonal benefits of flattery.
-Alternatively, people may still like the flattering advice and not fault the adviser for the bad outcome.
-Moreover, our setting involved only a single piece of advice on one task.
-Future research could examine whether people return to those who gave them flattering advice, or if they prefer someone who gave them the honest (but unpleasant) truth.
+Honest feedback, however, may be painful to learn if it falls short of
+one's expectations. As prior work notes, this may motivate people to
+avoid information and avoid seeking help (Bénabou et al., 2022; Golman
+et al., 2017; Jaroszewicz et al., 2021). We present evidence from two
+experiments that advisers are also cognizant of this cost. As a result,
+they present flattering advice that avoids disappointing the recipient,
+and correctly anticipate that this boosts how advisees perceive them.
+However, this flattering advice comes at a cost to advisees, who would
+do worse if they followed it blindly, as we show in Study 1.
+
+Moreover, a desire to avoid disappointment also means that advisers have
+to take into account the expectations of the advisee. We document that
+men are more optimistic about their performance than women are. As a
+result, they receive more flattering advice and are more likely to be
+told to aim higher. Notably, in the context of our experiment, this
+turns out to be bad advice ex post.
+
+Our findings have implications for organizational practice, where
+mentoring and advice-giving may take into account an employees'
+expectation. We document this as a novel source of gender bias.
+Organizations could reduce this bias by calibrating employees'
+expectations to reduce overconfidence.
+
+Participants in our experiment were paired anonymously. Even so, we
+document this desire to avoid disappointment. We anticipate that advice
+would be more flattering in face-to-face communication and without
+anonymity. Moreover, existing relationships might make it even more
+difficult for advisers to be honest.
+
+In our experiments, participants only received advice once and did not
+evaluate the adviser after observing the outcome of their decision. For
+example, advice that leads to bad outcomes may undermine the
+interpersonal benefits of flattery. Alternatively, people may still like
+the flattering advice and not fault the adviser for the bad outcome.
+Moreover, our setting involved only a single piece of advice on one
+task. Future research could examine whether people return to those who
+gave them flattering advice, or if they prefer someone who gave them the
+honest (but unpleasant) truth.
 
 Advice has long been studied from the perspective of the receiver.
-Similarly, research on belief utility has examined how recipients respond to the valence of the information they receive.
-Here, we show that advisers, too, take into account the psychological impact of the information they convey.
-They may have even greater motivations to avoid conveying bad news, because they incur the interpersonal costs of delivering unfavorable information without reaping the benefits from helping someone make a better choice.
-
-# References
-
-::: {#refs}
-:::
+Similarly, research on belief utility has examined how recipients
+respond to the valence of the information they receive. Here, we show
+that advisers, too, take into account the psychological impact of the
+information they convey. They may have even greater motivations to avoid
+conveying bad news, because they incur the interpersonal costs of
+delivering unfavorable information without reaping the benefits from
+helping someone make a better choice.
+
+\section{References}\label{references}
+
+\phantomsection\label{refs}
+\begin{CSLReferences}{1}{0}
+\bibitem[\citeproctext]{ref-Benabou2022}
+Bénabou, R., Jaroszewicz, A., \& Loewenstein, G. (2022). \emph{It
+{Hurts} to {Ask}}. National Bureau of Economic Research.
+
+\bibitem[\citeproctext]{ref-Fiske2007}
+Fiske, S. T., Cuddy, A. J., \& Glick, P. (2007). Universal dimensions of
+social cognition: Warmth and competence. \emph{Trends in Cognitive
+Sciences}, \emph{11}(2), 77--83.
+
+\bibitem[\citeproctext]{ref-Gino2007}
+Gino, F., \& Moore, D. A. (2007). Effects of task difficulty on use of
+advice. \emph{Journal of Behavioral Decision Making}, \emph{20}(1),
+21--35.
+
+\bibitem[\citeproctext]{ref-Golman2017}
+Golman, R., Hagmann, D., \& Loewenstein, G. (2017). Information
+avoidance. \emph{Journal of Economic Literature}, \emph{55}(1), 96--135.
+\url{https://doi.org/10.1257/jel.20151245}
+
+\bibitem[\citeproctext]{ref-Harvey1997}
+Harvey, N., \& Fischer, I. (1997). Taking advice: {Accepting} help,
+improving judgment, and sharing responsibility. \emph{Organizational
+Behavior and Human Decision Processes}, \emph{70}(2), 117--133.
+
+\bibitem[\citeproctext]{ref-Jaroszewicz2022}
+Jaroszewicz, A., Loewenstein, G., \& Bénabou, R. (2021). \emph{The pain
+of asking and being asked for informal help}.
+
+\bibitem[\citeproctext]{ref-John2019}
+John, L. K., Jeong, M., Gino, F., \& Huang, L. (2019). The
+self-presentational consequences of upholding one's stance in spite of
+the evidence. \emph{Organizational Behavior and Human Decision
+Processes}, \emph{154}, 1--14.
+
+\bibitem[\citeproctext]{ref-Loewenstein2018}
+Loewenstein, G., \& Molnar, A. (2018). The renaissance of belief-based
+utility in economics. \emph{Nature Human Behaviour}, \emph{2}(3),
+166--167.
+
+\bibitem[\citeproctext]{ref-Shalvi2019}
+Shalvi, S., Soraperra, I., Weele, J. J. van der, \& Villeval, M. C.
+(2019). \emph{Shooting the messenger? Supply and demand in markets for
+willful ignorance}.
+
+\bibitem[\citeproctext]{ref-Soll2009}
+Soll, J. B., \& Larrick, R. P. (2009). Strategies for revising judgment:
+How (and how well) people use others' opinions. \emph{Journal of
+Experimental Psychology: Learning, Memory, and Cognition}, \emph{35}(3),
+780.
+
+\end{CSLReferences}
+
+\end{document}

### 2025-01-10 manuscript/manuscript.qmd
Add citations to the first paragraph.

@@
     prefer-html: true
+editor: 
+  markdown: 
+    wrap: 72
 ---
@@
 
-Career trajectories for men and women often differ substantially, even among those with similar qualifications.
-One source of such differences may be the advice that people receive.
-Prior work has documented that men receive more aspirational advice and women more risk-averse advice, which may explain why women are less likely to apply for and ultimately obtain more rewarding positions (Kanze et al., 2018).
-Research on gender discrimination has focused on the role of unconscious bias (Greenwald et al., 2009; Greenwald & Banaji, 1995), but interventions that try to reduce this bias have been largely unsuccessful (Chang et al., 2019; Paluck & Green, 2009).
-Recent work has proposed cognitive, rather than unconscious, biases that can lead to gender discrimination through the formation of false beliefs (Hagmann et al., 2024).
-Here, we propose a novel source of differences in advice by drawing on recent work on belief-based utility, expectation-based reference points (Köszegi, 2006; Kőszegi & Rabin, 2009), and the hedonic consequences of information (Golman et al., 2017).
-
-Advice figures prominently in workplace and personal decision-making, shaping choices about promotions, career paths, and everyday dilemmas [@Gino2007; @Harvey1997; @Soll2009].
-Its fundamental premise is to improve outcomes by enabling decision-makers to learn from others' expertise.
-However, while honest advice can lead to better decisions, it can also lead to disappointment when it suggests a desired outcome is unlikely to materialize.
-Advisers may be motivated to offer flattering recommendations that align with advisees' hopes, sparing them the disappointment of a more sobering forecast.
-
-Advice with the potential for disappointment appears in diverse organizational settings: supervisors deliver feedback on employee performance, lawyers convey likely outcomes of litigation to their clients, and academics offer thoughts on colleagues' manuscripts.
-Ideally, honest information would help people identify their strengths and weaknesses, make informed decisions about whether to pursue legal cases, and strengthen papers prior to submission to academic journals, thus improving long-term outcomes.
-In practice, however, interpersonal considerations may prevent candor.
-When someone's expectations are (too) high, an adviser might hesitate to deliver information that undermines it---particularly if doing so risks negative interpersonal repercussions.
-
-People often go to great lengths to avoid unpleasant information, deriving belief-based utility from maintaining favorable views of themselves [@Golman2017; @Ho2018; @Loewenstein2018].
-Moreover, they often prefer advisers who withhold bad news from them [@Shalvi2019] and punish those who communicate bad news [@John2019].
-Advisers, anticipating these preferences and consequences face a dilemma: Should they provide the accurate but potentially painful truth, or shade their recommendations to preserve the advisee's mood and the adviser's own standing?
-Advisers who fear they will be blamed or disliked for undermining someone's confidence may reasonably avoid candid feedback, particularly if they don't incur a cost when the advisee makes a mistake.
-
-In our experiments, however, advisees have no opportunity to punish the adviser, and advisers' financial incentives are linked to the decisions the advisees make.
-We propose that advisers nonetheless have reason to provide flattering advise because they recognize the psychological toll of disappointing news.
-As a result, they may similarly incur a hedonic cost for delivering unpleasant information that they anticipate may distress the advisee.
-Thus, even in the anonymized context of an online experiment, we hypothesize (and find) that advisers are relucant to disappoint advisees and advice is thus biased upward, away from accuracy and toward confirming advisees' priors.
-We show that this reduces the quality of advice—but that advisees nonetheless view flattering advisers more favorably.
-
-We present the results of three preregistered experiments in which participants are paired anonymously as advisers and advisees.
-Advisers are incentivized to offer accurate advice, with bonus earnings depending on the outcome of an advisee's decision.
-We study a setting in which advisees can communicate their expectations to an adviser, and experimentally manipulate whether advisers observe this expectation.
-Our design simulates organizational contexts where mentors and managers often have some sense of an employee's confidence or aspirations and thus could adjust their feedback to avoid disappointing them.
-Interpersonal considerations would likely be stronger in situations in which the adviser and advisee have an existing relationship and when the advice is delivered face-to-face.
-Moreover, advisers usually do not suffer any direct costs when their flattering advice leads to a poor outcome for the recipient, particularly when it is not clear what would have happened under a counterfactual.\^\[In some cases, however, repeated interaction might also increase incentives for honest feedback.
-Someone who is known to persistently give overoptimistic advice may be viewed as less trustworthy in the long run.\]
-
-In Study 1, we nudge advisees into a preference for competing against either a group of top-performers or a group of low-performers, through the use of a default option.
-Advisers who observe the actual performance of advisees and therefore have the relevant information needed to make a recommendation nonetheless take into account the initial preference when recommending which group they should compete against.
-In Study 2, we ask advisees to upload photos of themselves and advisers rank them on their attractiveness.
-Advisers then recommend which rank the advisee should bet on, receiving an incentive either for the advisee's accuracy or for being evaluated favorably.
-Both groups of advisers recommend a rank that is more attractive than what they themselves have evaluated the advisee, and those incentivized for likability further inflate the ranking.
-Advisees evaluate advisers more favorably when they recommend betting on a more attractive rank, including viewing them as more trustworthy.
-
-In Study 3, we examine a setting in which participants report their expected performance on a mathematics quiz.
-Advisers observe the test-taker's true score and, in one treatment, the score they guessed they would receive.
-They then recommend whether the advisee should compete against a group of high performers or low performers.
-Importantly, this "competition" is based on the past performance observed by the adviser and thus the advisee's expectation does not provide instrumental information.
-However, we find that (1) men expect to perform better than women, given identical performance, and (2) advisers take these expectations into account.
-As a result, when expectations (but not gender) are known to advisers, the advice given to men and women differs, and men are more often advised to compete against the group of high performers.
-Notably, this leads to worse advice for men than for women.
+Career trajectories for men and women often differ substantially, even
+among those with similar qualifications. One source of such differences
+may be the advice that people receive. Prior work has documented that
+men receive more aspirational advice and women more risk-averse advice,
+which may explain why women are less likely to apply for and ultimately
+obtain more rewarding positions [@Kanze2018]. Research on gender
+discrimination has focused on the role of unconscious bias
+[@Greenwald2009; @Greenwald1995], but interventions that try to reduce
+this bias have been largely unsuccessful [@Chang2019; @Paluck2009].
+Recent work has proposed cognitive, rather than unconscious, biases that
+can lead to gender discrimination through the formation of false beliefs
+[@Hagmann2024]. Here, we propose a novel source of differences in advice
+by drawing on recent work on belief-based utility, expectation-based
+reference points [@Koszegi2006; @Koszegi2009], and the hedonic
+consequences of information [@Golman2017].
+
+Advice figures prominently in workplace and personal decision-making,
+shaping choices about promotions, career paths, and everyday dilemmas
+[@Gino2007; @Harvey1997; @Soll2009]. Its fundamental premise is to
+improve outcomes by enabling decision-makers to learn from others'
+expertise. However, while honest advice can lead to better decisions, it
+can also lead to disappointment when it suggests a desired outcome is
+unlikely to materialize. Advisers may be motivated to offer flattering
+recommendations that align with advisees' hopes, sparing them the
+disappointment of a more sobering forecast.
+
+Advice with the potential for disappointment appears in diverse
+organizational settings: supervisors deliver feedback on employee
+performance, lawyers convey likely outcomes of litigation to their
+clients, and academics offer thoughts on colleagues' manuscripts.
+Ideally, honest information would help people identify their strengths
+and weaknesses, make informed decisions about whether to pursue legal
+cases, and strengthen papers prior to submission to academic journals,
+thus improving long-term outcomes. In practice, however, interpersonal
+considerations may prevent candor. When someone's expectations are (too)
+high, an adviser might hesitate to deliver information that undermines
+it---particularly if doing so risks negative interpersonal
+repercussions.
+
+People often go to great lengths to avoid unpleasant information,
+deriving belief-based utility from maintaining favorable views of
+themselves [@Golman2017; @Ho2018; @Loewenstein2018]. Moreover, they
+often prefer advisers who withhold bad news from them [@Shalvi2019] and
+punish those who communicate bad news [@John2019]. Advisers,
+anticipating these preferences and consequences face a dilemma: Should
+they provide the accurate but potentially painful truth, or shade their
+recommendations to preserve the advisee's mood and the adviser's own
+standing? Advisers who fear they will be blamed or disliked for
+undermining someone's confidence may reasonably avoid candid feedback,
+particularly if they don't incur a cost when the advisee makes a
+mistake.
+
+In our experiments, however, advisees have no opportunity to punish the
+adviser, and advisers' financial incentives are linked to the decisions
+the advisees make. We propose that advisers nonetheless have reason to
+provide flattering advise because they recognize the psychological toll
+of disappointing news. As a result, they may similarly incur a hedonic
+cost for delivering unpleasant information that they anticipate may
+distress the advisee. Thus, even in the anonymized context of an online
+experiment, we hypothesize (and find) that advisers are relucant to
+disappoint advisees and advice is thus biased upward, away from accuracy
+and toward confirming advisees' priors. We show that this reduces the
+quality of advice—but that advisees nonetheless view flattering advisers
+more favorably.
+
+We present the results of three preregistered experiments in which
+participants are paired anonymously as advisers and advisees. Advisers
+are incentivized to offer accurate advice, with bonus earnings depending
+on the outcome of an advisee's decision. We study a setting in which
+advisees can communicate their expectations to an adviser, and
+experimentally manipulate whether advisers observe this expectation. Our
+design simulates organizational contexts where mentors and managers
+often have some sense of an employee's confidence or aspirations and
+thus could adjust their feedback to avoid disappointing them.
+Interpersonal considerations would likely be stronger in situations in
+which the adviser and advisee have an existing relationship and when the
+advice is delivered face-to-face. Moreover, advisers usually do not
+suffer any direct costs when their flattering advice leads to a poor
+outcome for the recipient, particularly when it is not clear what would
+have happened under a counterfactual.\^\[In some cases, however,
+repeated interaction might also increase incentives for honest feedback.
+Someone who is known to persistently give overoptimistic advice may be
+viewed as less trustworthy in the long run.\]
+
+In Study 1, we nudge advisees into a preference for competing against
+either a group of top-performers or a group of low-performers, through
+the use of a default option. Advisers who observe the actual performance
+of advisees and therefore have the relevant information needed to make a
+recommendation nonetheless take into account the initial preference when
+recommending which group they should compete against. In Study 2, we ask
+advisees to upload photos of themselves and advisers rank them on their
+attractiveness. Advisers then recommend which rank the advisee should
+bet on, receiving an incentive either for the advisee's accuracy or for
+being evaluated favorably. Both groups of advisers recommend a rank that
+is more attractive than what they themselves have evaluated the advisee,
+and those incentivized for likability further inflate the ranking.
+Advisees evaluate advisers more favorably when they recommend betting on
+a more attractive rank, including viewing them as more trustworthy.
+
+In Study 3, we examine a setting in which participants report their
+expected performance on a mathematics quiz. Advisers observe the
+test-taker's true score and, in one treatment, the score they guessed
+they would receive. They then recommend whether the advisee should
+compete against a group of high performers or low performers.
+Importantly, this "competition" is based on the past performance
+observed by the adviser and thus the advisee's expectation does not
+provide instrumental information. However, we find that (1) men expect
+to perform better than women, given identical performance, and (2)
+advisers take these expectations into account. As a result, when
+expectations (but not gender) are known to advisers, the advice given to
+men and women differs, and men are more often advised to compete against
+the group of high performers. Notably, this leads to worse advice for
+men than for women.
 
@@
 
-We report all manipulations, measures, and data exclusion in our experiments.
-The preregistration reports, screenshots of all experimental materials, and the analysis code to replicate all statistical analyses and figures are available on the Open Science Framework (<https://osf.io/8r3d4/?view_only=5ad7bafcd16b4d4ba08bb28b0e2bd02d>).
+We report all manipulations, measures, and data exclusion in our
+experiments. The preregistration reports, screenshots of all
+experimental materials, and the analysis code to replicate all
+statistical analyses and figures are available on the Open Science
+Framework
+(<https://osf.io/8r3d4/?view_only=5ad7bafcd16b4d4ba08bb28b0e2bd02d>).
 
@@
 
-We first examine whether advisers take into account the expectations of advisees when providing a recommendation.
-A group of participants ("Advisees") complete a quiz consisting of ten questions that draw on ego-relevant domains.
-They then express a non-binding preference to compete against a group of high performers or low performers on the same task, based on their past performance.
-We nudge participants towards picking either the low or the high performer group by selecting one of the two by default.
-A second group of participants ("Advisers") observe Advisees' score on the quiz and, in one treatment, also which group they had selected.
-We predicted that Advisees who were nudged toward the high performer group would be more likely to receive advice to compete against this high group when Advisers observed their non-binding choice.
+We first examine whether advisers take into account the expectations of
+advisees when providing a recommendation. A group of participants
+("Advisees") complete a quiz consisting of ten questions that draw on
+ego-relevant domains. They then express a non-binding preference to
+compete against a group of high performers or low performers on the same
+task, based on their past performance. We nudge participants towards
+picking either the low or the high performer group by selecting one of
+the two by default. A second group of participants ("Advisers") observe
+Advisees' score on the quiz and, in one treatment, also which group they
+had selected. We predicted that Advisees who were nudged toward the high
+performer group would be more likely to receive advice to compete
+against this high group when Advisers observed their non-binding choice.
 
@@
 
-In a preliminary stage, we recruited `r scales::comma(dim(study1_ability50)[1])` participants from Prolific and gave them five minutes to complete a quiz consisting of ten items.
-The quiz included word puzzles, identifying emotions from photos, and selecting the best responses for hypothetical scenarios.
-These questions were adapted from surveys that measure problem-solving, emotional intelligence, and communication skills---which we pre-tested as being important in modern society and hence where participants might have a stake in doing well.
-Participants received a bonus of five cents for each correctly answered question.
-We then ranked them based on their score and label the 20 participants with the lowest (highest) scores as the Low (High) Performer Group.
-
-Next, we recruited `r scales::comma(dim(study1_time1)[1])` participants for the role of Advisees.
-They completed the same 10-item quiz, also earning five cents for each correct answer.
-We then asked them to express a non-binding preference for whether they would like to compete against the High or Low Performer Group.
-We informed them that they would be invited back at a later date when they could make a binding decision and they could earn a bonus based on whether their score on this quiz was equal to or higher than a randomly selected member from their comparison group.
-If they picked the High Performer Group and had an equal or higher score than a randomly selected member of that group, they would earn a bonus of 50 cents.
-If they picked the Low Performer Group and outperformed a randomly selected member of that group, they could earn a bonus of 20 cents.
-If their score was lower in this comparison, they would not earn an additional bonus.
-We randomized which of the two groups (High or Low Performers) was selected by default, and Advisees were free to select the other group.
-They also made a guess as to their score, and the survey concluded with basic demographic questions.
-
-We then recruited `r scales::comma(dim(study1_time2_giver)[1])` participants for the role of Advisers, and the focal part of our experiment.
-They were informed of the ability quiz that the Advisees had completed, how the Low Performer Group and High Performer Groups were constructed, as well as the choice and incentives for the Advisees.
-We then asked Advisers to give advice to ten participants on which group they should compete against.
-Advisers were randomly assigned to one of two treatments.
-In the "Performance" treatment, they observed only the score of the other participant.
-In the "Performance + Expectation" treatment, they additionally observed the advisee's non-binding choice of which group to compete against.
-However, since the outcome was based solely on the past quiz score and advisers, but not advisees, know the score, this initial choice was not informative for the purpose of recommending competing against one group or the other.
-Advisers could earn the same bonus as one of the participants they had given advice to and who returned to make a decision.
-The survey concluded with basic demographic questions.
-
-Finally, we invited Advisees back for the follow-up survey.
-Following our preregistration, we kept the survey open for 7 days.
-In total, `r scales::comma(dim(study1_time3)[1])` Advisees returned.
-The short survey reminded them of the task they completed in the previous survey, informed them that other participants from Prolific had observed their real score and given them advice on which group to compete against, and finally reminded them of how many questions they guessed they had answered correctly.
-They were not informed of their true score or the score of the groups they could compete against.
-Participants then observed the advice from a randomly selected adviser and made their decision.
+In a preliminary stage, we recruited
+`r scales::comma(dim(study1_ability50)[1])` participants from Prolific
+and gave them five minutes to complete a quiz consisting of ten items.
+The quiz included word puzzles, identifying emotions from photos, and
+selecting the best responses for hypothetical scenarios. These questions
+were adapted from surveys that measure problem-solving, emotional
+intelligence, and communication skills---which we pre-tested as being
+important in modern society and hence where participants might have a
+stake in doing well. Participants received a bonus of five cents for
+each correctly answered question. We then ranked them based on their
+score and label the 20 participants with the lowest (highest) scores as
+the Low (High) Performer Group.
+
+Next, we recruited `r scales::comma(dim(study1_time1)[1])` participants
+for the role of Advisees. They completed the same 10-item quiz, also
+earning five cents for each correct answer. We then asked them to
+express a non-binding preference for whether they would like to compete
+against the High or Low Performer Group. We informed them that they
+would be invited back at a later date when they could make a binding
+decision and they could earn a bonus based on whether their score on
+this quiz was equal to or higher than a randomly selected member from
+their comparison group. If they picked the High Performer Group and had
+an equal or higher score than a randomly selected member of that group,
+they would earn a bonus of 50 cents. If they picked the Low Performer
+Group and outperformed a randomly selected member of that group, they
+could earn a bonus of 20 cents. If their score was lower in this
+comparison, they would not earn an additional bonus. We randomized which
+of the two groups (High or Low Performers) was selected by default, and
+Advisees were free to select the other group. They also made a guess as
+to their score, and the survey concluded with basic demographic
+questions.
+
+We then recruited `r scales::comma(dim(study1_time2_giver)[1])`
+participants for the role of Advisers, and the focal part of our
+experiment. They were informed of the ability quiz that the Advisees had
+completed, how the Low Performer Group and High Performer Groups were
+constructed, as well as the choice and incentives for the Advisees. We
+then asked Advisers to give advice to ten participants on which group
+they should compete against. Advisers were randomly assigned to one of
+two treatments. In the "Performance" treatment, they observed only the
+score of the other participant. In the "Performance + Expectation"
+treatment, they additionally observed the advisee's non-binding choice
+of which group to compete against. However, since the outcome was based
+solely on the past quiz score and advisers, but not advisees, know the
+score, this initial choice was not informative for the purpose of
+recommending competing against one group or the other. Advisers could
+earn the same bonus as one of the participants they had given advice to
+and who returned to make a decision. The survey concluded with basic
+demographic questions.
+
+Finally, we invited Advisees back for the follow-up survey. Following
+our preregistration, we kept the survey open for 7 days. In total,
+`r scales::comma(dim(study1_time3)[1])` Advisees returned. The short
+survey reminded them of the task they completed in the previous survey,
+informed them that other participants from Prolific had observed their
+real score and given them advice on which group to compete against, and
+finally reminded them of how many questions they guessed they had
+answered correctly. They were not informed of their true score or the
+score of the groups they could compete against. Participants then
+observed the advice from a randomly selected adviser and made their
+decision.
 
@@
 We begin by examining the performance of the Stage 1 participants.
-Because our default treatment takes place after participants completed the ability quiz, we do not expect a difference in performance across the Low and High Default treatments.
-Indeed, the two groups scored no different from one another (`r round(mean(study1_time1[study1_time1$default == "Low",]$Score),2)` and `r round(mean(study1_time1[study1_time1$default == "High",]$Score),2)` for the Low Default and High Default treatments, respectively, `r papaja::apa_print(t.test(Score ~ default, data = study1_time1, var.equal = T))$statistic`).
-The default manipulation affected their initial choices.
-In the "Low Default" treatment, only `r round(mean(study1_time1[study1_time1$default == "Low",]$Guess),2)*100`% of participants initially preferred competing against the High Performer Group, compared to `r round(mean(study1_time1[study1_time1$default == "High",]$Guess),2)*100`% of participants who saw the High Performer Group highlighted ($\chi^2$(1, n = 201) = 36.62, p \< .001).
+Because our default treatment takes place after participants completed
+the ability quiz, we do not expect a difference in performance across
+the Low and High Default treatments. Indeed, the two groups scored no
+different from one another
+(`r round(mean(study1_time1[study1_time1$default == "Low",]$Score),2)`
+and
+`r round(mean(study1_time1[study1_time1$default == "High",]$Score),2)`
+for the Low Default and High Default treatments, respectively,
+`r papaja::apa_print(t.test(Score ~ default, data = study1_time1, var.equal = T))$statistic`).
+The default manipulation affected their initial choices. In the "Low
+Default" treatment, only
+`r round(mean(study1_time1[study1_time1$default == "Low",]$Guess),2)*100`%
+of participants initially preferred competing against the High Performer
+Group, compared to
+`r round(mean(study1_time1[study1_time1$default == "High",]$Guess),2)*100`%
+of participants who saw the High Performer Group highlighted
+($\chi^2$(1, n = 201) = 36.62, p \< .001).
 
@@
 
-We now examine whether advisers took the advisees' expectations into account.
-Recall that advisees who were defaulted to competing against the High Performer Group were indeed more likely to choose this group, which, from the advisers' perspective, could signal high confidence in their abilities.
-Our theory predicts that showing expectations should lead to more flattering advice--- specifically, a recommendation to compete against the High Performer Group--- for advisees with a high default choice compared to those with a low default choice.
-Column 1 of @tbl-study1regs reports a linear probability model with advice to compete against the high group as the outcome measure, incorporating the default choice advisees saw, whether expectations were shown to the adviser, and the interaction of the two.
-Because each adviser made ten recommendations, we cluster standard errors at the adviser level.
-As predicted, we find a marginally significant interaction effect: advisees with a default choice to compete against the High Performer Group (nudged to have high expectations, though not necessarily holding them) were more likely to receive advice to compete against stronger competitors when their expectations were shown compared to when they were hidden.
-We reported a linear probability model on advising to compete against the High Performer group for advisers in the "Expectations" treatment, controlling for the true performance of the advisee in Column 2 of @tbl-study1regs.
-We observe a significant main effect of the default treatment, where a high default increased the likelihood of receiving flattering advice.
-It is worth noting that, since only `r round(mean(study1_time1[study1_time1$default == "High",]$Guess),2)*100` % of advisees in the high default group actually stuck with their default choice, this represents a conservative test of the effect of high expectations on the likelihood of receiving flattering advice.
+We now examine whether advisers took the advisees' expectations into
+account. Recall that advisees who were defaulted to competing against
+the High Performer Group were indeed more likely to choose this group,
+which, from the advisers' perspective, could signal high confidence in
+their abilities. Our theory predicts that showing expectations should
+lead to more flattering advice--- specifically, a recommendation to
+compete against the High Performer Group--- for advisees with a high
+default choice compared to those with a low default choice. Column 1 of
+@tbl-study1regs reports a linear probability model with advice to
+compete against the high group as the outcome measure, incorporating the
+default choice advisees saw, whether expectations were shown to the
+adviser, and the interaction of the two. Because each adviser made ten
+recommendations, we cluster standard errors at the adviser level. As
+predicted, we find a marginally significant interaction effect: advisees
+with a default choice to compete against the High Performer Group
+(nudged to have high expectations, though not necessarily holding them)
+were more likely to receive advice to compete against stronger
+competitors when their expectations were shown compared to when they
+were hidden. We reported a linear probability model on advising to
+compete against the High Performer group for advisers in the
+"Expectations" treatment, controlling for the true performance of the
+advisee in Column 2 of @tbl-study1regs. We observe a significant main
+effect of the default treatment, where a high default increased the
+likelihood of receiving flattering advice. It is worth noting that,
+since only
+`r round(mean(study1_time1[study1_time1$default == "High",]$Guess),2)*100`
+% of advisees in the high default group actually stuck with their
+default choice, this represents a conservative test of the effect of
+high expectations on the likelihood of receiving flattering advice.
 
@@
 
-When the quality of a decision does not depend on someone's expectations, the adviser's awareness of the advisee's expectations should not influence the advice given.
-However, in line with our argument that advisers take into account the belief utility of the advisee and prefer to flatter rather than disappoint, we find that displaying the advisee's expectations does make a difference.
-Specifically, advisees who expressed a preference for stronger competitors were more likely to receive 'flattering' advice, encouraging them to pursue that option.
-One possible explanation for this finding is that, rather than trying to flatter, advisers may simply be telling advisees what they want to hear.
-In the next study, we aim to investigate the mechanism behind this discrepancy in advice-giving when expectations are revealed, exploring the question: Why do people give flattering advice?
+When the quality of a decision does not depend on someone's
+expectations, the adviser's awareness of the advisee's expectations
+should not influence the advice given. However, in line with our
+argument that advisers take into account the belief utility of the
+advisee and prefer to flatter rather than disappoint, we find that
+displaying the advisee's expectations does make a difference.
+Specifically, advisees who expressed a preference for stronger
+competitors were more likely to receive 'flattering' advice, encouraging
+them to pursue that option. One possible explanation for this finding is
+that, rather than trying to flatter, advisers may simply be telling
+advisees what they want to hear. In the next study, we aim to
+investigate the mechanism behind this discrepancy in advice-giving when
+expectations are revealed, exploring the question: Why do people give
+flattering advice?
 
@@
 
-So far, we have shown that displaying expectations influences the advice given.
-Specifically, advisers were more likely to recommend competing against a group of high performers to advisees with higher performance expectations compared to those without.
-We now directly test whether this effect is driven by interpersonal concerns.
-In particular, we explore whether more flattering advice stems from a desire to be liked, and whether advisees, in turn, like advisers more when they receive flattering advice.
-
-We conducted a three-stage experiment in which we experimentally manipulated the incentives for advisers.
-We began by inviting a group of advisees to upload photos of themselves ("selfies") and informed them that they would be rated on their attractiveness.
-We grouped them with nine other participants of the same gender and recruited participants of the opposing gender to rank them from most to least attractive and to provide advice.
-Specifically, we asked them to advise the participant they ranked as the 7th most attractive (4th least attractive) on what rank they should bet they were ranked by a larger group of raters.
-Advisers were randomly assigned to two treatments, receiving a bonus payment either if the advisee guessed their rank accurately or if the advisee evaluated the adviser as likeable as measured by an unincentivized scale response.
-We hypothesize that advisers who want to be liked by advisees will recommend that they bet on a lower rank, i.e.
+So far, we have shown that displaying expectations influences the advice
+given. Specifically, advisers were more likely to recommend competing
+against a group of high performers to advisees with higher performance
+expectations compared to those without. We now directly test whether
+this effect is driven by interpersonal concerns. In particular, we
+explore whether more flattering advice stems from a desire to be liked,
+and whether advisees, in turn, like advisers more when they receive
+flattering advice.
+
+We conducted a three-stage experiment in which we experimentally
+manipulated the incentives for advisers. We began by inviting a group of
+advisees to upload photos of themselves ("selfies") and informed them
+that they would be rated on their attractiveness. We grouped them with
+nine other participants of the same gender and recruited participants of
+the opposing gender to rank them from most to least attractive and to
+provide advice. Specifically, we asked them to advise the participant
+they ranked as the 7th most attractive (4th least attractive) on what
+rank they should bet they were ranked by a larger group of raters.
+Advisers were randomly assigned to two treatments, receiving a bonus
+payment either if the advisee guessed their rank accurately or if the
+advisee evaluated the adviser as likeable as measured by an
+unincentivized scale response. We hypothesize that advisers who want to
+be liked by advisees will recommend that they bet on a lower rank, i.e.
 that they are more attractive.
@@
 
-We recruited 300 participants from Prolific and, after asking demographic questions, invited them to upload photos of themselves (selfies) to be rated by other participants on attractiveness.
-`r scales::comma(dim(study2_time1[study2_time1$gender == 'Male',])[1])` men and `r scales::comma(dim(study2_time1[study2_time1$gender == 'Female',])[1])` women agreed to do so and uploaded pictures that adhered to our instructions (e.g., did not include other people).
-We selected the first 100 photos from women to arrive at a gender-balanced sample ($M_{\text{Age}}$ = `r mean(study2_time1_200$age)` years).
-Participants were informed that their selfies would be randomly grouped with those of nine other participants of their gender and ranked in terms of attractiveness by a group of new Prolific participants of the opposite gender.
-Lastly, they guessed their rank (unincentivized).
-
-Next, we recruited a new, gender-balanced sample for the role of advisers.
-`r scales::comma(dim(study2_time2)[1])` participants from Prolific ($M_{\text{Age}}$ = `r mean(study2_time2$age)` years; `r round(mean(study2_time2$gender == "Female")*100, 2)`% Female) started by providing demographic information, then were matched to a group of the opposite gender.
-They then ranked participants from most to least attractive using a drop-down menu next to each picture.
-Because of a limitation with the survey software, participants were able to select the same rank for multiple participants, rather than rank them uniquely.
-We remove 115 participants who did not follow instructions and provide a unique ranking.
-
-After submitting their ratings, they saw the photo of the participant they had ranked as the 7th most attractive (i.e., the 4th least attractive).
-They were reminded of the rank they had given to that person and informed that this participant would be invited back and could earn a \$1 bonus if they guessed their rank correctly.
-The rank was determined by the aggregate ratings of all participants who had ranked this group.
-Their task was to give advice to this participant about the rank they should bet on based on having observed all ten selfies and their own assessment.
-We randomly assigned participants to one of two incentivization schemes.
-In the "Accuracy" treatment, they received a bonus identical to the advisee: \$1 if they guessed their rank correctly.
-In the "Likeability" treatment, we informed them that they would be rated by the advisee on a 5-point Likert scale for how likeable they thought they were.
-Each point on the scale would translate to a bonus of 20 cents.
-They then selected a rank that they would recommend the advisee to bet on.
-
-Finally, we invited participants from Stage 1 and were ranked as the 7th attractive by at least one adviser (so that they received advice) back for the follow-up survey.
-Following our preregistration, we kept the survey open for 7 days.
-In total, `r scales::comma(dim(study2_time3)[1])` participants (`r scales::comma(dim(study2_time3[study2_time3$gender == 'Male',])[1])` men, `r scales::comma(dim(study2_time3[study2_time3$gender == 'Female',])[1])` women) returned.
-They were reminded of the selfie they uploaded in Stage 1 and informed that a group of 10 selfies, including theirs, had been rated by other participants from Prolific.
-They then saw the advice from a randomly selected adviser and made their estimate with a \$1 incentive for guessing accurately.
-They then saw the rank they had been advised to bet on one more time and were asked to rate the adviser's likability, warmth, friendliness, good-naturedness, trustworthiness, and sincerity on 5-point Likert scales (adapted from @Fiske2007).
+We recruited 300 participants from Prolific and, after asking
+demographic questions, invited them to upload photos of themselves
+(selfies) to be rated by other participants on attractiveness.
+`r scales::comma(dim(study2_time1[study2_time1$gender == 'Male',])[1])`
+men and
+`r scales::comma(dim(study2_time1[study2_time1$gender == 'Female',])[1])`
+women agreed to do so and uploaded pictures that adhered to our
+instructions (e.g., did not include other people). We selected the first
+100 photos from women to arrive at a gender-balanced sample
+($M_{\text{Age}}$ = `r mean(study2_time1_200$age)` years). Participants
+were informed that their selfies would be randomly grouped with those of
+nine other participants of their gender and ranked in terms of
+attractiveness by a group of new Prolific participants of the opposite
+gender. Lastly, they guessed their rank (unincentivized).
+
+Next, we recruited a new, gender-balanced sample for the role of
+advisers. `r scales::comma(dim(study2_time2)[1])` participants from
+Prolific ($M_{\text{Age}}$ = `r mean(study2_time2$age)` years;
+`r round(mean(study2_time2$gender == "Female")*100, 2)`% Female) started
+by providing demographic information, then were matched to a group of
+the opposite gender. They then ranked participants from most to least
+attractive using a drop-down menu next to each picture. Because of a
+limitation with the survey software, participants were able to select
+the same rank for multiple participants, rather than rank them uniquely.
+We remove 115 participants who did not follow instructions and provide a
+unique ranking.
+
+After submitting their ratings, they saw the photo of the participant
+they had ranked as the 7th most attractive (i.e., the 4th least
+attractive). They were reminded of the rank they had given to that
+person and informed that this participant would be invited back and
+could earn a \$1 bonus if they guessed their rank correctly. The rank
+was determined by the aggregate ratings of all participants who had
+ranked this group. Their task was to give advice to this participant
+about the rank they should bet on based on having observed all ten
+selfies and their own assessment. We randomly assigned participants to
+one of two incentivization schemes. In the "Accuracy" treatment, they
+received a bonus identical to the advisee: \$1 if they guessed their
+rank correctly. In the "Likeability" treatment, we informed them that
+they would be rated by the advisee on a 5-point Likert scale for how
+likeable they thought they were. Each point on the scale would translate
+to a bonus of 20 cents. They then selected a rank that they would
+recommend the advisee to bet on.
+
+Finally, we invited participants from Stage 1 and were ranked as the 7th
+attractive by at least one adviser (so that they received advice) back
+for the follow-up survey. Following our preregistration, we kept the
+survey open for 7 days. In total,
+`r scales::comma(dim(study2_time3)[1])` participants
+(`r scales::comma(dim(study2_time3[study2_time3$gender == 'Male',])[1])`
+men,
+`r scales::comma(dim(study2_time3[study2_time3$gender == 'Female',])[1])`
+women) returned. They were reminded of the selfie they uploaded in Stage
+1 and informed that a group of 10 selfies, including theirs, had been
+rated by other participants from Prolific. They then saw the advice from
+a randomly selected adviser and made their estimate with a \$1 incentive
+for guessing accurately. They then saw the rank they had been advised to
+bet on one more time and were asked to rate the adviser's likability,
+warmth, friendliness, good-naturedness, trustworthiness, and sincerity
+on 5-point Likert scales (adapted from @Fiske2007).
 
@@
 
-We begin by examining the prior beliefs of advisees who uploaded their selfies.
-On average, men guessed they ranked `r round(mean(study2_time1[study2_time1$gender == "Male",]$Guess),2)` in their group of 10 and women guessed that they ranked `r round(mean(study2_time1[study2_time1$gender == "Female",]$Guess),2)`.
-Participants overall underestimate their attractiveness relative to the benchmark average of 5.5.
-Moreover, women do so more than men `r papaja::apa_print(t.test(Guess ~ gender, data = study2_time1, var.equal = T))$statistic`.
-Notably, people's self-perceptions correlated strongly with the aggregate ratings of the advisers (`r round(cor(study2_finalRank$Guess, study2_finalRank$finalRank),2)`, `r papaja::apa_print(cor.test(study2_finalRank$Guess, study2_finalRank$finalRank))$statistic`).
-However, there was substantial heterogeneity in perceptions of attractiveness.
-Of the 200 participants, `r length(unique(study2_time2$Target))` were ranked as 7th most attractive by at least one adviser.
-On average, men in this subset estimated they were ranked `r round(mean(TargetsUnique[TargetsUnique$gender == 'Male',]$Guess),2)`th and women estimated they were ranked `r round(mean(TargetsUnique[TargetsUnique$gender == 'Female',]$Guess),2)`th (`r papaja::apa_print(t.test(Guess ~ gender, data = TargetsUnique, var.equal = T))$statistic`).
-
-Next, we turn our attention to the advisers (@fig-study2advice).
-In the Accuracy condition, those uploading selfies were advised to bet on rank `r round(mean(study2_time2[study2_time2$Condition == "Accurate",]$Advice),2)`.
-Notably, this is significantly more attractive than the 7th rank those advisers had themselves guessed just on the prior screen (`r papaja::apa_print(t.test(study2_time2[study2_time2$Condition == "Accurate",]$Advice, mu = 7, var.equal = T))$statistic`).
-This suggests that even when incentivized for accuracy, participants offered flattering advice.[^1] Importantly, and as predicted, we find that advisers in the Likeable treatment recommend betting on a lower rank, communicating that they think the participant in the selfie is more attractive (`r round(mean(study2_time2[study2_time2$Condition == "Likable",]$Advice),2)`, `r papaja::apa_print(t.test(Advice ~ Condition, data = study2_time2, var.equal = T))$statistic`).
-This suggests that advisers inferred that advising someone that they were more attractive would make the adviser appear more likeable and therefore provided advice that communicated a more favorable impression of the participants' attractiveness.
-The distribution shown in @fig-study2advice shows that participants do not simply tell participants that they are the most attractive person in the group.
-They may infer that flattering advise needs to be somewhat realistic to be believable.
-We return to this in the general discussion.
+We begin by examining the prior beliefs of advisees who uploaded their
+selfies. On average, men guessed they ranked
+`r round(mean(study2_time1[study2_time1$gender == "Male",]$Guess),2)` in
+their group of 10 and women guessed that they ranked
+`r round(mean(study2_time1[study2_time1$gender == "Female",]$Guess),2)`.
+Participants overall underestimate their attractiveness relative to the
+benchmark average of 5.5. Moreover, women do so more than men
+`r papaja::apa_print(t.test(Guess ~ gender, data = study2_time1, var.equal = T))$statistic`.
+Notably, people's self-perceptions correlated strongly with the
+aggregate ratings of the advisers
+(`r round(cor(study2_finalRank$Guess, study2_finalRank$finalRank),2)`,
+`r papaja::apa_print(cor.test(study2_finalRank$Guess, study2_finalRank$finalRank))$statistic`).
+However, there was substantial heterogeneity in perceptions of
+attractiveness. Of the 200 participants,
+`r length(unique(study2_time2$Target))` were ranked as 7th most
+attractive by at least one adviser. On average, men in this subset
+estimated they were ranked
+`r round(mean(TargetsUnique[TargetsUnique$gender == 'Male',]$Guess),2)`th
+and women estimated they were ranked
+`r round(mean(TargetsUnique[TargetsUnique$gender == 'Female',]$Guess),2)`th
+(`r papaja::apa_print(t.test(Guess ~ gender, data = TargetsUnique, var.equal = T))$statistic`).
+
+Next, we turn our attention to the advisers (@fig-study2advice). In the
+Accuracy condition, those uploading selfies were advised to bet on rank
+`r round(mean(study2_time2[study2_time2$Condition == "Accurate",]$Advice),2)`.
+Notably, this is significantly more attractive than the 7th rank those
+advisers had themselves guessed just on the prior screen
+(`r papaja::apa_print(t.test(study2_time2[study2_time2$Condition == "Accurate",]$Advice, mu = 7, var.equal = T))$statistic`).
+This suggests that even when incentivized for accuracy, participants
+offered flattering advice.[^1] Importantly, and as predicted, we find
+that advisers in the Likeable treatment recommend betting on a lower
+rank, communicating that they think the participant in the selfie is
+more attractive
+(`r round(mean(study2_time2[study2_time2$Condition == "Likable",]$Advice),2)`,
+`r papaja::apa_print(t.test(Advice ~ Condition, data = study2_time2, var.equal = T))$statistic`).
+This suggests that advisers inferred that advising someone that they
+were more attractive would make the adviser appear more likeable and
+therefore provided advice that communicated a more favorable impression
+of the participants' attractiveness. The distribution shown in
+@fig-study2advice shows that participants do not simply tell
+participants that they are the most attractive person in the group. They
+may infer that flattering advise needs to be somewhat realistic to be
+believable. We return to this in the general discussion.
 
 [^1]: This shading could be due to concerns of avoiding disappointment.
-However, it could also be that advisers are uncertain about the rankings they had given and make a recommendation that combines their own belief with a uniform prior.
+    However, it could also be that advisers are uncertain about the
+    rankings they had given and make a recommendation that combines
+    their own belief with a uniform prior.
 
@@
 
-Finally, we examine whether flattering advice indeed leads to more positive evaluations of advisers, or whether flattering advice is dismissed as insencere.
-Following our preregistration, we average the ratings on likeability, warmth, friendliness, and good-naturedness to create a scale of likeability ($\alpha$ = `r cronbach.alpha(study2_time3[, 5:8])$alpha`); and we create a scale of trustworthiness by averaging the ratings of trustworthiness and sincerity ($\alpha$ = `r cronbach.alpha(study2_time3[, 9:10])$alpha`).
+Finally, we examine whether flattering advice indeed leads to more
+positive evaluations of advisers, or whether flattering advice is
+dismissed as insencere. Following our preregistration, we average the
+ratings on likeability, warmth, friendliness, and good-naturedness to
+create a scale of likeability ($\alpha$ =
+`r cronbach.alpha(study2_time3[, 5:8])$alpha`); and we create a scale of
+trustworthiness by averaging the ratings of trustworthiness and
+sincerity ($\alpha$ = `r cronbach.alpha(study2_time3[, 9:10])$alpha`).
 
@@
 
-As seen in @fig-study2rating, we found that advisees who suggested that the advisee was more attractive (lower rank) were indeed rated as more likeable and warm (b = -0.109, p \< .05; b = -0.133, p \< .001, respectively; See Columns 1 and 2 of @tbl-study2regs).
-When using their self-expectations as a reference point, advisors who suggest a rank lower than that point are perceived as less likable and warm (see @fig-study2ratingByGroup).
-Interestingly, these benefits are not at the cost of being hypocritical; advisers who recommend a more favorable rank are viewed as no less trustworthy (Column 3 of @tbl-study2regs).
-
-We were not powered to do a comparison across the two experimental groups and did not preregister such a difference.
-Indeed, we find no difference in likeability and warmth across the two treatments (`r papaja::apa_print(t.test(likable ~ Condition, data = study2_time3, var.equal = T))$statistic`, and `r papaja::apa_print(t.test(warmAvg ~ Condition, data = study2_time3, var.equal = T))$statistic`, respectively).
-We also assess the quality of advice by measuring the discrepancy between the advised rank and the final rank.
-Our analysis revealed no significant difference between the two treatments in terms of how helpful the advice was for advisees in making accurate guesses, `r papaja::apa_print(t.test(accuracy ~ Condition, data = study2_time3, var.equal = T))$statistic`.
+As seen in @fig-study2rating, we found that advisees who suggested that
+the advisee was more attractive (lower rank) were indeed rated as more
+likeable and warm (b = -0.109, p \< .05; b = -0.133, p \< .001,
+respectively; See Columns 1 and 2 of @tbl-study2regs). When using their
+self-expectations as a reference point, advisors who suggest a rank
+lower than that point are perceived as less likable and warm (see
+@fig-study2ratingByGroup). Interestingly, these benefits are not at the
+cost of being hypocritical; advisers who recommend a more favorable rank
+are viewed as no less trustworthy (Column 3 of @tbl-study2regs).
+
+We were not powered to do a comparison across the two experimental
+groups and did not preregister such a difference. Indeed, we find no
+difference in likeability and warmth across the two treatments
+(`r papaja::apa_print(t.test(likable ~ Condition, data = study2_time3, var.equal = T))$statistic`,
+and
+`r papaja::apa_print(t.test(warmAvg ~ Condition, data = study2_time3, var.equal = T))$statistic`,
+respectively). We also assess the quality of advice by measuring the
+discrepancy between the advised rank and the final rank. Our analysis
+revealed no significant difference between the two treatments in terms
+of how helpful the advice was for advisees in making accurate guesses,
+`r papaja::apa_print(t.test(accuracy ~ Condition, data = study2_time3, var.equal = T))$statistic`.
 
@@
 
-In another context where advice communicates ego-relevant information (here, people's attractiveness), we find that the advice people give is contingent on their incentives.
-Specifically, when they get rewarded for being more likeable, they recommend that the advisee bet on a more favorable rank than when they are incentivized for accuracy.
-Importantly, advisees do not discount flattering advice and instead evaluate people who advise them to bet on a more attractive rank as warmer and more likeable.
-These gains to interpersonal perceptions do not come at the cost of trustworthiness, even when the advice is substantially inflated (e.g., a recommendation that the advisee is the most attractive in the group).
+In another context where advice communicates ego-relevant information
+(here, people's attractiveness), we find that the advice people give is
+contingent on their incentives. Specifically, when they get rewarded for
+being more likeable, they recommend that the advisee bet on a more
+favorable rank than when they are incentivized for accuracy.
+Importantly, advisees do not discount flattering advice and instead
+evaluate people who advise them to bet on a more attractive rank as
+warmer and more likeable. These gains to interpersonal perceptions do
+not come at the cost of trustworthiness, even when the advice is
+substantially inflated (e.g., a recommendation that the advisee is the
+most attractive in the group).
 
@@
 
-In Study 3, we replicate the main effect in a different ego-relevant domain: intelligence.
-The experimental design is conceptually identical to Study 1, but this time we utilize a more direct measure of expectation by asking participants to estimate their scores.
+In Study 3, we replicate the main effect in a different ego-relevant
+domain: intelligence. The experimental design is conceptually identical
+to Study 1, but this time we utilize a more direct measure of
+expectation by asking participants to estimate their scores.
 
 This three-stage experiment begins with measuring actual performance.
-Participants are then anchored to low or high performance expectations and asked to guess how many questions they answered correctly.
-As in previous studies, we recruit advisers who are presented with either just the advisee's true performance or both the true performance and the number of questions the advisee believes they answered correctly.
+Participants are then anchored to low or high performance expectations
+and asked to guess how many questions they answered correctly. As in
+previous studies, we recruit advisers who are presented with either just
+the advisee's true performance or both the true performance and the
+number of questions the advisee believes they answered correctly.
 Advisers are then asked to provide advice on choosing a competitor.
-Finally, we present the advice to the advisees and ask them to make their final choice.
-Our key hypotheses are: (1) advisees anchored to high expectations will be more likely to receive advice to compete against the high-performing group, and (2) men will be more likely than women to be advised to compete against the high-performing group when expectations are disclosed.
+Finally, we present the advice to the advisees and ask them to make
+their final choice. Our key hypotheses are: (1) advisees anchored to
+high expectations will be more likely to receive advice to compete
+against the high-performing group, and (2) men will be more likely than
+women to be advised to compete against the high-performing group when
+expectations are disclosed.
 
@@
 
-We begin by first recruiting a sample of `r scales::comma(dim(study3_math50)[1])` participants from Prolific to complete a 10-question multiple choice mathematics quiz.
-The questions were taken from a paper-version of the ASVAB standardized exam, such that answers were not available online.
-Participants had five minutes to answer the quiz and were paid 10 cents for each correctly answered question.
-Like before, we define top 20 scores as "High Performers" and the bottom 20 scorers as the "Low Performers." On average, participants answered `r round(mean(study3_math50$Score),2)` questions correctly, High Performers scored between `r HP_lower` and `r HP_upper`, and Low Performers scored between `r LP_lower` and `r LP_upper`.
-In order to anchor the expectations of participants in our main experiment, we simulated 1,000 pairings of groups of five participants, with the 5<sup>th</sup> percentile of groups scoring an average of `r p5` and the 95 th percentile scoring an average of `r p95`.
-We report these averages to participants in the Low Expectations and High Expectations treatment, respectively.
-
-We then recruited `r scales::comma(dim(study3_time1All)[1])` participants for the role of advisees in Stage 1 of our main experiment.
-To arrive at a gender-balanced sample, we dropped the last two male participants to complete the survey, ending up with a sample of 500 men and 500 women ($M_{\text{Age}}$ = `r mean(study3_time1$Age)`).
-Participants completed the same 10-item mathematics quiz as the earlier participants and were informed that their performance would affect their bonus earnings in a follow-up stage to be conducted a few days later.
-After completing the quiz, we informed them of the average score of a group of five participants from the preliminary survey.
-We randomly assigned them to learn about the 5<sup>th</sup> percentile of groups, which scored `r p5`.
-("Low Expectations" treatment) or the 95<sup>th</sup> percentile of groups, which scored `r p95` ("High Expectations" treatment).
-Participants then made a guess (unincentivized) about how many questions they think they answered correctly.
-The survey concluded with basic demographic questions.
-
-We then recruited `r scales::comma(dim(study3_time2_giver)[1])` participants for Stage 2, placing them in the role of advisers.
-We began by informing them of the mathematics quiz that participants in the preliminary study and Stage 1 had completed, and informed them of the average score of all participants in the preliminary study.
-Advisers had to recommend whether an advisee should compete against the Low Performers or the High Performers (we used these terms in the survey).
-We anticipated that being told to compete against High Performers is more flattering and hence being told to compete against the Low Performers would be disappointing if one had expected to do well.
-Advisees could earn a bonus if their score was equal to or higher than that of a randomly selected member from their chosen group.
-Competing against the High Performers was more challenging, resulting in an average bonus of 50 cents, compared to 30 cents when competing against other groups.
+We begin by first recruiting a sample of
+`r scales::comma(dim(study3_math50)[1])` participants from Prolific to
+complete a 10-question multiple choice mathematics quiz. The questions
+were taken from a paper-version of the ASVAB standardized exam, such
+that answers were not available online. Participants had five minutes to
+answer the quiz and were paid 10 cents for each correctly answered
+question. Like before, we define top 20 scores as "High Performers" and
+the bottom 20 scorers as the "Low Performers." On average, participants
+answered `r round(mean(study3_math50$Score),2)` questions correctly,
+High Performers scored between `r HP_lower` and `r HP_upper`, and Low
+Performers scored between `r LP_lower` and `r LP_upper`. In order to
+anchor the expectations of participants in our main experiment, we
+simulated 1,000 pairings of groups of five participants, with the
+5<sup>th</sup> percentile of groups scoring an average of `r p5` and the
+95 th percentile scoring an average of `r p95`. We report these averages
+to participants in the Low Expectations and High Expectations treatment,
+respectively.
+
+We then recruited `r scales::comma(dim(study3_time1All)[1])`
+participants for the role of advisees in Stage 1 of our main experiment.
+To arrive at a gender-balanced sample, we dropped the last two male
+participants to complete the survey, ending up with a sample of 500 men
+and 500 women ($M_{\text{Age}}$ = `r mean(study3_time1$Age)`).
+Participants completed the same 10-item mathematics quiz as the earlier
+participants and were informed that their performance would affect their
+bonus earnings in a follow-up stage to be conducted a few days later.
+After completing the quiz, we informed them of the average score of a
+group of five participants from the preliminary survey. We randomly
+assigned them to learn about the 5<sup>th</sup> percentile of groups,
+which scored `r p5`. ("Low Expectations" treatment) or the
+95<sup>th</sup> percentile of groups, which scored `r p95` ("High
+Expectations" treatment). Participants then made a guess
+(unincentivized) about how many questions they think they answered
+correctly. The survey concluded with basic demographic questions.
+
+We then recruited `r scales::comma(dim(study3_time2_giver)[1])`
+participants for Stage 2, placing them in the role of advisers. We began
+by informing them of the mathematics quiz that participants in the
+preliminary study and Stage 1 had completed, and informed them of the
+average score of all participants in the preliminary study. Advisers had
+to recommend whether an advisee should compete against the Low
+Performers or the High Performers (we used these terms in the survey).
+We anticipated that being told to compete against High Performers is
+more flattering and hence being told to compete against the Low
+Performers would be disappointing if one had expected to do well.
+Advisees could earn a bonus if their score was equal to or higher than
+that of a randomly selected member from their chosen group. Competing
+against the High Performers was more challenging, resulting in an
+average bonus of 50 cents, compared to 30 cents when competing against
+other groups.
 
 Like before, advisers were randomly assigned to one of two treatments.
-In the "Baseline" treatment, they only observed the score of the advisee on the mathematics quiz.
-In the "Expectation" treatment, they observed the score as well as the advisee's guess for how many questions they answered correctly.
-We want to emphasize that sice the outcome is determined only by the past score on the quiz, the advisee's guess is immaterial to which group they should compete against.
-Moreover, in neither treatment did they receive any demographic information about their advisee.
-Participants gave recommendations to 10 advisees, which unbeknownst to them were five men and five women matched to have identical performance on the test.[^2] They were informed that if their advice was shown to a participant who returned for the follow-up survey, they would receive the identical bonus as that participant.
-The survey then concluded with basic demographic questions.
-
-[^2]: We made this decision to account for the possibility of gender differences in performance.
-
-Finally, we invited participants from Stage 1 back for the follow-up survey.
-Following our preregistration, we kept the survey open for 7 days.
-In total, `r scales::comma(dim(study3_time3)[1])` participants (`r scales::comma(dim(study3_time3[study3_time3$Gender == 'Male',])[1])` men, `r scales::comma(dim(study3_time3[study3_time3$Gender == 'Female',])[1])` women) returned.
-The brief survey reminded them of the task they completed in Stage 1, informed them that other participants from Prolific had observed their real score and given them advice against which group to compete against, and finally were reminded them of how many questions they guessed they had answered correctly.
-Importantly, they were not informed of their true score or the score of the groups they could compete against.
-Participants then observed the advice from a randomly selected adviser and made their decision.
+In the "Baseline" treatment, they only observed the score of the advisee
+on the mathematics quiz. In the "Expectation" treatment, they observed
+the score as well as the advisee's guess for how many questions they
+answered correctly. We want to emphasize that sice the outcome is
+determined only by the past score on the quiz, the advisee's guess is
+immaterial to which group they should compete against. Moreover, in
+neither treatment did they receive any demographic information about
+their advisee. Participants gave recommendations to 10 advisees, which
+unbeknownst to them were five men and five women matched to have
+identical performance on the test.[^2] They were informed that if their
+advice was shown to a participant who returned for the follow-up survey,
+they would receive the identical bonus as that participant. The survey
+then concluded with basic demographic questions.
+
+[^2]: We made this decision to account for the possibility of gender
+    differences in performance.
+
+Finally, we invited participants from Stage 1 back for the follow-up
+survey. Following our preregistration, we kept the survey open for 7
+days. In total, `r scales::comma(dim(study3_time3)[1])` participants
+(`r scales::comma(dim(study3_time3[study3_time3$Gender == 'Male',])[1])`
+men,
+`r scales::comma(dim(study3_time3[study3_time3$Gender == 'Female',])[1])`
+women) returned. The brief survey reminded them of the task they
+completed in Stage 1, informed them that other participants from
+Prolific had observed their real score and given them advice against
+which group to compete against, and finally were reminded them of how
+many questions they guessed they had answered correctly. Importantly,
+they were not informed of their true score or the score of the groups
+they could compete against. Participants then observed the advice from a
+randomly selected adviser and made their decision.
 
@@
 We begin by examining the performance of the Stage 1 participants.
-Because our treatment takes place after participants completed the mathematics quiz, we would not expect a difference in performance across the Low and High Expectations treatments.
-Indeed, the two groups scored no different from one another (`r round(mean(study3_time1[study3_time1$Condition == "Low",]$count),2)` and `r round(mean(study3_time1[study3_time1$Condition == "High",]$count),2)` for the Low Expectations and High Expectations treatments, respectively, `r papaja::apa_print(t.test(count ~ Condition, data = study3_time1, var.equal = T))$statistic`).
-The expectations treatment did, however, affect how well they thought they performed.
-Participants in the "Low Expectations" treatment guessed a score of `r round(mean(study3_time1[study3_time1$Condition == "Low",]$count),2)` vs.
-`r round(mean(study3_time1[study3_time1$Condition == "High",]$Guess),2)` in the High Expectations treatment (`r papaja::apa_print(t.test(Guess ~ Condition, data = study3_time1, var.equal = T))$statistic`), showing that the manipulation was successful, albeit small.
-Contrary to our expectations, we did find a gender difference in performance: men scored `r round(mean(study3_time1[study3_time1$Gender == "Male",]$count),2)` on average, while women scored `r round(mean(study3_time1[study3_time1$Gender == "Female",]$count),2)` (`r papaja::apa_print(t.test(count ~ Gender, data = study3_time1, var.equal = T))$statistic`).
-Consistent with this difference, men thought they answered more questions correctly than did women (`r round(mean(study3_time1[study3_time1$Gender == "Male",]$Guess),2)` vs `r round(mean(study3_time1[study3_time1$Gender == "Female",]$Guess),2)`, `r papaja::apa_print(t.test(Guess ~ Gender, data = study3_time1, var.equal = T))$statistic`).
-This difference, however, does not affect the interpretation of our findings, which will rely on an interaction of gender with an experimental treatment for Stage 2 participants.
-
-We define a measure of "overconfidence" as (Performance - Estimate).
-We observe that women underestimate their performance by 0.76 points, while men do so by only 0.27 points `r papaja::apa_print(t.test(overconfidence ~ Gender, data = study3_time1 %>% dplyr::mutate(overconfidence = Guess - count)))$full_result`.
-Although neither gender is overconfident, men on average are more confident in their performance than are women, as we had expected.
+Because our treatment takes place after participants completed the
+mathematics quiz, we would not expect a difference in performance across
+the Low and High Expectations treatments. Indeed, the two groups scored
+no different from one another
+(`r round(mean(study3_time1[study3_time1$Condition == "Low",]$count),2)`
+and
+`r round(mean(study3_time1[study3_time1$Condition == "High",]$count),2)`
+for the Low Expectations and High Expectations treatments, respectively,
+`r papaja::apa_print(t.test(count ~ Condition, data = study3_time1, var.equal = T))$statistic`).
+The expectations treatment did, however, affect how well they thought
+they performed. Participants in the "Low Expectations" treatment guessed
+a score of
+`r round(mean(study3_time1[study3_time1$Condition == "Low",]$count),2)`
+vs.
+`r round(mean(study3_time1[study3_time1$Condition == "High",]$Guess),2)`
+in the High Expectations treatment
+(`r papaja::apa_print(t.test(Guess ~ Condition, data = study3_time1, var.equal = T))$statistic`),
+showing that the manipulation was successful, albeit small. Contrary to
+our expectations, we did find a gender difference in performance: men
+scored
+`r round(mean(study3_time1[study3_time1$Gender == "Male",]$count),2)` on
+average, while women scored
+`r round(mean(study3_time1[study3_time1$Gender == "Female",]$count),2)`
+(`r papaja::apa_print(t.test(count ~ Gender, data = study3_time1, var.equal = T))$statistic`).
+Consistent with this difference, men thought they answered more
+questions correctly than did women
+(`r round(mean(study3_time1[study3_time1$Gender == "Male",]$Guess),2)`
+vs
+`r round(mean(study3_time1[study3_time1$Gender == "Female",]$Guess),2)`,
+`r papaja::apa_print(t.test(Guess ~ Gender, data = study3_time1, var.equal = T))$statistic`).
+This difference, however, does not affect the interpretation of our
+findings, which will rely on an interaction of gender with an
+experimental treatment for Stage 2 participants.
+
+We define a measure of "overconfidence" as (Performance - Estimate). We
+observe that women underestimate their performance by 0.76 points, while
+men do so by only 0.27 points
+`r papaja::apa_print(t.test(overconfidence ~ Gender, data = study3_time1 %>% dplyr::mutate(overconfidence = Guess - count)))$full_result`.
+Although neither gender is overconfident, men on average are more
+confident in their performance than are women, as we had expected.
 
@@
 
-Next, we examine whether advisers took the advisee's expectations into account.
-Column 1 of @tbl-study3regs reports a linear probability model on advising to compete against the High Performer group for advisers in the "Expectations" treatment, controlling for the true performance of the advisee.
-Because each adviser made ten recommendations, we cluster standard errors at the adviser level.
-However, contrary to our expectations, we do not see a significant effect of the expectations treatment.
-This may be because the induced difference in expectations was too small.
-
-However, recall that men were more confident in their performance than were women.
-Our theory thus predicts that showing expectations should lead to more flattering advice (i.e., a recommendation to compete against the High Performer group) for men than for women.
-We report a linear probability model with advice to compete against the high group as the outcome measure, and the advisee's gender, whether expectations were shown to the adviser, and the interaction of the two in Column 2 of @tbl-study3regs.
-As predicted, we find a significant interaction effect: men are more likely to be advised to compete against the High Performers when expectations are shown than when they are hidden ($p < 0.001$).
-We show this result graphically in @fig-study3genderdiff.
-
-To examine the quality of advice, we computed the expected bonus earnings for someone who followed the recommendations.
-For example, if an adviser suggested competing against the High Performer group, we matched the advisee against all 20 members of that group and determined how often their score matched or exceeded that of the member.
-We then multiplied this number by the respective bonus earnings (50 cents and 30 cents for the High and Low Performer group, respectively).
-To see if including expectations leads to worse advise for men, we report a linear probability model with the experimental treatment of the adviser, the gender of the advisee, and their interaction in Column 3 of @tbl-study3regs.
-Displaying expectations led men to be advised to compete against the High Performer group more often, and this advise turned out to be bad: men receive worse advise than do women when expectations are displayed, but not in their absence.[^3]
-
-[^3]: This analysis was not preregistered, and we note here that the reduction in expected earnings is small.
-However, it is interesting that expectations have a negative effect for men who underestimate their performance on average.
-One possibility is that advisers suggest the High Performer group more often than is optimal.
-We return to the possibility that advice is overall biased to be flattering in Study 2.
+Next, we examine whether advisers took the advisee's expectations into
+account. Column 1 of @tbl-study3regs reports a linear probability model
+on advising to compete against the High Performer group for advisers in
+the "Expectations" treatment, controlling for the true performance of
+the advisee. Because each adviser made ten recommendations, we cluster
+standard errors at the adviser level. However, contrary to our
+expectations, we do not see a significant effect of the expectations
+treatment. This may be because the induced difference in expectations
+was too small.
+
+However, recall that men were more confident in their performance than
+were women. Our theory thus predicts that showing expectations should
+lead to more flattering advice (i.e., a recommendation to compete
+against the High Performer group) for men than for women. We report a
+linear probability model with advice to compete against the high group
+as the outcome measure, and the advisee's gender, whether expectations
+were shown to the adviser, and the interaction of the two in Column 2 of
+@tbl-study3regs. As predicted, we find a significant interaction effect:
+men are more likely to be advised to compete against the High Performers
+when expectations are shown than when they are hidden ($p < 0.001$). We
+show this result graphically in @fig-study3genderdiff.
+
+To examine the quality of advice, we computed the expected bonus
+earnings for someone who followed the recommendations. For example, if
+an adviser suggested competing against the High Performer group, we
+matched the advisee against all 20 members of that group and determined
+how often their score matched or exceeded that of the member. We then
+multiplied this number by the respective bonus earnings (50 cents and 30
+cents for the High and Low Performer group, respectively). To see if
+including expectations leads to worse advise for men, we report a linear
+probability model with the experimental treatment of the adviser, the
+gender of the advisee, and their interaction in Column 3 of
+@tbl-study3regs. Displaying expectations led men to be advised to
+compete against the High Performer group more often, and this advise
+turned out to be bad: men receive worse advise than do women when
+expectations are displayed, but not in their absence.[^3]
+
+[^3]: This analysis was not preregistered, and we note here that the
+    reduction in expected earnings is small. However, it is interesting
+    that expectations have a negative effect for men who underestimate
+    their performance on average. One possibility is that advisers
+    suggest the High Performer group more often than is optimal. We
+    return to the possibility that advice is overall biased to be
+    flattering in Study 2.
 
@@
 
-To determine whether flattering advice is truly costly, however, we need to examine the outcome of the advisees.
-In particular, they could ignore flattering advice, recognizing it as such and thus failing to adhere to it.
-Align with our prediction, participants who were primed with high expectations earned less when their expectations were conveyed to the advisers, although this result is only directional (see Column 1 of @tbl-study3time3).
-Similarly, as shown in Column 2 of @tbl-study3time3, we also found that male participants received less reward when their expectations were presented, even when their performance was the same.
-These findings suggest that flattering advice is not without consequences.
-Furthermore, our research indicates that because males are more likely to follow such advice (see Column 4 of @tbl-study3time3), their tendency towards competition intensifies the cost of such advice.
+To determine whether flattering advice is truly costly, however, we need
+to examine the outcome of the advisees. In particular, they could ignore
+flattering advice, recognizing it as such and thus failing to adhere to
+it. Align with our prediction, participants who were primed with high
+expectations earned less when their expectations were conveyed to the
+advisers, although this result is only directional (see Column 1 of
+@tbl-study3time3). Similarly, as shown in Column 2 of @tbl-study3time3,
+we also found that male participants received less reward when their
+expectations were presented, even when their performance was the same.
+These findings suggest that flattering advice is not without
+consequences. Furthermore, our research indicates that because males are
+more likely to follow such advice (see Column 4 of @tbl-study3time3),
+their tendency towards competition intensifies the cost of such advice.
 
@@
 We found supportive evidence for our argument in a different domain.
-Advisors tend to consider advisees' self-expectations and match their advice accordingly, aiming to avoid disappointment.
-Consistent with the confidence gap narrative, men tend to underestimate their mathematics test scores less than women.
-When these expectations are displayed to advisors, they are more likely to advise men to compete against high performers.
-Notably, this turns out to be poor advice: men whose advisors were aware of their expectations received worse advice.
-Our findings suggest that men with the same scores as their female counterparts ended up earning less, although this result is only directional.
-This discrepancy may be due to men receiving more favorable advice, being more likely to follow it, and ultimately facing worse outcomes.
+Advisors tend to consider advisees' self-expectations and match their
+advice accordingly, aiming to avoid disappointment. Consistent with the
+confidence gap narrative, men tend to underestimate their mathematics
+test scores less than women. When these expectations are displayed to
+advisors, they are more likely to advise men to compete against high
+performers. Notably, this turns out to be poor advice: men whose
+advisors were aware of their expectations received worse advice. Our
+findings suggest that men with the same scores as their female
+counterparts ended up earning less, although this result is only
+directional. This discrepancy may be due to men receiving more favorable
+advice, being more likely to follow it, and ultimately facing worse
+outcomes.
 
@@
 Advice has the potential to shape people's career and personal outcomes.
-Honest feedback, however, may be painful to learn if it falls short of one's expectations.
-As prior work notes, this may motivate people to avoid information and avoid seeking help [@Benabou2022; @Golman2017; @Jaroszewicz2022].
-We present evidence from two experiments that advisers are also cognizant of this cost.
-As a result, they present flattering advice that avoids disappointing the recipient, and correctly anticipate that this boosts how advisees perceive them.
-However, this flattering advice comes at a cost to advisees, who would do worse if they followed it blindly, as we show in Study 1.
-
-Moreover, a desire to avoid disappointment also means that advisers have to take into account the expectations of the advisee.
-We document that men are more optimistic about their performance than women are.
-As a result, they receive more flattering advice and are more likely to be told to aim higher.
-Notably, in the context of our experiment, this turns out to be bad advice ex post.
-
-Our findings have implications for organizational practice, where mentoring and advice-giving may take into account an employees' expectation.
-We document this as a novel source of gender bias.
-Organizations could reduce this bias by calibrating employees' expectations to reduce overconfidence.
-
-Participants in our experiment were paired anonymously.
-Even so, we document this desire to avoid disappointment.
-We anticipate that advice would be more flattering in face-to-face communication and without anonymity.
-Moreover, existing relationships might make it even more difficult for advisers to be honest.
-
-In our experiments, participants only received advice once and did not evaluate the adviser after observing the outcome of their decision.
-For example, advice that leads to bad outcomes may undermine the interpersonal benefits of flattery.
-Alternatively, people may still like the flattering advice and not fault the adviser for the bad outcome.
-Moreover, our setting involved only a single piece of advice on one task.
-Future research could examine whether people return to those who gave them flattering advice, or if they prefer someone who gave them the honest (but unpleasant) truth.
+Honest feedback, however, may be painful to learn if it falls short of
+one's expectations. As prior work notes, this may motivate people to
+avoid information and avoid seeking help [@Benabou2022; @Golman2017;
+@Jaroszewicz2022]. We present evidence from two experiments that
+advisers are also cognizant of this cost. As a result, they present
+flattering advice that avoids disappointing the recipient, and correctly
+anticipate that this boosts how advisees perceive them. However, this
+flattering advice comes at a cost to advisees, who would do worse if
+they followed it blindly, as we show in Study 1.
+
+Moreover, a desire to avoid disappointment also means that advisers have
+to take into account the expectations of the advisee. We document that
+men are more optimistic about their performance than women are. As a
+result, they receive more flattering advice and are more likely to be
+told to aim higher. Notably, in the context of our experiment, this
+turns out to be bad advice ex post.
+
+Our findings have implications for organizational practice, where
+mentoring and advice-giving may take into account an employees'
+expectation. We document this as a novel source of gender bias.
+Organizations could reduce this bias by calibrating employees'
+expectations to reduce overconfidence.
+
+Participants in our experiment were paired anonymously. Even so, we
+document this desire to avoid disappointment. We anticipate that advice
+would be more flattering in face-to-face communication and without
+anonymity. Moreover, existing relationships might make it even more
+difficult for advisers to be honest.
+
+In our experiments, participants only received advice once and did not
+evaluate the adviser after observing the outcome of their decision. For
+example, advice that leads to bad outcomes may undermine the
+interpersonal benefits of flattery. Alternatively, people may still like
+the flattering advice and not fault the adviser for the bad outcome.
+Moreover, our setting involved only a single piece of advice on one
+task. Future research could examine whether people return to those who
+gave them flattering advice, or if they prefer someone who gave them the
+honest (but unpleasant) truth.
 
 Advice has long been studied from the perspective of the receiver.
-Similarly, research on belief utility has examined how recipients respond to the valence of the information they receive.
-Here, we show that advisers, too, take into account the psychological impact of the information they convey.
-They may have even greater motivations to avoid conveying bad news, because they incur the interpersonal costs of delivering unfavorable information without reaping the benefits from helping someone make a better choice.
+Similarly, research on belief utility has examined how recipients
+respond to the valence of the information they receive. Here, we show
+that advisers, too, take into account the psychological impact of the
+information they convey. They may have even greater motivations to avoid
+conveying bad news, because they incur the interpersonal costs of
+delivering unfavorable information without reaping the benefits from
+helping someone make a better choice.
 

### 2025-01-19 manuscript/manuscript.qmd
David's Edits (Part 1)

@@
 reference points [@Koszegi2006; @Koszegi2009], and the hedonic
-consequences of information [@Golman2017].
+consequences of information [@Golman2017]. Specifically, we hypothesize
+that advice-givers want to avoid causing disappointment and hence
+match the advisee's expectations. In settings where expectations differ
+by gender, this can then lead to different advice for men and women.
 
@@
 
-People often go to great lengths to avoid unpleasant information,
+People go to great lengths to avoid unpleasant information,
 deriving belief-based utility from maintaining favorable views of
@@
 experiment, we hypothesize (and find) that advisers are relucant to
-disappoint advisees and advice is thus biased upward, away from accuracy
-and toward confirming advisees' priors. We show that this reduces the
+disappoint advisees and advice is thus biased upward, away from accuracy. 
+We show that this reduces the
 quality of advice—but that advisees nonetheless view flattering advisers
@@
 outcome for the recipient, particularly when it is not clear what would
-have happened under a counterfactual.\^\[In some cases, however,
+have happened under a counterfactual.^[In some cases, however,
 repeated interaction might also increase incentives for honest feedback.
 Someone who is known to persistently give overoptimistic advice may be
-viewed as less trustworthy in the long run.\]
+viewed as less trustworthy in the long run.]
 
@@
 Advisees' score on the quiz and, in one treatment, also which group they
-had selected. We predicted that Advisees who were nudged toward the high
-performer group would be more likely to receive advice to compete
-against this high group when Advisers observed their non-binding choice.
+had selected. We predict that Advisees who are nudged toward the high
+performer group will be more likely to receive advice to compete
+against this high group, consistent with Advisers aiming to meet their
+expectations.
 
@@
 
-In a preliminary stage, we recruited
+In a preliminary stage, we recruit
 `r scales::comma(dim(study1_ability50)[1])` participants from Prolific
-and gave them five minutes to complete a quiz consisting of ten items.
-The quiz included word puzzles, identifying emotions from photos, and
+and give them five minutes to complete a quiz consisting of ten items.
+The quiz consists of word puzzles, identifying emotions from photos, and
 selecting the best responses for hypothetical scenarios. These questions
-were adapted from surveys that measure problem-solving, emotional
+are adapted from surveys that measure problem-solving, emotional
 intelligence, and communication skills---which we pre-tested as being
 important in modern society and hence where participants might have a
-stake in doing well. Participants received a bonus of five cents for
-each correctly answered question. We then ranked them based on their
+stake in doing well. Participants receive a bonus of five cents for
+each correctly answered question. We then rank them based on their
 score and label the 20 participants with the lowest (highest) scores as
@@
 
-Next, we recruited `r scales::comma(dim(study1_time1)[1])` participants
-for the role of Advisees. They completed the same 10-item quiz, also
-earning five cents for each correct answer. We then asked them to
+Next, we recruit `r scales::comma(dim(study1_time1)[1])` participants
+for the role of Advisees. They complete the same 10-item quiz, also
+earning five cents for each correct answer. We then ask them to
 express a non-binding preference for whether they would like to compete
-against the High or Low Performer Group. We informed them that they
-would be invited back at a later date when they could make a binding
+against the High or Low Performer Group. We inform them that they
+will be invited back at a later date when they could make a binding
 decision and they could earn a bonus based on whether their score on
-this quiz was equal to or higher than a randomly selected member from
-their comparison group. If they picked the High Performer Group and had
+this quiz is equal to or higher than a randomly selected member from
+their comparison group. If they pick the High (Low) Performer Group and have
 an equal or higher score than a randomly selected member of that group,
-they would earn a bonus of 50 cents. If they picked the Low Performer
-Group and outperformed a randomly selected member of that group, they
-could earn a bonus of 20 cents. If their score was lower in this
-comparison, they would not earn an additional bonus. We randomized which
-of the two groups (High or Low Performers) was selected by default, and
-Advisees were free to select the other group. They also made a guess as
-to their score, and the survey concluded with basic demographic
-questions.
-
-We then recruited `r scales::comma(dim(study1_time2_giver)[1])`
+they earn a bonus of 50 cents (20 cents). If their score is lower in this
+comparison, they earn no additional bonus. We randomize which
+of the two groups (High or Low Performers) is selected by default, and
+Advisees are free to change to the other group. They also make a guess about
+their score, and the survey concludes with basic demographic questions.
+
+We then recruit `r scales::comma(dim(study1_time2_giver)[1])`
 participants for the role of Advisers, and the focal part of our

### 2025-01-19 manuscript/manuscript.qmd
David's edits (continued)

--- 2025-01-10 manuscript/manuscript.qmd
@@
 the ability quiz, we do not expect a difference in performance across
-the Low and High Default treatments. Indeed, the two groups scored no
+the Low and High Default treatments. Indeed, the two groups score no
 different from one another
-(`r round(mean(study1_time1[study1_time1$default == "Low",]$Score),2)`
+(`r papaja::printnum(round(mean(study1_time1[study1_time1$default == "Low",]$Score),2))`
 and
@@
 `r papaja::apa_print(t.test(Score ~ default, data = study1_time1, var.equal = T))$statistic`).
-The default manipulation affected their initial choices. In the "Low
+As expected, the default manipulation changes their initial choices. In the "Low
 Default" treatment, only
 `r round(mean(study1_time1[study1_time1$default == "Low",]$Guess),2)*100`%
-of participants initially preferred competing against the High Performer
+of participants prefer to compete against the High Performer
 Group, compared to
 `r round(mean(study1_time1[study1_time1$default == "High",]$Guess),2)*100`%
-of participants who saw the High Performer Group highlighted
+of participants in the "High Default" treatment
 ($\chi^2$(1, n = 201) = 36.62, p \< .001).
@@
 #| tbl-cap: "Advice to compete against the High Performer Group in Study 1.
-Displaying the non-binding choice of those for whom the Low Performer Group was selected by default makes it more likely that they are advised to compete against the High Performer Group (Column 1).
-Column 2 restricts the analysis to advisers who observed advisees' initial non-binding choice and controls for advisees' score on the quiz.
+Displaying the non-binding choice of those for whom the Low Performer Group was selected by default makes it less likely that they are advised to compete against the High Performer Group (Column 1).
+Column 2 restricts the analysis to advisers who observe advisees' initial non-binding choice and controls for advisees' score on the quiz.
 Standard errors are clustered at the adviser level."
@@
 modelsummary::modelsummary(
-  list(`(1)` = lm(Advice ~ ExpShow * Treatment, data = study1_advice), 
-       `(2)` = lm(Advice ~ Treatment + Score, data = study1_advice %>% dplyr::filter(ExpShow == 1))),
+  list(`All Advice` = lm(Advice ~ ExpShow * Treatment, data = study1_advice), 
+       `Expectations Shown` = lm(Advice ~ Treatment + Score, data = study1_advice %>% dplyr::filter(ExpShow == 1))),
   vcov = ~GiverID,
@@
     "ExpShow:TreatmentHigh" = "Expectation x High Default",
-    "Score" = "Performance",
+    "Score" = "Score",
     "(Intercept)" = "Constant"
@@
   gof_map = list(list('raw' = 'nobs', 'clean' = 'N', 'fmt' = 0))
-)
-
-```
-
-We now examine whether advisers took the advisees' expectations into
-account. Recall that advisees who were defaulted to competing against
-the High Performer Group were indeed more likely to choose this group,
-which, from the advisers' perspective, could signal high confidence in
-their abilities. Our theory predicts that showing expectations should
-lead to more flattering advice--- specifically, a recommendation to
-compete against the High Performer Group--- for advisees with a high
-default choice compared to those with a low default choice. Column 1 of
-@tbl-study1regs reports a linear probability model with advice to
-compete against the high group as the outcome measure, incorporating the
-default choice advisees saw, whether expectations were shown to the
-adviser, and the interaction of the two. Because each adviser made ten
-recommendations, we cluster standard errors at the adviser level. As
-predicted, we find a marginally significant interaction effect: advisees
+) %>%
+  tinytable::group_tt(
+   j = list("Advice to Compete Against High Performers" = 2:3))
+
+```
+
+We now examine whether advisers take the advisees' expectations into
+account. Advisers observe the true performance of the advisee, such that
+expectations about performance add no additional information. However,
+because participants who score higher are also more likely to pick the
+High Performer Group, we use our Default treatment as an instrument.
+We show linear probability models for the decision of the Advisers, which is
+equal to 1 if they recommend competing against the High Performer Group and
+0 if they recommend the Low Performer Group. In Column 1 of @tbl-study1regs,
+we show our main specificiation with the experimental assignment for Advisees
+(High Performer Default vs. Low Performer Default) and Advisers
+(Expectation Shown vs. Expectation Hidden), as well as their interaction.
+Because each adviser made ten
+recommendations, we cluster standard errors at the adviser level. We find that
+displaying expectations of those in the Low Performer Default reduces recommendations
+to compete against the Top group by 4 percentage points, or about 10\% relative
+to when expectations are hidden. This decrease is marginally smaller advisees
 with a default choice to compete against the High Performer Group

### 2025-01-19 manuscript/manuscript.qmd
Edited through Study 2.

--- 2025-01-19 manuscript/manuscript.qmd
@@
 because participants who score higher are also more likely to pick the
-High Performer Group, we use our Default treatment as an instrument.
+High Performer Group, we use our Default treatment as an instrument that reflect
+higher expectations.
 We show linear probability models for the decision of the Advisers, which is
@@
 to compete against the Top group by 4 percentage points, or about 10\% relative
-to when expectations are hidden. This decrease is marginally smaller advisees
+to when expectations are hidden. This decrease is marginally smaller for advisees
 with a default choice to compete against the High Performer Group
-(nudged to have high expectations, though not necessarily holding them)
-were more likely to receive advice to compete against stronger
-competitors when their expectations were shown compared to when they
-were hidden. We reported a linear probability model on advising to
+(nudged to have high expectations, though not necessarily holding them), and whose
+advice did not differ based on whether their expectations were shown or hidden.
+We reported a linear probability model on advising to
 compete against the High Performer group for advisers in the
@@
 #| label: fig-study1Advice
-#| fig-cap: "Advisees who were nudged to express high expectations were more likely to receive advice to compete against the High Performer Group."
+#| fig-cap: "Advice given in Study 1. Advisees who were nudged to express high expectations were more likely to receive advice to compete against the High Performer Group."
 
@@
                          position = ggplot2::position_dodge(0.9), linewidth = 0.2, width = 0.1) +
-  ggtitle("Advice: Meeting Expectations vs. Absent Expectations") +
+  # ggtitle("Advice: Meeting Expectations vs. Absent Expectations") +
   scale_fill_manual(values = c("#2A629A",'#FF7F3E')) +
-  theme_bw() +
-  labs(y = "P(Compete Against High Performer)", x = NULL) +
+  scale_y_continuous("P(Compete Against High Performer)",
+                     labels = scales::percent) +
+  geom_text(aes(x = Condition, y = 0.02,
+                label = paste0(round(avg_count*100), "%")),
+            position = position_dodge(0.9),
+            color = "white") +
+  papaja::theme_apa() +
   theme(panel.grid = element_blank(),
@@
         axis.text.x = element_text(size = 12),
+        axis.ticks.x = element_blank(),
+        axis.ticks.y = element_blank(),
+        axis.title.x = element_blank(),
         legend.position = "none", # No legend
         plot.title = element_text(hjust = 0.5, size = 16)) +
-  scale_x_discrete(labels = c("Expectation shown", "Expectation Absent")) +
+  scale_x_discrete(labels = c("Expectation Shown", "Expectation Hidden")) +
    geom_text(aes(label=Treatment, y = -0.01), position = position_dodge(0.90))
@@
 
-When the quality of a decision does not depend on someone's
-expectations, the adviser's awareness of the advisee's expectations
-should not influence the advice given. However, in line with our
+When an adviser knows an outcome that an advisee can only estimate, learning
+this estimate should not change the advice that is given. However, in line with our
 argument that advisers take into account the belief utility of the
-advisee and prefer to flatter rather than disappoint, we find that
-displaying the advisee's expectations does make a difference.
+advisee and prefer to avoid disappointing them, we find that providing information
+about expectations makes a difference.
 Specifically, advisees who expressed a preference for stronger
-competitors were more likely to receive 'flattering' advice, encouraging
-them to pursue that option. One possible explanation for this finding is
-that, rather than trying to flatter, advisers may simply be telling
-advisees what they want to hear. In the next study, we aim to
-investigate the mechanism behind this discrepancy in advice-giving when
-expectations are revealed, exploring the question: Why do people give
-flattering advice?
+competitors were more likely to receive flattering advice, encouraging
+them to pursue that option. This occurs even though advisers are incentivized
+to give good advice.
 
@@
 
-So far, we have shown that displaying expectations influences the advice
-given. Specifically, advisers were more likely to recommend competing
-against a group of high performers to advisees with higher performance
-expectations compared to those without. We now directly test whether
-this effect is driven by interpersonal concerns. In particular, we
-explore whether more flattering advice stems from a desire to be liked,
-and whether advisees, in turn, like advisers more when they receive
-flattering advice.
+We next examine if advisers believe that flattering advice will improve
+how advisees perceive them, and whether this perception is true. We do this
+by manipulating the incentives for advisers, who receive a bonus either based
+on how they are evaluated by an advisee, or a bonus for the advisee's accuracy.
 

### 2025-01-28 manuscript/manuscript.qmd
Study 2

--- 2025-01-19 manuscript/manuscript.qmd
@@
 We next examine if advisers believe that flattering advice will improve
-how advisees perceive them, and whether this perception is true. We do this
+how they are perceived, and if so, whether this perception is true. We do this
 by manipulating the incentives for advisers, who receive a bonus either based
@@
 
-We conducted a three-stage experiment in which we experimentally
-manipulated the incentives for advisers. We began by inviting a group of
-advisees to upload photos of themselves ("selfies") and informed them
-that they would be rated on their attractiveness. We grouped them with
-nine other participants of the same gender and recruited participants of
-the opposing gender to rank them from most to least attractive and to
-provide advice. Specifically, we asked them to advise the participant
-they ranked as the 7th most attractive (4th least attractive) on what
+The study takes place in three stages. First, a group of
+advisees upload photos of themselves ("selfies") and are grouped with 
+nine other participants of the same sex We then recruit participants of
+the opposing sex to rank them from most to least attractive and to
+provide advice. Specifically, they advise the participant
+they ranked as the 7th most attractive (i.e., 4th least attractive) on what
 rank they should bet they were ranked by a larger group of raters.
@@
 payment either if the advisee guessed their rank accurately or if the
-advisee evaluated the adviser as likeable as measured by an
-unincentivized scale response. We hypothesize that advisers who want to
-be liked by advisees will recommend that they bet on a lower rank, i.e.
-that they are more attractive.
+advisee evaluated the adviser as likeable as measured by a scale response. 
+We hypothesize that advisers incentivized to be liked will recommend betting on
+a lower rank, i.e. that the advisee is more attractive.
 
@@
 
-We recruited 300 participants from Prolific and, after asking
-demographic questions, invited them to upload photos of themselves
+We recruit 300 participants from Prolific and, after asking
+demographic questions, invite them to upload photos of themselves
 (selfies) to be rated by other participants on attractiveness.
-`r scales::comma(dim(study2_time1[study2_time1$gender == 'Male',])[1])`
+We obtain selfies from `r scales::comma(dim(study2_time1[study2_time1$gender == 'Male',])[1])`
 men and
 `r scales::comma(dim(study2_time1[study2_time1$gender == 'Female',])[1])`
-women agreed to do so and uploaded pictures that adhered to our
-instructions (e.g., did not include other people). We selected the first
-100 photos from women to arrive at a gender-balanced sample
+women adhering to our
+instructions (e.g., did not include other people). In line with our preregistration,
+we select the first 100 photos from women to arrive at a gender-balanced sample
 ($M_{\text{Age}}$ = `r mean(study2_time1_200$age)` years). Participants
-were informed that their selfies would be randomly grouped with those of
-nine other participants of their gender and ranked in terms of
+are informed that their selfies will be randomly grouped with those of
+nine other participants of their sex and ranked in terms of
 attractiveness by a group of new Prolific participants of the opposite
-gender. Lastly, they guessed their rank (unincentivized).
-
-Next, we recruited a new, gender-balanced sample for the role of
-advisers. `r scales::comma(dim(study2_time2)[1])` participants from
-Prolific ($M_{\text{Age}}$ = `r mean(study2_time2$age)` years;
-`r round(mean(study2_time2$gender == "Female")*100, 2)`% Female) started
-by providing demographic information, then were matched to a group of
-the opposite gender. They then ranked participants from most to least
+sex. They then make an unincentivized guess of their rank.
+
+Next, we recruit `r scales::comma(dim(study2_time2)[1])` participants from Prolific
+for the role of advisers ($M_{\text{Age}}$ = `r mean(study2_time2$age)` years;
+`r round(mean(study2_time2$gender == "Female")*100, 2)`% Female). We first
+collect demographic information, then match them to a group of
+the opposite sex. They rank selfies from ten participants from most to least
 attractive using a drop-down menu next to each picture. Because of a
-limitation with the survey software, participants were able to select
-the same rank for multiple participants, rather than rank them uniquely.
-We remove 115 participants who did not follow instructions and provide a
-unique ranking.
-
-After submitting their ratings, they saw the photo of the participant
-they had ranked as the 7th most attractive (i.e., the 4th least
-attractive). They were reminded of the rank they had given to that
-person and informed that this participant would be invited back and
-could earn a \$1 bonus if they guessed their rank correctly. The rank
-was determined by the aggregate ratings of all participants who had
-ranked this group. Their task was to give advice to this participant
-about the rank they should bet on based on having observed all ten
-selfies and their own assessment. We randomly assigned participants to
+limitation with the survey software, we could not validate that each rank is
+given only once, and we remove 115 participants who failed to follow instructions 
+and did not provide a complete ranking.^[Moreover, we could not collect data from any participant who did not select any participant as the 7th most attractive participant, as that image would be shown on subsequent pages.]
+
+After submitting their ratings, participants see the photo of the participant
+they ranked as the 7th most attractive (i.e., the 4th least
+attractive). We remind them of the rank they have just given to that
+person and inform them that this participant will be invited back and
+can earn a \$1 bonus if they correctly guess their rank. The rank
+is determined by the aggregate ratings of all participants who have
+ranked this group. Because the participant does not observe the other nine
+people in the group, they would depend on the adviser's recommendation along with
+their own assessment. We randomly assign advisers to
 one of two incentivization schemes. In the "Accuracy" treatment, they
-received a bonus identical to the advisee: \$1 if they guessed their
-rank correctly. In the "Likeability" treatment, we informed them that
-they would be rated by the advisee on a 5-point Likert scale for how
-likeable they thought they were. Each point on the scale would translate
-to a bonus of 20 cents. They then selected a rank that they would
+receive a bonus identical to the advisee: \$1 if they guess their
+rank correctly. In the "Likeability" treatment, we inform them that
+the advisee will rate them on a 5-point Likert scale on how
+likeable they thought they are. Each point on the scale would translate
+to a bonus of 20 cents. Advisers then select a rank (from 1 to 10) that they
 recommend the advisee to bet on.
 
-Finally, we invited participants from Stage 1 and were ranked as the 7th
-attractive by at least one adviser (so that they received advice) back
-for the follow-up survey. Following our preregistration, we kept the
+Finally, we invite participants from Stage 1 who were ranked as the 7th most
+attractive participant by at least one adviser (so that they received advice) back
+for the follow-up survey. Following our preregistration, we keep the
 survey open for 7 days. In total,
@@
 `r scales::comma(dim(study2_time3[study2_time3$gender == 'Female',])[1])`
-women) returned. They were reminded of the selfie they uploaded in Stage
-1 and informed that a group of 10 selfies, including theirs, had been
-rated by other participants from Prolific. They then saw the advice from
-a randomly selected adviser and made their estimate with a \$1 incentive
-for guessing accurately. They then saw the rank they had been advised to
-bet on one more time and were asked to rate the adviser's likability,
+women) complete the follow-up survey. We remind them of the selfie they uploaded in Stage
+1 and that a group of 10 selfies, including theirs, had been
+rated by other participants from Prolific. They then see the advice from
+a randomly selected adviser and make their own guess with a \$1 incentive
+for accuracy. Finally, they rate the adviser's likability,
 warmth, friendliness, good-naturedness, trustworthiness, and sincerity
-on 5-point Likert scales (adapted from @Fiske2007).
+on 5-point Likert scales [adapted from @Fiske2007].
 
@@
 However, when incentivized for likability, many participants gave flattering advice by suggesting betting on higher ranks that imply a higher evaluation of attractiveness."
+#| eval: false
 
@@
     theme_bw() +
+  coord_flip() +
     theme(panel.grid = element_blank(),
@@
           axis.line = element_line(colour = "black"),
-          legend.position = "bottom",
+          legend.position = "none",
           legend.title = element_blank(),
@@
 ```
+```{r}
+#| label: fig-study2advice
+#| fig-cap: "Participants in Study 2 give advice to the person they rank 7th most attractive out of 10.
+When incentivized for accuracy, the majority recommends betting on that rank.
+However, when incentivized for likeability, participants inflate their advice to flatter the recipient as more attractive."
+study2_time2 %>%
+  dplyr::group_by(Condition) %>%
+  dplyr::mutate(total_per_condition = dplyr::n()) %>%
+  dplyr::group_by(Condition, Advice, total_per_condition) %>%
+  dplyr::summarize(n = dplyr::n()) %>%
+  dplyr::mutate(pct = ifelse(Condition == "Accurate", -n/total_per_condition, n/total_per_condition),
+                Advice = factor(Advice)) %>%
+  ggplot(aes(x = pct, y = Advice, fill = Condition)) +
+  geom_col() +
+  scale_x_continuous("Share of Advice",
+                     limits = c(-0.6, 0.6),
+                     labels = \(x) scales::percent(abs(x))) +
+  scale_y_discrete(limits = rev) +
+  # Dashed 'horizontal' line at Advice = 7
+  geom_hline(yintercept = 4, col = 'black', linetype = 'dashed', linewidth = 0.7) +
+  # Example text annotation (adjust x/y for positioning)
+  annotate("text", x = -0.3, y = 9, label = "Accuracy Incentive", hjust = 1, size = 4, fontface = "bold") +
+  annotate("text", x = 0.6, y = 9, label = "Likeable Incentive", hjust = 1, size = 4, fontface = "bold") +
+  # scale_y_continuous(name = "Advised Rank", breaks = seq(1, 10)) +
+  scale_fill_manual(values = c("#2A629A", "#FF7F3E")) +
+  papaja::theme_apa() +
+  theme(
+    legend.position  = "none",
+    axis.text.x  = element_text(size = 14),
+    axis.text.y  = element_text(size = 14),
+    axis.title.x = element_text(size = 16, face = "bold"),
+    axis.title.y = element_text(size = 16, face = "bold")
+  )
+```
 
 We begin by examining the prior beliefs of advisees who uploaded their
-selfies. On average, men guessed they ranked
+selfies. On average, men guess they rank
 `r round(mean(study2_time1[study2_time1$gender == "Male",]$Guess),2)` in
-their group of 10 and women guessed that they ranked
-`r round(mean(study2_time1[study2_time1$gender == "Female",]$Guess),2)`.
-Participants overall underestimate their attractiveness relative to the
-benchmark average of 5.5. Moreover, women do so more than men
-`r papaja::apa_print(t.test(Guess ~ gender, data = study2_time1, var.equal = T))$statistic`.
-Notably, people's self-perceptions correlated strongly with the
+their group of 10 and women guess that they rank
+`r round(mean(study2_time1[study2_time1$gender == "Female",]$Guess),2)`
+(`r papaja::apa_print(t.test(Guess ~ gender, data = study2_time1, var.equal = T))$statistic`).
+Notably, people's self-perceptions correlate strongly with the
 aggregate ratings of the advisers
@@
 `r papaja::apa_print(cor.test(study2_finalRank$Guess, study2_finalRank$finalRank))$statistic`).
-However, there was substantial heterogeneity in perceptions of
+However, there is substantial heterogeneity in perceptions of
 attractiveness. Of the 200 participants,
-`r length(unique(study2_time2$Target))` were ranked as 7th most
+`r length(unique(study2_time2$Target))` are ranked as 7th most
 attractive by at least one adviser. On average, men in this subset
-estimated they were ranked
+estimate they rank
 `r round(mean(TargetsUnique[TargetsUnique$gender == 'Male',]$Guess),2)`th
-and women estimated they were ranked
+and women estimate they rank
 `r round(mean(TargetsUnique[TargetsUnique$gender == 'Female',]$Guess),2)`th
@@
 
-Next, we turn our attention to the advisers (@fig-study2advice). In the
-Accuracy condition, those uploading selfies were advised to bet on rank
+Next, we turn our attention to the advisers (see @fig-study2advice). In the
+Accuracy condition, those uploading selfies are on average advised to bet on rank
 `r round(mean(study2_time2[study2_time2$Condition == "Accurate",]$Advice),2)`.
@@
 This suggests that even when incentivized for accuracy, participants
-offered flattering advice.[^1] Importantly, and as predicted, we find
+offer flattering advice.[^1] Importantly, and as predicted, we find
 that advisers in the Likeable treatment recommend betting on a lower
@@
 `r papaja::apa_print(t.test(Advice ~ Condition, data = study2_time2, var.equal = T))$statistic`).
-This suggests that advisers inferred that advising someone that they
-were more attractive would make the adviser appear more likeable and
-therefore provided advice that communicated a more favorable impression
-of the participants' attractiveness. The distribution shown in
+This suggests that advisers infer flattering someone with pleasant advice
+would make the adviser appear more likeable. The distribution shown in
 @fig-study2advice shows that participants do not simply tell
@@
     However, it could also be that advisers are uncertain about the
-    rankings they had given and make a recommendation that combines
-    their own belief with a uniform prior.
+    rankings they have given and make a recommendation that combines
+    their own belief with a uniform prior. Therefore, our analyses focus
+    on the difference between the two conditions.
 
@@
   # Add points for each observation
-  geom_point(size = 2, alpha = 0.7) +
+  geom_point(size = 2, alpha = 0.7,
+             position = position_jitter()) +
 
@@
 #| label: fig-study2ratingByGroup
-#| fig-cap: "After participants received advice that suggested betting on a rank that was lower than, equal to, or higher than their self-expectations, they evaluated advisors based on their likability and warmth.
-Participants rated advisors who gave flattering advice and delivered a high evaluation of their attractiveness as more likable and warm than those whose advice implied a lower evaluation of their attractiveness."
+#| fig-cap: "After participants receive advice that suggests betting on a rank that was lower than, equal to, or higher than their own guess, they evaluate advisors based on their likability and warmth.
+Participants rate advisors who give flattering advice and deliver a high evaluation of their attractiveness as more likable and warm than those whose advice implied a lower evaluation of their attractiveness."
 
@@
   geom_tile(color = "white") +
-  scale_fill_gradient(low = "grey80", high = "grey30", name = "Rating") +  # Grey gradient from light to dark
+  scale_fill_gradient(low = "darkblue", high = "orange", name = "Rating") +  # Grey gradient from light to dark
   geom_text(aes(label = sprintf("%.2f", Rating)), color = "white", size = 8) +
@@
 
-As seen in @fig-study2rating, we found that advisees who suggested that
+As seen in @fig-study2rating, we advisers who suggested that
 the advisee was more attractive (lower rank) were indeed rated as more
@@
 respectively; See Columns 1 and 2 of @tbl-study2regs). When using their
-self-expectations as a reference point, advisors who suggest a rank
-lower than that point are perceived as less likable and warm (see
+own initial guess as a reference point, advisers who suggest a worse rank
+are perceived as less likable and warm (see
 @fig-study2ratingByGroup). Interestingly, these benefits are not at the
-cost of being hypocritical; advisers who recommend a more favorable rank
+cost of sincerity; advisers who recommend a more favorable rank
 are viewed as no less trustworthy (Column 3 of @tbl-study2regs).
 
-We were not powered to do a comparison across the two experimental
+We are not powered to do a comparison across the two experimental
 groups and did not preregister such a difference. Indeed, we find no
@@
 respectively). We also assess the quality of advice by measuring the
-discrepancy between the advised rank and the final rank. Our analysis
-revealed no significant difference between the two treatments in terms
-of how helpful the advice was for advisees in making accurate guesses,
-`r papaja::apa_print(t.test(accuracy ~ Condition, data = study2_time3, var.equal = T))$statistic`.
+discrepancy between the advised rank and the correct rank. We find
+no difference in accuracy across the advice treatments
+(`r papaja::apa_print(t.test(accuracy ~ Condition, data = study2_time3, var.equal = T))$statistic`).
 
@@
 not come at the cost of trustworthiness, even when the advice is
-substantially inflated (e.g., a recommendation that the advisee is the
-most attractive in the group).
+inflated.
 

### 2025-01-28 manuscript/manuscript.qmd
Revised version :)

--- 2025-01-28 manuscript/manuscript.qmd
@@
     - id: id1
-author-note:
-  disclosures:
-    gratitude: The authors are grateful to XXX for their helpful comments.
+# author-note:
+  # disclosures:
+    # gratitude: The authors are grateful to XXX for their helpful comments.
 abstract: Good advice improves decision quality but often requires delivering unpleasant truths that may disappoint advisees.
@@
 outcome for the recipient, particularly when it is not clear what would
-have happened under a counterfactual.\^\[In some cases, however,
-repeated interaction might also increase incentives for honest feedback.
-Someone who is known to persistently give overoptimistic advice may be
-viewed as less trustworthy in the long run.\]
+have happened under a counterfactual.[^1]
+
+[^1]: In some cases, however, repeated interaction might also increase
+    incentives for honest feedback. Someone who is known to persistently
+    give overoptimistic advice may be viewed as less trustworthy in the
+    long run.
 
@@
 `r papaja::apa_print(t.test(Score ~ default, data = study1_time1, var.equal = T))$statistic`).
-As expected, the default manipulation changes their initial choices. In the "Low
-Default" treatment, only
+As expected, the default manipulation changes their initial choices. In
+the "Low Default" treatment, only
 `r round(mean(study1_time1[study1_time1$default == "Low",]$Guess),2)*100`%
-of participants prefer to compete against the High Performer
-Group, compared to
+of participants prefer to compete against the High Performer Group,
+compared to
 `r round(mean(study1_time1[study1_time1$default == "High",]$Guess),2)*100`%
-of participants in the "High Default" treatment
-($\chi^2$(1, n = 201) = 36.62, p \< .001).
+of participants in the "High Default" treatment ($\chi^2$(1, n = 201) =
+36.62, p \< .001).
+
+\linespread{1}
 
@@
 Standard errors are clustered at the adviser level."
+#| after-caption-space: 0pt
 
@@
 because participants who score higher are also more likely to pick the
-High Performer Group, we use our Default treatment as an instrument that reflect
-higher expectations.
-We show linear probability models for the decision of the Advisers, which is
-equal to 1 if they recommend competing against the High Performer Group and
-0 if they recommend the Low Performer Group. In Column 1 of @tbl-study1regs,
-we show our main specificiation with the experimental assignment for Advisees
-(High Performer Default vs. Low Performer Default) and Advisers
-(Expectation Shown vs. Expectation Hidden), as well as their interaction.
-Because each adviser made ten
-recommendations, we cluster standard errors at the adviser level. We find that
-displaying expectations of those in the Low Performer Default reduces recommendations
-to compete against the Top group by 4 percentage points, or about 10\% relative
-to when expectations are hidden. This decrease is marginally smaller for advisees
-with a default choice to compete against the High Performer Group
-(nudged to have high expectations, though not necessarily holding them), and whose
-advice did not differ based on whether their expectations were shown or hidden.
-We reported a linear probability model on advising to
-compete against the High Performer group for advisers in the
-"Expectations" treatment, controlling for the true performance of the
-advisee in Column 2 of @tbl-study1regs. We observe a significant main
-effect of the default treatment, where a high default increased the
-likelihood of receiving flattering advice. It is worth noting that,
-since only
+High Performer Group, we use our Default treatment as an instrument that
+reflect higher expectations. We show linear probability models for the
+decision of the Advisers, which is equal to 1 if they recommend
+competing against the High Performer Group and 0 if they recommend the
+Low Performer Group. In Column 1 of @tbl-study1regs, we show our main
+specificiation with the experimental assignment for Advisees (High
+Performer Default vs. Low Performer Default) and Advisers (Expectation
+Shown vs. Expectation Hidden), as well as their interaction. Because
+each adviser made ten recommendations, we cluster standard errors at the
+adviser level. We find that displaying expectations of those in the Low
+Performer Default reduces recommendations to compete against the Top
+group by 4 percentage points, or about 10% relative to when expectations
+are hidden. This decrease is marginally smaller for advisees with a
+default choice to compete against the High Performer Group (nudged to
+have high expectations, though not necessarily holding them), and whose
+advice did not differ based on whether their expectations were shown or
+hidden. We reported a linear probability model on advising to compete
+against the High Performer group for advisers in the "Expectations"
+treatment, controlling for the true performance of the advisee in Column
+2 of @tbl-study1regs. We observe a significant main effect of the
+default treatment, where a high default increased the likelihood of
+receiving flattering advice. It is worth noting that, since only
 `r round(mean(study1_time1[study1_time1$default == "High",]$Guess),2)*100`
@@
 
-When an adviser knows an outcome that an advisee can only estimate, learning
-this estimate should not change the advice that is given. However, in line with our
-argument that advisers take into account the belief utility of the
-advisee and prefer to avoid disappointing them, we find that providing information
-about expectations makes a difference.
+When an adviser knows an outcome that an advisee can only estimate,
+learning this estimate should not change the advice that is given.
+However, in line with our argument that advisers take into account the
+belief utility of the advisee and prefer to avoid disappointing them, we
+find that providing information about expectations makes a difference.
 Specifically, advisees who expressed a preference for stronger
 competitors were more likely to receive flattering advice, encouraging
-them to pursue that option. This occurs even though advisers are incentivized
-to give good advice.
+them to pursue that option. This occurs even though advisers are
+incentivized to give good advice.
 
@@
 We next examine if advisers believe that flattering advice will improve
-how they are perceived, and if so, whether this perception is true. We do this
-by manipulating the incentives for advisers, who receive a bonus either based
-on how they are evaluated by an advisee, or a bonus for the advisee's accuracy.
-
-The study takes place in three stages. First, a group of
-advisees upload photos of themselves ("selfies") and are grouped with 
-nine other participants of the same sex We then recruit participants of
-the opposing sex to rank them from most to least attractive and to
-provide advice. Specifically, they advise the participant
-they ranked as the 7th most attractive (i.e., 4th least attractive) on what
-rank they should bet they were ranked by a larger group of raters.
-Advisers were randomly assigned to two treatments, receiving a bonus
-payment either if the advisee guessed their rank accurately or if the
-advisee evaluated the adviser as likeable as measured by a scale response. 
-We hypothesize that advisers incentivized to be liked will recommend betting on
-a lower rank, i.e. that the advisee is more attractive.
+how they are perceived, and if so, whether this perception is true. We
+do this by manipulating the incentives for advisers, who receive a bonus
+either based on how they are evaluated by an advisee, or a bonus for the
+advisee's accuracy.
+
+The study takes place in three stages. First, a group of advisees upload
+photos of themselves ("selfies") and are grouped with nine other
+participants of the same sex We then recruit participants of the
+opposing sex to rank them from most to least attractive and to provide
+advice. Specifically, they advise the participant they ranked as the 7th
+most attractive (i.e., 4th least attractive) on what rank they should
+bet they were ranked by a larger group of raters. Advisers were randomly
+assigned to two treatments, receiving a bonus payment either if the
+advisee guessed their rank accurately or if the advisee evaluated the
+adviser as likeable as measured by a scale response. We hypothesize that
+advisers incentivized to be liked will recommend betting on a lower
+rank, i.e. that the advisee is more attractive.
 
@@
 
-We recruit 300 participants from Prolific and, after asking
-demographic questions, invite them to upload photos of themselves
-(selfies) to be rated by other participants on attractiveness.
-We obtain selfies from `r scales::comma(dim(study2_time1[study2_time1$gender == 'Male',])[1])`
+We recruit 300 participants from Prolific and, after asking demographic
+questions, invite them to upload photos of themselves (selfies) to be
+rated by other participants on attractiveness. We obtain selfies from
+`r scales::comma(dim(study2_time1[study2_time1$gender == 'Male',])[1])`
 men and
 `r scales::comma(dim(study2_time1[study2_time1$gender == 'Female',])[1])`
-women adhering to our
-instructions (e.g., did not include other people). In line with our preregistration,
-we select the first 100 photos from women to arrive at a gender-balanced sample
-($M_{\text{Age}}$ = `r mean(study2_time1_200$age)` years). Participants
-are informed that their selfies will be randomly grouped with those of
-nine other participants of their sex and ranked in terms of
-attractiveness by a group of new Prolific participants of the opposite
-sex. They then make an unincentivized guess of their rank.
-
-Next, we recruit `r scales::comma(dim(study2_time2)[1])` participants from Prolific
-for the role of advisers ($M_{\text{Age}}$ = `r mean(study2_time2$age)` years;
-`r round(mean(study2_time2$gender == "Female")*100, 2)`% Female). We first
-collect demographic information, then match them to a group of
-the opposite sex. They rank selfies from ten participants from most to least
+women adhering to our instructions (e.g., did not include other people).
+In line with our preregistration, we select the first 100 photos from
+women to arrive at a gender-balanced sample ($M_{\text{Age}}$ =
+`r mean(study2_time1_200$age)` years). Participants are informed that
+their selfies will be randomly grouped with those of nine other
+participants of their sex and ranked in terms of attractiveness by a
+group of new Prolific participants of the opposite sex. They then make
+an unincentivized guess of their rank.
+
+Next, we recruit `r scales::comma(dim(study2_time2)[1])` participants
+from Prolific for the role of advisers ($M_{\text{Age}}$ =
+`r mean(study2_time2$age)` years;
+`r round(mean(study2_time2$gender == "Female")*100, 2)`% Female). We
+first collect demographic information, then match them to a group of the
+opposite sex. They rank selfies from ten participants from most to least
 attractive using a drop-down menu next to each picture. Because of a
-limitation with the survey software, we could not validate that each rank is
-given only once, and we remove 115 participants who failed to follow instructions 
-and did not provide a complete ranking.^[Moreover, we could not collect data from any participant who did not select any participant as the 7th most attractive participant, as that image would be shown on subsequent pages.]
-
-After submitting their ratings, participants see the photo of the participant
-they ranked as the 7th most attractive (i.e., the 4th least
+limitation with the survey software, we could not validate that each
+rank is given only once, and we remove 115 participants who failed to
+follow instructions and did not provide a complete ranking.[^2]
+
+[^2]: Moreover, we could not collect data from any participant who did
+    not select any participant as the 7th most attractive participant,
+    as that image would be shown on subsequent pages.
+
+After submitting their ratings, participants see the photo of the
+participant they ranked as the 7th most attractive (i.e., the 4th least
 attractive). We remind them of the rank they have just given to that
 person and inform them that this participant will be invited back and
-can earn a \$1 bonus if they correctly guess their rank. The rank
-is determined by the aggregate ratings of all participants who have
-ranked this group. Because the participant does not observe the other nine
-people in the group, they would depend on the adviser's recommendation along with
-their own assessment. We randomly assign advisers to
-one of two incentivization schemes. In the "Accuracy" treatment, they
-receive a bonus identical to the advisee: \$1 if they guess their
-rank correctly. In the "Likeability" treatment, we inform them that
-the advisee will rate them on a 5-point Likert scale on how
-likeable they thought they are. Each point on the scale would translate
-to a bonus of 20 cents. Advisers then select a rank (from 1 to 10) that they
-recommend the advisee to bet on.
-
-Finally, we invite participants from Stage 1 who were ranked as the 7th most
-attractive participant by at least one adviser (so that they received advice) back
-for the follow-up survey. Following our preregistration, we keep the
-survey open for 7 days. In total,
+can earn a \$1 bonus if they correctly guess their rank. The rank is
+determined by the aggregate ratings of all participants who have ranked
+this group. Because the participant does not observe the other nine
+people in the group, they would depend on the adviser's recommendation
+along with their own assessment. We randomly assign advisers to one of
+two incentivization schemes. In the "Accuracy" treatment, they receive a
+bonus identical to the advisee: \$1 if they guess their rank correctly.
+In the "Likeability" treatment, we inform them that the advisee will
+rate them on a 5-point Likert scale on how likeable they thought they
+are. Each point on the scale would translate to a bonus of 20 cents.
+Advisers then select a rank (from 1 to 10) that they recommend the
+advisee to bet on.
+
+Finally, we invite participants from Stage 1 who were ranked as the 7th
+most attractive participant by at least one adviser (so that they
+received advice) back for the follow-up survey. Following our
+preregistration, we keep the survey open for 7 days. In total,
 `r scales::comma(dim(study2_time3)[1])` participants
@@
 `r scales::comma(dim(study2_time3[study2_time3$gender == 'Female',])[1])`
-women) complete the follow-up survey. We remind them of the selfie they uploaded in Stage
-1 and that a group of 10 selfies, including theirs, had been
-rated by other participants from Prolific. They then see the advice from
-a randomly selected adviser and make their own guess with a \$1 incentive
-for accuracy. Finally, they rate the adviser's likability,
+women) complete the follow-up survey. We remind them of the selfie they
+uploaded in Stage 1 and that a group of 10 selfies, including theirs,
+had been rated by other participants from Prolific. They then see the
+advice from a randomly selected adviser and make their own guess with a
+\$1 incentive for accuracy. Finally, they rate the adviser's likability,
 warmth, friendliness, good-naturedness, trustworthiness, and sincerity
@@
 ```{r}
-#| label: fig-study2advice
+#| label: fig-study2advice-old
 #| fig-cap: "Advisers were asked to suggest what rank to bet on for someone they ranked as the 7th most attractive out of ten people.
@@
 ```
+
 ```{r}
@@
 However, when incentivized for likeability, participants inflate their advice to flatter the recipient as more attractive."
+
+study2_time2 <- study2_time2 %>% dplyr::mutate(Advice = as.numeric(Advice))
+
 study2_time2 %>%
@@
 (`r papaja::apa_print(t.test(Guess ~ gender, data = study2_time1, var.equal = T))$statistic`).
-Notably, people's self-perceptions correlate strongly with the
-aggregate ratings of the advisers
+Notably, people's self-perceptions correlate strongly with the aggregate
+ratings of the advisers
 (`r round(cor(study2_finalRank$Guess, study2_finalRank$finalRank),2)`,
@@
 
-Next, we turn our attention to the advisers (see @fig-study2advice). In the
-Accuracy condition, those uploading selfies are on average advised to bet on rank
+Next, we turn our attention to the advisers (see @fig-study2advice). In
+the Accuracy condition, those uploading selfies are on average advised
+to bet on rank
 `r round(mean(study2_time2[study2_time2$Condition == "Accurate",]$Advice),2)`.
@@
 This suggests that even when incentivized for accuracy, participants
-offer flattering advice.[^1] Importantly, and as predicted, we find
-that advisers in the Likeable treatment recommend betting on a lower
-rank, communicating that they think the participant in the selfie is
-more attractive
+offer flattering advice.[^3] Importantly, and as predicted, we find that
+advisers in the Likeable treatment recommend betting on a lower rank,
+communicating that they think the participant in the selfie is more
+attractive
 (`r round(mean(study2_time2[study2_time2$Condition == "Likable",]$Advice),2)`,
 `r papaja::apa_print(t.test(Advice ~ Condition, data = study2_time2, var.equal = T))$statistic`).
-This suggests that advisers infer flattering someone with pleasant advice
-would make the adviser appear more likeable. The distribution shown in
-@fig-study2advice shows that participants do not simply tell
+This suggests that advisers infer flattering someone with pleasant
+advice would make the adviser appear more likeable. The distribution
+shown in @fig-study2advice shows that participants do not simply tell
 participants that they are the most attractive person in the group. They
@@
 
-[^1]: This shading could be due to concerns of avoiding disappointment.
+[^3]: This shading could be due to concerns of avoiding disappointment.
     However, it could also be that advisers are uncertain about the
@@
 Column 3 shows that advisors are rated as more trustworthy when they advice lower ranks, but this relationship is only directional."
+#| after-caption-space: 0pt
 
@@
 
-As seen in @fig-study2rating, we advisers who suggested that
-the advisee was more attractive (lower rank) were indeed rated as more
-likeable and warm (b = -0.109, p \< .05; b = -0.133, p \< .001,
-respectively; See Columns 1 and 2 of @tbl-study2regs). When using their
-own initial guess as a reference point, advisers who suggest a worse rank
-are perceived as less likable and warm (see
-@fig-study2ratingByGroup). Interestingly, these benefits are not at the
-cost of sincerity; advisers who recommend a more favorable rank
-are viewed as no less trustworthy (Column 3 of @tbl-study2regs).
-
-We are not powered to do a comparison across the two experimental
-groups and did not preregister such a difference. Indeed, we find no
-difference in likeability and warmth across the two treatments
+As seen in @fig-study2rating, we advisers who suggested that the advisee
+was more attractive (lower rank) were indeed rated as more likeable and
+warm (b = -0.109, p \< .05; b = -0.133, p \< .001, respectively; See
+Columns 1 and 2 of @tbl-study2regs). When using their own initial guess
+as a reference point, advisers who suggest a worse rank are perceived as
+less likable and warm (see @fig-study2ratingByGroup). Interestingly,
+these benefits are not at the cost of sincerity; advisers who recommend
+a more favorable rank are viewed as no less trustworthy (Column 3 of
+@tbl-study2regs).
+
+We are not powered to do a comparison across the two experimental groups
+and did not preregister such a difference. Indeed, we find no difference
+in likeability and warmth across the two treatments
 (`r papaja::apa_print(t.test(likable ~ Condition, data = study2_time3, var.equal = T))$statistic`,
@@
 respectively). We also assess the quality of advice by measuring the
-discrepancy between the advised rank and the correct rank. We find
-no difference in accuracy across the advice treatments
+discrepancy between the advised rank and the correct rank. We find no
+difference in accuracy across the advice treatments
 (`r papaja::apa_print(t.test(accuracy ~ Condition, data = study2_time3, var.equal = T))$statistic`).
@@
 
-In Study 3, we replicate the main effect in a different ego-relevant
-domain: intelligence. The experimental design is conceptually identical
-to Study 1, but this time we utilize a more direct measure of
-expectation by asking participants to estimate their scores.
-
-This three-stage experiment begins with measuring actual performance.
-Participants are then anchored to low or high performance expectations
-and asked to guess how many questions they answered correctly. As in
-previous studies, we recruit advisers who are presented with either just
-the advisee's true performance or both the true performance and the
-number of questions the advisee believes they answered correctly.
-Advisers are then asked to provide advice on choosing a competitor.
-Finally, we present the advice to the advisees and ask them to make
-their final choice. Our key hypotheses are: (1) advisees anchored to
-high expectations will be more likely to receive advice to compete
-against the high-performing group, and (2) men will be more likely than
-women to be advised to compete against the high-performing group when
-expectations are disclosed.
+In Study 3, we examine how advisers who want to avoid disappointment may
+inadvertently contribute to gender differences in advice. We ask
+participants to estimate their score on a mathematics test, and
+anticipate that men will guess higher than women. Moreover, we expect
+that advisers take into account the expected score when recommending
+whether someone should compete against a group of High or Low
+performers. As a result, we hypothesize that, when expectations are
+known to advisers, men will be advised to compete against High
+Performers more than women, even when advisers do not know gender and
+expectations are uninformative.
 
@@
 complete a 10-question multiple choice mathematics quiz. The questions
-were taken from a paper-version of the ASVAB standardized exam, such
-that answers were not available online. Participants had five minutes to
-answer the quiz and were paid 10 cents for each correctly answered
-question. Like before, we define top 20 scores as "High Performers" and
-the bottom 20 scorers as the "Low Performers." On average, participants
-answered `r round(mean(study3_math50$Score),2)` questions correctly,
-High Performers scored between `r HP_lower` and `r HP_upper`, and Low
-Performers scored between `r LP_lower` and `r LP_upper`. In order to
-anchor the expectations of participants in our main experiment, we
-simulated 1,000 pairings of groups of five participants, with the
-5<sup>th</sup> percentile of groups scoring an average of `r p5` and the
-95 th percentile scoring an average of `r p95`. We report these averages
-to participants in the Low Expectations and High Expectations treatment,
-respectively.
-
-We then recruited `r scales::comma(dim(study3_time1All)[1])`
-participants for the role of advisees in Stage 1 of our main experiment.
-To arrive at a gender-balanced sample, we dropped the last two male
-participants to complete the survey, ending up with a sample of 500 men
-and 500 women ($M_{\text{Age}}$ = `r mean(study3_time1$Age)`).
-Participants completed the same 10-item mathematics quiz as the earlier
-participants and were informed that their performance would affect their
-bonus earnings in a follow-up stage to be conducted a few days later.
-After completing the quiz, we informed them of the average score of a
-group of five participants from the preliminary survey. We randomly
-assigned them to learn about the 5<sup>th</sup> percentile of groups,
-which scored `r p5`. ("Low Expectations" treatment) or the
-95<sup>th</sup> percentile of groups, which scored `r p95` ("High
-Expectations" treatment). Participants then made a guess
-(unincentivized) about how many questions they think they answered
-correctly. The survey concluded with basic demographic questions.
-
-We then recruited `r scales::comma(dim(study3_time2_giver)[1])`
-participants for Stage 2, placing them in the role of advisers. We began
+are taken from a paper-version of the ASVAB standardized exam, such that
+answers are not available online. Participants have five minutes to
+answer the quiz and are paid 10 cents for each correctly answered
+question. Like in Study 1, we define the top 20 scores as "High
+Performers" and the bottom 20 scorers as the "Low Performers." On
+average, participants answered `r round(mean(study3_math50$Score),2)`
+questions correctly, High Performers scored between `r HP_lower` and
+`r HP_upper`, and Low Performers scored between `r LP_lower` and
+`r LP_upper`. In order to anchor the expectations of participants in our
+main experiment, we simulated 1,000 pairings of groups of five
+participants, with the 5<sup>th</sup> percentile of groups scoring an
+average of `r p5` and the 95 th percentile scoring an average of
+`r p95`. We report these averages to participants in the Low
+Expectations and High Expectations treatment, respectively.
+
+We then recruit `r scales::comma(dim(study3_time1All)[1])` participants
+for the role of advisees in Stage 1 of our main experiment. To arrive at
+a gender-balanced sample, we drop the last two male participants to
+complete the survey, ending up with a sample of 500 men and 500 women
+($M_{\text{Age}}$ = `r mean(study3_time1$Age)`). Participants complete
+the same 10-item mathematics quiz as the earlier participants and are
+informed that their performance would affect their bonus earnings in a
+follow-up stage to be conducted a few days later. After completing the
+quiz, we inform them of the average score of a group of five
+participants from the preliminary survey. We randomly assign them to
+learn about the 5<sup>th</sup> percentile of groups, which scored
+`r p5`. ("Low Expectations" treatment) or the 95<sup>th</sup> percentile
+of groups, which scored `r p95` ("High Expectations" treatment).
+Participants then make an unincentivized guess about how many questions
+they think they answered correctly. The survey concludes with basic
+demographic questions.
+
+We then recruit `r scales::comma(dim(study3_time2_giver)[1])`
+participants for Stage 2, placing them in the role of advisers. We begin
 by informing them of the mathematics quiz that participants in the
-preliminary study and Stage 1 had completed, and informed them of the
-average score of all participants in the preliminary study. Advisers had
-to recommend whether an advisee should compete against the Low
-Performers or the High Performers (we used these terms in the survey).
-We anticipated that being told to compete against High Performers is
-more flattering and hence being told to compete against the Low
-Performers would be disappointing if one had expected to do well.
-Advisees could earn a bonus if their score was equal to or higher than
-that of a randomly selected member from their chosen group. Competing
-against the High Performers was more challenging, resulting in an
-average bonus of 50 cents, compared to 30 cents when competing against
-other groups.
-
-Like before, advisers were randomly assigned to one of two treatments.
-In the "Baseline" treatment, they only observed the score of the advisee
-on the mathematics quiz. In the "Expectation" treatment, they observed
-the score as well as the advisee's guess for how many questions they
-answered correctly. We want to emphasize that sice the outcome is
-determined only by the past score on the quiz, the advisee's guess is
-immaterial to which group they should compete against. Moreover, in
-neither treatment did they receive any demographic information about
-their advisee. Participants gave recommendations to 10 advisees, which
-unbeknownst to them were five men and five women matched to have
-identical performance on the test.[^2] They were informed that if their
-advice was shown to a participant who returned for the follow-up survey,
-they would receive the identical bonus as that participant. The survey
-then concluded with basic demographic questions.
-
-[^2]: We made this decision to account for the possibility of gender
+preliminary study and Stage 1 have completed, and inform them of the
+average score of all participants in the preliminary study. Advisers
+have to recommend whether an advisee should compete against the Low
+Performers or the High Performers (we use these terms in the survey). We
+anticipate that being told to compete against High Performers is more
+flattering and hence being told to compete against the Low Performers
+would be disappointing if one had expected to do well. Advisees would
+earn a bonus if their score is equal to or higher than that of a
+randomly selected member from their chosen group. They earn 50 cents if
+they outperform a High Performer and 30 cents if they outperform a Low
+Performer.
+
+Advisers are randomly assigned to one of two treatments. In the
+"Baseline" treatment, they only observe the score of the advisee on the
+mathematics quiz. In the "Expectation" treatment, they observe the score
+as well as the advisee's guess for how many questions they answered
+correctly. Since the outcome is determined only by the past score on the
+quiz, the advisee's guess is not informative for the recommendation,
+which can be based on the revealed score. Moreover, in neither treatment
+did they receive any demographic information about the advisees.
+Participants give recommendations to 10 advisees, which unbeknownst to
+them are five men and five women matched to have identical performance
+on the test.[^4] They are informed that if their advice is shown to a
+participant who returns for the follow-up survey, they will receive the
+identical bonus as that participant. The survey then concludes with
+basic demographic questions.
+
+[^4]: We made this decision to account for the possibility of gender
     differences in performance.
 
-Finally, we invited participants from Stage 1 back for the follow-up
-survey. Following our preregistration, we kept the survey open for 7
+Finally, we invite participants from Stage 1 back for the follow-up
+survey. Following our preregistration, we keep the survey open for seven
 days. In total, `r scales::comma(dim(study3_time3)[1])` participants
@@
 `r scales::comma(dim(study3_time3[study3_time3$Gender == 'Female',])[1])`
-women) returned. The brief survey reminded them of the task they
-completed in Stage 1, informed them that other participants from
-Prolific had observed their real score and given them advice against
-which group to compete against, and finally were reminded them of how
-many questions they guessed they had answered correctly. Importantly,
-they were not informed of their true score or the score of the groups
-they could compete against. Participants then observed the advice from a
-randomly selected adviser and made their decision.
+women) return. The brief survey reminds them of the task they completed
+in Stage 1, informs them that other participants from Prolific have
+observed their real score and given them advice on which group to
+compete against, and finally are reminded of how many questions they
+guessed they had answered correctly. Importantly, they are not informed
+of their true score or the score of the groups they could compete
+against. Participants then observe the advice from a randomly selected
+adviser and make their decision.
 
@@
 We begin by examining the performance of the Stage 1 participants.
-Because our treatment takes place after participants completed the
+Because our treatment takes place after participants complete the
 mathematics quiz, we would not expect a difference in performance across
-the Low and High Expectations treatments. Indeed, the two groups scored
+the Low and High Expectations treatments. Indeed, the two groups score
 no different from one another
@@
 `r papaja::apa_print(t.test(count ~ Condition, data = study3_time1, var.equal = T))$statistic`).
-The expectations treatment did, however, affect how well they thought
-they performed. Participants in the "Low Expectations" treatment guessed
-a score of
+As intended, the expectations treatment does affect how well they
+thought they performed. Participants in the "Low Expectations" treatment
+guess a score of
 `r round(mean(study3_time1[study3_time1$Condition == "Low",]$count),2)`
@@
 (`r papaja::apa_print(t.test(Guess ~ Condition, data = study3_time1, var.equal = T))$statistic`),
-showing that the manipulation was successful, albeit small. Contrary to
-our expectations, we did find a gender difference in performance: men
-scored
+showing that the manipulation is successful, albeit small. Contrary to
+our expectations, we find a gender difference in performance: men score
 `r round(mean(study3_time1[study3_time1$Gender == "Male",]$count),2)` on
-average, while women scored
+average, while women score
 `r round(mean(study3_time1[study3_time1$Gender == "Female",]$count),2)`
 (`r papaja::apa_print(t.test(count ~ Gender, data = study3_time1, var.equal = T))$statistic`).
-Consistent with this difference, men thought they answered more
-questions correctly than did women
+Consistent with this difference, men think they answered more questions
+correctly than do women
 (`r round(mean(study3_time1[study3_time1$Gender == "Male",]$Guess),2)`
@@
 men do so by only 0.27 points
-`r papaja::apa_print(t.test(overconfidence ~ Gender, data = study3_time1 %>% dplyr::mutate(overconfidence = Guess - count)))$full_result`.
+(`r papaja::apa_print(t.test(overconfidence ~ Gender, data = study3_time1 %>% dplyr::mutate(overconfidence = Guess - count)))$full_result`).
 Although neither gender is overconfident, men on average are more
@@
 All standard errors clustered at the level of the advisor."
+#| after-caption-space: 0pt
 
@@
 
-Next, we examine whether advisers took the advisee's expectations into
+Next, we examine whether advisers take the advisee's expectations into
 account. Column 1 of @tbl-study3regs reports a linear probability model
@@
 the "Expectations" treatment, controlling for the true performance of
-the advisee. Because each adviser made ten recommendations, we cluster
+the advisee. Because each adviser makes ten recommendations, we cluster
 standard errors at the adviser level. However, contrary to our
@@
 
-However, recall that men were more confident in their performance than
-were women. Our theory thus predicts that showing expectations should
+However, recall that men are more confident in their performance than
+are women. Our theory thus predicts that showing expectations should
 lead to more flattering advice (i.e., a recommendation to compete
@@
 when expectations are shown than when they are hidden ($p < 0.001$). We
-show this result graphically in @fig-study3genderdiff.
+show this result graphically in @fig-study3genderdiff. As the figure
+makes clear, this effect is driven by advice given to those who scored
+in the middle of the possible range. Thus, when it is clear that someone
+should compete against Low or High performers, advisers are not
+deferring to expectations.
 
 To examine the quality of advice, we computed the expected bonus
-earnings for someone who followed the recommendations. For example, if
-an adviser suggested competing against the High Performer group, we
-matched the advisee against all 20 members of that group and determined
-how often their score matched or exceeded that of the member. We then
-multiplied this number by the respective bonus earnings (50 cents and 30
+earnings for someone who follows the recommendations. For example, if an
+adviser suggests competing against the High Performer group, we match
+the advisee against all 20 members of that group and determined how
+often their score matches or exceeds that of the member. We then
+multiply this number by the respective bonus earnings (50 cents and 30
 cents for the High and Low Performer group, respectively). To see if
@@
 gender of the advisee, and their interaction in Column 3 of
-@tbl-study3regs. Displaying expectations led men to be advised to
-compete against the High Performer group more often, and this advise
-turned out to be bad: men receive worse advise than do women when
-expectations are displayed, but not in their absence.[^3]
-
-[^3]: This analysis was not preregistered, and we note here that the
+@tbl-study3regs. Displaying expectations leads men to be advised to
+compete against the High Performer group more often, and this advice
+turns out to be costly: men receive worse advise than do women when
+expectations are displayed, but not in their absence.[^5]
+
+[^5]: This analysis was not preregistered, and we note here that the
     reduction in expected earnings is small. However, it is interesting
@@
     their performance on average. One possibility is that advisers
-    suggest the High Performer group more often than is optimal. We
-    return to the possibility that advice is overall biased to be
-    flattering in Study 2.
+    suggest the High Performer group more often than is optimal. This is
+    consistent with our finding from Study 2, in which participants
+    offered flattering advice even when incentivized only for accuracy.
 
@@
 The former considers only the main effect, while the latter also includes the interactive effect."
+#| after-caption-space: 0pt
 
@@
 flattering advice, recognizing it as such and thus failing to adhere to
-it. Align with our prediction, participants who were primed with high
-expectations earned less when their expectations were conveyed to the
+it. In line with our prediction, participants who are primed with high
+expectations earn less when their expectations are shown to the
 advisers, although this result is only directional (see Column 1 of
 @tbl-study3time3). Similarly, as shown in Column 2 of @tbl-study3time3,
-we also found that male participants received less reward when their
-expectations were presented, even when their performance was the same.
-These findings suggest that flattering advice is not without
-consequences. Furthermore, our research indicates that because males are
+we also find that male participants earn less when their expectations
+are shown. These findings suggest that flattering advice is not without
+consequences. Furthermore, our research indicates that because men are
 more likely to follow such advice (see Column 4 of @tbl-study3time3),
-their tendency towards competition intensifies the cost of such advice.
+they compete more as a result of flattering advice.
 
@@
 
-We found supportive evidence for our argument in a different domain.
-Advisors tend to consider advisees' self-expectations and match their
-advice accordingly, aiming to avoid disappointment. Consistent with the
-confidence gap narrative, men tend to underestimate their mathematics
-test scores less than women. When these expectations are displayed to
-advisors, they are more likely to advise men to compete against high
-performers. Notably, this turns out to be poor advice: men whose
-advisors were aware of their expectations received worse advice. Our
+Our findings suggest that attempts to avoid disappointment can be a
+novel source of gender differences in advice. Women underestimate their
+mathematics test scores more than men. When these expectations are shown
+to advisors, they are more likely to tell men to compete against high
+performers than women. Notably, this turns out to be poor advice: men
+whose advisors are aware of their expectations receive worse advice. Our
 findings suggest that men with the same scores as their female
-counterparts ended up earning less, although this result is only
+counterparts end up earning less, although this result is only
 directional. This discrepancy may be due to men receiving more favorable
@@
 outcomes.
-
-<!-- David: One more sentence about the earnings difference here, which does not -->
-
-<!-- differ significantly. And one sentence about the new analysis of whether -->
-
-<!-- people follow the advice or not. -->
 
@@
 avoid information and avoid seeking help [@Benabou2022; @Golman2017;
-@Jaroszewicz2022]. We present evidence from two experiments that
+@Jaroszewicz2022]. We present evidence from three experiments that
 advisers are also cognizant of this cost. As a result, they present
@@
 flattering advice comes at a cost to advisees, who would do worse if
-they followed it blindly, as we show in Study 1.
+they followed it blindly.
 

### 2025-01-28 manuscript/manuscript.tex
Revised version :)

@@
 
-\par{     The authors are grateful to XXX for their helpful comments.  }
+\par{       }
 \par{Correspondence concerning this article should be addressed
@@
 obtain more rewarding positions (Kanze et al., 2018). Research on gender
-discrimination has focused on the role of unconscious bias (Greenwald et
-al., 2009; Greenwald \& Banaji, 1995), but interventions that try to
+discrimination has focused on the role of unconscious bias (Banaji \&
+Greenwald, 1995; Nosek et al., 2009), but interventions that try to
 reduce this bias have been largely unsuccessful (Chang et al., 2019;
@@
 novel source of differences in advice by drawing on recent work on
-belief-based utility, expectation-based reference points (Köszegi, 2006;
-Kőszegi \& Rabin, 2009), and the hedonic consequences of information
-(Golman et al., 2017).
+belief-based utility, expectation-based reference points (Kőszegi \&
+Rabin, 2006, 2009), and the hedonic consequences of information (Golman
+et al., 2017).
 
@@
 deriving belief-based utility from maintaining favorable views of
-themselves (Golman et al., 2017; Loewenstein \& Molnar, 2018;
-\textbf{Ho2018?}). Moreover, they often prefer advisers who withhold bad
-news from them (Shalvi et al., 2019) and punish those who communicate
-bad news (John et al., 2019). Advisers, anticipating these preferences
-and consequences face a dilemma: Should they provide the accurate but
+themselves (Golman et al., 2017; Ho et al., 2021; Loewenstein \& Molnar,
+2018). Moreover, they often prefer advisers who withhold bad news from
+them (Shalvi et al., 2019) and punish those who communicate bad news
+(John et al., 2019). Advisers, anticipating these preferences and
+consequences face a dilemma: Should they provide the accurate but
 potentially painful truth, or shade their recommendations to preserve
@@
 outcome for the recipient, particularly when it is not clear what would
-have happened under a counterfactual.\^{}{[}In some cases, however,
-repeated interaction might also increase incentives for honest feedback.
-Someone who is known to persistently give overoptimistic advice may be
-viewed as less trustworthy in the long run.{]}
+have happened under a counterfactual.\footnote{In some cases, however,
+  repeated interaction might also increase incentives for honest
+  feedback. Someone who is known to persistently give overoptimistic
+  advice may be viewed as less trustworthy in the long run.}
 
@@
 the ability quiz, we do not expect a difference in performance across
-the Low and High Default treatments. Indeed, the two groups scored no
-different from one another (5.1 and 5.18 for the Low Default and High
-Default treatments, respectively, \(t(199) = 0.31\), \(p = .756\)). The
-default manipulation affected their initial choices. In the ``Low
-Default'' treatment, only 22\% of participants initially preferred
-competing against the High Performer Group, compared to 65\% of
-participants who saw the High Performer Group highlighted (\(\chi^2\)(1,
-n = 201) = 36.62, p \textless{} .001).
+the Low and High Default treatments. Indeed, the two groups score no
+different from one another (5.10 and 5.18 for the Low Default and High
+Default treatments, respectively, \(t(199) = 0.31\), \(p = .756\)). As
+expected, the default manipulation changes their initial choices. In the
+``Low Default'' treatment, only 22\% of participants prefer to compete
+against the High Performer Group, compared to 65\% of participants in
+the ``High Default'' treatment (\(\chi^2\)(1, n = 201) = 36.62, p
+\textless{} .001).
+
+\linespread{1}
 
@@
 1. Displaying the non-binding choice of those for whom the Low Performer
-Group was selected by default makes it more likely that they are advised
+Group was selected by default makes it less likely that they are advised
 to compete against the High Performer Group (Column 1). Column 2
-restricts the analysis to advisers who observed advisees' initial
+restricts the analysis to advisers who observe advisees' initial
 non-binding choice and controls for advisees' score on the quiz.
 Standard errors are clustered at the adviser
-level.}{\label{tbl-study1regs}}}
-\vspace{-20pt}}
+level.}{\label{tbl-study1regs}}}\vspace{0pt}
+}
 
@@
 colspec={Q[]Q[]Q[]},
-column{2,3}={}{halign=c,},
+column{3}={}{halign=c,},
 column{1}={}{halign=l,},
-hline{12}={1,2,3}{solid, black, 0.05em},
+cell{2}{2}={}{halign=c,},
+cell{3}{2}={}{halign=c,},
+cell{4}{2}={}{halign=c,},
+cell{5}{2}={}{halign=c,},
+cell{6}{2}={}{halign=c,},
+cell{7}{2}={}{halign=c,},
+cell{8}{2}={}{halign=c,},
+cell{9}{2}={}{halign=c,},
+cell{10}{2}={}{halign=c,},
+cell{11}{2}={}{halign=c,},
+cell{12}{2}={}{halign=c,},
+cell{13}{2}={}{halign=c,},
+cell{1}{2}={c=2,}{halign=c, halign=c,},
+hline{13}={1,2,3}{solid, black, 0.05em},
 }                     %% tabularray inner close
 \toprule
-& (1) & (2) \\ \midrule %% TinyTableHeader
+& Advice to Compete Against High Performers &  \\ \cmidrule[lr]{2-3}
+& All Advice & Expectations Shown \\ \midrule %% TinyTableHeader
 High Default               & \num{0.011}    & \num{0.025}*    \\
@@
 & (\num{0.019})  &                  \\
-Performance                &                 & \num{0.168}***  \\
+Score                      &                 & \num{0.168}***  \\
 &                 & (\num{0.004})   \\
@@
 
-We now examine whether advisers took the advisees' expectations into
-account. Recall that advisees who were defaulted to competing against
-the High Performer Group were indeed more likely to choose this group,
-which, from the advisers' perspective, could signal high confidence in
-their abilities. Our theory predicts that showing expectations should
-lead to more flattering advice--- specifically, a recommendation to
-compete against the High Performer Group--- for advisees with a high
-default choice compared to those with a low default choice. Column 1 of
-Table~\ref{tbl-study1regs} reports a linear probability model with
-advice to compete against the high group as the outcome measure,
-incorporating the default choice advisees saw, whether expectations were
-shown to the adviser, and the interaction of the two. Because each
-adviser made ten recommendations, we cluster standard errors at the
-adviser level. As predicted, we find a marginally significant
-interaction effect: advisees with a default choice to compete against
+We now examine whether advisers take the advisees' expectations into
+account. Advisers observe the true performance of the advisee, such that
+expectations about performance add no additional information. However,
+because participants who score higher are also more likely to pick the
+High Performer Group, we use our Default treatment as an instrument that
+reflect higher expectations. We show linear probability models for the
+decision of the Advisers, which is equal to 1 if they recommend
+competing against the High Performer Group and 0 if they recommend the
+Low Performer Group. In Column 1 of Table~\ref{tbl-study1regs}, we show
+our main specificiation with the experimental assignment for Advisees
+(High Performer Default vs.~Low Performer Default) and Advisers
+(Expectation Shown vs.~Expectation Hidden), as well as their
+interaction. Because each adviser made ten recommendations, we cluster
+standard errors at the adviser level. We find that displaying
+expectations of those in the Low Performer Default reduces
+recommendations to compete against the Top group by 4 percentage points,
+or about 10\% relative to when expectations are hidden. This decrease is
+marginally smaller for advisees with a default choice to compete against
 the High Performer Group (nudged to have high expectations, though not
-necessarily holding them) were more likely to receive advice to compete
-against stronger competitors when their expectations were shown compared
-to when they were hidden. We reported a linear probability model on
-advising to compete against the High Performer group for advisers in the
-``Expectations'' treatment, controlling for the true performance of the
-advisee in Column 2 of Table~\ref{tbl-study1regs}. We observe a
-significant main effect of the default treatment, where a high default
-increased the likelihood of receiving flattering advice. It is worth
-noting that, since only 65 \% of advisees in the high default group
-actually stuck with their default choice, this represents a conservative
-test of the effect of high expectations on the likelihood of receiving
-flattering advice.
+necessarily holding them), and whose advice did not differ based on
+whether their expectations were shown or hidden. We reported a linear
+probability model on advising to compete against the High Performer
+group for advisers in the ``Expectations'' treatment, controlling for
+the true performance of the advisee in Column 2 of
+Table~\ref{tbl-study1regs}. We observe a significant main effect of the
+default treatment, where a high default increased the likelihood of
+receiving flattering advice. It is worth noting that, since only 65 \%
+of advisees in the high default group actually stuck with their default
+choice, this represents a conservative test of the effect of high
+expectations on the likelihood of receiving flattering advice.
 
@@
 
-\caption{\label{fig-study1Advice}Advisees who were nudged to express
-high expectations were more likely to receive advice to compete against
-the High Performer Group.}
+\caption{\label{fig-study1Advice}Advice given in Study 1. Advisees who
+were nudged to express high expectations were more likely to receive
+advice to compete against the High Performer Group.}
 
@@
 
-When the quality of a decision does not depend on someone's
-expectations, the adviser's awareness of the advisee's expectations
-should not influence the advice given. However, in line with our
-argument that advisers take into account the belief utility of the
-advisee and prefer to flatter rather than disappoint, we find that
-displaying the advisee's expectations does make a difference.
+When an adviser knows an outcome that an advisee can only estimate,
+learning this estimate should not change the advice that is given.
+However, in line with our argument that advisers take into account the
+belief utility of the advisee and prefer to avoid disappointing them, we
+find that providing information about expectations makes a difference.
 Specifically, advisees who expressed a preference for stronger
-competitors were more likely to receive `flattering' advice, encouraging
-them to pursue that option. One possible explanation for this finding is
-that, rather than trying to flatter, advisers may simply be telling
-advisees what they want to hear. In the next study, we aim to
-investigate the mechanism behind this discrepancy in advice-giving when
-expectations are revealed, exploring the question: Why do people give
-flattering advice?
+competitors were more likely to receive flattering advice, encouraging
+them to pursue that option. This occurs even though advisers are
+incentivized to give good advice.
 
@@
 
-So far, we have shown that displaying expectations influences the advice
-given. Specifically, advisers were more likely to recommend competing
-against a group of high performers to advisees with higher performance
-expectations compared to those without. We now directly test whether
-this effect is driven by interpersonal concerns. In particular, we
-explore whether more flattering advice stems from a desire to be liked,
-and whether advisees, in turn, like advisers more when they receive
-flattering advice.
-
-We conducted a three-stage experiment in which we experimentally
-manipulated the incentives for advisers. We began by inviting a group of
-advisees to upload photos of themselves (``selfies'') and informed them
-that they would be rated on their attractiveness. We grouped them with
-nine other participants of the same gender and recruited participants of
-the opposing gender to rank them from most to least attractive and to
-provide advice. Specifically, we asked them to advise the participant
-they ranked as the 7th most attractive (4th least attractive) on what
-rank they should bet they were ranked by a larger group of raters.
-Advisers were randomly assigned to two treatments, receiving a bonus
-payment either if the advisee guessed their rank accurately or if the
-advisee evaluated the adviser as likeable as measured by an
-unincentivized scale response. We hypothesize that advisers who want to
-be liked by advisees will recommend that they bet on a lower rank,
-i.e.~that they are more attractive.
+We next examine if advisers believe that flattering advice will improve
+how they are perceived, and if so, whether this perception is true. We
+do this by manipulating the incentives for advisers, who receive a bonus
+either based on how they are evaluated by an advisee, or a bonus for the
+advisee's accuracy.
+
+The study takes place in three stages. First, a group of advisees upload
+photos of themselves (``selfies'') and are grouped with nine other
+participants of the same sex We then recruit participants of the
+opposing sex to rank them from most to least attractive and to provide
+advice. Specifically, they advise the participant they ranked as the 7th
+most attractive (i.e., 4th least attractive) on what rank they should
+bet they were ranked by a larger group of raters. Advisers were randomly
+assigned to two treatments, receiving a bonus payment either if the
+advisee guessed their rank accurately or if the advisee evaluated the
+adviser as likeable as measured by a scale response. We hypothesize that
+advisers incentivized to be liked will recommend betting on a lower
+rank, i.e.~that the advisee is more attractive.
 
@@
 
-We recruited 300 participants from Prolific and, after asking
-demographic questions, invited them to upload photos of themselves
-(selfies) to be rated by other participants on attractiveness. 100 men
-and 107 women agreed to do so and uploaded pictures that adhered to our
-instructions (e.g., did not include other people). We selected the first
-100 photos from women to arrive at a gender-balanced sample
-(\(M_{\text{Age}}\) = 39.37 years). Participants were informed that
-their selfies would be randomly grouped with those of nine other
-participants of their gender and ranked in terms of attractiveness by a
-group of new Prolific participants of the opposite gender. Lastly, they
-guessed their rank (unincentivized).
-
-Next, we recruited a new, gender-balanced sample for the role of
-advisers. 472 participants from Prolific (\(M_{\text{Age}}\) =
-41.0275424 years; 49.79\% Female) started by providing demographic
-information, then were matched to a group of the opposite gender. They
-then ranked participants from most to least attractive using a drop-down
-menu next to each picture. Because of a limitation with the survey
-software, participants were able to select the same rank for multiple
-participants, rather than rank them uniquely. We remove 115 participants
-who did not follow instructions and provide a unique ranking.
-
-After submitting their ratings, they saw the photo of the participant
-they had ranked as the 7th most attractive (i.e., the 4th least
-attractive). They were reminded of the rank they had given to that
-person and informed that this participant would be invited back and
-could earn a \$1 bonus if they guessed their rank correctly. The rank
-was determined by the aggregate ratings of all participants who had
-ranked this group. Their task was to give advice to this participant
-about the rank they should bet on based on having observed all ten
-selfies and their own assessment. We randomly assigned participants to
-one of two incentivization schemes. In the ``Accuracy'' treatment, they
-received a bonus identical to the advisee: \$1 if they guessed their
-rank correctly. In the ``Likeability'' treatment, we informed them that
-they would be rated by the advisee on a 5-point Likert scale for how
-likeable they thought they were. Each point on the scale would translate
-to a bonus of 20 cents. They then selected a rank that they would
-recommend the advisee to bet on.
-
-Finally, we invited participants from Stage 1 and were ranked as the 7th
-attractive by at least one adviser (so that they received advice) back
-for the follow-up survey. Following our preregistration, we kept the
-survey open for 7 days. In total, 146 participants (77 men, 69 women)
-returned. They were reminded of the selfie they uploaded in Stage 1 and
-informed that a group of 10 selfies, including theirs, had been rated by
-other participants from Prolific. They then saw the advice from a
-randomly selected adviser and made their estimate with a \$1 incentive
-for guessing accurately. They then saw the rank they had been advised to
-bet on one more time and were asked to rate the adviser's likability,
-warmth, friendliness, good-naturedness, trustworthiness, and sincerity
-on 5-point Likert scales (adapted from Fiske et al. (2007)).
+We recruit 300 participants from Prolific and, after asking demographic
+questions, invite them to upload photos of themselves (selfies) to be
+rated by other participants on attractiveness. We obtain selfies from
+100 men and 107 women adhering to our instructions (e.g., did not
+include other people). In line with our preregistration, we select the
+first 100 photos from women to arrive at a gender-balanced sample
+(\(M_{\text{Age}}\) = 39.37 years). Participants are informed that their
+selfies will be randomly grouped with those of nine other participants
+of their sex and ranked in terms of attractiveness by a group of new
+Prolific participants of the opposite sex. They then make an
+unincentivized guess of their rank.
+
+Next, we recruit 472 participants from Prolific for the role of advisers
+(\(M_{\text{Age}}\) = 41.0275424 years; 49.79\% Female). We first
+collect demographic information, then match them to a group of the
+opposite sex. They rank selfies from ten participants from most to least
+attractive using a drop-down menu next to each picture. Because of a
+limitation with the survey software, we could not validate that each
+rank is given only once, and we remove 115 participants who failed to
+follow instructions and did not provide a complete ranking.\footnote{Moreover,
+  we could not collect data from any participant who did not select any
+  participant as the 7th most attractive participant, as that image
+  would be shown on subsequent pages.}
+
+After submitting their ratings, participants see the photo of the
+participant they ranked as the 7th most attractive (i.e., the 4th least
+attractive). We remind them of the rank they have just given to that
+person and inform them that this participant will be invited back and
+can earn a \$1 bonus if they correctly guess their rank. The rank is
+determined by the aggregate ratings of all participants who have ranked
+this group. Because the participant does not observe the other nine
+people in the group, they would depend on the adviser's recommendation
+along with their own assessment. We randomly assign advisers to one of
+two incentivization schemes. In the ``Accuracy'' treatment, they receive
+a bonus identical to the advisee: \$1 if they guess their rank
+correctly. In the ``Likeability'' treatment, we inform them that the
+advisee will rate them on a 5-point Likert scale on how likeable they
+thought they are. Each point on the scale would translate to a bonus of
+20 cents. Advisers then select a rank (from 1 to 10) that they recommend
+the advisee to bet on.
+
+Finally, we invite participants from Stage 1 who were ranked as the 7th
+most attractive participant by at least one adviser (so that they
+received advice) back for the follow-up survey. Following our
+preregistration, we keep the survey open for 7 days. In total, 146
+participants (77 men, 69 women) complete the follow-up survey. We remind
+them of the selfie they uploaded in Stage 1 and that a group of 10
+selfies, including theirs, had been rated by other participants from
+Prolific. They then see the advice from a randomly selected adviser and
+make their own guess with a \$1 incentive for accuracy. Finally, they
+rate the adviser's likability, warmth, friendliness, good-naturedness,
+trustworthiness, and sincerity on 5-point Likert scales (adapted from
+Fiske et al., 2007).
 
@@
 
-\caption{\label{fig-study2advice}Advisers were asked to suggest what
-rank to bet on for someone they ranked as the 7th most attractive out of
-ten people. When incentivized for accuracy, most of them advised betting
-on 7, which was based on their evaluation of the recipient's
-attractiveness. However, when incentivized for likability, many
-participants gave flattering advice by suggesting betting on higher
-ranks that imply a higher evaluation of attractiveness.}
+\caption{\label{fig-study2advice}Participants in Study 2 give advice to
+the person they rank 7th most attractive out of 10. When incentivized
+for accuracy, the majority recommends betting on that rank. However,
+when incentivized for likeability, participants inflate their advice to
+flatter the recipient as more attractive.}
 
@@
 We begin by examining the prior beliefs of advisees who uploaded their
-selfies. On average, men guessed they ranked 5.76 in their group of 10
-and women guessed that they ranked 6.37. Participants overall
-underestimate their attractiveness relative to the benchmark average of
-5.5. Moreover, women do so more than men \(t(205) = 2.15\),
-\(p = .033\). Notably, people's self-perceptions correlated strongly
-with the aggregate ratings of the advisers (0.43, \(t(193) = 6.70\),
-\(p < .001\)). However, there was substantial heterogeneity in
-perceptions of attractiveness. Of the 200 participants, 149 were ranked
-as 7th most attractive by at least one adviser. On average, men in this
-subset estimated they were ranked 5.94th and women estimated they were
-ranked 6.59th (\(t(143) = 1.94\), \(p = .054\)).
-
-Next, we turn our attention to the advisers
-(Figure~\ref{fig-study2advice}). In the Accuracy condition, those
-uploading selfies were advised to bet on rank 6.19. Notably, this is
-significantly more attractive than the 7th rank those advisers had
-themselves guessed just on the prior screen (\(t(234) = -8.82\),
+selfies. On average, men guess they rank 5.76 in their group of 10 and
+women guess that they rank 6.37 (\(t(205) = 2.15\), \(p = .033\)).
+Notably, people's self-perceptions correlate strongly with the aggregate
+ratings of the advisers (0.43, \(t(193) = 6.70\), \(p < .001\)).
+However, there is substantial heterogeneity in perceptions of
+attractiveness. Of the 200 participants, 149 are ranked as 7th most
+attractive by at least one adviser. On average, men in this subset
+estimate they rank 5.94th and women estimate they rank 6.59th
+(\(t(143) = 1.94\), \(p = .054\)).
+
+Next, we turn our attention to the advisers (see
+Figure~\ref{fig-study2advice}). In the Accuracy condition, those
+uploading selfies are on average advised to bet on rank 6.19. Notably,
+this is significantly more attractive than the 7th rank those advisers
+had themselves guessed just on the prior screen (\(t(234) = -8.82\),
 \(p < .001\)). This suggests that even when incentivized for accuracy,
-participants offered flattering advice.\footnote{This shading could be
-  due to concerns of avoiding disappointment. However, it could also be
-  that advisers are uncertain about the rankings they had given and make
-  a recommendation that combines their own belief with a uniform prior.}
-Importantly, and as predicted, we find that advisers in the Likeable
-treatment recommend betting on a lower rank, communicating that they
-think the participant in the selfie is more attractive (5.38,
-\(t(470) = 5.44\), \(p < .001\)). This suggests that advisers inferred
-that advising someone that they were more attractive would make the
-adviser appear more likeable and therefore provided advice that
-communicated a more favorable impression of the participants'
-attractiveness. The distribution shown in Figure~\ref{fig-study2advice}
+participants offer flattering advice.\footnote{This shading could be due
+  to concerns of avoiding disappointment. However, it could also be that
+  advisers are uncertain about the rankings they have given and make a
+  recommendation that combines their own belief with a uniform prior.
+  Therefore, our analyses focus on the difference between the two
+  conditions.} Importantly, and as predicted, we find that advisers in
+the Likeable treatment recommend betting on a lower rank, communicating
+that they think the participant in the selfie is more attractive (5.38,
+\(t(470) = 5.44\), \(p < .001\)). This suggests that advisers infer
+flattering someone with pleasant advice would make the adviser appear
+more likeable. The distribution shown in Figure~\ref{fig-study2advice}
 shows that participants do not simply tell participants that they are
@@
 are rated as more trustworthy when they advice lower ranks, but this
-relationship is only directional.}{\label{tbl-study2regs}}}
-\vspace{-20pt}}
+relationship is only directional.}{\label{tbl-study2regs}}}\vspace{0pt}
+}
 
@@
 
-\caption{\label{fig-study2ratingByGroup}After participants received
-advice that suggested betting on a rank that was lower than, equal to,
-or higher than their self-expectations, they evaluated advisors based on
-their likability and warmth. Participants rated advisors who gave
-flattering advice and delivered a high evaluation of their
-attractiveness as more likable and warm than those whose advice implied
-a lower evaluation of their attractiveness.}
+\caption{\label{fig-study2ratingByGroup}After participants receive
+advice that suggests betting on a rank that was lower than, equal to, or
+higher than their own guess, they evaluate advisors based on their
+likability and warmth. Participants rate advisors who give flattering
+advice and deliver a high evaluation of their attractiveness as more
+likable and warm than those whose advice implied a lower evaluation of
+their attractiveness.}
 
@@
 
-As seen in Figure~\ref{fig-study2rating}, we found that advisees who
-suggested that the advisee was more attractive (lower rank) were indeed
-rated as more likeable and warm (b = -0.109, p \textless{} .05; b =
--0.133, p \textless{} .001, respectively; See Columns 1 and 2 of
-Table~\ref{tbl-study2regs}). When using their self-expectations as a
-reference point, advisors who suggest a rank lower than that point are
-perceived as less likable and warm (see
-Figure~\ref{fig-study2ratingByGroup}). Interestingly, these benefits are
-not at the cost of being hypocritical; advisers who recommend a more
-favorable rank are viewed as no less trustworthy (Column 3 of
-Table~\ref{tbl-study2regs}).
-
-We were not powered to do a comparison across the two experimental
-groups and did not preregister such a difference. Indeed, we find no
-difference in likeability and warmth across the two treatments
-(\(t(144) = 1.09\), \(p = .275\), and \(t(144) = 0.58\), \(p = .562\),
-respectively). We also assess the quality of advice by measuring the
-discrepancy between the advised rank and the final rank. Our analysis
-revealed no significant difference between the two treatments in terms
-of how helpful the advice was for advisees in making accurate guesses,
-\(t(144) = -0.29\), \(p = .776\).
+As seen in Figure~\ref{fig-study2rating}, we advisers who suggested that
+the advisee was more attractive (lower rank) were indeed rated as more
+likeable and warm (b = -0.109, p \textless{} .05; b = -0.133, p
+\textless{} .001, respectively; See Columns 1 and 2 of
+Table~\ref{tbl-study2regs}). When using their own initial guess as a
+reference point, advisers who suggest a worse rank are perceived as less
+likable and warm (see Figure~\ref{fig-study2ratingByGroup}).
+Interestingly, these benefits are not at the cost of sincerity; advisers
+who recommend a more favorable rank are viewed as no less trustworthy
+(Column 3 of Table~\ref{tbl-study2regs}).
+
+We are not powered to do a comparison across the two experimental groups
+and did not preregister such a difference. Indeed, we find no difference
+in likeability and warmth across the two treatments (\(t(144) = 1.09\),
+\(p = .275\), and \(t(144) = 0.58\), \(p = .562\), respectively). We
+also assess the quality of advice by measuring the discrepancy between
+the advised rank and the correct rank. We find no difference in accuracy
+across the advice treatments (\(t(144) = -0.29\), \(p = .776\)).
 
@@
 to complete a 10-question multiple choice mathematics quiz. The
-questions were taken from a paper-version of the ASVAB standardized
-exam, such that answers were not available online. Participants had five
-minutes to answer the quiz and were paid 10 cents for each correctly
-answered question. Like before, we define top 20 scores as ``High
-Performers'' and the bottom 20 scorers as the ``Low Performers.'' On
-average, participants answered 4.42 questions correctly, High Performers
-scored between 5 and 10, and Low Performers scored between 0 and 3. In
-order to anchor the expectations of participants in our main experiment,
-we simulated 1,000 pairings of groups of five participants, with the 5th
-percentile of groups scoring an average of 2.6 and the 95 th percentile
-scoring an average of 6.4. We report these averages to participants in
-the Low Expectations and High Expectations treatment, respectively.
-
-We then recruited 1,002 participants for the role of advisees in Stage 1
-of our main experiment. To arrive at a gender-balanced sample, we
-dropped the last two male participants to complete the survey, ending up
-with a sample of 500 men and 500 women (\(M_{\text{Age}}\) = 42.16).
-Participants completed the same 10-item mathematics quiz as the earlier
-participants and were informed that their performance would affect their
+questions are taken from a paper-version of the ASVAB standardized exam,
+such that answers are not available online. Participants have five
+minutes to answer the quiz and are paid 10 cents for each correctly
+answered question. Like in Study 1, we define the top 20 scores as
+``High Performers'' and the bottom 20 scorers as the ``Low Performers.''
+On average, participants answered 4.42 questions correctly, High
+Performers scored between 5 and 10, and Low Performers scored between 0
+and 3. In order to anchor the expectations of participants in our main
+experiment, we simulated 1,000 pairings of groups of five participants,
+with the 5th percentile of groups scoring an average of 2.6 and the 95
+th percentile scoring an average of 6.4. We report these averages to
+participants in the Low Expectations and High Expectations treatment,
+respectively.
+
+We then recruit 1,002 participants for the role of advisees in Stage 1
+of our main experiment. To arrive at a gender-balanced sample, we drop
+the last two male participants to complete the survey, ending up with a
+sample of 500 men and 500 women (\(M_{\text{Age}}\) = 42.16).
+Participants complete the same 10-item mathematics quiz as the earlier
+participants and are informed that their performance would affect their
 bonus earnings in a follow-up stage to be conducted a few days later.
-After completing the quiz, we informed them of the average score of a
+After completing the quiz, we inform them of the average score of a
 group of five participants from the preliminary survey. We randomly
-assigned them to learn about the 5th percentile of groups, which scored
+assign them to learn about the 5th percentile of groups, which scored
 2.6. (``Low Expectations'' treatment) or the 95th percentile of groups,
 which scored 6.4 (``High Expectations'' treatment). Participants then
-made a guess (unincentivized) about how many questions they think they
-answered correctly. The survey concluded with basic demographic
+make an unincentivized guess about how many questions they think they
+answered correctly. The survey concludes with basic demographic
 questions.
 
-We then recruited 1,000 participants for Stage 2, placing them in the
-role of advisers. We began by informing them of the mathematics quiz
-that participants in the preliminary study and Stage 1 had completed,
-and informed them of the average score of all participants in the
-preliminary study. Advisers had to recommend whether an advisee should
-compete against the Low Performers or the High Performers (we used these
-terms in the survey). We anticipated that being told to compete against
-High Performers is more flattering and hence being told to compete
-against the Low Performers would be disappointing if one had expected to
-do well. Advisees could earn a bonus if their score was equal to or
-higher than that of a randomly selected member from their chosen group.
-Competing against the High Performers was more challenging, resulting in
-an average bonus of 50 cents, compared to 30 cents when competing
-against other groups.
-
-Like before, advisers were randomly assigned to one of two treatments.
-In the ``Baseline'' treatment, they only observed the score of the
-advisee on the mathematics quiz. In the ``Expectation'' treatment, they
-observed the score as well as the advisee's guess for how many questions
-they answered correctly. We want to emphasize that sice the outcome is
-determined only by the past score on the quiz, the advisee's guess is
-immaterial to which group they should compete against. Moreover, in
-neither treatment did they receive any demographic information about
-their advisee. Participants gave recommendations to 10 advisees, which
-unbeknownst to them were five men and five women matched to have
+We then recruit 1,000 participants for Stage 2, placing them in the role
+of advisers. We begin by informing them of the mathematics quiz that
+participants in the preliminary study and Stage 1 have completed, and
+inform them of the average score of all participants in the preliminary
+study. Advisers have to recommend whether an advisee should compete
+against the Low Performers or the High Performers (we use these terms in
+the survey). We anticipate that being told to compete against High
+Performers is more flattering and hence being told to compete against
+the Low Performers would be disappointing if one had expected to do
+well. Advisees would earn a bonus if their score is equal to or higher
+than that of a randomly selected member from their chosen group. They
+earn 50 cents if they outperform a High Performer and 30 cents if they
+outperform a Low Performer.
+
+Advisers are randomly assigned to one of two treatments. In the
+``Baseline'' treatment, they only observe the score of the advisee on
+the mathematics quiz. In the ``Expectation'' treatment, they observe the
+score as well as the advisee's guess for how many questions they
+answered correctly. Since the outcome is determined only by the past
+score on the quiz, the advisee's guess is not informative for the
+recommendation, which can be based on the revealed score. Moreover, in
+neither treatment did they receive any demographic information about the
+advisees. Participants give recommendations to 10 advisees, which
+unbeknownst to them are five men and five women matched to have
 identical performance on the test.\footnote{We made this decision to
   account for the possibility of gender differences in performance.}
-They were informed that if their advice was shown to a participant who
-returned for the follow-up survey, they would receive the identical
-bonus as that participant. The survey then concluded with basic
-demographic questions.
-
-Finally, we invited participants from Stage 1 back for the follow-up
-survey. Following our preregistration, we kept the survey open for 7
-days. In total, 951 participants (481 men, 470 women) returned. The
-brief survey reminded them of the task they completed in Stage 1,
-informed them that other participants from Prolific had observed their
-real score and given them advice against which group to compete against,
-and finally were reminded them of how many questions they guessed they
-had answered correctly. Importantly, they were not informed of their
-true score or the score of the groups they could compete against.
-Participants then observed the advice from a randomly selected adviser
-and made their decision.
+They are informed that if their advice is shown to a participant who
+returns for the follow-up survey, they will receive the identical bonus
+as that participant. The survey then concludes with basic demographic
+questions.
+
+Finally, we invite participants from Stage 1 back for the follow-up
+survey. Following our preregistration, we keep the survey open for seven
+days. In total, 951 participants (481 men, 470 women) return. The brief
+survey reminds them of the task they completed in Stage 1, informs them
+that other participants from Prolific have observed their real score and
+given them advice on which group to compete against, and finally are
+reminded of how many questions they guessed they had answered correctly.
+Importantly, they are not informed of their true score or the score of
+the groups they could compete against. Participants then observe the
+advice from a randomly selected adviser and make their decision.
 
@@
 We begin by examining the performance of the Stage 1 participants.
-Because our treatment takes place after participants completed the
+Because our treatment takes place after participants complete the
 mathematics quiz, we would not expect a difference in performance across
-the Low and High Expectations treatments. Indeed, the two groups scored
+the Low and High Expectations treatments. Indeed, the two groups score
 no different from one another (4.79 and 4.55 for the Low Expectations
 and High Expectations treatments, respectively, \(t(998) = -1.64\),
-\(p = .102\)). The expectations treatment did, however, affect how well
-they thought they performed. Participants in the ``Low Expectations''
-treatment guessed a score of 4.79 vs.~4.42 in the High Expectations
-treatment (\(t(998) = 3.78\), \(p < .001\)), showing that the
-manipulation was successful, albeit small. Contrary to our expectations,
-we did find a gender difference in performance: men scored 5.02 on
-average, while women scored 4.33 (\(t(998) = -4.73\), \(p < .001\)).
-Consistent with this difference, men thought they answered more
-questions correctly than did women (4.75 vs 3.56, \(t(998) = -8.60\),
+\(p = .102\)). As intended, the expectations treatment does affect how
+well they thought they performed. Participants in the ``Low
+Expectations'' treatment guess a score of 4.79 vs. 4.42 in the High
+Expectations treatment (\(t(998) = 3.78\), \(p < .001\)), showing that
+the manipulation is successful, albeit small. Contrary to our
+expectations, we find a gender difference in performance: men score 5.02
+on average, while women score 4.33 (\(t(998) = -4.73\), \(p < .001\)).
+Consistent with this difference, men think they answered more questions
+correctly than do women (4.75 vs 3.56, \(t(998) = -8.60\),
 \(p < .001\)). This difference, however, does not affect the
@@
 We observe that women underestimate their performance by 0.76 points,
-while men do so by only 0.27 points \(\Delta M = -0.49\), 95\% CI
-\([-0.73, -0.25]\), \(t(997.87) = -4.03\), \(p < .001\). Although
+while men do so by only 0.27 points (\(\Delta M = -0.49\), 95\% CI
+\([-0.73, -0.25]\), \(t(997.87) = -4.03\), \(p < .001\)). Although
 neither gender is overconfident, men on average are more confident in
@@
 the advisor. All standard errors clustered at the level of the
-advisor.}{\label{tbl-study3regs}}}
-\vspace{-20pt}}
+advisor.}{\label{tbl-study3regs}}}\vspace{0pt}
+}
 
@@
 
-Next, we examine whether advisers took the advisee's expectations into
+Next, we examine whether advisers take the advisee's expectations into
 account. Column 1 of Table~\ref{tbl-study3regs} reports a linear
@@
 group for advisers in the ``Expectations'' treatment, controlling for
-the true performance of the advisee. Because each adviser made ten
+the true performance of the advisee. Because each adviser makes ten
 recommendations, we cluster standard errors at the adviser level.
@@
 hidden (\(p < 0.001\)). We show this result graphically in
-Figure~\ref{fig-study3genderdiff}.
+Figure~\ref{fig-study3genderdiff}. As the figure makes clear, this
+effect is driven by advice given to those who scored in the middle of
+the possible range. Thus, when it is clear that someone should compete
+against Low or High performers, advisers are not deferring to
+expectations.
 
 To examine the quality of advice, we computed the expected bonus
-earnings for someone who followed the recommendations. For example, if
-an adviser suggested competing against the High Performer group, we
-matched the advisee against all 20 members of that group and determined
-how often their score matched or exceeded that of the member. We then
-multiplied this number by the respective bonus earnings (50 cents and 30
+earnings for someone who follows the recommendations. For example, if an
+adviser suggests competing against the High Performer group, we match
+the advisee against all 20 members of that group and determined how
+often their score matches or exceeds that of the member. We then
+multiply this number by the respective bonus earnings (50 cents and 30
 cents for the High and Low Performer group, respectively). To see if
@@
 gender of the advisee, and their interaction in Column 3 of
-Table~\ref{tbl-study3regs}. Displaying expectations led men to be
+Table~\ref{tbl-study3regs}. Displaying expectations leads men to be
 advised to compete against the High Performer group more often, and this
-advise turned out to be bad: men receive worse advise than do women when
-expectations are displayed, but not in their absence.\footnote{This
+advice turns out to be costly: men receive worse advise than do women
+when expectations are displayed, but not in their absence.\footnote{This
   analysis was not preregistered, and we note here that the reduction in
@@
   performance on average. One possibility is that advisers suggest the
-  High Performer group more often than is optimal. We return to the
-  possibility that advice is overall biased to be flattering in Study 2.}
+  High Performer group more often than is optimal. This is consistent
+  with our finding from Study 2, in which participants offered
+  flattering advice even when incentivized only for accuracy.}
 
@@
 performers. The former considers only the main effect, while the latter
-also includes the interactive effect.}{\label{tbl-study3time3}}}
-\vspace{-20pt}}
+also includes the interactive
+effect.}{\label{tbl-study3time3}}}\vspace{0pt}
+}
 
@@
 flattering advice, recognizing it as such and thus failing to adhere to
-it. Align with our prediction, participants who were primed with high
-expectations earned less when their expectations were conveyed to the
+it. In line with our prediction, participants who are primed with high
+expectations earn less when their expectations are shown to the
 advisers, although this result is only directional (see Column 1 of
 Table~\ref{tbl-study3time3}). Similarly, as shown in Column 2 of
-Table~\ref{tbl-study3time3}, we also found that male participants
-received less reward when their expectations were presented, even when
-their performance was the same. These findings suggest that flattering
-advice is not without consequences. Furthermore, our research indicates
-that because males are more likely to follow such advice (see Column 4
-of Table~\ref{tbl-study3time3}), their tendency towards competition
-intensifies the cost of such advice.
+Table~\ref{tbl-study3time3}, we also find that male participants earn
+less when their expectations are shown. These findings suggest that
+flattering advice is not without consequences. Furthermore, our research
+indicates that because men are more likely to follow such advice (see
+Column 4 of Table~\ref{tbl-study3time3}), they compete more as a result
+of flattering advice.
 
@@
 avoid information and avoid seeking help (Bénabou et al., 2022; Golman
-et al., 2017; Jaroszewicz et al., 2021). We present evidence from two
+et al., 2017; Jaroszewicz et al., 2021). We present evidence from three
 experiments that advisers are also cognizant of this cost. As a result,
@@
 However, this flattering advice comes at a cost to advisees, who would
-do worse if they followed it blindly, as we show in Study 1.
+do worse if they followed it blindly.
 
@@
 \begin{CSLReferences}{1}{0}
+\bibitem[\citeproctext]{ref-Greenwald1995}
+Banaji, M. R., \& Greenwald, A. G. (1995). Implicit gender stereotyping
+in judgments of fame. \emph{Journal of Personality and Social
+Psychology}, \emph{68}(2), 181.
+
 \bibitem[\citeproctext]{ref-Benabou2022}
@@
 {Hurts} to {Ask}}. National Bureau of Economic Research.
+
+\bibitem[\citeproctext]{ref-Chang2019}
+Chang, E. H., Milkman, K. L., Gromet, D. M., Rebele, R. W., Massey, C.,
+Duckworth, A. L., \& Grant, A. M. (2019). The mixed effects of online
+diversity training. \emph{Proceedings of the National Academy of
+Sciences}, \emph{116}(16), 7778--7783.
 
@@
 
+\bibitem[\citeproctext]{ref-Hagmann2024}
+Hagmann, D., Sajons, G. B., \& Tinsley, C. H. (2024). \emph{Base rate
+neglect as a source of inaccurate statistical discrimination}.
+
 \bibitem[\citeproctext]{ref-Harvey1997}
@@
 Behavior and Human Decision Processes}, \emph{70}(2), 117--133.
+
+\bibitem[\citeproctext]{ref-Ho2018}
+Ho, E. H., Hagmann, D., \& Loewenstein, G. (2021). Measuring information
+preferences. \emph{Management Science}, \emph{67}(1), 126--145.
 
@@
 
+\bibitem[\citeproctext]{ref-Kanze2018}
+Kanze, D., Huang, L., Conley, M. A., \& Higgins, E. T. (2018). We ask
+men to win and women not to lose: {Closing} the gender gap in startup
+funding. \emph{Academy of Management Journal}, \emph{61}(2), 586--614.
+
+\bibitem[\citeproctext]{ref-Koszegi2006}
+Kőszegi, B., \& Rabin, M. (2006). A model of reference-dependent
+preferences. \emph{The Quarterly Journal of Economics}, \emph{121}(4),
+1133--1165.
+
+\bibitem[\citeproctext]{ref-Koszegi2009}
+Kőszegi, B., \& Rabin, M. (2009). Reference-dependent consumption plans.
+\emph{American Economic Review}, \emph{99}(3), 909--936.
+
 \bibitem[\citeproctext]{ref-Loewenstein2018}
@@
 166--167.
+
+\bibitem[\citeproctext]{ref-Greenwald2009}
+Nosek, B. A., Smyth, F. L., Sriram, N., Lindner, N. M., Devos, T.,
+Ayala, A., Bar-Anan, Y., Bergh, R., Cai, H., Gonsalkorale, K., et al.
+(2009). National differences in gender--science stereotypes predict
+national sex differences in science and math achievement.
+\emph{Proceedings of the National Academy of Sciences}, \emph{106}(26),
+10593--10597.
+
+\bibitem[\citeproctext]{ref-Paluck2009}
+Paluck, E. L., \& Green, D. P. (2009). Prejudice reduction: What works?
+A review and assessment of research and practice. \emph{Annual Review of
+Psychology}, \emph{60}, 339--367.
 

### 2025-01-28 manuscript/manuscript.qmd

@@
 
+People go to great lengths to avoid unpleasant information,
 People often go to great lengths to avoid unpleasant information,
@@
 experiment, we hypothesize (and find) that advisers are relucant to
+disappoint advisees and advice is thus biased upward, away from accuracy. 
+We show that this reduces the
 disappoint advisees and advice is thus biased upward, away from accuracy

### 2025-01-28 manuscript/manuscript.qmd
minor changes

@@
 of the two groups (High or Low Performers) was selected by default, and
-Advisees were free to select the other group. They also made a guess as
-to their score, and the survey concluded with basic demographic
-questions.
+Advisees were free to select the other group. The survey concluded 
+with basic demographic questions.
 
@@
 informed them that other participants from Prolific had observed their
-real score and given them advice on which group to compete against, and
-finally reminded them of how many questions they guessed they had
-answered correctly. They were not informed of their true score or the
+real score and given them advice on which group to compete against, and, 
+finally, reminded them of their initial choice of comparison group. 
+They were not informed of their true score or the
 score of the groups they could compete against. Participants then
@@
         axis.line = element_line(colour = "grey"),
-        axis.text.x = element_text(size = 12),
+        axis.text.x = element_text(size = 12, face = "bold",color = "black"),
+        axis.title.y = element_text(size = 12, face = "bold"),
         axis.ticks.x = element_blank(),
@@
   scale_x_discrete(labels = c("Expectation Shown", "Expectation Hidden")) +
-   geom_text(aes(label=Treatment, y = -0.01), position = position_dodge(0.90))
+   geom_text(aes(label=Treatment, y = -0.02), position = position_dodge(0.90), color = "#464747"  )
 
@@
 photos of themselves ("selfies") and are grouped with nine other
-participants of the same sex We then recruit participants of the
+participants of the same sex. We then recruit participants of the
 opposing sex to rank them from most to least attractive and to provide
@@
 from Prolific for the role of advisers ($M_{\text{Age}}$ =
-`r mean(study2_time2$age)` years;
+`r round(mean(study2_time2$age),2)` years;
 `r round(mean(study2_time2$gender == "Female")*100, 2)`% Female). We
 first collect demographic information, then match them to a group of the
-opposite sex. They rank selfies from ten participants from most to least
-attractive using a drop-down menu next to each picture. Because of a
-limitation with the survey software, we could not validate that each
+opposite sex. They rank selfies of ten participants from most to least 
+attractive by entering their rankings into a text box next to each picture. 
+Because of a limitation with the survey software, we could not validate that each
 rank is given only once, and we remove 115 participants who failed to
@@
 create a scale of likeability ($\alpha$ =
-`r cronbach.alpha(study2_time3[, 5:8])$alpha`); and we create a scale of
+`r round(cronbach.alpha(study2_time3[, 5:8])$alpha,2)`); and we create a scale of
 trustworthiness by averaging the ratings of trustworthiness and
-sincerity ($\alpha$ = `r cronbach.alpha(study2_time3[, 9:10])$alpha`).
+sincerity ($\alpha$ = `r round(cronbach.alpha(study2_time3[, 9:10])$alpha,2)`).
 

### 2025-01-28 manuscript/manuscript.tex
minor changes

@@
 
-People often go to great lengths to avoid unpleasant information,
-deriving belief-based utility from maintaining favorable views of
-themselves (Golman et al., 2017; Ho et al., 2021; Loewenstein \& Molnar,
-2018). Moreover, they often prefer advisers who withhold bad news from
-them (Shalvi et al., 2019) and punish those who communicate bad news
-(John et al., 2019). Advisers, anticipating these preferences and
-consequences face a dilemma: Should they provide the accurate but
-potentially painful truth, or shade their recommendations to preserve
-the advisee's mood and the adviser's own standing? Advisers who fear
-they will be blamed or disliked for undermining someone's confidence may
-reasonably avoid candid feedback, particularly if they don't incur a
-cost when the advisee makes a mistake.
+People go to great lengths to avoid unpleasant information, People often
+go to great lengths to avoid unpleasant information, deriving
+belief-based utility from maintaining favorable views of themselves
+(Golman et al., 2017; Ho et al., 2021; Loewenstein \& Molnar, 2018).
+Moreover, they often prefer advisers who withhold bad news from them
+(Shalvi et al., 2019) and punish those who communicate bad news (John et
+al., 2019). Advisers, anticipating these preferences and consequences
+face a dilemma: Should they provide the accurate but potentially painful
+truth, or shade their recommendations to preserve the advisee's mood and
+the adviser's own standing? Advisers who fear they will be blamed or
+disliked for undermining someone's confidence may reasonably avoid
+candid feedback, particularly if they don't incur a cost when the
+advisee makes a mistake.
 
@@
 experiment, we hypothesize (and find) that advisers are relucant to
-disappoint advisees and advice is thus biased upward, away from accuracy
-and toward confirming advisees' priors. We show that this reduces the
-quality of advice---but that advisees nonetheless view flattering
-advisers more favorably.
+disappoint advisees and advice is thus biased upward, away from
+accuracy. We show that this reduces the disappoint advisees and advice
+is thus biased upward, away from accuracy and toward confirming
+advisees' priors. We show that this reduces the quality of advice---but
+that advisees nonetheless view flattering advisers more favorably.
 
@@
 was selected by default, and Advisees were free to select the other
-group. They also made a guess as to their score, and the survey
-concluded with basic demographic questions.
+group. The survey concluded with basic demographic questions.
 
@@
 from Prolific had observed their real score and given them advice on
-which group to compete against, and finally reminded them of how many
-questions they guessed they had answered correctly. They were not
-informed of their true score or the score of the groups they could
-compete against. Participants then observed the advice from a randomly
-selected adviser and made their decision.
+which group to compete against, and, finally, reminded them of their
+initial choice of comparison group. They were not informed of their true
+score or the score of the groups they could compete against.
+Participants then observed the advice from a randomly selected adviser
+and made their decision.
 
@@
 photos of themselves (``selfies'') and are grouped with nine other
-participants of the same sex We then recruit participants of the
+participants of the same sex. We then recruit participants of the
 opposing sex to rank them from most to least attractive and to provide
@@
 Next, we recruit 472 participants from Prolific for the role of advisers
-(\(M_{\text{Age}}\) = 41.0275424 years; 49.79\% Female). We first
-collect demographic information, then match them to a group of the
-opposite sex. They rank selfies from ten participants from most to least
-attractive using a drop-down menu next to each picture. Because of a
-limitation with the survey software, we could not validate that each
+(\(M_{\text{Age}}\) = 41.03 years; 49.79\% Female). We first collect
+demographic information, then match them to a group of the opposite sex.
+They rank selfies of ten participants from most to least attractive by
+entering their rankings into a text box next to each picture. Because of
+a limitation with the survey software, we could not validate that each
 rank is given only once, and we remove 115 participants who failed to
@@
 ratings on likeability, warmth, friendliness, and good-naturedness to
-create a scale of likeability (\(\alpha\) = 0.9243334); and we create a
-scale of trustworthiness by averaging the ratings of trustworthiness and
-sincerity (\(\alpha\) = 0.8740347).
+create a scale of likeability (\(\alpha\) = 0.92); and we create a scale
+of trustworthiness by averaging the ratings of trustworthiness and
+sincerity (\(\alpha\) = 0.87).
 

### 2025-01-29 manuscript/manuscript.qmd
Add in "interpersonal concerns"

@@
 
-People go to great lengths to avoid unpleasant information,
+While much of the literature on advice assumes that advisers aim to provide
+the most helpful advice, thier motivations are often more complex [@Yaniv2012;@Dalal2010; @Rader2017]. 
+Advisers are not only concerned with the accuracy and usefulness of their advice 
+but also with their relationships with advisees. Interpersonal concerns—such
+as maintaining a positive image, avoiding conflict, or preserving social 
+harmony—can shape the way advice is delivered [@Van2009; @Schaerer2018; @Chentsova2012].
+In particular, advisers may strategically soften their messages or withhold 
+unfavorable information to manage how they are perceived or to prevent discomfort
+for both themselves and the advisee [@Sniezek2001;@Levine2020]. These interpersonal dynamics 
+suggest that advice is not always optimized for the recipient’s best interest but
+is instead filtered through social and psychological considerations.
+
+Just as advisers may hesitate to provide unwelcome truths, advisees themselves are o
+ften resistant to hearing them. People go to great lengths to avoid unpleasant information,
 People often go to great lengths to avoid unpleasant information,

### 2025-01-29 manuscript/manuscript.tex
Add in "interpersonal concerns"

@@
 
-People go to great lengths to avoid unpleasant information, People often
-go to great lengths to avoid unpleasant information, deriving
-belief-based utility from maintaining favorable views of themselves
-(Golman et al., 2017; Ho et al., 2021; Loewenstein \& Molnar, 2018).
-Moreover, they often prefer advisers who withhold bad news from them
-(Shalvi et al., 2019) and punish those who communicate bad news (John et
-al., 2019). Advisers, anticipating these preferences and consequences
-face a dilemma: Should they provide the accurate but potentially painful
-truth, or shade their recommendations to preserve the advisee's mood and
-the adviser's own standing? Advisers who fear they will be blamed or
-disliked for undermining someone's confidence may reasonably avoid
-candid feedback, particularly if they don't incur a cost when the
-advisee makes a mistake.
+While much of the literature on advice assumes that advisers aim to
+provide the most helpful advice, thier motivations are often more
+complex (Dalal \& Bonaccio, 2010; Rader et al., 2017; Yaniv \&
+Choshen-Hillel, 2012). Advisers are not only concerned with the accuracy
+and usefulness of their advice but also with their relationships with
+advisees. Interpersonal concerns---such as maintaining a positive image,
+avoiding conflict, or preserving social harmony---can shape the way
+advice is delivered (Chentsova-Dutton \& Vaughn, 2012; Schaerer et al.,
+2018; Van Swol, 2009). In particular, advisers may strategically soften
+their messages or withhold unfavorable information to manage how they
+are perceived or to prevent discomfort for both themselves and the
+advisee (Levine et al., 2020; Sniezek \& Van Swol, 2001). These
+interpersonal dynamics suggest that advice is not always optimized for
+the recipient's best interest but is instead filtered through social and
+psychological considerations.
+
+Just as advisers may hesitate to provide unwelcome truths, advisees
+themselves are o ften resistant to hearing them. People go to great
+lengths to avoid unpleasant information, People often go to great
+lengths to avoid unpleasant information, deriving belief-based utility
+from maintaining favorable views of themselves (Golman et al., 2017; Ho
+et al., 2021; Loewenstein \& Molnar, 2018). Moreover, they often prefer
+advisers who withhold bad news from them (Shalvi et al., 2019) and
+punish those who communicate bad news (John et al., 2019). Advisers,
+anticipating these preferences and consequences face a dilemma: Should
+they provide the accurate but potentially painful truth, or shade their
+recommendations to preserve the advisee's mood and the adviser's own
+standing? Advisers who fear they will be blamed or disliked for
+undermining someone's confidence may reasonably avoid candid feedback,
+particularly if they don't incur a cost when the advisee makes a
+mistake.
 
@@
 
+\bibitem[\citeproctext]{ref-Chentsova2012}
+Chentsova-Dutton, Y. E., \& Vaughn, A. (2012). Let me tell you what to
+do: Cultural differences in advice-giving. \emph{Journal of
+Cross-Cultural Psychology}, \emph{43}(5), 687--703.
+
+\bibitem[\citeproctext]{ref-Dalal2010}
+Dalal, R. S., \& Bonaccio, S. (2010). What types of advice do
+decision-makers prefer? \emph{Organizational Behavior and Human Decision
+Processes}, \emph{112}(1), 11--23.
+
 \bibitem[\citeproctext]{ref-Fiske2007}
@@
 \emph{American Economic Review}, \emph{99}(3), 909--936.
+
+\bibitem[\citeproctext]{ref-Levine2020}
+Levine, E. E., Roberts, A. R., \& Cohen, T. R. (2020). Difficult
+conversations: Navigating the tension between honesty and benevolence.
+\emph{Current Opinion in Psychology}, \emph{31}, 38--43.
 
@@
 
+\bibitem[\citeproctext]{ref-Rader2017}
+Rader, C. A., Larrick, R. P., \& Soll, J. B. (2017). Advice as a form of
+social influence: Informational motives and the consequences for
+accuracy. \emph{Social and Personality Psychology Compass},
+\emph{11}(8), e12329.
+
+\bibitem[\citeproctext]{ref-Schaerer2018}
+Schaerer, M., Tost, L. P., Huang, L., Gino, F., \& Larrick, R. (2018).
+Advice giving: A subtle pathway to power. \emph{Personality and Social
+Psychology Bulletin}, \emph{44}(5), 746--761.
+
 \bibitem[\citeproctext]{ref-Shalvi2019}
@@
 willful ignorance}.
+
+\bibitem[\citeproctext]{ref-Sniezek2001}
+Sniezek, J. A., \& Van Swol, L. M. (2001). Trust, confidence, and
+expertise in a judge-advisor system. \emph{Organizational Behavior and
+Human Decision Processes}, \emph{84}(2), 288--307.
 
@@
 
+\bibitem[\citeproctext]{ref-Van2009}
+Van Swol, L. M. (2009). The effects of confidence and advisor motives on
+advice utilization. \emph{Communication Research}, \emph{36}(6),
+857--873.
+
+\bibitem[\citeproctext]{ref-Yaniv2012}
+Yaniv, I., \& Choshen-Hillel, S. (2012). Exploiting the wisdom of others
+to make better decisions: Suspending judgment reduces egocentrism and
+increases accuracy. \emph{Journal of Behavioral Decision Making},
+\emph{25}(5), 427--434.
+
 \end{CSLReferences}

### 2025-01-30 manuscript/manuscript.qmd
Correct typo

@@
 
-Just as advisers may hesitate to provide unwelcome truths, advisees themselves are o
-ften resistant to hearing them. People go to great lengths to avoid unpleasant information,
-People often go to great lengths to avoid unpleasant information,
+Just as advisers may hesitate to provide unwelcome truths, advisees themselves are often 
+resistant to hearing them. People often go to great lengths to avoid unpleasant information,
 deriving belief-based utility from maintaining favorable views of

### 2025-01-30 manuscript/manuscript.tex
Correct typo

@@
 Just as advisers may hesitate to provide unwelcome truths, advisees
-themselves are o ften resistant to hearing them. People go to great
-lengths to avoid unpleasant information, People often go to great
+themselves are often resistant to hearing them. People often go to great
 lengths to avoid unpleasant information, deriving belief-based utility

### 2025-02-01 manuscript/manuscript.qmd
Updated keywords

@@
 
-keywords: [Gender difference, Advice, Interpresonal relationship]
+keywords: [advice, interpersonal relationship, discrimination, gender bias]
 bibliography: bibliography.bib

### 2025-03-12 manuscript/manuscript.Rmd
manuscript_0311

@@
 which may explain why women are less likely to apply for and ultimately
-obtain more rewarding positions (Kanze et al., 2018). Research on gender
-discrimination has focused on the role of unconscious bias (Greenwald et
-al., 2009; Greenwald & Banaji, 1995), but interventions that try to
-reduce this bias have been largely unsuccessful (Chang et al., 2019;
-Paluck & Green, 2009). Recent work has proposed cognitive, rather than
+obtain more rewarding positions [@Kanze2018]. Research on gender
+discrimination has focused on the role of unconscious bias [@Greenwald2009; @Greenwald1995], but interventions that try to
+reduce this bias have been largely unsuccessful [@Chang2019;
+@Paluck2009]. Recent work has proposed cognitive, rather than
 unconscious, biases that can lead to gender discrimination through the
-formation of false beliefs (Hagmann et al., 2024). Here, we propose a
+formation of false beliefs [@Hagmann2024]. Here, we propose a
 novel source of differences in advice by drawing on recent work on
-belief-based utility, expectation-based reference points (Köszegi, 2006;
-Kőszegi & Rabin, 2009), and the hedonic consequences of information
-(Golman et al., 2017).
+belief-based utility, expectation-based reference points [@Koszegi2006;
+@Koszegi2009], and the hedonic consequences of information
+[@Golman2017].
 

### 2025-03-12 manuscript/manuscript.qmd
manuscript_0311

--- 2025-01-30 manuscript/manuscript.qmd
@@
     # gratitude: The authors are grateful to XXX for their helpful comments.
-abstract: Good advice improves decision quality but often requires delivering unpleasant truths that may disappoint advisees.
+abstract: Advice that improves decision-making does not always feel good.
+While advice has the potential to improve decision-making by helping advisees more accurately assess feasibility and predict potential outcomes, it can also lead to disappointment when it challenges the advisee’s overly optimistic expectations.
 Across three pre-registered and incentivized experiments involving real adviser-advisee interactions (N = 3,900), we show that advisers prioritize avoiding disappointment at the expense of accuracy and their own earnings.
-In Study 1, advisers financially rewarded for accuracy still tailor recommendations to aspirational goals expressed by advisees, resulting in worse advice.
-When incentivized to be liked, advisers provide even more flattering advice, and advisees reward this by rating these advisers as more likable, despite the advice being less honest and less accurate (Study 2).
-The desire to avoid disappointment may lead to inequities if there are differences in expectations across social groups.
+In study 1, advisers use flattering advice to create more positive impressions, and advisees reward this by rating these advisers as more likable, despite the advice being less honest and less accurate.
+Even advisers incentivised for accuracy still tailor recommendations to aspirational goals expressed by advisees, resulting in financial loss for them and the advisees (Study 2).
+The concern for interpersonal consequences may lead to inequities if there are differences in expectations across social groups.
 In Study 3, we examine a setting in which men expect to perform better than women.
@@
 
-keywords: [Gender difference, Advice, Interpresonal relationship]
+keywords: [Advice, Interpresonal relationship, Gender difference]
 bibliography: bibliography.bib
@@
 
-study1_time1 <- readRDS(here::here("Data/Study1_time1.Rds"))
-study1_ability50 <- read.csv(here::here("Data/Cleaned Data/S1_Ability50_clean.csv"))
-study1_time2_giver <- readRDS(here::here("Data/Study1_time2_giver.Rds"))
-study1_time2_advice <- readRDS(here::here("Data/Study1_time2_advice.Rds"))
-study1_time3 <- readRDS(here::here("Data/Study1_time3.Rds"))
-
-```
+```
+
+<!--# Amanda: I replaced all 'advisers' with 'adviser' for consistency. -->
 
 # Introduction
-
-Career trajectories for men and women often differ substantially, even
-among those with similar qualifications. One source of such differences
-may be the advice that people receive. Prior work has documented that
-men receive more aspirational advice and women more risk-averse advice,
-which may explain why women are less likely to apply for and ultimately
-obtain more rewarding positions [@Kanze2018]. Research on gender
-discrimination has focused on the role of unconscious bias
-[@Greenwald2009; @Greenwald1995], but interventions that try to reduce
-this bias have been largely unsuccessful [@Chang2019; @Paluck2009].
-Recent work has proposed cognitive, rather than unconscious, biases that
-can lead to gender discrimination through the formation of false beliefs
-[@Hagmann2024]. Here, we propose a novel source of differences in advice
-by drawing on recent work on belief-based utility, expectation-based
-reference points [@Koszegi2006; @Koszegi2009], and the hedonic
-consequences of information [@Golman2017].
 
@@
 shaping choices about promotions, career paths, and everyday dilemmas
-[@Gino2007; @Harvey1997; @Soll2009]. Its fundamental premise is to
-improve outcomes by enabling decision-makers to learn from others'
-expertise. However, while honest advice can lead to better decisions, it
-can also lead to disappointment when it suggests a desired outcome is
-unlikely to materialize. Advisers may be motivated to offer flattering
-recommendations that align with advisees' hopes, sparing them the
-disappointment of a more sobering forecast.
-
-Advice with the potential for disappointment appears in diverse
-organizational settings: supervisors deliver feedback on employee
-performance, lawyers convey likely outcomes of litigation to their
-clients, and academics offer thoughts on colleagues' manuscripts.
-Ideally, honest information would help people identify their strengths
-and weaknesses, make informed decisions about whether to pursue legal
-cases, and strengthen papers prior to submission to academic journals,
-thus improving long-term outcomes. In practice, however, interpersonal
-considerations may prevent candor. When someone's expectations are (too)
-high, an adviser might hesitate to deliver information that undermines
-it---particularly if doing so risks negative interpersonal
-repercussions.
-
-While much of the literature on advice assumes that advisers aim to provide
-the most helpful advice, thier motivations are often more complex [@Yaniv2012;@Dalal2010; @Rader2017]. 
-Advisers are not only concerned with the accuracy and usefulness of their advice 
-but also with their relationships with advisees. Interpersonal concerns—such
-as maintaining a positive image, avoiding conflict, or preserving social 
-harmony—can shape the way advice is delivered [@Van2009; @Schaerer2018; @Chentsova2012].
-In particular, advisers may strategically soften their messages or withhold 
-unfavorable information to manage how they are perceived or to prevent discomfort
-for both themselves and the advisee [@Sniezek2001;@Levine2020]. These interpersonal dynamics 
-suggest that advice is not always optimized for the recipient’s best interest but
-is instead filtered through social and psychological considerations.
-
-Just as advisers may hesitate to provide unwelcome truths, advisees themselves are often 
-resistant to hearing them. People often go to great lengths to avoid unpleasant information,
-deriving belief-based utility from maintaining favorable views of
-themselves [@Golman2017; @Ho2018; @Loewenstein2018]. Moreover, they
-often prefer advisers who withhold bad news from them [@Shalvi2019] and
-punish those who communicate bad news [@John2019]. Advisers,
-anticipating these preferences and consequences face a dilemma: Should
-they provide the accurate but potentially painful truth, or shade their
-recommendations to preserve the advisee's mood and the adviser's own
-standing? Advisers who fear they will be blamed or disliked for
-undermining someone's confidence may reasonably avoid candid feedback,
+[@Gino2007; @Harvey1997; @Soll2009]. While others can provide
+information in the form of opinions [@Trouche2018], feedback
+[@Kluger1996], or personal observations [@Yoon2021] to influence the
+decision-maker, this project focuses specifically on advice—defined as
+"information that is perceived as intended to help an advisee deal with
+their issue of deliberation" [@Milyavsky2024]. Advice is distinct from
+other forms of input because its primary purpose is to improve
+decision-making by leveraging others' expertise.
+
+Advice has the power to enhance decisions, yet it also carries the risk
+of disappointment. For example, a career consultant might advise an
+employee to enroll in a management program to strengthen their skill set
+before competing for a leadership role. Ideally, such honest advice
+helps the employee identify areas for personal growth. In practice,
+however, the employee might feel overlooked and frustrated that their
+ambitions are not immediately supported. As a result, advisers may be
+inclined to offer flattering recommendations that align with—or even
+exceed—advisees' hopes, such as encouraging the employee to pursue the
+leadership role despite concerns about their readiness. In this way,
+interpersonal dynamics may discourage full candor in giving advice.
+
+The objective of this research is to examine the dilemma advisers face:
+Should they provide accurate but potentially painful advice, or soften
+their recommendations to preserve the advisee's mood and protect their
+own standing? Given that advisees tend to prefer advisers who withhold
+bad news [@Shalvi2019] nd penalize those who deliver it [@John2019],
+advisers may reasonably avoid full candor—especially when they bear no
+cost for the advisee’s mistakes. Specifically, when someone's
+expectations are (too) high, an adviser may hesitate to provide advice
+that challenges them, particularly if doing so risks straining the
+relationship or causing negative interpersonal consequences.
+
+Our research contributes to the growing literature on advisers' motives
+and intentions in advice-giving. This line of work examines how
+advisers' perceived dishonesty or helping intentions influence advice
+utilization [@Haran2020; @Mackinger2017; @Milyavsky2024; @Van2009]. By
+examining advice within its interactional and communicative context, we
+extend this research by incorporating another dimension of advisers'
+motives—interpersonal concerns. We demonstrate that advisers adjust
+their recommendations to avoid hurting the advisee’s feelings and
+self-image. Second, we contribute to the belief-based utility
+literature, which suggests that individuals derive satisfaction from
+their beliefs about the world and themselves [@Loewenstein2018]. We show
+that advisers also place value on preserving advisees' self-perceptions,
+often tailoring their advice to align with the advisee’s expectations.
+Furthermore, we reveal that this advice-giving strategy has unintended
+consequences—it transforms the confidence gap [where women tend to be
+less confident than men; @Lundeberg1994] into an advice gap, in which
+women are less likely than men to receive advice to aim higher, thereby
+reinforcing existing gender inequalities.
+
+## The Motives Behind Advice-Giving
+
+While much of the literature on advice assumes that advisers aim to
+provide the most helpful advice, their motivations are often more
+complex [@Yaniv2012; @Dalal2010; @Rader2017]. Other than the accuracy
+and usefulness of the advice, interpersonal concerns—such as maintaining
+a positive image, avoiding conflict, or preserving social harmony—can
+shape what advice is delivered and how [@Sniezek2001; @Levine2020]. For
+example, research has shown how people often avoid providing negative
+feedback directly, opting instead for ambiguity or indirect phrasing to
+minimize discomfort [@Levine2020]. These interpersonal dynamics suggest
+that advice is not always optimized for the recipient’s best interest
+but is instead filtered through social and psychological considerations.
+
+In particular, advisers may strategically soften their messages or
+withhold unfavorable evaluations to manage how they are perceived or to
+prevent discomfort for both themselves and the advisee [@Van2009;
+@Schaerer2018; @Chentsova2012]. When advisers anticipate disagreement or
+resistance, they may soften their recommendations or frame them more
+diplomatically, sometimes at the expense of accuracy. This suggests that
+advice is not merely a means of sharing information but also a tool for
+managing social interactions and reducing potential friction [@Van2009].
+These interpersonal considerations become even more pronounced when
+there is a power imbalance between the adviser and advisee, as
+lower-power advisers may be more hesitant to offer direct or critical
+guidance to avoid negative repercussions [@Schaerer2018].
+
+Just as advisers may hesitate to provide unwelcome truths, advisees
+themselves are often resistant to hearing them. People often go to great
+lengths to avoid unpleasant information, deriving belief-based utility
+from maintaining favorable views of themselves [@Golman2017; @Ho2018;
+@Loewenstein2018]. Moreover, they often prefer advisers who withhold bad
+news from them [@Shalvi2019] and punish those who communicate bad news
+[@John2019]. Advisers who fear they will be blamed or disliked for
+undermining someone's confidence may reasonably avoid candid advice,
 particularly if they don't incur a cost when the advisee makes a
 mistake.
+
+Providing flattering advice, however, should not be seen as maliciously
+misleading the advisee. Rather than being irrational, it tends to be
+more optimistic, and this optimism is not necessarily misplaced. Often,
+the advisee possesses insights about themselves—such as their motivation
+and past experiences—that the adviser may overlook or have no access to.
+Take, for example, an employee deciding whether to compete for a
+leadership role. While the adviser might focus on the employee’s lack of
+management knowledge, the employee may have strong leadership
+characteristics, excellent communication skills, and persuasive
+abilities. In this way, flattering advice can encourage the advisee to
+set ambitious goals, fostering a self-fulfilling prophecy where
+confidence drives success [@Jussim1986; @Locke2006].
+
+Of course, if the advice is overly inflated, it may become unhelpful.
+However, this is unlikely to happen, as advisers typically aim to boost
+the advisee’s confidence while maintaining credibility. Suggesting an
+unrealistic option—such as encouraging an entry-level employee to
+compete for a CEO position—would come across as insincere or even
+mocking rather than flattering.
+
+Beyond protecting the advisee's beliefs and fostering their confidence
+and motivation, advisers may also offer flattering advice to shield
+themselves from blame if the ultimate decision leads to a poor outcome.
+Although both the adviser and advisee recognize the inherent uncertainty
+between the advice, the decision, and the final outcome, people tend to
+attribute poor outcomes to the adviser [@Weiner1985; @Palmeira2015].
+However, research suggests that people differentiate between errors made
+intentionally—such as those driven by insufficient knowledge or
+deliberate bias—and those made unintentionally, with harsher penalties
+imposed on advisers perceived to have deliberately undermined the
+decision [@Haran2020]. Flattering advice, even when ultimately
+unhelpful, may reduce the likelihood of blame because advisees are less
+likely to suspect ill intent from an adviser who appears supportive.
+Advisees may instead interpret the poor outcome as an unintended error
+rather than deliberate misguidance, particularly because they view the
+adviser positively and believe the adviser genuinely holds them in high
+regard [@Palmeira2015; @Haran2020]. Even when advisees recognize that
+flattering advice was intended to boost their confidence, research shows
+that people tend to appreciate such misplaced good intentions, as they
+strengthen social bonds by making the gift-giver feel socially closer
+[@Zhang2012].
+
+Advisers may choose to inflate their advice for different reasons,
+depending on their relationship with the advisee and the stakes of the
+decision. For instance, advisers might offer flattering advice to
+strangers out of politeness, provide inflated encouragement to friends
+to offer emotional support [@Dalal2010], or use their recommendations to
+motivate individuals with particularly ambitious or competitive
+personalities. We recognize that multiple motives may simultaneously
+drive this behavior, and their relative influence—as well as advisers'
+overall tendency to inflate advice—may vary across situations. However,
+in this project, we focus specifically on whether advisers intentionally
+inflate their advice and explore the potential consequences of doing so.
+
+One downstream consequence of giving flattering advice is the potential
+to reinforce gender differences — specifically, men are more likely to
+receive such inflated advice. Prior work has documented that men receive
+more aspirational advice and women more risk-averse advice, which may
+explain why women are less likely to apply for and ultimately obtain
+more rewarding positions [@Kanze2018]. Research on gender discrimination
+has focused on the role of unconscious bias [@Greenwald2009;
+@Greenwald1995], but interventions that try to reduce this bias have
+been largely unsuccessful [@Chang2019; @Paluck2009]. Recent work has
+proposed cognitive, rather than unconscious, biases that can lead to
+gender discrimination through the formation of false beliefs
+[@Hagmann2024]. Here, we propose that one overlooked mechanism driving
+gender disparities in career outcomes may lie in the differential
+provision of flattering advice, shaped by the advisee's
+self-expectations.
+
+Specifically, when advisers aim to make their advice appear flattering,
+they may rely less on an objective evaluation of the advisee's
+competence and instead anchor their advice on the advisee’s
+self-expectations. Drawing on the literature on belief-based utility and
+expectation-based reference points [@Koszegi2006; @Koszegi2009], we
+suggest that advisers may align their advice with how ambitious or
+confident the advisee appears, so that they give optimistic but not
+entirely unrealistic recommendations. This dynamic may inadvertently
+disadvantage women. Research shows that men generally hold higher
+self-expectations or are more likely to display confidence, while women
+tend to exhibit more modest self-assessments despite comparable
+competence [@Kanze2018]. As a result, advisers may unintentionally offer
+men more ambitious and aspirational advice, encouraging them to pursue
+higher-rewarding opportunities, while offering women more cautious,
+conservative advice that aligns with their lower expressed
+self-expectations. This differential treatment, though seemingly
+well-intentioned, can have profound downstream consequences. By
+tailoring advice to match the advisee's perceived self-expectations,
+advisers may subtly nudge men toward risk-taking, leadership roles, or
+competitive opportunities, while directing women toward safer, less
+ambitious paths — ultimately reinforcing existing gender disparities in
+career outcomes.
+
+# Overview of studies
 
@@
 experiment, we hypothesize (and find) that advisers are relucant to
-disappoint advisees and advice is thus biased upward, away from accuracy. 
-We show that this reduces the
-disappoint advisees and advice is thus biased upward, away from accuracy
-and toward confirming advisees' priors. We show that this reduces the
-quality of advice—but that advisees nonetheless view flattering advisers
-more favorably.
+disappoint advisees and advice is thus biased upward, away from
+accuracy. We show that this reduces the disappoint advisees and advice
+is thus biased upward, away from accuracy and toward confirming
+advisees' priors. We show that this reduces the quality of advice—but
+that advisees nonetheless view flattering advisers more favorably.
 
@@
 often have some sense of an employee's confidence or aspirations and
-thus could adjust their feedback to avoid disappointing them.
+thus could adjust their advice to avoid disappointing them.
 Interpersonal considerations would likely be stronger in situations in
@@
 
-In Study 1, we nudge advisees into a preference for competing against
+Across all three studies, we use a three-stage design. In Stage 1, we
+measure the advisee’s performance and their self-expectations. In Stage
+2, we show the measured performance to the adviser and ask them to
+provide advice on how the advisee can maximize their chances of earning
+a bonus. Half of the advisers also receive information about the
+advisee’s self-expectations. Importantly, this expectation information
+is objectively irrelevant to the task, as the bonus is solely based on
+the advisee’s performance, which is already measured. While in real
+life, self-expectations might contain useful insights (such as
+unobservable skills or motivation), in our setup, self-expectations
+serve no informative value. Moreover, flattering advice provided in this
+setup cannot be justified as a motivational boost (like a pep talk)
+because the performance has already been fixed. Finally, in Stage 3, we
+re-invite the advisees from Stage 1, show them the advice they received,
+and observe how they make their final decisions.
+
+In Study 1, we ask advisees to upload photos of themselves and advisers
+rank them on their attractiveness. Advisers then recommend which rank
+the advisee should bet on, receiving an incentive either for the
+advisee's accuracy or for being evaluated favorably. Both groups of
+advisers recommend a rank that is more attractive than what they
+themselves have evaluated the advisee, and those incentivized for
+likability further inflate the ranking. Advisees evaluate advisers more
+favorably when they recommend betting on a more attractive rank,
+including viewing them as more trustworthy.
+
+In Study 2, we nudge advisees into a preference for competing against
 either a group of top-performers or a group of low-performers, through
@@
 recommendation nonetheless take into account the initial preference when
-recommending which group they should compete against. In Study 2, we ask
-advisees to upload photos of themselves and advisers rank them on their
-attractiveness. Advisers then recommend which rank the advisee should
-bet on, receiving an incentive either for the advisee's accuracy or for
-being evaluated favorably. Both groups of advisers recommend a rank that
-is more attractive than what they themselves have evaluated the advisee,
-and those incentivized for likability further inflate the ranking.
-Advisees evaluate advisers more favorably when they recommend betting on
-a more attractive rank, including viewing them as more trustworthy.
+recommending which group they should compete against.
 
@@
 
-We first examine whether advisers take into account the expectations of
+We first examine if advisers believe that flattering advice will improve
+how they are perceived, and if so, whether this perception is true. We
+do this by manipulating the incentives for advisers, who receive a bonus
+either based on how they are evaluated by an advisee, or a bonus for the
+advisee's accuracy.
+
+The study takes place in three stages. First, a group of advisees upload
+photos of themselves ("selfies") and are grouped with nine other
+participants of the same sex. We then recruit participants of the
+opposing sex to rank them from most to least attractive and to provide
+advice. Specifically, they advise the participant they ranked as the 7th
+most attractive (i.e., 4th least attractive) on what rank they should
+bet they were ranked by a larger group of raters. Advisers were randomly
+assigned to two treatments, receiving a bonus payment either if the
+advisee guessed their rank accurately or if the advisee evaluated the
+adviser as likeable as measured by a scale response. We hypothesize that
+advisers incentivized to be liked will recommend betting on a lower
+rank, i.e. that the advisee is more attractive.
+
+```{r}
+
+study1_time1 <- readRDS(here::here("Data/Study1_time1.Rds"))
+study1_time1_200 <- readRDS(here::here("Data/Study1_time1_200.Rds"))
+study1_time2 <- readRDS(here::here("Data/Study1_time2.Rds"))
+study1_finalRank <- readRDS(here::here("Data/Study1_finalRank.Rds"))
+study1_time3 <- readRDS(here::here("Data/Study1_time3.Rds"))
+
+```
+
+## Methods
+
+We recruit 300 participants from Prolific and, after asking demographic
+questions, invite them to upload photos of themselves (selfies) to be
+rated by other participants on attractiveness. We obtain selfies from
+`r scales::comma(dim(study1_time1[study1_time1$gender == 'Male',])[1])`
+men and
+`r scales::comma(dim(study1_time1[study1_time1$gender == 'Female',])[1])`
+women adhering to our instructions (e.g., did not include other people).
+In line with our preregistration, we select the first 100 photos from
+women to arrive at a gender-balanced sample ($M_{\text{Age}}$ =
+`r mean(study1_time1_200$age)` years). Participants are informed that
+their selfies will be randomly grouped with those of nine other
+participants of their sex and ranked in terms of attractiveness by a
+group of new Prolific participants of the opposite sex. They then make
+an unincentivized guess of their rank.
+
+Next, we recruit `r scales::comma(dim(study1_time2)[1])` participants
+from Prolific for the role of advisers ($M_{\text{Age}}$ =
+`r round(mean(study1_time2$age),2)` years;
+`r round(mean(study1_time2$gender == "Female")*100, 2)`% Female). We
+first collect demographic information, then match them to a group of the
+opposite sex. They rank selfies of ten participants from most to least
+attractive by entering their rankings into a text box next to each
+picture. Because of a limitation with the survey software, we could not
+validate that each rank is given only once, and we remove 115
+participants who failed to follow instructions and did not provide a
+complete ranking.[^2]
+
+[^2]: Moreover, we could not collect data from any participant who did
+    not select any participant as the 7th most attractive participant,
+    as that image would be shown on subsequent pages.
+
+After submitting their ratings, participants see the photo of the
+participant they ranked as the 7th most attractive (i.e., the 4th least
+attractive). We remind them of the rank they have just given to that
+person and inform them that this participant will be invited back and
+can earn a \$1 bonus if they correctly guess their rank. The rank is
+determined by the aggregate ratings of all participants who have ranked
+this group. Because the participant does not observe the other nine
+people in the group, they would depend on the adviser's recommendation
+along with their own assessment. We randomly assign advisers to one of
+two incentivization schemes. In the "Accuracy" treatment, they receive a
+bonus identical to the advisee: \$1 if they guess their rank correctly.
+In the "Likeability" treatment, we inform them that the advisee will
+rate them on a 5-point Likert scale on how likeable they thought they
+are. Each point on the scale would translate to a bonus of 20 cents.
+Advisers then select a rank (from 1 to 10) that they recommend the
+advisee to bet on.
+
+Finally, we invite participants from Stage 1 who were ranked as the 7th
+most attractive participant by at least one adviser (so that they
+received advice) back for the follow-up survey. Following our
+preregistration, we keep the survey open for 7 days. In total,
+`r scales::comma(dim(study1_time3)[1])` participants
+(`r scales::comma(dim(study1_time3[study1_time3$gender == 'Male',])[1])`
+men,
+`r scales::comma(dim(study1_time3[study1_time3$gender == 'Female',])[1])`
+women) complete the follow-up survey. We remind them of the selfie they
+uploaded in Stage 1 and that a group of 10 selfies, including theirs,
+had been rated by other participants from Prolific. They then see the
+advice from a randomly selected adviser and make their own guess with a
+\$1 incentive for accuracy. Finally, they rate the adviser's likability,
+warmth, friendliness, good-naturedness, trustworthiness, and sincerity
+on 5-point Likert scales [adapted from @Fiske2007].
+
+## Results
+
+```{r}
+#| include: false
+library(dplyr)
+
+TargetsUnique <- study1_time2 %>%
+  dplyr::select(Target) %>%
+  unique()
+
+TargetsUnique <- merge(TargetsUnique,study1_finalRank, by.x = 'Target', by.y = 'QID7_Id')
+
+```
+
+```{r}
+#| label: fig-study1advice-old
+#| fig-cap: "Advisers were asked to suggest what rank to bet on for someone they ranked as the 7th most attractive out of ten people.
+When incentivized for accuracy, most of them advised betting on 7, which was based on their evaluation of the recipient's attractiveness.
+However, when incentivized for likability, many participants gave flattering advice by suggesting betting on higher ranks that imply a higher evaluation of attractiveness."
+#| eval: false
+
+library(ggplot2)
+library(ggridges)
+
+study1_time2 <- study1_time2 %>% dplyr::mutate(Advice = as.numeric(Advice))
+
+ggplot(study1_time2, aes(x = Advice, y = Condition, fill = Condition)) +
+    # Reduce vertical spacing with rel_min_height and scale
+    geom_density_ridges(scale = 1.0, rel_min_height = 0.01, alpha = 0.7) +
+
+    # Shading the left side of x = 7 in light grey
+    geom_rect(aes(xmin = 7, xmax = Inf, ymin = -Inf, ymax = Inf), fill = "gray95", alpha = 0.01) +
+
+    # Add the dashed line at x = 7
+    geom_vline(xintercept = 7, col = 'black', linetype = 'dashed', linewidth = 0.7) +
+
+    # Add the text "Flattering" on the left of the line
+    annotate("text", x = 5, y = 0.6, label = "Flattering Ranks", hjust = 1, size = 8, fontface = "bold") +
+
+    # Manual fill colors
+    scale_fill_manual(values = c("#2A629A", '#FF7F3E'), labels = c("Accurate", "Likable")) +
+
+    # X-axis adjustments
+    scale_x_continuous(name = "Advised Rank", breaks = seq(1, 10)) +
+
+    # Theme adjustments
+    theme_bw() +
+  coord_flip() +
+    theme(panel.grid = element_blank(),
+          panel.border = element_blank(),
+          axis.line = element_line(colour = "black"),
+          legend.position = "none",
+          legend.title = element_blank(),
+          legend.key.size = unit(1.2, "lines"),
+          legend.text = element_text(size = 12),
+          plot.title = element_text(hjust = 0.5, size = 20),
+          axis.text.x = element_text(size = 14),  # X-axis text size
+          axis.text.y = element_text(size = 14),
+          axis.title.x = element_text(size = 16, face = "bold"),  # X-axis title size
+          axis.title.y = element_text(size = 16, face = "bold"))
+
+```
+
+```{r}
+#| label: fig-study1advice
+#| fig-cap: "Participants in Study 2 give advice to the person they rank 7th most attractive out of 10.
+When incentivized for accuracy, the majority recommends betting on that rank.
+However, when incentivized for likeability, participants inflate their advice to flatter the recipient as more attractive."
+
+study1_time2 <- study1_time2 %>% dplyr::mutate(Advice = as.numeric(Advice))
+
+study1_time2 %>%
+  dplyr::group_by(Condition) %>%
+  dplyr::mutate(total_per_condition = dplyr::n()) %>%
+  dplyr::group_by(Condition, Advice, total_per_condition) %>%
+  dplyr::summarize(n = dplyr::n()) %>%
+  dplyr::mutate(pct = ifelse(Condition == "Accurate", -n/total_per_condition, n/total_per_condition),
+                Advice = factor(Advice)) %>%
+  ggplot(aes(x = pct, y = Advice, fill = Condition)) +
+  geom_col() +
+  scale_x_continuous("Share of Advice",
+                     limits = c(-0.6, 0.6),
+                     labels = \(x) scales::percent(abs(x))) +
+  scale_y_discrete(limits = rev) +
+  # Dashed 'horizontal' line at Advice = 7
+  geom_hline(yintercept = 4, col = 'black', linetype = 'dashed', linewidth = 0.7) +
+  # Example text annotation (adjust x/y for positioning)
+  annotate("text", x = -0.3, y = 9, label = "Accuracy Incentive", hjust = 1, size = 4, fontface = "bold") +
+  annotate("text", x = 0.6, y = 9, label = "Likeable Incentive", hjust = 1, size = 4, fontface = "bold") +
+  # scale_y_continuous(name = "Advised Rank", breaks = seq(1, 10)) +
+  scale_fill_manual(values = c("#2A629A", "#FF7F3E")) +
+  papaja::theme_apa() +
+  theme(
+    legend.position  = "none",
+    axis.text.x  = element_text(size = 14),
+    axis.text.y  = element_text(size = 14),
+    axis.title.x = element_text(size = 16, face = "bold"),
+    axis.title.y = element_text(size = 16, face = "bold")
+  )
+```
+
+We begin by examining the prior beliefs of advisees who uploaded their
+selfies. On average, men guess they rank
+`r round(mean(study1_time1[study1_time1$gender == "Male",]$Guess),2)` in
+their group of 10 and women guess that they rank
+`r round(mean(study1_time1[study1_time1$gender == "Female",]$Guess),2)`
+(`r papaja::apa_print(t.test(Guess ~ gender, data = study1_time1, var.equal = T))$statistic`).
+Notably, people's self-perceptions correlate strongly with the aggregate
+ratings of the advisers
+(`r round(cor(study1_finalRank$Guess, study1_finalRank$finalRank),2)`,
+`r papaja::apa_print(cor.test(study1_finalRank$Guess, study1_finalRank$finalRank))$statistic`).
+However, there is substantial heterogeneity in perceptions of
+attractiveness. Of the 200 participants,
+`r length(unique(study1_time2$Target))` are ranked as 7th most
+attractive by at least one adviser. On average, men in this subset
+estimate they rank
+`r round(mean(TargetsUnique[TargetsUnique$gender == 'Male',]$Guess),2)`th
+and women estimate they rank
+`r round(mean(TargetsUnique[TargetsUnique$gender == 'Female',]$Guess),2)`th
+(`r papaja::apa_print(t.test(Guess ~ gender, data = TargetsUnique, var.equal = T))$statistic`).
+
+Next, we turn our attention to the advisers (see @fig-study1advice). In
+the Accuracy condition, those uploading selfies are on average advised
+to bet on rank
+`r round(mean(study1_time2[study1_time2$Condition == "Accurate",]$Advice),2)`.
+Notably, this is significantly more attractive than the 7th rank those
+advisers had themselves guessed just on the prior screen
+(`r papaja::apa_print(t.test(study1_time2[study1_time2$Condition == "Accurate",]$Advice, mu = 7, var.equal = T))$statistic`).
+This suggests that even when incentivized for accuracy, participants
+offer flattering advice.[^3] Importantly, and as predicted, we find that
+advisers in the Likeable treatment recommend betting on a lower rank,
+communicating that they think the participant in the selfie is more
+attractive
+(`r round(mean(study1_time2[study1_time2$Condition == "Likable",]$Advice),2)`,
+`r papaja::apa_print(t.test(Advice ~ Condition, data = study1_time2, var.equal = T))$statistic`).
+This suggests that advisers infer flattering someone with pleasant
+advice would make the adviser appear more likeable. The distribution
+shown in @fig-study1advice shows that participants do not simply tell
+participants that they are the most attractive person in the group. They
+may infer that flattering advise needs to be somewhat realistic to be
+believable. We return to this in the general discussion.
+
+[^3]: This shading could be due to concerns of avoiding disappointment.
+    However, it could also be that advisers are uncertain about the
+    rankings they have given and make a recommendation that combines
+    their own belief with a uniform prior. Therefore, our analyses focus
+    on the difference between the two conditions.
+
+<!-- David: Making a note here that we should be sure to discuss this at the end -->
+
+<!-- as something for future research. -->
+
+<!-- David: We should also report something on accuracy of the advice given across -->
+
+<!-- the treatments. Even if no difference. -->
+
+```{r}
+#| label: tbl-study1regs
+#| tbl-cap: "When individuals receive advice that implies a high level of attractiveness (lower rank), they tend to perceive the advice giver as more likable (Column 1), warm (Column 2).
+Column 3 shows that advisers are rated as more trustworthy when they advice lower ranks, but this relationship is only directional."
+#| after-caption-space: 0pt
+
+modelsummary::modelsummary(list(`(1)` = lm(likable ~ Advice, data = study1_time3),
+                                `(2)` = lm(warmAvg ~ Advice, data = study1_time3),
+                                `(3)` = lm(trustAvg ~ Advice, data = study1_time3)),
+                           vcov = c("classical", "classical", "classical"),
+                           coef_map = c("Advice" = "Advised Rank",
+                                        "(Intercept)" = "Constant"),
+                           stars = T,
+                           gof_map = list(list('raw' = 'nobs', 'clean' = 'N', 'fmt' = 0)))
+
+```
+
+Finally, we examine whether flattering advice indeed leads to more
+positive evaluations of advisers, or whether flattering advice is
+dismissed as insencere. Following our preregistration, we average the
+ratings on likeability, warmth, friendliness, and good-naturedness to
+create a scale of likeability ($\alpha$ =
+`r round(cronbach.alpha(study1_time3[, 5:8])$alpha,2)`); and we create a
+scale of trustworthiness by averaging the ratings of trustworthiness and
+sincerity ($\alpha$ =
+`r round(cronbach.alpha(study1_time3[, 9:10])$alpha,2)`).
+
+```{r}
+#| label: fig-study1rating
+#| fig-cap: "Participants tend to rate advisers who suggest betting on a higher rank (implying greater attractiveness) as more likable and warm."
+
+library(ggplot2)
+library(dplyr)
+library(tidyr)
+
+study1_time3 <- study1_time3 %>% dplyr::mutate(Advice = as.numeric(Advice))
+
+# Reshape the data to long format
+study1_long <- study1_time3 %>%
+  pivot_longer(cols = c(likable, warmAvg), 
+               names_to = "Evaluation", 
+               values_to = "Value")
+
+# Create the plot
+ggplot(study1_long, aes(x = Advice, y = Value, color = Evaluation)) +  
+  # Add points for each observation
+  geom_point(size = 2, alpha = 0.7,
+             position = position_jitter()) +
+
+  # Add linear regression lines for each metric
+  geom_smooth(method = "lm", se = TRUE, aes(fill = Evaluation), alpha = 0.2, show.legend = FALSE) +
+
+  # Customize axis labels
+  scale_y_continuous(name = "Evaluation",limits = c(0.9, 5.1)) +  
+  scale_x_continuous(name = "Advised Rank",limits = c(1, 10), breaks = c(1,2,3,4,5,6,7,8,9,10)) +
+
+  # Apply a theme
+  theme_bw() +  
+  theme(panel.grid = element_blank(),
+        panel.border = element_blank(),
+        axis.line = element_line(colour = "grey"),
+        legend.position = "right",
+        plot.title = element_text(hjust = 0.5, size = 20)) +
+
+  # Set custom colors for each metric
+  scale_color_manual(values = c("#FF7F3E", "#2A629A"), 
+                     labels = c("Likability", "Warm")) + 
+  scale_fill_manual(values = c("#FF7F3E", "#2A629A"))
+
+```
+
+```{r}
+#| label: fig-study1ratingByGroup
+#| fig-cap: "After participants receive advice that suggests betting on a rank that was lower than, equal to, or higher than their own guess, they evaluate advisers based on their likability and warmth.
+Participants rate advisers who give flattering advice and deliver a high evaluation of their attractiveness as more likable and warm than those whose advice implied a lower evaluation of their attractiveness."
+
+library(dplyr)
+library(ggplot2)
+library(reshape2)
+
+study1_time3 <- study1_time3 %>% dplyr::mutate(Guess = as.numeric(Guess), Advice = as.numeric(Advice)) %>%
+  dplyr::mutate(HorL = ifelse(Guess == Advice,0, ifelse(Guess > Advice, 1,-1))) %>%
+  dplyr::mutate(HorL = as.factor(HorL)) %>% 
+  dplyr::mutate(bonus = ifelse(bet == `Final Rank`,1,0)) %>%
+  dplyr::mutate(accuracy = `Final Rank`-Advice)
+
+ratings <- study1_time3 %>%
+  group_by(HorL) %>%
+  summarise(like = round(mean(likable),2), warmth = round(mean(warmAvg),2))
+
+rating_table <- matrix(c(ratings$like,ratings$warmth), nrow = 2, byrow = TRUE, dimnames = list( c("Likable",'Warm'),c("Lower than", "Equal to", "Higher than")))
+
+rating_df = as.data.frame.table(rating_table) %>%
+  dplyr::rename( 'Condition'='Var1', 'Advice' ='Var2') %>%
+  dplyr::mutate(Freq = round(Freq,2))
+
+# Create a data frame similar to your structure
+data <- rating_df
+
+# Reshape the data to wide format for the heatmap
+heatmap_data <- dcast(data, Condition ~ Advice, value.var = "Freq")
+
+# Melt the data for ggplot
+melted_data <- melt(heatmap_data, id.vars = "Condition", variable.name = "Advice", value.name = "Rating")
+
+# Create the heatmap
+ggplot(melted_data, aes(x = Advice, y = Condition, fill = Rating)) +
+  geom_tile(color = "white") +
+  scale_fill_gradient(low = "darkblue", high = "orange", name = "Rating") +  # Grey gradient from light to dark
+  geom_text(aes(label = sprintf("%.2f", Rating)), color = "white", size = 8) +
+  theme_minimal() +
+  labs(x = "Attractiveness (Advice Relative to Self-Expectations)", y = "Evaluation") +
+  theme(
+    axis.text.x = element_text(size = 12),  # X-axis text size
+          axis.text.y = element_text(size = 12),
+          axis.title.x = element_text(size = 12),  # X-axis title size
+          axis.title.y = element_text(size = 12))
+
+```
+
+As seen in @fig-study1rating, we advisers who suggested that the advisee
+was more attractive (lower rank) were indeed rated as more likeable and
+warm (b = -0.109, p \< .05; b = -0.133, p \< .001, respectively; See
+Columns 1 and 2 of @tbl-study1regs). When using their own initial guess
+as a reference point, advisers who suggest a worse rank are perceived as
+less likable and warm (see @fig-study1ratingByGroup). Interestingly,
+these benefits are not at the cost of sincerity; advisers who recommend
+a more favorable rank are viewed as no less trustworthy (Column 3 of
+@tbl-study1regs).
+
+We are not powered to do a comparison across the two experimental groups
+and did not preregister such a difference. Indeed, we find no difference
+in likeability and warmth across the two treatments
+(`r papaja::apa_print(t.test(likable ~ Condition, data = study1_time3, var.equal = T))$statistic`,
+and
+`r papaja::apa_print(t.test(warmAvg ~ Condition, data = study1_time3, var.equal = T))$statistic`,
+respectively). We also assess the quality of advice by measuring the
+discrepancy between the advised rank and the correct rank. We find no
+difference in accuracy across the advice treatments
+(`r papaja::apa_print(t.test(accuracy ~ Condition, data = study1_time3, var.equal = T))$statistic`).
+
+## Discussion
+
+When advice communicates ego-relevant information (here, people's
+attractiveness), we find that the advice people give is contingent on
+their incentives. Specifically, when they get rewarded for being more
+likeable, they recommend that the advisee bet on a more favorable rank
+than when they are incentivized for accuracy. People understand that the
+advice they give can influence how others perceive them and often use
+flattering advice as a tool to boost their likeablity. Importantly,
+advisees do not discount flattering advice and instead evaluate people
+who advise them to bet on a more attractive rank as warmer and more
+likeable. These gains to interpersonal perceptions do not come at the
+cost of trustworthiness, even when the advice is inflated.
+
+# Study 2
+
+We next examine whether advisers take into account the expectations of
 advisees when providing a recommendation. A group of participants
@@
 
+```{r}
+
+study2_time1 <- readRDS(here::here("Data/Study2_time1.Rds"))
+study2_ability50 <- read.csv(here::here("Data/Cleaned Data/S2_Ability50_clean.csv"))
+study2_time2_giver <- readRDS(here::here("Data/Study2_time2_giver.Rds"))
+study2_time2_advice <- readRDS(here::here("Data/Study2_time2_advice.Rds"))
+study2_time3 <- readRDS(here::here("Data/Study2_time3.Rds"))
+
+```
+
 In a preliminary stage, we recruited
-`r scales::comma(dim(study1_ability50)[1])` participants from Prolific
+`r scales::comma(dim(study2_ability50)[1])` participants from Prolific
 and gave them five minutes to complete a quiz consisting of ten items.
@@
 
-Next, we recruited `r scales::comma(dim(study1_time1)[1])` participants
+Next, we recruited `r scales::comma(dim(study2_time1)[1])` participants
 for the role of Advisees. They completed the same 10-item quiz, also
@@
 of the two groups (High or Low Performers) was selected by default, and
-Advisees were free to select the other group. The survey concluded 
-with basic demographic questions.
-
-We then recruited `r scales::comma(dim(study1_time2_giver)[1])`
+Advisees were free to select the other group. The survey concluded with
+basic demographic questions.
+
+We then recruited `r scales::comma(dim(study2_time2_giver)[1])`
 participants for the role of Advisers, and the focal part of our
@@
 our preregistration, we kept the survey open for 7 days. In total,
-`r scales::comma(dim(study1_time3)[1])` Advisees returned. The short
+`r scales::comma(dim(study2_time3)[1])` Advisees returned. The short
 survey reminded them of the task they completed in the previous survey,
@@
 real score and given them advice on which group to compete against, and,
-finally, reminded them of their initial choice of comparison group. 
-They were not informed of their true score or the
-score of the groups they could compete against. Participants then
-observed the advice from a randomly selected adviser and made their
-decision.
+finally, reminded them of their initial choice of comparison group. They
+were not informed of their true score or the score of the groups they
+could compete against. Participants then observed the advice from a
+randomly selected adviser and made their decision.
 
@@
 ```{r}
-contingency_table <- table(study1_time1$Guess, study1_time1$default)
+contingency_table <- table(study2_time1$Guess, study2_time1$default)
 
@@
 different from one another
-(`r papaja::printnum(round(mean(study1_time1[study1_time1$default == "Low",]$Score),2))`
+(`r papaja::printnum(round(mean(study2_time1[study2_time1$default == "Low",]$Score),2))`
 and
-`r round(mean(study1_time1[study1_time1$default == "High",]$Score),2)`
+`r round(mean(study2_time1[study2_time1$default == "High",]$Score),2)`
 for the Low Default and High Default treatments, respectively,
-`r papaja::apa_print(t.test(Score ~ default, data = study1_time1, var.equal = T))$statistic`).
+`r papaja::apa_print(t.test(Score ~ default, data = study2_time1, var.equal = T))$statistic`).
 As expected, the default manipulation changes their initial choices. In
 the "Low Default" treatment, only
-`r round(mean(study1_time1[study1_time1$default == "Low",]$Guess),2)*100`%
+`r round(mean(study2_time1[study2_time1$default == "Low",]$Guess),2)*100`%
 of participants prefer to compete against the High Performer Group,
 compared to
-`r round(mean(study1_time1[study1_time1$default == "High",]$Guess),2)*100`%
+`r round(mean(study2_time1[study2_time1$default == "High",]$Guess),2)*100`%
 of participants in the "High Default" treatment ($\chi^2$(1, n = 201) =
@@
 ```{r}
-#| label: tbl-study1regs
+#| label: tbl-study2regs
 #| tbl-cap: "Advice to compete against the High Performer Group in Study 1.
@@
 
-study1_advice <- study1_time2_advice %>%
+study2_advice <- study2_time2_advice %>%
   dplyr::mutate(Treatment = factor(Treatment, levels = c('Low', 'High'))) %>%
@@
 modelsummary::modelsummary(
-  list(`All Advice` = lm(Advice ~ ExpShow * Treatment, data = study1_advice), 
-       `Expectations Shown` = lm(Advice ~ Treatment + Score, data = study1_advice %>% dplyr::filter(ExpShow == 1))),
+  list(`All Advice` = lm(Advice ~ ExpShow * Treatment, data = study2_advice), 
+       `Expectations Shown` = lm(Advice ~ Treatment + Score, data = study2_advice %>% dplyr::filter(ExpShow == 1))),
   vcov = ~GiverID,
@@
 competing against the High Performer Group and 0 if they recommend the
-Low Performer Group. In Column 1 of @tbl-study1regs, we show our main
+Low Performer Group. In Column 1 of @tbl-study2regs, we show our main
 specificiation with the experimental assignment for Advisees (High
@@
 treatment, controlling for the true performance of the advisee in Column
-2 of @tbl-study1regs. We observe a significant main effect of the
+2 of @tbl-study2regs. We observe a significant main effect of the
 default treatment, where a high default increased the likelihood of
 receiving flattering advice. It is worth noting that, since only
-`r round(mean(study1_time1[study1_time1$default == "High",]$Guess),2)*100`
+`r round(mean(study2_time1[study2_time1$default == "High",]$Guess),2)*100`
 % of advisees in the high default group actually stuck with their
@@
 ```{r}
-#| label: fig-study1Advice
-#| fig-cap: "Advice given in Study 1. Advisees who were nudged to express high expectations were more likely to receive advice to compete against the High Performer Group."
-
-study1_time2_advice %>%
+#| label: fig-study2Advice
+#| fig-cap: "Advice given in Study 2. Advisees who were nudged to express high expectations were more likely to receive advice to compete against the High Performer Group."
+
+study2_time2_advice %>%
   mutate(Treatment=factor(Treatment, levels=c('High','Low'), labels = c('High default', 'Low default'))) %>%
@@
 competitors were more likely to receive flattering advice, encouraging
-them to pursue that option. This occurs even though advisers are
-incentivized to give good advice.
-
-# Study 2
-
-We next examine if advisers believe that flattering advice will improve
-how they are perceived, and if so, whether this perception is true. We
-do this by manipulating the incentives for advisers, who receive a bonus
-either based on how they are evaluated by an advisee, or a bonus for the
-advisee's accuracy.
-
-The study takes place in three stages. First, a group of advisees upload
-photos of themselves ("selfies") and are grouped with nine other
-participants of the same sex. We then recruit participants of the
-opposing sex to rank them from most to least attractive and to provide
-advice. Specifically, they advise the participant they ranked as the 7th
-most attractive (i.e., 4th least attractive) on what rank they should
-bet they were ranked by a larger group of raters. Advisers were randomly
-assigned to two treatments, receiving a bonus payment either if the
-advisee guessed their rank accurately or if the advisee evaluated the
-adviser as likeable as measured by a scale response. We hypothesize that
-advisers incentivized to be liked will recommend betting on a lower
-rank, i.e. that the advisee is more attractive.
-
-```{r}
-#| include: false
-
-study2_time1 <- readRDS(here::here("Data/Study2_time1.Rds"))
-study2_time1_200 <- readRDS(here::here("Data/Study2_time1_200.Rds"))
-study2_time2 <- readRDS(here::here("Data/Study2_time2.Rds"))
-study2_finalRank <- readRDS(here::here("Data/Study2_finalRank.Rds"))
-study2_time3 <- readRDS(here::here("Data/Study2_time3.Rds"))
-
-```
-
-## Methods
-
-We recruit 300 participants from Prolific and, after asking demographic
-questions, invite them to upload photos of themselves (selfies) to be
-rated by other participants on attractiveness. We obtain selfies from
-`r scales::comma(dim(study2_time1[study2_time1$gender == 'Male',])[1])`
-men and
-`r scales::comma(dim(study2_time1[study2_time1$gender == 'Female',])[1])`
-women adhering to our instructions (e.g., did not include other people).
-In line with our preregistration, we select the first 100 photos from
-women to arrive at a gender-balanced sample ($M_{\text{Age}}$ =
-`r mean(study2_time1_200$age)` years). Participants are informed that
-their selfies will be randomly grouped with those of nine other
-participants of their sex and ranked in terms of attractiveness by a
-group of new Prolific participants of the opposite sex. They then make
-an unincentivized guess of their rank.
-
-Next, we recruit `r scales::comma(dim(study2_time2)[1])` participants
-from Prolific for the role of advisers ($M_{\text{Age}}$ =
-`r round(mean(study2_time2$age),2)` years;
-`r round(mean(study2_time2$gender == "Female")*100, 2)`% Female). We
-first collect demographic information, then match them to a group of the
-opposite sex. They rank selfies of ten participants from most to least 
-attractive by entering their rankings into a text box next to each picture. 
-Because of a limitation with the survey software, we could not validate that each
-rank is given only once, and we remove 115 participants who failed to
-follow instructions and did not provide a complete ranking.[^2]
-
-[^2]: Moreover, we could not collect data from any participant who did
-    not select any participant as the 7th most attractive participant,
-    as that image would be shown on subsequent pages.
-
-After submitting their ratings, participants see the photo of the
-participant they ranked as the 7th most attractive (i.e., the 4th least
-attractive). We remind them of the rank they have just given to that
-person and inform them that this participant will be invited back and
-can earn a \$1 bonus if they correctly guess their rank. The rank is
-determined by the aggregate ratings of all participants who have ranked
-this group. Because the participant does not observe the other nine
-people in the group, they would depend on the adviser's recommendation
-along with their own assessment. We randomly assign advisers to one of
-two incentivization schemes. In the "Accuracy" treatment, they receive a
-bonus identical to the advisee: \$1 if they guess their rank correctly.
-In the "Likeability" treatment, we inform them that the advisee will
-rate them on a 5-point Likert scale on how likeable they thought they
-are. Each point on the scale would translate to a bonus of 20 cents.
-Advisers then select a rank (from 1 to 10) that they recommend the
-advisee to bet on.
-
-Finally, we invite participants from Stage 1 who were ranked as the 7th
-most attractive participant by at least one adviser (so that they
-received advice) back for the follow-up survey. Following our
-preregistration, we keep the survey open for 7 days. In total,
-`r scales::comma(dim(study2_time3)[1])` participants
-(`r scales::comma(dim(study2_time3[study2_time3$gender == 'Male',])[1])`
-men,
-`r scales::comma(dim(study2_time3[study2_time3$gender == 'Female',])[1])`
-women) complete the follow-up survey. We remind them of the selfie they
-uploaded in Stage 1 and that a group of 10 selfies, including theirs,
-had been rated by other participants from Prolific. They then see the
-advice from a randomly selected adviser and make their own guess with a
-\$1 incentive for accuracy. Finally, they rate the adviser's likability,
-warmth, friendliness, good-naturedness, trustworthiness, and sincerity
-on 5-point Likert scales [adapted from @Fiske2007].
-
-## Results
-
-```{r}
-#| include: false
-library(dplyr)
-
-TargetsUnique <- study2_time2 %>%
-  dplyr::select(Target) %>%
-  unique()
-
-TargetsUnique <- merge(TargetsUnique,study2_finalRank, by.x = 'Target', by.y = 'QID7_Id')
-
-```
-
-```{r}
-#| label: fig-study2advice-old
-#| fig-cap: "Advisers were asked to suggest what rank to bet on for someone they ranked as the 7th most attractive out of ten people.
-When incentivized for accuracy, most of them advised betting on 7, which was based on their evaluation of the recipient's attractiveness.
-However, when incentivized for likability, many participants gave flattering advice by suggesting betting on higher ranks that imply a higher evaluation of attractiveness."
-#| eval: false
-
-library(ggplot2)
-library(ggridges)
-
-study2_time2 <- study2_time2 %>% dplyr::mutate(Advice = as.numeric(Advice))
-
-ggplot(study2_time2, aes(x = Advice, y = Condition, fill = Condition)) +
-    # Reduce vertical spacing with rel_min_height and scale
-    geom_density_ridges(scale = 1.0, rel_min_height = 0.01, alpha = 0.7) +
-
-    # Shading the left side of x = 7 in light grey
-    geom_rect(aes(xmin = 7, xmax = Inf, ymin = -Inf, ymax = Inf), fill = "gray95", alpha = 0.01) +
-
-    # Add the dashed line at x = 7
-    geom_vline(xintercept = 7, col = 'black', linetype = 'dashed', linewidth = 0.7) +
-
-    # Add the text "Flattering" on the left of the line
-    annotate("text", x = 5, y = 0.6, label = "Flattering Ranks", hjust = 1, size = 8, fontface = "bold") +
-
-    # Manual fill colors
-    scale_fill_manual(values = c("#2A629A", '#FF7F3E'), labels = c("Accurate", "Likable")) +
-
-    # X-axis adjustments
-    scale_x_continuous(name = "Advised Rank", breaks = seq(1, 10)) +
-
-    # Theme adjustments
-    theme_bw() +
-  coord_flip() +
-    theme(panel.grid = element_blank(),
-          panel.border = element_blank(),
-          axis.line = element_line(colour = "black"),
-          legend.position = "none",
-          legend.title = element_blank(),
-          legend.key.size = unit(1.2, "lines"),
-          legend.text = element_text(size = 12),
-          plot.title = element_text(hjust = 0.5, size = 20),
-          axis.text.x = element_text(size = 14),  # X-axis text size
-          axis.text.y = element_text(size = 14),
-          axis.title.x = element_text(size = 16, face = "bold"),  # X-axis title size
-          axis.title.y = element_text(size = 16, face = "bold"))
-
-```
-
-```{r}
-#| label: fig-study2advice
-#| fig-cap: "Participants in Study 2 give advice to the person they rank 7th most attractive out of 10.
-When incentivized for accuracy, the majority recommends betting on that rank.
-However, when incentivized for likeability, participants inflate their advice to flatter the recipient as more attractive."
-
-study2_time2 <- study2_time2 %>% dplyr::mutate(Advice = as.numeric(Advice))
-
-study2_time2 %>%
-  dplyr::group_by(Condition) %>%
-  dplyr::mutate(total_per_condition = dplyr::n()) %>%
-  dplyr::group_by(Condition, Advice, total_per_condition) %>%
-  dplyr::summarize(n = dplyr::n()) %>%
-  dplyr::mutate(pct = ifelse(Condition == "Accurate", -n/total_per_condition, n/total_per_condition),
-                Advice = factor(Advice)) %>%
-  ggplot(aes(x = pct, y = Advice, fill = Condition)) +
-  geom_col() +
-  scale_x_continuous("Share of Advice",
-                     limits = c(-0.6, 0.6),
-                     labels = \(x) scales::percent(abs(x))) +
-  scale_y_discrete(limits = rev) +
-  # Dashed 'horizontal' line at Advice = 7
-  geom_hline(yintercept = 4, col = 'black', linetype = 'dashed', linewidth = 0.7) +
-  # Example text annotation (adjust x/y for positioning)
-  annotate("text", x = -0.3, y = 9, label = "Accuracy Incentive", hjust = 1, size = 4, fontface = "bold") +
-  annotate("text", x = 0.6, y = 9, label = "Likeable Incentive", hjust = 1, size = 4, fontface = "bold") +
-  # scale_y_continuous(name = "Advised Rank", breaks = seq(1, 10)) +
-  scale_fill_manual(values = c("#2A629A", "#FF7F3E")) +
-  papaja::theme_apa() +
-  theme(
-    legend.position  = "none",
-    axis.text.x  = element_text(size = 14),
-    axis.text.y  = element_text(size = 14),
-    axis.title.x = element_text(size = 16, face = "bold"),
-    axis.title.y = element_text(size = 16, face = "bold")
-  )
-```
-
-We begin by examining the prior beliefs of advisees who uploaded their
-selfies. On average, men guess they rank
-`r round(mean(study2_time1[study2_time1$gender == "Male",]$Guess),2)` in
-their group of 10 and women guess that they rank
-`r round(mean(study2_time1[study2_time1$gender == "Female",]$Guess),2)`
-(`r papaja::apa_print(t.test(Guess ~ gender, data = study2_time1, var.equal = T))$statistic`).
-Notably, people's self-perceptions correlate strongly with the aggregate
-ratings of the advisers
-(`r round(cor(study2_finalRank$Guess, study2_finalRank$finalRank),2)`,
-`r papaja::apa_print(cor.test(study2_finalRank$Guess, study2_finalRank$finalRank))$statistic`).
-However, there is substantial heterogeneity in perceptions of
-attractiveness. Of the 200 participants,
-`r length(unique(study2_time2$Target))` are ranked as 7th most
-attractive by at least one adviser. On average, men in this subset
-estimate they rank
-`r round(mean(TargetsUnique[TargetsUnique$gender == 'Male',]$Guess),2)`th
-and women estimate they rank
-`r round(mean(TargetsUnique[TargetsUnique$gender == 'Female',]$Guess),2)`th
-(`r papaja::apa_print(t.test(Guess ~ gender, data = TargetsUnique, var.equal = T))$statistic`).
-
-Next, we turn our attention to the advisers (see @fig-study2advice). In
-the Accuracy condition, those uploading selfies are on average advised
-to bet on rank
-`r round(mean(study2_time2[study2_time2$Condition == "Accurate",]$Advice),2)`.
-Notably, this is significantly more attractive than the 7th rank those
-advisers had themselves guessed just on the prior screen
-(`r papaja::apa_print(t.test(study2_time2[study2_time2$Condition == "Accurate",]$Advice, mu = 7, var.equal = T))$statistic`).
-This suggests that even when incentivized for accuracy, participants
-offer flattering advice.[^3] Importantly, and as predicted, we find that
-advisers in the Likeable treatment recommend betting on a lower rank,
-communicating that they think the participant in the selfie is more
-attractive
-(`r round(mean(study2_time2[study2_time2$Condition == "Likable",]$Advice),2)`,
-`r papaja::apa_print(t.test(Advice ~ Condition, data = study2_time2, var.equal = T))$statistic`).
-This suggests that advisers infer flattering someone with pleasant
-advice would make the adviser appear more likeable. The distribution
-shown in @fig-study2advice shows that participants do not simply tell
-participants that they are the most attractive person in the group. They
-may infer that flattering advise needs to be somewhat realistic to be
-believable. We return to this in the general discussion.
-
-[^3]: This shading could be due to concerns of avoiding disappointment.
-    However, it could also be that advisers are uncertain about the
-    rankings they have given and make a recommendation that combines
-    their own belief with a uniform prior. Therefore, our analyses focus
-    on the difference between the two conditions.
-
-<!-- David: Making a note here that we should be sure to discuss this at the end -->
-
-<!-- as something for future research. -->
-
-<!-- David: We should also report something on accuracy of the advice given across -->
-
-<!-- the treatments. Even if no difference. -->
-
-```{r}
-#| label: tbl-study2regs
-#| tbl-cap: "When individuals receive advice that implies a high level of attractiveness (lower rank), they tend to perceive the advice giver as more likable (Column 1), warm (Column 2).
-Column 3 shows that advisors are rated as more trustworthy when they advice lower ranks, but this relationship is only directional."
-#| after-caption-space: 0pt
-
-modelsummary::modelsummary(list(`(1)` = lm(likable ~ Advice, data = study2_time3),
-                                `(2)` = lm(warmAvg ~ Advice, data = study2_time3),
-                                `(3)` = lm(trustAvg ~ Advice, data = study2_time3)),
-                           vcov = c("classical", "classical", "classical"),
-                           coef_map = c("Advice" = "Advised Rank",
-                                        "(Intercept)" = "Constant"),
-                           stars = T,
-                           gof_map = list(list('raw' = 'nobs', 'clean' = 'N', 'fmt' = 0)))
-
-```
-
-Finally, we examine whether flattering advice indeed leads to more
-positive evaluations of advisers, or whether flattering advice is
-dismissed as insencere. Following our preregistration, we average the
-ratings on likeability, warmth, friendliness, and good-naturedness to
-create a scale of likeability ($\alpha$ =
-`r round(cronbach.alpha(study2_time3[, 5:8])$alpha,2)`); and we create a scale of
-trustworthiness by averaging the ratings of trustworthiness and
-sincerity ($\alpha$ = `r round(cronbach.alpha(study2_time3[, 9:10])$alpha,2)`).
-
-```{r}
-#| label: fig-study2rating
-#| fig-cap: "Participants tend to rate advisors who suggest betting on a higher rank (implying greater attractiveness) as more likable and warm."
-
-library(ggplot2)
-library(dplyr)
-library(tidyr)
-
-study2_time3 <- study2_time3 %>% dplyr::mutate(Advice = as.numeric(Advice))
-
-# Reshape the data to long format
-study2_long <- study2_time3 %>%
-  pivot_longer(cols = c(likable, warmAvg), 
-               names_to = "Evaluation", 
-               values_to = "Value")
-
-# Create the plot
-ggplot(study2_long, aes(x = Advice, y = Value, color = Evaluation)) +  
-  # Add points for each observation
-  geom_point(size = 2, alpha = 0.7,
-             position = position_jitter()) +
-
-  # Add linear regression lines for each metric
-  geom_smooth(method = "lm", se = TRUE, aes(fill = Evaluation), alpha = 0.2, show.legend = FALSE) +
-
-  # Customize axis labels
-  scale_y_continuous(name = "Evaluation",limits = c(0.9, 5.1)) +  
-  scale_x_continuous(name = "Advised Rank",limits = c(1, 10), breaks = c(1,2,3,4,5,6,7,8,9,10)) +
-
-  # Apply a theme
-  theme_bw() +  
-  theme(panel.grid = element_blank(),
-        panel.border = element_blank(),
-        axis.line = element_line(colour = "grey"),
-        legend.position = "right",
-        plot.title = element_text(hjust = 0.5, size = 20)) +
-
-  # Set custom colors for each metric
-  scale_color_manual(values = c("#FF7F3E", "#2A629A"), 
-                     labels = c("Likability", "Warm")) + 
-  scale_fill_manual(values = c("#FF7F3E", "#2A629A"))
-
-```
-
-```{r}
-#| label: fig-study2ratingByGroup
-#| fig-cap: "After participants receive advice that suggests betting on a rank that was lower than, equal to, or higher than their own guess, they evaluate advisors based on their likability and warmth.
-Participants rate advisors who give flattering advice and deliver a high evaluation of their attractiveness as more likable and warm than those whose advice implied a lower evaluation of their attractiveness."
-
-library(dplyr)
-library(ggplot2)
-library(reshape2)
-
-study2_time3 <- study2_time3 %>% dplyr::mutate(Guess = as.numeric(Guess), Advice = as.numeric(Advice)) %>%
-  dplyr::mutate(HorL = ifelse(Guess == Advice,0, ifelse(Guess > Advice, 1,-1))) %>%
-  dplyr::mutate(HorL = as.factor(HorL)) %>% 
-  dplyr::mutate(bonus = ifelse(bet == `Final Rank`,1,0)) %>%
-  dplyr::mutate(accuracy = `Final Rank`-Advice)
-
-ratings <- study2_time3 %>%
-  group_by(HorL) %>%
-  summarise(like = round(mean(likable),2), warmth = round(mean(warmAvg),2))
-
-rating_table <- matrix(c(ratings$like,ratings$warmth), nrow = 2, byrow = TRUE, dimnames = list( c("Likable",'Warm'),c("Lower than", "Equal to", "Higher than")))
-
-rating_df = as.data.frame.table(rating_table) %>%
-  dplyr::rename( 'Condition'='Var1', 'Advice' ='Var2') %>%
-  dplyr::mutate(Freq = round(Freq,2))
-
-# Create a data frame similar to your structure
-data <- rating_df
-
-# Reshape the data to wide format for the heatmap
-heatmap_data <- dcast(data, Condition ~ Advice, value.var = "Freq")
-
-# Melt the data for ggplot
-melted_data <- melt(heatmap_data, id.vars = "Condition", variable.name = "Advice", value.name = "Rating")
-
-# Create the heatmap
-ggplot(melted_data, aes(x = Advice, y = Condition, fill = Rating)) +
-  geom_tile(color = "white") +
-  scale_fill_gradient(low = "darkblue", high = "orange", name = "Rating") +  # Grey gradient from light to dark
-  geom_text(aes(label = sprintf("%.2f", Rating)), color = "white", size = 8) +
-  theme_minimal() +
-  labs(x = "Attractiveness (Advice Relative to Self-Expectations)", y = "Evaluation") +
-  theme(
-    axis.text.x = element_text(size = 12),  # X-axis text size
-          axis.text.y = element_text(size = 12),
-          axis.title.x = element_text(size = 12),  # X-axis title size
-          axis.title.y = element_text(size = 12))
-
-```
-
-As seen in @fig-study2rating, we advisers who suggested that the advisee
-was more attractive (lower rank) were indeed rated as more likeable and
-warm (b = -0.109, p \< .05; b = -0.133, p \< .001, respectively; See
-Columns 1 and 2 of @tbl-study2regs). When using their own initial guess
-as a reference point, advisers who suggest a worse rank are perceived as
-less likable and warm (see @fig-study2ratingByGroup). Interestingly,
-these benefits are not at the cost of sincerity; advisers who recommend
-a more favorable rank are viewed as no less trustworthy (Column 3 of
-@tbl-study2regs).
-
-We are not powered to do a comparison across the two experimental groups
-and did not preregister such a difference. Indeed, we find no difference
-in likeability and warmth across the two treatments
-(`r papaja::apa_print(t.test(likable ~ Condition, data = study2_time3, var.equal = T))$statistic`,
-and
-`r papaja::apa_print(t.test(warmAvg ~ Condition, data = study2_time3, var.equal = T))$statistic`,
-respectively). We also assess the quality of advice by measuring the
-discrepancy between the advised rank and the correct rank. We find no
-difference in accuracy across the advice treatments
-(`r papaja::apa_print(t.test(accuracy ~ Condition, data = study2_time3, var.equal = T))$statistic`).
-
-## Discussion
-
-In another context where advice communicates ego-relevant information
-(here, people's attractiveness), we find that the advice people give is
-contingent on their incentives. Specifically, when they get rewarded for
-being more likeable, they recommend that the advisee bet on a more
-favorable rank than when they are incentivized for accuracy.
-Importantly, advisees do not discount flattering advice and instead
-evaluate people who advise them to bet on a more attractive rank as
-warmer and more likeable. These gains to interpersonal perceptions do
-not come at the cost of trustworthiness, even when the advice is
-inflated.
+them to pursue that option. This occurs even though advisers share the
+potential costs of recommending a more challenging competition.
+
+```{=html}
+<!-- Amanda: I try to avoid using the term "good advice" or bring in risk.
+-->
+```
 
@@
 #| label: tbl-study3regs
-#| tbl-cap: "Column 1 displays the advice given to compete against a High Performance group based on whether the advisees were primed with low or high expectations and the expectation level shown to the advisor.
-Column 2 displays the advice given to compete against a High Performance group based on the gender of the targets and the expectation level shown to the advisor.
-Column 3 displays the expected bonus of the advice received based on the gender of the targets and the expectation level shown to the advisor.
-All standard errors clustered at the level of the advisor."
+#| tbl-cap: "Column 1 displays the advice given to compete against a High Performance group based on whether the advisees were primed with low or high expectations and the expectation level shown to the adviser.
+Column 2 displays the advice given to compete against a High Performance group based on the gender of the targets and the expectation level shown to the adviser.
+Column 3 displays the expected bonus of the advice received based on the gender of the targets and the expectation level shown to the adviser.
+All standard errors clustered at the level of the adviser."
 #| after-caption-space: 0pt
@@
 mathematics test scores more than men. When these expectations are shown
-to advisors, they are more likely to tell men to compete against high
+to advisers, they are more likely to tell men to compete against high
 performers than women. Notably, this turns out to be poor advice: men
-whose advisors are aware of their expectations receive worse advice. Our
+whose advisers are aware of their expectations receive worse advice. Our
 findings suggest that men with the same scores as their female
@@
 Advice has the potential to shape people's career and personal outcomes.
-Honest feedback, however, may be painful to learn if it falls short of
+Honest advice, however, may be painful to learn if it falls short of
 one's expectations. As prior work notes, this may motivate people to
@@
 told to aim higher. Notably, in the context of our experiment, this
-turns out to be bad advice ex post.
+turns out to lead to lower bonus compared to more conservative advice.
+While we focus on gender groups here, our findings may extend to other
+social groups where differences in expectations exist. This dynamic may
+create a reinforcing cycle — individuals with higher confidence are more
+likely to receive encouragement and positive reinforcement, further
+boosting their confidence. In contrast, individuals with lower
+confidence have fewer opportunities to receive such encouragement,
+despite potentially needing it the most.
+
+<!--# I tried to replace "bad advice". -->
 
 Our findings have implications for organizational practice, where
-mentoring and advice-giving may take into account an employees'
-expectation. We document this as a novel source of gender bias.
-Organizations could reduce this bias by calibrating employees'
-expectations to reduce overconfidence.
-
-Participants in our experiment were paired anonymously. Even so, we
-document this desire to avoid disappointment. We anticipate that advice
-would be more flattering in face-to-face communication and without
-anonymity. Moreover, existing relationships might make it even more
-difficult for advisers to be honest.
+mentoring and advice-giving often consider employees' expectations. On
+one hand, offering flattering advice may enhance relationships between
+mentors and mentees, enhancing trust and communication, which are
+crucial for collaboration and long-term organizational success. However,
+flattering advice may also lead to talent misallocation, as employees
+are more likely to be encouraged to pursue career paths aligned with
+their stated preferences and less likely to be recommended to explore
+alternative directions that might better match their potential.
+Additionally, when advisers hold significantly more power than advisees,
+interpersonal concerns may diminish [@Schaerer2018], resulting in advice
+that is more blunt or even harsh. As a result, advisees may seek
+flattering advice from peers or subordinates instead, missing out on
+valuable expertise from their supervisors. Lastly, we identify
+flattering advice as a novel source of gender bias, as women may receive
+less ambitious advice due to lower expressed confidence. Organizations
+could reduce this bias by calibrating employees' expectations to curb
+overconfidence and/or compensate for a lack of confidence.
+
+Participants in our experiment were paired online and remained
+anonymous. Even so, we document this desire to avoid disappointment.
+Given that communications mediated by computer tends to be less
+emotionally rich [@Kiesler1985], and that anonymity reduces the
+psychological burden of responsibility for the advisee's feelings, as it
+cannot be traced back to the adviser. We anticipate that advice would be
+more flattering in face-to-face communication and without anonymity.
+
+Moreover, existing relationships might make it even harder for advisers
+to be fully honest. Advisers tend to feel more concerned and emotionally
+attached to how friends, family, or colleagues feel compared to how a
+stranger would feel, which may increase their motivation to provide
+flattering advice. Conversetly, advisees also tend to value the
+emotional support embedded in advice from their friends, even when it
+lacks informational utility. Moreover, people generally prefer their
+close ones to demonstrate benevolence toward them rather than apply
+impartial integrity during interactions [@Levine2020]. In response to
+these expectations, advisers might intentionally inflate their advice to
+strengthen their bond with the advisee and protect them from discomfort.
+
+The closeness of the relationship may moderate the tendency to provide
+flattering advice. On one hand, advisers may prioritize the advisee’s
+best interests above other considerations when offering advice to
+someone they have a close and strong relationship with, making them more
+willing to provide the most helpful advice, even if it is unflattering.
+Advisers may also feel more confident that a close relationship is
+resilient enough to withstand any immediate disappointment the advisee
+may experience if the advice falls short of their self-expectations. On
+the other hand, closer relationships may also strengthed the adviser’s
+motivation to protect the advisee’s feelings, increasing the likelihood
+of offering flattering advice. Future research could explore how
+relationship closeness influences the balance between providing
+flattering versus candid advice.
 
@@
 
-Advice has long been studied from the perspective of the receiver.
+Advice has long been studied from the perspective of the receiver
+[@Rader2017; @yaniv2004receiving; @bonaccio2006Review; @Milyavsky2024].
 Similarly, research on belief utility has examined how recipients

### 2025-03-12 manuscript/manuscript.tex
Updated keywords
manuscript_0311

@@
 
-\abstract{Good advice improves decision quality but often requires
-delivering unpleasant truths that may disappoint advisees. Across three
+\abstract{Advice that improves decision-making does not always feel
+good. While advice has the potential to improve decision-making by
+helping advisees more accurately assess feasibility and predict
+potential outcomes, it can also lead to disappointment when it
+challenges the advisee's overly optimistic expectations. Across three
 pre-registered and incentivized experiments involving real
@@
 prioritize avoiding disappointment at the expense of accuracy and their
-own earnings. In Study 1, advisers financially rewarded for accuracy
-still tailor recommendations to aspirational goals expressed by
-advisees, resulting in worse advice. When incentivized to be liked,
-advisers provide even more flattering advice, and advisees reward this
-by rating these advisers as more likable, despite the advice being less
-honest and less accurate (Study 2). The desire to avoid disappointment
-may lead to inequities if there are differences in expectations across
-social groups. In Study 3, we examine a setting in which men expect to
-perform better than women. We show that advisers take into account these
-expectations, leading to systematically different advice for men and
-women even when their gender is unknown to advisers. Advisers' efforts
-to avoid disappointment may thus contribute to systematic gender
-disparities in advice, with implications for downstream
-decision-making.}
-
-\keywords{Gender difference, Advice, Interpresonal relationship}
+own earnings. In study 1, advisers use flattering advice to create more
+positive impressions, and advisees reward this by rating these advisers
+as more likable, despite the advice being less honest and less accurate.
+Even advisers incentivised for accuracy still tailor recommendations to
+aspirational goals expressed by advisees, resulting in financial loss
+for them and the advisees (Study 2). The concern for interpersonal
+consequences may lead to inequities if there are differences in
+expectations across social groups. In Study 3, we examine a setting in
+which men expect to perform better than women. We show that advisers
+take into account these expectations, leading to systematically
+different advice for men and women even when their gender is unknown to
+advisers. Advisers' efforts to avoid disappointment may thus contribute
+to systematic gender disparities in advice, with implications for
+downstream decision-making.}
+
+\keywords{Advice, Interpresonal relationship, Gender difference}
 
@@
 
-Career trajectories for men and women often differ substantially, even
-among those with similar qualifications. One source of such differences
-may be the advice that people receive. Prior work has documented that
-men receive more aspirational advice and women more risk-averse advice,
-which may explain why women are less likely to apply for and ultimately
-obtain more rewarding positions (Kanze et al., 2018). Research on gender
-discrimination has focused on the role of unconscious bias (Banaji \&
-Greenwald, 1995; Nosek et al., 2009), but interventions that try to
-reduce this bias have been largely unsuccessful (Chang et al., 2019;
-Paluck \& Green, 2009). Recent work has proposed cognitive, rather than
-unconscious, biases that can lead to gender discrimination through the
-formation of false beliefs (Hagmann et al., 2024). Here, we propose a
-novel source of differences in advice by drawing on recent work on
-belief-based utility, expectation-based reference points (Kőszegi \&
-Rabin, 2006, 2009), and the hedonic consequences of information (Golman
-et al., 2017).
-
 Advice figures prominently in workplace and personal decision-making,
@@
 (Gino \& Moore, 2007; Harvey \& Fischer, 1997; Soll \& Larrick, 2009).
-Its fundamental premise is to improve outcomes by enabling
-decision-makers to learn from others' expertise. However, while honest
-advice can lead to better decisions, it can also lead to disappointment
-when it suggests a desired outcome is unlikely to materialize. Advisers
-may be motivated to offer flattering recommendations that align with
-advisees' hopes, sparing them the disappointment of a more sobering
-forecast.
-
-Advice with the potential for disappointment appears in diverse
-organizational settings: supervisors deliver feedback on employee
-performance, lawyers convey likely outcomes of litigation to their
-clients, and academics offer thoughts on colleagues' manuscripts.
-Ideally, honest information would help people identify their strengths
-and weaknesses, make informed decisions about whether to pursue legal
-cases, and strengthen papers prior to submission to academic journals,
-thus improving long-term outcomes. In practice, however, interpersonal
-considerations may prevent candor. When someone's expectations are (too)
-high, an adviser might hesitate to deliver information that undermines
-it---particularly if doing so risks negative interpersonal
-repercussions.
+While others can provide information in the form of opinions (Trouche et
+al., 2018), feedback (Kluger \& DeNisi, 1996), or personal observations
+(Yoon et al., 2021) to influence the decision-maker, this project
+focuses specifically on advice---defined as ``information that is
+perceived as intended to help an advisee deal with their issue of
+deliberation'' (Milyavsky \& Gvili, 2024). Advice is distinct from other
+forms of input because its primary purpose is to improve decision-making
+by leveraging others' expertise.
+
+Advice has the power to enhance decisions, yet it also carries the risk
+of disappointment. For example, a career consultant might advise an
+employee to enroll in a management program to strengthen their skill set
+before competing for a leadership role. Ideally, such honest advice
+helps the employee identify areas for personal growth. In practice,
+however, the employee might feel overlooked and frustrated that their
+ambitions are not immediately supported. As a result, advisers may be
+inclined to offer flattering recommendations that align with---or even
+exceed---advisees' hopes, such as encouraging the employee to pursue the
+leadership role despite concerns about their readiness. In this way,
+interpersonal dynamics may discourage full candor in giving advice.
+
+The objective of this research is to examine the dilemma advisers face:
+Should they provide accurate but potentially painful advice, or soften
+their recommendations to preserve the advisee's mood and protect their
+own standing? Given that advisees tend to prefer advisers who withhold
+bad news (Shalvi et al., 2019) nd penalize those who deliver it (John et
+al., 2019), advisers may reasonably avoid full candor---especially when
+they bear no cost for the advisee's mistakes. Specifically, when
+someone's expectations are (too) high, an adviser may hesitate to
+provide advice that challenges them, particularly if doing so risks
+straining the relationship or causing negative interpersonal
+consequences.
+
+Our research contributes to the growing literature on advisers' motives
+and intentions in advice-giving. This line of work examines how
+advisers' perceived dishonesty or helping intentions influence advice
+utilization (Haran \& Shalvi, 2020; Mackinger et al., 2017; Milyavsky \&
+Gvili, 2024; Van Swol, 2009). By examining advice within its
+interactional and communicative context, we extend this research by
+incorporating another dimension of advisers' motives---interpersonal
+concerns. We demonstrate that advisers adjust their recommendations to
+avoid hurting the advisee's feelings and self-image. Second, we
+contribute to the belief-based utility literature, which suggests that
+individuals derive satisfaction from their beliefs about the world and
+themselves (Loewenstein \& Molnar, 2018). We show that advisers also
+place value on preserving advisees' self-perceptions, often tailoring
+their advice to align with the advisee's expectations. Furthermore, we
+reveal that this advice-giving strategy has unintended consequences---it
+transforms the confidence gap {[}where women tend to be less confident
+than men; Lundeberg et al. (1994){]} into an advice gap, in which women
+are less likely than men to receive advice to aim higher, thereby
+reinforcing existing gender inequalities.
+
+\subsection{The Motives Behind
+Advice-Giving}\label{the-motives-behind-advice-giving}
 
 While much of the literature on advice assumes that advisers aim to
-provide the most helpful advice, thier motivations are often more
+provide the most helpful advice, their motivations are often more
 complex (Dalal \& Bonaccio, 2010; Rader et al., 2017; Yaniv \&
-Choshen-Hillel, 2012). Advisers are not only concerned with the accuracy
-and usefulness of their advice but also with their relationships with
-advisees. Interpersonal concerns---such as maintaining a positive image,
-avoiding conflict, or preserving social harmony---can shape the way
-advice is delivered (Chentsova-Dutton \& Vaughn, 2012; Schaerer et al.,
-2018; Van Swol, 2009). In particular, advisers may strategically soften
-their messages or withhold unfavorable information to manage how they
-are perceived or to prevent discomfort for both themselves and the
-advisee (Levine et al., 2020; Sniezek \& Van Swol, 2001). These
+Choshen-Hillel, 2012). Other than the accuracy and usefulness of the
+advice, interpersonal concerns---such as maintaining a positive image,
+avoiding conflict, or preserving social harmony---can shape what advice
+is delivered and how (Levine et al., 2020; Sniezek \& Van Swol, 2001).
+For example, research has shown how people often avoid providing
+negative feedback directly, opting instead for ambiguity or indirect
+phrasing to minimize discomfort (Levine et al., 2020). These
 interpersonal dynamics suggest that advice is not always optimized for
@@
 psychological considerations.
+
+In particular, advisers may strategically soften their messages or
+withhold unfavorable evaluations to manage how they are perceived or to
+prevent discomfort for both themselves and the advisee (Chentsova-Dutton
+\& Vaughn, 2012; Schaerer et al., 2018; Van Swol, 2009). When advisers
+anticipate disagreement or resistance, they may soften their
+recommendations or frame them more diplomatically, sometimes at the
+expense of accuracy. This suggests that advice is not merely a means of
+sharing information but also a tool for managing social interactions and
+reducing potential friction (Van Swol, 2009). These interpersonal
+considerations become even more pronounced when there is a power
+imbalance between the adviser and advisee, as lower-power advisers may
+be more hesitant to offer direct or critical guidance to avoid negative
+repercussions (Schaerer et al., 2018).
 
@@
 advisers who withhold bad news from them (Shalvi et al., 2019) and
-punish those who communicate bad news (John et al., 2019). Advisers,
-anticipating these preferences and consequences face a dilemma: Should
-they provide the accurate but potentially painful truth, or shade their
-recommendations to preserve the advisee's mood and the adviser's own
-standing? Advisers who fear they will be blamed or disliked for
-undermining someone's confidence may reasonably avoid candid feedback,
-particularly if they don't incur a cost when the advisee makes a
-mistake.
+punish those who communicate bad news (John et al., 2019). Advisers who
+fear they will be blamed or disliked for undermining someone's
+confidence may reasonably avoid candid advice, particularly if they
+don't incur a cost when the advisee makes a mistake.
+
+Providing flattering advice, however, should not be seen as maliciously
+misleading the advisee. Rather than being irrational, it tends to be
+more optimistic, and this optimism is not necessarily misplaced. Often,
+the advisee possesses insights about themselves---such as their
+motivation and past experiences---that the adviser may overlook or have
+no access to. Take, for example, an employee deciding whether to compete
+for a leadership role. While the adviser might focus on the employee's
+lack of management knowledge, the employee may have strong leadership
+characteristics, excellent communication skills, and persuasive
+abilities. In this way, flattering advice can encourage the advisee to
+set ambitious goals, fostering a self-fulfilling prophecy where
+confidence drives success (Jussim, 1986; Locke \& Latham, 2006).
+
+Of course, if the advice is overly inflated, it may become unhelpful.
+However, this is unlikely to happen, as advisers typically aim to boost
+the advisee's confidence while maintaining credibility. Suggesting an
+unrealistic option---such as encouraging an entry-level employee to
+compete for a CEO position---would come across as insincere or even
+mocking rather than flattering.
+
+Beyond protecting the advisee's beliefs and fostering their confidence
+and motivation, advisers may also offer flattering advice to shield
+themselves from blame if the ultimate decision leads to a poor outcome.
+Although both the adviser and advisee recognize the inherent uncertainty
+between the advice, the decision, and the final outcome, people tend to
+attribute poor outcomes to the adviser (Palmeira et al., 2015; Weiner,
+1985). However, research suggests that people differentiate between
+errors made intentionally---such as those driven by insufficient
+knowledge or deliberate bias---and those made unintentionally, with
+harsher penalties imposed on advisers perceived to have deliberately
+undermined the decision (Haran \& Shalvi, 2020). Flattering advice, even
+when ultimately unhelpful, may reduce the likelihood of blame because
+advisees are less likely to suspect ill intent from an adviser who
+appears supportive. Advisees may instead interpret the poor outcome as
+an unintended error rather than deliberate misguidance, particularly
+because they view the adviser positively and believe the adviser
+genuinely holds them in high regard (Haran \& Shalvi, 2020; Palmeira et
+al., 2015). Even when advisees recognize that flattering advice was
+intended to boost their confidence, research shows that people tend to
+appreciate such misplaced good intentions, as they strengthen social
+bonds by making the gift-giver feel socially closer (Zhang \& Epley,
+2012).
+
+Advisers may choose to inflate their advice for different reasons,
+depending on their relationship with the advisee and the stakes of the
+decision. For instance, advisers might offer flattering advice to
+strangers out of politeness, provide inflated encouragement to friends
+to offer emotional support (Dalal \& Bonaccio, 2010), or use their
+recommendations to motivate individuals with particularly ambitious or
+competitive personalities. We recognize that multiple motives may
+simultaneously drive this behavior, and their relative influence---as
+well as advisers' overall tendency to inflate advice---may vary across
+situations. However, in this project, we focus specifically on whether
+advisers intentionally inflate their advice and explore the potential
+consequences of doing so.
+
+One downstream consequence of giving flattering advice is the potential
+to reinforce gender differences --- specifically, men are more likely to
+receive such inflated advice. Prior work has documented that men receive
+more aspirational advice and women more risk-averse advice, which may
+explain why women are less likely to apply for and ultimately obtain
+more rewarding positions (Kanze et al., 2018). Research on gender
+discrimination has focused on the role of unconscious bias (Banaji \&
+Greenwald, 1995; Nosek et al., 2009), but interventions that try to
+reduce this bias have been largely unsuccessful (Chang et al., 2019;
+Paluck \& Green, 2009). Recent work has proposed cognitive, rather than
+unconscious, biases that can lead to gender discrimination through the
+formation of false beliefs (Hagmann et al., 2024). Here, we propose that
+one overlooked mechanism driving gender disparities in career outcomes
+may lie in the differential provision of flattering advice, shaped by
+the advisee's self-expectations.
+
+Specifically, when advisers aim to make their advice appear flattering,
+they may rely less on an objective evaluation of the advisee's
+competence and instead anchor their advice on the advisee's
+self-expectations. Drawing on the literature on belief-based utility and
+expectation-based reference points (Kőszegi \& Rabin, 2006, 2009), we
+suggest that advisers may align their advice with how ambitious or
+confident the advisee appears, so that they give optimistic but not
+entirely unrealistic recommendations. This dynamic may inadvertently
+disadvantage women. Research shows that men generally hold higher
+self-expectations or are more likely to display confidence, while women
+tend to exhibit more modest self-assessments despite comparable
+competence (Kanze et al., 2018). As a result, advisers may
+unintentionally offer men more ambitious and aspirational advice,
+encouraging them to pursue higher-rewarding opportunities, while
+offering women more cautious, conservative advice that aligns with their
+lower expressed self-expectations. This differential treatment, though
+seemingly well-intentioned, can have profound downstream consequences.
+By tailoring advice to match the advisee's perceived self-expectations,
+advisers may subtly nudge men toward risk-taking, leadership roles, or
+competitive opportunities, while directing women toward safer, less
+ambitious paths --- ultimately reinforcing existing gender disparities
+in career outcomes.
+
+\section{Overview of studies}\label{overview-of-studies}
 
@@
 
-In Study 1, we nudge advisees into a preference for competing against
+Across all three studies, we use a three-stage design. In Stage 1, we
+measure the advisee's performance and their self-expectations. In Stage
+2, we show the measured performance to the adviser and ask them to
+provide advice on how the advisee can maximize their chances of earning
+a bonus. Half of the advisers also receive information about the
+advisee's self-expectations. Importantly, this expectation information
+is objectively irrelevant to the task, as the bonus is solely based on
+the advisee's performance, which is already measured. While in real
+life, self-expectations might contain useful insights (such as
+unobservable skills or motivation), in our setup, self-expectations
+serve no informative value. Moreover, flattering advice provided in this
+setup cannot be justified as a motivational boost (like a pep talk)
+because the performance has already been fixed. Finally, in Stage 3, we
+re-invite the advisees from Stage 1, show them the advice they received,
+and observe how they make their final decisions.
+
+In Study 1, we ask advisees to upload photos of themselves and advisers
+rank them on their attractiveness. Advisers then recommend which rank
+the advisee should bet on, receiving an incentive either for the
+advisee's accuracy or for being evaluated favorably. Both groups of
+advisers recommend a rank that is more attractive than what they
+themselves have evaluated the advisee, and those incentivized for
+likability further inflate the ranking. Advisees evaluate advisers more
+favorably when they recommend betting on a more attractive rank,
+including viewing them as more trustworthy.
+
+In Study 2, we nudge advisees into a preference for competing against
 either a group of top-performers or a group of low-performers, through
@@
 
-We first examine whether advisers take into account the expectations of
+We first examine if advisers believe that flattering advice will improve
+how they are perceived, and if so, whether this perception is true. We
+do this by manipulating the incentives for advisers, who receive a bonus
+either based on how they are evaluated by an advisee, or a bonus for the
+advisee's accuracy.
+
+The study takes place in three stages. First, a group of advisees upload
+photos of themselves (``selfies'') and are grouped with nine other
+participants of the same sex. We then recruit participants of the
+opposing sex to rank them from most to least attractive and to provide
+advice. Specifically, they advise the participant they ranked as the 7th
+most attractive (i.e., 4th least attractive) on what rank they should
+bet they were ranked by a larger group of raters. Advisers were randomly
+assigned to two treatments, receiving a bonus payment either if the
+advisee guessed their rank accurately or if the advisee evaluated the
+adviser as likeable as measured by a scale response. We hypothesize that
+advisers incentivized to be liked will recommend betting on a lower
+rank, i.e.~that the advisee is more attractive.
+
+\subsection{Methods}\label{methods}
+
+We recruit 300 participants from Prolific and, after asking demographic
+questions, invite them to upload photos of themselves (selfies) to be
+rated by other participants on attractiveness. We obtain selfies from
+100 men and 107 women adhering to our instructions (e.g., did not
+include other people). In line with our preregistration, we select the
+first 100 photos from women to arrive at a gender-balanced sample
+(\(M_{\text{Age}}\) = 39.37 years). Participants are informed that their
+selfies will be randomly grouped with those of nine other participants
+of their sex and ranked in terms of attractiveness by a group of new
+Prolific participants of the opposite sex. They then make an
+unincentivized guess of their rank.
+
+Next, we recruit 472 participants from Prolific for the role of advisers
+(\(M_{\text{Age}}\) = 41.03 years; 49.79\% Female). We first collect
+demographic information, then match them to a group of the opposite sex.
+They rank selfies of ten participants from most to least attractive by
+entering their rankings into a text box next to each picture. Because of
+a limitation with the survey software, we could not validate that each
+rank is given only once, and we remove 115 participants who failed to
+follow instructions and did not provide a complete ranking.\footnote{Moreover,
+  we could not collect data from any participant who did not select any
+  participant as the 7th most attractive participant, as that image
+  would be shown on subsequent pages.}
+
+After submitting their ratings, participants see the photo of the
+participant they ranked as the 7th most attractive (i.e., the 4th least
+attractive). We remind them of the rank they have just given to that
+person and inform them that this participant will be invited back and
+can earn a \$1 bonus if they correctly guess their rank. The rank is
+determined by the aggregate ratings of all participants who have ranked
+this group. Because the participant does not observe the other nine
+people in the group, they would depend on the adviser's recommendation
+along with their own assessment. We randomly assign advisers to one of
+two incentivization schemes. In the ``Accuracy'' treatment, they receive
+a bonus identical to the advisee: \$1 if they guess their rank
+correctly. In the ``Likeability'' treatment, we inform them that the
+advisee will rate them on a 5-point Likert scale on how likeable they
+thought they are. Each point on the scale would translate to a bonus of
+20 cents. Advisers then select a rank (from 1 to 10) that they recommend
+the advisee to bet on.
+
+Finally, we invite participants from Stage 1 who were ranked as the 7th
+most attractive participant by at least one adviser (so that they
+received advice) back for the follow-up survey. Following our
+preregistration, we keep the survey open for 7 days. In total, 146
+participants (77 men, 69 women) complete the follow-up survey. We remind
+them of the selfie they uploaded in Stage 1 and that a group of 10
+selfies, including theirs, had been rated by other participants from
+Prolific. They then see the advice from a randomly selected adviser and
+make their own guess with a \$1 incentive for accuracy. Finally, they
+rate the adviser's likability, warmth, friendliness, good-naturedness,
+trustworthiness, and sincerity on 5-point Likert scales (adapted from
+Fiske et al., 2007).
+
+\subsection{Results}\label{results}
+
+\begin{figure}
+
+\caption{\label{fig-study1advice}Participants in Study 2 give advice to
+the person they rank 7th most attractive out of 10. When incentivized
+for accuracy, the majority recommends betting on that rank. However,
+when incentivized for likeability, participants inflate their advice to
+flatter the recipient as more attractive.}
+
+\centering{
+
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-study1advice-1.pdf}}
+
+}
+
+\end{figure}%
+
+We begin by examining the prior beliefs of advisees who uploaded their
+selfies. On average, men guess they rank 5.76 in their group of 10 and
+women guess that they rank 6.37 (\(t(205) = 2.15\), \(p = .033\)).
+Notably, people's self-perceptions correlate strongly with the aggregate
+ratings of the advisers (0.43, \(t(193) = 6.70\), \(p < .001\)).
+However, there is substantial heterogeneity in perceptions of
+attractiveness. Of the 200 participants, 149 are ranked as 7th most
+attractive by at least one adviser. On average, men in this subset
+estimate they rank 5.94th and women estimate they rank 6.59th
+(\(t(143) = 1.94\), \(p = .054\)).
+
+Next, we turn our attention to the advisers (see
+Figure~\ref{fig-study1advice}). In the Accuracy condition, those
+uploading selfies are on average advised to bet on rank 6.19. Notably,
+this is significantly more attractive than the 7th rank those advisers
+had themselves guessed just on the prior screen (\(t(234) = -8.82\),
+\(p < .001\)). This suggests that even when incentivized for accuracy,
+participants offer flattering advice.\footnote{This shading could be due
+  to concerns of avoiding disappointment. However, it could also be that
+  advisers are uncertain about the rankings they have given and make a
+  recommendation that combines their own belief with a uniform prior.
+  Therefore, our analyses focus on the difference between the two
+  conditions.} Importantly, and as predicted, we find that advisers in
+the Likeable treatment recommend betting on a lower rank, communicating
+that they think the participant in the selfie is more attractive (5.38,
+\(t(470) = 5.44\), \(p < .001\)). This suggests that advisers infer
+flattering someone with pleasant advice would make the adviser appear
+more likeable. The distribution shown in Figure~\ref{fig-study1advice}
+shows that participants do not simply tell participants that they are
+the most attractive person in the group. They may infer that flattering
+advise needs to be somewhat realistic to be believable. We return to
+this in the general discussion.
+
+\begin{table}
+
+{\caption{{When individuals receive advice that implies a high level of
+attractiveness (lower rank), they tend to perceive the advice giver as
+more likable (Column 1), warm (Column 2). Column 3 shows that advisers
+are rated as more trustworthy when they advice lower ranks, but this
+relationship is only directional.}{\label{tbl-study1regs}}}\vspace{0pt}
+}
+
+\centering
+\begin{talltblr}[         %% tabularray outer open
+entry=none,label=none,
+note{}={+ p \num{< 0.1}, * p \num{< 0.05}, ** p \num{< 0.01}, *** p \num{< 0.001}},
+]                     %% tabularray outer close
+{                     %% tabularray inner open
+colspec={Q[]Q[]Q[]Q[]},
+column{1}={halign=l,},
+column{2}={halign=c,},
+column{3}={halign=c,},
+column{4}={halign=c,},
+hline{6}={1,2,3,4}{solid, 0.05em, black},
+}                     %% tabularray inner close
+\toprule
+& (1) & (2) & (3) \\ \midrule %% TinyTableHeader
+Advised Rank & \num{-0.109}*  & \num{-0.133}** & \num{-0.054}   \\
+& (\num{0.046})  & (\num{0.044})  & (\num{0.042})  \\
+Constant     & \num{3.777}*** & \num{3.903}*** & \num{3.397}*** \\
+& (\num{0.279})  & (\num{0.266})  & (\num{0.257})  \\
+N            & \num{146}      & \num{146}      & \num{146}      \\
+\bottomrule
+\end{talltblr}
+
+\end{table}
+
+Finally, we examine whether flattering advice indeed leads to more
+positive evaluations of advisers, or whether flattering advice is
+dismissed as insencere. Following our preregistration, we average the
+ratings on likeability, warmth, friendliness, and good-naturedness to
+create a scale of likeability (\(\alpha\) = 0.92); and we create a scale
+of trustworthiness by averaging the ratings of trustworthiness and
+sincerity (\(\alpha\) = 0.87).
+
+\begin{figure}
+
+\caption{\label{fig-study1rating}Participants tend to rate advisers who
+suggest betting on a higher rank (implying greater attractiveness) as
+more likable and warm.}
+
+\centering{
+
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-study1rating-1.pdf}}
+
+}
+
+\end{figure}%
+
+\begin{figure}
+
+\caption{\label{fig-study1ratingByGroup}After participants receive
+advice that suggests betting on a rank that was lower than, equal to, or
+higher than their own guess, they evaluate advisers based on their
+likability and warmth. Participants rate advisers who give flattering
+advice and deliver a high evaluation of their attractiveness as more
+likable and warm than those whose advice implied a lower evaluation of
+their attractiveness.}
+
+\centering{
+
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-study1ratingByGroup-1.pdf}}
+
+}
+
+\end{figure}%
+
+As seen in Figure~\ref{fig-study1rating}, we advisers who suggested that
+the advisee was more attractive (lower rank) were indeed rated as more
+likeable and warm (b = -0.109, p \textless{} .05; b = -0.133, p
+\textless{} .001, respectively; See Columns 1 and 2 of
+Table~\ref{tbl-study1regs}). When using their own initial guess as a
+reference point, advisers who suggest a worse rank are perceived as less
+likable and warm (see Figure~\ref{fig-study1ratingByGroup}).
+Interestingly, these benefits are not at the cost of sincerity; advisers
+who recommend a more favorable rank are viewed as no less trustworthy
+(Column 3 of Table~\ref{tbl-study1regs}).
+
+We are not powered to do a comparison across the two experimental groups
+and did not preregister such a difference. Indeed, we find no difference
+in likeability and warmth across the two treatments (\(t(144) = 1.09\),
+\(p = .275\), and \(t(144) = 0.58\), \(p = .562\), respectively). We
+also assess the quality of advice by measuring the discrepancy between
+the advised rank and the correct rank. We find no difference in accuracy
+across the advice treatments (\(t(144) = -0.29\), \(p = .776\)).
+
+\subsection{Discussion}\label{discussion}
+
+When advice communicates ego-relevant information (here, people's
+attractiveness), we find that the advice people give is contingent on
+their incentives. Specifically, when they get rewarded for being more
+likeable, they recommend that the advisee bet on a more favorable rank
+than when they are incentivized for accuracy. People understand that the
+advice they give can influence how others perceive them and often use
+flattering advice as a tool to boost their likeablity. Importantly,
+advisees do not discount flattering advice and instead evaluate people
+who advise them to bet on a more attractive rank as warmer and more
+likeable. These gains to interpersonal perceptions do not come at the
+cost of trustworthiness, even when the advice is inflated.
+
+\section{Study 2}\label{study-2}
+
+We next examine whether advisers take into account the expectations of
 advisees when providing a recommendation. A group of participants
@@
 
-\subsection{Methods}\label{methods}
+\subsection{Methods}\label{methods-1}
 
@@
 
-\subsection{Results}\label{results}
+\subsection{Results}\label{results-1}
 
@@
 Standard errors are clustered at the adviser
-level.}{\label{tbl-study1regs}}}\vspace{0pt}
+level.}{\label{tbl-study2regs}}}\vspace{0pt}
 }
@@
 colspec={Q[]Q[]Q[]},
-column{3}={}{halign=c,},
-column{1}={}{halign=l,},
-cell{2}{2}={}{halign=c,},
-cell{3}{2}={}{halign=c,},
-cell{4}{2}={}{halign=c,},
-cell{5}{2}={}{halign=c,},
-cell{6}{2}={}{halign=c,},
-cell{7}{2}={}{halign=c,},
-cell{8}{2}={}{halign=c,},
-cell{9}{2}={}{halign=c,},
-cell{10}{2}={}{halign=c,},
-cell{11}{2}={}{halign=c,},
-cell{12}{2}={}{halign=c,},
-cell{13}{2}={}{halign=c,},
-cell{1}{2}={c=2,}{halign=c, halign=c,},
-hline{13}={1,2,3}{solid, black, 0.05em},
+cell{1}{2}={c=2,}{halign=c,},
+column{1}={halign=l,},
+column{2}={halign=c,},
+column{3}={halign=c,},
+hline{13}={1,2,3}{solid, 0.05em, black},
 }                     %% tabularray inner close
@@
 competing against the High Performer Group and 0 if they recommend the
-Low Performer Group. In Column 1 of Table~\ref{tbl-study1regs}, we show
+Low Performer Group. In Column 1 of Table~\ref{tbl-study2regs}, we show
 our main specificiation with the experimental assignment for Advisees
@@
 the true performance of the advisee in Column 2 of
-Table~\ref{tbl-study1regs}. We observe a significant main effect of the
+Table~\ref{tbl-study2regs}. We observe a significant main effect of the
 default treatment, where a high default increased the likelihood of
@@
 
-\caption{\label{fig-study1Advice}Advice given in Study 1. Advisees who
+\caption{\label{fig-study2Advice}Advice given in Study 2. Advisees who
 were nudged to express high expectations were more likely to receive
@@
 
-\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-study1Advice-1.pdf}}
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-study2Advice-1.pdf}}
 
@@
 
-\subsection{Discussion}\label{discussion}
+\subsection{Discussion}\label{discussion-1}
 
@@
 competitors were more likely to receive flattering advice, encouraging
-them to pursue that option. This occurs even though advisers are
-incentivized to give good advice.
-
-\section{Study 2}\label{study-2}
-
-We next examine if advisers believe that flattering advice will improve
-how they are perceived, and if so, whether this perception is true. We
-do this by manipulating the incentives for advisers, who receive a bonus
-either based on how they are evaluated by an advisee, or a bonus for the
-advisee's accuracy.
-
-The study takes place in three stages. First, a group of advisees upload
-photos of themselves (``selfies'') and are grouped with nine other
-participants of the same sex. We then recruit participants of the
-opposing sex to rank them from most to least attractive and to provide
-advice. Specifically, they advise the participant they ranked as the 7th
-most attractive (i.e., 4th least attractive) on what rank they should
-bet they were ranked by a larger group of raters. Advisers were randomly
-assigned to two treatments, receiving a bonus payment either if the
-advisee guessed their rank accurately or if the advisee evaluated the
-adviser as likeable as measured by a scale response. We hypothesize that
-advisers incentivized to be liked will recommend betting on a lower
-rank, i.e.~that the advisee is more attractive.
-
-\subsection{Methods}\label{methods-1}
-
-We recruit 300 participants from Prolific and, after asking demographic
-questions, invite them to upload photos of themselves (selfies) to be
-rated by other participants on attractiveness. We obtain selfies from
-100 men and 107 women adhering to our instructions (e.g., did not
-include other people). In line with our preregistration, we select the
-first 100 photos from women to arrive at a gender-balanced sample
-(\(M_{\text{Age}}\) = 39.37 years). Participants are informed that their
-selfies will be randomly grouped with those of nine other participants
-of their sex and ranked in terms of attractiveness by a group of new
-Prolific participants of the opposite sex. They then make an
-unincentivized guess of their rank.
-
-Next, we recruit 472 participants from Prolific for the role of advisers
-(\(M_{\text{Age}}\) = 41.03 years; 49.79\% Female). We first collect
-demographic information, then match them to a group of the opposite sex.
-They rank selfies of ten participants from most to least attractive by
-entering their rankings into a text box next to each picture. Because of
-a limitation with the survey software, we could not validate that each
-rank is given only once, and we remove 115 participants who failed to
-follow instructions and did not provide a complete ranking.\footnote{Moreover,
-  we could not collect data from any participant who did not select any
-  participant as the 7th most attractive participant, as that image
-  would be shown on subsequent pages.}
-
-After submitting their ratings, participants see the photo of the
-participant they ranked as the 7th most attractive (i.e., the 4th least
-attractive). We remind them of the rank they have just given to that
-person and inform them that this participant will be invited back and
-can earn a \$1 bonus if they correctly guess their rank. The rank is
-determined by the aggregate ratings of all participants who have ranked
-this group. Because the participant does not observe the other nine
-people in the group, they would depend on the adviser's recommendation
-along with their own assessment. We randomly assign advisers to one of
-two incentivization schemes. In the ``Accuracy'' treatment, they receive
-a bonus identical to the advisee: \$1 if they guess their rank
-correctly. In the ``Likeability'' treatment, we inform them that the
-advisee will rate them on a 5-point Likert scale on how likeable they
-thought they are. Each point on the scale would translate to a bonus of
-20 cents. Advisers then select a rank (from 1 to 10) that they recommend
-the advisee to bet on.
-
-Finally, we invite participants from Stage 1 who were ranked as the 7th
-most attractive participant by at least one adviser (so that they
-received advice) back for the follow-up survey. Following our
-preregistration, we keep the survey open for 7 days. In total, 146
-participants (77 men, 69 women) complete the follow-up survey. We remind
-them of the selfie they uploaded in Stage 1 and that a group of 10
-selfies, including theirs, had been rated by other participants from
-Prolific. They then see the advice from a randomly selected adviser and
-make their own guess with a \$1 incentive for accuracy. Finally, they
-rate the adviser's likability, warmth, friendliness, good-naturedness,
-trustworthiness, and sincerity on 5-point Likert scales (adapted from
-Fiske et al., 2007).
-
-\subsection{Results}\label{results-1}
-
-\begin{figure}
-
-\caption{\label{fig-study2advice}Participants in Study 2 give advice to
-the person they rank 7th most attractive out of 10. When incentivized
-for accuracy, the majority recommends betting on that rank. However,
-when incentivized for likeability, participants inflate their advice to
-flatter the recipient as more attractive.}
-
-\centering{
-
-\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-study2advice-1.pdf}}
-
-}
-
-\end{figure}%
-
-We begin by examining the prior beliefs of advisees who uploaded their
-selfies. On average, men guess they rank 5.76 in their group of 10 and
-women guess that they rank 6.37 (\(t(205) = 2.15\), \(p = .033\)).
-Notably, people's self-perceptions correlate strongly with the aggregate
-ratings of the advisers (0.43, \(t(193) = 6.70\), \(p < .001\)).
-However, there is substantial heterogeneity in perceptions of
-attractiveness. Of the 200 participants, 149 are ranked as 7th most
-attractive by at least one adviser. On average, men in this subset
-estimate they rank 5.94th and women estimate they rank 6.59th
-(\(t(143) = 1.94\), \(p = .054\)).
-
-Next, we turn our attention to the advisers (see
-Figure~\ref{fig-study2advice}). In the Accuracy condition, those
-uploading selfies are on average advised to bet on rank 6.19. Notably,
-this is significantly more attractive than the 7th rank those advisers
-had themselves guessed just on the prior screen (\(t(234) = -8.82\),
-\(p < .001\)). This suggests that even when incentivized for accuracy,
-participants offer flattering advice.\footnote{This shading could be due
-  to concerns of avoiding disappointment. However, it could also be that
-  advisers are uncertain about the rankings they have given and make a
-  recommendation that combines their own belief with a uniform prior.
-  Therefore, our analyses focus on the difference between the two
-  conditions.} Importantly, and as predicted, we find that advisers in
-the Likeable treatment recommend betting on a lower rank, communicating
-that they think the participant in the selfie is more attractive (5.38,
-\(t(470) = 5.44\), \(p < .001\)). This suggests that advisers infer
-flattering someone with pleasant advice would make the adviser appear
-more likeable. The distribution shown in Figure~\ref{fig-study2advice}
-shows that participants do not simply tell participants that they are
-the most attractive person in the group. They may infer that flattering
-advise needs to be somewhat realistic to be believable. We return to
-this in the general discussion.
-
-\begin{table}
-
-{\caption{{When individuals receive advice that implies a high level of
-attractiveness (lower rank), they tend to perceive the advice giver as
-more likable (Column 1), warm (Column 2). Column 3 shows that advisors
-are rated as more trustworthy when they advice lower ranks, but this
-relationship is only directional.}{\label{tbl-study2regs}}}\vspace{0pt}
-}
-
-\centering
-\begin{talltblr}[         %% tabularray outer open
-entry=none,label=none,
-note{}={+ p \num{< 0.1}, * p \num{< 0.05}, ** p \num{< 0.01}, *** p \num{< 0.001}},
-]                     %% tabularray outer close
-{                     %% tabularray inner open
-colspec={Q[]Q[]Q[]Q[]},
-column{2,3,4}={}{halign=c,},
-column{1}={}{halign=l,},
-hline{6}={1,2,3,4}{solid, black, 0.05em},
-}                     %% tabularray inner close
-\toprule
-& (1) & (2) & (3) \\ \midrule %% TinyTableHeader
-Advised Rank & \num{-0.109}*  & \num{-0.133}** & \num{-0.054}   \\
-& (\num{0.046})  & (\num{0.044})  & (\num{0.042})  \\
-Constant     & \num{3.777}*** & \num{3.903}*** & \num{3.397}*** \\
-& (\num{0.279})  & (\num{0.266})  & (\num{0.257})  \\
-N            & \num{146}      & \num{146}      & \num{146}      \\
-\bottomrule
-\end{talltblr}
-
-\end{table}
-
-Finally, we examine whether flattering advice indeed leads to more
-positive evaluations of advisers, or whether flattering advice is
-dismissed as insencere. Following our preregistration, we average the
-ratings on likeability, warmth, friendliness, and good-naturedness to
-create a scale of likeability (\(\alpha\) = 0.92); and we create a scale
-of trustworthiness by averaging the ratings of trustworthiness and
-sincerity (\(\alpha\) = 0.87).
-
-\begin{figure}
-
-\caption{\label{fig-study2rating}Participants tend to rate advisors who
-suggest betting on a higher rank (implying greater attractiveness) as
-more likable and warm.}
-
-\centering{
-
-\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-study2rating-1.pdf}}
-
-}
-
-\end{figure}%
-
-\begin{figure}
-
-\caption{\label{fig-study2ratingByGroup}After participants receive
-advice that suggests betting on a rank that was lower than, equal to, or
-higher than their own guess, they evaluate advisors based on their
-likability and warmth. Participants rate advisors who give flattering
-advice and deliver a high evaluation of their attractiveness as more
-likable and warm than those whose advice implied a lower evaluation of
-their attractiveness.}
-
-\centering{
-
-\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-study2ratingByGroup-1.pdf}}
-
-}
-
-\end{figure}%
-
-As seen in Figure~\ref{fig-study2rating}, we advisers who suggested that
-the advisee was more attractive (lower rank) were indeed rated as more
-likeable and warm (b = -0.109, p \textless{} .05; b = -0.133, p
-\textless{} .001, respectively; See Columns 1 and 2 of
-Table~\ref{tbl-study2regs}). When using their own initial guess as a
-reference point, advisers who suggest a worse rank are perceived as less
-likable and warm (see Figure~\ref{fig-study2ratingByGroup}).
-Interestingly, these benefits are not at the cost of sincerity; advisers
-who recommend a more favorable rank are viewed as no less trustworthy
-(Column 3 of Table~\ref{tbl-study2regs}).
-
-We are not powered to do a comparison across the two experimental groups
-and did not preregister such a difference. Indeed, we find no difference
-in likeability and warmth across the two treatments (\(t(144) = 1.09\),
-\(p = .275\), and \(t(144) = 0.58\), \(p = .562\), respectively). We
-also assess the quality of advice by measuring the discrepancy between
-the advised rank and the correct rank. We find no difference in accuracy
-across the advice treatments (\(t(144) = -0.29\), \(p = .776\)).
-
-\subsection{Discussion}\label{discussion-1}
-
-In another context where advice communicates ego-relevant information
-(here, people's attractiveness), we find that the advice people give is
-contingent on their incentives. Specifically, when they get rewarded for
-being more likeable, they recommend that the advisee bet on a more
-favorable rank than when they are incentivized for accuracy.
-Importantly, advisees do not discount flattering advice and instead
-evaluate people who advise them to bet on a more attractive rank as
-warmer and more likeable. These gains to interpersonal perceptions do
-not come at the cost of trustworthiness, even when the advice is
-inflated.
+them to pursue that option. This occurs even though advisers share the
+potential costs of recommending a more challenging competition.
 
@@
 Performance group based on whether the advisees were primed with low or
-high expectations and the expectation level shown to the advisor. Column
+high expectations and the expectation level shown to the adviser. Column
 2 displays the advice given to compete against a High Performance group
 based on the gender of the targets and the expectation level shown to
-the advisor. Column 3 displays the expected bonus of the advice received
+the adviser. Column 3 displays the expected bonus of the advice received
 based on the gender of the targets and the expectation level shown to
-the advisor. All standard errors clustered at the level of the
-advisor.}{\label{tbl-study3regs}}}\vspace{0pt}
+the adviser. All standard errors clustered at the level of the
+adviser.}{\label{tbl-study3regs}}}\vspace{0pt}
 }
@@
 colspec={Q[]Q[]Q[]Q[]},
-column{2,3,4}={}{halign=c,},
-column{1}={}{halign=l,},
-hline{14}={1,2,3,4}{solid, black, 0.05em},
+column{1}={halign=l,},
+column{2}={halign=c,},
+column{3}={halign=c,},
+column{4}={halign=c,},
+hline{14}={1,2,3,4}{solid, 0.05em, black},
 }                     %% tabularray inner close
@@
 colspec={Q[]Q[]Q[]Q[]Q[]},
-column{2,3,4,5}={}{halign=c,},
-column{1}={}{halign=l,},
-hline{20}={1,2,3,4,5}{solid, black, 0.05em},
+column{1}={halign=l,},
+column{2}={halign=c,},
+column{3}={halign=c,},
+column{4}={halign=c,},
+column{5}={halign=c,},
+hline{20}={1,2,3,4,5}{solid, 0.05em, black},
 }                     %% tabularray inner close
@@
 told to aim higher. Notably, in the context of our experiment, this
-turns out to be bad advice ex post.
+turns out to lead to lower bonus compared to more conservative advice.
+While we focus on gender groups here, our findings may extend to other
+social groups where differences in expectations exist. This dynamic may
+create a reinforcing cycle --- individuals with higher confidence are
+more likely to receive encouragement and positive reinforcement, further
+boosting their confidence. In contrast, individuals with lower
+confidence have fewer opportunities to receive such encouragement,
+despite potentially needing it the most.
 
 Our findings have implications for organizational practice, where
-mentoring and advice-giving may take into account an employees'
-expectation. We document this as a novel source of gender bias.
-Organizations could reduce this bias by calibrating employees'
-expectations to reduce overconfidence.
-
-Participants in our experiment were paired anonymously. Even so, we
-document this desire to avoid disappointment. We anticipate that advice
-would be more flattering in face-to-face communication and without
-anonymity. Moreover, existing relationships might make it even more
-difficult for advisers to be honest.
+mentoring and advice-giving often consider employees' expectations. On
+one hand, offering flattering advice may enhance relationships between
+mentors and mentees, enhancing trust and communication, which are
+crucial for collaboration and long-term organizational success. However,
+flattering advice may also lead to talent misallocation, as employees
+are more likely to be encouraged to pursue career paths aligned with
+their stated preferences and less likely to be recommended to explore
+alternative directions that might better match their potential.
+Additionally, when advisers hold significantly more power than advisees,
+interpersonal concerns may diminish (Schaerer et al., 2018), resulting
+in advice that is more blunt or even harsh. As a result, advisees may
+seek flattering advice from peers or subordinates instead, missing out
+on valuable expertise from their supervisors. Lastly, we identify
+flattering advice as a novel source of gender bias, as women may receive
+less ambitious advice due to lower expressed confidence. Organizations
+could reduce this bias by calibrating employees' expectations to curb
+overconfidence and/or compensate for a lack of confidence.
+
+Participants in our experiment were paired online and remained
+anonymous. Even so, we document this desire to avoid disappointment.
+Given that communications mediated by computer tends to be less
+emotionally rich (Kiesler et al., 1985), and that anonymity reduces the
+psychological burden of responsibility for the advisee's feelings, as it
+cannot be traced back to the adviser. We anticipate that advice would be
+more flattering in face-to-face communication and without anonymity.
+
+Moreover, existing relationships might make it even harder for advisers
+to be fully honest. Advisers tend to feel more concerned and emotionally
+attached to how friends, family, or colleagues feel compared to how a
+stranger would feel, which may increase their motivation to provide
+flattering advice. Conversetly, advisees also tend to value the
+emotional support embedded in advice from their friends, even when it
+lacks informational utility. Moreover, people generally prefer their
+close ones to demonstrate benevolence toward them rather than apply
+impartial integrity during interactions (Levine et al., 2020). In
+response to these expectations, advisers might intentionally inflate
+their advice to strengthen their bond with the advisee and protect them
+from discomfort.
+
+The closeness of the relationship may moderate the tendency to provide
+flattering advice. On one hand, advisers may prioritize the advisee's
+best interests above other considerations when offering advice to
+someone they have a close and strong relationship with, making them more
+willing to provide the most helpful advice, even if it is unflattering.
+Advisers may also feel more confident that a close relationship is
+resilient enough to withstand any immediate disappointment the advisee
+may experience if the advice falls short of their self-expectations. On
+the other hand, closer relationships may also strengthed the adviser's
+motivation to protect the advisee's feelings, increasing the likelihood
+of offering flattering advice. Future research could explore how
+relationship closeness influences the balance between providing
+flattering versus candid advice.
 
@@
 
-Advice has long been studied from the perspective of the receiver.
-Similarly, research on belief utility has examined how recipients
-respond to the valence of the information they receive. Here, we show
-that advisers, too, take into account the psychological impact of the
-information they convey. They may have even greater motivations to avoid
-conveying bad news, because they incur the interpersonal costs of
-delivering unfavorable information without reaping the benefits from
+Advice has long been studied from the perspective of the receiver
+(Bonaccio \& Dalal, 2006; Milyavsky \& Gvili, 2024; Rader et al., 2017;
+Yaniv, 2004). Similarly, research on belief utility has examined how
+recipients respond to the valence of the information they receive. Here,
+we show that advisers, too, take into account the psychological impact
+of the information they convey. They may have even greater motivations
+to avoid conveying bad news, because they incur the interpersonal costs
+of delivering unfavorable information without reaping the benefits from
 helping someone make a better choice.
@@
 
+\bibitem[\citeproctext]{ref-bonaccio2006Review}
+Bonaccio, S., \& Dalal, R. S. (2006). Advice taking and decision-making:
+An integrative literature review, and implications for the
+organizational sciences. \emph{Organizational Behavior and Human
+Decision Processes}, \emph{101}(2), 127--151.
+
 \bibitem[\citeproctext]{ref-Chang2019}
@@
 
+\bibitem[\citeproctext]{ref-Haran2020}
+Haran, U., \& Shalvi, S. (2020). The implicit honesty premium: Why
+honest advice is more persuasive than highly informed advice.
+\emph{Journal of Experimental Psychology: General}, \emph{149}(4), 757.
+
 \bibitem[\citeproctext]{ref-Harvey1997}
@@
 
+\bibitem[\citeproctext]{ref-Jussim1986}
+Jussim, L. (1986). Self-fulfilling prophecies: A theoretical and
+integrative review. \emph{Psychological Review}, \emph{93}(4), 429.
+
 \bibitem[\citeproctext]{ref-Kanze2018}
@@
 
+\bibitem[\citeproctext]{ref-Kiesler1985}
+Kiesler, S., Sproull, L., \& Eccles, J. S. (1985). Pool halls, chips,
+and war games: Women in the culture of computing. \emph{Psychology of
+Women Quarterly}, \emph{9}(4), 451--462.
+
+\bibitem[\citeproctext]{ref-Kluger1996}
+Kluger, A. N., \& DeNisi, A. (1996). The effects of feedback
+interventions on performance: A historical review, a meta-analysis, and
+a preliminary feedback intervention theory. \emph{Psychological
+Bulletin}, \emph{119}(2), 254.
+
 \bibitem[\citeproctext]{ref-Koszegi2006}
@@
 
+\bibitem[\citeproctext]{ref-Locke2006}
+Locke, E. A., \& Latham, G. P. (2006). New directions in goal-setting
+theory. \emph{Current Directions in Psychological Science},
+\emph{15}(5), 265--268.
+
 \bibitem[\citeproctext]{ref-Loewenstein2018}
@@
 166--167.
+
+\bibitem[\citeproctext]{ref-Lundeberg1994}
+Lundeberg, M. A., Fox, P. W., \& Punćcohaŕ, J. (1994). Highly confident
+but wrong: Gender differences and similarities in confidence judgments.
+\emph{Journal of Educational Psychology}, \emph{86}(1), 114.
+
+\bibitem[\citeproctext]{ref-Mackinger2017}
+Mackinger, B., Jonas, E., \& Mühlberger, C. (2017). When advisors' true
+intentions are in question. How do bank customers cope with uncertainty
+in financial consultancies? \emph{Frontiers in Psychology}, \emph{8},
+1112.
+
+\bibitem[\citeproctext]{ref-Milyavsky2024}
+Milyavsky, M., \& Gvili, Y. (2024). Advice taking vs. Combining
+opinions: Framing social information as advice increases source's
+perceived helping intentions, trust, and influence. \emph{Organizational
+Behavior and Human Decision Processes}, \emph{183}, 104328.
 
@@
 
+\bibitem[\citeproctext]{ref-Palmeira2015}
+Palmeira, M., Spassova, G., \& Keh, H. T. (2015). Other-serving bias in
+advice-taking: When advisors receive more credit than blame.
+\emph{Organizational Behavior and Human Decision Processes}, \emph{130},
+13--25.
+
 \bibitem[\citeproctext]{ref-Paluck2009}
@@
 
+\bibitem[\citeproctext]{ref-Trouche2018}
+Trouche, E., Johansson, P., Hall, L., \& Mercier, H. (2018). Vigilant
+conservatism in evaluating communicated information. \emph{PloS One},
+\emph{13}(1), e0188825.
+
 \bibitem[\citeproctext]{ref-Van2009}
@@
 857--873.
+
+\bibitem[\citeproctext]{ref-Weiner1985}
+Weiner, B. (1985). An attributional theory of achievement motivation and
+emotion. \emph{Psychological Review}, \emph{92}(4), 548.
+
+\bibitem[\citeproctext]{ref-yaniv2004receiving}
+Yaniv, I. (2004). Receiving other people{'}s advice: Influence and
+benefit. \emph{Organizational Behavior and Human Decision Processes},
+\emph{93}(1), 1--13.
 
@@
 
+\bibitem[\citeproctext]{ref-Yoon2021}
+Yoon, H., Scopelliti, I., \& Morewedge, C. K. (2021). Decision making
+can be improved through observational learning. \emph{Organizational
+Behavior and Human Decision Processes}, \emph{162}, 155--188.
+
+\bibitem[\citeproctext]{ref-Zhang2012}
+Zhang, Y., \& Epley, N. (2012). Exaggerated, mispredicted, and
+misplaced: When {``it's the thought that counts''} in gift exchanges.
+\emph{Journal of Experimental Psychology: General}, \emph{141}(4), 667.
+
 \end{CSLReferences}

### 2025-04-06 manuscript/manuscript.qmd
Revised abstract

@@
     # gratitude: The authors are grateful to XXX for their helpful comments.
-abstract: Advice that improves decision-making does not always feel good.
-While advice has the potential to improve decision-making by helping advisees more accurately assess feasibility and predict potential outcomes, it can also lead to disappointment when it challenges the advisee’s overly optimistic expectations.
-Across three pre-registered and incentivized experiments involving real adviser-advisee interactions (N = 3,900), we show that advisers prioritize avoiding disappointment at the expense of accuracy and their own earnings.
-In study 1, advisers use flattering advice to create more positive impressions, and advisees reward this by rating these advisers as more likable, despite the advice being less honest and less accurate.
-Even advisers incentivised for accuracy still tailor recommendations to aspirational goals expressed by advisees, resulting in financial loss for them and the advisees (Study 2).
-The concern for interpersonal consequences may lead to inequities if there are differences in expectations across social groups.
-In Study 3, we examine a setting in which men expect to perform better than women.
-We show that advisers take into account these expectations, leading to systematically different advice for men and women even when their gender is unknown to advisers.
-Advisers' efforts to avoid disappointment may thus contribute to systematic gender disparities in advice, with implications for downstream decision-making.
-
-keywords: [Advice, Interpresonal relationship, Gender difference]
+abstract: Advice can improve decisions when it offers an unbiased evaluation of information, but the painful truth can disappoint an advisee's overoptimistic expectations.
+Across three pre-registered and incentivized experiments involving real adviser-advisee interactions (N = 3,900), we show that advisers avoid such disappointment at the expense of accuracy and their own earnings.
+Participants inflate the attractiveness of advisees and do so to a greater extent when incentivized to be viewed as likeable.
+Advisers who provide flattering advice are rated as more likable and trustworthy, even as their advice is less honest and accurate (Study 1).
+When advisers observe an advisee's quiz performance along with a signal expressing a preference for competing against a group of low or higher performers, the (uninformative) signal influences their advice (Study 2).
+Finally, in a context where men expect to do better than women, advisers who observe expectations (but not gender) on top of actual performance are more likely to tell men to enter a tougher (but potentially more rewarding) competition.
+Advisers' efforts to avoid disappointment may thus contribute to systematic gender disparities in advice.
+
+keywords: [advice, belief-based utility, interpersonal relationships, gender, discrimination]
 bibliography: bibliography.bib

### 2025-04-06 manuscript/manuscript.qmd
Revised introduction

@@
     # gratitude: The authors are grateful to XXX for their helpful comments.
-abstract: Advice can improve decisions when it offers an unbiased evaluation of information, but the painful truth can disappoint an advisee's overoptimistic expectations.
-Across three pre-registered and incentivized experiments involving real adviser-advisee interactions (N = 3,900), we show that advisers avoid such disappointment at the expense of accuracy and their own earnings.
+abstract: Advice can improve decisions when it offers an unbiased evaluation of information, but the painful truth can disappoint an advisee's expectations.
+Across three pre-registered and incentivized experiments involving real adviser-advisee interactions (N = 3,900), we show that advisers avoid delivering such disappointment at the expense of accuracy and their own earnings.
 Participants inflate the attractiveness of advisees and do so to a greater extent when incentivized to be viewed as likeable.
-Advisers who provide flattering advice are rated as more likable and trustworthy, even as their advice is less honest and accurate (Study 1).
-When advisers observe an advisee's quiz performance along with a signal expressing a preference for competing against a group of low or higher performers, the (uninformative) signal influences their advice (Study 2).
+Advisers who provide flattering advice are indeed rated as more likable and trustworthy, even as their advice is less honest and accurate (Study 1).
+When advisers observe an advisee's quiz performance along with a signal expressing a preference for competing against a group of low or higher performers, the (uninformative) signal influences the advice they give (Study 2).
 Finally, in a context where men expect to do better than women, advisers who observe expectations (but not gender) on top of actual performance are more likely to tell men to enter a tougher (but potentially more rewarding) competition.
-Advisers' efforts to avoid disappointment may thus contribute to systematic gender disparities in advice.
+Advisers' efforts to avoid disappointment may thus contribute to systematic gender disparities in advice and outcomes.
 
@@
 
-Advice figures prominently in workplace and personal decision-making,
-shaping choices about promotions, career paths, and everyday dilemmas
-[@Gino2007; @Harvey1997; @Soll2009]. While others can provide
-information in the form of opinions [@Trouche2018], feedback
-[@Kluger1996], or personal observations [@Yoon2021] to influence the
-decision-maker, this project focuses specifically on advice—defined as
-"information that is perceived as intended to help an advisee deal with
-their issue of deliberation" [@Milyavsky2024]. Advice is distinct from
-other forms of input because its primary purpose is to improve
-decision-making by leveraging others' expertise.
-
-Advice has the power to enhance decisions, yet it also carries the risk
-of disappointment. For example, a career consultant might advise an
-employee to enroll in a management program to strengthen their skill set
-before competing for a leadership role. Ideally, such honest advice
-helps the employee identify areas for personal growth. In practice,
-however, the employee might feel overlooked and frustrated that their
-ambitions are not immediately supported. As a result, advisers may be
-inclined to offer flattering recommendations that align with—or even
-exceed—advisees' hopes, such as encouraging the employee to pursue the
-leadership role despite concerns about their readiness. In this way,
-interpersonal dynamics may discourage full candor in giving advice.
+Advice figures prominently in professional and personal life,
+shaping choices about career paths, promotions, and everyday dilemmas
+[@Gino2007; @Harvey1997; @Soll2009].
+An extensive body of research has examined the behavior and beliefs of those
+receiving advice, including how willing they are to seek advice [@Heikensten2019], 
+whom they want to get advice from [@Hur2020], and how much they revise their beliefs 
+in response to advice [@Bailey2023].
+In this paper, we shift the focus to the behavior of advisers. Prior work 
+assumes that they (absent conflicts of interest) are motivated 
+to help someone else make a better decision, even defining advice as being 
+intended to help another decision-maker [@Milyavsky2024 -- David Q: is this a right interpretation of the previous quote here?].
+We propose that advisers are not merely concerned about the outcome of the action
+they recommend, however, but also consider the hedonic impact of the advice itself.
+Across three experiments, we show that advisers are responsive to the expectations
+of an advisee and tailor their recommendations to avoid disappointing them,
+even when doing so leads to worse advice and is costly for both parties.
+
+In many situations, people turn to those who are better informed to advise them
+on what actions to take. For example, an employee may discuss career
+opportunities with a supervisor or mentor to see if they should apply for a
+promotion or take on a risky project. Ideally, they would receive an unbiased
+assessment based on the adviser's experience and impression of the advice-seeker,
+taking into account the potential costs (e.g., opportunity costs) and benefits
+(e.g., promotion chances and compensation). Indeed, in an experimental context, 
+advisers are helpful in encouraging
+high-performers to enter competitions and discouraging low-performers from doing so
+[@Brandts2015]. However, people often reveal their expectations along with a
+request for advice. For example, someone may express a desire to take on more
+challenging projects before asking for advice on whether to do so. In such cases,
+honest advice may discourage someone from an action they intended to take,
+frustrating and disappointing them in the process. An adviser who is concerned
+about the hedonic impact of information on the recipient, for example because
+they recognize the psychological cost of disappointment [@Gul1991; @Golman2017]
+or do not want to be blamed for delivering bad news [@John2019], 
+may give advice that makes the recipient feel good in the moment, even if they 
+expect it to lead to a bad outcome. We refer to such advice as "flattering"
+because it communicates a more favorable belief about the recipient than the
+sender in fact holds.
+
+In the workplace, prior research has documented stark gender differences in what
+kind of advice employees receive. In particular, men receive more critical 
+performance feedback than women, which although
+painful in the moment, facilitates learning and leads to better performance
+in the future (CITE). While such differences
+are often attributed to unconscious biases, we propose that avoiding disappointment
+may be another, belief-based contributing factor. Prior work has found that
+men are more confident in their performance than equally well-performing
+women [@Exley2024; @Lundeberg1994; @Mobius2022]. As a result,
+women are less likely to enter into competitions and less likely to apply for 
+more challenging (but better compensated) work [@Niederle2007; @Coffman2024].
+We propose that in addition to self-selection, confidence may also impact the
+advice men and women receive. An adviser who is motivated to avoid disappointment
+will take into account how someone *expects* to perform, even when they are
+fully informed about how that individual *actually* performs. Thus, people
+who are more (over)confident receive more flattering advice, leading to gender
+differences driven by differences in expectations.
+
+We present results from three preregistered and incentivized experiments involving
+advisers and advisees. Each study consists of three asynchronous stages with a group of
+participants performing an initial task, a second group of participants providing
+advice, and the original participants returning to receive the advice and make
+a decision. Advisers have a financial incentive for the advisee to make a good
+decision, except in one treatment in Study 1 where they are incentivized to be
+viewed as likeable.
+
+In the first study, participants upload photos of themselves and
+are matched with nine other participants of the same gender. A new group of
+participants of the opposite gender then rank the selfies and provide advice
+to one participant (whom they ranked low on attractiveness) on what rank they
+should bet on. The original participants return, receive advice, bet on
+how attractive other participants ranked them, and evaluate the adviser on
+measures such as likeability and trustworthiness. Advisers who receive an
+incentive for being rated as likeable advise the other participant to bet that
+they are more attractive, relative to those incentivized for accuracy and relative
+to their own assessment. Advisees, moreover, evaluate those who flatter them as
+more likeable and more trustworthy, even as they receive less honest and less
+accurate advice.
+
+In Study 2, participants complete a quiz assessing different personally relevant
+skills (problem-solving,
+emotional intelligence, and communications) and make a non-binding decision about
+whether they would like to compete against a group that did well on this quiz
+or a group that did poorly. Competing against high performers offers the opportunity
+of a higher payment, but requires a higher score. We randomly assign participants
+to have one of the two groups selected by default. Advisers then observe a
+participant's real score on the quiz and, in one treatment, also which of the
+two groups they had selected. We show that participants' random assignment to
+a default influences the advice they receive when their choice (but not the
+random assignment) is visible.
+
+Finally, we look at a setting in which we expect gender differences in confidence.
+Participants complete a mathematics quiz and make an (unincentivized) guess about
+their score. Advisers then observe the actual quiz score and, in one treatment,
+also the unincentivized guess. They then advise the participant whether to
+compete against a group of high performers or a group of low performers. As 
+expected, men are more confident in their performance than are women, holding
+fixed their actual performance. Importantly, we show that when participants' 
+guesses are shown to advisers, men are more likely than women to be advised to
+compete against the strong group.
+
+The remainder of this paper is organized as follows. Section 2 provides an
+overview of the literature on advice and disappointment aversion. Section 3
+presents results from three preregistered and incentivized experiments
+involving adviser-advisee pairs. Section 4 concludes.
+
+# Literature Review
 
@@
 
-# Overview of studies
+## Disappointment Aversion
+Information, including advice, has traditionally been seen as valuable when 
+(and to the extent that) it leads to better decisions [@Stigler1961]. However, 
+even information that is available at no economic cost can be unpleasant and 
+thus impose a psychological cost [@Golman2017; @Ho2021; @Loewenstein2018]. One reason
+for why information can be painful to receive is because it leads to disappointment
+[@Gul1991]. Disappointment is costly if it suggests that a desired outcome is
+not realized, but also because it provides information about future consumption
+[@Koszegi2010]. Someone receiving advice against applying for a promotion, for
+example, would not only learn that they are not as competitive as they had
+believed, but also has to update their beliefs about their future income stream.
+
+@Bell1985 shows that disappointment aversion implies providing good news
+immediately, but breaking bad news piecewise to adjust expectations---and 
+observes that this is indeed how people inform others. Notably, this is assuming
+delivering the bad news is unavoidable. In the context of advice, however,
+people can elect not to deliver the bad news at all and instead shade their
+evaluation to meet expectations and flatter the recipient.
+
+## Gender Differences in Advice and Expectations
+
+[A few sentences summarizing the literature review and tying it closely to the experiments.]
+
+# Experiments
 
@@
 
-# Open Science Statement
+## Open Science Statement
 
@@
 
-# Study 1
+## Study 1
 
@@
 
-## Methods
+### Methods
 
@@
 
-## Results
+### Results
 
@@
 
-## Discussion
+### Discussion
 
@@
 
-# Study 2
+## Study 2
 
@@
 
-# Study 3
+## Study 3
 
@@
 
-# General Discussion
+# Discussion
 
